### 2020-10-01 manuscript.Rmd
#4 add manuscript.Rmd

---
title: "Recruiting Chapter"
author: "Ozan Jaquette"
bibliography: ./other/spencer-bib.bib
output: pdf_document
csl: ./other/apa.csl
urlcolor: blue
---

# Introduction

@RN5659 found that this is true. Here's an example of parenthetical citation [@RN4552]. More info in this [documentation](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).

# References

### 2020-10-01 manuscript.Rmd
started draft manuscript

@@
 author: "Ozan Jaquette"
-bibliography: ./other/spencer-bib.bib
+bibliography: ./other/burd_recruiting_chapter.bib
 output: pdf_document
@@
 
+```{r setup, include=FALSE}
+library(knitr)
+
+```
+
 # Introduction
 
-@RN5659 found that this is true. Here's an example of parenthetical citation [@RN4552]. More info in this [documentation](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).
+When we contrast research about enrollment management to descriptions of enrollment management practice, from investigative journalists or from consulting firms [cite], it becomes apparent that the research community is decades behind practice and has ignored a great number of enrollment management practices that affect access to higher education.
+Thus, the enrollment management remains an opaque industry to researchers and, in turn, to policymakers and the public.
+Developing thoughtful state and federal policies about enrollment management depends on researchers doing the slow, methodical work of developing an empirical literature that documents enrollment management practices and evaluates their effect on opportunities for students.
+
+The "enrollment funnel," a conceptual heuristic used by the enrollment management industry and shown in figure X, is helpful for framing the development of this empirical literature.
+The enrollment funnel describes the stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, enrolled) in order to inform targeted recruiting interventions.
+The majority of research on enrollment management focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees.<!-- [@RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948] -->By contrast, the enrollment management industry expends substantial resources on earlier stages of the funnel [@RN4664].
+“Prospects” are “all the potential students you would want to attract to your institution” [@RN4322].
+“Inquiries” are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own.
+
+Table X shows the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.
+^[table drawn directly from @RN4664 figure 9; based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions].
+Institutions identify undergradaute prospects largely by purchasing "student lists" from College Board, ACT, and other vendors.
+Table X indicates that private and public institutions spent 14% and 12%, respectively, of their undergraduate recruitment budget on student list purchases.
+Institutions utilize digital advertising, traditional advertising, and social media to solicit inquiries and to create positive "buzz" amongst potential stealth applicants [@RN4411][CITE OTHER].
+<!-- Table X indicates that...
+[summarize expenditure on stuff related to soliciting inquiries once you figure out answers to below questions] -->  Once identified, prospects/inquiries are targeted with face-to-face and remote recruiting interventions designed to solit applications and deepen engagement.
+Remote recruiting interventions include postcards, brochures, email, and text messages.
+<!-- Table X indicates that these "prospective student communications" account for 13% of the recruiting budget at private institutions and 17% of the budget at public institutions.
+-->Face-to-face recruiting interventions include on-campus visits (12% and 11% of budget, respectively, at private and public institutions) and off-campus recruiting events, often referred to as "travel" (17% and 16% of budget, respectively, at private and public institutions).
+<!-- QUESTIONS ABOUT THE RNL 2020 COST OF RECRUITING AN UNDERGRADUATE STUDENT REPORT, FIGURE 9
+
+What does "recruitment publications" include?
+what does "prospective student communications" include?
+what does "event" include? can I assume this is on-campus events only cuz "travel" is a separate category?
+what does "web services and digital advertising" include? Does this include social media?
+-->
+Having identified prominent marketing and recruiting activities (e.g., student list purchases, digital advertising, off-campus recruiting visits), why have so few researchers studied higher education marketing and recruitng?
+One challenge is that empirical research depends on data but obtaining concrete data about marketing and recruiting behaviors is difficult, especially for conventional data collection methods like surveys and interviews.
+Thus, empirical research requires different approaches to data collection, including public records requests and "data science" methodologies, such as web-scraping and streaming social media data.
+
+This chapter analyzes off-campus recruiting visits made in 2017 by a sample of public research universities and a sample of selective private colleges and universities.
+We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") from admissions websites.
+Pages were scraped once per week for the entire 2017 calendar year.
+In addition, for the sample of public research universities, we also issued public records requests.
+
+To date, our analyses have focused on recruiting visits by public research universities.
+As described below, the majority of public universities in our sample made far more out-of-state visits than in-state visits.
+These out-of-state visits focused on wealthy, predominantly white communities, with a disproportionate number of visits to private high schools.
+This chapter analyzes visits to private high schools.
+Using social network methods, we analyze visits by private colleges and universities to private high schools, visits by public research universities to private high schools, and then compare similarities and differences between public and private postsecondary institutions [as a means of saying something about "privatization"?]
+
+# What Do We Know About Off-campus Recruiting?
+
+PARAGARPH SAYING HARD TO GET DATA ON RECRUITING BEHAVIOR
+
+Empirical research depends on data but obtaining data about marketing and recruiting behaviors is difficult, at least through conventional data collection methods such as surveys and interviews.
+
+PARAGRAPH SAYING WHAT WE DID TO OBTAIN DATA ON OFF-CAMPUS RECRUITNG
+
+@RN5659 found that this is true. Here's an example of parenthetical citation [@RN4552].
+
+![The enrollment funnel](assets/images/enrollment_funnel.png)
+
+```{r, echo=FALSE}
+pct_budget <- data.frame(
+  activity = c("Travel","Student search (purchased lists)","Prospective student communications","Events","Recruitment publications","Web services and digital advertising","Traditional advertising","International recruitment","Transfer recruitment","Other"),
+  private = c(17,14,13,12,11,11,6,5,4,8),
+  public = c(16,12,17,11,15,13,6,3,4,3)
+)
+
+#pct_budget
+#str(pct_budget)
+#attributes(pct_budget)
+kable(
+  x = pct_budget, 
+  col.names = c("Activity", "Private", "Public"),
+  caption = "Percentage of budget allocated to marketing/recruiting activities by private non-profit 4yr and public 4yr institutions"
+)
+# 
+```
+
+More info in this [documentation](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).
 

### 2020-10-05 manuscript.Rmd
draft changes front end manuscript

@@
 
-When we contrast research about enrollment management to descriptions of enrollment management practice, from investigative journalists or from consulting firms [cite], it becomes apparent that the research community is decades behind practice and has ignored a great number of enrollment management practices that affect access to higher education.
+We present this chapter as one example of empirical research about enrollment management behavior.
+When we contrast research about enrollment management to descriptions of enrollment management practice, from investigative journalists or from consulting firms [cite], it becomes apparent that the research community is decades behind practice and has ignored a great number of enrollment management practices that affect access to higher education [AN EXCEPTION TO THE CRITIQUE IS A SMALL BUT HIGH-QUALITY CASE STUDY LITERATURE FROM SOCIOLOGY].
 Thus, the enrollment management remains an opaque industry to researchers and, in turn, to policymakers and the public.
 Developing thoughtful state and federal policies about enrollment management depends on researchers doing the slow, methodical work of developing an empirical literature that documents enrollment management practices and evaluates their effect on opportunities for students.
+[TONE DOWN THE CRITIQUE; DON'T WANT TO MAKE IT SEEM LIKE WE THINK WE ARE THE FIRST TO STUDY THIS STUFF; GIVE CREDIT TO THE EXCELLENT CASE STUDY RESEARCH]
 
@@
 
+[REVISE BELOW PARAGRAPH TO TAKE OUT MOST OF THE NUMBERS OF PERCENT SPENT ON EACH ACTIVITY; BOGS DOWN THE PROSE; MAIN POINT IS HIGHLIGHTING THE ACTIVITIES THAT TARGET SPECIFIC ELEMENTS OF THE FUNNEL; READER CAN READ THE PERCENTAGES ON THEIR OWN]
 Table X shows the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.
@@
 Using social network methods, we analyze visits by private colleges and universities to private high schools, visits by public research universities to private high schools, and then compare similarities and differences between public and private postsecondary institutions [as a means of saying something about "privatization"?]
+[MOTIVATE PARTICULAR FOCUS OF THIS CHAPTER: NETWORK ANALYSIS OF VISITS TO PRIVATE HIGH SCHOOLS BY BOTH PUBLIC AND PRIVATE COLLEGES/UNIVERSITIES]
 
@@
 
-PARAGARPH SAYING HARD TO GET DATA ON RECRUITING BEHAVIOR
+Our research analyzes off-campus recruiting visits by college and university admissions staff.
+So what do we know about off-campus recruiting?
+As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practioner-oriented publications.
+Market research conceives of off-campus recruiting visits as a means of identifying prospects, deepening engagement with prospects already being targeted through mail/email, and maintaining relationships with guidance counselors at “feeder schools” [@RN4323; @RN4402; @RN4664].
+With respect to expenditure, @RN4664 found that private (non-profit) 4-yr institutions spent an average of 17% of their undergraduate marketing/recruiting budget on "travel" to high schools and college fairs (as shown in Table X), a higher percentage of budget allocation than any other marketing/recruiting activity.
+Public institutions spent an average of 16% of their budget on travel, second only to "prospective student communications" at 17%.
+An emergent trend over the past decade -- partially a response to public universities seeking nonresident students -- has been the growth of "regional recruiters" who target specific metropolitan areas in the US and abroad.
+These regional recruiters may be college/university employees or they may be independent contractors who live in the metropolitan area they recruit.
 
-Empirical research depends on data but obtaining data about marketing and recruiting behaviors is difficult, at least through conventional data collection methods such as surveys and interviews.
+@RN4402 documents the self-reported efficacy of marketing/recruiting interventions.
+For the median private 4-yr institution, off-campus visits were the second highest source of inquiries (after student list purchases), accounting for 17% of inquiries.
+Off-campus visits were tied with student list purchases as the highest source of enrollees, accounting for 18% of enrollees.
+For the median public institution, off-campus visits accounted for 19% of inquiries (second only to student list purchases) and accounted for 16% of enrollees (ranked third after stealth applicants and on-campus visits).
 
-PARAGRAPH SAYING WHAT WE DID TO OBTAIN DATA ON OFF-CAMPUS RECRUITNG
+A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits.
+@RN4324 analyzes visits from the perspective of students at two racially and socioeconomically diverse public high schools.
+@RN4324 found that high school visits -- including college fairs, instant decision events, and small-group representative visits -- influenced where students applied and where they enrolled.
+This finding was strongest for first-generation students and under-represented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college." This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and "made them feel wanted."  @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more." By contrast, affluent students with college educated parents were less taken by such overtures and more concerned with college prestige.
 
-@RN5659 found that this is true. Here's an example of parenthetical citation [@RN4552].
+Of particular importance for this chapter, @RN3519 and @RN4321;@RN4407 highlight the relational function of visits.
+@RN3519 provides an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of visits.
+During the autumn "travel season," admissions officers visited selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
+53-54) because "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide" {@RN3519} [p.
+54].
+The College tended to visit the same schools year after year because recruiting depends on long-term relationships with high schools.
+The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and had the resources and motivation to host a successful visit.
+Whereas @RN4402 highlights the effect of recruiting visits on inquiries and enrollees, findings from @RN3519 suggest that the College may have valued recruiting visits primarily as a means of maintaining relationships with guidance counselors.
+From this perspective, recruiting visits may affect outcomes such as inquiries, applications, and matriculation through their affect on high school guidance counselors.
+The logic is that a guidance counselor who views a college favorably will steer students to the college.
+
+@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities." The answer to this question begins by thinking about the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors.
+Colleges want high achieving students who can pay tuition and donate.
+Additionally, drawing from @@RN3519, colleges want a class composed of "interesting characters" whose curricular and extracurricular strengths meet the needs of different campus constituents (e.g., academic majors, the athletic department, clubs, etc.).
+Colleges also want low acceptance and high yield rates to move up the rankings.
+Private high schools want to send _all_ students to the best college possible.
+Here, high school guidance counselors face "the pressure of making sure their school seems worth it – that...paying some $40,000+, really does aid students in the college process" [FROM CHAPTER.
+FIND PG NUMBER]  The challenge counselors face is "some of these students are slightly better than others.
+These students will likely get into more than one school -- but they can only attend one.
+And this will lower the chances of your "second-best" students getting into top schools" [@RN4407] [p.
+173-174].
+
+"Luckily," @RN4321 [pg.
+xx] writes, "the problem for elite boarding schools matches up quite nicely with the problem faced by elite colleges." Specifically, college admissions officers receive applications from many outstanding students.
+But "These outstanding students will also be outstanding to Princeton, Yale, Stanford, and everywhere else.
+How do you know the ones you pick will attend your school?
+you can't quite trust applicants, as they are all likely to tell you how much they want to go to your school.
+And if students you accept go somewhere else, there's not much you can do.
+But you can get better information -- information you want -- from their high school" [@RN4407] [pg.
+173?].
+
+@RN4407 argues that the desire by colleges for trustworthy information about applicant intentions creates an opportunity for high school counselors to advocate on behalf of their students.
+This opportunity depends on guidance counselors having personal relationships with university admissions offices and on having small enough caseloads to advocate for each student individually.
+To explain how the process works, @RN4407 describes two hypothetical students -- Susan and Billy -- who both apply to Harvard and Yale.
+Susan is a shoo-in at both universities, but wants to attend Harvard.
+Billy has a weaker academic record than most Ivy League students, but has strong extracurricular activities.
+The guidance counselor tells Harvard that Susan wants to attend Harvard.
+Next, he informs Yale that Susan will choose Harvard, but Billy loves Yale and has great "character" and extracurricular activities.
+In the end, Harvard rejects Billy and accepts Susan (decreasing acceptance rate, increasing yield).
+Yale rejects Susan and accepts Billy (decreasing acceptance rate, increasing yield).
+
+The horsetrading described by @RN4407 depends on a relationship where the college can trust statements made by the high school counselor and vice-versa.
+This relationship is the product of repeated interactions over many years.
+@RN4407 writes that colleges "can reward that [high] school for good information and sanction it for bad information" [p.
+173].
+A high school that makes false statements about applicant intentions faces consequences.
+The college "might stop taking these telephone calls and ignore the information provided.
+They may even start accepting fewer students from the school, thinking it is less than an honest place." [CITE BOOK CHAPTER; PG NUMBER].
+Because the college and the high school are mutually dependent, however, both "have an incentive to continue with a strong, honest relationship" [CITE BOOK CHAPTER; PG NUMBER].
+Such horsetrading may be less pervasive than now than it was in prior decades, less common at non-elite private schools, and also public university admissions officers likely have less authority to engage in these tacit negotiations.
+
+Nevertheless, maintaining a strong relationships is mutually important for the college and the high school.
+Both the college admissions counselor and the high school guidance counselor need to tell one another "their story" and relay that story to constituents.
+The college admissions counselor explains why the college/university is a "special place" that high school students should want to attend.
+The guidance counselor explains why the high school is a special place, that even students with lower grades have outstanding extracurricular strengths that will benefit the college.
+[CITES FOR THIS PARAGRAPH]
+
+Circling back to the focus of this chapter, off-campus recruiting visits are necessary for the maintenance of strong relationships that enable colleges and high schools to negotiate and send trustworthy information to one another.
+Without face-to-face visits, it is less likely that that a college admissions counselor will "take the call" of a guidance counselor.
+Simultaneously, a recruiting visit between a college and a high school can be conceived as an indicator.
+First, the fact that the college took time and effort to make the visit suggests that the college wants to enroll students from the high school.
+Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
+Third, the presence of the recruiting visit indicates that the high school and the college have a relationship and suggests the probability of additional interactions (e.g., phone calls).
+
+Our project collected data about off-campus recruiting visits made in 2017 by a convenience sample of colleges universities.
+Our analysis sample is based on three different lists of postsecondary institutions: first, the set of public research universities (which category) as defined by the YYYY Carnegie Classification; second, private universities in the top 100 of USNWR YYYY "national universities"; and, third, private colleges in the top 50 of USNWR YYYY "national liberal arts colleges" rankings.
+For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits.
+For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year.
+Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
+These institutions are excluded from the analyses.
+Our final analysis sample consists of X public research universities, X private research universities, and X private liberal arts colleges.
+[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]
+
+Our analyses to date have focused only on visits by public research universities [CITE].
+The big-picture takeaways are as follows.
+Most public research universities in our sample made more out-of-state than in-state recruiting visits.
+The exceptions were UC-Berkeley, UC-Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps.
+Accross all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropoitan areas.
+Most public universities also made a disproportionate number of out-of-state visits to private high schools.
+Analyses of in-state visits also found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools.
+Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.
+
+Tables/Figures X and X show simple counts and descriptive staitistics of off-campus recruiting visits by colleges and universities in our sample.
+TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES....
+Table/Figure X demonstrates the disproportionate number of visits to private high schools.
+The goal of this chapter is to investigate off-campus recruiting visits to private high schools.
+Which types of private high schools receive visits from which types of colleges and universities?
+Additionally, to what extent were visits a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics?
+Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition.
+WHAT TO SHOW IN TABLES/FIGURES:
+<!--
+- Table/figure of number of visits by visit type and in/out-of-state
+- Table/figure showing disproportionate number of visits to private high schools.
+-->
+
+[PARAGRAPH ABOUT TABLE THAT DESCRIBES CHARACTERISTICS OF VISITED VS. NON-VISITED PRIVATE SCHOOLS]
+Before proceeding to network analyses, Table/Figure X compares the characteristics of private high schools that received at least one recruiting visit from a college/university in our sample to those of private high schools that did not receive a visit.
+WHICH CHARACTERISTICS TO SHOW: geographic region; religious affiliation; academic reputation; racial composition; enrollment size.
+
+# Network Analyses of Off-Campus Recruiting Visits
+
+## Why Network Analysis and Network Basics
+
+We utilize network methods rather than conventional descriptive statistics for two, related reasons.
+First, the theory and analytic methods of social network analysis privileges the relationship between actors.
+The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407] [pg.
+175].
+Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network.
+
+We briefly define essential social network analysis concepts and their operationalization in our analyses.
+A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "edges" between these actors.
+Whereas "one mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two mode" networks consit of vertices associated with one type of actor/entity having connections to vertices of another type.
+For example, an an actor-movie network consists of actors -- mode 1 -- who appear in movies -- mode 2 and an actor shares an edge with a movie if the actor appears in the movie.
+The social network analyzed in this chapter is a two-mode network, where vertices consists of colleges/universities (mode 1) and high schools (mode 2) and an "edge" is defined as a visit from a college/university to a private high school.
+
+Our analyses draw from analyses of "corporate board-director" networks because these are the most commonly analyzed two-mode networks in the social networks literature.
+Board-director networks consist of directors (mode 1) who serve on organizational boards (mode 2).
+@RN4663 states that "Overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" [pg.
+xx].
+Similarly, our college-school network can be conceive of colleges as vertices that are connected to high school verticies by a tie of an off-campus recruiting visit.
+In practice, two-mode networks are ofen analyzed as one-mode networks.
+In the corporate board interlock literature a one-mode director-by-director matrix is created by identifying whether two directors serve on one ore more board (e.g., two directors share a tie if both serve on the board of Google) and a one-mode company-by-company matrix is created by identifying whether two boards have one or more directors who serve on both boards (e.g., xxxxxx).
+Similarly, we create a one-mode college network in which two colleges share a connection if both colleges visit at least one high school in common and a one-mode high school network in which two high schools share an edge if they are visited by at least one college/university in common.
+
+A two-mode board-director network can also be conceived as two one-mode networks.
+
+In the social network analysis literature, the corporate board-director network is most commonly analyzed two-mode network [CITE].
+These networks consist of directors (mode 1) who serve on organizational boards (mode 2).
+
+The most commonly analyzed two-mode network is the "corporate board interlock."
+
+For example, in a two-mode actor-movie network consists of two modes of vertices, actors and movies.
 

### 2020-10-13 manuscript.Rmd
working on manuscript draft

@@
 
-We present this chapter as one example of empirical research about enrollment management behavior.
-When we contrast research about enrollment management to descriptions of enrollment management practice, from investigative journalists or from consulting firms [cite], it becomes apparent that the research community is decades behind practice and has ignored a great number of enrollment management practices that affect access to higher education [AN EXCEPTION TO THE CRITIQUE IS A SMALL BUT HIGH-QUALITY CASE STUDY LITERATURE FROM SOCIOLOGY].
-Thus, the enrollment management remains an opaque industry to researchers and, in turn, to policymakers and the public.
-Developing thoughtful state and federal policies about enrollment management depends on researchers doing the slow, methodical work of developing an empirical literature that documents enrollment management practices and evaluates their effect on opportunities for students.
-[TONE DOWN THE CRITIQUE; DON'T WANT TO MAKE IT SEEM LIKE WE THINK WE ARE THE FIRST TO STUDY THIS STUFF; GIVE CREDIT TO THE EXCELLENT CASE STUDY RESEARCH]
+<!-- The "enrollment funnel," shown in Figure X, describes stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students). -->
 
-The "enrollment funnel," a conceptual heuristic used by the enrollment management industry and shown in figure X, is helpful for framing the development of this empirical literature.
-The enrollment funnel describes the stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, enrolled) in order to inform targeted recruiting interventions.
-The majority of research on enrollment management focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees.<!-- [@RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948] -->By contrast, the enrollment management industry expends substantial resources on earlier stages of the funnel [@RN4664].
-“Prospects” are “all the potential students you would want to attract to your institution” [@RN4322].
+Figure X shows the "enrollment funnel," a conceptual heurisitc used by the enrollment management industry, which describe the stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students).
+For example, “prospects” are “all the potential students you would want to attract to your institution” [@RN4322].
 “Inquiries” are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own.
+The enrollment management industry uses the enrollment funnel to inform interventions that target specific stages of the funnel.
 
-[REVISE BELOW PARAGRAPH TO TAKE OUT MOST OF THE NUMBERS OF PERCENT SPENT ON EACH ACTIVITY; BOGS DOWN THE PROSE; MAIN POINT IS HIGHLIGHTING THE ACTIVITIES THAT TARGET SPECIFIC ELEMENTS OF THE FUNNEL; READER CAN READ THE PERCENTAGES ON THEIR OWN]
-Table X shows the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.
+Table X, reproduced from @RN4664, shows the the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.
 ^[table drawn directly from @RN4664 figure 9; based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions].
 Institutions identify undergradaute prospects largely by purchasing "student lists" from College Board, ACT, and other vendors.
-Table X indicates that private and public institutions spent 14% and 12%, respectively, of their undergraduate recruitment budget on student list purchases.
-Institutions utilize digital advertising, traditional advertising, and social media to solicit inquiries and to create positive "buzz" amongst potential stealth applicants [@RN4411][CITE OTHER].
-<!-- Table X indicates that...
-[summarize expenditure on stuff related to soliciting inquiries once you figure out answers to below questions] -->  Once identified, prospects/inquiries are targeted with face-to-face and remote recruiting interventions designed to solit applications and deepen engagement.
-Remote recruiting interventions include postcards, brochures, email, and text messages.
-<!-- Table X indicates that these "prospective student communications" account for 13% of the recruiting budget at private institutions and 17% of the budget at public institutions.
--->Face-to-face recruiting interventions include on-campus visits (12% and 11% of budget, respectively, at private and public institutions) and off-campus recruiting events, often referred to as "travel" (17% and 16% of budget, respectively, at private and public institutions).
+Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411][CITE OTHER].
+Given the the rise in “stealth applicants” who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.
+Once prospects and inquiries are identified, they are targeted with face-to-face and remote recruiting interventions designed to solit applications and deepen engagement.
+Face-to-face recruiting interventions include on-campus visits by prospects and off-campus recruiting visits by admissions representatives to high schools, community colleges, college fairs, etc.
+Remote recruiting interventions include postcards, brochures, email, text messages, and targeted social media.
 <!-- QUESTIONS ABOUT THE RNL 2020 COST OF RECRUITING AN UNDERGRADUATE STUDENT REPORT, FIGURE 9
@@
 -->
-Having identified prominent marketing and recruiting activities (e.g., student list purchases, digital advertising, off-campus recruiting visits), why have so few researchers studied higher education marketing and recruitng?
-One challenge is that empirical research depends on data but obtaining concrete data about marketing and recruiting behaviors is difficult, especially for conventional data collection methods like surveys and interviews.
-Thus, empirical research requires different approaches to data collection, including public records requests and "data science" methodologies, such as web-scraping and streaming social media data.
 
-This chapter analyzes off-campus recruiting visits made in 2017 by a sample of public research universities and a sample of selective private colleges and universities.
-We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") from admissions websites.
-Pages were scraped once per week for the entire 2017 calendar year.
-In addition, for the sample of public research universities, we also issued public records requests.
+Each of these marketing/recruiting interventions -- and dozens of other interventions described in this book -- represent organizational behaviors that could be the subject of empirical research.
+However, the vast majority of research on enrollment management behaviors focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [E.G.] <!-- [@RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948] -->.
+By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664] [GIVE SOME CONCRETE BUDGET NUMBERS INDICATING BALL PARK SPENDING?].
+When we consider descriptions of enrollment management practice from investigative journalism [e.g., ], from enrollment management consulting firms and from this volume [e.g., ], it becomes apparent that -- with the notable exception of a small sociological case-study literature [e.g., ] -- the research community has ignores a great number of enrollment management practices that plausibly affect access to higher education.
+As a consequence, enrollment management remains an opaque industry to policymakers and the public.
+We argue that developing thoughtful policies about enrollment management depends on researchers collectively devloping empirical literatures that document enrollment management practices and evaluate the effects of these practices on opportunities for students.
 
-To date, our analyses have focused on recruiting visits by public research universities.
-As described below, the majority of public universities in our sample made far more out-of-state visits than in-state visits.
-These out-of-state visits focused on wealthy, predominantly white communities, with a disproportionate number of visits to private high schools.
-This chapter analyzes visits to private high schools.
-Using social network methods, we analyze visits by private colleges and universities to private high schools, visits by public research universities to private high schools, and then compare similarities and differences between public and private postsecondary institutions [as a means of saying something about "privatization"?]
-[MOTIVATE PARTICULAR FOCUS OF THIS CHAPTER: NETWORK ANALYSIS OF VISITS TO PRIVATE HIGH SCHOOLS BY BOTH PUBLIC AND PRIVATE COLLEGES/UNIVERSITIES]
+Access to concrete data about marketing and recruiting behaviors has been a persistent barrier to empirical research.
+To the extent that marketing/recruiting behaviors are inconsistent with public relations rhetoric (e.g., "our commitment to access"), colleges and universities may have incentive to withhold data from researchers.
+Therefore, conventional data collection methods such as surveys and even interviews should be appraised with healthy skepticism.
+We argue that pushing forward an empirical research agenda on marketing/recruiting behaviors depends on different modes of data collection -- including public records requests and "data science" methodologies, such as web-scraping and streaming social media data -- that record actual behaviors (e.g., contracts, transactions, records of expenditure) as opposed to statements by colleges/universities about their behavior.
+
+We present this chapter as an example of empirical research about marketing/recruiting behavior.
+This chapter analyzes off-campus recruiting visits by a sample of public research universities and a sample of selective private colleges and universities in 2017.
+We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.
+Our analyses to date have focused on public research universities.
+As described in more detail below, 12 of the 15 public research universities in our sample made far more out-of-state visits than in-state visits, a finding antithetical to the stated mission of most public research universities.
+These out-of-state visits focused on wealthy, predominantly white schools and communities.
+Additionally, most public research universities made a disproportionate number of out-of-state visits to private schools, but visited few in-state private schools.
+
+Building on these findings, this chapter analyzes off-campus visits to private schools.
+In particular, we compare visits by public research universities to visits by selective private colleges and universities.
+The motivation for this public-private comparision is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities.
+By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities.
+From this perspective, out-of-state visits to private schools by public research universities is one example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543].
+Therefore, by comparing the (mostly out-of-state) visits to private high schools by public research universities to those of private colleges and universities, we hope to develop new insights about the privatization of public higher education.
+
+Analyses are motivated by two, related research questions.
+First, which types of private high schools receive visits from which types of colleges and universities?
+Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+We use social network analysis (SNA) to analyze off-campus recruiting visits.
+The motivation for using SNA is that SNA privileges relationships between actorsQualitative scholarship on private high schools finds that college access is substantially determined by the quality of the relationship between a particular college and a particular private high school [@RN4321; @RN4407].
+An off-campus recruiting visit is an indicator of a relationship between a college and a school that can be analyzed using standard tools of SNA.
+
+[ADD ONE-PARAGRAPH OUTLINE?]
 
@@
 
-# Network Analyses of Off-Campus Recruiting Visits
-
-## Why Network Analysis and Network Basics
+# Network Methods and Data
 
 We utilize network methods rather than conventional descriptive statistics for two, related reasons.
-First, the theory and analytic methods of social network analysis privileges the relationship between actors.
+First, social network analysis privileges the relationship between actors.
 The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407] [pg.
@@
 For example, an an actor-movie network consists of actors -- mode 1 -- who appear in movies -- mode 2 and an actor shares an edge with a movie if the actor appears in the movie.
-The social network analyzed in this chapter is a two-mode network, where vertices consists of colleges/universities (mode 1) and high schools (mode 2) and an "edge" is defined as a visit from a college/university to a private high school.
+The social network analyzed in this chapter is a two-mode network, where vertices consists of colleges/universities (mode 1) and high schools (mode 2) and an "edge" is defined as a visit from a college/university to a private high school [DELETE THIS SENTENCE OR THE REDUNDANT ONE IN BELOW PARAGRAPH].
 
-Our analyses draw from analyses of "corporate board-director" networks because these are the most commonly analyzed two-mode networks in the social networks literature.
+Our analyses draw from analyses of "corporate board-director" networks because these are the most commonly analyzed two-mode networks in the social networks literature [e.g.] [@RN4663].
 Board-director networks consist of directors (mode 1) who serve on organizational boards (mode 2).
-@RN4663 states that "Overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" [pg.
+Our school-college network is a two-mode network composed of two sets of vertices, private high schools (mode 1) and colleges/universities (mode 2).
+Off-campus recruiting visits are edges (e.g., high school $i$ shares an edge with college $j$ if high school $i$ receives at least one visit from college $j$) and visits can only occur between a school-college pair (not a school-school pair or a college-college pair).
+Our school-college network is a two-mode network composed of high schools (mode 1) who are visited by colleges and universities (mode 2).
+This (weighted) network is represented as a school-by-college matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 colleges/universities) in which matrix cell $a_{i,j}$ identifies the number of visits that high school $i$ received from college/university $j$.
+[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
+UNWEIGHTED SOMEWHERE]
+
+Two-mode networks are ofen analyzed as one-mode networks [@RN2457].
+@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" [pg.
 xx].
-Similarly, our college-school network can be conceive of colleges as vertices that are connected to high school verticies by a tie of an off-campus recruiting visit.
-In practice, two-mode networks are ofen analyzed as one-mode networks.
-In the corporate board interlock literature a one-mode director-by-director matrix is created by identifying whether two directors serve on one ore more board (e.g., two directors share a tie if both serve on the board of Google) and a one-mode company-by-company matrix is created by identifying whether two boards have one or more directors who serve on both boards (e.g., xxxxxx).
-Similarly, we create a one-mode college network in which two colleges share a connection if both colleges visit at least one high school in common and a one-mode high school network in which two high schools share an edge if they are visited by at least one college/university in common.
+Thus, a two-mode board-director network can be transformed into two one-mode networks.
+A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ do not serve on three boards together.
+Similarly, a one-mode board network is created based on a board-by-board matrix in which two boards share an edge if a director sits on both boards and matrix cell $a_{i,j}$ identifies the number of directors that serve on both board $i$ and board $j$.
+Following this approach, we create a one-mode high school network in which two private high schools share an edge if both receive a visit by the same college/university and cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of colleges/universities that visited both school $i$ and school $j$ [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING].
+Similarly, we create a one-mode college/university network (herein the college network) in which two colleges share an edge if both colleges visited the same high school and cell $c_{i,j}$ of the college-by-college matrix $C$ indicates the number of private high schools that received at least one visit from both college $i$ and college $j$ [SHOW EXCERPT OF ONE-MODE COLLEGE BY COLLEGE MATRIX, LIKE 3 BY 3 OR SOMETHING].
 
-A two-mode board-director network can also be conceived as two one-mode networks.
+A limitation of our data collection is that we collected off-campus visit data only from a convenience sample of X colleges and universities, as described above.
+Thus, for each college and university in our sample, we know all the private high schools they visited (assuming no measurement error).
+However, for each private high school in our sample, we only know visits they received from the set of X colleges/universities in our sample.
+Given this limitation, it may be useful to think of our data collection as resulting in X "ego networks." An "ego" is a single "focal" node (e.g., The University of Notre Dame).
+An ego network consists "of a focal node ("ego") and the nodes to whom ego is directly connected to (these are called "alters") plus the ties, if any, among the alters" [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ].
+For example, the University of Notre Dame ego network consists of all private high schools that received at least one visit from Notre Dame.
+Additionally, for each high school visited by Notre Dame, the ego network may include all colleges/universities in our sample that also visited the high school.
 
-In the social network analysis literature, the corporate board-director network is most commonly analyzed two-mode network [CITE].
-These networks consist of directors (mode 1) who serve on organizational boards (mode 2).
+Figure X shows the ego network of all high schools visited by Notre Dame.
 
-The most commonly analyzed two-mode network is the "corporate board interlock."
+When analyzing ego networks, researchers often investigate the extent of "homophily" versus "heterophily" [@RN1722].
+Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be freinds on Facebook if they have similar political ideologies).
+Heterophily, the opposite of homophily, is when pairs of connected vertices have different characteristics from one another.
+Figure X shows the University of Notre Dame ego network, with separate panels for vertex characteristics (academic reputation, geography, religious affiliation, and racial composition) and with vertex shapes (?colors?) to identify values of vertex characteristics [INSERT FIGURE].
+Visually, we can see that ....[DESCRIBE BIG TAKEAWAYS].
 
-For example, in a two-mode actor-movie network consists of two modes of vertices, actors and movies.
+Figure X augments the Notre Dame ego network by including the private colleges/universities in our sample that visited private high schools visited by Notre Dame [INSERT FIGURE].
+ADD BRIEF TEXT ABOUT FIGURE?
+
+# Network Analyses of Off-Campus Recruiting Visits
+
+This section presents network analyses of visits by colleges and universities to private high schools.
+Analyses are motivated by two, related research questions.
+First, which types of private high schools receive visits from which types of colleges and universities?
+Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
+
+We present results in three steps: First, visits by private colleges and universities; second, visits by public research universities; and, third, comparisons of visits by public research universities to visits by private colleges and universities.
+
+## Visits by Private Colleges and Universities
+
+CRYSTAL ADDS TABLES/FIGURES
+
+## Visits by Public Research Universities
+
+CRYSTAL ADDS TABLES/FIGURES
+
+## Comparison of Public Versus Private Colleges and Universities
+
+CRYSTAL ADDS TABLES/FIGURES
 

### 2020-10-15 manuscript.Rmd
minor changes draft manuscript

@@
 
-Building on these findings, this chapter analyzes off-campus visits to private schools.
-In particular, we compare visits by public research universities to visits by selective private colleges and universities.
-The motivation for this public-private comparision is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities.
+Building on these findings, this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities.
+We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
+Analyses are informed by two broad, related questions.
+First, which types of private high schools receive visits from which types of colleges and universities?
+Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+
+The motivation for comparing the behavior of public and private coleges/universities is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities.
 By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities.
@@
 
-Analyses are motivated by two, related research questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
 We use social network analysis (SNA) to analyze off-campus recruiting visits.

### 2020-10-26 scripts/network_recruiting_analysis.R
modest changes

@@ -110,25 +110,6 @@ events_data %>% left_join(y = univ_df, by = c("univ_id" = "school_id")) %>% grou
 ## EGO IGRAPH FUNCTION (can utilize order =1, order =2, or both)
 ## --------------------
 
-  # Vertex color [CUT CODE HERE]    
-  if (is.na(characteristic)==TRUE) { # do not use characteristic to determine vertex color/shape
-    
-    if (graph_order == 1) { # order == 1; only show ego and high schools {
-      vertex_color <- if_else(V(network)$type, 'lightblue', 'salmon')
-    } else {  # order == 'both' or 2: show ego, high schools, colleges that visited those high schools
-      vertex_color <- case_when(
-        vertex_attr(network, "type") == FALSE ~ 'salmon',
-        vertex_attr(network, "type") == TRUE &  vertex_attr(network, "name") != univ_id ~ 'lightblue',
-        vertex_attr(network, "type") == TRUE &  vertex_attr(network, "name") == univ_id ~ 'purple',
-      )
-    }
-  } else {  # use characteristic to determine vertex color/shape
-    color_palette <- colors
-    names(color_palette) <- values
-    
-    vertex_color <- recode(vertex_attr(network, characteristic), !!!color_palette) # use characteristic to determine vertex color/shape
-  }
-    
 # function to plot ego graph
 
 plot_ego_graph <- function(network, characteristic, values, keys, colors = c('blue', 'purple', 'red', 'green'), title = '', graph_order = 'both') {
@@ -201,7 +182,7 @@ plot_ego_graph <- function(network, characteristic, values, keys, colors = c('bl
     edge.width = edge_width,
     layout = graph_layout,  
     main = str_to_title(title),
-    margin = -0.2
+    margin = 0.0 # -0.2
   )  
 
   if (is.na(characteristic)==FALSE) {  # if characteristic ! FALSE then create legend    
@@ -215,7 +196,8 @@ plot_ego_graph <- function(network, characteristic, values, keys, colors = c('bl
   }
   
 }
-
+# dev.off() # to fix this: Error in .Call.graphics(C_palette, value) : invalid graphics state
+    
 par(mfrow=c(1, 1))  # resets to single plot
 
 plot_ego_graph(ego_network, characteristic = NA, values = NA, keys = NA, colors = NA, title = "", graph_order = 1)
@@ -267,20 +249,20 @@ par(mfrow=c(1, 1))  # resets to single plot
[…]

### 2020-10-26 tables.Rmd
add draft of 2mode table

---
title: "Tables"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Top visited private HS (2-mode network)

```{r cars}
library(kableExtra)

df <- readRDS('./assets/tables/table_2mode.RDS')

knitr::kable(head(df, n = 20)) %>% kable_styling(latex_options = 'scale_down')
```

### 2020-10-26 scripts/network_recruiting_analysis.R
draft changes branch

@@ -360,6 +360,7 @@ full_2mode_table %>% str()
 vertex_attr_names(g_2mode_privu)
 
 c_2mode_privu <- cluster_fast_greedy(g_2mode_privu)
+class(c_2mode_privu)
 length(c_2mode_privu)
 sizes(c_2mode_privu)
 

### 2020-10-26 scripts/network_recruiting_analysis.R
draft changes branch

@@ -252,6 +252,8 @@ par(mfrow=c(1, 1))  # resets to single plot
 #graph_layout <- layout_with_kk
 graph_layout <- layout_with_fr
 
+# open file
+pdf("")
 plot(
   x = g_2mode_privu, 
   vertex.label = if_else(V(g_2mode_privu)$type, V(g_2mode_privu)$school_name, ''),
@@ -360,6 +362,7 @@ full_2mode_table %>% str()
 vertex_attr_names(g_2mode_privu)
 
 c_2mode_privu <- cluster_fast_greedy(g_2mode_privu)
+class(c_2mode_privu)
 length(c_2mode_privu)
 sizes(c_2mode_privu)
 

### 2020-10-26 scripts/network_recruiting_analysis.R
save 2mode table

@@ -319,8 +319,10 @@ t_2mode_privu <- data.frame(
   state = V(g_2mode_privu)$state_code,
   region = V(g_2mode_privu)$region,
   religion = V(g_2mode_privu)$religion,
-  pct_white = V(g_2mode_privu)$pct_white,
-  race = V(g_2mode_privu)$pct_white_cat,
+  pct_blacklatinxnative = V(g_2mode_privu)$pct_blacklatinxnative,
+  race = V(g_2mode_privu)$pct_blacklatinxnative_cat,
+  ranking_score = V(g_2mode_privu)$ranking,
+  ranking_numeric = V(g_2mode_privu)$ranking_numeric,
   ranking = V(g_2mode_privu)$rank_cat1,
   type = V(g_2mode_privu)$type,
   degree = V(g_2mode_privu)$degree,
@@ -329,18 +331,24 @@ t_2mode_privu <- data.frame(
 )
 
 # temporarily get rid of unmerged rows
-full_2mode_table <- t_2mode_privu %>% filter(type == F, !is.na(school_name)) %>% arrange(-closeness) %>%
+t_2mode_privu <- t_2mode_privu %>% filter(type == F, !is.na(school_name)) %>%
   mutate(degree_band = case_when(degree >= 15 ~ '15+',
                                  degree >= 10 ~ '10-14',
                                  degree >= 5 ~ '5-9',
-                                 TRUE ~ as.character(degree))) %>%
-  select(school_id, school_name, city, state, region, religion, race, ranking, closeness, degree, degree_band, strength)
+                                 TRUE ~ as.character(degree)))
+
+full_2mode_table <- t_2mode_privu %>% arrange(-degree) %>%
+  select(school_id, school_name, city, state, region, religion, pct_blacklatinxnative, ranking_score, ranking_numeric, degree, closeness, strength)
 
 View(full_2mode_table)
 
+saveRDS(full_2mode_table, file = './assets/tables/table_2mode.RDS')
+# readr::write_file(knitr::kable(head(full_2mode_table), 'latex'), 'assets/tables/table_2mode.tex')
+
+# Aggregated table
 characteristic <- 'race'
 
-agg_2mode_table <- full_2mode_table %>% select_('degree_band', characteristic) %>%
+agg_2mode_table <- t_2mode_privu %>% select_('degree_band', characteristic) %>%
   group_by_('degree_band', characteristic) %>%
[…]

### 2020-10-26 scripts/network_recruiting_analysis.R
draft changes

@@ -252,8 +252,8 @@ par(mfrow=c(1, 1))  # resets to single plot
 #graph_layout <- layout_with_kk
 graph_layout <- layout_with_fr
 
-# open file
-pdf("")
+
+pdf("assets/figures/plot_g_2mode_privu.pdf") # open file
 plot(
   x = g_2mode_privu, 
   vertex.label = if_else(V(g_2mode_privu)$type, V(g_2mode_privu)$school_name, ''),
@@ -267,6 +267,7 @@ plot(
   margin = -0.8
 )
 
+dev.off() # close the file
 
 ## ------------------------------
 ## TABLE FROM EGO IGRAPH OBJECTS

### 2020-10-26 manuscript.Rmd
draft changes

@@
 bibliography: ./other/burd_recruiting_chapter.bib
-output: pdf_document
+output: 
+  bookdown::pdf_document2
 csl: ./other/apa.csl
@@
 library(knitr)
+library(bookdown)
 
@@
 
-CRYSTAL ADDS TABLES/FIGURES
+<!--
+As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la
+ fig.cap="2-mode plot of visits by private colleges and universities", 
+-->
+
+```{r plot_g_2mode_privu, echo=FALSE, out.width = '100%'}
+knitr::include_graphics("assets/figures/plot_g_2mode_privu.pdf")
+```
+As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la
 
@@
 )
-# 
+#  <div id="refs"></div>
 ```

### 2020-10-26 scripts/network_recruiting_analysis.R

@@ -249,11 +249,12 @@ par(mfrow=c(1, 1))  # resets to single plot
     #Often more effective for creating useful drawings are layouts based on exploiting analogies between the relational structure in graphs and the forces among elements in physical systems. One approach in this area, and the earliest proposed, is to introduce attractive and repulsive forces by associating vertices with balls and edges with springs. If a literal system of balls connected by springs is disrupted, thereby stretching some of the springs and compressing others, upon being let go it will return to its natural state. So-called spring-embedder methods of graph drawing define a notion of force for each vertex in the graph depending, at the very least, on the positions of pairs of vertices and the distances between them, and seek to iteratively update the placement of vertices until a vector of net forces across vertices converges. 
     #The method of Fruchterman and Reingold [6] is a commonly used example of this type.
 
-#graph_layout <- layout_with_kk
-graph_layout <- layout_with_fr
 
 
 pdf("assets/figures/plot_g_2mode_privu.pdf") # open file
+#graph_layout <- layout_with_kk
+graph_layout <- layout_with_fr
+
 plot(
   x = g_2mode_privu, 
   vertex.label = if_else(V(g_2mode_privu)$type, V(g_2mode_privu)$school_name, ''),

### 2020-10-26 scripts/network_recruiting_analysis.R
add ego table drafts

@@ -274,9 +274,11 @@ dev.off() # close the file
 ## TABLE FROM EGO IGRAPH OBJECTS
 ## ------------------------------
 
-ego_table <- data.frame(univ_id = character(0), characteristics = character(0),
-                        private_hs_region = character(0), private_hs_religion = character(0),
-                        private_hs_race = character(0), private_hs_ranking = character(0),
+ego_table <- data.frame(univ_name = character(0), characteristics = character(0),
+                        private_hs_region_1 = character(0), private_hs_region_2 = character(0), private_hs_region_3 = character(0), private_hs_region_4 = character(0),
+                        private_hs_religion_1 = character(0), private_hs_religion_2 = character(0), private_hs_religion_3 = character(0), private_hs_religion_4 = character(0),
+                        private_hs_race_1 = character(0), private_hs_race_2 = character(0), private_hs_race_3 = character(0), private_hs_race_4 = character(0),
+                        private_hs_ranking_1 = character(0), private_hs_ranking_2 = character(0), private_hs_ranking_3 = character(0), private_hs_ranking_4 = character(0),
                         stringsAsFactors=FALSE)
 
 for (i in seq_along(privu_vec)) {
@@ -290,17 +292,42 @@ for (i in seq_along(privu_vec)) {
   privhs_characteristics <- ego_df %>% filter(type == FALSE)
   num_privhs <- nrow(privhs_characteristics)
   
-  pct_privhs_region <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(region == univ_characteristics$region)) / num_privhs * 100)
-  pct_privhs_religion <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(religion == univ_characteristics$religion)) / num_privhs * 100)
-  pct_privhs_race <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(pct_white_cat == univ_characteristics$pct_white_cat)) / num_privhs * 100)
-  pct_privhs_ranking <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(rank_cat1 == 'c1_top100')) / num_privhs * 100)
[…]

### 2020-10-26 manuscript.Rmd
draft changes

@@
 
-```{r plot_g_2mode_privu, echo=FALSE, out.width = '100%'}
-knitr::include_graphics("assets/figures/plot_g_2mode_privu.pdf")
+As shown in Figure \@ref(fig:two-mode-plot).
+
+```{r two-mode-plot, fig.align = 'center', out.width = "100%", fig.cap = "caption of 2 mode graph"}
+knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
 ```
-As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la
+
+plot_g_2mode.pdf
 

### 2020-10-26 scripts/network_recruiting_analysis.R

@@ -249,9 +249,34 @@ par(mfrow=c(1, 1))  # resets to single plot
     #Often more effective for creating useful drawings are layouts based on exploiting analogies between the relational structure in graphs and the forces among elements in physical systems. One approach in this area, and the earliest proposed, is to introduce attractive and repulsive forces by associating vertices with balls and edges with springs. If a literal system of balls connected by springs is disrupted, thereby stretching some of the springs and compressing others, upon being let go it will return to its natural state. So-called spring-embedder methods of graph drawing define a notion of force for each vertex in the graph depending, at the very least, on the positions of pairs of vertices and the distances between them, and seek to iteratively update the placement of vertices until a vector of net forces across vertices converges. 
     #The method of Fruchterman and Reingold [6] is a commonly used example of this type.
 
+vertex_attr_names(g_2mode)
 
+#graph_layout <- layout_with_kk
+graph_layout <- layout_with_fr
+
+pdf("assets/figures/plot_g_2mode.pdf") # open file
+
+plot(
+  x = g_2mode, 
+  vertex.label = if_else(V(g_2mode)$type, V(g_2mode)$school_name, ''),
+  vertex.color = case_when(
+      vertex_attr(g_2mode, "type") == FALSE ~ 'salmon',
+      vertex_attr(g_2mode, "type") == TRUE &  vertex_attr(g_2mode, "name") %in% privu_vec ~ 'green',
+      vertex_attr(g_2mode, "type") == TRUE &  vertex_attr(g_2mode, "name") %in% pubu_vec  ~ 'violet',
+    ),
+  vertex.shape = if_else(V(g_2mode)$type, 'circle', 'circle'),
+  vertex.size = if_else(V(g_2mode)$type, 3, 1),
+  edge.lty = 3, # 0 (“blank”), 1 (“solid”), 2 (“dashed”), 3 (“dotted”), 4 (“dotdash”), 5 (“longdash”), 6 (“twodash”).
+  edge.lty = .5,
+  edge.color = 'lightgrey',
+  layout = graph_layout,
+  margin = -0.6
+)
+
+dev.off() # close the file
 
 pdf("assets/figures/plot_g_2mode_privu.pdf") # open file
+
 #graph_layout <- layout_with_kk
 graph_layout <- layout_with_fr
 
@@ -265,10 +290,11 @@ plot(
   edge.lty = .5,
   edge.color = 'lightgrey',
[…]

### 2020-10-26 tables.Rmd

@@
 title: "Tables"
-output: pdf_document
+output: bookdown::pdf_document2
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
+
+library(kableExtra)
+library(tidyverse)
 ```
 
-## Top visited private HS (2-mode network)
+# Top visited private HS (2-mode network)
 
-```{r cars}
-library(kableExtra)
-
+```{r}
 df <- readRDS('./assets/tables/table_2mode.RDS')
@@
 ```
+
+# Ego network table
+
+```{r}
+df <- readRDS('./assets/tables/table_ego.RDS')
+
+knitr::kable(df %>% select(-Characteristics)) %>% kable_styling(latex_options = 'scale_down')
+```
+
+# Ego network graph
+
+See Figure \@ref(fig:ego-plot).
+
+```{r ego-plot, fig.align = 'center', out.width = '50%', fig.cap = 'Ego network'}
+knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
+```

### 2020-10-26 manuscript.Rmd
draft changes

--- 2020-10-26 manuscript.Rmd
@@
 
+Figure \@ref(fig:two-mode-plot) shows a plot of the two-mode network, with private high schools vertices the color salmon, public research universities shown in violet, and private colleges and universities shown in green green.
+The graph layout places vertices closer together if they are similar to one another in terms of network structure.
+[SAY WHAT THIS MEANS, DRAWING FROM NOTES FROM RUSS].
+Figure \@ref(fig:two-mode-plot) suggests that the recruiting visit patterns of private colleges and universities tend to be more similar to one another than they are to those of public research universities.
+By contrast, many public research universities are far away from one another and a subset of public researchg universities appear to have network structure similar to many of the private colleges and universities (e.g., CU Boulder, UC Berkeley, University of South Carolina )
+
+```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
+knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
+```
+
 We present results in three steps: First, visits by private colleges and universities; second, visits by public research universities; and, third, comparisons of visits by public research universities to visits by private colleges and universities.
@@
 
-<!--
-As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la
- fig.cap="2-mode plot of visits by private colleges and universities", 
--->
+Figure \@ref(fig:two-mode-plot-privu) shows a plot of the two-mode network of private colleges and universities
 
-```{r plot_g_2mode_privu, echo=FALSE, out.width = '100%'}
-knitr::include_graphics("assets/figures/plot_g_2mode_privu.pdf")
+```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
+knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
 ```
-As shown in Figure \@ref(fig:plot_g_2mode_privu), the la la la
+
+INSERT COMMUNITY DETECTION
 

### 2020-10-26 scripts/network_recruiting_analysis.R

@@ -270,7 +270,7 @@ plot(
   edge.lty = .5,
   edge.color = 'lightgrey',
   layout = graph_layout,
-  margin = -0.6
+  margin = -0.7
 )
 
 dev.off() # close the file
@@ -283,14 +283,14 @@ graph_layout <- layout_with_fr
 plot(
   x = g_2mode_privu, 
   vertex.label = if_else(V(g_2mode_privu)$type, V(g_2mode_privu)$school_name, ''),
-  vertex.color = if_else(V(g_2mode_privu)$type, 'lightblue', 'salmon'),
+  vertex.color = if_else(V(g_2mode_privu)$type, 'green', 'salmon'),
   vertex.shape = if_else(V(g_2mode_privu)$type, 'circle', 'circle'),
   vertex.size = if_else(V(g_2mode_privu)$type, 3, 1),
   edge.lty = 3, # 0 (“blank”), 1 (“solid”), 2 (“dashed”), 3 (“dotted”), 4 (“dotdash”), 5 (“longdash”), 6 (“twodash”).
   edge.lty = .5,
   edge.color = 'lightgrey',
   layout = graph_layout,
-  margin = -0.7
+  margin = -0.8
 )
 
 dev.off() # close the file
@@ -433,6 +433,7 @@ membership(c_2mode_privu)
 
 length(V(g_2mode_privu)$type)
 membership(c_2mode_privu)[V(g_2mode_privu)$type==T]
+table(membership(c_2mode_privu)[V(g_2mode_privu)$type==T])
 
 plot(c_2mode_privu,
      g_2mode_privu,

### 2020-10-26 scripts/network_recruiting_analysis.R
add rest of table drafts

@@ -321,22 +321,22 @@ for (i in seq_along(privu_vec)) {
   pct_privhs_region_1 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(region == 1)) / num_privhs * 100)
   pct_privhs_religion_1 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(religion == 'catholic')) / num_privhs * 100)
   pct_privhs_race_1 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(pct_blacklatinxnative_cat == 'c1_lt10')) / num_privhs * 100)
-  pct_privhs_ranking_1 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(rank_cat1 == 'c1_top100')) / num_privhs * 100)
+  pct_privhs_ranking_1 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(rank_cat2 == 'c1_top200')) / num_privhs * 100)
   
   pct_privhs_region_2 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(region == 2)) / num_privhs * 100)
   pct_privhs_religion_2 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(religion == 'conservative_christian')) / num_privhs * 100)
   pct_privhs_race_2 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(pct_blacklatinxnative_cat == 'c2_10to25')) / num_privhs * 100)
-  pct_privhs_ranking_2 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(rank_cat1 == 'c2_top200')) / num_privhs * 100)
+  pct_privhs_ranking_2 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(rank_cat2 == 'c2_A+')) / num_privhs * 100)
   
   pct_privhs_region_3 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(region == 3)) / num_privhs * 100)
   pct_privhs_religion_3 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(religion == 'nonsectarian')) / num_privhs * 100)
   pct_privhs_race_3 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(pct_blacklatinxnative_cat == 'c3_25to50')) / num_privhs * 100)
[…]

### 2020-10-26 scripts/network_recruiting_analysis.R
save 2mode/community plot

@@ -275,7 +275,19 @@ plot(
 
 dev.off() # close the file
 
-pdf("assets/figures/plot_g_2mode_privu.pdf") # open file
+
+
+c_2mode_privu <- cluster_fast_greedy(g_2mode_privu)
+m_2mode_privu <- membership(c_2mode_privu)
+
+colors_2mode_privu <- revalue(as.character(m_2mode_privu), c(
+  '1' = 'red',
+  '2' = 'blue',
+  '3' = 'green',
+  '4' = 'yellow'
+))
+
+pdf("assets/figures/plot_g_2mode_privu_community.pdf") # open file
 
 #graph_layout <- layout_with_kk
 graph_layout <- layout_with_fr
@@ -283,7 +295,9 @@ graph_layout <- layout_with_fr
 plot(
   x = g_2mode_privu, 
   vertex.label = if_else(V(g_2mode_privu)$type, V(g_2mode_privu)$school_name, ''),
-  vertex.color = if_else(V(g_2mode_privu)$type, 'green', 'salmon'),
+  # vertex.color = if_else(V(g_2mode_privu)$type, 'green', 'salmon'),
+  vertex.color = colors_2mode_privu,
+  vertex.frame.color = if_else(V(g_2mode_privu)$type, 'black', 'lightgray'),
   vertex.shape = if_else(V(g_2mode_privu)$type, 'circle', 'circle'),
   vertex.size = if_else(V(g_2mode_privu)$type, 3, 1),
   edge.lty = 3, # 0 (“blank”), 1 (“solid”), 2 (“dashed”), 3 (“dotted”), 4 (“dotdash”), 5 (“longdash”), 6 (“twodash”).

### 2020-10-27 tables.Rmd
add rest of table drafts
update ego table

@@
 
+# Aggregated visited private HS (2-mode network)
+
+```{r}
+df <- readRDS('./assets/tables/table_2mode_agg.RDS')
+
+knitr::kable(df) %>% kable_styling(latex_options = 'scale_down')
+```
+
 # Ego network table
@@
 
-knitr::kable(df %>% select(-Characteristics)) %>% kable_styling(latex_options = 'scale_down')
+knitr::kable(df %>% select(-ID, -Characteristics), row.names = F) %>% kable_styling(latex_options = 'scale_down')
 ```

### 2020-10-27 scripts/network_recruiting_analysis.R

@@ -287,9 +287,9 @@ colors_2mode_privu <- revalue(as.character(m_2mode_privu), c(
   '4' = 'yellow'
 ))
 
-pdf("assets/figures/plot_g_2mode_privu_community.pdf") # open file
+pdf("assets/figures/plot_g_2mode_privu.pdf") # open file
 
-#graph_layout <- layout_with_kk
+# graph_layout <- layout_with_kk
 graph_layout <- layout_with_fr
 
 plot(
@@ -314,7 +314,7 @@ dev.off() # close the file
 ## TABLE FROM EGO IGRAPH OBJECTS
 ## ------------------------------
 
-ego_table <- data.frame(univ_name = character(0), characteristics = character(0),
+ego_table <- data.frame(univ_id = character(0), univ_name = character(0), univ_ranking = character(0), characteristics = character(0),
                         private_hs_region_1 = character(0), private_hs_region_2 = character(0), private_hs_region_3 = character(0), private_hs_region_4 = character(0),
                         private_hs_religion_1 = character(0), private_hs_religion_2 = character(0), private_hs_religion_3 = character(0), private_hs_religion_4 = character(0),
                         private_hs_race_1 = character(0), private_hs_race_2 = character(0), private_hs_race_3 = character(0), private_hs_race_4 = character(0),
@@ -352,7 +352,7 @@ for (i in seq_along(privu_vec)) {
   pct_privhs_race_4 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(pct_blacklatinxnative_cat == 'c4_50+')) / num_privhs * 100)
   pct_privhs_ranking_4 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(rank_cat2 == 'c4_ltA')) / num_privhs * 100)
   
-  ego_table[i, ] <- c(as.character(univ_characteristics$school_name),
+  ego_table[i, ] <- c(as.character(univ_characteristics$name), as.character(univ_characteristics$school_name), as.character(univ_characteristics$ranking_numeric),
                       str_c(val_label(univ_df$region, univ_characteristics$region), univ_characteristics$religion, univ_characteristics$pct_blacklatinxnative_cat, univ_characteristics$ranking, sep = '|'),
                       pct_privhs_region_1, pct_privhs_region_2, pct_privhs_region_3, pct_privhs_region_4,
[…]

### 2020-10-27 scripts/network_recruiting_analysis.R
draft of ego table function

@@ -314,6 +314,75 @@ dev.off() # close the file
 ## TABLE FROM EGO IGRAPH OBJECTS
 ## ------------------------------
 
+create_ego_table <- function(race_var = 'pct_blacklatinxnative_cat', ranking_var = 'rank_cat2') {
+  ego_tbl <- data.frame(univ_id = character(0), univ_name = character(0), univ_ranking = character(0), characteristics = character(0),
+                          private_hs_region_1 = character(0), private_hs_region_2 = character(0), private_hs_region_3 = character(0), private_hs_region_4 = character(0),
+                          private_hs_religion_1 = character(0), private_hs_religion_2 = character(0), private_hs_religion_3 = character(0), private_hs_religion_4 = character(0),
+                          private_hs_race_1 = character(0), private_hs_race_2 = character(0), private_hs_race_3 = character(0), private_hs_race_4 = character(0),
+                          private_hs_ranking_1 = character(0), private_hs_ranking_2 = character(0), private_hs_ranking_3 = character(0), private_hs_ranking_4 = character(0),
+                          stringsAsFactors=FALSE)
+  
+  for (i in seq_along(privu_vec)) {
+    ego_network <- egos_psi_privu[[privu_vec[[i]]]]
+    ego_network_order1 <- subgraph.edges(graph = ego_network, eids = E(ego_network)[E(ego_network)$order==1])
+    
+    ego_df <- as.data.frame(vertex_attr(ego_network_order1))
+    
+    univ_characteristics <- ego_df %>% filter(type == TRUE)
+    
+    privhs_characteristics <- ego_df %>% filter(type == FALSE)
+    num_privhs <- nrow(privhs_characteristics)
+    
+    # Region
+    pct_privhs_region_1 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(region == 1)) / num_privhs * 100)
+    pct_privhs_region_2 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(region == 2)) / num_privhs * 100)
+    pct_privhs_region_3 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(region == 3)) / num_privhs * 100)
+    pct_privhs_region_4 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(region == 4)) / num_privhs * 100)
+
+    # Religion
[…]

### 2020-10-27 manuscript.Rmd
draft changes

@@
 bibliography: ./other/burd_recruiting_chapter.bib
-output: 
-  bookdown::pdf_document2
+output: bookdown::pdf_document2
 csl: ./other/apa.csl
 urlcolor: blue
+header-includes:
+      - \usepackage{pdflscape}
 ---
@@
 
+library(kableExtra)
+library(tidyverse)
 ```
@@
 
-```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
-knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
-```
-
 We present results in three steps: First, visits by private colleges and universities; second, visits by public research universities; and, third, comparisons of visits by public research universities to visits by private colleges and universities.
@@
 
-```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
-knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
-```
+Table \@ref(tab:ego-table-privu) shows characteristics of private high schools visited by each private college and university
 
-INSERT COMMUNITY DETECTION
+Table \@ref(tab:hs-print-privu) shows characteristics of the 20 private high schools that were visited by the most private colleges and universities
+
+Table \@ref(tab:hs-table-privu-agg) shows characteristics of private high schools by number of private colleges and universities that visited
 
@@
 
-CRYSTAL ADDS TABLES/FIGURES
+# References
 
-![The enrollment funnel](assets/images/enrollment_funnel.png)
+<div id="refs"></div>
+
+<!-- TABLES -->
 
@@
 
-More info in this [documentation](https://rmarkdown.rstudio.com/authoring_bibliographies_and_citations.html).
+```{r, ego-table-privu, echo = FALSE}
+df <- readRDS('./assets/tables/table_ego.RDS')
+knitr::kable(
+  df %>% select(-ID, -Characteristics), row.names = F, 
+  caption = 'ego table caption') %>% landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
 
-# References
+```{r, hs-print-privu, echo = FALSE}
+df <- readRDS('./assets/tables/table_2mode.RDS') %>% head(n=20)
+
+knitr::kable(
+  df %>% select(-school_id,-closeness), caption = 'ego table 3') %>% 
+  landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r, hs-table-privu-agg, echo = FALSE}
+df <- readRDS('./assets/tables/table_2mode_agg.RDS')
+
+knitr::kable(df, caption = 'ego table caption') %>% 
+  landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+<!-- FIGURES -->
+
+![The enrollment funnel](assets/images/enrollment_funnel.png)
+
+\newpage
+
+\begin{landscape}
+
+```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "125%", fig.cap = "caption of 2 mode graph"}
+knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
+#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
+```
+
+```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "125%", fig.cap = "caption of 2 mode graph"}
+knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
+```
+
+\end{landscape}

### 2020-10-27 tables.Rmd
draft changes

@@
 
+Table \@ref(tab:hs-print-privu) shows characteristics of the 20 private high schools that were visited by the most private colleges and universities
+
+```{r, hs-print-privu, echo = FALSE}
+df <- readRDS('./assets/tables/table_2mode.RDS')
+
+knitr::kable(head(df, n = 20, caption = 'ego table 3')) %>% kable_styling(latex_options = 'scale_down')
+```
+
 # Aggregated visited private HS (2-mode network)
@@
 df <- readRDS('./assets/tables/table_ego.RDS')
-
 knitr::kable(df %>% select(-ID, -Characteristics), row.names = F) %>% kable_styling(latex_options = 'scale_down')

### 2020-10-27 scripts/network_recruiting_analysis.R

@@ -280,12 +280,16 @@ dev.off() # close the file
 c_2mode_privu <- cluster_fast_greedy(g_2mode_privu)
 m_2mode_privu <- membership(c_2mode_privu)
 
+
+
+library(plyr)
 colors_2mode_privu <- revalue(as.character(m_2mode_privu), c(
   '1' = 'red',
-  '2' = 'blue',
+  '2' = 'lightblue',
   '3' = 'green',
   '4' = 'yellow'
 ))
+detach(package:plyr, unload = TRUE)
 
 pdf("assets/figures/plot_g_2mode_privu.pdf") # open file
 
@@ -315,6 +319,7 @@ dev.off() # close the file
 ## ------------------------------
 
 create_ego_table <- function(race_var = 'pct_blacklatinxnative_cat', ranking_var = 'rank_cat2') {
+  
   ego_tbl <- data.frame(univ_id = character(0), univ_name = character(0), univ_ranking = character(0), characteristics = character(0),
                           private_hs_region_1 = character(0), private_hs_region_2 = character(0), private_hs_region_3 = character(0), private_hs_region_4 = character(0),
                           private_hs_religion_1 = character(0), private_hs_religion_2 = character(0), private_hs_religion_3 = character(0), private_hs_religion_4 = character(0),
@@ -346,17 +351,17 @@ create_ego_table <- function(race_var = 'pct_blacklatinxnative_cat', ranking_var
     pct_privhs_religion_4 <- sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(religion == 'other_religion')) / num_privhs * 100)
 
     # Race
-    race_vals <- levels(privhs_characteristics[[race_var]])
+    race_vals <- levels(as.factor(privhs_characteristics[[race_var]]))
     for (j in seq_along(race_vals)) {
       assign(paste0('pct_privhs_race_', j), sprintf('%.1f%%', nrow(privhs_characteristics %>% filter(get(race_var) == race_vals[[j]])) / num_privhs * 100))
     }
-    
+
     # Ranking
-    ranking_vals <- levels(privhs_characteristics[[ranking_var]])
+    ranking_vals <- levels(as.factor(privhs_characteristics[[ranking_var]]))
     for (j in seq_along(ranking_vals)) {
[…]

### 2020-10-27 manuscript.Rmd
draft changes

@@
       - \usepackage{pdflscape}
+      - \usepackage{geometry}
 ---
@@
 
-Figure X shows the "enrollment funnel," a conceptual heurisitc used by the enrollment management industry, which describe the stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students).
+Figure \@ref(fig:em-funnel) shows the "enrollment funnel," a conceptual heurisitc used by the enrollment management industry, which describe the stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students).
 For example, “prospects” are “all the potential students you would want to attract to your institution” [@RN4322].
@@
 knitr::kable(
-  df %>% select(-ID, -Characteristics), row.names = F, 
+  df %>% select(-Characteristics), row.names = F, # select(-ID, -Characteristics)
   caption = 'ego table caption') %>% landscape(margin = NULL) %>%
@@
 
-![The enrollment funnel](assets/images/enrollment_funnel.png)
+```{r em-funnel, echo = FALSE, fig.cap = "The enrollment funnel"}
+knitr::include_graphics('assets/images/enrollment_funnel.png')
+#![The enrollment funnel](assets/images/enrollment_funnel.png)
+```
 
@@
 
+\newgeometry{margin=0cm}
+
 \begin{landscape}
 
-```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "125%", fig.cap = "caption of 2 mode graph"}
+```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
 knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
@@
 
-```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "125%", fig.cap = "caption of 2 mode graph"}
+```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "caption of 2 mode graph"}
 knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
@@
 \end{landscape}
+
+\restoregeometry

### 2020-10-27 scripts/network_recruiting_analysis.R

@@ -46,7 +46,7 @@ V(g_1mode_hs)$ranking
 
 #events_data %>% left_join(y = univ_df, by = c("univ_id" = "school_id")) %>% group_by(school_name) %>% count() %>% View()
 
-events_data %>% left_join(y = univ_df, by = c("univ_id" = "school_id")) %>% group_by(school_name) %>% count() %>% View()
+events_data %>% left_join(y = univ_df, by = c("univ_id" = "school_id")) %>% group_by(school_name) %>% count()
 
 # Create ego network and ego network order =1
 
@@ -111,9 +111,18 @@ events_data %>% left_join(y = univ_df, by = c("univ_id" = "school_id")) %>% grou
 ## --------------------
 
 # function to plot ego graph
+    univ_id <- "160755" # Tulane # why does Tulane ego network order = 1 contain several universities from our sample?
+    #univ_id <- "228246" # Southern methodist university
+    #univ_id <- "216597" # Villanova
 
-plot_ego_graph <- function(network, characteristic, values, keys, colors = c('blue', 'purple', 'red', 'green'), title = '', graph_order = 'both') {
+    
+  # ego network
+  ego_network <- egos_psi_privu[[univ_id]]
+    
+plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('blue', 'purple', 'red', 'green'), title = univ_info[univ_info$univ_id == univ_id, ] %>% select(univ_abbrev) %>% as.character(), graph_order = 'both') {
 
+  network <- egos_psi_privu[[univ_id]]
+  
   # network object
   if (graph_order != 'both') {  # order == 1 or 2
     network <- subgraph.edges(graph = network, eids = E(network)[E(network)$order == graph_order]) # create subgraph network object if order != "both"
@@ -199,14 +208,75 @@ plot_ego_graph <- function(network, characteristic, values, keys, colors = c('bl
 # dev.off() # to fix this: Error in .Call.graphics(C_palette, value) : invalid graphics state
     
 par(mfrow=c(1, 1))  # resets to single plot
+plot_ego_graph(univ_id = "160755", characteristic = NA, values = NA, keys = NA, colors = NA, graph_order = 1)
 
[…]

### 2020-10-28 soc_of_ed_proposal.Rmd
add soc of ed proposal draft

---
title: "Sociology of Education Association Proposal"
output:
  bookdown::pdf_document2:
    toc: false
    number_sections: false
bibliography: ./other/burd_recruiting_chapter.bib
csl: ./other/apa.csl
urlcolor: blue
header-includes:
  - \usepackage{pdflscape}
  - \usepackage{geometry}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(kableExtra)
```

<!-- https://www.dropbox.com/s/3dseuoel3fwc64n/2021%20SEA%20Call%20for%20Papers.pdf -->

\pagenumbering{gobble}

<!--
Title page:
- Name
- Position
- Institutional affiliation
- Address
- Office telephone
- Email address
-->

\vspace{1in}
\begin{center}
Ozan Jaquette

Associate Professor

University of California, Los Angeles

Moore Hall 3038

310-206-3030

ozanj@ucla.edu
\end{center}

\newpage

<!--
2-page proposal:
- Brief discussion of topic
- Pertinent research literature and theory
- Research methods
- Findings
- Study significance
-->

<!-- Topic: Off-campus recruiting visits and its significance -->

Our research analyzes off-campus recruiting visits by college and university admissions staff. Market research conceives of off-campus visits as a means of identifying prospects, deepening engagement with prospects already being targeted through mail/email, and maintaining relationships with guidance counselors at "feeder schools" [@RN4323; @RN4402; @RN4664]. With respect to expenditure, @RN4664 found that private (non-profit) 4-yr institutions spent an average of 17% of their undergraduate marketing/recruiting budget on "travel" to high schools and college fairs, a higher percentage of budget allocation than any other marketing/recruiting activity. Public institutions spent an average of 16% of their budget on travel, second only to "prospective student communications" at 17%.

<!-- Literature: Importance of visits to students and guidance counselor relationship -->

A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits. @RN4324 analyzes visits from the perspective of students at two racially and socioeconomically diverse public high schools. @RN4324 found that high school visits -- including college fairs, instant decision events, and small-group representative visits -- influenced where students applied and where they enrolled. This finding was strongest for first-generation students and underrepresented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college." This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and "made them feel wanted." @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more." By contrast, affluent students with college-educated parents were less taken by such overtures and more concerned with college prestige.

Scholarship also highlight the relational function of visits. @RN3519 provides an ethnography of the admissions office at a selective private liberal arts college. During the autumn "travel season," admissions officers visited selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (pp. 53-54) because "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide" [@RN3519, p. 54]. The College tended to visit the same schools year after year because recruiting depends on long-term relationships with high schools. The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and had the resources and motivation to host a successful visit. Recruiting visits may affect outcomes such as inquiries, applications, and matriculation through their affect on high school guidance counselors. The logic is that a guidance counselor who views a college favorably will steer students to the college.

@RN4407 also argues that the desire by colleges for trustworthy information about applicant intentions creates an opportunity for high school counselors to advocate on behalf of their students. This opportunity depends on guidance counselors having personal relationships with university admissions offices and on having small enough caseloads to advocate for each student individually. There needs to be a relationship where the college can trust statements made by the high school counselor and vice versa. This relationship is the product of repeated interactions over many years.

In sum, off-campus recruiting visits are necessary for the maintenance of strong relationships that enable colleges and high schools to negotiate and send trustworthy information to one another. Without face-to-face visits, it is less likely that a college admissions counselor will "take the call" of a guidance counselor. Simultaneously, a recruiting visit between a college and a high school can be conceived as an indicator. First, the fact that the college took time and effort to make the visit suggests that the college wants to enroll students from the high school. Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students. Third, the presence of the recruiting visit indicates that the high school and the college have a relationship and suggests the probability of additional interactions (e.g., phone calls).

<!-- Research methods -->

Our project collected data about off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities. Our analysis sample is based on three different lists of post-secondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S. News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S. News and World Report Liberal Arts Colleges rankings (N=47). For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits. For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year. Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions are excluded from the analyses. Of the remaining public universities, we also issued public records requests asking for recruiting events data as a means of quality assurance. Our final analysis sample consists of 17 public research universities, 13 private research universities, and 13 private liberal arts colleges.

We utilize network methods to analyze the recruiting visits data for two, related reasons. First, social network analysis privileges the relationship between actors. The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p. 175]. Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network.

We will focus on network analyses of visits by colleges and universities to private high schools. Analyses are motivated by two, related research questions. First, which types of private high schools receive visits from which types of colleges and universities? Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?

<!-- Findings -->

Figure \@ref(fig:two-mode-plot) shows a two-mode network plot consisting of visits by public and private colleges and universities to private high schools.

Figure \@ref(fig:two-mode-plot-privu) shows a two-mode network plot consisting of visits by private colleges and universities to private high schools.

Table \@ref(tab:ego-table-privu) shows characteristics of private high schools visited by each private college and university.

Table \@ref(tab:hs-print-privu) shows characteristics of the top 20 most visited private high schools by private colleges and universities.

Table \@ref(tab:hs-table-privu-agg) shows characteristics of private high schools by number of private colleges and universities that visited.

<!-- Study significance -->

\newpage

# References

<div id="refs"></div>

\newpage

```{r, ego-table-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_ego.RDS')
knitr::kable(
  df %>% select(-Characteristics), row.names = F, # select(-ID, -Characteristics)
  caption = 'Characteristics of private high schools visited by each private college and university') %>% landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-print-privu, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-school_id,-closeness), caption = 'Characteristics of the top 20 most visited private high schools by private colleges and universities') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r, hs-table-privu-agg, echo = FALSE}
df <- readRDS('./assets/tables/table_2mode_agg.RDS')

knitr::kable(df, caption = 'Characteristics of private high schools by number of private colleges and universities that visited') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

\newpage

\newgeometry{margin=0cm}

\begin{landscape}

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network plot consisting of visits by public and private colleges and universities to private high schools"}
knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```

```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "2-mode network plot consisting of visits by private colleges and universities to private high schools"}
knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
```

\end{landscape}

### 2020-10-28 manuscript.Rmd
draft changes

@@
 
+Figure \@ref(fig:villanova-religion) shows the ego network of Villanova University, with religious affiliation
+
+Figure \@ref(fig:emory-region) shows the ego network of Emory University, with geographic region
+
+Figure \@ref(fig:rank-cluster1) shows the academic reputation of private high schools visited by selected colleges universities in cluster 1
+
+Figure \@ref(fig:race-cluster4) shows the racial composition of visited private high schools, selected colleges
+
 Table \@ref(tab:ego-table-privu) shows characteristics of private high schools visited by each private college and university
@@
 
+```{r}
+df <- readRDS('./assets/tables/table_ego.RDS')
+knitr::kable(
+  df %>% select(ID,University,Cluster,Type,Rank,Characteristics,c1_lt10,c2_10to25,c3_25to50,`c4_50+`), row.names = F, # select(-ID, -Characteristics)
+  caption = 'la la') %>% landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
 ```{r, hs-print-privu, echo = FALSE}
@@
 
+```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Ego network of Villanova University, with religious affiliation"}
+knitr::include_graphics('assets/figures/villanova_religion.pdf')
+```
+
+```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Ego network of Emory University, with geographic region"}
+knitr::include_graphics('assets/figures/emory_region.pdf')
+```
+
+```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
+knitr::include_graphics('assets/figures/rank_cluster1.pdf')
+```
+
+```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
+knitr::include_graphics('assets/figures/race_cluster4.pdf')
+```
+
 \end{landscape}

### 2020-10-28 scripts/network_recruiting_analysis.R

@@ -111,18 +111,76 @@ events_data %>% left_join(y = univ_df, by = c("univ_id" = "school_id")) %>% grou
 ## --------------------
 
 # function to plot ego graph
-    univ_id <- "160755" # Tulane # why does Tulane ego network order = 1 contain several universities from our sample?
+    #univ_id <- "160755" # Tulane # why does Tulane ego network order = 1 contain several universities from our sample?
     #univ_id <- "228246" # Southern methodist university
-    #univ_id <- "216597" # Villanova
+    univ_id <- "216597" # Villanova
 
     
   # ego network
   ego_network <- egos_psi_privu[[univ_id]]
-    
-plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('blue', 'purple', 'red', 'green'), title = univ_info[univ_info$univ_id == univ_id, ] %>% select(univ_abbrev) %>% as.character(), graph_order = 'both') {
+
+  
+  vertex_attr_names(ego_network)
+  
+  table(V(ego_network)$religion,  useNA = "always")
+  
+  V(ego_network)$name[V(ego_network)$type == TRUE]
+  
+proportions(table(V(ego_network_order1)$ranking, useNA = "always"))  
+
+V(ego_network)$religion[V(ego_network)$type == TRUE]
+V(ego_network)$religion[V(ego_network)$type == FALSE]
+
+univ_id <- "216597" # Villanova
+# ego network
+ego_network <- egos_psi_privu[[univ_id]]
+
+
+vertex_attr(ego_network, "religion")
+
+vertex_attr(ego_network, "religion") <- case_when(
+        vertex_attr(network, "type") == FALSE ~ 'salmon',
+        vertex_attr(network, "type") == TRUE &  vertex_attr(network, "name") != univ_id ~ 'lightblue',
+        vertex_attr(network, "type") == TRUE &  vertex_attr(network, "name") == univ_id ~ 'purple',
+      )
+
+      
+# The U.S. Department of Education classifies conservative Christian schools
+# as those that have membership in at least one of four associations (Kena et al., 2016): 
+  # Accelerated Christian Education
+  # American Association of Christian Schools
+  # Association of Christian Schools International
+  # Oral Roberts University Education Fellowship
+
[…]

### 2020-10-28 manuscript.Rmd
finished rough draft of changes to visits by private colleges/universities

--- 2020-10-27 manuscript.Rmd
@@
 
-Figure \@ref(fig:two-mode-plot) shows a plot of the two-mode network, with private high schools vertices the color salmon, public research universities shown in violet, and private colleges and universities shown in green green.
+Figure \@ref(fig:two-mode-plot) plots the two-mode network of visits to private high schools by all colleges and universities in our sample, with private high schools vertices the color salmon, public research universities shown in violet, and private colleges and universities shown in green green.
 The graph layout places vertices closer together if they are similar to one another in terms of network structure.
@@
 
-Figure \@ref(fig:two-mode-plot-privu) shows a plot of the two-mode network of private colleges and universities
+Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
+Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
+We used XYZ community detection approach [add footnote w/ details?] to allocate private colleges and universities [?
+and private high schools] to clusters.
+Four clusters emerge.
+The largest cluster consists largely of nonsectarian liberal arts colleges (e.g., Williams, Swarthmore, Colorado College).
+Cluster 2 consists of Emory University, Tulane, Northwestern, and Sewanee.
+These universities all have relatively strong ties to Southern private high schools.
+Cluster 3 consists of three catholic universities -- Notre Dame, Villanova, Boston College -- and Case Western Reserve and Stevens Institute of Technology.
+Although not a Catholic University, Stevens Institute of Technology has strong ties to Catholic private schools (representing X% of visits).
+Finally, cluster 4 consists of three religiously affiliated Texas universities -- Southern Methodist, Baylor, Texas Christian University -- and the University of Denver.
 
-Table \@ref(tab:ego-table-privu) shows characteristics of private high schools visited by each private college and university
+Figure \@ref(fig:two-mode-plot-privu) plots the two-mode network of visits by private colleges and universities to private high schools, with vertex color determined by community cluster.
+The placement of college and high school vertices on an X-Y axis/coordinates is determined such that vertices with many direct and indirect ties are closer together.
+Although the process of placing vertices was separate from the process of determining community cluster, vertices within the same cluster tend to be closer to one another than those of different clusters.
+For example, the nonsectarian liberal arts colleges in Cluster 1 tend to be be close to one another and also relatively close to the highest concentration of private high schools in cluster 1, suggesting that these colleges visit substantially overlapping sets of private high schools.
+For Cluster 2, by contrast, Northwestern and Emory are relatively far from Tulane and Sewanee.
 
-Table \@ref(tab:hs-print-privu) shows characteristics of the 20 private high schools that were visited by the most private colleges and universities
+Addressing our two motivating research questions -- which schools receive visits from which colleges/universities and the extent to which visits are more likely to occur between organizations that share certain characteristics -- requires analyses that are more granular than Figure \@ref(fig:two-mode-plot-privu).
 
-Table \@ref(tab:hs-table-privu-agg) shows characteristics of private high schools by number of private colleges and universities that visited
+Table \@ref(tab:ego-table-privu) shows the characteristics of private high schools visited by each private college and university.
+This table was created from the ego networks of each private college and university.
+As such, we visualize selected ego networks to illustrate several patterns that emerge from Table \@ref(tab:ego-table-privu).
+Ego networks consist of an ego (a single college/university), the set of high schools the ego visted (one degree of separation from the ego), and the set of colleges/universities that also visited high schools visited by the ego (two degrees of separation from the ego).
+Figure \@ref(fig:villanova-religion) shows the ego network of Villanova University, with vertex color determined by religious affiliation.
+About 50% of Villanova's visits were to Catholic schools, a percentage [?percent?] much higher than most colleges and universities shown in Table \@ref(tab:ego-table-privu), and second only to Notre Dame University.
+In Figure \@ref(fig:villanova-religion), Notre Dame is closer to Villanova than any other college/university in the Villanova ego network, suggesting that Villanova and Notre Dame visit substantially overlapping sets of schools.
+Boston College, another Catholic university, is situated a bit further away from Villanova in the clump of colleges that includes Case Western, Tulane, Sewanee, Southern Methodist, and TCU, all of which visit a relatively high share of Catholic high schools, despite not being Catholic universities.
+By contrast, Villanova is far from nonsectarian liberal arts colleges (e.g., Swarthmore, Smith, Colorado College) which visit fewer Catholic high schools.
+
+Figure \@ref(fig:emory-region) shows the ego network of Emory University, with vertex color determined by geographic region.
+Located in Atlanta, about 47% of Emory's visits were to schools in the South.
+Figure \@ref(fig:emory-region) indicates that Emory's network structure is similar to several other southern universities -- including Tulane, TCU, SMU, and Sewanee, but is dissimilar from Baylor University which made about 56% of visits in the South, but with a focus on schools with a Christian religious affiliation.
+Figure \@ref(fig:emory-region) also suggests that the set of schools visited by Emory overlaps substantially with several institutions located in the Northeast (e.g., Villanova, Boston College, Middlebury) and the Midwest (e.g., Case Western Reserve, Northwestern, Notre Dame).
+
+Figure \@ref(fig:rank-cluster1) shows the academic reputation of private high schools visited by [selected] private colleges and universities.
+Compared to other institutions, the cluster of nonsectarian liberal arts colleges visits a higher share of high schools ranked in the top 200 of Niche and a lower share of schools with a grade of "A" or lower.
+By contrast, Catholic universities (in cluster 3) and Christian affiliated Texas universities (cluster 4) tend to visit a higher share of high schools graded as "A" or lower by Niche.
+
+Figure \@ref(fig:race-cluster4) shows the racial composition of visited private high schools by college [REVISE PARAGRAPH ONCE WE FIX MISSING VALUES FOR RACE].
+The big take-away is that the most colleges predominantly visit high schools where fewer than 25% of students identify as Black, Latinx, or Native.
+This finding is largely true across clusters.
+Private high schools tend to have a higher share of White students than public high schools.
+Moreover, the private high schools that were visited by private colleges and universities in our sample had a lower share of Black/Latinx/Native students, on average, than the population of private high schools.
+Our findings suggest that the low number of Black/Latinx/Native students at private colleges and universities may be driven by thse institutions explicitly recruiting from private high schools that enroll few Black/Latinx/Native students.
+
+[NEED TRANSITION TO FOCUS NOW ON HIGH SCHOOLS]
+Which private high schools receive the most visits?
+Table \@ref(tab:hs-print-privu) shows characteristics of the 20 private high schools that were visited by the most private colleges and universities.
+The last two columns of Table \@ref(tab:hs-print-privu) are "degree" and "strength," which are related measures of vertex "centrality." Measures of centrality attempt to identify the most important or influential actors in a social network.
+"Degree" is defined as the number of edges direclty connected to a vertex.
+In Table \@ref(tab:hs-print-privu), the degree of a high school is the number of private colleges and universities in our sample that visited.
+The concept "strength" is generally defined as a weighted measure of degree.
+In our study, colleges often made more than one visit to the same high school in 2017.
+Thus, Table \@ref(tab:hs-print-privu) defines strength as the total number of visits from private colleges and universities in our sample.
+
+The Kent Denver School, the top ranked school in \@ref(tab:hs-print-privu),was visited by 23 of the 26 private colleges and universities in our sample.
+Choate Rosemary Hall was visited by 21 colleges and universities, but these 21 institutions made 34 total visits.
+Most schools in Table \@ref(tab:hs-print-privu) are mostly nonsectarian.
+Although all received a Niche grade of "A+", they are not uniformly in the upper-echelon of schools ranked in the top 50 or top 100 nationwide.
+With the exception of St.
+Ignatius Prep in Chicago and the Maret School in Washington DC, students who identify as Black, Latinx, or Native comprise less than 20% of all students.
+
+Table \@ref(tab:hs-table-privu-agg) shows the characteristics of private high schools by degree band (e.g., visits from 15+, 10-14, etc).
+Schools that received visits from 4 or fewer private colleges and universities enrolled a greater share of Black/Latinx/Native students.
+These schools were also disproportionately Catholic schools and were more likely to recieve a grade of "A" or lower from Niche.
+
+Whereas Tables \@ref(tab:hs-print-privu) and \@ref(tab:hs-table-privu-agg) examine centrality, they do not assess the extent to which high schools cluster into groups, with some high schools visited by nearly all colleges and universities and other groups of high schools only receiving visits from a particular subset of colleges and universities.
+[THIS IS WHERE THE DIRECT VS.
+INDIRECT CONNECTION ANALYSIS RECOMMENDED BY RUSS WOULD GO.
+WE MIGHT ADD THIS TO BURD CHAPTER OR DO AFTER BURD CHAPTER SUBMITTED]
 
@@
 
-CRYSTAL ADDS TABLES/FIGURES
+ADD TABLES/FIGURES OF VISITS BY PUBLIC RESEARCH UNIVERSITIES.
 
@@
   caption = 'ego table caption') %>% landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r, include = FALSE, eval = FALSE}
+df <- readRDS('./assets/tables/table_ego.RDS')
+#df %>% select(ID,University,Cluster,Type,Rank,c1_lt10,c2_10to25,c3_25to50,`c4_50+`) %>%mutate(lt25 = as.numeric(c1_lt10) + as.numeric(c2_10to25))
+
+knitr::kable(
+  df %>% select(ID,University,Cluster,Rank,c1_lt10,c2_10to25,c3_25to50,`c4_50+`), row.names = F, # select(-ID, -Characteristics) Characteristics ,Type
+  caption = 'la la') %>% landscape(margin = NULL) %>%
   kable_styling(latex_options = 'scale_down')
@@
 
+```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, with religious affiliation"}
+knitr::include_graphics('assets/figures/villanova_religion.pdf')
+```
+
+```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Ego network of Emory University, with geographic region"}
+knitr::include_graphics('assets/figures/emory_region.pdf')
+```
+
+```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
+knitr::include_graphics('assets/figures/rank_cluster1.pdf')
+```
+
+```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
+knitr::include_graphics('assets/figures/race_cluster4.pdf')
+```
+
 \end{landscape}

### 2020-10-28 scripts/network_recruiting_analysis.R

@@ -267,6 +267,8 @@ plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('bl
  dev.off() # to fix this: Error in .Call.graphics(C_palette, value) : invalid graphics state
 
 
+
+
 par(mfrow=c(1, 1))  # resets to single plot
 plot_ego_graph(univ_id = "160755", characteristic = NA, values = NA, keys = NA, colors = NA, graph_order = 1)
 
@@ -305,17 +307,16 @@ plot_ego_graph(univ_id = "115409", characteristic = 'rank_cat2', values = c('c1_
 # 115409
 dev.off() # close the file
 
-pdf("assets/figures/race_cluster1.pdf") # open file
-
 #For catholic, show order equals both. one big graph of one univ and maybe characteristic equals religious
 
   # villanova ego network, religion overlayed
-  pdf("assets/figures/villanova_religion.pdf") # open file
+  pdf("assets/figures/villanova_religion.pdf", paper = "a4r") # open file
   
     par(mar=c(5, 4, 4, 2) + 0.1) # default margins
     #par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
   
-    plot_ego_graph(univ_id = "216597", characteristic = 'religion', values = c('catholic', 'conservative_christian', 'nonsectarian', 'other_religion'), keys = c('Catholic', 'Conservative Christian', 'Nonsectarian', 'Other'), title = "", graph_order = 'both')
+    plot_ego_graph(univ_id = "216597", characteristic = 'religion', values = c('catholic', 'conservative_christian', 'nonsectarian', 'other_religion'), keys = c('Catholic', 'Conservative Christian', 'Nonsectarian', 'Other'), title = "", graph_order = 'both', margin = -0.3)
+    
   dev.off() # close the file  
 
 
@@ -339,6 +340,10 @@ dev.off() # close the file
   # 147767 Northwestern
   # 139658 Emory
   # 160755 Tulane
+  # 223232 baylor
+
+# baylor
+plot_ego_graph(univ_id = "223232", characteristic = 'religion', values = c('catholic', 'conservative_christian', 'nonsectarian', 'other_religion'), keys = c('Catholic', 'Conservative Christian', 'Nonsectarian', 'Other'), title = "", graph_order = 'both', margin = -0.3)
     
 # Maybe for TEXAS cluster show small multiples of race 
 

### 2020-10-30 sea_conference/soc_of_ed_proposal.Rmd
moved soc of ed to a sub-directory

--- 2020-10-28 soc_of_ed_proposal.Rmd
@@
     number_sections: false
-bibliography: ./other/burd_recruiting_chapter.bib
-csl: ./other/apa.csl
+bibliography: ./../other/burd_recruiting_chapter.bib
+csl: ./../other/apa.csl
 urlcolor: blue
@@
 ozanj@ucla.edu
+
+!!!!!!!!!!!CRYSTAL ADD YOUR CONTACT INFO HERE!!!!!!!!!!!
 \end{center}
@@
 <!-- Topic: Off-campus recruiting visits and its significance -->
+
+# Overview
+
+This paper analyzes off-campus recruiting visits to U.S. private high schools made by a sample of public research universities and sample of selective private colleges and universities in 2017.
+
+We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
+Analyses are informed by two broad, related questions.
+First, which types of private high schools receive visits from which types of colleges and universities?
+Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+
+This chapter analyzes off-campus recruiting visits by a sample of public research universities and a sample of selective private colleges and universities in 2017.
+We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.
+
+this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities.
+
+The motivation for comparing the behavior of public and private coleges/universities is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities.
+By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities.
+From this perspective, out-of-state visits to private schools by public research universities is one example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543].
+Therefore, by comparing the (mostly out-of-state) visits to private high schools by public research universities to those of private colleges and universities, we hope to develop new insights about the privatization of public higher education.
+
+We utilize network methods to analyze the recruiting visits data for two, related reasons.
+First, social network analysis privileges the relationship between actors.
+The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
+175].
+Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network.
+
+We will focus on network analyses of visits by colleges and universities to private high schools.
+Analyses are motivated by two, related research questions.
+First, which types of private high schools receive visits from which types of colleges and universities?
+Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
+
+# Literature review and theory
+
+# Data and methods
+
+# Findings
+
+# Significance
 
@@
 ```{r, ego-table-privu, echo = FALSE}
-df <- readRDS('./assets/tables/table_ego.RDS')
+df <- readRDS('./../assets/tables/table_ego.RDS')
 knitr::kable(
@@
 ```{r, hs-print-privu, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode.RDS') %>% head(n=20)
+df <- readRDS('./../assets/tables/table_2mode.RDS') %>% head(n=20)
 
@@
 ```{r, hs-table-privu-agg, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode_agg.RDS')
+df <- readRDS('./../assets/tables/table_2mode_agg.RDS')
 
@@
 ```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network plot consisting of visits by public and private colleges and universities to private high schools"}
-knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
+knitr::include_graphics('./../assets/figures/plot_g_2mode.pdf')
 #https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
@@
 ```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "2-mode network plot consisting of visits by private colleges and universities to private high schools"}
-knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
+knitr::include_graphics('./../assets/figures/plot_g_2mode_privu.pdf')
 ```

### 2020-10-30 scripts/network_recruiting_analysis.R
update 2mode tables

@@ -606,51 +606,6 @@ saveRDS(ego_table_pubu, file = './assets/tables/table_ego_pubu.RDS')
 ## TABLE FROM 2-MODE IGRAPH OBJECTS
 ## ---------------------------------
 
-# Create table of characteristics
-vertex_attr_names(g_2mode_privu)
-
-V(g_2mode_privu)$degree <- degree(g_2mode_privu)
-V(g_2mode_privu)$strength <- strength(g_2mode_privu)
-V(g_2mode_privu)$closeness <- closeness(graph = g_2mode_privu, normalized = T)
-
-t_2mode_privu <- data.frame(
-  school_id = V(g_2mode_privu)$name,
-  school_name = V(g_2mode_privu)$school_name,
-  city = V(g_2mode_privu)$city,
-  state = V(g_2mode_privu)$state_code,
-  region = V(g_2mode_privu)$region,
-  religion = V(g_2mode_privu)$religion,
-  pct_blacklatinxnative = V(g_2mode_privu)$pct_blacklatinxnative,
-  race = V(g_2mode_privu)$pct_blacklatinxnative_cat,
-  ranking_score = V(g_2mode_privu)$ranking,
-  ranking_numeric = V(g_2mode_privu)$ranking_numeric,
-  ranking = V(g_2mode_privu)$rank_cat2,
-  type = V(g_2mode_privu)$type,
-  degree = V(g_2mode_privu)$degree,
-  strength = V(g_2mode_privu)$strength,
-  closeness = V(g_2mode_privu)$closeness
-)
-
-# temporarily get rid of unmerged rows
-t_2mode_privu <- t_2mode_privu %>% filter(type == F, !is.na(school_name)) %>%
-  mutate(degree_band = case_when(degree >= 15 ~ '15+',
-                                 degree >= 10 ~ '10-14',
-                                 degree >= 5 ~ '5-9',
-                                 TRUE ~ as.character(degree)))
-
-full_2mode_table <- t_2mode_privu %>% arrange(-degree) %>%
-  select(school_id, school_name, city, state, region, religion, pct_blacklatinxnative, ranking_score, ranking_numeric, degree, closeness, strength)
-
-View(full_2mode_table)
-
-saveRDS(full_2mode_table, file = './assets/tables/table_2mode.RDS')
-# readr::write_file(knitr::kable(head(full_2mode_table), 'latex'), 'assets/tables/table_2mode.tex')
-
[…]

### 2020-10-30 sea_conference/soc_of_ed_proposal.Rmd
gotta go!

@@
 
-This paper analyzes off-campus recruiting visits to U.S. private high schools made by a sample of public research universities and sample of selective private colleges and universities in 2017.
-
-We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
-Analyses are informed by two broad, related questions.
+This paper uses social network methods to analyze off-campus recruiting visits to U.S.
+private high schools, utilizing data we collected in 2017 from a sample of public research universities and a sample of selective private colleges and universities.
+Analyses are broadly informed by two, related questions.
 First, which types of private high schools receive visits from which types of colleges and universities?
 Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+Third, after examining visit patterns separately for public and private postsecondary institutions, we examine similarities and differences across public versus private postsecondary institutions.
 
-This chapter analyzes off-campus recruiting visits by a sample of public research universities and a sample of selective private colleges and universities in 2017.
-We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.
-
-this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities.
+This study builds from previous research analyzing recruiting visits by public research universities.
+As described in more detail below, 12 of the 15 public research universities in our sample made far more out-of-state visits than in-state visits, a finding antithetical to the stated mission of most public research universities.
+These out-of-state visits focused on wealthy, predominantly white schools and communities.
+Additionally, most public research universities made a disproportionate number of out-of-state visits to private schools, but visited few in-state private schools.
+[TRIM]
 
@@
 
+# DATA/METHODS
+
+This chapter analyzes off-campus recruiting visits by a sample of public research universities and a sample of selective private colleges and universities in 2017.
+We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.
+
+this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities.
+
+PREVIOUS TEXT
 We will focus on network analyses of visits by colleges and universities to private high schools.

### 2020-10-31 scripts/network_recruiting_analysis.R
add 2mode plots colored by clusters

@@ -526,6 +526,52 @@ plot(
 dev.off() # close the file
 
 
+## ---------------------------
+## PLOT 2-MODE IGRAPH OBJECTS
+## ---------------------------
+
+par(mfrow=c(1, 1))
+
+save_2mode_plot <- function(network, plot_name, plot_margin = -0.5) {
+  
+  cluster_2mode <- cluster_fast_greedy(network)
+  membership_2mode <- membership(cluster_2mode)
+  
+  library(plyr)
+  colors_2mode_privu <- revalue(as.character(membership_2mode), c(
+    '1' = 'red',
+    '2' = 'lightblue',
+    '3' = 'green',
+    '4' = 'yellow'
+  ))
+  detach(package:plyr, unload = TRUE)
+  
+  pdf(paste0('assets/figures/', plot_name))
+  
+  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
+  
+  plot(
+    x = network, 
+    vertex.label = if_else(V(network)$type, V(network)$school_name, ''),
+    vertex.color = colors_2mode_privu,
+    vertex.frame.color = if_else(V(network)$type, 'black', 'lightgray'),
+    vertex.shape = 'circle',
+    vertex.size = if_else(V(network)$type, 3, 1),
+    edge.lty = 3,
+    edge.lty = 0.5,
+    edge.color = 'lightgrey',
+    layout = layout_with_fr,
+    margin = plot_margin
+  )
+  
+  dev.off()
+}
+
+save_2mode_plot(g_2mode, 'plot_2mode.pdf', plot_margin = -0.6)
+save_2mode_plot(g_2mode_privu, 'plot_2mode_privu.pdf', plot_margin = -0.7)
+save_2mode_plot(g_2mode_pubu, 'plot_2mode_pubu.pdf')
+
+
 ## ------------------------------
 ## TABLE FROM EGO IGRAPH OBJECTS
 ## ------------------------------

### 2020-10-31 sea_conference/soc_of_ed_proposal.Rmd
draft changes

--- 2020-10-30 sea_conference/soc_of_ed_proposal.Rmd
@@
 
-This paper analyzes off-campus recruiting visits to U.S. private high schools made by a sample of public research universities and sample of selective private colleges and universities in 2017.
+This paper uses social network methods to analyze off-campus recruiting visits to U.S.
+private high schools by a sample of public research universities and selective private colleges and universities.
+Analyses are informed by three broad research questions.
+First, which types of private high schools receive visits from which types of colleges and universities?
+Related, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+Third, how does the off-campus recruiting networt of public research universities compare to that of selective private colleges and universities.
 
-We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
-Analyses are informed by two broad, related questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+Our focus on private high schools is motivated by previous research on recruiting visits by pubilc research universities [Author XXXX].
+The majority made far more out-of-state visits than in-state visits.
+These out-of-state visits were concentrated on wealthy, predominantly white schools and communities, and with a disproportionate number of out-of-state visits to private schools.
 
-This chapter analyzes off-campus recruiting visits by a sample of public research universities and a sample of selective private colleges and universities in 2017.
-We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.
-
-this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities.
-
-The motivation for comparing the behavior of public and private coleges/universities is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities.
+The motivation for comparing the behavior of public and private coleges/universities is based on the idea that out-of-state visits to private high schools are antithetical to the stated mission of public research universities.
 By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities.
-From this perspective, out-of-state visits to private schools by public research universities is one example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543].
+We suggest that out-of-state visits to private schools by public research universities is an example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543].
 Therefore, by comparing the (mostly out-of-state) visits to private high schools by public research universities to those of private colleges and universities, we hope to develop new insights about the privatization of public higher education.
@@
 First, social network analysis privileges the relationship between actors.
-The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
+The discussion of Stevens and Khan [CITE] suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
 175].
-Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network.
-
-We will focus on network analyses of visits by colleges and universities to private high schools.
-Analyses are motivated by two, related research questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
+Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network, making it suitable for social network analyses.
 
@@
 
-# Data and methods
+<!-- Literature: Importance of visits to students and guidance counselor relationship -->
 
-# Findings
-
-# Significance
-
-Our research analyzes off-campus recruiting visits by college and university admissions staff.
 Market research conceives of off-campus visits as a means of identifying prospects, deepening engagement with prospects already being targeted through mail/email, and maintaining relationships with guidance counselors at "feeder schools" [@RN4323; @RN4402; @RN4664].
@@
 
-<!-- Literature: Importance of visits to students and guidance counselor relationship -->
-
-A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits.
-@RN4324 analyzes visits from the perspective of students at two racially and socioeconomically diverse public high schools.
-@RN4324 found that high school visits -- including college fairs, instant decision events, and small-group representative visits -- influenced where students applied and where they enrolled.
-This finding was strongest for first-generation students and underrepresented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college." This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and "made them feel wanted." @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more." By contrast, affluent students with college-educated parents were less taken by such overtures and more concerned with college prestige.
-
-Scholarship also highlight the relational function of visits.
+A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits [EG] [RN4520; RN4538; RN4324; RN3519].
+This literature highlights the relational function of visits.
 @RN3519 provides an ethnography of the admissions office at a selective private liberal arts college.
@@
 
+@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities." The answer to this question begins by thinking about the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors.
+Private high school counselors face pressure to send _all_ students to the best college possible.
+However,  "some of these students are slightly better than others.
+These students will likely get into more than one school -- but they can only attend one.
+And this will lower the chances of your "second-best" students getting into top schools" [@RN4407] [p.
+173-174].
+Selective colleges want high achieving students who can pay tuition and donate and they also want low acceptance and high yield rates to move up the rankings.
+College admissions officers receive applications from many outstanding students.
+But "These outstanding students will also be outstanding to Princeton, Yale, Stanford, and everywhere else.
+How do you know the ones you pick will attend your school?
+you can't quite trust applicants, as they are all likely to tell you how much they want to go to your school.
+And if students you accept go somewhere else, there's not much you can do.
+But you can get better information -- information you want -- from their high school" [@RN4407] [pg.
+173?].
+
 @RN4407 also argues that the desire by colleges for trustworthy information about applicant intentions creates an opportunity for high school counselors to advocate on behalf of their students.
@@
 This relationship is the product of repeated interactions over many years.
+Off-campus recruiting visits are necessary for the maintenance of strong relationships that enable colleges and high schools to negotiate and send trustworthy information to one another.
+Without face-to-face visits, it is less likely that a college admissions counselor will "take the call" of a guidance counselor.
 
-In sum, off-campus recruiting visits are necessary for the maintenance of strong relationships that enable colleges and high schools to negotiate and send trustworthy information to one another.
-Without face-to-face visits, it is less likely that a college admissions counselor will "take the call" of a guidance counselor.
-Simultaneously, a recruiting visit between a college and a high school can be conceived as an indicator.
-First, the fact that the college took time and effort to make the visit suggests that the college wants to enroll students from the high school.
-Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
-Third, the presence of the recruiting visit indicates that the high school and the college have a relationship and suggests the probability of additional interactions (e.g., phone calls).
+# Data
 
@@
 Our project collected data about off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities.
+We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.
 Our analysis sample is based on three different lists of post-secondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S.
@@
 
-We utilize network methods to analyze the recruiting visits data for two, related reasons.
-First, social network analysis privileges the relationship between actors.
-The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
-175].
-Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network.
+ADD ONE SENTENCE THAT SAYS WE MERGED IN THE FOLLOWING SET OF SECONDARY DATA SOURCES
 
-We will focus on network analyses of visits by colleges and universities to private high schools.
-Analyses are motivated by two, related research questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
+# Methods
+
+A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "edges" between these actors.
+Whereas "one mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two mode" networks consit of vertices associated with one type of actor/entity having connections to vertices of another type.
+For example, an an actor-movie network consists of actors -- mode 1 -- who appear in movies -- mode 2 and an actor shares an edge with a movie if the actor appears in the movie.
+The social network analyzed in this chapter is a two-mode network, where vertices consists of colleges/universities (mode 1) and high schools (mode 2) and an "edge" is defined as a visit from a college/university to a private high school [DELETE THIS SENTENCE OR THE REDUNDANT ONE IN BELOW PARAGRAPH].
+
+Our analyses draw from analyses of "corporate board-director" networks because these are the most commonly analyzed two-mode networks in the social networks literature [e.g.] [@RN4663].
+Board-director networks consist of directors (mode 1) who serve on organizational boards (mode 2).
+Our school-college network is a two-mode network composed of two sets of vertices, private high schools (mode 1) and colleges/universities (mode 2).
+Off-campus recruiting visits are edges (e.g., high school $i$ shares an edge with college $j$ if high school $i$ receives at least one visit from college $j$) and visits can only occur between a school-college pair (not a school-school pair or a college-college pair).
+Our school-college network is a two-mode network composed of high schools (mode 1) who are visited by colleges and universities (mode 2).
+This (weighted) network is represented as a school-by-college matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 colleges/universities) in which matrix cell $a_{i,j}$ identifies the number of visits that high school $i$ received from college/university $j$.
+
+# Findings
 
 <!-- Findings -->
+YOU CAN JUST EXPLICITLY SAY THAT WE DON'T HAVE SPACE TO TALK ABOUT RESULTS, BUT HERE ARE THE SORT OF ANALYSES WE ARE WORKING ON.
+SHOW THE PRIVATE COLLEGES/UNIVERSITIES 2-MODE NETWORK WITH COLORS DETERMINED BY COMMUNITY CLUSTER.
+SHOW THE PRIVATE COLLEGE/UNIVERSITY EGO TABLE; SHOW THE FULL  2-MODE NETWORK WITH COLORS DETERMINED BY COMMUNITY CLUSTER.
+SHOW THE LIST OF TOP 20 MOST CENTRAL.
 
@@
 Table \@ref(tab:hs-table-privu-agg) shows characteristics of private high schools by number of private colleges and universities that visited.
+
+# Significance
+
+The vast majority of research on enrollment management behaviors focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [E.G.] <!-- [@RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948] -->.
+By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664].
+With the notable exception of a small sociological case-study literature [e.g., ] -- the research community has ignores a great number of enrollment management practices that plausibly affect access to higher education.
+As a consequence, enrollment management remains an opaque industry to policymakers and the public.
+We argue that developing thoughtful policies about enrollment management depends on researchers collectively devloping empirical literatures that document enrollment management practices and evaluate the effects of these practices on opportunities for students.
 

### 2020-10-31 sea_conference/soc_of_ed_proposal.Rmd
update soc of ed proposal

--- 2020-10-30 sea_conference/soc_of_ed_proposal.Rmd
@@
   - \usepackage{geometry}
+  - \usepackage{titlesec}
+  - \titlespacing*{\section}{0pt}{8pt plus 4pt minus 2pt}{4pt plus 4pt minus 2pt}
 ---
@@
 
-!!!!!!!!!!!CRYSTAL ADD YOUR CONTACT INFO HERE!!!!!!!!!!!
+\vspace{1cm}
+
+Crystal Han
+
+University of California, Los Angeles
+
+669-255-7617
+
+cyouh95@ucla.edu
 \end{center}
@@
 
-<!-- Topic: Off-campus recruiting visits and its significance -->
-
 # Overview
 
-This paper analyzes off-campus recruiting visits to U.S. private high schools made by a sample of public research universities and sample of selective private colleges and universities in 2017.
+This study uses social network methods to analyze off-campus recruiting visits to U.S.
+private high schools by a sample of public research universities and selective private colleges and universities.
+Analyses are informed by three broad research questions.
+First, which types of private high schools receive visits from which types of colleges and universities?
+Related, to what extent do colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+Third, how does the off-campus recruiting network of public research universities compare to that of selective private colleges and universities?
 
-We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
-Analyses are informed by two broad, related questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
-
-This chapter analyzes off-campus recruiting visits by a sample of public research universities and a sample of selective private colleges and universities in 2017.
-We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.
-
-this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities.
-
-The motivation for comparing the behavior of public and private coleges/universities is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities.
+Our focus on private high schools is motivated by previous research on recruiting visits by public research universities, which found that a majority of universities made a disproportionate number of out-of-state visits to private schools [@RN1234].
+The motivation for comparing the behavior of public and private colleges/universities is based on the idea that out-of-state visits to private high schools are antithetical to the stated mission of public research universities.
 By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities.
-From this perspective, out-of-state visits to private schools by public research universities is one example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543].
+We suggest that out-of-state visits to private schools by public research universities is an example of "privatization." A weakness of the privatization literature is that few empirical studies compare public and private institutions with respect to particular behaviors associated with privatization [@RN4543].
 Therefore, by comparing the (mostly out-of-state) visits to private high schools by public research universities to those of private colleges and universities, we hope to develop new insights about the privatization of public higher education.
@@
 First, social network analysis privileges the relationship between actors.
-The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
+The discussion of @RN3519 and @RN4407 suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
 175].
-Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network.
-
-We will focus on network analyses of visits by colleges and universities to private high schools.
-Analyses are motivated by two, related research questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
+Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network, making it suitable for social network analyses.
 
@@
 
-# Data and methods
-
-# Findings
-
-# Significance
-
-Our research analyzes off-campus recruiting visits by college and university admissions staff.
 Market research conceives of off-campus visits as a means of identifying prospects, deepening engagement with prospects already being targeted through mail/email, and maintaining relationships with guidance counselors at "feeder schools" [@RN4323; @RN4402; @RN4664].
-With respect to expenditure, @RN4664 found that private (non-profit) 4-yr institutions spent an average of 17% of their undergraduate marketing/recruiting budget on "travel" to high schools and college fairs, a higher percentage of budget allocation than any other marketing/recruiting activity.
-Public institutions spent an average of 16% of their budget on travel, second only to "prospective student communications" at 17%.
-
-<!-- Literature: Importance of visits to students and guidance counselor relationship -->
-
-A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits.
-@RN4324 analyzes visits from the perspective of students at two racially and socioeconomically diverse public high schools.
-@RN4324 found that high school visits -- including college fairs, instant decision events, and small-group representative visits -- influenced where students applied and where they enrolled.
-This finding was strongest for first-generation students and underrepresented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college." This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and "made them feel wanted." @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more." By contrast, affluent students with college-educated parents were less taken by such overtures and more concerned with college prestige.
-
-Scholarship also highlight the relational function of visits.
 @RN3519 provides an ethnography of the admissions office at a selective private liberal arts college.
-During the autumn "travel season," admissions officers visited selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (pp.
-53-54) because "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide" [@RN3519, p.
-54].
 The College tended to visit the same schools year after year because recruiting depends on long-term relationships with high schools.
@@
 
+@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities." Private high school counselors face pressure to send _all_ students to the best college possible.
+Selective colleges want high achieving students who can pay tuition and donate and they also want low acceptance and high yield rates to move up the rankings.
+For both sides to attain their goal, it is essential that colleges get information from high schools about which schools students actually wish to attend.
+
 @RN4407 also argues that the desire by colleges for trustworthy information about applicant intentions creates an opportunity for high school counselors to advocate on behalf of their students.
@@
 This relationship is the product of repeated interactions over many years.
+Off-campus recruiting visits are necessary for the maintenance of strong relationships that enable colleges and high schools to negotiate and send trustworthy information to one another.
+Without face-to-face visits, it is less likely that a college admissions counselor will "take the call" of a guidance counselor.
 
-In sum, off-campus recruiting visits are necessary for the maintenance of strong relationships that enable colleges and high schools to negotiate and send trustworthy information to one another.
-Without face-to-face visits, it is less likely that a college admissions counselor will "take the call" of a guidance counselor.
-Simultaneously, a recruiting visit between a college and a high school can be conceived as an indicator.
-First, the fact that the college took time and effort to make the visit suggests that the college wants to enroll students from the high school.
-Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
-Third, the presence of the recruiting visit indicates that the high school and the college have a relationship and suggests the probability of additional interactions (e.g., phone calls).
-
-<!-- Research methods -->
+# Data and methods
 
 Our project collected data about off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities.
+We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you" pages that post recruiting events) once per week from college/university admissions websites and -- for the sample of public research universities -- by issuing public records requests.
 Our analysis sample is based on three different lists of post-secondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S.
@@
 News and World Report Liberal Arts Colleges rankings (N=47).
-For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits.
-For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year.
-Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
-These institutions are excluded from the analyses.
-Of the remaining public universities, we also issued public records requests asking for recruiting events data as a means of quality assurance.
+We narrowed the sample down to universities that we were able to collect complete recruiting events data on.
 Our final analysis sample consists of 17 public research universities, 13 private research universities, and 13 private liberal arts colleges.
+We merged the recruiting events data to the following secondary data sources: 2017-18 NCES Private School Universe Survey (PSS); 2017 Integrated Postsecondary Education Data System (IPEDS); 2020 Best Private High Schools ranking by Niche; and 2020 Best Colleges ranking by U.S.
+News & World Report.
 
-We utilize network methods to analyze the recruiting visits data for two, related reasons.
-First, social network analysis privileges the relationship between actors.
-The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
-175].
-Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network.
+A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "edges" between these actors.
+Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
+For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
+The social network analyzed in this study is a two-mode network, where vertices consist of colleges/universities (mode 1) and high schools (mode 2), and an edge is defined as a visit from a college/university to a private high school (e.g., high school $i$ shares an edge with college $j$ if high school $i$ received at least one visit from college $j$).
+This (weighted) network is represented as a school-by-college matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 colleges/universities) in which matrix cell $a_{i,j}$ identifies the number of visits that high school $i$ received from college $j$.
 
-We will focus on network analyses of visits by colleges and universities to private high schools.
-Analyses are motivated by two, related research questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
+# Findings
 
-<!-- Findings -->
+With the page limitation of this proposal, we won't be able to discuss results in detail; however, we have included some preliminary examples of the type of analyses we are working on.Figure \@ref(fig:two-mode-plot-privu) shows a two-mode network plot consisting of visits by private colleges and universities to private high schools.
+Table \@ref(tab:ego-table-privu) shows characteristics of private high schools visited by each private institution.
+Figure \@ref(fig:two-mode-plot-both) shows a two-mode network plot consisting of visits by public and private colleges and universities to private high schools.
+Table \@ref(tab:top-hs-both) shows characteristics of the top 20 most visited private high schools by these institutions.
 
-Figure \@ref(fig:two-mode-plot) shows a two-mode network plot consisting of visits by public and private colleges and universities to private high schools.
+# Significance
 
-Figure \@ref(fig:two-mode-plot-privu) shows a two-mode network plot consisting of visits by private colleges and universities to private high schools.
-
-Table \@ref(tab:ego-table-privu) shows characteristics of private high schools visited by each private college and university.
-
-Table \@ref(tab:hs-print-privu) shows characteristics of the top 20 most visited private high schools by private colleges and universities.
-
-Table \@ref(tab:hs-table-privu-agg) shows characteristics of private high schools by number of private colleges and universities that visited.
-
-<!-- Study significance -->
+The vast majority of research on enrollment management behaviors focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [e.g., @RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948].
+By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664].
+With the notable exception of a small sociological case-study literature [@RN4324] -- the research community has ignored a great number of enrollment management practices that plausibly affect access to higher education.
+As a consequence, enrollment management remains an opaque industry to policymakers and the public.
+We argue that developing thoughtful policies about enrollment management depends on researchers collectively developing empirical literature that document enrollment management practices and evaluate the effects of these practices on opportunities for students.
 
@@
 ```{r, ego-table-privu, echo = FALSE}
-df <- readRDS('./../assets/tables/table_ego.RDS')
+df <- readRDS('./../assets/tables/table_ego_privu.RDS')
+
 knitr::kable(
@@
 
-```{r, hs-print-privu, echo = FALSE}
-df <- readRDS('./../assets/tables/table_2mode.RDS') %>% head(n=20)
+```{r, top-hs-both, echo = FALSE}
+df <- readRDS('./../assets/tables/table_2mode_both.RDS') %>% head(n=20)
 
 knitr::kable(
-  df %>% select(-school_id,-closeness), caption = 'Characteristics of the top 20 most visited private high schools by private colleges and universities') %>% 
-  landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r, hs-table-privu-agg, echo = FALSE}
-df <- readRDS('./../assets/tables/table_2mode_agg.RDS')
-
-knitr::kable(df, caption = 'Characteristics of private high schools by number of private colleges and universities that visited') %>% 
+  df %>% select(-name,-closeness), caption = 'Characteristics of the top 20 most visited private high schools by public and private colleges and universities') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network plot consisting of visits by public and private colleges and universities to private high schools"}
-knitr::include_graphics('./../assets/figures/plot_g_2mode.pdf')
+```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network plot consisting of visits by private colleges and universities to private high schools"}
+knitr::include_graphics('./../assets/figures/plot_g_2mode_privu.pdf')
+```
+
+```{r two-mode-plot-both, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network plot consisting of visits by public and private colleges and universities to private high schools"}
+knitr::include_graphics('./../assets/figures/plot_2mode.pdf')
 #https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
@@
 
-```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "2-mode network plot consisting of visits by private colleges and universities to private high schools"}
-knitr::include_graphics('./../assets/figures/plot_g_2mode_privu.pdf')
-```
-
 \end{landscape}

### 2020-10-31 scripts/network_recruiting_analysis.R

@@ -712,6 +712,10 @@ create_2mode_table <- function(twomode_network, race_var = 'pct_blacklatinxnativ
   list(full_table = full_twomode_table, agg_table = agg_twomode_table)
 }
 
+twomode_both <- create_2mode_table(g_2mode)
+saveRDS(twomode_both$full_table, file = './assets/tables/table_2mode_both.RDS')
+saveRDS(twomode_both$agg_table, file = './assets/tables/table_2mode_agg_both.RDS')
+
 twomode_privu <- create_2mode_table(g_2mode_privu)
 saveRDS(twomode_privu$full_table, file = './assets/tables/table_2mode_privu.RDS')
 saveRDS(twomode_privu$agg_table, file = './assets/tables/table_2mode_agg_privu.RDS')

### 2020-11-03 sea_conference/soc_of_ed_proposal_jaquette_han.Rmd
meh

--- 2020-10-31 sea_conference/soc_of_ed_proposal.Rmd
@@
 
+Department of Education
+
 University of California, Los Angeles
@@
 Crystal Han
+
+Data Scientist
+
+Department of Education
 
@@
 This study uses social network methods to analyze off-campus recruiting visits to U.S.
-private high schools by a sample of public research universities and selective private colleges and universities.
+private high schools made by a sample of public research universities and selective private colleges and universities.
 Analyses are informed by three broad research questions.
 First, which types of private high schools receive visits from which types of colleges and universities?
-Related, to what extent do colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+Related, to what extent do colleges and universities visit private high schools that share similar characteristics with the college, in particular, geographic region, religious affiliation, academic reputation, and racial composition?
 Third, how does the off-campus recruiting network of public research universities compare to that of selective private colleges and universities?
@@
 
-# Literature review and theory
+# Literature Review
 
 Market research conceives of off-campus visits as a means of identifying prospects, deepening engagement with prospects already being targeted through mail/email, and maintaining relationships with guidance counselors at "feeder schools" [@RN4323; @RN4402; @RN4664].
+
 @RN3519 provides an ethnography of the admissions office at a selective private liberal arts college.
@@
 Selective colleges want high achieving students who can pay tuition and donate and they also want low acceptance and high yield rates to move up the rankings.
-For both sides to attain their goal, it is essential that colleges get information from high schools about which schools students actually wish to attend.
+These colleges value reliable information about which college students actually wish to attend.
 
@@
 Without face-to-face visits, it is less likely that a college admissions counselor will "take the call" of a guidance counselor.
+We argue that off-campus recruiting visits are an indicator of a substantive relationsnhip between a college/university and a private high school.
+Despite the importance of these relationships to college access, we know littel about which colleges/universities visit which beyond several small qualitative case studies [@RN4538; @RN4520; @RN4324; @RN3519]
 
@@
 
+__Data__.
 Our project collected data about off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities.
@@
 
+__Methods__.
 A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "edges" between these actors.
 Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
-For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
 The social network analyzed in this study is a two-mode network, where vertices consist of colleges/universities (mode 1) and high schools (mode 2), and an edge is defined as a visit from a college/university to a private high school (e.g., high school $i$ shares an edge with college $j$ if high school $i$ received at least one visit from college $j$).
-This (weighted) network is represented as a school-by-college matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 colleges/universities) in which matrix cell $a_{i,j}$ identifies the number of visits that high school $i$ received from college $j$.
 
@@
 
-With the page limitation of this proposal, we won't be able to discuss results in detail; however, we have included some preliminary examples of the type of analyses we are working on.Figure \@ref(fig:two-mode-plot-privu) shows a two-mode network plot consisting of visits by private colleges and universities to private high schools.
+With the page limitation of this proposal, we do not discuss results; however, we have included some preliminary examples of the type of analyses we are working on.
+Figure \@ref(fig:two-mode-plot-privu) shows a two-mode network plot consisting of visits by private colleges and universities to private high schools.
 Table \@ref(tab:ego-table-privu) shows characteristics of private high schools visited by each private institution.
@@
 By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664].
-With the notable exception of a small sociological case-study literature [@RN4324] -- the research community has ignored a great number of enrollment management practices that plausibly affect access to higher education.
+With the notable exception of a small sociological case-study literature, the research community has ignored a great number of enrollment management practices that plausibly affect access to higher education.
 As a consequence, enrollment management remains an opaque industry to policymakers and the public.

### 2020-11-03 manuscript.Rmd
added number of visits to private high schools (total, in-st, out-st) to ego tables

@@
 
+<!-- private col/univ -->
+
 ```{r, ego-table-privu, echo = FALSE}
-df <- readRDS('./assets/tables/table_ego.RDS')
+df <- readRDS('./assets/tables/table_ego_privu.RDS')
 knitr::kable(
-  df %>% select(-Characteristics), row.names = F, # select(-ID, -Characteristics)
-  caption = 'ego table caption') %>% landscape(margin = NULL) %>%
+  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
+  caption = 'ego table private colleges and universities') %>% landscape(margin = NULL) %>%
   kable_styling(latex_options = 'scale_down')
@@
 ```{r, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego.RDS')
+df <- readRDS('./assets/tables/table_ego_privu.RDS')
 #df %>% select(ID,University,Cluster,Type,Rank,c1_lt10,c2_10to25,c3_25to50,`c4_50+`) %>%mutate(lt25 = as.numeric(c1_lt10) + as.numeric(c2_10to25))
@@
 ```{r, hs-print-privu, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode.RDS') %>% head(n=20)
+df <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20)
 
 knitr::kable(
-  df %>% select(-school_id,-closeness), caption = 'ego table 3') %>% 
+  df %>% select(-name,-closeness), caption = 'most central private high schools, private colleges and universities') %>% 
   landscape(margin = NULL) %>%
@@
 ```{r, hs-table-privu-agg, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode_agg.RDS')
+df <- readRDS('./assets/tables/table_2mode_agg_privu.RDS')
 
-knitr::kable(df, caption = 'ego table caption') %>% 
+knitr::kable(df, caption = 'characteristics of high schools by degree band, private colleges and universities') %>% 
+  landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+<!-- public research universities -->
+
+```{r, ego-table-pubu, echo = FALSE}
+df <- readRDS('./assets/tables/table_ego_pubu.RDS')
+knitr::kable(
+  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
+  caption = 'ego table caption public universities') %>% landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r, hs-print-pubu, echo = FALSE}
+df <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)
+
+knitr::kable(
+  df %>% select(-name,-closeness), caption = 'most central private high schools, private colleges and universities') %>% 
+  landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r, hs-table-pubu-agg, echo = FALSE}
+df <- readRDS('./assets/tables/table_2mode_agg_pubu.RDS')
+
+knitr::kable(df, caption = 'characteristics of high schools by degree band, private colleges and universities') %>% 
+  landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+<!-- public and private col/univ -->
+
+```{r, hs-print-both, echo = FALSE}
+df <- readRDS('./assets/tables/table_2mode_both.RDS') %>% head(n=20)
+
+knitr::kable(
+  df %>% select(-name,-closeness), caption = 'most central private high schools, public and private colleges and universities') %>% 
+  landscape(margin = NULL) %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r, hs-table-both-agg, echo = FALSE}
+df <- readRDS('./assets/tables/table_2mode_agg_both.RDS')
+
+knitr::kable(df, caption = 'characteristics of high schools by degree band, public and private colleges and universities') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "caption of 2 mode graph"}
-knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
+```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
+knitr::include_graphics('assets/figures/plot_2mode_privu.pdf')
 ```
@@
 
-```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Ego network of Emory University, with geographic region"}
+```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, with geographic region"}
 knitr::include_graphics('assets/figures/emory_region.pdf')
@@
 
-```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
+```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
 knitr::include_graphics('assets/figures/rank_cluster1.pdf')
@@
 
-```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "75%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
+```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
 knitr::include_graphics('assets/figures/race_cluster4.pdf')
+```
+
+```{r two-mode-plot-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
+knitr::include_graphics('assets/figures/plot_2mode_pubu.pdf')
+```
+
+```{r two-mode-plot-community, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
+knitr::include_graphics('assets/figures/plot_2mode.pdf')
+#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
 ```

### 2020-11-03 scripts/network_recruiting_analysis.R

@@ -458,6 +458,9 @@ par(mfrow=c(1, 1))  # resets to single plot
 
 vertex_attr_names(g_2mode)
 
+vcount(g_2mode)
+V(g_2mode)$state_code
+
 #graph_layout <- layout_with_kk
 graph_layout <- layout_with_fr
 
@@ -546,7 +549,7 @@ save_2mode_plot <- function(network, plot_name, plot_margin = -0.5) {
   ))
   detach(package:plyr, unload = TRUE)
   
-  pdf(paste0('assets/figures/', plot_name))
+  pdf(paste0('assets/figures/', plot_name), paper = "a4r")
   
   par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
   
@@ -567,6 +570,7 @@ save_2mode_plot <- function(network, plot_name, plot_margin = -0.5) {
   dev.off()
 }
 
+
 save_2mode_plot(g_2mode, 'plot_2mode.pdf', plot_margin = -0.6)
 save_2mode_plot(g_2mode_privu, 'plot_2mode_privu.pdf', plot_margin = -0.7)
 save_2mode_plot(g_2mode_pubu, 'plot_2mode_pubu.pdf')
@@ -575,6 +579,7 @@ save_2mode_plot(g_2mode_pubu, 'plot_2mode_pubu.pdf')
 ## ------------------------------
 ## TABLE FROM EGO IGRAPH OBJECTS
 ## ------------------------------
+
 
 create_ego_table <- function(twomode_network, ego_networks, univs, race_var = 'pct_blacklatinxnative_cat', ranking_var = 'rank_cat2') {
   
@@ -633,7 +638,20 @@ create_ego_table <- function(twomode_network, ego_networks, univs, race_var = 'p
   
   ego_tbl <- ego_tbl %>% arrange(as.numeric(cluster), univ_type, as.numeric(univ_ranking))
   
-  names(ego_tbl) <- c('ID', 'University', 'Cluster', 'Type', 'Rank', 'Characteristics',
+  # merge in number of visits to private high schools (total, inst, outst)
+    ego_tbl <- events_data %>% filter(event_type == "priv_hs") %>% group_by(univ_id) %>% 
+      summarize(phs_visits_tot = n()) %>% right_join(y = ego_tbl)
+      
+    ego_tbl <- events_data %>% filter(event_type == "priv_hs", univ_state == event_state) %>% group_by(univ_id) %>% 
[…]

### 2020-11-03 scripts/create_igraph_objects.R
add edge attributes for instate/outofstate and public/private visiting univ

@@ -169,6 +169,17 @@ df <- igraph::as_data_frame(g_2mode, 'both')
 # Edge list
 e_2mode <- df$edges %>% rename(ncessch = 'from', univ_id = 'to') %>% as_tibble()
 
+v_get_loc <- Vectorize(function(x, y) ifelse(privhs_events[privhs_events$school_id == x, ]$event_state[1] == univ_info[univ_info$univ_id == y, ]$state_code, 'instate', 'outofstate'))
+v_get_states <- Vectorize(function(x, y) paste0(privhs_events[privhs_events$school_id == x, ]$event_state[1], '|', univ_info[univ_info$univ_id == y, ]$state_code))
+e_2mode <- e_2mode %>% mutate(
+  visiting_univ = case_when(
+    univ_id %in% privu_vec ~ 'private',
+    univ_id %in% pubu_vec ~ 'public'
+  ),
+  visit_loc = v_get_loc(ncessch, univ_id),
+  state_codes = v_get_states(ncessch, univ_id)
+)
+
 # Vertex list (`name` must come first)
 v_2mode <- tibble(name = df$vertices$name, type = df$vertices$type)
 v_2mode <- left_join(v_2mode, attributes_df, c('name' = 'school_id'))

### 2020-11-10 tables.Rmd
add draft of ego barcharts

@@
 library(tidyverse)
+library(ggplot2)
 ```
@@
 
+# Ego network barplot
+
+```{r, fig.width=3.5, fig.height=3}
+ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
+univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University
+
+plot_characteristic <- function(df, type, characteristics) {
+  sub_df <- df %>% select(University, characteristics) %>%
+    gather(key, value, characteristics) %>%
+    mutate(value = parse_number(value))
+
+  # colors <- sub_df$color[order(sub_df$University)]
+
+  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))
+
+  ggplot(sub_df, aes(fill = key, y = value, x = University)) + 
+    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
+    ggtitle('Title') +
+    xlab('') + ylab('') +
+    labs(fill = type) +
+    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
+    theme(legend.position = 'top',
+          legend.title = element_text(size = 6, face = 'bold'),
+          legend.text = element_text(size = 6),
+          legend.margin = margin(0, 0, 0, 0),
+          legend.box.margin = margin(0, 0, -5, -30),
+          legend.key.size = unit(0.3, 'cm'),
+          panel.background = element_blank(),
+          axis.ticks.y = element_blank(),
+          # axis.text.y = element_text(color = rep(c('red', 'green', 'blue', 'yellow', 'black'), 5)),
+          text = element_text(size = 8),
+          plot.title = element_text(color = 'white')) +
+    coord_flip()
+}
+
+plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
+plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
+plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
+plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
+```
+
 # Ego network graph
@@
 
-```{r ego-plot, fig.align = 'center', out.width = '50%', fig.cap = 'Ego network'}
-knitr::include_graphics('assets/figures/plot_g_2mode_privu.pdf')
+```{r ego-plot, fig.align = 'center', out.width = '100%', fig.cap = 'Ego network'}
+knitr::include_graphics('assets/figures/plot_2mode_privu.pdf')
 ```

### 2020-11-11 scripts/chicken_scratch/figuring-out-how-to-do-cluster_fast_and_greedy.R
draft changes

@@ -1,0 +1,114 @@
+library(igraph)
+library(tidyverse)
+
+options(max.print=2000)
+## -------------
+## LOAD OBJECTS
+## -------------
+
+# Run create_igraph_objects.R
+scripts_dir <- file.path('.', 'scripts')
+source(file = file.path(scripts_dir, 'create_igraph_objects.R'))
+
+
+
+library(ape)  
+
+#bipartite.projection(g_2mode_privu)[["proj2"]] %>% cluster_fast_greedy() %>% membership()
+
+vertex_attr_names(bipartite.projection(g_2mode)[["proj2"]])
+
+edge_attr_names(bipartite.projection(g_2mode)[["proj2"]])
+edge_attr_names(g_1mode_psi)
+
+ecount(bipartite.projection(g_2mode)[["proj2"]])
+ecount(g_1mode_psi)
+
+
+as_adjacency_matrix(
+  graph = bipartite.projection(g_2mode)[["proj2"]],  # creates one-mode object w/ mode = universities
+  sparse = FALSE, 
+  attr = 'weight'
+)
+affil_1mode_psi %>% str()
+
+
+E(bipartite.projection(g_2mode)[["proj2"]])$weight
+E(g_1mode_psi)$weight
+
+bipartite.projection(g_2mode)[["proj2"]]
+
+c_obj <- cluster_fast_greedy(
+  graph = bipartite.projection(g_2mode)[["proj2"]],
+  merges = TRUE,
+  modularity = TRUE,
+  membership = TRUE,
+  weights = E(bipartite.projection(g_2mode)[["proj2"]])$weight
+)
+
+c_obj %>% membership()
+
+
+# investigating communities object
+c_2mode <- bipartite.projection(g_2mode)[["proj2"]] %>% cluster_fast_greedy() 
+c_2mode %>% membership() %>% table()
+c_2mode %>% str()
+
+c_2mode$merges %>% str()
+c_2mode$modularity %>% str()
+
+c_2mode %>% str()
+c_2mode %>% class()
+
+c_2mode %>% cut_at(steps = 41) %>% table()
+
+bipartite.projection(g_2mode_pubu)[["proj2"]] %>% cluster_fast_greedy() %>% cut_at(steps = 16) %>% table()
+
+cut_2mode <- c_2mode %>% cut_at(no = 2)
+cut_2mode %>% str()
+
+
[…]

### 2020-11-11 scripts/chicken_scratch/figuring-out-how-to-do-hierarchical-cluster-analysis.R

@@ -113,8 +113,13 @@ hclust_1mode_psi <- hclust(
 )
 hclust_1mode_psi %>% class()
 hclust_1mode_psi %>% str()
-plot(hclust_1mode_psi)
 
+hclust_1mode_psi %>% as.dendrogram() %>% plot(horiz = TRUE)
+
+
+
+hclust_1mode_psi %>% as.() %>%   dendPlot(mode = "auto")
+  as.dendrogram(hang = -1, use.modularity = FALSE) %>%  dendPlot(mode = "auto")
 # cut the dendrogram to create the desired number of clusters using stats::cutree
   # https://www.datacamp.com/community/tutorials/hierarchical-clustering-R
   # note: At least one of k or h must be specified, k overrides h if both are given.
@@ -191,3 +196,34 @@ df_temp3 %>% select(`100751`,`106397`)
 
 # we want to know which universities are visiting the same high schools;
 
+g_2mode
+g_1mode_hs
+
+V(g_1mode_hs
+  
+  
+  
+  
+################ SOMETHING ELSE
+
+twomode_both <- create_2mode_table(g_2mode)
+saveRDS(twomode_both$full_table, file = './assets/tables/table_2mode_both.RDS')
+saveRDS(twomode_both$agg_table, file = './assets/tables/table_2mode_agg_both.RDS')
+  
+full <- twomode_both$full_table
+
+full %>% filter(state_code == "NE") %>% select(name, school_name, religion, pct_blacklatinxnative, ranking_numeric, degree, strength)
+
+
+events_data %>% left_join(y = univ_df, by = c("univ_id" = "school_id")) %>% filter(event_type == "priv_hs" & school_id == "02161678") %>%
+  select(univ_id, school_name)
+
+
+events_data %>% filter(event_type == "priv_hs" & school_id == "02161678") %>% select(univ_id)
+
+events_data %>% left_join(y = univ_df, by = c("univ_id" = "school_id")) %>% filter(event_type == "priv_hs") %>% group_by(school_name) %>% count() %>% View()
+
+%>% select()
+glimpse(events_data)
+full %>% glimpse()
+ 

### 2020-11-11 scripts/network_recruiting_analysis.R

@@ -340,37 +340,6 @@ plot_ego_graph(ego_network, characteristic = 'pct_blacklatinxnative_cat', values
 ## WRITE COMMUNITY DETECTION FUNCTION
 ## ------------------------------
 
-# STEPS IN HIERARCHICAL CLUSTER ANALYSIS
-  #create adjacency matrix of 1-mode university object
-  # create "distance matrix" using stats::dist() function
-  # conduct hierarchical clustering using stats::hclust
-  # cut the dendrogram to create the desired number of clusters using stats::cutree
-  # merge the cluster assignments to the igraph object as a vertex attribute
-
-
-  # cluster analysis to create
-  cluster_2mode <- cluster_fast_greedy(network)
-  membership_2mode <- membership(cluster_2mode)
-
-    # cluster analysis to create
-  cluster_2mode <- cluster_fast_greedy(network)
-  membership_2mode <- membership(cluster_2mode)
-
-  # cluster analysis to create
-  cluster_2mode <- cluster_fast_greedy(g_1mode_psi_pubu)
-  membership_2mode <- membership(cluster_2mode)
-  membership_2mode
-  
-
-    
-
-
-bipartite.projection(g_2mode_privu)[["proj2"]] %>% cluster_fast_greedy() %>% membership()
-
-bipartite.projection(g_2mode)[["proj1"]] %>% cluster_fast_greedy() %>% membership()
-
-library(ape)  
-
 # FUNCTION TO RUN HIERARCHICAL CLUSTER ANALYSIS
   # STEPS IN HIERARCHICAL CLUSTER ANALYSIS:
   #create adjacency matrix of 1-mode university object
@@ -379,7 +348,8 @@ library(ape)
   # cut the dendrogram to create the desired number of clusters using stats::cutree
   # merge the cluster assignments to the igraph object as a vertex attribute
 
-create_hclust <- function(network, mode, k = NULL, h = NULL) {
+
+create_hclust <- function(network, mode, k = NULL, h = NULL, dist_method = "euclidean", hclust_method = "complete") {
 
   # mode = psi or hs
   if (mode == "hs") {
@@ -389,9 +359,7 @@ create_hclust <- function(network, mode, k = NULL, h = NULL) {
     proj <- "proj2"
     
   }
-  
-  m <- "complete" # cluster analysis agglomeration method to use: "average" "complete" 
-  
+
   #create adjacency matrix of 1-mode university object
   hclust_obj <- as_adjacency_matrix(
[…]

### 2020-11-11 tables.Rmd
not great

@@
 ```{r, fig.width=3.5, fig.height=3}
-ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
+#ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
+ego_df <- readRDS('./assets/tables/table_ego_pubu.RDS')
 univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University
@@
 
+pdf(str_c('assets/figures/', "ego_network_figure.pdf"), paper = "a4r")
+par(mfrow=c(2, 2))
 plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
@@
 plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
+
+dev.off()
+
+```
+
+```{r, fig.width=3.5, fig.height=3}
+type_vec <- c("privu","pubu")
+  #type_vec
+
+for (i in 1:length(type_vec)) {
+
+  #df_name <- str_c("table_ego_",type_vec[i],".RDS")
+  ego_df <-readRDS(file.path('.','assets','tables',str_c("table_ego_",type_vec[i],".RDS")))
+  #ego_df %>% glimpse() %>% print()
+
+  univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University
+
+  pdf(file.path('.','assets','figures',str_c("ego_network_figure_",type_vec[i],".pdf")), paper = "a4r")
+
+  plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
+  plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
+  plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
+  plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
+
+  dev.off()
+}
+
 ```

### 2020-11-11 tables.Rmd
update to ego barcharts

--- 2020-11-10 tables.Rmd
@@
 library(ggplot2)
+library(gridExtra)
 ```
@@
 ```{r, fig.width=3.5, fig.height=3}
-ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
-univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University
-
 plot_characteristic <- function(df, type, characteristics) {
@@
   # colors <- sub_df$color[order(sub_df$University)]
-
+  univ_order <- (df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University  
   sub_df$University <- factor(sub_df$University, levels = rev(univ_order))
@@
 
-plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
-plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
-plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
-plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
+type_vec <- c('privu', 'pubu')
+
+for (i in 1:length(type_vec)) {
+  ego_df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))
+
+  pdf(file.path('.', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')), paper = 'a4r')
+  par(mfrow=c(2, 2))
+
+  a <- plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
+  b <- plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
+  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
+  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
+
+  grid.arrange(a, b, c, d, nrow=2, ncol=2)
+  dev.off()
+
+  # Need to use print() for ggplot inside loop in order for it to appear
+  # https://stackoverflow.com/a/15678596/6373540
+  print(a)
+  print(b)
+  print(c)
+  print(d)
+}
 ```

### 2020-11-13 manuscript.Rmd
muddling through analyses...

@@
 library(tidyverse)
+library(gridExtra)
 ```
@@
 
-Figure \@ref(fig:two-mode-plot-privu) plots the two-mode network of visits by private colleges and universities to private high schools, with vertex color determined by community cluster.
+Figure \@ref(fig:plot-1mode-privu) plots the two-mode network of visits by private colleges and universities to private high schools, with vertex color determined by community cluster.
 The placement of college and high school vertices on an X-Y axis/coordinates is determined such that vertices with many direct and indirect ties are closer together.
@@
 
-Addressing our two motivating research questions -- which schools receive visits from which colleges/universities and the extent to which visits are more likely to occur between organizations that share certain characteristics -- requires analyses that are more granular than Figure \@ref(fig:two-mode-plot-privu).
+Addressing our two motivating research questions -- which schools receive visits from which colleges/universities and the extent to which visits are more likely to occur between organizations that share certain characteristics -- requires analyses that are more granular than Figure \@ref(fig:plot-1mode-privu).
 
@@
 
+\newpage
+
 ```{r, echo=FALSE}
@@
 
-```{r, ego-table-privu, echo = FALSE}
+```{r, ego-table-privu, echo = FALSE, include = FALSE, eval = FALSE}
 df <- readRDS('./assets/tables/table_ego_privu.RDS')
@@
 
-```{r, ego-table-pubu, echo = FALSE}
+```{r, ego-table-pubu, echo = FALSE, include = FALSE, eval = FALSE}
 df <- readRDS('./assets/tables/table_ego_pubu.RDS')
@@
 
-```{r two-mode-plot-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
-knitr::include_graphics('assets/figures/plot_2mode_privu.pdf')
+```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-privu"}
+knitr::include_graphics('assets/figures/plot_1mode_privu.pdf')
 ```
+
+\end{landscape}
+
+\restoregeometry
+
+\newpage
+
+```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
+plot_characteristic <- function(df, type, characteristics) {
+  sub_df <- df %>% select(University, characteristics) %>%
+    gather(key, value, characteristics) %>%
+    mutate(value = parse_number(value))
+
+  # colors <- sub_df$color[order(sub_df$University)]
+  univ_order <- (df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University  
+  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))
+
+  ggplot(sub_df, aes(fill = key, y = value, x = University)) + 
+    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
+    ggtitle('Title') +
+    xlab('') + ylab('') +
+    labs(fill = type) +
+    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
+    theme(legend.position = 'top',
+          legend.title = element_text(size = 6, face = 'bold'),
+          legend.text = element_text(size = 6),
+          legend.margin = margin(0, 0, 0, 0),
+          legend.box.margin = margin(0, 0, -5, -30),
+          legend.key.size = unit(0.3, 'cm'),
+          panel.background = element_blank(),
+          axis.ticks.y = element_blank(),
+          # axis.text.y = element_text(color = rep(c('red', 'green', 'blue', 'yellow', 'black'), 5)),
+          text = element_text(size = 8),
+          plot.title = element_text(color = 'white')) +
+    coord_flip()
+}
+
+type_vec <- c('privu', 'pubu')
+
+for (i in 1:length(type_vec)) {
+  ego_df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))
+
+  pdf(file.path('.', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')))
+  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
+  par(mfrow=c(2, 2))
+
+  a <- plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
+  b <- plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
+  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
+  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
+
+  grid.arrange(a, b, c, d, nrow=2, ncol=2)
+  dev.off()
+
+  # Need to use print() for ggplot inside loop in order for it to appear
+  # https://stackoverflow.com/a/15678596/6373540
+  #print(a)
+  #print(b)
+  #print(c)
+  #print(d)
+}
+```
+
+\newgeometry{margin=0cm}
+
+\newpage
+
+```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by private colleges and universities"}
+knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
+```
+
+\newpage
+```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by private colleges and universities"}
+knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
+```
+
+\begin{landscape}
+
+\newpage
 
@@
 
-```{r rank-cluster1, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Academic rating of private high schools visited by selected colleges from cluster 1"}
-knitr::include_graphics('assets/figures/rank_cluster1.pdf')
+```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu"}
+knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
 ```
 
-```{r race-cluster4, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Racial composition of visited private high schools, selected colleges"}
-knitr::include_graphics('assets/figures/race_cluster4.pdf')
+```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu out-of-state visits only"}
+knitr::include_graphics('assets/figures/plot_1mode_pubu_outst.pdf')
 ```
 
-```{r two-mode-plot-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
-knitr::include_graphics('assets/figures/plot_2mode_pubu.pdf')
+```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all"}
+knitr::include_graphics('assets/figures/plot_1mode_all.pdf')
 ```
 
-```{r two-mode-plot-community, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
-knitr::include_graphics('assets/figures/plot_2mode.pdf')
-#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
+```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all, out-of-state visits only for public universities"}
+knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
 ```

### 2020-11-13 scripts/create_igraph_objects.R

@@ -8,11 +8,13 @@ library(labelled)
 ## ----------
 
 # Recruiting events data from 43 univs (17 public research, 13 private national, 13 private liberal arts)
-events_data <- read.csv('./data/events_data_2020-07-27.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble()
+  # but get rid of wellesley; data seem messed up
+events_data <- read.csv('./data/events_data_2020-07-27.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble() %>% filter(univ_id != "168218") 
 
 # University data from IPEDS
-univ_data <- readRDS('./data/ipeds_1718.RDS')
-univ_info <- read.csv('./data/univ_data.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'zip_code' = 'character')) %>% as_tibble()
+univ_data <- readRDS('./data/ipeds_1718.RDS') %>% filter(univ_id != "168218")
+
+univ_info <- read.csv('./data/univ_data.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'zip_code' = 'character')) %>% as_tibble() %>% filter(univ_id != "168218")
 
 # Private HS data from PSS
 privhs_data <- readRDS('./data/pss_1718.RDS')
@@ -22,7 +24,6 @@ niche_data  <- read.csv('./data/niche_private.csv', header = TRUE, na.strings = 
 
 # Rankings data from US News & World Report
 usnews_data <- read.csv('./data/usnews_rankings.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character')) %>% as_tibble()
-
 
 ## ----------
 ## PREP DATA
@@ -193,7 +194,7 @@ e_2mode <- e_2mode %>% mutate(
   state_codes = v_get_states(ncessch, univ_id)
 )
 
-# Vertex list (`name` must come first)
+# Vertex list (name must come first)
[…]

### 2020-11-13 scripts/network_recruiting_analysis.R

@@ -37,7 +37,7 @@ source(file = file.path(scripts_dir, 'create_igraph_objects.R'))
 ## EGO IGRAPH FUNCTION (can utilize order =1, order =2, or both)
 ## --------------------
 
-plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('blue', 'purple', 'red', 'green'), title = univ_info[univ_info$univ_id == univ_id, ] %>% select(univ_abbrev) %>% as.character(), graph_order = 'both', margin = 0) {
+plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('lightblue', 'lightgreen', 'violet', 'yellow'), title = univ_info[univ_info$univ_id == univ_id, ] %>% select(univ_abbrev) %>% as.character(), graph_order = 'both', margin = 0) {
 
   network <- egos_psi_privu[[univ_id]]
     
@@ -66,9 +66,9 @@ plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('bl
   # vertex size; edge width, color, line type
   if (graph_order %in% c('both',2)) {  # graph order is 'both' 1 and 2; or graph order == 2
     vertex_size <- case_when(
-      vertex_attr(network, "type") == FALSE ~ 3,
-      vertex_attr(network, "type") == TRUE &  vertex_attr(network, "name") != univ_id ~ 12,
-      vertex_attr(network, "type") == TRUE &  vertex_attr(network, "name") == univ_id ~ 18,
+      vertex_attr(network, "type") == FALSE ~ 2,
+      vertex_attr(network, "type") == TRUE &  vertex_attr(network, "name") != univ_id ~ 10,
+      vertex_attr(network, "type") == TRUE &  vertex_attr(network, "name") == univ_id ~ 15,
     )
     
     edge_width <- if_else(E(network)$order == 1, 0.5, 0)
@@ -76,7 +76,7 @@ plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('bl
     edge_lty <- 5
 
   } else {  # graph order == 1
-    vertex_size <- if_else(V(network)$type, 18, 4)
+    vertex_size <- if_else(V(network)$type, 15, 2)
     
[…]

### 2020-11-17 manuscript.Rmd
draft changes. not very good!

@@
 
-Two-mode networks are ofen analyzed as one-mode networks [@RN2457].
+## Two-mode vs. One-mode networks
+
+Two-mode networks are often analyzed as one-mode networks [@RN2457].
 @RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" [pg.
@@
 Similarly, we create a one-mode college/university network (herein the college network) in which two colleges share an edge if both colleges visited the same high school and cell $c_{i,j}$ of the college-by-college matrix $C$ indicates the number of private high schools that received at least one visit from both college $i$ and college $j$ [SHOW EXCERPT OF ONE-MODE COLLEGE BY COLLEGE MATRIX, LIKE 3 BY 3 OR SOMETHING].
+
+## Ego networks
 
@@
 
-Figure X shows the ego network of all high schools visited by Notre Dame.
-
 When analyzing ego networks, researchers often investigate the extent of "homophily" versus "heterophily" [@RN1722].
@@
 Heterophily, the opposite of homophily, is when pairs of connected vertices have different characteristics from one another.
+Analyses investigate the extent to which network ties are homopholous or heteropholous, focusing on the vertex characteristics of
+
+<!--
+
 Figure X shows the University of Notre Dame ego network, with separate panels for vertex characteristics (academic reputation, geography, religious affiliation, and racial composition) and with vertex shapes (?colors?) to identify values of vertex characteristics [INSERT FIGURE].
@@
 ADD BRIEF TEXT ABOUT FIGURE?
+
+-->
+
+## Community detection
+
+Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
+Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
+We used XYZ community detection approach [add footnote w/ details?] to allocate private colleges and universities [?
+and private high schools] to clusters.
 
@@
 
-Figure \@ref(fig:two-mode-plot) plots the two-mode network of visits to private high schools by all colleges and universities in our sample, with private high schools vertices the color salmon, public research universities shown in violet, and private colleges and universities shown in green green.
+Figure \@ref(fig:two-mode-plot) plots the two-mode network of visits to private high schools by all colleges and universities in our sample, with large vertices indicating a college/university, small verticies indicating private high schools and with vertex color determined by geographic region (Northeast, Midwest, South, West).
+The graph layout places vertices closer together if they are similar to one another in terms of network structure.
+[SAY WHAT THIS MEANS, DRAWING FROM NOTES FROM RUSS].
+Figure \@ref(fig:two-mode-plot) suggests a modest relationship between geographic region and network structure.
+For instance, the high school vertices closest to University of Alabama and University of Arkansas tend to be located in the south.
+Further, universities located in the same geographic region (e.g., SUNY Stony Brook and Rutgers) tend to be closer to one another than universities located in other regions.
+However, this relationship is not consistent, for example, Scripps College located in CA is closest to University of Pittsburgh (PA) and Stevens Institute of Technology (NJ).
+Moreover, the network depicted by \@ref(fig:two-mode-plot) is too large to detect nuanced patterns of network structure.
+
+<!--
+Figure \@ref(fig:two-mode-plot) plots the two-mode network of visits to private high schools by all colleges and universities in our sample with private high schools vertices the color salmon, public research universities shown in violet, and private colleges and universities shown in green green.
 The graph layout places vertices closer together if they are similar to one another in terms of network structure.
@@
 By contrast, many public research universities are far away from one another and a subset of public researchg universities appear to have network structure similar to many of the private colleges and universities (e.g., CU Boulder, UC Berkeley, University of South Carolina )
+-->
 
@@
 
-Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
-Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
-We used XYZ community detection approach [add footnote w/ details?] to allocate private colleges and universities [?
-and private high schools] to clusters.
+Figure \@ref(fig:plot-1mode-privu) plots the one-mode network of visits by private colleges and universities.
+Here, the number of ties between a pair of universities (e.g., Sewanee and Texas Christian University) equals the number of private high schools visited by both universities.
+The graph layout places colleges/universities closer together if they have similar network structure [MAYBE SAY WHAT THIS MEANS IF YOU HAVEN'T YET].
+Additionally, vertex color is determined by hierarchical cluster analysis specified to create $k = 4$ clusters.
+Although the process of placing vertices was separate from the process of determining community cluster, vertices within the same cluster tend to be closer to one another than those of different clusters.
+Accompanying Figure \@ref(fig:plot-1mode-privu) is Figure \@ref(fig:ego-network-figure-privu), which shows the characteristics -- geographic region, religious affiliation, academic reputation, and racial composition -- of private high schools visited our sample of private colleges and universities.
+
+One cluster consists of Notre Dame, Villanova, Tulane, and Southern Methodist University. [text about this cluster]
+
+One cluster consists of Baylor, Harvey Mudd, Scripps, and Stevens Institute of Technology.
+Figure \@ref(fig:plot-1mode-privu) indicates that all four institutions are rather peripheral to the overall network.
+Harvey Mudd, Scripps and -- to a lesser extent -- Stevens made relatively fewer visits to private high schools.
+By contrast, Baylor visited a fundamentally different set of schools than other private colleges and universities in that they visited a large number of conservative Christian private high schools.
+
+Figure \@ref(fig:ego-network-figure-privu) indicates that, with the exception of Harvey Mudd and Scripps, these four institutions share little in common with respect to the characteristics of high schools they visit.
+
+```{r, include = FALSE, eval = FALSE}
+
+df <- readRDS('./assets/tables/table_ego_privu.RDS')
+df %>% glimpse()
+df %>% select(ID,University,Cluster,total) %>% 
+  arrange(Cluster,University)
+```
+
+is based on ego graphs of private colleges and universities and 
+<!--
+
+ 1  2  3  4 
+ 4  6 11  4
+
+   name              cluster
+   <chr>               <int>
+ 1 Baylor                  1
+ 2 Harvey Mudd             1
+ 3 Scripps                 1
+ 4 Stevens Ins. Tech       1
+ 5 Case Western Res.       2
+ 6 Macalester              2
+ 7 Occidental              2
+ 8 Smith                   2
+ 9 Swarthmore              2
+10 Williams                2
+11 Boston Coll.            3
+12 Colorado Coll.          3
+13 Conn Coll.              3
+14 Emory                   3
+15 Middlebury              3
+16 Northwestern            3
+17 Oberlin                 3
+18 Sewanee                 3
+19 TCU                     3
+20 Tufts                   3
+21 U of Denver             3
+22 Notre Dame              4
+23 SMU                     4
+24 Tulane                  4
+25 Villanova               4
+
+-->
+
+For example, the nonsectarian liberal arts colleges in Cluster 1 tend to be be close to one another and also relatively close to the highest concentration of private high schools in cluster 1, suggesting that these colleges visit substantially overlapping sets of private high schools.
+For Cluster 2, by contrast, Northwestern and Emory are relatively far from Tulane and Sewanee.
+
 Four clusters emerge.
@@
 Finally, cluster 4 consists of three religiously affiliated Texas universities -- Southern Methodist, Baylor, Texas Christian University -- and the University of Denver.
-
-Figure \@ref(fig:plot-1mode-privu) plots the two-mode network of visits by private colleges and universities to private high schools, with vertex color determined by community cluster.
-The placement of college and high school vertices on an X-Y axis/coordinates is determined such that vertices with many direct and indirect ties are closer together.
-Although the process of placing vertices was separate from the process of determining community cluster, vertices within the same cluster tend to be closer to one another than those of different clusters.
-For example, the nonsectarian liberal arts colleges in Cluster 1 tend to be be close to one another and also relatively close to the highest concentration of private high schools in cluster 1, suggesting that these colleges visit substantially overlapping sets of private high schools.
-For Cluster 2, by contrast, Northwestern and Emory are relatively far from Tulane and Sewanee.
 
@@
 ```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
-knitr::include_graphics('assets/figures/plot_g_2mode.pdf')
+knitr::include_graphics('assets/figures/plot_2mode_all_region.pdf')
+
 #https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown

### 2020-11-17 scripts/network_recruiting_analysis.R

@@ -37,6 +37,7 @@ source(file = file.path(scripts_dir, 'create_igraph_objects.R'))
 ## EGO IGRAPH FUNCTION (can utilize order =1, order =2, or both)
 ## --------------------
 
+
 plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('lightblue', 'lightgreen', 'violet', 'yellow'), title = univ_info[univ_info$univ_id == univ_id, ] %>% select(univ_abbrev) %>% as.character(), graph_order = 'both', margin = 0) {
 
   network <- egos_psi_privu[[univ_id]]
@@ -279,8 +280,15 @@ create_hclust(network = g_2mode, mode = "psi", k = 4, h = NULL, hclust_method = 
 
 create_hclust(network = g_2mode, mode = "psi", k = 6, h = NULL, hclust_method = "complete") %>% table()
 
+create_hclust(network = g_2mode, mode = "psi", k = 4, h = NULL, hclust_method = "ward.D") %>% table()
 #create_hclust(network = g_2mode, mode = "psi", k = NULL, h = 600)
 
+bipartite.projection(g_2mode_privu)[["proj2"]] %>%
+  as_adjacency_matrix(
+    #graph = bipartite.projection(network)[[proj]],  # creates one-mode object w/ mode = universities
+    sparse = FALSE, 
+    attr = 'weight'
+  )
 ## ---------------------------
 ## PLOT 2-MODE IGRAPH OBJECT; PUBLIC AND PRIVATE COLLEGES/UNIVERSITIES AND ALL HIGH SCHOOLS THEY VISIT
 ## ---------------------------
@@ -319,7 +327,7 @@ plot(
   edge.lty = .5,
   edge.color = 'lightgrey',
   layout = graph_layout,
-  margin = -0.65
+  margin = -0.5
 )
 
 dev.off() # close the file
@@ -363,7 +371,7 @@ save_2mode_plot <- function(network, pubu_visits = 'all', privu_visits = 'all', 
 
       vertex_attr(graph = network, name = "cluster_psi", index = V(network)$name[V(network)$type == TRUE]) <- create_hclust(network = network, mode = "psi", k = k, h = h, hclust_method = hclust_method)
       
-  } else {  # run igraph::fast_and_greedy() cluster analysis
+  } else if (c_analysis == "fast") {  # run igraph::fast_and_greedy() cluster analysis
     
[…]

### 2020-11-18 manuscript.Rmd
muddling along

@@
 
+```{r, include = FALSE, eval = FALSE}
+df <- readRDS('./assets/tables/table_ego_privu.RDS')
+df %>% glimpse()
+df %>% select(ID,University,Cluster,total) %>% 
+  arrange(desc(Cluster),University) %>% print(n=30)
+```
+
 Figure \@ref(fig:plot-1mode-privu) plots the one-mode network of visits by private colleges and universities.
@@
 Although the process of placing vertices was separate from the process of determining community cluster, vertices within the same cluster tend to be closer to one another than those of different clusters.
-Accompanying Figure \@ref(fig:plot-1mode-privu) is Figure \@ref(fig:ego-network-figure-privu), which shows the characteristics -- geographic region, religious affiliation, academic reputation, and racial composition -- of private high schools visited our sample of private colleges and universities.
 
-One cluster consists of Notre Dame, Villanova, Tulane, and Southern Methodist University. [text about this cluster]
-
-One cluster consists of Baylor, Harvey Mudd, Scripps, and Stevens Institute of Technology.
-Figure \@ref(fig:plot-1mode-privu) indicates that all four institutions are rather peripheral to the overall network.
-Harvey Mudd, Scripps and -- to a lesser extent -- Stevens made relatively fewer visits to private high schools.
-By contrast, Baylor visited a fundamentally different set of schools than other private colleges and universities in that they visited a large number of conservative Christian private high schools.
-
-Figure \@ref(fig:ego-network-figure-privu) indicates that, with the exception of Harvey Mudd and Scripps, these four institutions share little in common with respect to the characteristics of high schools they visit.
-
-```{r, include = FALSE, eval = FALSE}
-
-df <- readRDS('./assets/tables/table_ego_privu.RDS')
-df %>% glimpse()
-df %>% select(ID,University,Cluster,total) %>% 
-  arrange(Cluster,University)
-```
-
-is based on ego graphs of private colleges and universities and 
-<!--
-
- 1  2  3  4 
- 4  6 11  4
-
-   name              cluster
-   <chr>               <int>
- 1 Baylor                  1
- 2 Harvey Mudd             1
- 3 Scripps                 1
- 4 Stevens Ins. Tech       1
- 5 Case Western Res.       2
- 6 Macalester              2
- 7 Occidental              2
- 8 Smith                   2
- 9 Swarthmore              2
-10 Williams                2
-11 Boston Coll.            3
-12 Colorado Coll.          3
-13 Conn Coll.              3
-14 Emory                   3
-15 Middlebury              3
-16 Northwestern            3
-17 Oberlin                 3
-18 Sewanee                 3
-19 TCU                     3
-20 Tufts                   3
-21 U of Denver             3
-22 Notre Dame              4
-23 SMU                     4
-24 Tulane                  4
-25 Villanova               4
-
--->
-
-For example, the nonsectarian liberal arts colleges in Cluster 1 tend to be be close to one another and also relatively close to the highest concentration of private high schools in cluster 1, suggesting that these colleges visit substantially overlapping sets of private high schools.
-For Cluster 2, by contrast, Northwestern and Emory are relatively far from Tulane and Sewanee.
-
-Four clusters emerge.
-The largest cluster consists largely of nonsectarian liberal arts colleges (e.g., Williams, Swarthmore, Colorado College).
-Cluster 2 consists of Emory University, Tulane, Northwestern, and Sewanee.
-These universities all have relatively strong ties to Southern private high schools.
-Cluster 3 consists of three catholic universities -- Notre Dame, Villanova, Boston College -- and Case Western Reserve and Stevens Institute of Technology.
-Although not a Catholic University, Stevens Institute of Technology has strong ties to Catholic private schools (representing X% of visits).
-Finally, cluster 4 consists of three religiously affiliated Texas universities -- Southern Methodist, Baylor, Texas Christian University -- and the University of Denver.
+One cluster consists of Notre Dame, Villanova, Tulane, and Southern Methodist University.
+Each of these four universities made a relatively high number of visits to private high schools and are relatively centrally located in Figure \@ref(fig:plot-1mode-privu).
 
 Addressing our two motivating research questions -- which schools receive visits from which colleges/universities and the extent to which visits are more likely to occur between organizations that share certain characteristics -- requires analyses that are more granular than Figure \@ref(fig:plot-1mode-privu).
+Figure \@ref(fig:ego-network-figure-privu) shows characteristics of private high schools visited our sample of private colleges and universities, specifically, geographic region, religious affiliation, academic reputation, and racial composition.
 
-Table \@ref(tab:ego-table-privu) shows the characteristics of private high schools visited by each private college and university.
-This table was created from the ego networks of each private college and university.
-As such, we visualize selected ego networks to illustrate several patterns that emerge from Table \@ref(tab:ego-table-privu).
-Ego networks consist of an ego (a single college/university), the set of high schools the ego visted (one degree of separation from the ego), and the set of colleges/universities that also visited high schools visited by the ego (two degrees of separation from the ego).
-Figure \@ref(fig:villanova-religion) shows the ego network of Villanova University, with vertex color determined by religious affiliation.
-About 50% of Villanova's visits were to Catholic schools, a percentage [?percent?] much higher than most colleges and universities shown in Table \@ref(tab:ego-table-privu), and second only to Notre Dame University.
+Figure \@ref(fig:ego-network-figure-privu) indicates that Notre Dame, Villanova, Tulane, and Southern Methodist University made a large share of visits in the South and the Northeast.
+With respect to religious affiliation, Notre Dame and Villanova -- both Catholic universities -- predictably focused visits on Catholic Schools.
+However, Tulane and SMU also visited a higher share of Catholic schools than most other private colleges and universities.
+These four universities also visited a lower share of private schools ranked in the top 200 nationally by Niche.
+
+Figure \@ref(fig:ego-network-figure-privu) was created from the ego network of each private college and university.
+Ego networks consist of an ego (e.g., a single college or university), the set of high schools the ego visted (one degree of separation from the ego), and the set of colleges/universities that also visited high schools visited by the ego (two degrees of separation from the ego).
+Figure \@ref(fig:villanova-religion) plots the ego network of Villanova University, with vertex color determined by religious affiliation.
+About 50% of Villanova's visits were to Catholic schools, a percentage [?percent?] much higher than most colleges and universities shown in Figure \@ref(fig:ego-network-figure-privu), and second only to Notre Dame University.
 In Figure \@ref(fig:villanova-religion), Notre Dame is closer to Villanova than any other college/university in the Villanova ego network, suggesting that Villanova and Notre Dame visit substantially overlapping sets of schools.
-Boston College, another Catholic university, is situated a bit further away from Villanova in the clump of colleges that includes Case Western, Tulane, Sewanee, Southern Methodist, and TCU, all of which visit a relatively high share of Catholic high schools, despite not being Catholic universities.
+Boston College, another Catholic university, is situated a bit further away from Villanova in the clump of colleges that includes Case Western, Tulane, Sewanee, Southern Methodist, and TCU, most of which visit relatively high share of Catholic high schools.
 By contrast, Villanova is far from nonsectarian liberal arts colleges (e.g., Swarthmore, Smith, Colorado College) which visit fewer Catholic high schools.
+
+A second cluster consits of Boston College, Colorado College, Connecticut College, Emory University, Middlebury, Northwestern Oberlin, Sewanee, Texas Christian University, Tufts, and the University of Denver.
+This institutions also tend to be located relatively centrally in Figure \@ref(fig:plot-1mode-privu), indicating that many of the high schools they visit are also visited by many private colleges and universities in our sample.
+Compared to the first cluster, these institutions have a stronger focus on nonsectarian private high schools, with the exception of Boston College, Texas Christian, and Sewanee.
+The also tended to visit schools with relatively strong academic reputations.
 
@@
 
-Figure \@ref(fig:rank-cluster1) shows the academic reputation of private high schools visited by [selected] private colleges and universities.
-Compared to other institutions, the cluster of nonsectarian liberal arts colleges visits a higher share of high schools ranked in the top 200 of Niche and a lower share of schools with a grade of "A" or lower.
-By contrast, Catholic universities (in cluster 3) and Christian affiliated Texas universities (cluster 4) tend to visit a higher share of high schools graded as "A" or lower by Niche.
+A third cluster consists of Case Western Reserve, MaCalester, Occidental, Smith, Swarthmore, and Williams.
+These institutions made relatively fewer visits than institutions in the first two clusters and are located relatively peripherally in the one-mode network, as shown in Figure \@ref(fig:plot-1mode-privu).
+With the exception of Case Western Reserve, these institutions are liberal arts colleges rather than research universities.
+They tended to visit a high share of nonsectarian private high schools and also a high share of schools ranked in the top 200 nationally by Niche.
 
-Figure \@ref(fig:race-cluster4) shows the racial composition of visited private high schools by college [REVISE PARAGRAPH ONCE WE FIX MISSING VALUES FOR RACE].
-The big take-away is that the most colleges predominantly visit high schools where fewer than 25% of students identify as Black, Latinx, or Native.
-This finding is largely true across clusters.
-Private high schools tend to have a higher share of White students than public high schools.
+The final cluster consists of Baylor, Harvey Mudd, Scripps, and Stevens Institute of Technology.
+Figure \@ref(fig:plot-1mode-privu) indicates that all four institutions are rather peripheral to the network.
+Harvey Mudd, Scripps, and Stevens made relatively few visits to private high schools.
+By contrast, Baylor visited a fundamentally different set of schools than other private colleges and universities in that Baylor visited a large number of Christian private schools that were not visited by other private colleges and universities in the sample.
+Overall, these four institutions form a group more because they are peripheral to the overall network as opposed to having similar network structures to one another.
+
+Finally, we comment on the racial composition -- defined here as the percent of students who identify as Black, Latinx, or Native -- of private high schools visited by private colleges and universities in our sample.
+Figure \@ref(fig:ego-network-figure-privu) shows substantial variation across and within clusters in the geographic region, religious affiliation, and academic reputation of visited private schools.
+By contrast, the racial composition of visited private high schools was remarkably similar.
+On average, about one-third of visits were to schools where Black/Latinx/Native students comprised less than 10% of the student body, about 50% of visits were to schools where Black/Latinx/Native students comprised between 10% and 25% of the student body, and about 15% of visits were to schools where Black/Latinx/Native students comprsied more than 25% of the student body.
+Some colleges (e.g., Williams and Swarthmore) were better than others (e.g., Emory, Sewanee) at visiting schools where Black/Latinx/Native students comprised more than 50% of the population, but these visits to very diverse private schools represented a small share of all visits to private schools.
+The overall results suggest that when private colleges and universities visit private high schools, they are usually visiting schools that enroll few Black, Latinx, or Native students.
+
+[HOW DOES RACIAL COMPOSITION OF VISITED PRIVATE HIGH SCHOOLS COMPARE TO RACIAL COMPOSITION OF ALL PRIVATE HIGH SCHOOLS?
+CUT/REVISE TEXT DEPENDING ON ANSWER TO THIS QUESTION] Private high schools tend to have a higher share of White students than public high schools.
 Moreover, the private high schools that were visited by private colleges and universities in our sample had a lower share of Black/Latinx/Native students, on average, than the population of private high schools.
@@
 
-[NEED TRANSITION TO FOCUS NOW ON HIGH SCHOOLS]
-Which private high schools receive the most visits?
+[NEED TRANSITION TO FOCUS NOW ON HIGH SCHOOLS] Which private high schools received the most visits from private colleges and universities in our sample?
 Table \@ref(tab:hs-print-privu) shows characteristics of the 20 private high schools that were visited by the most private colleges and universities.
@@
 
+```{r, include = FALSE, eval = FALSE}
+df <- readRDS('./assets/tables/table_ego_pubu.RDS')
+df %>% glimpse()
+df %>% select(ID,University,Cluster,total) %>% 
+  arrange(Cluster,University) %>% print(n=30)
+```
+<!--
+
+   ID     University       Cluster total
+
+ 1 100751 U of Alabama     1         985
+
+16 126614 CU Boulder       4         379
+17 218663 U of S.Carolina  4         486
+
+ 2 186380 Rutgers          2         303
+ 3 106397 U of Arkansas    2         225
+ 4 201885 U of Cincinnati  2         283
+ 5 139959 U of Georgia     2         302
+ 6 155317 U of Kansas      2         235
+ 7 215293 U of Pitt        2         261
+ 8 110635 UC Berkeley      2         208
+ 9 110680 UC San Diego     2         197
+10 166629 UMass Amherst    2         292
+
+11 199193 NCSU             3          23
+12 196097 SUNY Stony Brook 3         146
+13 110653 UC Irvine        3          60
+14 110671 UC Riverside     3          87
+15 181464 UNL              3         159
+
+-->
+
+Figure \@ref(fig:plot-1mode-pubu) plots the one-mode network of visits by 17 public research universities, with vertex color determined by hierarchical cluster analysis specified to create $k = 4$ clusters.
+Accompanying Figure \@ref(fig:plot-1mode-pubu) and created from the respective ego networks of each university is Figure \@ref(fig:ego-network-figure-pubu), which shows the characteristics of private high schools visited by these public reearch universities.
+Figure \@ref(fig:ego-network-figure-pubu) indicates that public research universities tended to visit private high schools with weaker academic reputation than the set of schools visited by private colleges and universities [LATER, SAY GOING AFTER MONEY WITHOUT ACADEMIC REP].
+More surprisingly, despite being nonsectarian, most public research universities visited a higher share of private high schools that were Catholic or Chrisitan than those visited by private colleges and universities.`
+
+The University of Alabama is a cluster unto itself.
+In 2017, the University of Alabama made 985 visits to private high schools.
+This number was more than double the 486 visits made by the University of South Carolina, which ranked second amongst public research universities in terms of number of private school visits, and substantially more than the 687 visits made by Notre Dame, which ranked first amongst private colleges and universities.
+With respect to geographic region, more than 50% of visits were in the South.
+
+[AT SOME POINT SAY THAT THE GOEGRAPHIC REGION IS NOT ALWAYS THE SAME AS REGION THEY ARE LOCATED IN; IN GENERAL SAY A LOT ABOUT GEOGRAPHIC REGION]
+
+having made 985 visits to U.S. private high schools in 2017 In 2017
+At 985 visits, the University of Alabama made more
+
+created from the respective ego networks of each public research university, shows characteristics of private high schools visited our sample of private colleges and universities, specifically, geographic region, religious affiliation, academic reputation, and racial composition.
+
 ADD TABLES/FIGURES OF VISITS BY PUBLIC RESEARCH UNIVERSITIES.
@@
 
+shit to say about comparison
+
+- on avg. private colleges and universities made more visits than publics, except university of Aalabama.
+-
+
+```{r, include = FALSE, eval = FALSE}
+df <- readRDS('./assets/tables/table_ego_all.RDS')
+df %>% glimpse()
+df %>% select(ID,University,Cluster,total) %>% 
+  arrange(Cluster,total) %>% print(n=50)
+```
 # References
@@
 
-\end{landscape}
-
-\restoregeometry
-
-\newpage
-
 ```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
@@
   # colors <- sub_df$color[order(sub_df$University)]
-  univ_order <- (df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University  
+  univ_order <- (df %>% arrange(desc(Cluster), University))$University
+  #univ_order <- (df %>% arrange(desc(Cluster), Type, as.numeric(Rank), University))$University
   sub_df$University <- factor(sub_df$University, levels = rev(univ_order))
@@
 
-type_vec <- c('privu', 'pubu')
+type_vec <- c('privu', 'pubu', 'all')
 
@@
   a <- plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
-  b <- plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
+  b <- plot_characteristic(ego_df, 'Religion', c('Catholic', 'Christian', 'Nonsect', 'Other'))
   c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
@@
 
+\end{landscape}
+
+\restoregeometry
+
 \newgeometry{margin=0cm}
@@
 knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
-```
-
-\newpage
-```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by private colleges and universities"}
-knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
 ```
@@
 
-```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu out-of-state visits only"}
+```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu out-of-state visits only", eval = FALSE}
 knitr::include_graphics('assets/figures/plot_1mode_pubu_outst.pdf')
 ```
+
+\end{landscape}
+
+\restoregeometry
+
+\newgeometry{margin=0cm}
+
+\newpage
+
+```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by public research universities"}
+knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
+```
+
+\begin{landscape}
 
@@
 \restoregeometry
+
+\newgeometry{margin=0cm}
+
+\newpage
+
+```{r ego-network-figure-all, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by public and private colleges and universities"}
+knitr::include_graphics('assets/figures/ego_network_figure_all.pdf')
+#out.width="1.1\\linewidth", 
+```

### 2020-11-18 scripts/network_recruiting_analysis.R

@@ -158,8 +158,10 @@ plot_ego_graph(univ_id = "160755", characteristic = 'region', values = c(1, 2, 3
   # villanova ego network, religion overlayed
   pdf("assets/figures/villanova_religion.pdf", paper = "a4r") # open file
   
-    par(mar=c(5, 4, 4, 2) + 0.1) # default margins
+    #par(mar=c(5, 4, 4, 2) + 0.1) # default margins
     #par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
+    #par(mar=c(0, 0, 0, 2) + 0.1, mai=c(0, 0, 0, 0))
+    par(mar=c(0, 0, 0, 4))
   
     plot_ego_graph(univ_id = "216597", characteristic = 'religion_4', values = c('catholic', 'christian', 'nonsectarian', 'other'), keys = c('Catholic', 'Christian', 'Nonsectarian', 'Other'), title = "", graph_order = 'both', margin = -0.3)
     
@@ -231,10 +233,11 @@ create_hclust <- function(network, mode, k = NULL, h = NULL, dist_method = "eucl
   # mode = psi or hs
   if (mode == "hs") {
     proj <- "proj1"
+    type <- FALSE
   } else {  
     
     proj <- "proj2"
-    
+    type <- TRUE
   }
 
   #create adjacency matrix of 1-mode university object
@@ -258,15 +261,21 @@ create_hclust <- function(network, mode, k = NULL, h = NULL, dist_method = "eucl
       members = NULL # NULL or a vector with length size of d. See the ‘Details’ section. default = NUKK
     ) 
     
-    # plot dendrogram associated with hclust object
-    hclust_obj %>% as.dendrogram() %>% plot(horiz = TRUE)
+  # plot dendrogram associated with hclust object
+    hclust_obj2 <- hclust_obj
+    hclust_obj2$labels <- V(network)$school_name[V(network)$type == type] # replace "labels" with school name rather than unitid
     
-    # cut the dendrogram to create the desired number of clusters using stats::cutree
+    par(mar=c(3,1,1,8)) # set the margin
+    #par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
+    hclust_obj2 %>% as.dendrogram() %>% plot(horiz = TRUE)
+    
+  # cut the dendrogram to create the desired number of clusters using stats::cutree
     cutree(
[…]

### 2020-11-19 manuscript.Rmd
muddling along

@@
 Most schools in Table \@ref(tab:hs-print-privu) are mostly nonsectarian.
-Although all received a Niche grade of "A+", they are not uniformly in the upper-echelon of schools ranked in the top 50 or top 100 nationwide.
+Although all received a Niche grade of "A+", they are not uniformly in the upper-echelon of schools ranked in the top 100 nationwide.
 With the exception of St.
@@
 df %>% glimpse()
-df %>% select(ID,University,Cluster,total) %>% 
-  arrange(Cluster,University) %>% print(n=30)
+df %>% select(ID,University,Cluster,Rank,total, in_state, out_state) %>% 
+  arrange(Cluster,desc(total)) %>% print(n=30)
 ```
-<!--
-
-   ID     University       Cluster total
-
- 1 100751 U of Alabama     1         985
-
-16 126614 CU Boulder       4         379
-17 218663 U of S.Carolina  4         486
-
- 2 186380 Rutgers          2         303
- 3 106397 U of Arkansas    2         225
- 4 201885 U of Cincinnati  2         283
- 5 139959 U of Georgia     2         302
- 6 155317 U of Kansas      2         235
- 7 215293 U of Pitt        2         261
- 8 110635 UC Berkeley      2         208
- 9 110680 UC San Diego     2         197
-10 166629 UMass Amherst    2         292
-
-11 199193 NCSU             3          23
-12 196097 SUNY Stony Brook 3         146
-13 110653 UC Irvine        3          60
-14 110671 UC Riverside     3          87
-15 181464 UNL              3         159
-
--->
 
@@
 Accompanying Figure \@ref(fig:plot-1mode-pubu) and created from the respective ego networks of each university is Figure \@ref(fig:ego-network-figure-pubu), which shows the characteristics of private high schools visited by these public reearch universities.
-Figure \@ref(fig:ego-network-figure-pubu) indicates that public research universities tended to visit private high schools with weaker academic reputation than the set of schools visited by private colleges and universities [LATER, SAY GOING AFTER MONEY WITHOUT ACADEMIC REP].
-More surprisingly, despite being nonsectarian, most public research universities visited a higher share of private high schools that were Catholic or Chrisitan than those visited by private colleges and universities.`
 
-The University of Alabama is a cluster unto itself.
-In 2017, the University of Alabama made 985 visits to private high schools.
+We briefly sketch broad findings before discussing each cluster.
+First, for must public research universities in our sample, the vast majority of private school visits were to out-of-state schools [WHICH FIGURE/TABLE SHOWS THIS], which is consistent with the idea that public research universities pursue students from affluent households who can afford nonresident tuition price.
+Second, Figure \@ref(fig:ego-network-figure-pubu) indicates that public research universities tended to visit private high schools with weaker academic reputation than the set of schools visited by private colleges and universities [LATER, SAY GOING AFTER MONEY WITHOUT ACADEMIC REP].
+Third, despite being nonsectarian, most public research universities visited a higher share of private high schools that were Catholic or Chrisitan than those visited by private colleges and universities.
+Fourth, racial composition of schools visited by public research universities was similar to the set of schools visited by private colleges and universities.
+A few public research universities appear (e.g., UC Irvine, UC Riverside) appear to visit a more racially diverse set of schools, but these institutions visited very few private schools.
+
+<!--
+Truly singular in the realm of recruiting, the University of Alabama is a cluster unto itself
+-->
+
+The University of Alabama is a cluster unto itself and is centrally located in the network graph in Figure \@ref(fig:plot-1mode-pubu).
+In 2017, the University of Alabama made 985 visits to U.S.
+private high schools.
 This number was more than double the 486 visits made by the University of South Carolina, which ranked second amongst public research universities in terms of number of private school visits, and substantially more than the 687 visits made by Notre Dame, which ranked first amongst private colleges and universities.
-With respect to geographic region, more than 50% of visits were in the South.
+Drawing from Figure \@ref(fig:ego-network-figure-pubu), more than 50% of visits by the University of Alabama were in the South.
+With respect to religious affiliation, nearly 50% of visits were to Catholic schools and about 25% of visits were to Christian schools.
+In contrast to the majority of private colleges and universities in our sample, the University of Alabama made nearly 50% of its visits at schools that received a grade of less than "A+" by Niche.
+At the same time 80% of visited schools enrolled fewer than 25% of students who identified as Black, Latinx, or Native.
 
-[AT SOME POINT SAY THAT THE GOEGRAPHIC REGION IS NOT ALWAYS THE SAME AS REGION THEY ARE LOCATED IN; IN GENERAL SAY A LOT ABOUT GEOGRAPHIC REGION]
+A second cluster, located nearly as centrally in Figure \@ref(fig:plot-1mode-pubu) as the University of Alabama, consists of the University of South Carolina (486 visits) and the University of Colorado-Boulder (379 visits).
+These institutions ranked second and third amongst public universities in our sample in terms of number of visits.
+Geographically, both universities recruiting nationally but concentrated on some regions more than others.
+For both universities, the Northeast and Midwest accounted for about 25% of visits.
+The University of South Carolina concentrated visits in its home region, the South.
+CU-Boulder made X% of visits in its home region, the West, and made X% of visits in the South.
+Both universities made more than 60% of visits at Catholic or Christian affiliated schools.
+In terms of academic reputation, CU-Boulder visited a slightly stronger set of schools than the University of South Carolina and both universities visited a stronger set of schools than the University of Alabama.
 
-having made 985 visits to U.S. private high schools in 2017 In 2017
-At 985 visits, the University of Alabama made more
+Third, the largest cluster -- at nine universities -- and the most diverse in terms of geographic location and academic reputation consists of three universities from the Northeast (Rutgers, UMass Amherst, University of Pittsburgh), two Midwest universities (University of Cincinnati, University of Kansas), two universities in the South (University of Arkansas, University of Georgia), and two universities from the West (UC Berkeley, UC San Diego).
+Located between the center and periphery in Figure \@ref(fig:plot-1mode-pubu), these universities made a moderate number of private school visits, ranging from 197 by UC-San Diego to 302 and 303, respectively, by the University of Georgia and Rutgers.
 
-created from the respective ego networks of each public research university, shows characteristics of private high schools visited our sample of private colleges and universities, specifically, geographic region, religious affiliation, academic reputation, and racial composition.
+These universities differ in the extent to which visits were concentrated in their home geographic region.
+At the high end, the University of Georgia -- 47th in YYYY US News rankings -- and the University of Arkansas -- 160th in US News rankings -- are located in the South and made at least 75% of visits in the South.
+The remaining seven universities generally made more visits in their home geographic than other regions but while also making substantial visits outside their home region, particularly in the South.
+For example, three highly ranked universities -- University of Pittsburgh (ranked 58), UC-Berkeley (ranked 22), and UC-San Diego  (ranked 35) each made a substantial share of visits in the South.
+In contrast to private colleges and universities, several public research universities in this cluster largely ignored particular geographic regions altogether.
+For example, the University of Kansas and the University of Arkansas did not visit the Northeast.
+The University of Georgia, UC-San Diego, and UMass Amherst largely ignored the MidWest, while the University of Pittsburgh did not visit the West.
 
-ADD TABLES/FIGURES OF VISITS BY PUBLIC RESEARCH UNIVERSITIES.
+With the exception of UC-Berkeley, the universities in this cluster made more than 50% of visits to sectarian Catholic or Christian affiliated schools.
+Universities that made a substantial share of visits to Christian affiliated schools also tended to make a large share of visits in the share of visits in the South [OVERLAP BETWEEN SOUTH AND CHRISTIAN].
+Finally, with the exception of UC-Berkeley, UC-San Diego, and to a lesser extent the University of Georgia -- three highly ranked universities -- the academic repuation of schools visited by this cluster was substantially lower than those visited by the majority of private colleges and universities in our sample.
+These results suggest that non-prestigious public research universities visit a large number non-elite private high schools that generally did not receive visits from selective private colleges and universities.
+
+The final cluster consists of five universities -- University of Nebraska-Lincoln (159 visits, 104 out-of-state), SUNY Stony Brook (146 visits, 107 out-of-state), UC Riverside (87 visits, 32 out-of-state), UC Irvine (60 visits, 40 out-of-state), North Carolina State University  (23 visits, 20 out-of-state).
+These universities made fewer private school visits than the other public research universities, made a relatively higher share of in-state visits, and generally concentrated visits within their home geographic region.
+As such, they are located on the periphery of the network in Figure \@ref(fig:plot-1mode-pubu).
+
+<!-- reminder of RQs: 
+1. which schools receive visits from which colleges/universities? 
+2. to what extent are visits more likely to occur between organizations that share certain characteristics
+-->
+
+Transitioning from the focus on public research universities to a focus on the private high schools they visit, Table \@ref(tab:hs-print-pubu) shows the characteristics of the 20 private high schools that received visits from the greatest number of public research universities in our sample.
+
+The top five high schools in  Table \@ref(tab:hs-print-pubu) each received visits from 11 (i.e., "degree" equals 11) of the 17 public research universities in our sample.
+Notably, all five schools were located in either California and Texas.
+Four of these schools are Catholic and one -- The Greenhill School -- is nonsectarian.
+These five schools differed in terms of the number of visits received.
+For example, both Jesuit College Prep in Dallas, TX and Santa Margarita Catholic High School in Rancho Santa Margarita, CA received 19 visits from 11 public research universities, while Cathedral Catholic High School in San Diego, CA received 13 visits from 11 public research universities [SAY SOMETHING ABOUT WHICH PUBLIC [OR PRIVATE] UNIVERSITIES VISITED THESE HIGH SCHOOLS?
+THIS CODE BELOW DOES THAT WORK IF YOU WANT TO INCLUDE IT; MAYBE SHOW EGO NETWORK OF A COUPLE HIGH SCHOOLS?]
+
+```{r, include = FALSE, eval = FALSE}
+df <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)
+df %>% select(name, school_name, degree, strength)
+
+events_data %>% glimpse()
+events_data %>% left_join(y = univ_info, by = c("univ_id")) %>% count(control)
+
+# this shows which universities visited the top 5 high schools most visited by public resarch universities in our sample
+  # can filter on "control" below to show visits by public and/or private universities
+    # "Public"
+    # "Private not-for-profit"
+events_data %>% left_join(y = univ_info, by = c("univ_id")) %>% 
+  filter(event_type == "priv_hs", control == "Private not-for-profit") %>% 
+  filter(school_id %in% c("01324487","02187540","00071446","A0900259","A0109386")) %>% 
+  left_join(y = privhs_df, by = c("school_id")) %>% 
+  arrange(school_id, univ_id) %>%
+  select(school_id, school_name, event_state,univ_id, univ_name)
+```
+The set of schools visited by the greatest number of public research universities from our sample differs substanitally from the schools visited by the greatest number of private colleges and universities.
+Only four of the 20 schools in \@ref(tab:hs-print-pubu) were also in the anologous table for private colleges and universities (Table \@ref(tab:hs-print-privu)), specifically the Greenhill School in Addison, TX, Episcopal High School in Alexandria, VA, St.
+Ignatius College Prep in Chicago, IL, and the McDonogh School in Owings Mills, MD.
+Compared the top 20 private schools most visited by private colleges and universities, the 20 most-visited schools by public research universities were more likely to be Catholic schools and they had substantially lower academic reputations.
+Of the 20 schools in Table \@ref(tab:hs-print-pubu), only one -- The Greenhill School in Addison, TX, ranked 64 -- was ranked in the top 100 nationally by Niche.
+By contrast, of the 20 schools most visited by private colleges and universities, nine were ranked in the top 100 by Niche.
+
+```{r, include = FALSE, eval = FALSE}
+# which schools in top 20 most visited by public universities were also top 20 most visited by private colleges and universities
+df_pubu <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20) %>% rename(degree_pub = degree, strength_pub = strength)
+df_privu <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20) %>% rename(degree_priv = degree, strength_priv = strength )
+
+df_pubu %>% glimpse()
+
+df_privu %>% select(name, degree_priv, strength_priv) %>% right_join(y = df_pubu, by = c("name")) %>%
+  select(name, school_name, city, state_code, degree_pub, strength_pub, degree_priv, strength_priv, religion_4, pct_blacklatinxnative, ranking, ranking_numeric)
+```
+
+The top 20 most-visited schools by public research universities enrolled a somewhat higher percentage of students who identify as Black/Latinx/Native than the schools most-visited by private colleges and universities.
+For example, of the top-20 schools most visited by public research universities, there were five schools where students who identify as Black, Latinx, or Native represent at least 30% of student enrollment.
+By contrast, none of the top-20 schools most visited by private colleges and universities enrolled at least 30% of students who identify as Black, Latinx, or Native.
+
+```{r, include = FALSE, eval = FALSE}
+df_pubu <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)
+df_pubu %>% filter(pct_blacklatinxnative>=30)
+
+df_privu <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20) 
+df_privu %>% filter(pct_blacklatinxnative>=30)
+```
+Table \@ref(tab:hs-table-pubu-agg) shows the characteristics of private high schools by number of public research universities that visited (e.g., 6+, 5, 4, etc.).
+Compared to schools that received visits from three or fewer public research universities, schools that received visits from several public research universities were disproportionaly located in the South, were more likely to be Catholic schools than Christian or nonsectarian, and were likely to be ranked in the top 200 by Niche or be graded as "A+" by Niche.
 
@@
 
-shit to say about comparison
+<!-- reminder of RQs: 
+1. which schools receive visits from which colleges/universities? 
+2. to what extent are visits more likely to occur between organizations that share certain characteristics
+-->
 
-- on avg. private colleges and universities made more visits than publics, except university of Aalabama.
--
+WHICH TABLES/FIGURES IN THIS SECTION
+
+- one-mode plot w/ vertices colored by cluster
+  - probably better to show all or pub out-state but not both
+  - given the focus is which public universities behave like private universities, think there is rationale for restricting public university events to out-of-state because out-of-state visits are behavior associated w/ privatization; also this makes it slightly different than what has already been analyzed
+- show ego figure organized by cluster
+- maybe which schools most visited?
+
+WHAT SHOULD FOCUS OF RESULTS BE
+
+- which public universities behave like private universities
+  - this strikes me as the case for out-of-state only
+
+<!-- CLUSTERS, ALL
+
+ 1  2  3  4 
+ 4 21  5 12
+
+> save_1mode_plot(g_2mode, mode = "psi", layout = layout_with_fr, c_analysis = "hclust", k=4, h = NULL, hclust_method = "ward.D", plot_margin = 0.0, plot_name = "plot_1mode_all.pdf")
+# A tibble: 42 x 2
+   name              cluster
+   <chr>               <int>
+ 1 Notre Dame              1
+ 2 SMU                     1
+ 3 U of Alabama            1
+ 4 Villanova               1
+
+ 5 Baylor                  2
+ 6 Case Western Res.       2
+ 7 Emory                   2
+ 8 Harvey Mudd             2
+ 9 Macalester              2
+10 Occidental              2
+11 Rutgers                 2
+12 Scripps                 2
+13 Smith                   2
+14 Stevens Ins. Tech       2
+15 Swarthmore              2
+16 U of Arkansas           2
+17 U of Cincinnati         2
+18 U of Denver             2
+19 U of Georgia            2
+20 U of Kansas             2
+21 U of Pitt               2
+22 UC Berkeley             2
+23 UC San Diego            2
+24 UMass Amherst           2
+25 Williams                2
+
+26 NCSU                    3
+27 SUNY Stony Brook        3
+28 UC Irvine               3
+29 UC Riverside            3
+30 UNL                     3
+
+31 Boston Coll.            4
+32 Colorado Coll.          4
+33 Conn Coll.              4
+34 CU Boulder              4
+35 Middlebury              4
+36 Northwestern            4
+37 Oberlin                 4
+38 Sewanee                 4
+39 TCU                     4
+40 Tufts                   4
+41 Tulane                  4
+42 U of S.Carolina         4
+.
+
+-->
+DD
+
+<!-- CLUSTERS, ONLY OUT-OF-STATE FOR PUBLIC RESEARCH UNIVERSITIES
+
+.
+ 1  2  3  4 
+11 13  5 13
+
+> save_1mode_plot(g_2mode, mode = "psi", pubu_visits = 'outst', layout = layout_with_fr, c_analysis = "hclust", k=4, h = NULL, hclust_method = "ward.D", plot_margin = 0.0, plot_name = "plot_1mode_all_pubu_outst.pdf")
+
+# A tibble: 42 x 2
+
+   name              cluster
+   <chr>               <int>
+ 1 Boston Coll.            1
+ 2 CU Boulder              1
+ 3 Northwestern            1
+ 4 Notre Dame              1
+ 5 Sewanee                 1
+ 6 SMU                     1
+ 7 TCU                     1
+ 8 Tulane                  1
+ 9 U of Alabama            1
+10 U of S.Carolina         1
+11 Villanova               1
+
+12 Baylor                  2
+13 Harvey Mudd             2
+14 Rutgers                 2
+15 Scripps                 2
+16 Stevens Ins. Tech       2
+17 U of Arkansas           2
+18 U of Cincinnati         2
+19 U of Georgia            2
+20 U of Kansas             2
+21 U of Pitt               2
+22 UC Berkeley             2
+23 UC San Diego            2
+24 UMass Amherst           2
+
+25 NCSU                    3
+26 SUNY Stony Brook        3
+27 UC Irvine               3
+28 UC Riverside            3
+29 UNL                     3
+
+30 Case Western Res.       4
+31 Colorado Coll.          4
+32 Conn Coll.              4
+33 Emory                   4
+34 Macalester              4
+35 Middlebury              4
+36 Oberlin                 4
+37 Occidental              4
+38 Smith                   4
+39 Swarthmore              4
+40 Tufts                   4
+41 U of Denver             4
+42 Williams                4
+
+-->
 
@@
 
-```{r, ego-table-privu, echo = FALSE, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego_privu.RDS')
-knitr::kable(
-  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
-  caption = 'ego table private colleges and universities') %>% landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego_privu.RDS')
-#df %>% select(ID,University,Cluster,Type,Rank,c1_lt10,c2_10to25,c3_25to50,`c4_50+`) %>%mutate(lt25 = as.numeric(c1_lt10) + as.numeric(c2_10to25))
-
-knitr::kable(
-  df %>% select(ID,University,Cluster,Rank,c1_lt10,c2_10to25,c3_25to50,`c4_50+`), row.names = F, # select(-ID, -Characteristics) Characteristics ,Type
-  caption = 'la la') %>% landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
 ```{r, hs-print-privu, echo = FALSE}
@@
 knitr::kable(
-  df %>% select(-name,-closeness), caption = 'most central private high schools, private colleges and universities') %>% 
+  df %>% select(-name,-closeness), caption = 'The 20 most central private high schools with respect to visits from private colleges and universities') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r, ego-table-pubu, echo = FALSE, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego_pubu.RDS')
-knitr::kable(
-  df %>% select(-ID,-Characteristics), row.names = F, # select(-ID, -Characteristics)
-  caption = 'ego table caption public universities') %>% landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
 ```{r, hs-print-pubu, echo = FALSE}
@@
 knitr::kable(
-  df %>% select(-name,-closeness), caption = 'most central private high schools, private colleges and universities') %>% 
+  df %>% select(-name,-closeness), caption = 'The 20 most central private high schools with respect to visits from public research universities') %>% 
   landscape(margin = NULL) %>%
@@
 
-knitr::kable(df, caption = 'characteristics of high schools by degree band, private colleges and universities') %>% 
+knitr::kable(df, caption = 'characteristics of high schools by degree band, public research universities') %>% 
   landscape(margin = NULL) %>%

### 2020-11-19 scripts/network_recruiting_analysis.R

@@ -799,8 +799,8 @@ create_2mode_table <- function(twomode_network, race_var = 'pct_blacklatinxnativ
   
   #BREAK SUCKA!  
   # Full table
-  full_twomode_table <- twomode_df %>% arrange(-degree) %>%
-    select_('name', 'school_name', 'city', 'state_code', 'region', 'religion', race_var, 'ranking', 'ranking_numeric', 'degree', 'closeness', 'strength')
+  full_twomode_table <- twomode_df %>% arrange(-degree, -strength) %>%
+    select_('name', 'school_name', 'city', 'state_code', 'region', 'religion_4', race_var, 'ranking', 'ranking_numeric', 'degree', 'closeness', 'strength')
   
   # Aggregated table
   agg_twomode_table <- twomode_df %>%
@@ -808,7 +808,7 @@ create_2mode_table <- function(twomode_network, race_var = 'pct_blacklatinxnativ
     summarise(Count = n())
 
   agg_twomode_table <- left_join(agg_twomode_table, create_agg_table(twomode_df, 'region'))
-  agg_twomode_table <- left_join(agg_twomode_table, create_agg_table(twomode_df, 'religion'))
+  agg_twomode_table <- left_join(agg_twomode_table, create_agg_table(twomode_df, 'religion_4'))
   agg_twomode_table <- left_join(agg_twomode_table, create_agg_table(twomode_df, paste0(race_var, '_cat')))
   agg_twomode_table <- left_join(agg_twomode_table, create_agg_table(twomode_df, ranking_var))
   
@@ -817,13 +817,15 @@ create_2mode_table <- function(twomode_network, race_var = 'pct_blacklatinxnativ
   
   names(agg_twomode_table) <- c('Degree', 'Count',
                                 'Northeast', 'Midwest', 'South', 'West',
-                                'Catholic', 'Conservative Christian', 'Nonsectarian', 'Other',
+                                'Catholic', 'Christian', 'Nonsectarian', 'Other',
                                 levels(as.factor(twomode_df[[paste0(race_var, '_cat')]])),
                                 levels(as.factor(twomode_df$rank_cat2)), 'rank_NA')
   
[…]

### 2020-11-20 manuscript.Rmd
muddling through

@@
 Our analyses to date have focused on public research universities.
-As described in more detail below, 12 of the 15 public research universities in our sample made far more out-of-state visits than in-state visits, a finding antithetical to the stated mission of most public research universities.
+As described in more detail below, 12 of the 15 [FIX NUMBERS, IT'S 17 PUBLICS] public research universities in our sample made far more out-of-state visits than in-state visits, a finding antithetical to the stated mission of most public research universities.
 These out-of-state visits focused on wealthy, predominantly white schools and communities.
@@
 
+```{r, include = FALSE, eval = FALSE}
+# check to make sure ego table that exludes in-state events by public universities is correct
+df_all <- readRDS('./assets/tables/table_ego_all.RDS')
+df_all_pubu_outst <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
+
+df_all %>% glimpse()
+df_all_pubu_outst %>% glimpse()
+
+df_all %>% count(Cluster)
+df_all_pubu_outst %>% count(Cluster)
+
+df_all %>% arrange(ID) %>% filter(Type == "univ") %>% select(ID,University,total,Northeast,Midwest,South,West,Catholic,Christian,Nonsect,Other) %>% 
+   print(n=50)
+
+df_all_pubu_outst %>% arrange(ID) %>% filter(Type == "univ") %>% select(ID,University,total,Northeast,Midwest,South,West,Catholic,Christian,Nonsect,Other) %>% 
+   print(n=50)
+```
+
 <!-- reminder of RQs:
+
 1. which schools receive visits from which colleges/universities? 
 2. to what extent are visits more likely to occur between organizations that share certain characteristics
+
 -->
+
+We conclude by comparing the off-campus recruiting visits to private high schools by public research universities to those of private colleges and universities.
+
+For these analyses, we include both in-state and out-of-state visits made by private colleges and universities but we exclude in-state visits by public research universities but we do not exclude.
+The motivation for this decision is as follows.
+For most public research universities in our sample, the overwhelming majority of visits to private schools are to out-of-state private schools.
+Prior research suggests that nonresident enrollment growth by public research universities is substantially motivated by the goal of growing tuition revenue [CITE].
+Typically, nonresident tuition price at public research universities is substantially higher than resident tuition price but lower than the price charged by selective private colleges and universities (e.g., in 2018-19 fulltime annual resident tuition price at the University of Colorad-Boulder was \$10,728, compared to nonresident tuition price of \$35,482, compared to tuition price of $54,120 at Northwestern University).
+We argue that the pursuit of out-of-state students by public universities is an example of "privatization" because out-of-state enrollment is antithetical to the traditional mission of public universities but is consistent with the mission of private colleges and universities.
+Furthermore, we argue that out-of-state recruiting efforts by public research universities focus on affluent households who are also considering private colleges and universities.
+Therefore, comparing recruiting visits by private colleges and universities to out-of-state visits by public research universities provides a helpful test of the extent to which public institutions are mimicking the behavior of private institutions.
+<!-- tuition price numbers from here:
+https://www.collegesimply.com/colleges/search
+-->
+Figure \@ref(fig:plot-1mode-pubu) plots the one-mode network of visits by the 42 public and private colleges and universities in our sample, with vertex color determined by hierarchical cluster analysis specified to create $k = 4$ clusters.
+Figure \@ref(ego-network-figure-all-pubu-outst) shows the characteristics of private high schools visited by these 42 institutions, sorted by cluster.
+Of the four clusters from Figures \@ref(fig:plot-1mode-pubu) and \@ref(ego-network-figure-all-pubu-outst), one contains solely of public research universities, one contains solely of private colleges and universities, and two contain a mix of private and public institutions.
+
+The public-only cluster consists of five institutions: North Carolina State University, SUNY Stony Brook, UC Irvine, UC Riverside, and the Unviersity of Nebraska-Lincoln.
+These universities made relatively few (out-of-state) visits to private high schools -- ranging from 20 by NC State to 107 by SUNY Stony Brook -- and, thus, are located on the periphery of the network in Figure \@ref(fig:plot-1mode-pubu).
+The private-only cluster consists of 13 institutions: Case Western Reserve, Colorado College, Connecticut College, Emory University, Macalester, Middlebury, Oberlin, Occidental, Smith, Swarthmore, Tufts, University of Denver, Williams.
+This cluster contains nine liberal arts colleges and four universities (U of Denver, Emory, Tufts, Case Western Reserve).
+Geographically, six of these institutions are located in the Northeast, three in the Midwest, two in the West, and one in the South.
+Compared to other postsecondary institutions in our sample, the colleges in this cluster made a moderate number of private school visits, ranging from 164 visits by Smith to 337 by Oberlin.
+Drawing from \@ref(ego-network-figure-all-pubu-outst), visits were spread out geographically rather than concentrated in a particular region.
+The majority of visits were to nonsectarian schools.
+Compared to other clusters, these colleges visited schools with strong academic reputations.
+
+We devote more attention to the two clusters that contain a mix of public and private postsecondary institutions.
+The first of these contains 11 institutions, including eight private universities (Boston College, Northwestern University, Notre Dame, Sewanee, Southern Methodist, Texas Christian University, Tulane, Villanova) and three public research universities (University of Alabama, University of Colorado-Boulder, University of South Carolina).
+The universities in this cluster made, relatively, a very high number of private school visits -- ranging from 333 by Boston College to 931 (out-of-state) visits by the University of Alabama -- and are located in the center of the network in Figure \@ref(fig:plot-1mode-pubu).
+Geographically, five of these institutions are located in the South, two in the Northeast, two in the Midwest, and one in the West.
+\@ref(ego-network-figure-all-pubu-outst) shows that most of these institutions -- even those not located in the South -- made a disproportionate number of recruiting visits in the South.
+This cluster contains three private Catholic universities (Notre Dame, Villanova, Boston College), which visited a relatively high share of Catholic Schools, and X private Christian universities (Sewanee, Southern Methodist, Texas Christian), which visited a relatively high share of Christian affiliated schools.
+More notable, however, is the extent to which the three public research universities focused visits on Catholic or Christian private schools.
+Finally, the universities in this cluster -- albeit to a less extent for Boston College, Northwestern, and Tulane -- visited private high schools with weaker academic reputations than those visited by the cluster of 13 private colleges and universities.
+The weak academic reputation of schools visited by Notre Dame -- similar to those visited by the University of Alabama and the University of South Carolina -- is surprising given that Notre Dame is ranked 19th by US News.
+
+The final cluster contains 13 institutions, including nine public research universities (U.
+of Arkansas, U.
+of Cincinnati, U.
+of Georgia, U.
+of Kansas, U.
+of Pittsburgh, UC-Berkeley, UC-San Diego, and UMass Amherst) and four private institutions (Harvey Mudd, Scripps, Stevens Institute of Technology, and Baylor).
+The universities in this cluster made a moderate number of private school visits -- ranging from 111 by Scripps to 257 by Baylor -- and are located between the center and the periphery of the network in Figure \@ref(fig:plot-1mode-pubu).
+Whereas, the public and private institutions in the previous cluster (e.g., University of Alabama and Notre Dame) were clearly similar to one another in recruiting patterns, the similarities between public and private institutions in this cluster are less clear.
+Interestingly, in our analyses of visits by private colleges and universities (above), these four private institutiosn were their own cluster and were on the periphery of the network.
+Geographically, these institutions are spread across the country, with recruiting visits concentrated in their home region and often in the South.
+[COMMENT ON SIMILARITIES BETWEEN PUBLIC AND PRIVATE W/ RESPECT TO REGION/RELIGION, ACADEMIC REPUTATION]
+
+```{r, include = FALSE, eval = FALSE}
+df <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
+
+# cluster 2; public and private
+df %>% filter(Cluster ==2) %>% select(ID, University, Type, Rank, control, total, in_state, out_state) %>% arrange(total)
+df %>% filter(Cluster ==2) %>% count(Type)
+df %>% filter(Cluster ==2) %>% count(control)
+```
+
+```{r, include = FALSE, eval = FALSE}
+df <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
+
+# cluster 2; public and private
+df %>% filter(Cluster ==2) %>% select(ID, University, Type, Rank, control, total, in_state, out_state) %>% arrange(total)
+df %>% filter(Cluster ==2) %>% count(Type)
+df %>% filter(Cluster ==2) %>% count(control)
+
+# cluster 1; public and private
+df %>% filter(Cluster ==1) %>% select(ID, University, Type, Rank, total, in_state, out_state) %>% arrange(total)
+df %>% filter(Cluster ==1) %>% count(Type)
+
+# cluster 4; private only
+df %>% filter(Cluster ==4) %>% select(ID, University, Type, Rank, total, in_state, out_state) %>% arrange(total)
+df %>% filter(Cluster ==4) %>% count(Type)
+df %>% filter(Cluster ==4, Type == "univ") %>% select(ID, University, Type, Rank, total, in_state, out_state)
+
+# cluster 3; public only 
+df %>% filter(Cluster ==3) %>% select(ID, University, Type, Rank, total, in_state, out_state) %>% arrange(total)
+df %>% filter(Cluster ==4) %>% count(Type)
+df %>% filter(Cluster ==4, Type == "univ") %>% select(ID, University, Type, Rank, total, in_state, out_state)
+
+```
 
@@
 - show ego figure organized by cluster
+  - make this one only include out-of-state events for public research universities
 - maybe which schools most visited?
@@
 
-<!-- CLUSTERS, ALL
-
- 1  2  3  4 
- 4 21  5 12
-
-> save_1mode_plot(g_2mode, mode = "psi", layout = layout_with_fr, c_analysis = "hclust", k=4, h = NULL, hclust_method = "ward.D", plot_margin = 0.0, plot_name = "plot_1mode_all.pdf")
-# A tibble: 42 x 2
-   name              cluster
-   <chr>               <int>
- 1 Notre Dame              1
- 2 SMU                     1
- 3 U of Alabama            1
- 4 Villanova               1
-
- 5 Baylor                  2
- 6 Case Western Res.       2
- 7 Emory                   2
- 8 Harvey Mudd             2
- 9 Macalester              2
-10 Occidental              2
-11 Rutgers                 2
-12 Scripps                 2
-13 Smith                   2
-14 Stevens Ins. Tech       2
-15 Swarthmore              2
-16 U of Arkansas           2
-17 U of Cincinnati         2
-18 U of Denver             2
-19 U of Georgia            2
-20 U of Kansas             2
-21 U of Pitt               2
-22 UC Berkeley             2
-23 UC San Diego            2
-24 UMass Amherst           2
-25 Williams                2
-
-26 NCSU                    3
-27 SUNY Stony Brook        3
-28 UC Irvine               3
-29 UC Riverside            3
-30 UNL                     3
-
-31 Boston Coll.            4
-32 Colorado Coll.          4
-33 Conn Coll.              4
-34 CU Boulder              4
-35 Middlebury              4
-36 Northwestern            4
-37 Oberlin                 4
-38 Sewanee                 4
-39 TCU                     4
-40 Tufts                   4
-41 Tulane                  4
-42 U of S.Carolina         4
-.
-
--->
-DD
-
-<!-- CLUSTERS, ONLY OUT-OF-STATE FOR PUBLIC RESEARCH UNIVERSITIES
-
-.
- 1  2  3  4 
-11 13  5 13
-
-> save_1mode_plot(g_2mode, mode = "psi", pubu_visits = 'outst', layout = layout_with_fr, c_analysis = "hclust", k=4, h = NULL, hclust_method = "ward.D", plot_margin = 0.0, plot_name = "plot_1mode_all_pubu_outst.pdf")
-
-# A tibble: 42 x 2
-
-   name              cluster
-   <chr>               <int>
- 1 Boston Coll.            1
- 2 CU Boulder              1
- 3 Northwestern            1
- 4 Notre Dame              1
- 5 Sewanee                 1
- 6 SMU                     1
- 7 TCU                     1
- 8 Tulane                  1
- 9 U of Alabama            1
-10 U of S.Carolina         1
-11 Villanova               1
-
-12 Baylor                  2
-13 Harvey Mudd             2
-14 Rutgers                 2
-15 Scripps                 2
-16 Stevens Ins. Tech       2
-17 U of Arkansas           2
-18 U of Cincinnati         2
-19 U of Georgia            2
-20 U of Kansas             2
-21 U of Pitt               2
-22 UC Berkeley             2
-23 UC San Diego            2
-24 UMass Amherst           2
-
-25 NCSU                    3
-26 SUNY Stony Brook        3
-27 UC Irvine               3
-28 UC Riverside            3
-29 UNL                     3
-
-30 Case Western Res.       4
-31 Colorado Coll.          4
-32 Conn Coll.              4
-33 Emory                   4
-34 Macalester              4
-35 Middlebury              4
-36 Oberlin                 4
-37 Occidental              4
-38 Smith                   4
-39 Swarthmore              4
-40 Tufts                   4
-41 U of Denver             4
-42 Williams                4
-
--->
-
 ```{r, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego_all.RDS')
+#df <- readRDS('./assets/tables/table_ego_all.RDS')
+df <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
 df %>% glimpse()
@@
 ```
+
 # References
@@
 
-type_vec <- c('privu', 'pubu', 'all')
+type_vec <- c('privu', 'pubu', 'pubu_outst', 'all','all_pubu_outst')
 
@@
 
-```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all"}
+```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all", include= FALSE, eval = FALSE}
 knitr::include_graphics('assets/figures/plot_1mode_all.pdf')
@@
 
-```{r ego-network-figure-all, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by public and private colleges and universities"}
-knitr::include_graphics('assets/figures/ego_network_figure_all.pdf')
+```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by public and private colleges and universities, out-of-state visits only for public universities"}
+knitr::include_graphics('assets/figures/ego_network_figure_all_pubu_outst.pdf')
 #out.width="1.1\\linewidth", 

### 2020-11-20 scripts/network_recruiting_analysis.R

@@ -359,7 +359,7 @@ save_2mode_plot <- function(network, pubu_visits = 'all', privu_visits = 'all', 
   }
   
   # out-of-state visits only for both public and private colleges/universities
-  if (pubu_visits == 'outst' & privu_visits == 'outst') {
+  else if (pubu_visits == 'outst' & privu_visits == 'outst') {
     
     network <- subgraph.edges(graph = network, eids = E(g_2mode)[E(network)$visit_loc == "outofstate"])
   }
@@ -650,8 +650,7 @@ save_1mode_plot(g_2mode, mode = "psi", pubu_visits = 'outst', layout = layout_wi
 ## TABLE FROM EGO IGRAPH OBJECTS
 ## ------------------------------
 
-
-create_ego_table <- function(twomode_network, ego_networks, univs, c_analysis, race_var = 'pct_blacklatinxnative_cat', ranking_var = 'rank_cat2', k = NULL, h = NULL) {
+create_ego_table <- function(twomode_network, ego_networks, univs, pubu_visits = 'all', privu_visits = 'all', c_analysis, race_var = 'pct_blacklatinxnative_cat', ranking_var = 'rank_cat2', k = NULL, h = NULL) {
   
   ego_tbl <- data.frame(univ_id = character(0), univ_name = character(0), cluster = character(0), univ_type = character(0), univ_ranking = character(0), characteristics = character(0),
                         region_1 = character(0), region_2 = character(0), region_3 = character(0), region_4 = character(0),
@@ -659,10 +658,38 @@ create_ego_table <- function(twomode_network, ego_networks, univs, c_analysis, r
                         race_1 = character(0), race_2 = character(0), race_3 = character(0), race_4 = character(0),
                         ranking_1 = character(0), ranking_2 = character(0), ranking_3 = character(0), ranking_4 = character(0),
                         stringsAsFactors=FALSE)
+
+  # modify igraph objects depending on whether in-state visits are included
   
+    # all visits for private; out-of-state only for publics; 
+    if (pubu_visits == 'outst' & privu_visits != 'outst') {
+      
+      # modify two-mode network
[…]

### 2020-11-20 manuscript.Rmd
meh

@@
 
-WHICH TABLES/FIGURES IN THIS SECTION
+# Summary and Discussion
 
-- one-mode plot w/ vertices colored by cluster
-  - probably better to show all or pub out-state but not both
-  - given the focus is which public universities behave like private universities, think there is rationale for restricting public university events to out-of-state because out-of-state visits are behavior associated w/ privatization; also this makes it slightly different than what has already been analyzed
-- show ego figure organized by cluster
-  - make this one only include out-of-state events for public research universities
-- maybe which schools most visited?
-
-WHAT SHOULD FOCUS OF RESULTS BE
-
-- which public universities behave like private universities
-  - this strikes me as the case for out-of-state only
-
-```{r, include = FALSE, eval = FALSE}
-#df <- readRDS('./assets/tables/table_ego_all.RDS')
-df <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
-df %>% glimpse()
-df %>% select(ID,University,Cluster,total) %>% 
-  arrange(Cluster,total) %>% print(n=50)
-```
+[ADD SUCCINCT, CONCRETE SUMMARY FOCUSING ON BIG FINDINGS AND THEMES; VERY BRIEF DISCUSSION]
 

### 2020-11-30 manuscript.Rmd
ugh

@@
 ```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
+#df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS')))
+#df %>% glimpse()
+
 plot_characteristic <- function(df, type, characteristics) {
-  sub_df <- df %>% select(University, characteristics) %>%
+  sub_df <- df %>% select(univ_name, characteristics) %>%
     gather(key, value, characteristics) %>%
@@
   # colors <- sub_df$color[order(sub_df$University)]
-  univ_order <- (df %>% arrange(desc(Cluster), University))$University
+  univ_order <- (df %>% arrange(desc(cluster), univ_name))$univ_name
   #univ_order <- (df %>% arrange(desc(Cluster), Type, as.numeric(Rank), University))$University
-  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))
+  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
+  #sub_df$univ_name
 
-  ggplot(sub_df, aes(fill = key, y = value, x = University)) + 
+  ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
     geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
@@
 
-  a <- plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
-  b <- plot_characteristic(ego_df, 'Religion', c('Catholic', 'Christian', 'Nonsect', 'Other'))
+  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'))
+  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'nonsectarian', 'other'))
   c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))

### 2020-11-30 manuscript.Rmd
updates to ego plots

@@
 
-plot_characteristic <- function(df, type, characteristics) {
-  sub_df <- df %>% select(univ_name, characteristics) %>%
-    gather(key, value, characteristics) %>%
+plot_characteristic <- function(df, type, characteristic) {
+  sub_df <- df %>% select(univ_name, characteristic) %>%
+    gather(key, value, characteristic) %>%
     mutate(value = parse_number(value))

### 2020-11-30 scripts/network_recruiting_analysis.R

@@ -605,7 +605,7 @@ create_ego_table <- function(twomode_network, ego_networks, univs, c_analysis, k
   col_names <- c('univ_id', 'univ_name', 'cluster', 'type', 'rank', 'control', 'total', 'in_state', 'out_of_state', 'characteristics',
                  region_vals, religion_vals, race_vals, ranking_vals)
   
-  ego_tbl <-data.frame(matrix(NA_character_, ncol = length(col_names), nrow = 0, dimnames = list(NULL, col_names)), stringsAsFactors = F)
+  ego_tbl <- data.frame(matrix(NA_character_, ncol = length(col_names), nrow = 0, dimnames = list(NULL, col_names)), stringsAsFactors = F, check.names = F)
     
   # Populate ego table
   for (i in seq_along(univs)) {

### 2020-12-15 manuscript.Rmd
draft changes to intro

@@
 # Introduction
+
+<!-- 
+A pair of papers by Stevens provide interesting statements about the functions of higher education and the behavior of colleges and universities
+-->
+
+Colleges and universities visit high schools that enroll desirable prospects, while high schools accept visits from colleges and universities that offer enrollment opportunities valued by some segment of the class.
+Drawing from a pair of papers by Mitchell Stevens [@RN2377; @RN4517], we argue that analysis of which high schools receive visits from which colleges and univeristies provides an opportunity how K-12 and postsecondary organizations form relationships that serve social reproduction.
+
+@RN2377 introduces the metaphors "sieve" and a "hub" to describe how sociologists conceive of the functions of higher education.
+Sociology's stratification and schooling tradition conceives of higher education as a "sieve" -- an instrument that strains and separates -- that allocates people to occupational and social positions.
+The sieve metaphor builds on "Max Weber's core insight that education has a dual character" [@RN2377, p.
+129], on one hand, serving social mobility by redistributing access to privileged positions and, on the other, serving social reproduction by granting privileged families disproportionate access to universities that confer privileged positions.
+
+[CUT THIS PARAGRAPH AND JUST SKIP TO RELIANCE ON PATRONAGE FROM ELITE ACTORS] Building on the sociology of organizational behavior, @RN2377 conceives of higher education as a "hub" that connects, pollinates, and legitimizes "prominent institutional sectors of modern societies" (e.g., professions, the philanthropic sector, nation-state, larger economy).
+The paradox, writes @RN2377 is that as a hub, higher education is "simultaneously a powerful and fragile social institution.
+On the one hand, higher education [is powerful because it] connects and reciprocally blesses various forms of privilege.
+Elite groups (e.g., high-status families, professions, politicians, scientists, intellectuals) and those aspiring to be a part of them use higher education to certify their legitimacy" (p.
+137).
+On the other hand, higher education is fragile because it depends on "patronage as a primary source of revenue."
+
+Building on @RN2377, @RN4517 introduces three historical configurations that describe the relationship between higher education and society.
+The "association configuration" -- which defined higher education through the 19th century, but remains important particularly for private colleges -- views colleges as voluntary associations that depended on patronage from other associations (e.g., religious congregations, local business interests, professions).
+Second, the "national service" configuration -- most associated with the decades following World War II -- views higher education as an engine of nation building and economic development and thus worthy of investment from federal and state givernments.
+Third, "market" configuration -- which has emerged since the 1980s -- is associated with declining public investment, and competition between colleges for "students, patrons, and prestige" (p.
+121).
+
+These metaphors -- which describe higher education as simultaneously serving social mobility and social reproduction and depending on patronage from the government, from volunary associations, and private households -- provide a helpful lense from which to view the recruiting behavior of colleges and universities.
+Selective private colleges and universities operate substantially under the association configuration and primarily serve the social reproduction of families and institutions they depend on for patronage.
+Public universities were founded from the "national service" configuration to serve social mobility and economic development, but declines in public funding compel public universities to find new patrons.
+
+This paper analyzes the recruiting behavior of selective private colleges and universities to that of public research universities....
+
+Public universities were founded
+
+means of nation building and economic development and
+
+which defined higher education through the 19th century
+
+<!-- 
+\cite{RN4517} describes the transformation from a ``national service'' political economy to a ``market'' political economy.
+Under the national service arrangement the state views higher education as a primary means of nation building and economic development \citep{RN4517}.
+Thus, the national service arrangement is associated with federal and state investments in higher education.
+The decades following World War II are most associated with this arrangement.
+At the federal level, the GI Bill in 1944, the National Defense Education Act of 1958, and the Higher Education Act of 1965 collectively increased federal investment in university research and created the federal financial aid system.
+State governments dramatically increased appropriations to public universities, with the California Master Plan serving as a model for other states.
+This federal and state funded expansion institutionalized the role of higher education in determining the allocation of individuals to occupations.
+In turn, higher education became the primary mechanism of social reproduction and a primary means of social mobility.
+This arrangement benefited universities directly, through increased government funding, and indirectly, in that ``they became the purveyors of the very credentials increasingly required for prosperous lives'' \citep[p.~128]{RN4517}.
+-->
+
+``patronage as a primary revenue source'' \citep[p.~138]{RN2377}.
+
+The paradox, writes @RN2377 is that as
+
+As a hub, @RN2377 writes that the paradox of higher
+
+Building on the sociology of organizational behavior, @RN2377 conceives of higher education as a "hub" that connects, pollinates, and legitimizes "prominent institutional sectors of modern societies" (e.g., professions, philanthropic sector, : the labor market and the larger economy, the professions and the sciences, the philanthropic sector, the family, and the nation-state" (p.
+135).
+
+core functions of higher education.
+@RN2377 synthesizes how sociology conceives of the functions of higher education, introducing  functions of higher education by introducing
+
+@RN2377 synthesizes how sociology conceives the functions of higher education by introducing the metaphors "sieve," "incubator," "temple," and "hub." As a sieve - an instrument that strains and separates - higher education allocates people to occupational and social positions.
+The sieve metaphor builds on "Max Weber's core insight that education has a dual character" [@RN2377, p.
+129], on one hand, serving social mobility by redistributing access to privileged positions and, on the other, serving social reproduction by granting privileged families disproportionate access to universities that confer privileged positions.
+
+The extent to which higher education serves reproduction versus redistribution is sensitive to the external funding environment because universities depend on ``patronage as a primary revenue source'' [@RN2377, p.
+138].
 

### 2020-12-17 manuscript.Rmd
revising intro

--- 2020-11-30 manuscript.Rmd
@@
 bibliography: ./other/burd_recruiting_chapter.bib
-output: bookdown::pdf_document2
+output: 
+  bookdown::pdf_document2:
+    toc: FALSE
 csl: ./other/apa.csl
@@
 
+<!-- 
+A pair of papers by Stevens provide interesting statements about the functions of higher education and the behavior of colleges and universities
+Colleges and universities visit high schools that enroll desirable prospects, while high schools accept visits from colleges and universities that offer enrollment opportunities valued by some segment of the class.
+Drawing from a pair of papers by Mitchell Stevens [@RN2377; @RN4517], we argue that analysis of which high schools receive visits from which colleges and univeristies provides an opportunity how K-12 and postsecondary organizations form relationships that serve social reproduction.
+
+-->
+
+This chapter presents a social network analysis of off-campus recruiting visits made by US colleges and universities to US private high schools.
+Colleges and universities visit high schools that enroll desirable prospects, while high schools accept visits from colleges and universities that offer enrollment opportunities valued by some segment of the class.
+An off-campus recruiting visit is an indicator of a relationship between a college and a school that can be analyzed using standard tools of social network analysis.
+We analyze visits made in 2017 from a sample of 25 selective private colleges and universities and a sample of 17 public research universities.
+Analyses investigate which types of private high schools receive visits from which types of colleges and universities, emphasizing comparisons within and between public and private postsecondary institutions.
+
+The motivation for these analyses is grounded within the sociology of higher education, particularly two theoretical and empirical syntheses developed by Mitchell Stevens and colleagues [@RN2377; @RN4517].
+First, @RN2377 introduces metaphors that describe how sociology has conceived the functions of higher education.
+The stratification tradition conceives of higher education as a "sieve" -- an instrument that strains and separates -- that allocates people to occupational and social positions.
+This metaphor builds on "Max Weber's core insight that education has a dual character" [@RN2377, p.
+129], on one hand, serving social mobility by redistributing access to privileged positions and, on the other, serving social reproduction by granting privileged families disproportionate access to universities that confer privileged positions.
+The institutional theory tradition in sociology conceives of higher education as a "hub" that connects, pollinates, and legitimizes "prominent institutional sectors of modern societies" (e.g., professions, the philanthropic sector, corporate sector).
+As a hub, higher education is "simultaneously a powerful and fragile social institution.
+On the one hand, higher education [is powerful because it] connects and reciprocally blesses various forms of privilege.
+Elite groups (e.g., high-status families, professions, politicians, scientists, intellectuals) and those aspiring to be a part of them use higher education to certify their legitimacy" [@RN2377, p.
+137].
+On the other hand, higher education is fragile because it depends on "patronage as a primary source of revenue."
+
+@RN4517 introduces three alternative metaphors to describe the relationship between higher education and the American political economy.
+The "association" conceptualization, observed by @RN485, views colleges as voluntary (i.e., non-governmental) organizations founded by voluntary associations -- principally religious congregations and local business interests -- that rely "on the collective contributions and goodwill of their memberships" [@RN2377, p.
+126].
+Second, the "national service" configuration views higher education as a public-good engine of economic development and nation building and thus worthy of investment from federal and state governments.
+Third, "market" configuration conceives of higher education as a private good, suggesting that colleges should survive by competing for customers rather than rely on public funding.
+Each of these configurations is more or less associated with particular historical epochs and particular types of colleges and universities.
+For example, the association configuration defined US higher education through the 19th century, but remains salient for private colleges and universities.
+
+<!-- 
+The national service configuration is associated associated with massive public investment in higher education in the decades following World War II, while the market configuration is associated with declining state support for public universities since the 1980s.
+
+These metaphors -- which describe higher education simultaneously serving social mobility and social reproduction and depending on patronage from the government, from voluntary associations, and private households -- are useful for comparing public flagship universities to selective private colleges and universities
+-->
+
+These metaphors are useful for comparing the comparing public flagship universities to selective private colleges and universities.
+Selective private colleges and universities depend on patronage from affluent households (market configuration) and philanthropic interests (associational configuration) and primarily serve social reproduction rather than social mobility.
+Historically, public flagship universities depended on government funding associated with the national service configuration and served social mobility rather than reproduction.
+Since the 1980s, reductions in public funding associated with the emergence of the market configuration encourage public flagship universities to prioritize patronage from affluent households and philanthropic interests.
+As suggested by the adage, "he who pays the piper calls the tune," reliance on affluent private-sector interests increases the likelihood that public flagship universities -- like selective private colleges and universities -- will primarily serve social reproduction rather than social mobility.
+<!-- 
+The extent to which higher education serves reproduction versus redistribution is sensitive to the external funding environment because universities depend on ``patronage as a primary revenue source'' [@RN2377, p.
+138].
+-->
+
+We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction.
+However, access to concrete data on university recruiting behaviors has been a persistent barrier to empirical research.
+We collected data about off-campus recruiting visits made in 2017 by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for a sample of public research universities -- by issuing public records requests.
+The first study from this data collection analyzed visits made by 15 public research universities [@RN4450].
+The overwhelming majority of public research universities in our sample made more out-of-state visits than in-state visits, a finding antithetical to historic mission of public universities.
+These out-of-state visits focused on wealthy, predominantly white schools and communities, with a disproportionate number visits to out-of-state private high schools but relatively few visits to in-state private high schools.
+
+Building on [@RN4450], this chapter analyzes off-campus recruiting visits to private high schools made in 2017 by a sample of 25 selective private colleges and universities and 17 public research universities.
+We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
+Analyses are informed by two broad, related questions.
+First, which types of private high schools receive visits from which types of colleges and universities?
+Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+
+<!-- 
+Our decision to compare public and private colleges/universities on the dimension of visits to private schools is motivated by the idea that recruiting from private high schools serves social reproduction rather than social mobility.
+
+Our decision to compare public and private colleges/universities on the dimension of visits to private schools is motivated by the idea that recruiting from private high schools serves social reproduction rather than social mobility.
+Thus, visits to private schools are antithetical to the historic mission of public universities, especially given that the vast majority of visits are to out-of-state private schools.
+By contrast, recruiting from private high schools is consistent with the mission of selective private colleges and universities.
+From this perspective, visits to private schools by public research universities is one example of "privatization." A weakness of the empirical literature on privatization in higher education is that few studies public and private colleges/universities with respect to a behavior associated with privatization [@RN4543].
+By comparing public and private colleges/universities on the behavioral dimension of recruiting visits to private schools, we hope to develop new insights about the privatization of public higher education.
+
+-->
+
+Our decision to analyze visits to private schools is motivated by the idea that recruiting from private schools largely serves social reproduction [CITE A SOCIOLOGIST].
+Thus, visits to private school are antithetical to the historic "social mobility mission" of public universities [@RN2269], particularly since most private school visits by public research universities are to out-of-state schools [@RN4450].
+By contrast, recruiting from private high schools is consistent with the missions of selective private colleges and universities.
+From this perspective, private school visits by public research universities is an example of "privatization" that serves social reproduction.
+A weakness of the empirical literature on privatization in higher education is that few studies public and private colleges/universities with respect to a behavior associated with privatization [@RN4543].
+By comparing public and private colleges/universities on the behavioral dimension of recruiting visits to private schools, we hope to develop new insights about the privatization of public higher education.
+
+Finally, although private school students are more likely than public school students to come from affluent, college-educated households, the population of US private schools contains tremendous variation in religious affiliation, academic reputation, racial and socioeconomic composition, amongst other dimensions [@RN4504].
+Therefore, focusing solely on visits to private schools enables us to develop a nuanced analysis of which types of private high schools receive visits from which types colleges and universities.
+These nuances would be dificult to observe in an analysis that also included visits to public high schools.
+
+<!-- 
+We use social network analysis (SNA) to analyze off-campus recruiting visits.
+The motivation for using SNA is that SNA privileges relationships between actorsQualitative scholarship on private high schools finds that college access is substantially determined by the quality of the relationship between a particular college and a particular private high school [@RN4321; @RN4407].
+An off-campus recruiting visit is an indicator of a relationship between a college and a school that can be analyzed using standard tools of SNA.
+-->
+
+# What Do We Know About Off-campus Recruiting?
+
 <!-- The "enrollment funnel," shown in Figure X, describes stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students). -->
+
+This section provides context for our analyses by, first, situating off-campus recruiting within the broader set of marketing and recruiting interventions.
+Second, we review what is known about off-campus recruiting from market research and from academic scholarship, with a particular focus on scholarship that examines the relationship between private high schools and colleges/universities.
 
@@
 
-Each of these marketing/recruiting interventions -- and dozens of other interventions described in this book -- represent organizational behaviors that could be the subject of empirical research.
-However, the vast majority of research on enrollment management behaviors focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [E.G.] <!-- [@RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948] -->.
-By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664] [GIVE SOME CONCRETE BUDGET NUMBERS INDICATING BALL PARK SPENDING?].
-When we consider descriptions of enrollment management practice from investigative journalism [e.g., ], from enrollment management consulting firms and from this volume [e.g., ], it becomes apparent that -- with the notable exception of a small sociological case-study literature [e.g., ] -- the research community has ignores a great number of enrollment management practices that plausibly affect access to higher education.
-As a consequence, enrollment management remains an opaque industry to policymakers and the public.
-We argue that developing thoughtful policies about enrollment management depends on researchers collectively devloping empirical literatures that document enrollment management practices and evaluate the effects of these practices on opportunities for students.
-
-Access to concrete data about marketing and recruiting behaviors has been a persistent barrier to empirical research.
-To the extent that marketing/recruiting behaviors are inconsistent with public relations rhetoric (e.g., "our commitment to access"), colleges and universities may have incentive to withhold data from researchers.
-Therefore, conventional data collection methods such as surveys and even interviews should be appraised with healthy skepticism.
-We argue that pushing forward an empirical research agenda on marketing/recruiting behaviors depends on different modes of data collection -- including public records requests and "data science" methodologies, such as web-scraping and streaming social media data -- that record actual behaviors (e.g., contracts, transactions, records of expenditure) as opposed to statements by colleges/universities about their behavior.
-
-We present this chapter as an example of empirical research about marketing/recruiting behavior.
-This chapter analyzes off-campus recruiting visits by a sample of public research universities and a sample of selective private colleges and universities in 2017.
-We collected visit data by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for the sample of public research universities -- by issuring public records requests.
-Our analyses to date have focused on public research universities.
-As described in more detail below, 12 of the 15 [FIX NUMBERS, IT'S 17 PUBLICS] public research universities in our sample made far more out-of-state visits than in-state visits, a finding antithetical to the stated mission of most public research universities.
-These out-of-state visits focused on wealthy, predominantly white schools and communities.
-Additionally, most public research universities made a disproportionate number of out-of-state visits to private schools, but visited few in-state private schools.
-
-Building on these findings, this chapter analyzes off-campus visits to private high schools by public research universities and by selective private colleges and universities.
-We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
-Analyses are informed by two broad, related questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
-
-The motivation for comparing the behavior of public and private coleges/universities is based on the idea that (out-of-state) visits to private high schools are antithetical to the stated mission of public research universities.
-By contrast, recruiting visits to private high schools are consistent with the mission of private colleges and universities.
-From this perspective, out-of-state visits to private schools by public research universities is one example of "privatization." A weakness of the privatization literature is that few empirical studies compare the public and private institutions with respect to particular behaviors associated with privatization [@RN4543].
-Therefore, by comparing the (mostly out-of-state) visits to private high schools by public research universities to those of private colleges and universities, we hope to develop new insights about the privatization of public higher education.
-
-We use social network analysis (SNA) to analyze off-campus recruiting visits.
-The motivation for using SNA is that SNA privileges relationships between actorsQualitative scholarship on private high schools finds that college access is substantially determined by the quality of the relationship between a particular college and a particular private high school [@RN4321; @RN4407].
-An off-campus recruiting visit is an indicator of a relationship between a college and a school that can be analyzed using standard tools of SNA.
-
-[ADD ONE-PARAGRAPH OUTLINE?]
-
-# What Do We Know About Off-campus Recruiting?
-
-Our research analyzes off-campus recruiting visits by college and university admissions staff.
-So what do we know about off-campus recruiting?
+What do we know about off-campus recruiting from previous research?
 As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practioner-oriented publications.
@@
 
+# Discussion
+
+TEXT LA LA 
+<!--
+
+Each of these marketing/recruiting interventions -- and dozens of other interventions described in this book -- represent organizational behaviors that could be the subject of empirical research.
+However, the vast majority of research on enrollment management behaviors focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [E.G.] [@RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948]
+
+.
+By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664] [GIVE SOME CONCRETE BUDGET NUMBERS INDICATING BALL PARK SPENDING?].
+When we consider descriptions of enrollment management practice from investigative journalism [e.g., ], from enrollment management consulting firms and from this volume [e.g., ], it becomes apparent that -- with the notable exception of a small sociological case-study literature [e.g., ] -- the research community has ignores a great number of enrollment management practices that plausibly affect access to higher education.
+As a consequence, enrollment management remains an opaque industry to policymakers and the public.
+We argue that developing thoughtful policies about enrollment management depends on researchers collectively devloping empirical literatures that document enrollment management practices and evaluate the effects of these practices on opportunities for students.
+
+Access to concrete data about marketing and recruiting behaviors has been a persistent barrier to empirical research.
+To the extent that marketing/recruiting behaviors are inconsistent with public relations rhetoric (e.g., "our commitment to access"), colleges and universities may have incentive to withhold data from researchers.
+Therefore, conventional data collection methods such as surveys and even interviews should be appraised with healthy skepticism.
+We argue that pushing forward an empirical research agenda on marketing/recruiting behaviors depends on different modes of data collection -- including public records requests and "data science" methodologies, such as web-scraping and streaming social media data -- that record actual behaviors (e.g., contracts, transactions, records of expenditure) as opposed to statements by colleges/universities about their behavior.
+
+-->
+
 ```{r, include = FALSE, eval = FALSE}

### 2020-12-18 tables.Rmd
muddling through analyses...
#9 updates to ego graphs

--- 2020-11-10 tables.Rmd
@@
 library(tidyverse)
+library(labelled)
 library(ggplot2)
+library(gridExtra)
 ```
@@
 
-```{r, fig.width=3.5, fig.height=3}
-ego_df <- readRDS('./assets/tables/table_ego_privu.RDS')
-univ_order <- (ego_df %>% arrange(Cluster, Type, as.numeric(Rank), University))$University
+\newpage
 
-plot_characteristic <- function(df, type, characteristics) {
-  sub_df <- df %>% select(University, characteristics) %>%
-    gather(key, value, characteristics) %>%
+```{r, fig.width=3.5, fig.height=3, message=FALSE}
+# ggplot's default color palette
+# library(scales)
+# show_col(hue_pal()(4))
+
+plot_characteristic <- function(df, type, characteristic, label_text, visit_count = FALSE) {
+  if (visit_count) {
+    df <- df %>% mutate(univ_name = str_c(univ_name, ' (N=', total, ')'))
+  }
+
+  ordered_df <- df %>% arrange(desc(cluster), univ_name)
+  univ_order <- ordered_df$univ_name
+  cluster_face <- map_chr(ordered_df$cluster, function(x) if_else(as.numeric(x) %% 2 == 0, 'bold', 'plain'))
+
+  sub_df <- df %>% select(univ_name, all_of(characteristic)) %>%
+    gather(key, value, characteristic) %>%
     mutate(value = parse_number(value))
 
-  # colors <- sub_df$color[order(sub_df$University)]
+  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
+  sub_df$key <- factor(sub_df$key, levels = characteristic)
 
-  sub_df$University <- factor(sub_df$University, levels = rev(univ_order))
-
-  ggplot(sub_df, aes(fill = key, y = value, x = University)) + 
+  ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
     geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
@@
     labs(fill = type) +
+    scale_fill_manual(labels = label_text, values = c('#F8766D', '#7CAE00', '#00BFC4', '#C77CFF')) +
     scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
@@
           axis.ticks.y = element_blank(),
-          # axis.text.y = element_text(color = rep(c('red', 'green', 'blue', 'yellow', 'black'), 5)),
+          axis.text.y = element_text(face = rev(cluster_face)),
           text = element_text(size = 8),
@@
 
-plot_characteristic(ego_df, 'Region', c('Northeast', 'Midwest', 'South', 'West'))
-plot_characteristic(ego_df, 'Religion', c('Catholic', 'Conserv', 'Nonsect', 'Other'))
-plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
-plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
+type_vec <- c('privu', 'pubu', 'pubu_outst', 'all', 'all_pubu_outst')
+
+for (i in 1:length(type_vec)) {
+  ego_df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))
+
+  pdf(file.path('.', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')))
+  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
+  par(mfrow=c(2, 2))
+
+  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE)
+  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
+  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'), c('<10%', '10-25%', '25-50%', '50%+'), visit_count = TRUE)
+  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))
+
+  grid.arrange(a, b, c, d, nrow=2, ncol=2, widths=c(1, 0.92))
+  dev.off()
+
+  # Need to use print() for ggplot inside loop in order for it to appear
+  # https://stackoverflow.com/a/15678596/6373540
+  # print(a)
+  # print(b)
+  # print(c)
+  # print(d)
+}
 ```
 
-# Ego network graph
+```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private high schools visited by private colleges and universities"}
+knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
+```
 
-See Figure \@ref(fig:ego-plot).
-
-```{r ego-plot, fig.align = 'center', out.width = '100%', fig.cap = 'Ego network'}
-knitr::include_graphics('assets/figures/plot_2mode_privu.pdf')
-```
+\begin{center}
+* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
+\end{center}

### 2020-12-18 tables.Rmd
#11 add private HS universe graph

@@
 library(gridExtra)
+```
+
+# Private HS universe
+
+```{r}
+privhs_universe <- readRDS('./data/privhs_universe.RDS')
+
+# Filter for private HS that fits our criteria
+# https://github.com/ksalazar3/recruiting-static-visuals/blob/62b08a202ca7c93433a91d7e72e6c0e93ac6eb5b/sql/update_imported_hs_data.sql#L52-L56
+val_labels(privhs_universe$school_type)
+privhs_universe %>% group_by(year) %>% count()
+
+v_get_val <- Vectorize(function(x) str_to_lower(val_label(privhs_universe$region, x)))
+
+df <- privhs_universe %>%
+  filter(school_type %in% c(1, 2, 5), total_12 > 10) %>% 
+  mutate(
+    region = v_get_val(region),
+    pct_blacklatinxnative = pct_black + pct_hispanic + pct_amerindian + pct_nativehawaii,
+    pct_blacklatinxnative_cat = case_when(
+      pct_blacklatinxnative < 10 ~ 'c1_lt10',
+      pct_blacklatinxnative < 25 ~ 'c2_10to25',
+      pct_blacklatinxnative < 50 ~ 'c3_25to50',
+      pct_blacklatinxnative >= 50 ~ 'c4_50+'
+    ),
+    rank_cat2 = case_when(
+      rank_within_category <= 200 & overall_niche_letter_grade == 'A+' ~ 'c1_top200',
+      rank_within_category > 200 & overall_niche_letter_grade == 'A+' ~ 'c2_A+',
+      overall_niche_letter_grade == 'A' ~ 'c3_A',
+      !is.na(overall_niche_letter_grade) ~ 'c4_ltA'
+    ) 
+  ) %>% 
+  select(total_12, region, religion, pct_blacklatinxnative_cat, rank_cat2)
+
+plot_characteristic <- function(var_name, type, characteristic, label_text) {
+
+  sub_df <- df %>% group_by(get(var_name)) %>% 
+    summarize(unweighted = n(), weighted = sum(total_12)) %>% 
+    pivot_longer(cols = c('unweighted', 'weighted'),
+                 names_to = 'universe',
+                 values_to = 'value')
+  names(sub_df) <- c('key', 'universe', 'value')
+  sub_df <- sub_df %>% filter(!is.na(key))
+
+  sub_df$universe <- factor(sub_df$universe, levels = c('weighted', 'unweighted'))
+  sub_df$key <- factor(sub_df$key, levels = characteristic)
+
+  ggplot(sub_df, aes(fill = key, y = value, x = universe)) + 
+      geom_bar(stat='identity', position = position_fill(reverse = TRUE), width = 0.7) +
+      ggtitle('Title') +
+      xlab('') + ylab('') +
+      labs(fill = type) +
+      scale_fill_manual(labels = label_text, values = c('#F8766D', '#7CAE00', '#00BFC4', '#C77CFF')) +
+      scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
+      theme(legend.position = 'top',
+            legend.title = element_text(size = 6, face = 'bold'),
+            legend.text = element_text(size = 6),
+            legend.margin = margin(0, 0, 0, 0),
+            legend.box.margin = margin(0, 0, -5, -30),
+            legend.key.size = unit(0.3, 'cm'),
+            panel.background = element_blank(),
+            axis.ticks.y = element_blank(),
+            text = element_text(size = 8),
+            plot.title = element_text(color = 'white')) +
+      coord_flip()
+}
+
+pdf(file.path('.', 'assets', 'figures', 'plot_pss_universe.pdf'), width = 8, height = 4)
+par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
+par(mfrow=c(2, 2))
+
+a <- plot_characteristic('region', 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'))
+b <- plot_characteristic('religion', 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
+c <- plot_characteristic('pct_blacklatinxnative_cat', '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'), c('<10%', '10-25%', '25-50%', '50%+'))
+d <- plot_characteristic('rank_cat2', 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))
+
+grid.arrange(a, b, c, d, nrow=2, ncol=2)
+dev.off()
 ```

### 2020-12-18 tables.Rmd
#10 add event count graphs

@@
 library(gridExtra)
+```
+
+# Visit event count
+
+```{r}
+events_data <- read.csv('./data/events_data_2020-07-27.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble()
+univ_info <- read.csv('./data/univ_data.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'zip_code' = 'character')) %>% as_tibble()
+
+df <- events_data %>%
+  select(univ_id, event_loc, event_type) %>% 
+  left_join(univ_info %>% select(univ_id, univ_name), by = 'univ_id') %>% 
+  mutate(event_loc = recode(event_loc, 'instate' = 'in', 'outofstate' = 'out'),
+         event_type = recode(event_type, 'pub_hs' = 'pub', 'priv_hs' = 'priv', 'pub_4yr' = 'other', 'pse' = 'other'),
+         event_cat = str_c(event_type, '_', event_loc),
+         univ_name = recode(univ_name,
+                            'The University of Alabama' = 'University of Alabama',
+                            'Tulane University of Louisiana' = 'Tulane University',
+                            'North Carolina State University at Raleigh' = 'North Carolina State University',
+                            'University of Colorado Boulder' = 'University of Colorado-Boulder',
+                            'University of Cincinnati-Main Campus' = 'University of Cincinnati',
+                            'University of Pittsburgh-Pittsburgh Campus' = 'University of Pittsburgh',
+                            'Sewanee-The University of the South' = 'Sewanee'
+                            )) %>% 
+  select(univ_id, univ_name, event_cat) %>% 
+  group_by(univ_id, univ_name, event_cat) %>% 
+  summarise(count = n()) %>% 
+  pivot_wider(names_from = event_cat, values_from = count, values_fill = list(count = 0)) %>% 
+  mutate(all_in = pub_in + priv_in + cc_in + other_in,
+         all_out = pub_out + priv_out + cc_out + other_out,
+         other_out = cc_out + other_out,
+         all = all_in + all_out) %>% 
+  arrange(univ_name)
+
+pub_df <- df %>% filter(univ_id %in% (univ_info %>% filter(classification == 'public_research'))$univ_id)
+priv_df <- df %>% filter(univ_id %in% (univ_info %>% filter(classification != 'public_research'))$univ_id, univ_id != '168218')
+
+write.csv(pub_df, './data/event_count_pub.csv', row.names = FALSE)
+write.csv(priv_df, './data/event_count_priv.csv', row.names = FALSE)
 ```

### 2020-12-18 manuscript.Rmd
draft changes manuscript

@@
 The motivation for these analyses is grounded within the sociology of higher education, particularly two theoretical and empirical syntheses developed by Mitchell Stevens and colleagues [@RN2377; @RN4517].
-First, @RN2377 introduces metaphors that describe how sociology has conceived the functions of higher education.
+@RN2377 introduces metaphors that describe how sociology has conceived the functions of higher education.
 The stratification tradition conceives of higher education as a "sieve" -- an instrument that strains and separates -- that allocates people to occupational and social positions.
@@
 
-# What Do We Know About Off-campus Recruiting?
+# What Do We Know About Off-Campus Recruiting?
 
-<!-- The "enrollment funnel," shown in Figure X, describes stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students). -->
+<!-- 
+This section provides context for our analyses by, first, situating off-campus visits within the broader set of marketing and recruiting interventions.
+Second, we review what is known about off-campus recruiting from market research and from academic scholarship, emphasizing scholarship that examines the relationship between private high schools and colleges/universities.
+-->
 
-This section provides context for our analyses by, first, situating off-campus recruiting within the broader set of marketing and recruiting interventions.
-Second, we review what is known about off-campus recruiting from market research and from academic scholarship, with a particular focus on scholarship that examines the relationship between private high schools and colleges/universities.
+This section provides context for our analyses.
+First, we situate off-campus recruiting within the broader set of marketing and recruiting interventions in higher education and review what market research says about off-campus recruiting.
+Second, we review empirical scholarship from sociology that considers off-campus recruiting, emphasizing scholarship that considers the relational aspects of recruiting visits and scholarship that considers private high schools.
 
-Figure \@ref(fig:em-funnel) shows the "enrollment funnel," a conceptual heurisitc used by the enrollment management industry, which describe the stages in the student recruitment process (e.g., prospects, inquiries, applicants, accepted applicants, and enrolled students).
-For example, “prospects” are “all the potential students you would want to attract to your institution” [@RN4322].
+## Situating Off-Campus Recruiting Within Enrollment Management
+
+The "enrollment funnel" -- depicted in Figure \@ref(fig:em-funnel) -- is a conceptual heuristic that identifies stages in the student recruitment process (prospects, inquiries, applicants, accepted applicants, and enrolled students).
+“Prospects” are “all the potential students you would want to attract to your institution” [@RN4322].
 “Inquiries” are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own.
-The enrollment management industry uses the enrollment funnel to inform interventions that target specific stages of the funnel.
+The enrollment management industry uses the enrollment funnel to inform marketing and recruiting interventions that target specific stages.
+Most scholarship on enrollment management focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [e.g., @RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948].
+By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664].
+[SHOULD WE TRY TO ADD SOME CONCRETE NUMBERS ON $ SPENDING AT PARTICULAR UNIVERSITIES?]
 
-Table X, reproduced from @RN4664, shows the the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.
-^[table drawn directly from @RN4664 figure 9; based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions].
-Institutions identify undergradaute prospects largely by purchasing "student lists" from College Board, ACT, and other vendors.
+Institutions identify undergraduate "prospects" by purchasing "student lists" -- containing contact, demographic, and academic achievement information -- from College Board, ACT, and other vendors.
+Universities control which prospects contained within a list by filtering on criteria such as zip code, test scores, and high school GPA.
+Once prospects and inquiries are identified, they are targeted with remote and face-to-face recruiting interventions designed to solicit applications and deepen engagement.
+Remote recruiting interventions include postcards, brochures, email, text messages, and targeted social media.
+Face-to-face recruiting interventions include on-campus visits by prospects and off-campus recruiting visits by admissions representatives to high schools, community colleges, college fairs, etc.
 Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411][CITE OTHER].
 Given the the rise in “stealth applicants” who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.
-Once prospects and inquiries are identified, they are targeted with face-to-face and remote recruiting interventions designed to solit applications and deepen engagement.
-Face-to-face recruiting interventions include on-campus visits by prospects and off-campus recruiting visits by admissions representatives to high schools, community colleges, college fairs, etc.
-Remote recruiting interventions include postcards, brochures, email, text messages, and targeted social media.
+
+What do we know about off-campus recruiting from previous research?
+As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practioner-oriented publications.
+Market research describes off-campus recruiting visits as a means of identifying prospects and deepening engagement with prospects already being targeted through mail/email [@RN4323; @RN4402; @RN4664].
+
+@RN4402 documents the self-reported efficacy of marketing/recruiting interventions.
+For the median private 4-yr institution, off-campus visits were the second highest source of inquiries (after student list purchases), accounting for 17% of inquiries.
+Off-campus visits were tied with student list purchases as the highest source of enrollees, accounting for 18% of enrollees.
+For the median public institution, off-campus visits accounted for 19% of inquiries (second only to student list purchases) and accounted for 16% of enrollees (ranked third after stealth applicants and on-campus visits).
+
+With respect to expenditure, Table \@ref(tab:ug-recruit-budget), reproduced from @RN4664, shows the the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.
+^[table drawn directly from @RN4664 Figure 9; based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions].
+The average public university spent 16% of its recruiting budget on off-campus recruiting visits, compared to 12% of its budget on purchasing student lists and 17% of its budget on "prospective student communications" (e.g., mail, email, text, social media) targeting prospects and inquiries.
+An emergent trend over the past decade -- partially a response to public universities seeking nonresident students -- has been the growth of "regional recruiters" who target specific metropolitan areas in the US and abroad [@RN4021].
+These regional recruiters may be college/university employees or they may be independent contractors who live in the metropolitan area they recruit.
+
 <!-- QUESTIONS ABOUT THE RNL 2020 COST OF RECRUITING AN UNDERGRADUATE STUDENT REPORT, FIGURE 9
@@
 
-What do we know about off-campus recruiting from previous research?
-As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practioner-oriented publications.
-Market research conceives of off-campus recruiting visits as a means of identifying prospects, deepening engagement with prospects already being targeted through mail/email, and maintaining relationships with guidance counselors at “feeder schools” [@RN4323; @RN4402; @RN4664].
-With respect to expenditure, @RN4664 found that private (non-profit) 4-yr institutions spent an average of 17% of their undergraduate marketing/recruiting budget on "travel" to high schools and college fairs (as shown in Table X), a higher percentage of budget allocation than any other marketing/recruiting activity.
-Public institutions spent an average of 16% of their budget on travel, second only to "prospective student communications" at 17%.
-An emergent trend over the past decade -- partially a response to public universities seeking nonresident students -- has been the growth of "regional recruiters" who target specific metropolitan areas in the US and abroad.
-These regional recruiters may be college/university employees or they may be independent contractors who live in the metropolitan area they recruit.
+## Empirical Scholarship from Sociology
 
-@RN4402 documents the self-reported efficacy of marketing/recruiting interventions.
-For the median private 4-yr institution, off-campus visits were the second highest source of inquiries (after student list purchases), accounting for 17% of inquiries.
-Off-campus visits were tied with student list purchases as the highest source of enrollees, accounting for 18% of enrollees.
-For the median public institution, off-campus visits accounted for 19% of inquiries (second only to student list purchases) and accounted for 16% of enrollees (ranked third after stealth applicants and on-campus visits).
+<!-- QUESTIONS ABOUT THE RNL 2020 COST OF RECRUITING AN UNDERGRADUATE STUDENT REPORT, FIGURE 9
 
-A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits.
+A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits [CITE].
+
+-->
+
+Empirical academic scholarship on off-campus recruiting is mostly limited to a modest number of sociological case studies, which typically analyze off-campus recruiting as part of a broader analysis of enrollment management [e.g., @RN4324; @RN3519; @RN4538; @RN4520; @RN4407].
 @RN4324 analyzes visits from the perspective of students at two racially and socioeconomically diverse public high schools.
 @RN4324 found that high school visits -- including college fairs, instant decision events, and small-group representative visits -- influenced where students applied and where they enrolled.
-This finding was strongest for first-generation students and under-represented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college." This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and "made them feel wanted."  @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more." By contrast, affluent students with college educated parents were less taken by such overtures and more concerned with college prestige.
+This finding was strongest for first-generation students and under-represented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college" (p.
+XXX) This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and made them feel wanted.
+For example, @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more" (p.
+XXX).
+By contrast, affluent students with college educated parents were less taken by such overtures and more concerned with college prestige.
 
-Of particular importance for this chapter, @RN3519 and @RN4321;@RN4407 highlight the relational function of visits.
-@RN3519 provides an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of visits.
-During the autumn "travel season," admissions officers visited selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
-53-54) because "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide" {@RN3519} [p.
-54].
-The College tended to visit the same schools year after year because recruiting depends on long-term relationships with high schools.
+@RN3519 and Khan [-@RN4321;-@RN4407] are centrally important to our study because they analyze relationships between college admissions counselors and high school guidance counselors.
+@RN3519, an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of visits.
+Stevens [-@RN3519, p.
+54] states that "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide." Therefore, during the autumn "travel season," admissions officers visit selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
+53-54).
+The College tended to visit the same "feeder" schools year after year because recruiting depends on long-term relationships with high schools.
 The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and had the resources and motivation to host a successful visit.
@@
 
-@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities." The answer to this question begins by thinking about the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors.
+@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p.
+98).
+The answer begins by considering the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors.
 Colleges want high achieving students who can pay tuition and donate.
-Additionally, drawing from @@RN3519, colleges want a class composed of "interesting characters" whose curricular and extracurricular strengths meet the needs of different campus constituents (e.g., academic majors, the athletic department, clubs, etc.).
-Colleges also want low acceptance and high yield rates to move up the rankings.
+They want low acceptance and high yield rates, which are important for rankings.
+Colleges also want a class composed of "interesting characters" whose curricular and extracurricular strengths meet the needs of important campus constituents (e.g., academic majors, the athletic department, clubs, etc.).
 Private high schools want to send _all_ students to the best college possible.
-Here, high school guidance counselors face "the pressure of making sure their school seems worth it – that...paying some $40,000+, really does aid students in the college process" [FROM CHAPTER.
-FIND PG NUMBER]  The challenge counselors face is "some of these students are slightly better than others.
+Here, high school guidance counselors face "the pressure of making sure their school seems worth it – that \ldots paying some $40,000+, really does aid students in the college process" [@RN4321, p.
+105].
+
+The challenge faced by high school counselors at elite private schools is that "some of these students are slightly better than others.
 These students will likely get into more than one school -- but they can only attend one.
-And this will lower the chances of your "second-best" students getting into top schools" [@RN4407] [p.
+And this will lower the chances of your 'second-best' students getting into top schools" [@RN4407, pp.
 173-174].
+"Luckily," Khan [-@RN4321, p.
+105] writes, "the problem for elite boarding schools matches up quite nicely with the problem faced by elite colleges." That is, although college admissions officers receive applications from many outstanding students,
 
-"Luckily," @RN4321 [pg.
-xx] writes, "the problem for elite boarding schools matches up quite nicely with the problem faced by elite colleges." Specifically, college admissions officers receive applications from many outstanding students.
-But "These outstanding students will also be outstanding to Princeton, Yale, Stanford, and everywhere else.
+> These outstanding students will also be  outstanding to Princeton, Yale, Stanford, and everywhere else.
 How do you know the ones you pick will attend your school?
-you can't quite trust applicants, as they are all likely to tell you how much they want to go to your school.
+You can't quite trust applicants, as they are all likely to tell you how much they want to go to your school.
 And if students you accept go somewhere else, there's not much you can do.
-But you can get better information -- information you want -- from their high school" [@RN4407] [pg.
-173?].
+But you can get better information -- information you want -- from their high school.
+And you can reward that school for good information and sanction it for bad information [@RN4407, p.
+173].
 
-@RN4407 argues that the desire by colleges for trustworthy information about applicant intentions creates an opportunity for high school counselors to advocate on behalf of their students.
+<!--
+
+ And you can reward that school for good information and sanction it for bad information [@RN4407, p. 173].
+
+-->
+
+This desire by colleges for trustworthy information about applicant intentions creates an opportunity for high school counselors to advocate on behalf of their students.
 This opportunity depends on guidance counselors having personal relationships with university admissions offices and on having small enough caseloads to advocate for each student individually.
-To explain how the process works, @RN4407 describes two hypothetical students -- Susan and Billy -- who both apply to Harvard and Yale.
+
+To explain how high school counselors capitalize on this opportunity, @RN4407 describes two hypothetical students -- Susan and Billy -- who both apply to Harvard and Yale.
 Susan is a shoo-in at both universities, but wants to attend Harvard.
@@
 Next, he informs Yale that Susan will choose Harvard, but Billy loves Yale and has great "character" and extracurricular activities.
-In the end, Harvard rejects Billy and accepts Susan (decreasing acceptance rate, increasing yield).
-Yale rejects Susan and accepts Billy (decreasing acceptance rate, increasing yield).
+In the end, Harvard rejects Billy and accepts Susan, thereby, decreasing acceptance rate and increasing yield.
+Yale rejects Susan and accepts Billy, thereby, decreasing acceptance rate and increasing yield.
 
@@
 This relationship is the product of repeated interactions over many years.
-@RN4407 writes that colleges "can reward that [high] school for good information and sanction it for bad information" [p.
-173].
 A high school that makes false statements about applicant intentions faces consequences.
 The college "might stop taking these telephone calls and ignore the information provided.
-They may even start accepting fewer students from the school, thinking it is less than an honest place." [CITE BOOK CHAPTER; PG NUMBER].
-Because the college and the high school are mutually dependent, however, both "have an incentive to continue with a strong, honest relationship" [CITE BOOK CHAPTER; PG NUMBER].
-Such horsetrading may be less pervasive than now than it was in prior decades, less common at non-elite private schools, and also public university admissions officers likely have less authority to engage in these tacit negotiations.
+They may even start accepting fewer students from the school, thinking it is less than an honest" [@RN4321, p.
+106].
+Because the college and the high school are mutually dependent, however, both "have an incentive to continue with a strong, honest relationship" [@RN4321, p.
+106].
+However, such horsetrading may be less pervasive than now than it was in prior decades and may be less common at non-elite private schools.
+Additionally, college admissions officer from public universities likely have less authority to engage in these tacit negotiations because admissions criteria at public universities face greater public scrutiny than admissions criteria at private colleges and universities.
 
-Nevertheless, maintaining a strong relationships is mutually important for the college and the high school.
-Both the college admissions counselor and the high school guidance counselor need to tell one another "their story" and relay that story to constituents.
+Even in the absence of horsetrading, maintaining strong relationships is mutually important for the college and for the high school.
+The college admissions counselor and the high school guidance counselor need to tell one another "their story" and relay that story to constituents [@RN3519].
 The college admissions counselor explains why the college/university is a "special place" that high school students should want to attend.
 The guidance counselor explains why the high school is a special place, that even students with lower grades have outstanding extracurricular strengths that will benefit the college.
-[CITES FOR THIS PARAGRAPH]
 
-Circling back to the focus of this chapter, off-campus recruiting visits are necessary for the maintenance of strong relationships that enable colleges and high schools to negotiate and send trustworthy information to one another.
-Without face-to-face visits, it is less likely that that a college admissions counselor will "take the call" of a guidance counselor.
-Simultaneously, a recruiting visit between a college and a high school can be conceived as an indicator.
-First, the fact that the college took time and effort to make the visit suggests that the college wants to enroll students from the high school.
+To summarize, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
+Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another and in the absence of strong relationships it is less likely that that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
+Building on these findings, we reason that the presence of a recruiting visit between a college and a high school is an indicator that the college and the high school have a relationship.
+First, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school.
 Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
-Third, the presence of the recruiting visit indicates that the high school and the college have a relationship and suggests the probability of additional interactions (e.g., phone calls).
+Third, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls).
 
@@
 -->
-
-[PARAGRAPH ABOUT TABLE THAT DESCRIBES CHARACTERISTICS OF VISITED VS. NON-VISITED PRIVATE SCHOOLS]
-Before proceeding to network analyses, Table/Figure X compares the characteristics of private high schools that received at least one recruiting visit from a college/university in our sample to those of private high schools that did not receive a visit.
-WHICH CHARACTERISTICS TO SHOW: geographic region; religious affiliation; academic reputation; racial composition; enrollment size.
 
@@
 Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
+
+[PARAGRAPH ABOUT TABLE THAT DESCRIBES CHARACTERISTICS OF VISITED VS. NON-VISITED PRIVATE SCHOOLS]
+Before proceeding to network analyses, Table/Figure X compares the characteristics of private high schools that received at least one recruiting visit from a college/university in our sample to those of private high schools that did not receive a visit.
+WHICH CHARACTERISTICS TO SHOW: geographic region; religious affiliation; academic reputation; racial composition; enrollment size.
 
@@
 Each of these marketing/recruiting interventions -- and dozens of other interventions described in this book -- represent organizational behaviors that could be the subject of empirical research.
-However, the vast majority of research on enrollment management behaviors focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [E.G.] [@RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948]
 
-.
-By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664] [GIVE SOME CONCRETE BUDGET NUMBERS INDICATING BALL PARK SPENDING?].
 When we consider descriptions of enrollment management practice from investigative journalism [e.g., ], from enrollment management consulting firms and from this volume [e.g., ], it becomes apparent that -- with the notable exception of a small sociological case-study literature [e.g., ] -- the research community has ignores a great number of enrollment management practices that plausibly affect access to higher education.

### 2020-12-18 tables.Rmd
#11 add bars for visited private HS characteristics

@@
 privhs_universe <- readRDS('./data/privhs_universe.RDS')
+privhs_visited <- readRDS('./data/privhs_visited.RDS')
 
@@
 
-df <- privhs_universe %>%
-  filter(school_type %in% c(1, 2, 5), total_12 > 10) %>% 
+universe_df <- privhs_universe %>% 
   mutate(
@@
     ) 
-  ) %>% 
-  select(total_12, region, religion, pct_blacklatinxnative_cat, rank_cat2)
+  )
+
+visited_df <- universe_df %>% filter(ncessch %in% privhs_visited$school_id)
+universe_df <- universe_df %>% filter(school_type %in% c(1, 2, 5), total_12 > 10)
 
@@
 
-  sub_df <- df %>% group_by(get(var_name)) %>% 
-    summarize(unweighted = n(), weighted = sum(total_12)) %>% 
-    pivot_longer(cols = c('unweighted', 'weighted'),
+  sub_df_visited <- visited_df %>% group_by(get(var_name)) %>% 
+    summarize(`visited (unweighted)` = n(), `visited (weighted)` = sum(total_12, na.rm = TRUE)) %>% 
+    pivot_longer(cols = c('visited (unweighted)', 'visited (weighted)'),
+                 names_to = 'universe',
+                 values_to = 'value')
+  names(sub_df_visited) <- c('key', 'universe', 'value')
+
+  sub_df <- universe_df %>% group_by(get(var_name)) %>% 
+    summarize(`universe (unweighted)` = n(), `universe (weighted)` = sum(total_12)) %>% 
+    pivot_longer(cols = c('universe (unweighted)', 'universe (weighted)'),
                  names_to = 'universe',
@@
   names(sub_df) <- c('key', 'universe', 'value')
+
+  sub_df <- dplyr::union(sub_df, sub_df_visited)
   sub_df <- sub_df %>% filter(!is.na(key))
 
-  sub_df$universe <- factor(sub_df$universe, levels = c('weighted', 'unweighted'))
+  sub_df$universe <- factor(sub_df$universe, levels = c('visited (weighted)', 'visited (unweighted)', 'universe (weighted)', 'universe (unweighted)'))
   sub_df$key <- factor(sub_df$key, levels = characteristic)
@@
       scale_fill_manual(labels = label_text, values = c('#F8766D', '#7CAE00', '#00BFC4', '#C77CFF')) +
+      scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) +
       scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
@@
 
-pdf(file.path('.', 'assets', 'figures', 'plot_pss_universe.pdf'), width = 8, height = 4)
+pdf(file.path('.', 'assets', 'figures', 'plot_pss_universe.pdf'))
 par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))

### 2020-12-18 scripts/create_igraph_objects.R

@@ -197,6 +197,9 @@ attributes_df <- attributes_df %>% mutate(
 View(attributes_df %>% filter(school_id %in% univ_vec))
 View(attributes_df %>% filter(school_id %in% privhs_vec))
 
+# Export universe of private HS
+saveRDS(attributes_df %>% filter(school_id %in% privhs_vec), file = str_c('./data/privhs_visited.RDS'))
+
 
 ## -------------------
 ## AFFILIATION MATRIX

### 2020-12-18 manuscript.Rmd
add figures to manuscript

@@
       - \usepackage{geometry}
+      - \usepackage{floatrow}
+      - \floatsetup{capposition=top}
 ---
@@
 
-Tables/Figures X and X show simple counts and descriptive staitistics of off-campus recruiting visits by colleges and universities in our sample.
+Figures \@ref(fig:event-count-figure-privu) and \@ref(fig:event-count-figure-pubu) show simple counts and descriptive statistics of off-campus recruiting visits by colleges and universities in our sample.
 TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES....
@@
 
-```{r, echo=FALSE}
+```{r ug-recruit-budget, echo=FALSE}
 pct_budget <- data.frame(
@@
 
-```{r, hs-print-privu, echo = FALSE}
+```{r hs-print-privu, echo = FALSE}
 df <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20)
@@
 knitr::kable(
-  df %>% select(-name,-closeness), caption = 'The 20 most central private high schools with respect to visits from private colleges and universities') %>% 
+  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by private institutions') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r, hs-table-privu-agg, echo = FALSE}
+```{r hs-table-privu-agg, echo = FALSE}
 df <- readRDS('./assets/tables/table_2mode_agg_privu.RDS')
 
-knitr::kable(df, caption = 'characteristics of high schools by degree band, private colleges and universities') %>% 
+knitr::kable(df, caption = 'Characteristics of private HS visited by private institutions, by degree band') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r, hs-print-pubu, echo = FALSE}
+```{r hs-print-pubu, echo = FALSE}
 df <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)
@@
 knitr::kable(
-  df %>% select(-name,-closeness), caption = 'The 20 most central private high schools with respect to visits from public research universities') %>% 
+  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by public institutions') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r, hs-table-pubu-agg, echo = FALSE}
+```{r hs-table-pubu-agg, echo = FALSE}
 df <- readRDS('./assets/tables/table_2mode_agg_pubu.RDS')
 
-knitr::kable(df, caption = 'characteristics of high schools by degree band, public research universities') %>% 
+knitr::kable(df, caption = 'Characteristics of private HS visited by public institutions, by degree band') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r, hs-print-both, echo = FALSE}
+```{r hs-print-both, echo = FALSE}
 df <- readRDS('./assets/tables/table_2mode_both.RDS') %>% head(n=20)
@@
 knitr::kable(
-  df %>% select(-name,-closeness), caption = 'most central private high schools, public and private colleges and universities') %>% 
+  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by all institutions') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r, hs-table-both-agg, echo = FALSE}
+```{r hs-table-both-agg, echo = FALSE}
 df <- readRDS('./assets/tables/table_2mode_agg_both.RDS')
 
-knitr::kable(df, caption = 'characteristics of high schools by degree band, public and private colleges and universities') %>% 
+knitr::kable(df, caption = 'Characteristics of private HS visited by all institutions, by degree band') %>% 
   landscape(margin = NULL) %>%
@@
 
-```{r em-funnel, echo = FALSE, fig.cap = "The enrollment funnel"}
+```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%"}
 knitr::include_graphics('assets/images/enrollment_funnel.png')
@@
 
+```{r event-count-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for private institutions"}
+knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
+```
+
+```{r event-count-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for public institutions"}
+knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
+```
+
 \newpage
 
-\newgeometry{margin=0cm}
+```{r privhs-universe, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
+knitr::include_graphics('assets/figures/plot_pss_universe.pdf')
+```
+
+\begin{center}
+* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12 students and is not a special education school, an alternative school, an early childhood center, or an independent school.}
+\end{center}
+
+\newpage
+
+\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
 
@@
 
-```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption of 2 mode graph"}
+```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
 knitr::include_graphics('assets/figures/plot_2mode_all_region.pdf')
@@
 
-```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-privu"}
+```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for private institutions, colored by cluster"}
 knitr::include_graphics('assets/figures/plot_1mode_privu.pdf')
@@
 ```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
-#df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS')))
-#df %>% glimpse()
+# ggplot's default color palette
+# library(scales)
+# show_col(hue_pal()(4))
 
-plot_characteristic <- function(df, type, characteristic) {
-  sub_df <- df %>% select(univ_name, characteristic) %>%
+plot_characteristic <- function(df, type, characteristic, label_text, visit_count = FALSE) {
+  if (visit_count) {
+    df <- df %>% mutate(univ_name = str_c(univ_name, ' (N=', total, ')'))
+  }
+
+  ordered_df <- df %>% arrange(desc(cluster), univ_name)
+  univ_order <- ordered_df$univ_name
+  cluster_face <- map_chr(ordered_df$cluster, function(x) if_else(as.numeric(x) %% 2 == 0, 'bold', 'plain'))
+
+  sub_df <- df %>% select(univ_name, all_of(characteristic)) %>%
     gather(key, value, characteristic) %>%
@@
 
-  # colors <- sub_df$color[order(sub_df$University)]
-  univ_order <- (df %>% arrange(desc(cluster), univ_name))$univ_name
-  #univ_order <- (df %>% arrange(desc(Cluster), Type, as.numeric(Rank), University))$University
   sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
-  #sub_df$univ_name
+  sub_df$key <- factor(sub_df$key, levels = characteristic)
 
@@
 
-type_vec <- c('privu', 'pubu', 'pubu_outst', 'all','all_pubu_outst')
+type_vec <- c('privu', 'pubu', 'pubu_outst', 'all', 'all_pubu_outst')
 
@@
 
-  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'))
-  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'nonsectarian', 'other'))
-  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'))
-  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'))
+  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE)
+  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
+  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'), c('<10%', '10-25%', '25-50%', '50%+'), visit_count = TRUE)
+  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))
 
-  grid.arrange(a, b, c, d, nrow=2, ncol=2)
+  grid.arrange(a, b, c, d, nrow=2, ncol=2, widths=c(1, 0.92))
   dev.off()
@@
   # https://stackoverflow.com/a/15678596/6373540
-  #print(a)
-  #print(b)
-  #print(c)
-  #print(d)
+  # print(a)
+  # print(b)
+  # print(c)
+  # print(d)
 }
@@
 
-\newgeometry{margin=0cm}
+\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
 
@@
 
-```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by private colleges and universities"}
+```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
 knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
 ```
+
+\begin{center}
+* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
+\end{center}
 
@@
 
-```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, with religious affiliation"}
+```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}
 knitr::include_graphics('assets/figures/villanova_religion.pdf')
@@
 
-```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, with geographic region"}
+```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, colored by geographic region"}
 knitr::include_graphics('assets/figures/emory_region.pdf')
@@
 
-```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu"}
+```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions, colored by cluster"}
 knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
@@
 
-```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-pubu out-of-state visits only", eval = FALSE}
+```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions and out-of-state visits only, colored by cluster", eval = FALSE}
 knitr::include_graphics('assets/figures/plot_1mode_pubu_outst.pdf')
@@
 
-```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by public research universities"}
+```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by public institutions"}
 knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
@@
 
+\begin{center}
+* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
+\end{center}
+
 \begin{landscape}
 
-```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all", include= FALSE, eval = FALSE}
+```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, colored by cluster", include= FALSE, eval = FALSE}
 knitr::include_graphics('assets/figures/plot_1mode_all.pdf')
@@
 
-```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "caption plot-1mode-all, out-of-state visits only for public universities"}
+```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster"}
 knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
@@
 
-```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "characteristics of private high schools visited by public and private colleges and universities, out-of-state visits only for public universities"}
+```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by all institutions, out-of-state visits only for public universities"}
 knitr::include_graphics('assets/figures/ego_network_figure_all_pubu_outst.pdf')
@@
 ```
+
+\begin{center}
+* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
+\end{center}

### 2020-12-19 manuscript.Rmd
copy-edit sections 1 & 2

@@
 
-These metaphors are useful for comparing the comparing public flagship universities to selective private colleges and universities.
-Selective private colleges and universities depend on patronage from affluent households (market configuration) and philanthropic interests (associational configuration) and primarily serve social reproduction rather than social mobility.
+These metaphors are useful for comparing public flagship universities to selective private colleges and universities.
+Selective private colleges and universities depend on patronage from affluent households (market configuration) and philanthropic interests (association configuration) and primarily serve social reproduction rather than social mobility.
 Historically, public flagship universities depended on government funding associated with the national service configuration and served social mobility rather than reproduction.
@@
 However, access to concrete data on university recruiting behaviors has been a persistent barrier to empirical research.
-We collected data about off-campus recruiting visits made in 2017 by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for a sample of public research universities -- by issuing public records requests.
+We collected data on off-campus recruiting visits made in 2017 by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for a sample of public research universities -- by issuing public records requests.
 The first study from this data collection analyzed visits made by 15 public research universities [@RN4450].
 The overwhelming majority of public research universities in our sample made more out-of-state visits than in-state visits, a finding antithetical to historic mission of public universities.
-These out-of-state visits focused on wealthy, predominantly white schools and communities, with a disproportionate number visits to out-of-state private high schools but relatively few visits to in-state private high schools.
-
-Building on [@RN4450], this chapter analyzes off-campus recruiting visits to private high schools made in 2017 by a sample of 25 selective private colleges and universities and 17 public research universities.
+These out-of-state visits focused on wealthy, predominantly white schools and communities, with a disproportionate number of visits to out-of-state private high schools but relatively few visits to in-state private high schools.
+
+Building on @RN4450, this chapter analyzes off-campus recruiting visits to private high schools made in 2017 by a sample of 25 selective private colleges and universities and 17 public research universities.
 We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
@@
 First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what do extent colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+Second, to what extent do colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
 
@@
 
-Our decision to analyze visits to private schools is motivated by the idea that recruiting from private schools largely serves social reproduction [CITE A SOCIOLOGIST].
-Thus, visits to private school are antithetical to the historic "social mobility mission" of public universities [@RN2269], particularly since most private school visits by public research universities are to out-of-state schools [@RN4450].
+Our decision to analyze visits to private schools is motivated by the idea that recruiting from private schools largely serves social reproduction<!-- [CITE A SOCIOLOGIST]-->.
+Thus, visits to private schools are antithetical to the historic "social mobility mission" of public universities [@RN2269], particularly since most private school visits by public research universities are to out-of-state schools [@RN4450].
 By contrast, recruiting from private high schools is consistent with the missions of selective private colleges and universities.
@@
 Finally, although private school students are more likely than public school students to come from affluent, college-educated households, the population of US private schools contains tremendous variation in religious affiliation, academic reputation, racial and socioeconomic composition, amongst other dimensions [@RN4504].
-Therefore, focusing solely on visits to private schools enables us to develop a nuanced analysis of which types of private high schools receive visits from which types colleges and universities.
-These nuances would be dificult to observe in an analysis that also included visits to public high schools.
+Therefore, focusing solely on visits to private schools enables us to develop a nuanced analysis of which types of private high schools receive visits from which types of colleges and universities.
+These nuances would be difficult to observe in an analysis that also included visits to public high schools.
 
@@
 The "enrollment funnel" -- depicted in Figure \@ref(fig:em-funnel) -- is a conceptual heuristic that identifies stages in the student recruitment process (prospects, inquiries, applicants, accepted applicants, and enrolled students).
-“Prospects” are “all the potential students you would want to attract to your institution” [@RN4322].
-“Inquiries” are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own.
+"Prospects" are "all the potential students you would want to attract to your institution" [@RN4322].
+"Inquiries" are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own.
 The enrollment management industry uses the enrollment funnel to inform marketing and recruiting interventions that target specific stages.
@@
 By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664].
-[SHOULD WE TRY TO ADD SOME CONCRETE NUMBERS ON $ SPENDING AT PARTICULAR UNIVERSITIES?]
+<!--[SHOULD WE TRY TO ADD SOME CONCRETE NUMBERS ON $ SPENDING AT PARTICULAR UNIVERSITIES?]-->
 
 Institutions identify undergraduate "prospects" by purchasing "student lists" -- containing contact, demographic, and academic achievement information -- from College Board, ACT, and other vendors.
-Universities control which prospects contained within a list by filtering on criteria such as zip code, test scores, and high school GPA.
+Universities control which prospects are contained within a list by filtering on criteria such as zip code, test scores, and high school GPA.
 Once prospects and inquiries are identified, they are targeted with remote and face-to-face recruiting interventions designed to solicit applications and deepen engagement.
-Remote recruiting interventions include postcards, brochures, email, text messages, and targeted social media.
+Remote recruiting interventions include postcards, brochures, emails, text messages, and targeted social media.
 Face-to-face recruiting interventions include on-campus visits by prospects and off-campus recruiting visits by admissions representatives to high schools, community colleges, college fairs, etc.
-Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411][CITE OTHER].
-Given the the rise in “stealth applicants” who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.
+Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411]<!--[CITE OTHER]-->.
+Given the the rise in "stealth applicants" who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.
 
 What do we know about off-campus recruiting from previous research?
-As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practioner-oriented publications.
+As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practitioner-oriented publications.
 Market research describes off-campus recruiting visits as a means of identifying prospects and deepening engagement with prospects already being targeted through mail/email [@RN4323; @RN4402; @RN4664].
@@
 
-With respect to expenditure, Table \@ref(tab:ug-recruit-budget), reproduced from @RN4664, shows the the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.
-^[table drawn directly from @RN4664 Figure 9; based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions].
-The average public university spent 16% of its recruiting budget on off-campus recruiting visits, compared to 12% of its budget on purchasing student lists and 17% of its budget on "prospective student communications" (e.g., mail, email, text, social media) targeting prospects and inquiries.
+With respect to expenditure, Table \@ref(tab:ug-recruit-budget), reproduced from @RN4664, shows the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.^[Table drawn directly from @RN4664 Figure 9, which is based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions.] The average public university spent 16% of its recruiting budget on off-campus recruiting visits, compared to 12% of its budget on purchasing student lists and 17% of its budget on "prospective student communications" (e.g., mail, email, text, social media) targeting prospects and inquiries.
 An emergent trend over the past decade -- partially a response to public universities seeking nonresident students -- has been the growth of "regional recruiters" who target specific metropolitan areas in the US and abroad [@RN4021].
@@
 The answer begins by considering the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors.
-Colleges want high achieving students who can pay tuition and donate.
+Colleges want high-achieving students who can pay tuition and donate.
 They want low acceptance and high yield rates, which are important for rankings.
@@
 In the end, Harvard rejects Billy and accepts Susan, thereby, decreasing acceptance rate and increasing yield.
-Yale rejects Susan and accepts Billy, thereby, decreasing acceptance rate and increasing yield.
+Yale rejects Susan and accepts Billy, thereby, also decreasing acceptance rate and increasing yield.
 
@@
 106].
-However, such horsetrading may be less pervasive than now than it was in prior decades and may be less common at non-elite private schools.
-Additionally, college admissions officer from public universities likely have less authority to engage in these tacit negotiations because admissions criteria at public universities face greater public scrutiny than admissions criteria at private colleges and universities.
+Although, such horsetrading may be less pervasive now than it was in prior decades and may be less common at non-elite private schools.
+Additionally, college admissions officers from public universities likely have less authority to engage in these tacit negotiations because admissions criteria at public universities face greater public scrutiny than admissions criteria at private colleges and universities.
 
@@
 To summarize, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
-Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another and in the absence of strong relationships it is less likely that that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
+Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another.
+In the absence of strong relationships, it is less likely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
 Building on these findings, we reason that the presence of a recruiting visit between a college and a high school is an indicator that the college and the high school have a relationship.
@@
 
-Our project collected data about off-campus recruiting visits made in 2017 by a convenience sample of colleges universities.
-Our analysis sample is based on three different lists of postsecondary institutions: first, the set of public research universities (which category) as defined by the YYYY Carnegie Classification; second, private universities in the top 100 of USNWR YYYY "national universities"; and, third, private colleges in the top 50 of USNWR YYYY "national liberal arts colleges" rankings.
+Our project collected data on off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities.
+Our analysis sample is based on three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S.
+News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S.
+News and World Report Liberal Arts Colleges rankings (N=47).
 For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits.
@@
 These institutions are excluded from the analyses.
-Our final analysis sample consists of X public research universities, X private research universities, and X private liberal arts colleges.
-[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]
-
-Our analyses to date have focused only on visits by public research universities [CITE].
+Our final analysis sample consists of 17 public research universities, 13 private research universities, and 12 private liberal arts colleges.
+<!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->
+
+Our analyses to date have focused only on visits by public research universities<!--[CITE]-->.
 The big-picture takeaways are as follows.
 Most public research universities in our sample made more out-of-state than in-state recruiting visits.
-The exceptions were UC-Berkeley, UC-Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps.
-Accross all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropoitan areas.
+The exceptions were UC Berkeley, UC Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps.
+Across all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropolitan areas.
 Most public universities also made a disproportionate number of out-of-state visits to private high schools.
-Analyses of in-state visits also found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools.
+In addition, analyses of in-state visits found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools.
 Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.
 
-Figures \@ref(fig:event-count-figure-privu) and \@ref(fig:event-count-figure-pubu) show simple counts and descriptive statistics of off-campus recruiting visits by colleges and universities in our sample.
-TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES....
-Table/Figure X demonstrates the disproportionate number of visits to private high schools.
+Figures \@ref(fig:event-count-figure-pubu) and \@ref(fig:event-count-figure-privu) show the number of off-campus recruiting visits by public and private colleges and universities in our sample, separated by event type and in-state vs.
+out-of-state.
+<!--TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES....
+-->Table/Figure X demonstrates the disproportionate number of visits to private high schools.
 The goal of this chapter is to investigate off-campus recruiting visits to private high schools.
 Which types of private high schools receive visits from which types of colleges and universities?
-Additionally, to what extent were visits a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics?
+Additionally, to what extent were visits by a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics?
 Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition.
+
+<!--
 WHAT TO SHOW IN TABLES/FIGURES:
-<!--
 - Table/figure of number of visits by visit type and in/out-of-state
@@
 [HOW DOES RACIAL COMPOSITION OF VISITED PRIVATE HIGH SCHOOLS COMPARE TO RACIAL COMPOSITION OF ALL PRIVATE HIGH SCHOOLS?
-CUT/REVISE TEXT DEPENDING ON ANSWER TO THIS QUESTION] Private high schools tend to have a higher share of White students than public high schools.
+CUT/REVISE TEXT DEPENDING ON ANSWER TO THIS QUESTION] See Figure \@ref(fig:privhs-universe).
+Private high schools tend to have a higher share of White students than public high schools.
 Moreover, the private high schools that were visited by private colleges and universities in our sample had a lower share of Black/Latinx/Native students, on average, than the population of private high schools.

### 2020-12-19 manuscript.Rmd
copy-edit section 3

@@
 First, social network analysis privileges the relationship between actors.
-The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407] [pg.
+The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
 175].
@@
 A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "edges" between these actors.
-Whereas "one mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two mode" networks consit of vertices associated with one type of actor/entity having connections to vertices of another type.
-For example, an an actor-movie network consists of actors -- mode 1 -- who appear in movies -- mode 2 and an actor shares an edge with a movie if the actor appears in the movie.
-The social network analyzed in this chapter is a two-mode network, where vertices consists of colleges/universities (mode 1) and high schools (mode 2) and an "edge" is defined as a visit from a college/university to a private high school [DELETE THIS SENTENCE OR THE REDUNDANT ONE IN BELOW PARAGRAPH].
-
-Our analyses draw from analyses of "corporate board-director" networks because these are the most commonly analyzed two-mode networks in the social networks literature [e.g.] [@RN4663].
+Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
+For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
+<!--The social network analyzed in this chapter is a two-mode network, where vertices consists of colleges/universities (mode 1) and high schools (mode 2), and an edge is defined as a visit from a college/university to a private high school [DELETE THIS SENTENCE OR THE REDUNDANT ONE IN BELOW PARAGRAPH].-->
+
+Our analyses draw from analyses of "corporate board-director" networks because these are the most commonly analyzed two-mode networks in the social networks literature [e.g., @RN4663].
 Board-director networks consist of directors (mode 1) who serve on organizational boards (mode 2).
-Our school-college network is a two-mode network composed of two sets of vertices, private high schools (mode 1) and colleges/universities (mode 2).
-Off-campus recruiting visits are edges (e.g., high school $i$ shares an edge with college $j$ if high school $i$ receives at least one visit from college $j$) and visits can only occur between a school-college pair (not a school-school pair or a college-college pair).
-Our school-college network is a two-mode network composed of high schools (mode 1) who are visited by colleges and universities (mode 2).
-This (weighted) network is represented as a school-by-college matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 colleges/universities) in which matrix cell $a_{i,j}$ identifies the number of visits that high school $i$ received from college/university $j$.
-[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
-UNWEIGHTED SOMEWHERE]
+In our school-college two-mode network, the vertices are private high schools (mode 1) and colleges/universities (mode 2), and an edge is defined as an off-campus recruiting visits made between the two (e.g., high school $i$ shares an edge with college $j$ if high school $i$ receives at least one visit from college $j$).
+Visits can only occur between a school-college pair (not a school-school pair or a college-college pair).
+This (weighted) network can be represented as a school-by-college matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 colleges/universities) in which matrix cell $a_{i,j}$ identifies the number of visits that high school $i$ received from college/university $j$.
+<!--[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
+UNWEIGHTED SOMEWHERE]-->
 
@@
 Two-mode networks are often analyzed as one-mode networks [@RN2457].
-@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" [pg.
-xx].
+@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" (p.
+XXX).
 Thus, a two-mode board-director network can be transformed into two one-mode networks.
-A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ do not serve on three boards together.
+A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ serve on three boards together).
 Similarly, a one-mode board network is created based on a board-by-board matrix in which two boards share an edge if a director sits on both boards and matrix cell $a_{i,j}$ identifies the number of directors that serve on both board $i$ and board $j$.
-Following this approach, we create a one-mode high school network in which two private high schools share an edge if both receive a visit by the same college/university and cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of colleges/universities that visited both school $i$ and school $j$ [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING].
-Similarly, we create a one-mode college/university network (herein the college network) in which two colleges share an edge if both colleges visited the same high school and cell $c_{i,j}$ of the college-by-college matrix $C$ indicates the number of private high schools that received at least one visit from both college $i$ and college $j$ [SHOW EXCERPT OF ONE-MODE COLLEGE BY COLLEGE MATRIX, LIKE 3 BY 3 OR SOMETHING].
+Following this approach, we create a one-mode high school network in which two private high schools share an edge if they both receive a visit by the same college/university.
+Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of colleges/universities that visited both school $i$ and school $j$<!-- [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
+Similarly, we create a one-mode college/university network (herein the college network) in which two colleges share an edge if both colleges visited the same high school.
+Cell $c_{i,j}$ of the college-by-college matrix $C$ indicates the number of private high schools that received at least one visit from both college $i$ and college $j$<!-- [SHOW EXCERPT OF ONE-MODE COLLEGE BY COLLEGE MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
 
@@
 
-A limitation of our data collection is that we collected off-campus visit data only from a convenience sample of X colleges and universities, as described above.
+A limitation of our data collection and analysis is that it is based on a convenience sample of 42 colleges and universities, as described above.
 Thus, for each college and university in our sample, we know all the private high schools they visited (assuming no measurement error).
-However, for each private high school in our sample, we only know visits they received from the set of X colleges/universities in our sample.
-Given this limitation, it may be useful to think of our data collection as resulting in X "ego networks." An "ego" is a single "focal" node (e.g., The University of Notre Dame).
-An ego network consists "of a focal node ("ego") and the nodes to whom ego is directly connected to (these are called "alters") plus the ties, if any, among the alters" [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ].
+However, for each private high school in our sample, we only know visits they received from the set of 42 colleges/universities in our sample.
+Given this limitation, it may be useful to think of our data collection as resulting in 42 "ego networks." An "ego" is a single "focal" node (e.g., The University of Notre Dame).
+An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" (p.
+XXX)<!-- [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ]-->.
 For example, the University of Notre Dame ego network consists of all private high schools that received at least one visit from Notre Dame.
@@
 When analyzing ego networks, researchers often investigate the extent of "homophily" versus "heterophily" [@RN1722].
-Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be freinds on Facebook if they have similar political ideologies).
+Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be friends on Facebook if they have similar political ideologies).
 Heterophily, the opposite of homophily, is when pairs of connected vertices have different characteristics from one another.
-Analyses investigate the extent to which network ties are homopholous or heteropholous, focusing on the vertex characteristics of
+In our analyses, we investigate the extent to which ego network ties are homophilous or heterophilous, focusing on the vertex characteristics of geographic region, religious affiliation, racial composition, and academic ranking.
 
@@
 Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
-We used XYZ community detection approach [add footnote w/ details?] to allocate private colleges and universities [?
-and private high schools] to clusters.
+We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits.<!--We used XYZ community detection approach [add footnote w/ details?] to allocate private colleges and universities [?
+and private high schools] to clusters.-->
 

### 2020-12-19 manuscript.Rmd
draft changes manuscript

@@
 title: "Recruiting Chapter"
-author: "Ozan Jaquette"
+author: 
+  - Ozan Jaquette
+  - Crystal Han
+  - Irma Castaneda
 bibliography: ./other/burd_recruiting_chapter.bib
@@
 
-Our project collected data on off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities.
+[CRYSTAL, CAN YOU CLEAN UP THIS PARAGRAPH AND THE NEXT ONE; THESE PARAGRAPHS ARE TRANSITIONING FROM LIT REVIEW INTRODUCTION/BACKGROUND TO OUR PROJECT; AND ALSO MOTIVATING THE ANELYSES THAT WE DO; JUST USE YOUR JUDGMENT.
+THANK YOU!] Our project collected data on off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities.
 Our analysis sample is based on three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S.

### 2020-12-19 manuscript.Rmd
updates to manuscript

@@
 
-[CRYSTAL, CAN YOU CLEAN UP THIS PARAGRAPH AND THE NEXT ONE; THESE PARAGRAPHS ARE TRANSITIONING FROM LIT REVIEW INTRODUCTION/BACKGROUND TO OUR PROJECT; AND ALSO MOTIVATING THE ANELYSES THAT WE DO; JUST USE YOUR JUDGMENT.
-THANK YOU!] Our project collected data on off-campus recruiting visits made in 2017 by a convenience sample of colleges and universities.
-Our analysis sample is based on three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S.
+Our broader project collected data on off-campus recruiting visits made by a convenience sample of colleges and universities during the 2017 calendar year.
+The data collection sample comes from three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S.
 News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S.
 News and World Report Liberal Arts Colleges rankings (N=47).
-For each of these institutions, we investigated their admissions website for pages that provided the details of upcoming off-campus recruiting visits.
-For institutions that posted such pages, we scraped the pages once per week throughout the 2017 calendar year.
+For each of these institutions, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits.
+For institutions that posted such pages, we scraped the pages once per week throughout 2017.
 Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
@@
 Our analyses to date have focused only on visits by public research universities<!--[CITE]-->.
-The big-picture takeaways are as follows.
-Most public research universities in our sample made more out-of-state than in-state recruiting visits.
+We found that most public research universities in our sample made more out-of-state than in-state recruiting visits.
 The exceptions were UC Berkeley, UC Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps.
 Across all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropolitan areas.
-Most public universities also made a disproportionate number of out-of-state visits to private high schools.
-In addition, analyses of in-state visits found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools.
-Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.
-
-Figures \@ref(fig:event-count-figure-pubu) and \@ref(fig:event-count-figure-privu) show the number of off-campus recruiting visits by public and private colleges and universities in our sample, separated by event type and in-state vs.
-out-of-state.
-<!--TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES....
--->Table/Figure X demonstrates the disproportionate number of visits to private high schools.
-The goal of this chapter is to investigate off-campus recruiting visits to private high schools.
-Which types of private high schools receive visits from which types of colleges and universities?
+Most public universities also made a disproportionate number of out-of-state visits to private high schools, which tend to be more affluent and white.
+<!--In addition, analyses of in-state visits found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools.
+Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.-->
+
+These findings motivated the goal of this chapter to investigate off-campus recruiting visits to private high schools.
+Public research universities have the mission of providing social mobility, yet their large number of out-of-state visits to private high schools are making them more similar to private institutions.
+Figures \@ref(fig:event-count-figure-pubu) and \@ref(fig:event-count-figure-privu) show the number of off-campus recruiting visits by public and private colleges/universities in our sample, respectively.
+A disproportionate number of out-of-state private high school visits can be seen for both public and private institutions.
+In this chapter, we will answer the research questions: Which types of private high schools receive visits from which types of colleges and universities?
 Additionally, to what extent were visits by a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics?
@@
 <!--
+TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES.... Table/Figure X demonstrates the disproportionate number of visits to private high schools.
+
 WHAT TO SHOW IN TABLES/FIGURES:

### 2021-05-03 educ250c_presentation.Rmd
created draft presentation to educ250c

---
title: "Recruiting Chapter"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castaneda
date: 
urlcolor: blue
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true # toc_float option to float the table of contents to the left of the main document content. floating table of contents will always be visible even when the document is scrolled
      #collapsed: false # collapsed (defaults to TRUE) controls whether the TOC appears with only the top-level (e.g., H2) headers. If collapsed initially, the TOC is automatically expanded inline when necessary
      #smooth_scroll: true # smooth_scroll (defaults to TRUE) controls whether page scrolls are animated when TOC items are navigated to via mouse clicks
    number_sections: true
    fig_caption: true # ? this option doesn't seem to be working for figure inserted below outside of r code chunk    
    highlight: tango # Supported styles include "default", "tango", "pygments", "kate", "monochrome", "espresso", "zenburn", and "haddock" (specify null to prevent syntax    
    theme: default # theme specifies the Bootstrap theme to use for the page. Valid themes include default, cerulean, journal, flatly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti.
    df_print: tibble #options: default, tibble, paged
bibliography: ./other/burd_recruiting_chapter.bib
csl: ./other/apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
#library(bookdown)

library(kableExtra)
library(tidyverse)
library(gridExtra)
```

# Introduction

@RN4450 analyzed off-campus recruiting visits made in 2017 by 15 public research universities

- 12 of the 15 universities made more visits to out-of-state high schools than in-state high schools
- @RN4450 focused on visits to public high schools, finding that out-of-state visits focused on schools in affluent, predominantly white communities
- However, @RN4450 also found that public research universities made a disproportionate number of out-of-state visits to private high schools. For example
  - _University of Pittsburgh_. 170 (28%) out of 605 out-of-state high school visits were to private high schools
  - _University of California-Berkeley_. 155 (43%) out of 360 out-of-state high school visits were to private high schools
  - _University of Colorado-Boulder_. 321 (36%) out of 901 out-of-state high school visits were to private high schools

<br>

This chapter analyzes visits to private high schools by public research universities in comparison to visits to private high schools by selective private universities.

## The privatization literature

This chapter contributes to scholarship on the "privatization" of public higher education by connecting this literature to ....

<br>

@RN4543 review scholarship on privatization in higher education

- One sub-literature conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization
  - Of relevance to this chapter, public universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753], who typically pay two- to three-times more than resident students
- Another sub-literature conceptualizes privatization as a process whereby public institutions become more similar to for-profit or private nonprofit sector organizations
  - A weakness of this literature is that few empirical studies analyze public institutions on a behavior associated with private institutions

<br>

The traditional mission of selective private universities vs. public research universities

- Selective private universities
  - Historically, these institutions serve the mission of social reproduction, defined as prioritizing access for affluent, college-educated households
    - (and at sectarian institutions, prioritizing access for students who share religious ideology of the institution)
  - Visits to private high schools are consistent with this social reproduction mission
- Public research universities
  - "public good" mission in access to public flagship/research universities
    - Contribute to economic and civic development by enrollinghigh achieving state residents who will be future civic, professional, and business leaders of the state
    - Contribute to *social mobility* in the state, by prioritizing the enrollment of high-achieving first-generation, low-income, and (more recently) non-white state residents
  - Visits to private high schools -- particularly out-of-state private high schools -- are antithetical to this public good access mission

<br>

Therefore, we conceptualize recruiting visits to private high schools as an ideal-type behavioral example of public flagship universities engaging in a behavior associated with the traditional social reproduction mission of selective private non-profit universities

- By analyzing visits to private high schools by public research universities and comparing them to visits made by selective private universities, we hope to develop broader insights about the privatization of public research universities

<br>

## Research questions

Analyses are motivated by three research questions

1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by private universities?
1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools 
1. To what extent do public research universities and private universities visit overlapping sets of private high schools?

For each research questions we look for: similarities and differences within public research universities; similarities and differences between public and private universities

```{r cars}
summary(cars)
```

# Background and literature review

This section provides context for our analyses of off-campus recruiting visits. First, we situate off-campus recruiting within the broader set of marketing and recruiting interventions in higher education and review what market research says about off-campus recruiting.

## Background

The "enrollment funnel" -- depicted in Figure \@ref(fig:em-funnel) -- is a conceptual heuristic that identifies stages in the student recruitment process (prospects, inquiries, applicants, accepted applicants, and enrolled students). The enrollment management industry uses the enrollment funnel to inform marketing and recruiting interventions that target specific stages.

- "Prospects" are "all the potential students you would want to attract to your institution" [@RN4322]. 
- "Inquiries" are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own.

```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%"}
knitr::include_graphics('assets/images/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

What do we know about off-campus recruiting from market research?

- Market research describes off-campus recruiting visits as a means of identifying prospects and deepening engagement with prospects already being targeted through mail/email [@RN4323; @RN4402; @RN4664].
- @RN4402 documents the self-reported efficacy of marketing/recruiting interventions. 
  - For the median private 4-yr institution, off-campus visits were the second highest source of inquiries (after student list purchases), accounting for 17% of inquiries, and tied with student list purchases as the highest source of enrollees, accounting for 18% of enrollees. 
  - For the median public institution, off-campus visits accounted for 19% of inquiries (second only to student list purchases) and accounted for 16% of enrollees (ranked third after stealth applicants and on-campus visits).
- With respect to expenditure, Table \@ref(tab:ug-recruit-budget), reproduced from @RN4664, shows the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities

<br>

```{r ug-recruit-budget, echo=FALSE}
pct_budget <- data.frame(
  activity = c("Travel","Student search (purchased lists)","Prospective student communications","Events","Recruitment publications","Web services and digital advertising","Traditional advertising","International recruitment","Transfer recruitment","Other"),
  private = c(17,14,13,12,11,11,6,5,4,8),
  public = c(16,12,17,11,15,13,6,3,4,3)
)

#pct_budget
#str(pct_budget)
#attributes(pct_budget)
kable(
  x = pct_budget, 
  col.names = c("Activity", "Private", "Public"),
  caption = "Percentage of budget allocated to marketing/recruiting activities by private non-profit 4yr and public 4yr institutions"
)
#  <div id="refs"></div>
```

## Literature review

We review empirical scholarship from sociology that analyzes recruiting by colleges and universities, emphasizing scholarship that analyzes off-campus recruiting and scholarship that considers private high schools.

<br>
A case study literature in sociology analyzes recruiting, often as part of a broader analysis of enrollment management or college access [e.g., @RN4324; @RN3519; @RN4538; @RN4520; @RN4407; @RN1814; @RN4647; @RN4321].

- @RN3519 and Khan [-@RN4321;-@RN4407] are particularly relevant to the present chapter because these studies analyze relationships between college admissions counselors and high school guidance counselors.

<br>

@RN3519, an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of visits.

- Stevens [-@RN3519, p. 54] states that "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide." 
- Whereas market research by @RN4402 highlights the effect of recruiting visits on inquiries and enrollees, findings from @RN3519 suggest that the College may have valued recruiting visits primarily as a means of maintaining relationships with guidance counselors. 
- The College tended to visit the same "feeder" schools year after year because recruiting depends on long-term relationships with high schools. 
- The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and had the resources and motivation to host a successful visit.

<br>

@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p. 98).

- What elite private colleges want
  - high achieving students who can pay tuition and donate
  - low acceptance rates and high yield rates
  - "interesting characters" whose curricular and extracurricular strengths meet the demands of campus constituents
- Problem faced by elite private high schools
  - some of their students are stronger than others
- Problem faced by elite private colleges  
  - Many outstanding applicants; but hard to get reliable information about which applicants will enroll if admitted
- How high school guidance counselors capitalize on this problem
  - tell colleges which high-achieving applicants are likely to accept admissions offer, which are likely to go elsewhere admissions offer and which are not
  - If a high-achieving applicant likely to go elsewhere, recommend the college consider an applicant with weaker academic credentials who would accept if admitted and brings extracurricular strengths the college values
- This horsetrading depends on
  - long-term relationship between high school and college, based on repeated interactions
  - small enough caseloads to advocate for each student

<br>

Rationale for treating off-campus recruiting visits as a relationship that can be analyzed using social network methods [from draft chapter]

> To summarize, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school. Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another. In the absence of strong relationships, it is less likely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].

> Building on these ideas, we reason that the presence of a recruiting visit between a college and a high school is an indicator that the college and the high school have a relationship. First, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school. Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.  Third, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls).

# Methods

## Data collection

Our broader project collected data on off-campus recruiting visits made by a convenience sample of colleges and universities during the 2017 calendar year.

The data collection sample comes from three different lists of postsecondary institutions:

- all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102)
- all private universities in the top 100 of U.S. News and World Report National Universities rankings (N=58)
- all private colleges in the top 50 of U.S. News and World Report Liberal Arts Colleges rankings (N=47).

For each of these institutions, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits.

- For institutions that posted such pages, we scraped the pages once per week throughout 2017. 
  - Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions are excluded from the analyses. 
- For public universities, we also collected data using public records requests

The analysis sample for this chapter consists of:

- 15 public research universities, 
- 13 private research universities
- 12 private liberal arts colleges [may cut from analysis sample]

<br>

## Social network analysis

<br>

A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "edges" between these actors.

- "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author)
- "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type. For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.

<br>

In our school-college two-mode network:

- the vertices are private high schools (mode 1) and colleges/universities (mode 2), 
- An edge is defined as an off-campus recruiting visits made between the two (e.g., high school $i$ shares an edge with college $j$ if high school $i$ receives at least one visit from college $j$). 
- Visits can only occur between a school-college pair (not a school-school pair or a college-college pair). 
- The resulting (weighted) network can be represented as a school-by-college matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 colleges/universities) in which matrix cell $a_{i,j}$ identifies the number of visits that high school $i$ received from college/university $j$.

<br>

Two-mode networks are often analyzed as one-mode networks for simplicity [@RN2457]

-  we create a one-mode high school network in which two private high schools share an edge if they both receive a visit by the same college/university. Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of colleges/universities that visited both school $i$ and school $j$<!-- [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING]-->. 
- Similarly, we create a one-mode college/university network (herein the college network) in which two colleges share an edge if both colleges visited the same high school. Cell $c_{i,j}$ of the college-by-college matrix $C$ indicates the number of private high schools that received at least one visit from both college $i$ and college $j$

<br>

Community detection

- Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties. 
- Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups. 
- We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits.

# Results

## Analysis sample

## RQ1: Scale of visits to private high schools

<br>

Number of events by type and in-state, out-of-state for public research universities institutions
```{r event-count-figure-pubu, echo = FALSE, out.width="125%"}
knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
```

<br>
<br>

Number of events by type and in-state, out-of-state for private institutions
```{r event-count-figure-privu, echo = FALSE, out.width="125%"}
knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
```

<br>
<br>

Actual versus proportional visits to out-of-state private high schools for public research universities
```{r, echo = FALSE, out.width="125%"}
knitr::include_graphics('assets/figures/figure_5.pdf')
```

<!-- ![Alternate Name](assets/figures/plot_event_count_privu.pdf){width=1000px; height = 1000px} -->

## RQ2: Characteristics of visits to private high schools

<br>

CRYSTAL - CAN YOU ADD FOLLOWING FIGURES CURRENTLY INCLUDED IN MANUSCRIPT.PDF

- FIG 7, CHARACTERISTICS OF PRIVATE HS VISITED BY PRIVATE INSTITUTIONS
- FIG 11, CHARACTERISTICS OF PRIVATE HS VISITED BY PUBLIC INSTITUTIONS

## RQ3: Overlapping networks of visits to private high schools

CYSTAL - CAN YOU ADD FOLLOWING FIGURES CURRENTLY INCLUDED IN MANUSCRIPT.PDF

- FIG 10, 1-mode network for public institutions, colored by cluster
- FIG 12, 1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster

# References

### 2021-05-03 scripts/create_igraph_objects.R

@@ -548,15 +548,13 @@ for(v in vec_2mode) {
 
 #vec_2mode <- c('','_priv','_pubu','_u','_privu','_privc')
 vec_2mode <- c('','_priv')
-vec_2mode
-
-vec_egos <- c('"" psi_vec privhs_vec','_priv priv_vec privhs_visited_by_priv_vec')
+#vec_egos <- c('"" psi_vec privhs_vec','_priv priv_vec privhs_visited_by_priv_vec')
 
 
 for(v in vec_egos) {
   
   writeLines(str_c(''))
-  writeLines(str_c('object v=', v))
+  #writeLines(str_c('object v=', v))
   
   #v2 <- str_c('g_2mode',v)
   #writeLines(str_c('object v2=',v2))
@@ -592,23 +590,8 @@ for(v in vec_egos) {
 
 # create 2-mode subgraph for private colleges and their private HS visits only
   # g_2mode_privc
-  # privc_vec    
-  # privhs_visited_by_privc_vec
-
-
-
-
-
-
-
-
-
-
-
-
+  
     
-privhs_vec
-
 for(v in vec_2mode) {
   
   writeLines(str_c(''))
@@ -624,14 +607,14 @@ for(v in vec_2mode) {
   writeLines(str_c('object psi=',psi))
   
   # Create ego networks for each private HS
-  ego1 <- make_ego_graph(graph = get(v2),
-                          order = 2,
-                          nodes = V(get(v2))[V(get(v2))$type == FALSE],  # only include private HS
-                          mindist = 0)
+  #ego1 <- make_ego_graph(graph = get(v2),
+    #                      order = 2,
+    #                      nodes = V(get(v2))[V(get(v2))$type == FALSE],  # only include private HS
+    #                      mindist = 0)
   #print(ego1)
   #assign(x= v1_hs, value = hs)
   #assign(x= v1_psi, value = psi)
-  names(ego1) <- privhs_vec %>% str_sort()  # name the list of ego networks  
+  #names(ego1) <- privhs_vec %>% str_sort()  # name the list of ego networks  
   
 }
 

### 2021-05-04 educ250c_presentation.Rmd
edit formatting of educ250c

@@
 output: 
-  html_document:
+  bookdown::html_document2:
     toc: true
@@
 ---
+
+<style>
+embed {
+  width: 745px;
+  height: 1000px;
+}
+
+#rq2-characteristics-of-visits-to-private-high-schools embed {
+  width: 690px;
+  height: 735px;
+}
+
+#rq3-overlapping-networks-of-visits-to-private-high-schools embed {
+  width: 750px;
+  height: 590px;
+}
+
+caption {
+  color: black;
+  font-weight: bold;
+  white-space: pre !important;
+} 
+</style>
 
@@
   caption = "Percentage of budget allocated to marketing/recruiting activities by private non-profit 4yr and public 4yr institutions"
-)
+) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "responsive"), full_width = F, position = "left")
 #  <div id="refs"></div>
@@
 
-Number of events by type and in-state, out-of-state for public research universities institutions
-```{r event-count-figure-pubu, echo = FALSE, out.width="125%"}
+**Number of events by type and in-state, out-of-state for public research universities institutions**
+
+```{r event-count-figure-pubu, echo = FALSE}
 knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
@@
 
-Number of events by type and in-state, out-of-state for private institutions
-```{r event-count-figure-privu, echo = FALSE, out.width="125%"}
+**Number of events by type and in-state, out-of-state for private institutions**
+
+```{r event-count-figure-privu, echo = FALSE}
 knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
@@
 
-Actual versus proportional visits to out-of-state private high schools for public research universities
-```{r, echo = FALSE, out.width="125%"}
+**Actual versus proportional visits to out-of-state private high schools for public research universities**
+
+```{r, echo = FALSE}
 knitr::include_graphics('assets/figures/figure_5.pdf')
@@
 
-CRYSTAL - CAN YOU ADD FOLLOWING FIGURES CURRENTLY INCLUDED IN MANUSCRIPT.PDF
+**Characteristics of private HS visited by private institutions**
 
-- FIG 7, CHARACTERISTICS OF PRIVATE HS VISITED BY PRIVATE INSTITUTIONS
-- FIG 11, CHARACTERISTICS OF PRIVATE HS VISITED BY PUBLIC INSTITUTIONS
+```{r ego-network-figure-privu, echo = FALSE}
+knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
+```
+
+<br><br>
+
+**Characteristics of private HS visited by public institutions**
+
+```{r ego-network-figure-pubu, echo = FALSE}
+knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
+```
 
@@
 
-CYSTAL - CAN YOU ADD FOLLOWING FIGURES CURRENTLY INCLUDED IN MANUSCRIPT.PDF
+<br>
 
-- FIG 10, 1-mode network for public institutions, colored by cluster
-- FIG 12, 1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster
+**1-mode network for public institutions, colored by cluster**
+
+```{r plot-1mode-pubu, echo = FALSE}
+knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
+```
+
+<br><br>
+
+**1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster**
+
+```{r plot-1mode-all-pubu-outst, echo = FALSE}
+knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
+```
 

### 2021-05-04 educ250c_presentation.Rmd
switch PDFs to PNGs for educ250c

@@
 ```{r event-count-figure-pubu, echo = FALSE}
-knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
+# knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
+knitr::include_graphics('assets/figures/plot_event_count_pubu.png')
 ```
-
-<br>
-<br>
 
@@
 ```{r event-count-figure-privu, echo = FALSE}
-knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
+# knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
+knitr::include_graphics('assets/figures/plot_event_count_privu.png')
 ```
-
-<br>
-<br>
 
@@
 ```{r, echo = FALSE}
-knitr::include_graphics('assets/figures/figure_5.pdf')
+# knitr::include_graphics('assets/figures/figure_5.pdf')
+knitr::include_graphics('assets/figures/figure_5.png')
 ```
@@
 ```{r ego-network-figure-privu, echo = FALSE}
-knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
+# knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
+knitr::include_graphics('assets/figures/ego_network_figure_privu.png')
 ```
@@
 ```{r ego-network-figure-pubu, echo = FALSE}
-knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
+# knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
+knitr::include_graphics('assets/figures/ego_network_figure_pubu.png')
 ```
@@
 ```{r plot-1mode-pubu, echo = FALSE}
-knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
+# knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
+knitr::include_graphics('assets/figures/plot_1mode_pubu.png')
 ```
@@
 ```{r plot-1mode-all-pubu-outst, echo = FALSE}
-knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
+# knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
+knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.png')
 ```

### 2021-05-04 educ250c_presentation.Rmd
presentation to 250c

@@
 
+### Two-mode network objects
+
 In our school-college two-mode network:
@@
 <br>
+*Two mode network of colleges (mode 1) visiting private high schools (mode 2), nodes colored by community cluster*
+```{r, echo = FALSE}
+# knitr::include_graphics('assets/figures/figure_5.pdf')
+knitr::include_graphics('assets/figures/plot_2mode_all-1.png')
+```
+
+### One-mode network objects
 
@@
 <br>
+*One-mode network of private universities, edges between two universities weighted by the number of high schools they both visited, nodes colored by community cluster*
+```{r, echo = FALSE}
+# knitr::include_graphics('assets/figures/figure_5.pdf')
+knitr::include_graphics('assets/figures/plot_1mode_privu-1.png')
+```
+
+### Ego networks
+
+A limitation of our data collection and analysis is that it is based on a convenience sample of colleges and universities, as described above.
+Thus, for each college and university in our sample, we know all the private high schools they visited (assuming no measurement error).
+However, for each private high school in our sample, we only know visits they received from the set of 42 colleges/universities in our sample.
+Given this limitation, it may be useful to think of our data collection as resulting in 40 "ego networks."
+
+Ego networks
+
+- An "ego" is a single "focal" node (e.g., The University of Notre Dame). 
+- An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" (p.
+XXX)<!-- [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ]-->.
+- For example, the University of Notre Dame ego network consists of all private high schools that received at least one visit from Notre Dame.
+Additionally, for each high school visited by Notre Dame, the ego network may include all colleges/universities in our sample that also visited the high school.
+
+<br>
+*Ego network of Emory University, nodes colored by geographic region*
+```{r, echo = FALSE}
+# knitr::include_graphics('assets/figures/figure_5.pdf')
+knitr::include_graphics('assets/figures/emory_region-1.png')
+```
 
@@
 # Results
-
-## Analysis sample
 
@@
 
+<br>
+<br>
+
 **Number of events by type and in-state, out-of-state for private institutions**
@@
 ```
+
+<br>
+<br>
 
@@
 
+**Characteristics of private HS visited by public institutions**
+
+```{r ego-network-figure-pubu, echo = FALSE}
+# knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
+knitr::include_graphics('assets/figures/ego_network_figure_pubu.png')
+```
+
+<br><br>
+
 **Characteristics of private HS visited by private institutions**
@@
 
-**Characteristics of private HS visited by public institutions**
-
-```{r ego-network-figure-pubu, echo = FALSE}
-# knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
-knitr::include_graphics('assets/figures/ego_network_figure_pubu.png')
-```
-
 ## RQ3: Overlapping networks of visits to private high schools
@@
 # knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
-knitr::include_graphics('assets/figures/plot_1mode_pubu.png')
+knitr::include_graphics('assets/figures/plot_1mode_pubu-1.png')
 ```
@@
 
-**1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster**
+**1-mode network for public institutions, out-of-state visits only, colored by cluster** 
+```{r plot-1mode-pubu-outst, echo = FALSE}
+# knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
+knitr::include_graphics('assets/figures/plot_1mode_pubu_outst-1.png')
+```
+
+<br><br>
+
+**1-mode network for private and public universities, out-of-state visits only for public universities, colored by cluster**
 
@@
 # knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
-knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.png')
+knitr::include_graphics('assets/figures/plot_1mode_u_pubu_outst-1.png')
 ```

### 2021-05-04 scripts/network_recruiting_analysis.R

@@ -387,7 +387,7 @@ plot_2mode_graph <- function(twomode_network, c_analysis, k = NULL, h = NULL, no
     vertex.shape = 'circle',
     vertex.size = if_else(V(twomode_network)$type, 3, 0.75),
     edge.lty = 3,
-    edge.lty = 0.5,
+    #edge.lty = 0.5,
     edge.color = 'lightgrey',
     layout = layout,
     margin = margin
@@ -485,7 +485,7 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
     vertex_label <- ''
   } else {  # mode == 'psi'
     proj <- 'proj2'
-    vertex_size <- 5
+    vertex_size <- 8
     vertex_label <- V(twomode_network)[V(twomode_network)$type]$school_name
   }
   
@@ -508,28 +508,40 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
     vertex.shape = 'circle',
     vertex.size = vertex_size,
     edge.lty = 3,
-    edge.lty = 0.5,
+    #edge.lty = 0.5,
+    edge.width = log(as.numeric(E(network)$weight)/10),
+    #edge.width = 1,
     edge.color = 'lightgrey',
     layout = layout,
     margin = margin
   )
 }
 
-# Usage
 plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 4)
-plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'fast', steps = 11, colors = c('red', 'orange', 'yellow', 'green', 'blue', 'purple'))
+# Usage
 
 # Private univs
 save_plot(plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 4),
           plot_name = 'plot_1mode_privu.pdf')
 
+# private colleges
+
+save_plot(plot_1mode_graph(g_2mode_privc, mode = 'psi', c_analysis = 'hclust', k = 5, colors = c('red', 'yellow', 'green', 'blue', 'purple')),
+          plot_name = 'plot_1mode_privc.pdf')
+
 # Public univs
 save_plot(plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 4),
           plot_name = 'plot_1mode_pubu.pdf')
[…]

### 2021-05-04 educ250c_presentation.Rmd
added links to 250c presentation
link

@@
 ---
-title: "Recruiting Chapter"
+title: "Recruiting visits to private high schools"
 author: 
@@
 ```
+
+Link to html presentation
+
+- [LINK](https://cyouh95.github.io/recruiting-chapter/educ250c_presentation.html)
+
+Link to slides by Prof Omar Lizardo
+
+- [LINK](https://docs.google.com/presentation/d/106TT6MHW-Fz5CmD23jZNrRbQ2wT7o07nBig0MUTSqPA/edit#slide=id.gbd14bdbd8f_0_1052)
 

### 2021-05-17 text/tables_figures_may_2021.Rmd
draft changes revising results

---
title: "Recruiting Chapter"
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castaneda
bibliography: ./../other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
csl: ./../other/apa.csl
urlcolor: blue
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \floatsetup{capposition=top}
---

```{r setup, include=FALSE}
library(knitr)
library(bookdown)

library(kableExtra)
library(tidyverse)
library(gridExtra)
```

# Results

ADD TABLE OF UNIVERSITY CHARACTERISTICS HERE

## RQ1: Scale

```{r event-count-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for public institutions"}
knitr::include_graphics('./../assets/figures/plot_event_count_pubu.pdf')
```

```{r event-count-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for private institutions"}
knitr::include_graphics('./../assets/figures/plot_event_count_privu.pdf')
```

## RQ2: Characteristics of high schools

```{r, include = FALSE}
# ggplot's default color palette
# library(scales)
# show_col(hue_pal()(4))

plot_characteristic <- function(df, type, characteristic, label_text, visit_count = FALSE) {

  if (visit_count) {
    df <- df %>% mutate(univ_name = str_c(univ_name, ' (N=', total, ')'))
  }

  # create variable for university region; and turn rank into a numeric variable
  df <- df %>% mutate(
    univ_region=factor(
      str_split(characteristics, pattern = '\\|', simplify=TRUE)[,1],levels = c('northeast','midwest','south','west')),
    rank = as.numeric(rank)
  )

  if (type == 'Region') {
    ordered_df <- df %>% arrange(univ_region, univ_name)
  } else {
    ordered_df <- df %>% arrange(rank, univ_name)
  }

  univ_order <- ordered_df$univ_name

  sub_df <- df %>% select(univ_name, all_of(characteristic)) %>%
    gather(key, value, characteristic) %>%
    mutate(value = parse_number(value))

  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
  sub_df$key <- factor(sub_df$key, levels = characteristic)

  ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
    ggtitle('Title') +
    xlab('') + ylab('') +
    labs(fill = type) +
    scale_fill_manual(labels = label_text, values = c('#F8766D', '#7CAE00', '#00BFC4', '#C77CFF')) +
    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
    theme(legend.position = 'top',
          legend.title = element_text(size = 6, face = 'bold'),
          legend.text = element_text(size = 6),
          legend.margin = margin(0, 0, 0, 0),
          legend.box.margin = margin(0, 0, -5, -30),
          legend.key.size = unit(0.3, 'cm'),
          panel.background = element_blank(),
          axis.ticks.y = element_blank(),
          text = element_text(size = 8),
          plot.title = element_text(color = 'white')) +
    coord_flip()
}

```

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE, include = FALSE}
#all univ privu all_pubu_outst pub pubu_outst
# running one plot at a time

# region

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'region', '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 1))

  a <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
  )

  b <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
  )

  grid.arrange(a, b, nrow=2, ncol=1)

  dev.off()

# religion

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'religion', '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 1))

  a <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'), visit_count = TRUE
  )

  b <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
    'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'), visit_count = TRUE
  )

  grid.arrange(a, b, nrow=2, ncol=1)

  dev.off()

# racial composition

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'race', '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 1))

  a <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE
  )

  b <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
    '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE
  )

  grid.arrange(a, b, nrow=2, ncol=1)

  dev.off()

# academic reputation

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'hs_rank', '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 1))

  a <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
    'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'), visit_count = TRUE
  )

  b <- plot_characteristic(
    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
    'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'), visit_count = TRUE
  )

  grid.arrange(a, b, nrow=2, ncol=1)

  dev.off()

```

\newpage

```{r ego-network-figure-region, eval = FALSE, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of visited private HS, region"}
knitr::include_graphics('./../assets/figures/ego_network_figure_region.pdf')
```

```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE, eval = FALSE}

type_vec <- c('pubu', 'pubu_outst','privu','univ','univ_pubu_outst')
#type_vec <- c('privu', 'pubu', 'pubu_outst', 'all', 'all_pubu_outst')

for (i in 1:length(type_vec)) {
  ego_df <-readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))

  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')))
  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
  par(mfrow=c(2, 2))

  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE)
  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE)
  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))

  grid.arrange(a, b, c, d, nrow=2, ncol=2, widths=c(1, 0.92))
  dev.off()

  # Need to use print() for ggplot inside loop in order for it to appear
  # https://stackoverflow.com/a/15678596/6373540
  # print(a)
  # print(b)
  # print(c)
  # print(d)
}
```

## RQ3: Overlapping sets of high schools

# References

<div id="refs"></div>

<!-- TABLES -->

\newpage
<!-- private col/univ -->

```{r hs-print-privu, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_privu.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by private institutions') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r hs-table-privu-agg, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_privu.RDS')

knitr::kable(df, caption = 'Characteristics of private HS visited by private institutions, by degree band') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

<!-- public research universities -->

```{r hs-print-pubu, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_pubu.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by public institutions') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r hs-table-pubu-agg, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_pubu.RDS')

knitr::kable(df, caption = 'Characteristics of private HS visited by public institutions, by degree band') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

<!-- public and private col/univ -->

```{r hs-print-both, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_both.RDS') %>% head(n=20)

knitr::kable(
  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by all institutions') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

```{r hs-table-both-agg, echo = FALSE}
df <- readRDS('./../assets/tables/table_2mode_agg_both.RDS')

knitr::kable(df, caption = 'Characteristics of private HS visited by all institutions, by degree band') %>% 
  landscape(margin = NULL) %>%
  kable_styling(latex_options = 'scale_down')
```

<!-- FIGURES -->

```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%"}
knitr::include_graphics('./../assets/images/enrollment_funnel.png')
#![The enrollment funnel](assets/images/enrollment_funnel.png)
```

\newpage

```{r privhs-universe, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
knitr::include_graphics('./../assets/figures/plot_pss_universe.pdf')
```

\begin{center}
* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12 students and is not a special education school, an alternative school, an early childhood center, or an independent school.}
\end{center}

\newpage

\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}

\begin{landscape}

```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
knitr::include_graphics('./../assets/figures/plot_2mode_all_region.pdf')

#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
```

```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for private institutions, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
```

\end{landscape}

\restoregeometry

\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}

\newpage

```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
knitr::include_graphics('./../assets/figures/ego_network_figure_privu.pdf')
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}

\begin{landscape}

\newpage

```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}
knitr::include_graphics('./../assets/figures/villanova_religion.pdf')
```

```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, colored by geographic region"}
knitr::include_graphics('./../assets/figures/emory_region.pdf')
```

```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
```

```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions and out-of-state visits only, colored by cluster", eval = FALSE}
knitr::include_graphics('./../assets/figures/plot_1mode_pubu_outst.pdf')
```

\end{landscape}

\restoregeometry

\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}

\newpage

```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by public institutions"}
knitr::include_graphics('./../assets/figures/ego_network_figure_pubu.pdf')
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}

\begin{landscape}

```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, colored by cluster", include= FALSE, eval = FALSE}
knitr::include_graphics('./../assets/figures/plot_1mode_all.pdf')
```

```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_all_pubu_outst.pdf')
```

\end{landscape}

\restoregeometry

\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}

\newpage

```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by all institutions, out-of-state visits only for public universities"}
knitr::include_graphics('./../assets/figures/ego_network_figure_all_pubu_outst.pdf')
#out.width="1.1\\linewidth", 
```

\begin{center}
* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
\end{center}

### 2021-05-17 scripts/create_igraph_objects.R

@@ -10,7 +10,10 @@ library(labelled)
 ## ----------
 
 # Recruiting events data from 43 univs (17 public research, 13 private national, 13 private liberal arts)
-events_data <- read.csv('./data/events_data_2020-07-27.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble()
+#events_data <- read.csv('./data/events_data_2020-07-27.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble()
+events_data_temp1 <- read.csv('./data/events_data_2020-10-20.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble()
+events_data_marquette <- read.csv('./data/events_data_marquette.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble()
+events_data <- events_data_temp1 %>% bind_rows(events_data_marquette)
 
 # University data from IPEDS
 univ_data <- readRDS('./data/ipeds_1718.RDS')
@@ -243,8 +246,8 @@ attributes_df <- attributes_df %>% mutate(
   pct_blacklatinxnative = pct_black + pct_hispanic + pct_amerindian + pct_nativehawaii,
   pct_blacklatinxnative_cat = case_when(
     pct_blacklatinxnative < 10 ~ 'c1_lt10',
-    pct_blacklatinxnative < 25 ~ 'c2_10to25',
-    pct_blacklatinxnative < 50 ~ 'c3_25to50',
+    pct_blacklatinxnative < 20 ~ 'c2_10to20',
+    pct_blacklatinxnative < 50 ~ 'c3_20to50',
     pct_blacklatinxnative >= 50 ~ 'c4_50+'
   )
 )
[…]

### 2021-05-17 scripts/network_recruiting_analysis.R

@@ -47,8 +47,8 @@ religion_values <- c('catholic', 'christian', 'nonsectarian', 'other')
 religion_keys <- c('Catholic', 'Christian', 'Nonsectarian', 'Other')
 religion_title <- 'religious affiliation'
 
-race_values <- c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+')
-race_keys <- c('LT 10%', '10-25%', '25-50%', 'GT 50%')
+race_values <- c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+')
+race_keys <- c('LT 10%', '10-20%', '20-50%', 'GT 50%')
 race_title <- 'percent black, latinx, or native'
 
 ranking_values <- c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA')
@@ -656,20 +656,44 @@ create_ego_table <- function(twomode_network, ego_networks, univs, c_analysis, k
 }
 
 # Save tables
-ego_table_all <- create_ego_table(g_2mode, egos_psi, univ_vec, c_analysis = 'hclust', k = 4)
-saveRDS(ego_table_all, file = './assets/tables/table_ego_all.RDS')
-
-ego_table_all_pubu_outst <- create_ego_table(g_2mode, egos_psi, univ_vec, c_analysis = 'hclust', k = 4, pubu_visits = 'outofstate', privu_visits = 'all')
-saveRDS(ego_table_all_pubu_outst, file = './assets/tables/table_ego_all_pubu_outst.RDS')
-
-ego_table_privu <- create_ego_table(g_2mode_privu, egos_psi_privu, privu_vec, c_analysis = 'hclust', k = 4)
-saveRDS(ego_table_privu, file = './assets/tables/table_ego_privu.RDS')
 
 ego_table_pubu <- create_ego_table(g_2mode_pubu, egos_psi_pubu, pubu_vec, c_analysis = 'hclust', k = 4)
 saveRDS(ego_table_pubu, file = './assets/tables/table_ego_pubu.RDS')
+ego_table_pubu
 
 ego_table_pubu_outst <- create_ego_table(g_2mode_pubu, egos_psi_pubu, pubu_vec, c_analysis = 'hclust', k = 4, pubu_visits = 'outofstate')
 saveRDS(ego_table_pubu_outst, file = './assets/tables/table_ego_pubu_outst.RDS')
+ego_table_pubu_outst
+
+
[…]

### 2021-05-17 text/tables_figures_may_2021.Rmd
draft changes

@@
 
-```{r event-count-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for public institutions"}
-knitr::include_graphics('./../assets/figures/plot_event_count_pubu.pdf')
-```
+Table \@ref(fig:event-count-figure-pubu): event count public universities
 
-```{r event-count-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for private institutions"}
-knitr::include_graphics('./../assets/figures/plot_event_count_privu.pdf')
-```
+Table \@ref(fig:event-count-figure-privu): event count, private univerisites
 
@@
 # ggplot's default color palette
-# library(scales)
+ library(scales)
 # show_col(hue_pal()(4))
@@
 
-  grid.arrange(a, b, nrow=2, ncol=1)
+  c <- plot_characteristic(
+    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privc', '.RDS'))),
+    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
+  )
+
+  grid.arrange(a, b, c, nrow=3, ncol=1)
 
@@
 
-\newpage
-
-```{r ego-network-figure-region, eval = FALSE, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of visited private HS, region"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_region.pdf')
-```
-
 ```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE, eval = FALSE}
@@
 
-```{r hs-print-privu, echo = FALSE}
+```{r hs-print-privu, echo = FALSE, eval = FALSE}
 df <- readRDS('./../assets/tables/table_2mode_privu.RDS') %>% head(n=20)
@@
 
-```{r hs-table-privu-agg, echo = FALSE}
+```{r hs-table-privu-agg, echo = FALSE, eval = FALSE}
 df <- readRDS('./../assets/tables/table_2mode_agg_privu.RDS')
@@
 
-```{r hs-print-pubu, echo = FALSE}
+```{r hs-print-pubu, echo = FALSE, eval = FALSE}
 df <- readRDS('./../assets/tables/table_2mode_pubu.RDS') %>% head(n=20)
@@
 
-```{r hs-table-pubu-agg, echo = FALSE}
+```{r hs-table-pubu-agg, echo = FALSE, eval = FALSE}
 df <- readRDS('./../assets/tables/table_2mode_agg_pubu.RDS')
@@
 
-```{r hs-print-both, echo = FALSE}
+```{r hs-print-both, echo = FALSE, eval = FALSE}
 df <- readRDS('./../assets/tables/table_2mode_both.RDS') %>% head(n=20)
@@
 
-```{r hs-table-both-agg, echo = FALSE}
+```{r hs-table-both-agg, echo = FALSE, eval = FALSE}
 df <- readRDS('./../assets/tables/table_2mode_agg_both.RDS')
@@
 
-<!-- FIGURES -->
+<!-- ###################################################################################### FIGURES -->
 
@@
 
+<!-- ########################################################## RQ 1: SCALE -->
+
+```{r event-count-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for public institutions"}
+knitr::include_graphics('./../assets/figures/plot_event_count_pubu.pdf')
+```
+
+```{r event-count-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for private institutions"}
+knitr::include_graphics('./../assets/figures/plot_event_count_privu.pdf')
+```
+
+<!-- ADD FIGURES: FIGURE X. Number of events at public high schools and private high schools 
+      within each university, separate line for in-state and out-of-state
+      separate figures for public and private universities
+-->
+
+<!-- ADD FIGURES: FIGURE X. Actual vs. proportional number of visits to private high schools
+      within each university, separate line for in-state and out-of-state
+      separate figures for public and private universities
+-->
+
+<!-- ########################################################## RQ 2: Characteristics of high schools -->
+
+\restoregeometry
+
+\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
+
 \newpage
 
-```{r privhs-universe, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
+```{r ego-network-figure-region, fig.align = 'center', echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
+knitr::include_graphics('./../assets/figures/ego_network_figure_region.pdf')
+```
+
+\newpage
+
+```{r ego-network-figure-religion, fig.align = 'center', echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
+knitr::include_graphics('./../assets/figures/ego_network_figure_religion.pdf')
+```
+
+\newpage
+
+```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "Academic reputation of of visited private high schools"}
+knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank.pdf')
+```
+
+\newpage
+
+```{r ego-network-figure-race, fig.align = 'center', echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
+knitr::include_graphics('./../assets/figures/ego_network_figure_race.pdf')
+```
+
+```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, eval=FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
+knitr::include_graphics('./../assets/figures/ego_network_figure_privu.pdf')
+```
+
+\newpage
+
+```{r privhs-universe, fig.align = 'center', echo = FALSE, eval = FALSE,fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
 knitr::include_graphics('./../assets/figures/plot_pss_universe.pdf')
@@
 
+<!-- 
 \begin{center}
@@
 \end{center}
+-->
+
+<!-- RQ3: Overlapping sets of high schools -->
 
@@
 \end{landscape}
-
-\restoregeometry
-
-\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
-
-\newpage
-
-```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_privu.pdf')
-```
-
-\begin{center}
-* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
-\end{center}
 

### 2021-05-17 scripts/create_igraph_objects.R

@@ -14,6 +14,7 @@ library(labelled)
 events_data_temp1 <- read.csv('./data/events_data_2020-10-20.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble()
 events_data_marquette <- read.csv('./data/events_data_marquette.csv', header = TRUE, na.strings = '', stringsAsFactors = FALSE, colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character', 'event_type' = 'character')) %>% as_tibble()
 events_data <- events_data_temp1 %>% bind_rows(events_data_marquette)
+rm(events_data_marquette,events_data_temp1)
 
 # University data from IPEDS
 univ_data <- readRDS('./data/ipeds_1718.RDS')
@@ -61,14 +62,25 @@ v_get_pss_override <- Vectorize(get_pss_override, USE.NAMES = FALSE)
 
 privhs_events <- privhs_events %>% mutate(school_id = v_get_pss_override(school_id))
 
+privhs_events %>% glimpse()
+
 # Combine 2017-18 PSS data w/ past years as needed
 pss_missing_ncessch <- setdiff(privhs_events$school_id, privhs_data_1718$ncessch)
 pss_1516_ncessch <- privhs_data_1516[privhs_data_1516$ncessch %in% pss_missing_ncessch, ]$ncessch
 pss_1314_ncessch <- setdiff(pss_missing_ncessch, pss_1516_ncessch)
 
+# criteria for private hs to be included in our analysis is 12th grade enrollment of 10 or more
+# CRYSTAL MAY/JUNE 2021 - PLEASE CHECK THAT WE HAVE NON-MISSING VALUES OF THE VARIABLE total_12 
 privhs_data <- privhs_data_1718 %>%
   dplyr::union(privhs_data_1516 %>% filter(ncessch %in% pss_1516_ncessch)) %>%
-  dplyr::union(privhs_data_1314 %>% filter(ncessch %in% pss_1314_ncessch))
+  dplyr::union(privhs_data_1314 %>% filter(ncessch %in% pss_1314_ncessch)) %>% filter(total_12>=10)
+
+
+
+# merge privatehs_events to privhs_data; remove private high schools that have less than 10 12th graders; override object privhs_events
+
[…]

### 2021-05-17 scripts/network_recruiting_analysis.R

@@ -670,6 +670,10 @@ ego_table_privu <- create_ego_table(g_2mode_privu, egos_psi_privu, privu_vec, c_
 saveRDS(ego_table_privu, file = './assets/tables/table_ego_privu.RDS')
 ego_table_privu
 
+ego_table_privc <- create_ego_table(g_2mode_privc, egos_psi_privc, privc_vec, c_analysis = 'hclust', k = 4)
+saveRDS(ego_table_privc, file = './assets/tables/table_ego_privc.RDS')
+ego_table_privc
+
 ego_table_univ <- create_ego_table(g_2mode_u, egos_psi_u, univ_vec, c_analysis = 'hclust', k = 4)
 saveRDS(ego_table_univ, file = './assets/tables/table_ego_univ.RDS')
 ego_table_univ

### 2021-05-18 text/tables_figures_may_2021.Rmd
draft changes

@@
 
-  if (type == 'Region') {
+  if (type == 'region') {
     ordered_df <- df %>% arrange(univ_region, univ_name)
@@
 
-```
+# create function to run the plot_characteristic() function
+#plot_characteristic <- function(df, type, characteristic, label_text, visit_count = FALSE) {
 
-```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE, include = FALSE}
-#all univ privu all_pubu_outst pub pubu_outst
-# running one plot at a time
+run_plot_characteristics <- function(which_psi,which_char,char_label,which_vars,which_labels) {
 
-# region
+  # stuff to use later
+    num_plot <- length(which_psi)
+    name_suf <- str_c(which_psi,collapse = '_')
 
-  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'region', '.pdf')))
+  #print function values as a check
+    print(which_psi)
+    #print(name_suf)
+    #print(num_plot)
+    print(str_c('which_char=',which_char))
+    print(str_c('char_label=',char_label))
+    #print(which_vars)
+    #print(which_labels)
+
+  # initiate pdf
+  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', which_char,'_',name_suf, '.pdf')))
     par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
@@
 
-  a <- plot_characteristic(
-    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
-    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
+  #loop to create figure separately for each psi type
+  plot_list <- vector("list", length(which_psi))
+  for (i in 1:length(which_psi)) {
+
+    plot_list[[i]] <- plot_characteristic(
+      df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', which_psi[i], '.RDS'))),
+      #df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
+      type = char_label,
+      characteristic = which_vars,
+      label_text = which_labels,
+      visit_count = TRUE
     )
 
-  b <- plot_characteristic(
-    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
-    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
-  )
+  }
 
-  c <- plot_characteristic(
-    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privc', '.RDS'))),
-    'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE
-  )
-
-  grid.arrange(a, b, c, nrow=3, ncol=1)
+  # plot sub-plots in grid
+  do.call("grid.arrange", c(plot_list, nrow=num_plot, ncol=1))
 
@@
 
+}
+
+# region
+  # pubu, privu, privc
+  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'region', char_label = 'Region', which_vars = c('northeast', 'midwest', 'south', 'west'),which_labels =c('Northeast', 'Midwest', 'South', 'West'))
+  # pubu and privu
+  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'region', char_label = 'Region', which_vars = c('northeast', 'midwest', 'south', 'west'),which_labels =c('Northeast', 'Midwest', 'South', 'West'))
+
 # religion
+  # pubu, privu, privc
+  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'religion', char_label = 'Religion', which_vars = c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
 
-  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'religion', '.pdf')))
-  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
-  par(mfrow=c(2, 1))
+  # pubu, privu
+  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'religion', char_label = 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
 
-  a <- plot_characteristic(
-    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
-    'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'), visit_count = TRUE
-  )
-
-  b <- plot_characteristic(
-    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
-    'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'), visit_count = TRUE
-  )
-
-  grid.arrange(a, b, nrow=2, ncol=1)
-
-  dev.off()
+# high school rank
+  # pubu, privu, privc
+  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'hs_rank', char_label = 'HS rank', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))
+  # pubu, privu  
+  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'hs_rank', char_label = 'HS rank', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))
 
 # racial composition
+  # pubu, privu, privc  
+  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'pct_black_latinx_native', char_label = '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'))
+  # pubu, privu  
+  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'pct_black_latinx_native', char_label = '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'))
 
-  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'race', '.pdf')))
-  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
-  par(mfrow=c(2, 1))
-
-  a <- plot_characteristic(
+  plot_characteristic(
     df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
@@
   )
-
-  b <- plot_characteristic(
-    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
-    '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE
-  )
-
-  grid.arrange(a, b, nrow=2, ncol=1)
-
-  dev.off()
-
-# academic reputation
-
-  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', 'hs_rank', '.pdf')))
-  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
-  par(mfrow=c(2, 1))
-
-  a <- plot_characteristic(
-    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'pubu', '.RDS'))),
-    'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'), visit_count = TRUE
-  )
-
-  b <- plot_characteristic(
-    df = readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', 'privu', '.RDS'))),
-    'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'), visit_count = TRUE
-  )
-
-  grid.arrange(a, b, nrow=2, ncol=1)
-
-  dev.off()
-
-```
-
-```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE, eval = FALSE}
-
-type_vec <- c('pubu', 'pubu_outst','privu','univ','univ_pubu_outst')
-#type_vec <- c('privu', 'pubu', 'pubu_outst', 'all', 'all_pubu_outst')
-
-for (i in 1:length(type_vec)) {
-  ego_df <-readRDS(file.path('.','..', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))
-
-  pdf(file.path('.','..', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')))
-  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
-  par(mfrow=c(2, 2))
-
-  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE)
-  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
-  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+'), c('<10%', '10-20%', '20-50%', '50%+'), visit_count = TRUE)
-  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))
-
-  grid.arrange(a, b, c, d, nrow=2, ncol=2, widths=c(1, 0.92))
-  dev.off()
-
-  # Need to use print() for ggplot inside loop in order for it to appear
-  # https://stackoverflow.com/a/15678596/6373540
-  # print(a)
-  # print(b)
-  # print(c)
-  # print(d)
-}
 ```
@@
 
+```{r privhs-universe, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private high schools"}
+knitr::include_graphics('./../assets/figures/plot_pss_universe.pdf')
+```
+
+\begin{center}
+* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12.}
+\end{center}
+
+\newpage
+
 ```{r ego-network-figure-region, fig.align = 'center', echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_region.pdf')
+#knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu_privc.pdf')
+knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu.pdf')
 ```
@@
 ```{r ego-network-figure-religion, fig.align = 'center', echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_religion.pdf')
+#knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu_privc.pdf')
+knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu.pdf')
 ```
@@
 
-```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "Academic reputation of of visited private high schools"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank.pdf')
+```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "High school rank of visited private high schools"}
+#knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu_privc.pdf')
+knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu.pdf')
 ```
@@
 ```{r ego-network-figure-race, fig.align = 'center', echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_race.pdf')
+#knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu_privc.pdf')
+knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu.pdf')
 ```
-
-```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, eval=FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_privu.pdf')
-```
-
-\newpage
-
-```{r privhs-universe, fig.align = 'center', echo = FALSE, eval = FALSE,fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
-knitr::include_graphics('./../assets/figures/plot_pss_universe.pdf')
-```
-
-<!-- 
-\begin{center}
-* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12 students and is not a special education school, an alternative school, an early childhood center, or an independent school.}
-\end{center}
--->
 
@@
 
-```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
+```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
+```
+
+```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private universities, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
+```
+
+```{r plot-1mode-privc, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private liberal arts colleges, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_privc.pdf')
+```
+
+```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
+```
+
+```{r plot-1mode-u-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster, five clusters"}
+knitr::include_graphics('./../assets/figures/plot_1mode_u_k5.pdf')
+```
+
+```{r plot-1mode-all, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_all.pdf')
+```
+
+```{r plot-1mode-all-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster, five clusters"}
+knitr::include_graphics('./../assets/figures/plot_1mode_all_k5.pdf')
+```
+
+```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, out-of-state visits only, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_pubu_outst.pdf')
+```
+
+```{r plot-1mode-u-pubu-outst, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, out-of-state visits only for public universities, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_u_pubu_outst.pdf')
+```
+
+```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "One-mode network for all institutions, out-of-state visits only for public universities, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_all_pubu_outst.pdf')
+```
+
+```{r two-mode-plot, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
+# <!-- plot of two-mode network; exclude for now -->
 knitr::include_graphics('./../assets/figures/plot_2mode_all_region.pdf')
@@
 
-```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for private institutions, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
+```{r villanova-religion, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}
+#<!-- Ego networks; exclude for now -->
+knitr::include_graphics('./../assets/figures/villanova_religion.pdf')
+```
+
+```{r emory-region, fig.align = 'center', echo = FALSE, eval= FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, colored by geographic region"}
+knitr::include_graphics('./../assets/figures/emory_region.pdf')
 ```
@@
 \end{landscape}
-
-\begin{landscape}
-
-\newpage
-
-```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}
-knitr::include_graphics('./../assets/figures/villanova_religion.pdf')
-```
-
-```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, colored by geographic region"}
-knitr::include_graphics('./../assets/figures/emory_region.pdf')
-```
-
-```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
-```
-
-```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions and out-of-state visits only, colored by cluster", eval = FALSE}
-knitr::include_graphics('./../assets/figures/plot_1mode_pubu_outst.pdf')
-```
-
-\end{landscape}
-
-\restoregeometry
-
-\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
-
-\newpage
-
-```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by public institutions"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_pubu.pdf')
-```
-
-\begin{center}
-* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
-\end{center}
-
-\begin{landscape}
-
-```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, colored by cluster", include= FALSE, eval = FALSE}
-knitr::include_graphics('./../assets/figures/plot_1mode_all.pdf')
-```
-
-```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_all_pubu_outst.pdf')
-```
-
-\end{landscape}
-
-\restoregeometry
-
-\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
-
-\newpage
-
-```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by all institutions, out-of-state visits only for public universities"}
-knitr::include_graphics('./../assets/figures/ego_network_figure_all_pubu_outst.pdf')
-#out.width="1.1\\linewidth", 
-```
-
-\begin{center}
-* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
-\end{center}

### 2021-05-18 scripts/network_recruiting_analysis.R

@@ -499,6 +499,12 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
   
   vertex_color <- recode(vertex_attr(network, 'cluster'), !!!color_palette)
   
+  # starting coordinates of graph
+    # layout_with_fr(g, coords); coords argument = "Optional starting positions for the vertices. If this argument is not NULL then it should be an appropriate matrix of starting coordinates"
+  coords_kk <- layout_with_kk(graph = network)
+    #print(coords_kk) # print layout_with_kk coordinates; these remain the same
+    #print(layout_with_fr(graph = network)) # print layout_with_fr coordinates; these change each time
+  
   # Plot graph
   plot(
     x = network, 
@@ -512,6 +518,7 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
     edge.width = log(as.numeric(E(network)$weight)/10),
     #edge.width = 1,
     edge.color = 'lightgrey',
+    cooords = coords_kk, # starting positions for vertices
     layout = layout,
     margin = margin
   )
@@ -526,18 +533,24 @@ save_plot(plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k
 
 # private colleges
 
-save_plot(plot_1mode_graph(g_2mode_privc, mode = 'psi', c_analysis = 'hclust', k = 5, colors = c('red', 'yellow', 'green', 'blue', 'purple')),
+save_plot(plot_1mode_graph(g_2mode_privc, mode = 'psi', c_analysis = 'hclust', k = 4),
           plot_name = 'plot_1mode_privc.pdf')
 
 # Public univs
 save_plot(plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 4),
           plot_name = 'plot_1mode_pubu.pdf')
-  plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 4, layout=layout_with_kk)
+
 
 # Public univs, out-of-state
 save_plot(plot_1mode_graph(g_2mode_pubu, mode = 'psi', pubu_visits = 'outofstate', c_analysis = 'hclust', k = 4),
           plot_name = 'plot_1mode_pubu_outst.pdf')
 
+# private and public universities
[…]

### 2021-05-19 text/tables_figures_may_2021.Rmd
draft changes results

@@
   )
+
+# enrollment
+  # pubu, privu, privc  
+  run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'g12_enroll', char_label = '12th grade enrollment', c('c1_lt50','c2_50to100','c3_100to150','c4_gt150'), c('LT 50','50-100','100-150','GT 150'))
+
+  #run_plot_characteristics(which_psi = c('pubu','privu','privc'), which_char = 'g12_enroll', char_label = '12th grade enrollment', c('c1_lt100','c2_100to150','c3_150to200','c4_gt200'), c('LT 100','100-150','150-200','GT 200'))
+
+  # pubu, privu
+  run_plot_characteristics(which_psi = c('pubu','privu'), which_char = 'g12_enroll', char_label = '12th grade enrollment', c('c1_lt50','c2_50to100','c3_100to150','c4_gt150'), c('LT 50','50-100','100-150','GT 150'))
+
 ```
@@
 ```{r ego-network-figure-region, fig.align = 'center', echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
-#knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu_privc.pdf')
-knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu.pdf')
+knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu_privc.pdf')
+#knitr::include_graphics('./../assets/figures/ego_network_figure_region_pubu_privu.pdf')
 ```
@@
 ```{r ego-network-figure-religion, fig.align = 'center', echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
-#knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu_privc.pdf')
-knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu.pdf')
+knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu_privc.pdf')
+#knitr::include_graphics('./../assets/figures/ego_network_figure_religion_pubu_privu.pdf')
+```
+
+\newpage
+
+```{r ego-network-figure-g12-enroll, fig.align = 'center', echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools"}
+knitr::include_graphics('./../assets/figures/ego_network_figure_g12_enroll_pubu_privu_privc.pdf')
+#knitr::include_graphics('./../assets/figures/ego_network_figure_g12_enroll_pubu_privu.pdf')
 ```
@@
 ```{r ego-network-figure-hs-rank, fig.align = 'center', echo = FALSE, fig.cap = "High school rank of visited private high schools"}
-#knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu_privc.pdf')
-knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu.pdf')
+knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu_privc.pdf')
+#knitr::include_graphics('./../assets/figures/ego_network_figure_hs_rank_pubu_privu.pdf')
 ```
@@
 ```{r ego-network-figure-race, fig.align = 'center', echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
-#knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu_privc.pdf')
-knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu.pdf')
+knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu_privc.pdf')
+#knitr::include_graphics('./../assets/figures/ego_network_figure_pct_black_latinx_native_pubu_privu.pdf')
 ```
@@
 <!-- RQ3: Overlapping sets of high schools -->
+
+\newpage
+
+```{r, echo = FALSE, eval = FALSE}
+g_1mode_pubu <- g_1mode_pubu_psi
+
+vertex_attr(graph=g_1mode_pubu, name='name') <- vertex_attr(graph=g_1mode_pubu, name='school_name')
+
+m_1mode_pubu <- as_adjacency_matrix(
+  #graph = g_1mode_u_psi,
+  graph = g_1mode_pubu,
+  type = "both",
+  attr="weight",
+  names = TRUE,
+  #edges = TRUE,
+  #sparse = igraph_opt("sparsematrices")
+  sparse = FALSE
+)
+
+m_1mode_pubu
+```
+
+```{r, echo = FALSE, eval = FALSE}
+g_1mode_privu <- g_1mode_privu_psi
+
+vertex_attr(graph=g_1mode_privu, name='name') <- vertex_attr(graph=g_1mode_privu, name='school_name')
+
+m_1mode_privu <- as_adjacency_matrix(
+  #graph = g_1mode_u_psi,
+  graph = g_1mode_privu,
+  type = "both",
+  attr="weight",
+  names = TRUE,
+  #edges = TRUE,
+  #sparse = igraph_opt("sparsematrices")
+  sparse = FALSE
+)
+
+m_1mode_privu
+```
 
@@
 
-```{r plot-1mode-privc, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private liberal arts colleges, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_privc.pdf')
-```
-
-```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
+```{r plot-1mode-u, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
 knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
@@
 
-```{r plot-1mode-all, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_all.pdf')
+```{r plot-2mode-u-k5, fig.align = 'center', echo = FALSE, eval = FALSE, out.width = "100%", fig.cap = "Two-mode network for public and private universities, colored by cluster, five clusters"}
+
+knitr::include_graphics('./../assets/figures/plot_2mode_u_k5.pdf')
+
+#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
+```
+
+```{r plot-1mode-privc, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private liberal arts colleges, colored by cluster"}
+# appendix
+knitr::include_graphics('./../assets/figures/plot_1mode_privc.pdf')
 ```
@@
 ```{r plot-1mode-all-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public universities, private universities, private liberal arts, colored by cluster, five clusters"}
+# appendix
 knitr::include_graphics('./../assets/figures/plot_1mode_all_k5.pdf')
@@
 
-```{r two-mode-plot, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
-# <!-- plot of two-mode network; exclude for now -->
-knitr::include_graphics('./../assets/figures/plot_2mode_all_region.pdf')
-
-#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
-```
-
 ```{r villanova-religion, fig.align = 'center', echo = FALSE, eval=FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}

### 2021-05-19 scripts/create_igraph_objects.R

@@ -87,9 +87,13 @@ privhs_data %>% group_by(year) %>% count()  # 105 from 2015-16, 144 from 2013-14
 # Select variables of interest from private HS data
 privhs_df <- privhs_data %>%
   mutate(type = 'priv hs', control = 'private') %>%
-  select(ncessch, name, city, state_code, region, religion, pct_white, pct_black, pct_hispanic, pct_asian, pct_amerindian, pct_nativehawaii, pct_tworaces, type, control)
+  select(ncessch, name, city, state_code, region, religion, pct_white, pct_black, pct_hispanic, pct_asian, pct_amerindian, pct_nativehawaii, pct_tworaces,total_12, type, control)
 val_labels(privhs_df$region)  # https://www2.census.gov/geo/pdfs/maps-data/maps/reference/us_regdiv.pdf
 
+
+#privhs_df %>% glimpse()
+#privhs_df %>% count(total_12) %>% print(n=350)
+  
 # Add ranking from Niche data
 niche_df <- niche_data %>% mutate(overall_niche_letter_grade = case_when(
   overall_niche_grade == 4.33 ~ 'A+',
@@ -120,6 +124,10 @@ privhs_universe <- privhs_data %>% left_join(dplyr::union(
 
 saveRDS(privhs_universe, file = str_c('./data/privhs_universe.RDS'))  # all 2017-18 + used schools from past years
 
+#privhs_universe %>% glimpse()
+#privhs_universe %>% count(total_12) %>% print(n=350)
+
+
 # Select variables of interest from univ data
 get_abbrev <- function(x, y) {
   univ_abbrev <- univ_info[univ_info$univ_id == x, ]$univ_abbrev
@@ -128,7 +136,7 @@ get_abbrev <- function(x, y) {
 v_get_abbrev <- Vectorize(get_abbrev, USE.NAMES = FALSE)
 
 univ_df <- univ_data %>% mutate(univ_abbrev = v_get_abbrev(univ_id, univ_name)) %>%
-  select(univ_id, univ_abbrev, city, state_code, region, religion, pct_white, pct_black, pct_hispanic, pct_asian, pct_amerindian, pct_nativehawaii, pct_tworaces)
[…]

### 2021-05-19 scripts/network_recruiting_analysis.R

@@ -55,6 +55,14 @@ ranking_values <- c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA')
 ranking_keys <- c('Rank top 200', 'A+', 'A', 'A- or below')
 ranking_title <- 'academic reputation'
 
+enroll1_values <- c('c1_lt50','c2_50to100','c3_100to150','c4_gt150')
+enroll1_keys <- c('LT 50','50-100','100-150','GT 150')
+enroll1_title <- '12th grade enrollment'
+
+enroll2_values <- c('c1_lt100','c2_100to150','c3_150to200','c4_gt200')
+enroll2_keys <- c('LT 100','100-150','150-200','GT 200')
+enroll2_title <- '12th grade enrollment'
+
 
 ## -------------------
 ## SAVE PLOT FUNCTION
@@ -317,8 +325,8 @@ create_fast_greedy <- function(twomode_network, mode, no = NULL, steps = NULL, p
 }
 
 # Usage
-create_fast_greedy(twomode_network = g_2mode, mode = 'psi', no = 4, plot_tree = TRUE)
-create_fast_greedy(twomode_network = g_2mode, mode = 'psi', steps = 38, plot_tree = TRUE)
+#create_fast_greedy(twomode_network = g_2mode, mode = 'psi', no = 4, plot_tree = TRUE)
+#create_fast_greedy(twomode_network = g_2mode, mode = 'psi', steps = 38, plot_tree = TRUE)
 
 
 ## ---------------------------
@@ -378,6 +386,13 @@ plot_2mode_graph <- function(twomode_network, c_analysis, k = NULL, h = NULL, no
     vertex_color <- recode(vertex_attr(twomode_network, c_analysis), !!!color_palette)
   }
   
+  
+  # starting coordinates of graph
+    # layout_with_fr(g, coords); coords argument = "Optional starting positions for the vertices. If this argument is not NULL then it should be an appropriate matrix of starting coordinates"
+  coords_kk <- layout_with_kk(graph = twomode_network)
+    #print(coords_kk) # print layout_with_kk coordinates; these remain the same
+    #print(layout_with_fr(graph = twomode_network)) # print layout_with_fr coordinates; these change each time
+  
   # Plot graph
   plot(
     x = twomode_network, 
@@ -389,6 +404,7 @@ plot_2mode_graph <- function(twomode_network, c_analysis, k = NULL, h = NULL, no
     edge.lty = 3,
     #edge.lty = 0.5,
[…]

### 2021-06-02 text/front_end_june_2021.Rmd
draft changes front end text

--- 2020-12-19 manuscript.Rmd
@@
   - Irma Castaneda
-bibliography: ./other/burd_recruiting_chapter.bib
+bibliography: ./../other/burd_recruiting_chapter.bib
 output: 
@@
     toc: FALSE
-csl: ./other/apa.csl
+csl: ./../other/apa.csl
 urlcolor: blue
@@
 
-<!-- 
-A pair of papers by Stevens provide interesting statements about the functions of higher education and the behavior of colleges and universities
-Colleges and universities visit high schools that enroll desirable prospects, while high schools accept visits from colleges and universities that offer enrollment opportunities valued by some segment of the class.
-Drawing from a pair of papers by Mitchell Stevens [@RN2377; @RN4517], we argue that analysis of which high schools receive visits from which colleges and univeristies provides an opportunity how K-12 and postsecondary organizations form relationships that serve social reproduction.
+Prior to the pandemic, admissions counselors from colleges and universities traveled to local high schools each year in order to meet prospective students and maintain relationships with guidance counselors at feeder schools [@RN3519].
+@RN4721 analyzed off-campus recruitiving visits made in 2017 by 15 public research universities.
+Surprisingly, 12 of the 15 universities made more visits to *out-of-state* high schools than *in-state* high schools.
+These out-of-state visits focused on public schools in affluent, predominantly white communities.
+Additionally, most public research universities in our sample made a disproportionate number of visits to out-of-state private high schools.
+For the University of California-Berkeley, for example, 155 (43%) of the 360 out-of-state high school visits were to private high schools.
+For the University of Colorado-Boulder, 321 (36%) of the 901 out-of-state high school visits were to private high schools.
 
--->
+Whereas @RN4721 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
+More specifically, we investigate how visits to private high schools by public research universities compare to visits to private high schools by selective private universities.
 
-This chapter presents a social network analysis of off-campus recruiting visits made by US colleges and universities to US private high schools.
-Colleges and universities visit high schools that enroll desirable prospects, while high schools accept visits from colleges and universities that offer enrollment opportunities valued by some segment of the class.
-An off-campus recruiting visit is an indicator of a relationship between a college and a school that can be analyzed using standard tools of social network analysis.
-We analyze visits made in 2017 from a sample of 25 selective private colleges and universities and a sample of 17 public research universities.
-Analyses investigate which types of private high schools receive visits from which types of colleges and universities, emphasizing comparisons within and between public and private postsecondary institutions.
+## Social mobility, social reproduction, and privatization
 
-The motivation for these analyses is grounded within the sociology of higher education, particularly two theoretical and empirical syntheses developed by Mitchell Stevens and colleagues [@RN2377; @RN4517].
-@RN2377 introduces metaphors that describe how sociology has conceived the functions of higher education.
-The stratification tradition conceives of higher education as a "sieve" -- an instrument that strains and separates -- that allocates people to occupational and social positions.
-This metaphor builds on "Max Weber's core insight that education has a dual character" [@RN2377, p.
-129], on one hand, serving social mobility by redistributing access to privileged positions and, on the other, serving social reproduction by granting privileged families disproportionate access to universities that confer privileged positions.
-The institutional theory tradition in sociology conceives of higher education as a "hub" that connects, pollinates, and legitimizes "prominent institutional sectors of modern societies" (e.g., professions, the philanthropic sector, corporate sector).
-As a hub, higher education is "simultaneously a powerful and fragile social institution.
-On the one hand, higher education [is powerful because it] connects and reciprocally blesses various forms of privilege.
-Elite groups (e.g., high-status families, professions, politicians, scientists, intellectuals) and those aspiring to be a part of them use higher education to certify their legitimacy" [@RN2377, p.
-137].
-On the other hand, higher education is fragile because it depends on "patronage as a primary source of revenue."
+The sociologist Max Weber is credited for the insight that education has a "dual character," on one hand, serving *social mobility* by redistributing access to privileged positions and, on the other, serving *social reproduction* by granting privileged families disproportionate access to the educational institutions that confer pathways to privileged positions [@RN2377].
 
-@RN4517 introduces three alternative metaphors to describe the relationship between higher education and the American political economy.
-The "association" conceptualization, observed by @RN485, views colleges as voluntary (i.e., non-governmental) organizations founded by voluntary associations -- principally religious congregations and local business interests -- that rely "on the collective contributions and goodwill of their memberships" [@RN2377, p.
-126].
-Second, the "national service" configuration views higher education as a public-good engine of economic development and nation building and thus worthy of investment from federal and state governments.
-Third, "market" configuration conceives of higher education as a private good, suggesting that colleges should survive by competing for customers rather than rely on public funding.
-Each of these configurations is more or less associated with particular historical epochs and particular types of colleges and universities.
-For example, the association configuration defined US higher education through the 19th century, but remains salient for private colleges and universities.
+The traditional, albeit mythologized, public good mission of public research universities is tied to social mobility and development of the state [@RN2269; @RN921].
+These institutions are designated the unique responsibility of educating the future civic, professional, and business leaders of the state.
+Quoting 19th century University of Michigan President James Angell, these institutions contribute to social mobility by providing “an uncommon education for the common man” [as cited in @RN3608, p.
+279] who could not afford tuition at elite private institutions.
 
-<!-- 
-The national service configuration is associated associated with massive public investment in higher education in the decades following World War II, while the market configuration is associated with declining state support for public universities since the 1980s.
+By contrast, the traditional mission of selective private colleges and universities is more squarely associated with reproduction.
+Historically, these institutions depend on patronage from philanthropic interests -- in connection with business interests and regligious congregations -- and depend on patronage from wealthy households who provide tuition revenue and donations [@RN4517].
+In turn, selective private institutions contribute to social reproduction by providing privileged access -- and the opportunities it confers -- to their wealthy patrons.
 
-These metaphors -- which describe higher education simultaneously serving social mobility and social reproduction and depending on patronage from the government, from voluntary associations, and private households -- are useful for comparing public flagship universities to selective private colleges and universities
--->
+Recruiting visits to private high schools are entirely consistent with the traditional social reproduction mission of selective private universities, regardless of whether the university is targeting a particular high school because of its academic reputation, religious affiliation, or the affluence of its student body.
+By contrast, visits to private high schools by public research universities -- and particularly to out-of-state private high schools -- particularly out-of-state schools -- are antithetical are antithetical to the public good mission of prioritizing meritorious state residents, particularly from humble means.
 
-These metaphors are useful for comparing public flagship universities to selective private colleges and universities.
-Selective private colleges and universities depend on patronage from affluent households (market configuration) and philanthropic interests (association configuration) and primarily serve social reproduction rather than social mobility.
-Historically, public flagship universities depended on government funding associated with the national service configuration and served social mobility rather than reproduction.
-Since the 1980s, reductions in public funding associated with the emergence of the market configuration encourage public flagship universities to prioritize patronage from affluent households and philanthropic interests.
-As suggested by the adage, "he who pays the piper calls the tune," reliance on affluent private-sector interests increases the likelihood that public flagship universities -- like selective private colleges and universities -- will primarily serve social reproduction rather than social mobility.
-<!-- 
-The extent to which higher education serves reproduction versus redistribution is sensitive to the external funding environment because universities depend on ``patronage as a primary revenue source'' [@RN2377, p.
-138].
--->
+We argue that an analysis of recruiting visits to private high schools can contribute novel insights about the "privatization" of public research universities to the interdisciplinary literature on privatization in the field of higher education research.
+One strand within this literature conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization [@RN4543@; @RN2101].
+Of relevance to this chapter, public research universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753], who typically pay two- to three-times more than resident students.
+Another strand within the privatization literature conceptualizes privatization as a process whereby public institutions become more similar -- in terms of characteristics or behavior -- to for-profit or private non-profit organizations [@RN4543].
+A weakness of this literature is that few empirical studies analyze public institutions on a behavior associated with private institutions.
 
-We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction.
-However, access to concrete data on university recruiting behaviors has been a persistent barrier to empirical research.
-We collected data on off-campus recruiting visits made in 2017 by "scraping" URLs (e.g., "Coming to a neighborhood near you") once per week from college/university admissions websites and -- for a sample of public research universities -- by issuing public records requests.
-The first study from this data collection analyzed visits made by 15 public research universities [@RN4450].
-The overwhelming majority of public research universities in our sample made more out-of-state visits than in-state visits, a finding antithetical to historic mission of public universities.
-These out-of-state visits focused on wealthy, predominantly white schools and communities, with a disproportionate number of visits to out-of-state private high schools but relatively few visits to in-state private high schools.
+This chapter compares public research universities to selective private universities on a behavior -- recruiting visits to private high schools -- that is consistent with the traditional mission of selective private institutions and antithetical to the traditional mission of public research universities.
+Empirical analyses are organized around the following three research questions:
 
-Building on @RN4450, this chapter analyzes off-campus recruiting visits to private high schools made in 2017 by a sample of 25 selective private colleges and universities and 17 public research universities.
-We utilize social network methods and emphasize comparisons within and between public and private postsecondary institutions.
-Analyses are informed by two broad, related questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what extent do colleges and universities visit private high schools that share similar characteristics with the college (e.g., geographic region, religious affiliation, academic reputation, and racial composition)?
+1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by private universities?
+1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by private universities?
+1. To what extent do public research universities and private universities visit overlapping sets of private high schools?
 
-<!-- 
-Our decision to compare public and private colleges/universities on the dimension of visits to private schools is motivated by the idea that recruiting from private high schools serves social reproduction rather than social mobility.
-
-Our decision to compare public and private colleges/universities on the dimension of visits to private schools is motivated by the idea that recruiting from private high schools serves social reproduction rather than social mobility.
-Thus, visits to private schools are antithetical to the historic mission of public universities, especially given that the vast majority of visits are to out-of-state private schools.
-By contrast, recruiting from private high schools is consistent with the mission of selective private colleges and universities.
-From this perspective, visits to private schools by public research universities is one example of "privatization." A weakness of the empirical literature on privatization in higher education is that few studies public and private colleges/universities with respect to a behavior associated with privatization [@RN4543].
-By comparing public and private colleges/universities on the behavioral dimension of recruiting visits to private schools, we hope to develop new insights about the privatization of public higher education.
-
--->
-
-Our decision to analyze visits to private schools is motivated by the idea that recruiting from private schools largely serves social reproduction<!-- [CITE A SOCIOLOGIST]-->.
-Thus, visits to private schools are antithetical to the historic "social mobility mission" of public universities [@RN2269], particularly since most private school visits by public research universities are to out-of-state schools [@RN4450].
-By contrast, recruiting from private high schools is consistent with the missions of selective private colleges and universities.
-From this perspective, private school visits by public research universities is an example of "privatization" that serves social reproduction.
-A weakness of the empirical literature on privatization in higher education is that few studies public and private colleges/universities with respect to a behavior associated with privatization [@RN4543].
-By comparing public and private colleges/universities on the behavioral dimension of recruiting visits to private schools, we hope to develop new insights about the privatization of public higher education.
-
-Finally, although private school students are more likely than public school students to come from affluent, college-educated households, the population of US private schools contains tremendous variation in religious affiliation, academic reputation, racial and socioeconomic composition, amongst other dimensions [@RN4504].
-Therefore, focusing solely on visits to private schools enables us to develop a nuanced analysis of which types of private high schools receive visits from which types of colleges and universities.
-These nuances would be difficult to observe in an analysis that also included visits to public high schools.
-
-<!-- 
-We use social network analysis (SNA) to analyze off-campus recruiting visits.
-The motivation for using SNA is that SNA privileges relationships between actorsQualitative scholarship on private high schools finds that college access is substantially determined by the quality of the relationship between a particular college and a particular private high school [@RN4321; @RN4407].
-An off-campus recruiting visit is an indicator of a relationship between a college and a school that can be analyzed using standard tools of SNA.
--->
-
-# What Do We Know About Off-Campus Recruiting?
-
-<!-- 
-This section provides context for our analyses by, first, situating off-campus visits within the broader set of marketing and recruiting interventions.
-Second, we review what is known about off-campus recruiting from market research and from academic scholarship, emphasizing scholarship that examines the relationship between private high schools and colleges/universities.
--->
+# What do we know about off-campus recruiting visits
 
@@
 
-<!--
-TEXT BRIEFLY DESCRIBING FINDINGS FROM DESCRIPTIVE TABLES.... Table/Figure X demonstrates the disproportionate number of visits to private high schools.
-
-WHAT TO SHOW IN TABLES/FIGURES:
-- Table/figure of number of visits by visit type and in/out-of-state
-- Table/figure showing disproportionate number of visits to private high schools.
--->
-
-# Network Methods and Data
-
-We utilize network methods rather than conventional descriptive statistics for two, related reasons.
-First, social network analysis privileges the relationship between actors.
-The discussion of Stevens and Khan suggests that for private school students, "it is not just the quality of the students that gets them into college but the quality of the relationship between elite high schools and colleges" [@RN4407, p.
-175].
-Second, a visit from a college/university admissions counselor to a high school can be conceived as a "network tie" connecting two actors in a social network.
-
-We briefly define essential social network analysis concepts and their operationalization in our analyses.
-A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "edges" between these actors.
-Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
-For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
-<!--The social network analyzed in this chapter is a two-mode network, where vertices consists of colleges/universities (mode 1) and high schools (mode 2), and an edge is defined as a visit from a college/university to a private high school [DELETE THIS SENTENCE OR THE REDUNDANT ONE IN BELOW PARAGRAPH].-->
-
-Our analyses draw from analyses of "corporate board-director" networks because these are the most commonly analyzed two-mode networks in the social networks literature [e.g., @RN4663].
-Board-director networks consist of directors (mode 1) who serve on organizational boards (mode 2).
-In our school-college two-mode network, the vertices are private high schools (mode 1) and colleges/universities (mode 2), and an edge is defined as an off-campus recruiting visits made between the two (e.g., high school $i$ shares an edge with college $j$ if high school $i$ receives at least one visit from college $j$).
-Visits can only occur between a school-college pair (not a school-school pair or a college-college pair).
-This (weighted) network can be represented as a school-by-college matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 colleges/universities) in which matrix cell $a_{i,j}$ identifies the number of visits that high school $i$ received from college/university $j$.
-<!--[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
-UNWEIGHTED SOMEWHERE]-->
-
-## Two-mode vs. One-mode networks
-
-Two-mode networks are often analyzed as one-mode networks [@RN2457].
-@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" (p.
-XXX).
-Thus, a two-mode board-director network can be transformed into two one-mode networks.
-A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ serve on three boards together).
-Similarly, a one-mode board network is created based on a board-by-board matrix in which two boards share an edge if a director sits on both boards and matrix cell $a_{i,j}$ identifies the number of directors that serve on both board $i$ and board $j$.
-Following this approach, we create a one-mode high school network in which two private high schools share an edge if they both receive a visit by the same college/university.
-Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of colleges/universities that visited both school $i$ and school $j$<!-- [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
-Similarly, we create a one-mode college/university network (herein the college network) in which two colleges share an edge if both colleges visited the same high school.
-Cell $c_{i,j}$ of the college-by-college matrix $C$ indicates the number of private high schools that received at least one visit from both college $i$ and college $j$<!-- [SHOW EXCERPT OF ONE-MODE COLLEGE BY COLLEGE MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
-
-## Ego networks
-
-A limitation of our data collection and analysis is that it is based on a convenience sample of 42 colleges and universities, as described above.
-Thus, for each college and university in our sample, we know all the private high schools they visited (assuming no measurement error).
-However, for each private high school in our sample, we only know visits they received from the set of 42 colleges/universities in our sample.
-Given this limitation, it may be useful to think of our data collection as resulting in 42 "ego networks." An "ego" is a single "focal" node (e.g., The University of Notre Dame).
-An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" (p.
-XXX)<!-- [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ]-->.
-For example, the University of Notre Dame ego network consists of all private high schools that received at least one visit from Notre Dame.
-Additionally, for each high school visited by Notre Dame, the ego network may include all colleges/universities in our sample that also visited the high school.
-
-When analyzing ego networks, researchers often investigate the extent of "homophily" versus "heterophily" [@RN1722].
-Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be friends on Facebook if they have similar political ideologies).
-Heterophily, the opposite of homophily, is when pairs of connected vertices have different characteristics from one another.
-In our analyses, we investigate the extent to which ego network ties are homophilous or heterophilous, focusing on the vertex characteristics of geographic region, religious affiliation, racial composition, and academic ranking.
-
-<!--
-
-Figure X shows the University of Notre Dame ego network, with separate panels for vertex characteristics (academic reputation, geography, religious affiliation, and racial composition) and with vertex shapes (?colors?) to identify values of vertex characteristics [INSERT FIGURE].
-Visually, we can see that ....[DESCRIBE BIG TAKEAWAYS].
-
-Figure X augments the Notre Dame ego network by including the private colleges/universities in our sample that visited private high schools visited by Notre Dame [INSERT FIGURE].
-ADD BRIEF TEXT ABOUT FIGURE?
-
--->
-
-## Community detection
-
-Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
-Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
-We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits.<!--We used XYZ community detection approach [add footnote w/ details?] to allocate private colleges and universities [?
-and private high schools] to clusters.-->
-
-# Network Analyses of Off-Campus Recruiting Visits
-
-This section presents network analyses of visits by colleges and universities to private high schools.
-Analyses are motivated by two, related research questions.
-First, which types of private high schools receive visits from which types of colleges and universities?
-Second, to what extent do off-campus recruiting visits by colleges and universities to private high schools exhibit homophily versus heterophily with respect to the vertex characteristics of geographic region, religious affiliation, academic reputation, and racial composition?
-
-[PARAGRAPH ABOUT TABLE THAT DESCRIBES CHARACTERISTICS OF VISITED VS. NON-VISITED PRIVATE SCHOOLS]
-Before proceeding to network analyses, Table/Figure X compares the characteristics of private high schools that received at least one recruiting visit from a college/university in our sample to those of private high schools that did not receive a visit.
-WHICH CHARACTERISTICS TO SHOW: geographic region; religious affiliation; academic reputation; racial composition; enrollment size.
-
-Figure \@ref(fig:two-mode-plot) plots the two-mode network of visits to private high schools by all colleges and universities in our sample, with large vertices indicating a college/university, small verticies indicating private high schools and with vertex color determined by geographic region (Northeast, Midwest, South, West).
-The graph layout places vertices closer together if they are similar to one another in terms of network structure.
-[SAY WHAT THIS MEANS, DRAWING FROM NOTES FROM RUSS].
-Figure \@ref(fig:two-mode-plot) suggests a modest relationship between geographic region and network structure.
-For instance, the high school vertices closest to University of Alabama and University of Arkansas tend to be located in the south.
-Further, universities located in the same geographic region (e.g., SUNY Stony Brook and Rutgers) tend to be closer to one another than universities located in other regions.
-However, this relationship is not consistent, for example, Scripps College located in CA is closest to University of Pittsburgh (PA) and Stevens Institute of Technology (NJ).
-Moreover, the network depicted by \@ref(fig:two-mode-plot) is too large to detect nuanced patterns of network structure.
-
-<!--
-Figure \@ref(fig:two-mode-plot) plots the two-mode network of visits to private high schools by all colleges and universities in our sample with private high schools vertices the color salmon, public research universities shown in violet, and private colleges and universities shown in green green.
-The graph layout places vertices closer together if they are similar to one another in terms of network structure.
-[SAY WHAT THIS MEANS, DRAWING FROM NOTES FROM RUSS].
-Figure \@ref(fig:two-mode-plot) suggests that the recruiting visit patterns of private colleges and universities tend to be more similar to one another than they are to those of public research universities.
-By contrast, many public research universities are far away from one another and a subset of public researchg universities appear to have network structure similar to many of the private colleges and universities (e.g., CU Boulder, UC Berkeley, University of South Carolina )
--->
-
-We present results in three steps: First, visits by private colleges and universities; second, visits by public research universities; and, third, comparisons of visits by public research universities to visits by private colleges and universities.
-
-## Visits by Private Colleges and Universities
-
-```{r, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego_privu.RDS')
-df %>% glimpse()
-df %>% select(ID,University,Cluster,total) %>% 
-  arrange(desc(Cluster),University) %>% print(n=30)
-```
-
-Figure \@ref(fig:plot-1mode-privu) plots the one-mode network of visits by private colleges and universities.
-Here, the number of ties between a pair of universities (e.g., Sewanee and Texas Christian University) equals the number of private high schools visited by both universities.
-The graph layout places colleges/universities closer together if they have similar network structure [MAYBE SAY WHAT THIS MEANS IF YOU HAVEN'T YET].
-Additionally, vertex color is determined by hierarchical cluster analysis specified to create $k = 4$ clusters.
-Although the process of placing vertices was separate from the process of determining community cluster, vertices within the same cluster tend to be closer to one another than those of different clusters.
-
-One cluster consists of Notre Dame, Villanova, Tulane, and Southern Methodist University.
-Each of these four universities made a relatively high number of visits to private high schools and are relatively centrally located in Figure \@ref(fig:plot-1mode-privu).
-
-Addressing our two motivating research questions -- which schools receive visits from which colleges/universities and the extent to which visits are more likely to occur between organizations that share certain characteristics -- requires analyses that are more granular than Figure \@ref(fig:plot-1mode-privu).
-Figure \@ref(fig:ego-network-figure-privu) shows characteristics of private high schools visited our sample of private colleges and universities, specifically, geographic region, religious affiliation, academic reputation, and racial composition.
-
-Figure \@ref(fig:ego-network-figure-privu) indicates that Notre Dame, Villanova, Tulane, and Southern Methodist University made a large share of visits in the South and the Northeast.
-With respect to religious affiliation, Notre Dame and Villanova -- both Catholic universities -- predictably focused visits on Catholic Schools.
-However, Tulane and SMU also visited a higher share of Catholic schools than most other private colleges and universities.
-These four universities also visited a lower share of private schools ranked in the top 200 nationally by Niche.
-
-Figure \@ref(fig:ego-network-figure-privu) was created from the ego network of each private college and university.
-Ego networks consist of an ego (e.g., a single college or university), the set of high schools the ego visted (one degree of separation from the ego), and the set of colleges/universities that also visited high schools visited by the ego (two degrees of separation from the ego).
-Figure \@ref(fig:villanova-religion) plots the ego network of Villanova University, with vertex color determined by religious affiliation.
-About 50% of Villanova's visits were to Catholic schools, a percentage [?percent?] much higher than most colleges and universities shown in Figure \@ref(fig:ego-network-figure-privu), and second only to Notre Dame University.
-In Figure \@ref(fig:villanova-religion), Notre Dame is closer to Villanova than any other college/university in the Villanova ego network, suggesting that Villanova and Notre Dame visit substantially overlapping sets of schools.
-Boston College, another Catholic university, is situated a bit further away from Villanova in the clump of colleges that includes Case Western, Tulane, Sewanee, Southern Methodist, and TCU, most of which visit relatively high share of Catholic high schools.
-By contrast, Villanova is far from nonsectarian liberal arts colleges (e.g., Swarthmore, Smith, Colorado College) which visit fewer Catholic high schools.
-
-A second cluster consits of Boston College, Colorado College, Connecticut College, Emory University, Middlebury, Northwestern Oberlin, Sewanee, Texas Christian University, Tufts, and the University of Denver.
-This institutions also tend to be located relatively centrally in Figure \@ref(fig:plot-1mode-privu), indicating that many of the high schools they visit are also visited by many private colleges and universities in our sample.
-Compared to the first cluster, these institutions have a stronger focus on nonsectarian private high schools, with the exception of Boston College, Texas Christian, and Sewanee.
-The also tended to visit schools with relatively strong academic reputations.
-
-Figure \@ref(fig:emory-region) shows the ego network of Emory University, with vertex color determined by geographic region.
-Located in Atlanta, about 47% of Emory's visits were to schools in the South.
-Figure \@ref(fig:emory-region) indicates that Emory's network structure is similar to several other southern universities -- including Tulane, TCU, SMU, and Sewanee, but is dissimilar from Baylor University which made about 56% of visits in the South, but with a focus on schools with a Christian religious affiliation.
-Figure \@ref(fig:emory-region) also suggests that the set of schools visited by Emory overlaps substantially with several institutions located in the Northeast (e.g., Villanova, Boston College, Middlebury) and the Midwest (e.g., Case Western Reserve, Northwestern, Notre Dame).
-
-A third cluster consists of Case Western Reserve, MaCalester, Occidental, Smith, Swarthmore, and Williams.
-These institutions made relatively fewer visits than institutions in the first two clusters and are located relatively peripherally in the one-mode network, as shown in Figure \@ref(fig:plot-1mode-privu).
-With the exception of Case Western Reserve, these institutions are liberal arts colleges rather than research universities.
-They tended to visit a high share of nonsectarian private high schools and also a high share of schools ranked in the top 200 nationally by Niche.
-
-The final cluster consists of Baylor, Harvey Mudd, Scripps, and Stevens Institute of Technology.
-Figure \@ref(fig:plot-1mode-privu) indicates that all four institutions are rather peripheral to the network.
-Harvey Mudd, Scripps, and Stevens made relatively few visits to private high schools.
-By contrast, Baylor visited a fundamentally different set of schools than other private colleges and universities in that Baylor visited a large number of Christian private schools that were not visited by other private colleges and universities in the sample.
-Overall, these four institutions form a group more because they are peripheral to the overall network as opposed to having similar network structures to one another.
-
-Finally, we comment on the racial composition -- defined here as the percent of students who identify as Black, Latinx, or Native -- of private high schools visited by private colleges and universities in our sample.
-Figure \@ref(fig:ego-network-figure-privu) shows substantial variation across and within clusters in the geographic region, religious affiliation, and academic reputation of visited private schools.
-By contrast, the racial composition of visited private high schools was remarkably similar.
-On average, about one-third of visits were to schools where Black/Latinx/Native students comprised less than 10% of the student body, about 50% of visits were to schools where Black/Latinx/Native students comprised between 10% and 25% of the student body, and about 15% of visits were to schools where Black/Latinx/Native students comprsied more than 25% of the student body.
-Some colleges (e.g., Williams and Swarthmore) were better than others (e.g., Emory, Sewanee) at visiting schools where Black/Latinx/Native students comprised more than 50% of the population, but these visits to very diverse private schools represented a small share of all visits to private schools.
-The overall results suggest that when private colleges and universities visit private high schools, they are usually visiting schools that enroll few Black, Latinx, or Native students.
-
-[HOW DOES RACIAL COMPOSITION OF VISITED PRIVATE HIGH SCHOOLS COMPARE TO RACIAL COMPOSITION OF ALL PRIVATE HIGH SCHOOLS?
-CUT/REVISE TEXT DEPENDING ON ANSWER TO THIS QUESTION] See Figure \@ref(fig:privhs-universe).
-Private high schools tend to have a higher share of White students than public high schools.
-Moreover, the private high schools that were visited by private colleges and universities in our sample had a lower share of Black/Latinx/Native students, on average, than the population of private high schools.
-Our findings suggest that the low number of Black/Latinx/Native students at private colleges and universities may be driven by thse institutions explicitly recruiting from private high schools that enroll few Black/Latinx/Native students.
-
-[NEED TRANSITION TO FOCUS NOW ON HIGH SCHOOLS] Which private high schools received the most visits from private colleges and universities in our sample?
-Table \@ref(tab:hs-print-privu) shows characteristics of the 20 private high schools that were visited by the most private colleges and universities.
-The last two columns of Table \@ref(tab:hs-print-privu) are "degree" and "strength," which are related measures of vertex "centrality." Measures of centrality attempt to identify the most important or influential actors in a social network.
-"Degree" is defined as the number of edges direclty connected to a vertex.
-In Table \@ref(tab:hs-print-privu), the degree of a high school is the number of private colleges and universities in our sample that visited.
-The concept "strength" is generally defined as a weighted measure of degree.
-In our study, colleges often made more than one visit to the same high school in 2017.
-Thus, Table \@ref(tab:hs-print-privu) defines strength as the total number of visits from private colleges and universities in our sample.
-
-The Kent Denver School, the top ranked school in \@ref(tab:hs-print-privu),was visited by 23 of the 26 private colleges and universities in our sample.
-Choate Rosemary Hall was visited by 21 colleges and universities, but these 21 institutions made 34 total visits.
-Most schools in Table \@ref(tab:hs-print-privu) are mostly nonsectarian.
-Although all received a Niche grade of "A+", they are not uniformly in the upper-echelon of schools ranked in the top 100 nationwide.
-With the exception of St.
-Ignatius Prep in Chicago and the Maret School in Washington DC, students who identify as Black, Latinx, or Native comprise less than 20% of all students.
-
-Table \@ref(tab:hs-table-privu-agg) shows the characteristics of private high schools by degree band (e.g., visits from 15+, 10-14, etc).
-Schools that received visits from 4 or fewer private colleges and universities enrolled a greater share of Black/Latinx/Native students.
-These schools were also disproportionately Catholic schools and were more likely to recieve a grade of "A" or lower from Niche.
-
-Whereas Tables \@ref(tab:hs-print-privu) and \@ref(tab:hs-table-privu-agg) examine centrality, they do not assess the extent to which high schools cluster into groups, with some high schools visited by nearly all colleges and universities and other groups of high schools only receiving visits from a particular subset of colleges and universities.
-[THIS IS WHERE THE DIRECT VS.
-INDIRECT CONNECTION ANALYSIS RECOMMENDED BY RUSS WOULD GO.
-WE MIGHT ADD THIS TO BURD CHAPTER OR DO AFTER BURD CHAPTER SUBMITTED]
-
-## Visits by Public Research Universities
-
-```{r, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego_pubu.RDS')
-df %>% glimpse()
-df %>% select(ID,University,Cluster,Rank,total, in_state, out_state) %>% 
-  arrange(Cluster,desc(total)) %>% print(n=30)
-```
-
-Figure \@ref(fig:plot-1mode-pubu) plots the one-mode network of visits by 17 public research universities, with vertex color determined by hierarchical cluster analysis specified to create $k = 4$ clusters.
-Accompanying Figure \@ref(fig:plot-1mode-pubu) and created from the respective ego networks of each university is Figure \@ref(fig:ego-network-figure-pubu), which shows the characteristics of private high schools visited by these public reearch universities.
-
-We briefly sketch broad findings before discussing each cluster.
-First, for must public research universities in our sample, the vast majority of private school visits were to out-of-state schools [WHICH FIGURE/TABLE SHOWS THIS], which is consistent with the idea that public research universities pursue students from affluent households who can afford nonresident tuition price.
-Second, Figure \@ref(fig:ego-network-figure-pubu) indicates that public research universities tended to visit private high schools with weaker academic reputation than the set of schools visited by private colleges and universities [LATER, SAY GOING AFTER MONEY WITHOUT ACADEMIC REP].
-Third, despite being nonsectarian, most public research universities visited a higher share of private high schools that were Catholic or Chrisitan than those visited by private colleges and universities.
-Fourth, racial composition of schools visited by public research universities was similar to the set of schools visited by private colleges and universities.
-A few public research universities appear (e.g., UC Irvine, UC Riverside) appear to visit a more racially diverse set of schools, but these institutions visited very few private schools.
-
-<!--
-Truly singular in the realm of recruiting, the University of Alabama is a cluster unto itself
--->
-
-The University of Alabama is a cluster unto itself and is centrally located in the network graph in Figure \@ref(fig:plot-1mode-pubu).
-In 2017, the University of Alabama made 985 visits to U.S.
-private high schools.
-This number was more than double the 486 visits made by the University of South Carolina, which ranked second amongst public research universities in terms of number of private school visits, and substantially more than the 687 visits made by Notre Dame, which ranked first amongst private colleges and universities.
-Drawing from Figure \@ref(fig:ego-network-figure-pubu), more than 50% of visits by the University of Alabama were in the South.
-With respect to religious affiliation, nearly 50% of visits were to Catholic schools and about 25% of visits were to Christian schools.
-In contrast to the majority of private colleges and universities in our sample, the University of Alabama made nearly 50% of its visits at schools that received a grade of less than "A+" by Niche.
-At the same time 80% of visited schools enrolled fewer than 25% of students who identified as Black, Latinx, or Native.
-
-A second cluster, located nearly as centrally in Figure \@ref(fig:plot-1mode-pubu) as the University of Alabama, consists of the University of South Carolina (486 visits) and the University of Colorado-Boulder (379 visits).
-These institutions ranked second and third amongst public universities in our sample in terms of number of visits.
-Geographically, both universities recruiting nationally but concentrated on some regions more than others.
-For both universities, the Northeast and Midwest accounted for about 25% of visits.
-The University of South Carolina concentrated visits in its home region, the South.
-CU-Boulder made X% of visits in its home region, the West, and made X% of visits in the South.
-Both universities made more than 60% of visits at Catholic or Christian affiliated schools.
-In terms of academic reputation, CU-Boulder visited a slightly stronger set of schools than the University of South Carolina and both universities visited a stronger set of schools than the University of Alabama.
-
-Third, the largest cluster -- at nine universities -- and the most diverse in terms of geographic location and academic reputation consists of three universities from the Northeast (Rutgers, UMass Amherst, University of Pittsburgh), two Midwest universities (University of Cincinnati, University of Kansas), two universities in the South (University of Arkansas, University of Georgia), and two universities from the West (UC Berkeley, UC San Diego).
-Located between the center and periphery in Figure \@ref(fig:plot-1mode-pubu), these universities made a moderate number of private school visits, ranging from 197 by UC-San Diego to 302 and 303, respectively, by the University of Georgia and Rutgers.
-
-These universities differ in the extent to which visits were concentrated in their home geographic region.
-At the high end, the University of Georgia -- 47th in YYYY US News rankings -- and the University of Arkansas -- 160th in US News rankings -- are located in the South and made at least 75% of visits in the South.
-The remaining seven universities generally made more visits in their home geographic than other regions but while also making substantial visits outside their home region, particularly in the South.
-For example, three highly ranked universities -- University of Pittsburgh (ranked 58), UC-Berkeley (ranked 22), and UC-San Diego  (ranked 35) each made a substantial share of visits in the South.
-In contrast to private colleges and universities, several public research universities in this cluster largely ignored particular geographic regions altogether.
-For example, the University of Kansas and the University of Arkansas did not visit the Northeast.
-The University of Georgia, UC-San Diego, and UMass Amherst largely ignored the MidWest, while the University of Pittsburgh did not visit the West.
-
-With the exception of UC-Berkeley, the universities in this cluster made more than 50% of visits to sectarian Catholic or Christian affiliated schools.
-Universities that made a substantial share of visits to Christian affiliated schools also tended to make a large share of visits in the share of visits in the South [OVERLAP BETWEEN SOUTH AND CHRISTIAN].
-Finally, with the exception of UC-Berkeley, UC-San Diego, and to a lesser extent the University of Georgia -- three highly ranked universities -- the academic repuation of schools visited by this cluster was substantially lower than those visited by the majority of private colleges and universities in our sample.
-These results suggest that non-prestigious public research universities visit a large number non-elite private high schools that generally did not receive visits from selective private colleges and universities.
-
-The final cluster consists of five universities -- University of Nebraska-Lincoln (159 visits, 104 out-of-state), SUNY Stony Brook (146 visits, 107 out-of-state), UC Riverside (87 visits, 32 out-of-state), UC Irvine (60 visits, 40 out-of-state), North Carolina State University  (23 visits, 20 out-of-state).
-These universities made fewer private school visits than the other public research universities, made a relatively higher share of in-state visits, and generally concentrated visits within their home geographic region.
-As such, they are located on the periphery of the network in Figure \@ref(fig:plot-1mode-pubu).
-
-<!-- reminder of RQs: 
-1. which schools receive visits from which colleges/universities? 
-2. to what extent are visits more likely to occur between organizations that share certain characteristics
--->
-
-Transitioning from the focus on public research universities to a focus on the private high schools they visit, Table \@ref(tab:hs-print-pubu) shows the characteristics of the 20 private high schools that received visits from the greatest number of public research universities in our sample.
-
-The top five high schools in  Table \@ref(tab:hs-print-pubu) each received visits from 11 (i.e., "degree" equals 11) of the 17 public research universities in our sample.
-Notably, all five schools were located in either California and Texas.
-Four of these schools are Catholic and one -- The Greenhill School -- is nonsectarian.
-These five schools differed in terms of the number of visits received.
-For example, both Jesuit College Prep in Dallas, TX and Santa Margarita Catholic High School in Rancho Santa Margarita, CA received 19 visits from 11 public research universities, while Cathedral Catholic High School in San Diego, CA received 13 visits from 11 public research universities [SAY SOMETHING ABOUT WHICH PUBLIC [OR PRIVATE] UNIVERSITIES VISITED THESE HIGH SCHOOLS?
-THIS CODE BELOW DOES THAT WORK IF YOU WANT TO INCLUDE IT; MAYBE SHOW EGO NETWORK OF A COUPLE HIGH SCHOOLS?]
-
-```{r, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)
-df %>% select(name, school_name, degree, strength)
-
-events_data %>% glimpse()
-events_data %>% left_join(y = univ_info, by = c("univ_id")) %>% count(control)
-
-# this shows which universities visited the top 5 high schools most visited by public resarch universities in our sample
-  # can filter on "control" below to show visits by public and/or private universities
-    # "Public"
-    # "Private not-for-profit"
-events_data %>% left_join(y = univ_info, by = c("univ_id")) %>% 
-  filter(event_type == "priv_hs", control == "Private not-for-profit") %>% 
-  filter(school_id %in% c("01324487","02187540","00071446","A0900259","A0109386")) %>% 
-  left_join(y = privhs_df, by = c("school_id")) %>% 
-  arrange(school_id, univ_id) %>%
-  select(school_id, school_name, event_state,univ_id, univ_name)
-```
-The set of schools visited by the greatest number of public research universities from our sample differs substanitally from the schools visited by the greatest number of private colleges and universities.
-Only four of the 20 schools in \@ref(tab:hs-print-pubu) were also in the anologous table for private colleges and universities (Table \@ref(tab:hs-print-privu)), specifically the Greenhill School in Addison, TX, Episcopal High School in Alexandria, VA, St.
-Ignatius College Prep in Chicago, IL, and the McDonogh School in Owings Mills, MD.
-Compared the top 20 private schools most visited by private colleges and universities, the 20 most-visited schools by public research universities were more likely to be Catholic schools and they had substantially lower academic reputations.
-Of the 20 schools in Table \@ref(tab:hs-print-pubu), only one -- The Greenhill School in Addison, TX, ranked 64 -- was ranked in the top 100 nationally by Niche.
-By contrast, of the 20 schools most visited by private colleges and universities, nine were ranked in the top 100 by Niche.
-
-```{r, include = FALSE, eval = FALSE}
-# which schools in top 20 most visited by public universities were also top 20 most visited by private colleges and universities
-df_pubu <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20) %>% rename(degree_pub = degree, strength_pub = strength)
-df_privu <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20) %>% rename(degree_priv = degree, strength_priv = strength )
-
-df_pubu %>% glimpse()
-
-df_privu %>% select(name, degree_priv, strength_priv) %>% right_join(y = df_pubu, by = c("name")) %>%
-  select(name, school_name, city, state_code, degree_pub, strength_pub, degree_priv, strength_priv, religion_4, pct_blacklatinxnative, ranking, ranking_numeric)
-```
-
-The top 20 most-visited schools by public research universities enrolled a somewhat higher percentage of students who identify as Black/Latinx/Native than the schools most-visited by private colleges and universities.
-For example, of the top-20 schools most visited by public research universities, there were five schools where students who identify as Black, Latinx, or Native represent at least 30% of student enrollment.
-By contrast, none of the top-20 schools most visited by private colleges and universities enrolled at least 30% of students who identify as Black, Latinx, or Native.
-
-```{r, include = FALSE, eval = FALSE}
-df_pubu <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)
-df_pubu %>% filter(pct_blacklatinxnative>=30)
-
-df_privu <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20) 
-df_privu %>% filter(pct_blacklatinxnative>=30)
-```
-Table \@ref(tab:hs-table-pubu-agg) shows the characteristics of private high schools by number of public research universities that visited (e.g., 6+, 5, 4, etc.).
-Compared to schools that received visits from three or fewer public research universities, schools that received visits from several public research universities were disproportionaly located in the South, were more likely to be Catholic schools than Christian or nonsectarian, and were likely to be ranked in the top 200 by Niche or be graded as "A+" by Niche.
-
-## Comparison of Public Versus Private Colleges and Universities
-
-```{r, include = FALSE, eval = FALSE}
-# check to make sure ego table that exludes in-state events by public universities is correct
-df_all <- readRDS('./assets/tables/table_ego_all.RDS')
-df_all_pubu_outst <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
-
-df_all %>% glimpse()
-df_all_pubu_outst %>% glimpse()
-
-df_all %>% count(Cluster)
-df_all_pubu_outst %>% count(Cluster)
-
-df_all %>% arrange(ID) %>% filter(Type == "univ") %>% select(ID,University,total,Northeast,Midwest,South,West,Catholic,Christian,Nonsect,Other) %>% 
-   print(n=50)
-
-df_all_pubu_outst %>% arrange(ID) %>% filter(Type == "univ") %>% select(ID,University,total,Northeast,Midwest,South,West,Catholic,Christian,Nonsect,Other) %>% 
-   print(n=50)
-```
-
-<!-- reminder of RQs:
-
-1. which schools receive visits from which colleges/universities? 
-2. to what extent are visits more likely to occur between organizations that share certain characteristics
-
--->
-
-We conclude by comparing the off-campus recruiting visits to private high schools by public research universities to those of private colleges and universities.
-
-For these analyses, we include both in-state and out-of-state visits made by private colleges and universities but we exclude in-state visits by public research universities but we do not exclude.
-The motivation for this decision is as follows.
-For most public research universities in our sample, the overwhelming majority of visits to private schools are to out-of-state private schools.
-Prior research suggests that nonresident enrollment growth by public research universities is substantially motivated by the goal of growing tuition revenue [CITE].
-Typically, nonresident tuition price at public research universities is substantially higher than resident tuition price but lower than the price charged by selective private colleges and universities (e.g., in 2018-19 fulltime annual resident tuition price at the University of Colorad-Boulder was \$10,728, compared to nonresident tuition price of \$35,482, compared to tuition price of $54,120 at Northwestern University).
-We argue that the pursuit of out-of-state students by public universities is an example of "privatization" because out-of-state enrollment is antithetical to the traditional mission of public universities but is consistent with the mission of private colleges and universities.
-Furthermore, we argue that out-of-state recruiting efforts by public research universities focus on affluent households who are also considering private colleges and universities.
-Therefore, comparing recruiting visits by private colleges and universities to out-of-state visits by public research universities provides a helpful test of the extent to which public institutions are mimicking the behavior of private institutions.
-<!-- tuition price numbers from here:
-https://www.collegesimply.com/colleges/search
--->
-Figure \@ref(fig:plot-1mode-pubu) plots the one-mode network of visits by the 42 public and private colleges and universities in our sample, with vertex color determined by hierarchical cluster analysis specified to create $k = 4$ clusters.
-Figure \@ref(ego-network-figure-all-pubu-outst) shows the characteristics of private high schools visited by these 42 institutions, sorted by cluster.
-Of the four clusters from Figures \@ref(fig:plot-1mode-pubu) and \@ref(ego-network-figure-all-pubu-outst), one contains solely of public research universities, one contains solely of private colleges and universities, and two contain a mix of private and public institutions.
-
-The public-only cluster consists of five institutions: North Carolina State University, SUNY Stony Brook, UC Irvine, UC Riverside, and the Unviersity of Nebraska-Lincoln.
-These universities made relatively few (out-of-state) visits to private high schools -- ranging from 20 by NC State to 107 by SUNY Stony Brook -- and, thus, are located on the periphery of the network in Figure \@ref(fig:plot-1mode-pubu).
-The private-only cluster consists of 13 institutions: Case Western Reserve, Colorado College, Connecticut College, Emory University, Macalester, Middlebury, Oberlin, Occidental, Smith, Swarthmore, Tufts, University of Denver, Williams.
-This cluster contains nine liberal arts colleges and four universities (U of Denver, Emory, Tufts, Case Western Reserve).
-Geographically, six of these institutions are located in the Northeast, three in the Midwest, two in the West, and one in the South.
-Compared to other postsecondary institutions in our sample, the colleges in this cluster made a moderate number of private school visits, ranging from 164 visits by Smith to 337 by Oberlin.
-Drawing from \@ref(ego-network-figure-all-pubu-outst), visits were spread out geographically rather than concentrated in a particular region.
-The majority of visits were to nonsectarian schools.
-Compared to other clusters, these colleges visited schools with strong academic reputations.
-
-We devote more attention to the two clusters that contain a mix of public and private postsecondary institutions.
-The first of these contains 11 institutions, including eight private universities (Boston College, Northwestern University, Notre Dame, Sewanee, Southern Methodist, Texas Christian University, Tulane, Villanova) and three public research universities (University of Alabama, University of Colorado-Boulder, University of South Carolina).
-The universities in this cluster made, relatively, a very high number of private school visits -- ranging from 333 by Boston College to 931 (out-of-state) visits by the University of Alabama -- and are located in the center of the network in Figure \@ref(fig:plot-1mode-pubu).
-Geographically, five of these institutions are located in the South, two in the Northeast, two in the Midwest, and one in the West.
-\@ref(ego-network-figure-all-pubu-outst) shows that most of these institutions -- even those not located in the South -- made a disproportionate number of recruiting visits in the South.
-This cluster contains three private Catholic universities (Notre Dame, Villanova, Boston College), which visited a relatively high share of Catholic Schools, and X private Christian universities (Sewanee, Southern Methodist, Texas Christian), which visited a relatively high share of Christian affiliated schools.
-More notable, however, is the extent to which the three public research universities focused visits on Catholic or Christian private schools.
-Finally, the universities in this cluster -- albeit to a less extent for Boston College, Northwestern, and Tulane -- visited private high schools with weaker academic reputations than those visited by the cluster of 13 private colleges and universities.
-The weak academic reputation of schools visited by Notre Dame -- similar to those visited by the University of Alabama and the University of South Carolina -- is surprising given that Notre Dame is ranked 19th by US News.
-
-The final cluster contains 13 institutions, including nine public research universities (U.
-of Arkansas, U.
-of Cincinnati, U.
-of Georgia, U.
-of Kansas, U.
-of Pittsburgh, UC-Berkeley, UC-San Diego, and UMass Amherst) and four private institutions (Harvey Mudd, Scripps, Stevens Institute of Technology, and Baylor).
-The universities in this cluster made a moderate number of private school visits -- ranging from 111 by Scripps to 257 by Baylor -- and are located between the center and the periphery of the network in Figure \@ref(fig:plot-1mode-pubu).
-Whereas, the public and private institutions in the previous cluster (e.g., University of Alabama and Notre Dame) were clearly similar to one another in recruiting patterns, the similarities between public and private institutions in this cluster are less clear.
-Interestingly, in our analyses of visits by private colleges and universities (above), these four private institutiosn were their own cluster and were on the periphery of the network.
-Geographically, these institutions are spread across the country, with recruiting visits concentrated in their home region and often in the South.
-[COMMENT ON SIMILARITIES BETWEEN PUBLIC AND PRIVATE W/ RESPECT TO REGION/RELIGION, ACADEMIC REPUTATION]
-
-# Discussion
-
-TEXT LA LA 
-<!--
-
-Each of these marketing/recruiting interventions -- and dozens of other interventions described in this book -- represent organizational behaviors that could be the subject of empirical research.
-
-When we consider descriptions of enrollment management practice from investigative journalism [e.g., ], from enrollment management consulting firms and from this volume [e.g., ], it becomes apparent that -- with the notable exception of a small sociological case-study literature [e.g., ] -- the research community has ignores a great number of enrollment management practices that plausibly affect access to higher education.
-As a consequence, enrollment management remains an opaque industry to policymakers and the public.
-We argue that developing thoughtful policies about enrollment management depends on researchers collectively devloping empirical literatures that document enrollment management practices and evaluate the effects of these practices on opportunities for students.
-
-Access to concrete data about marketing and recruiting behaviors has been a persistent barrier to empirical research.
-To the extent that marketing/recruiting behaviors are inconsistent with public relations rhetoric (e.g., "our commitment to access"), colleges and universities may have incentive to withhold data from researchers.
-Therefore, conventional data collection methods such as surveys and even interviews should be appraised with healthy skepticism.
-We argue that pushing forward an empirical research agenda on marketing/recruiting behaviors depends on different modes of data collection -- including public records requests and "data science" methodologies, such as web-scraping and streaming social media data -- that record actual behaviors (e.g., contracts, transactions, records of expenditure) as opposed to statements by colleges/universities about their behavior.
-
--->
-
-```{r, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
-
-# cluster 2; public and private
-df %>% filter(Cluster ==2) %>% select(ID, University, Type, Rank, control, total, in_state, out_state) %>% arrange(total)
-df %>% filter(Cluster ==2) %>% count(Type)
-df %>% filter(Cluster ==2) %>% count(control)
-```
-
-```{r, include = FALSE, eval = FALSE}
-df <- readRDS('./assets/tables/table_ego_all_pubu_outst.RDS')
-
-# cluster 2; public and private
-df %>% filter(Cluster ==2) %>% select(ID, University, Type, Rank, control, total, in_state, out_state) %>% arrange(total)
-df %>% filter(Cluster ==2) %>% count(Type)
-df %>% filter(Cluster ==2) %>% count(control)
-
-# cluster 1; public and private
-df %>% filter(Cluster ==1) %>% select(ID, University, Type, Rank, total, in_state, out_state) %>% arrange(total)
-df %>% filter(Cluster ==1) %>% count(Type)
-
-# cluster 4; private only
-df %>% filter(Cluster ==4) %>% select(ID, University, Type, Rank, total, in_state, out_state) %>% arrange(total)
-df %>% filter(Cluster ==4) %>% count(Type)
-df %>% filter(Cluster ==4, Type == "univ") %>% select(ID, University, Type, Rank, total, in_state, out_state)
-
-# cluster 3; public only 
-df %>% filter(Cluster ==3) %>% select(ID, University, Type, Rank, total, in_state, out_state) %>% arrange(total)
-df %>% filter(Cluster ==4) %>% count(Type)
-df %>% filter(Cluster ==4, Type == "univ") %>% select(ID, University, Type, Rank, total, in_state, out_state)
-
-```
-
-# Summary and Discussion
-
-[ADD SUCCINCT, CONCRETE SUMMARY FOCUSING ON BIG FINDINGS AND THEMES; VERY BRIEF DISCUSSION]
+ADD TABLE OF UNIVERSITY CHARACTERISTICS HERE
 
@@
 
-<!-- private col/univ -->
-
-```{r hs-print-privu, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode_privu.RDS') %>% head(n=20)
-
-knitr::kable(
-  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by private institutions') %>% 
-  landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r hs-table-privu-agg, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode_agg_privu.RDS')
-
-knitr::kable(df, caption = 'Characteristics of private HS visited by private institutions, by degree band') %>% 
-  landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-<!-- public research universities -->
-
-```{r hs-print-pubu, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode_pubu.RDS') %>% head(n=20)
-
-knitr::kable(
-  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by public institutions') %>% 
-  landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r hs-table-pubu-agg, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode_agg_pubu.RDS')
-
-knitr::kable(df, caption = 'Characteristics of private HS visited by public institutions, by degree band') %>% 
-  landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-<!-- public and private col/univ -->
-
-```{r hs-print-both, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode_both.RDS') %>% head(n=20)
-
-knitr::kable(
-  df %>% select(-name,-closeness), caption = 'Top 20 most central private HS visited by all institutions') %>% 
-  landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r hs-table-both-agg, echo = FALSE}
-df <- readRDS('./assets/tables/table_2mode_agg_both.RDS')
-
-knitr::kable(df, caption = 'Characteristics of private HS visited by all institutions, by degree band') %>% 
-  landscape(margin = NULL) %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
 <!-- FIGURES -->
@@
 ```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%"}
-knitr::include_graphics('assets/images/enrollment_funnel.png')
+knitr::include_graphics('./../assets/images/enrollment_funnel.png')
 #![The enrollment funnel](assets/images/enrollment_funnel.png)
 ```
-
-```{r event-count-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for private institutions"}
-knitr::include_graphics('assets/figures/plot_event_count_privu.pdf')
-```
-
-```{r event-count-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Number of events by type and in-state, out-of-state for public institutions"}
-knitr::include_graphics('assets/figures/plot_event_count_pubu.pdf')
-```
-
-\newpage
-
-```{r privhs-universe, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of universe of private HS and private HS that received at least 1 visit from sample institutions, unweighted and weighted by 12th grade enrollment"}
-knitr::include_graphics('assets/figures/plot_pss_universe.pdf')
-```
-
-\begin{center}
-* \textit{Universe of private HS (N=3673), private HS visited by sample institutions (N=1738); Universe of private HS is defined as any private schools that enrolls at least ten grade 12 students and is not a special education school, an alternative school, an early childhood center, or an independent school.}
-\end{center}
-
-\newpage
-
-\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
-
-\begin{landscape}
-
-```{r two-mode-plot, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "2-mode network for all institutions, colored by geographic region"}
-knitr::include_graphics('assets/figures/plot_2mode_all_region.pdf')
-
-#https://stackoverflow.com/questions/15625990/how-to-set-size-for-local-image-using-knitr-for-markdown
-```
-
-```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for private institutions, colored by cluster"}
-knitr::include_graphics('assets/figures/plot_1mode_privu.pdf')
-```
-
-```{r, fig.width=3.5, fig.height=3, echo = FALSE, message = FALSE}
-# ggplot's default color palette
-# library(scales)
-# show_col(hue_pal()(4))
-
-plot_characteristic <- function(df, type, characteristic, label_text, visit_count = FALSE) {
-  if (visit_count) {
-    df <- df %>% mutate(univ_name = str_c(univ_name, ' (N=', total, ')'))
-  }
-
-  ordered_df <- df %>% arrange(desc(cluster), univ_name)
-  univ_order <- ordered_df$univ_name
-  cluster_face <- map_chr(ordered_df$cluster, function(x) if_else(as.numeric(x) %% 2 == 0, 'bold', 'plain'))
-
-  sub_df <- df %>% select(univ_name, all_of(characteristic)) %>%
-    gather(key, value, characteristic) %>%
-    mutate(value = parse_number(value))
-
-  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(univ_order))
-  sub_df$key <- factor(sub_df$key, levels = characteristic)
-
-  ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
-    geom_bar(stat='identity', position = position_fill(reverse = TRUE)) +
-    ggtitle('Title') +
-    xlab('') + ylab('') +
-    labs(fill = type) +
-    scale_fill_manual(labels = label_text, values = c('#F8766D', '#7CAE00', '#00BFC4', '#C77CFF')) +
-    scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
-    theme(legend.position = 'top',
-          legend.title = element_text(size = 6, face = 'bold'),
-          legend.text = element_text(size = 6),
-          legend.margin = margin(0, 0, 0, 0),
-          legend.box.margin = margin(0, 0, -5, -30),
-          legend.key.size = unit(0.3, 'cm'),
-          panel.background = element_blank(),
-          axis.ticks.y = element_blank(),
-          axis.text.y = element_text(face = rev(cluster_face)),
-          text = element_text(size = 8),
-          plot.title = element_text(color = 'white')) +
-    coord_flip()
-}
-
-type_vec <- c('privu', 'pubu', 'pubu_outst', 'all', 'all_pubu_outst')
-
-for (i in 1:length(type_vec)) {
-  ego_df <-readRDS(file.path('.', 'assets', 'tables', str_c('table_ego_', type_vec[i], '.RDS')))
-
-  pdf(file.path('.', 'assets', 'figures', str_c('ego_network_figure_', type_vec[i], '.pdf')))
-  par(mar=c(0, 0, 0, 0) + 0.1, mai=c(0, 0, 0, 0))
-  par(mfrow=c(2, 2))
-
-  a <- plot_characteristic(ego_df, 'Region', c('northeast', 'midwest', 'south', 'west'), c('Northeast', 'Midwest', 'South', 'West'), visit_count = TRUE)
-  b <- plot_characteristic(ego_df, 'Religion', c('catholic', 'christian', 'other', 'nonsectarian'), c('Catholic', 'Christian', 'Other religion', 'Nonsectarian'))
-  c <- plot_characteristic(ego_df, '% Black/Latinx/Native', c('c1_lt10', 'c2_10to25', 'c3_25to50', 'c4_50+'), c('<10%', '10-25%', '25-50%', '50%+'), visit_count = TRUE)
-  d <- plot_characteristic(ego_df, 'Ranking', c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA'), c('Top 200 A+', 'Other A+', 'A', 'Less than A'))
-
-  grid.arrange(a, b, c, d, nrow=2, ncol=2, widths=c(1, 0.92))
-  dev.off()
-
-  # Need to use print() for ggplot inside loop in order for it to appear
-  # https://stackoverflow.com/a/15678596/6373540
-  # print(a)
-  # print(b)
-  # print(c)
-  # print(d)
-}
-```
-
-\end{landscape}
-
-\restoregeometry
-
-\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
-
-\newpage
-
-```{r ego-network-figure-privu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by private institutions"}
-knitr::include_graphics('assets/figures/ego_network_figure_privu.pdf')
-```
-
-\begin{center}
-* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
-\end{center}
-
-\begin{landscape}
-
-\newpage
-
-```{r villanova-religion, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Villanova University, colored by religious affiliation"}
-knitr::include_graphics('assets/figures/villanova_religion.pdf')
-```
-
-```{r emory-region, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "Ego network of Emory University, colored by geographic region"}
-knitr::include_graphics('assets/figures/emory_region.pdf')
-```
-
-```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions, colored by cluster"}
-knitr::include_graphics('assets/figures/plot_1mode_pubu.pdf')
-```
-
-```{r plot-1mode-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for public institutions and out-of-state visits only, colored by cluster", eval = FALSE}
-knitr::include_graphics('assets/figures/plot_1mode_pubu_outst.pdf')
-```
-
-\end{landscape}
-
-\restoregeometry
-
-\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
-
-\newpage
-
-```{r ego-network-figure-pubu, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by public institutions"}
-knitr::include_graphics('assets/figures/ego_network_figure_pubu.pdf')
-```
-
-\begin{center}
-* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
-\end{center}
-
-\begin{landscape}
-
-```{r plot-1mode-all, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, colored by cluster", include= FALSE, eval = FALSE}
-knitr::include_graphics('assets/figures/plot_1mode_all.pdf')
-```
-
-```{r plot-1mode-all-pubu-outst, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "1-mode network for all institutions, out-of-state visits only for public universities, colored by cluster"}
-knitr::include_graphics('assets/figures/plot_1mode_all_pubu_outst.pdf')
-```
-
-\end{landscape}
-
-\restoregeometry
-
-\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
-
-\newpage
-
-```{r ego-network-figure-all-pubu-outst, fig.align = 'center', echo = FALSE, fig.cap = "Characteristics of private HS visited by all institutions, out-of-state visits only for public universities"}
-knitr::include_graphics('assets/figures/ego_network_figure_all_pubu_outst.pdf')
-#out.width="1.1\\linewidth", 
-```
-
-\begin{center}
-* \textit{Universities are grouped by clusters, as indicated by alternating bolded and normal font}
-\end{center}

### 2021-06-04 scripts/ipeds_data_saving.R
update ipeds data + graph

@@ -2,23 +2,29 @@ library(tidyverse)
 library(labelled)
 
 
+data_dir <- file.path('.', 'data')
+
+
 # Function for labeling variables and values
-label_df <- function(df, df_dict, df_vals) {
+label_df <- function(df, df_dict, df_vals = NULL) {
 
   # Turn variables to lowercase
   names(df) <- tolower(names(df))
   df_dict <- df_dict %>% mutate(varname_lc = tolower(varname))
-  df_vals <- df_vals %>% mutate(varname_lc = tolower(varname))
   
-  # Label values
-  for (i in 1:nrow(df_vals)) {
-    varname <- df_vals[[i, 'varname_lc']]
+  if (!is.null(df_vals)) {
+    df_vals <- df_vals %>% mutate(varname_lc = tolower(varname))
     
-    if (class(df[[varname]]) != 'haven_labelled') {
-      df[[varname]] <- as.character(df[[varname]])
+    # Label values
+    for (i in 1:nrow(df_vals)) {
+      varname <- df_vals[[i, 'varname_lc']]
+      
+      if (class(df[[varname]]) != 'haven_labelled') {
+        df[[varname]] <- as.character(df[[varname]])
+      }
+      
+      val_label(df[[varname]], df_vals[[i, 'codevalue']]) <- df_vals[[i, 'valuelabel']]
     }
-    
-    val_label(df[[varname]], df_vals[[i, 'codevalue']]) <- df_vals[[i, 'valuelabel']]
   }
   
   # Label variables
@@ -32,9 +38,9 @@ label_df <- function(df, df_dict, df_vals) {
 
 
 # Read in HD data and dictionary (7153 obs. of 72 variables)
-hd <- read.csv('./data/ipeds_hd2017.csv', header = TRUE, na.strings = c('', ' ', 'NA'), stringsAsFactors = F,  colClasses = c('UNITID' = 'character', 'OPEID' = 'character', 'FIPS' = 'character'))
-hd_dictionary <- read.csv('./data/ipeds_hd2017_dictionary.csv', header = TRUE, na.strings=c('', 'NA'), stringsAsFactors = F)
-hd_values <- read.csv('./data/ipeds_hd2017_values.csv', header = TRUE, na.strings=c('', 'NA'), stringsAsFactors = F)
[…]

### 2021-06-04 scripts/network_recruiting_analysis.R

@@ -1,5 +1,6 @@
 library(igraph)
 library(tidyverse)
+library(gridExtra)
 
 options(max.print = 2000)
 
@@ -769,7 +770,7 @@ create_ego_table <- function(twomode_network, ego_networks, univs, c_analysis, k
                       if_else(privhs_visits_var == 'all', univ_characteristics$privhs_visits_tot, univ_characteristics[[privhs_visits_var]]),
                       if_else(privhs_visits_var == 'privhs_visits_out', 0L, univ_characteristics$privhs_visits_in),
                       if_else(privhs_visits_var == 'privhs_visits_in', 0L, univ_characteristics$privhs_visits_out),
-                      str_c(univ_characteristics$region, univ_characteristics$religion, univ_characteristics[[race_var]], univ_characteristics$ranking, sep = '|'),
+                      str_c(univ_characteristics$region, univ_characteristics$religion, univ_characteristics[[str_sub(race_var, end = -5)]], univ_characteristics$ranking_numeric, univ_characteristics$enroll, sep = '|'),
                       get_characteristic_pct(hs_characteristics, 'region', region_vals),
                       get_characteristic_pct(hs_characteristics, 'religion', religion_vals),
                       get_characteristic_pct(hs_characteristics, race_var, race_vals),
@@ -821,7 +822,106 @@ saveRDS(ego_table_all_pubu_outst, file = './assets/tables/table_ego_all_pubu_out
 ego_table_all_pubu_outst
 
 
+## ------------------------------
+## PLOT USING EGO IGRAPH OBJECTS
+## ------------------------------
 
+universe_df <- readRDS('./data/privhs_universe.RDS')
+visited_df <- readRDS('./data/privhs_visited.RDS')
+
+ego_df <- ego_table_all %>% 
+  mutate(
+    univ_region = str_split(characteristics, '\\|', simplify = T)[,1],
+    univ_religion = str_split(characteristics, '\\|', simplify = T)[,2],
+    univ_race = round(as.numeric(str_split(characteristics, '\\|', simplify = T)[,3]), 1),
+    univ_rank = as.numeric(str_split(characteristics, '\\|', simplify = T)[,4]),
+    univ_enroll = as.numeric(str_split(characteristics, '\\|', simplify = T)[,5])
+  )
+
+
+
[…]

### 2021-06-04 text/front_end_june_2021.Rmd
draft changes to front end

@@
 
+The mission of selective private colleges and universities is more squarely associated with social reproduction rather than social mobility.
+Historically, these institutions depend on patronage from philanthropic interests -- in connection with business and religious interests -- and depend from wealthy households who provide tuition revenue and donations [@RN4517].
+In turn, selective private institutions contribute to social reproduction by providing access to their patrons.
+The "Chetty" data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile [@RN4722; @RN4723].
+A significant caveat is that religiously affiliated universities may prioritize enrollment opportunities for students of the same faith regardless of wealth, but even here the mission is to benefit families from a particular cultural status group [CITE].
+
 The traditional, albeit mythologized, public good mission of public research universities is tied to social mobility and development of the state [@RN2269; @RN921].
-These institutions are designated the unique responsibility of educating the future civic, professional, and business leaders of the state.
+Public research universities are designated the unique responsibility of educating the future civic, professional, and business leaders of the state.
 Quoting 19th century University of Michigan President James Angell, these institutions contribute to social mobility by providing “an uncommon education for the common man” [as cited in @RN3608, p.
@@
 
-By contrast, the traditional mission of selective private colleges and universities is more squarely associated with reproduction.
-Historically, these institutions depend on patronage from philanthropic interests -- in connection with business interests and regligious congregations -- and depend on patronage from wealthy households who provide tuition revenue and donations [@RN4517].
-In turn, selective private institutions contribute to social reproduction by providing privileged access -- and the opportunities it confers -- to their wealthy patrons.
+We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction.
+Recruiting visits to private high schools are consistent with the social reproduction mission of selective private universities, regardless of whether the university is targeting a particular high school because of its academic reputation, religious affiliation, or the affluence of its student body.
+By contrast, for public research universities, visits to private high schools -- particularly out-of-state schools -- are antithetical to mission of social mobility for high-achieving, low-income state residents.
 
-Recruiting visits to private high schools are entirely consistent with the traditional social reproduction mission of selective private universities, regardless of whether the university is targeting a particular high school because of its academic reputation, religious affiliation, or the affluence of its student body.
-By contrast, visits to private high schools by public research universities -- and particularly to out-of-state private high schools -- particularly out-of-state schools -- are antithetical are antithetical to the public good mission of prioritizing meritorious state residents, particularly from humble means.
-
-We argue that an analysis of recruiting visits to private high schools can contribute novel insights about the "privatization" of public research universities to the interdisciplinary literature on privatization in the field of higher education research.
-One strand within this literature conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization [@RN4543@; @RN2101].
+Analyses of recruiting visits to private high schools can contribute novel insights about the "privatization" of public research universities.
+Within the scholarly literature on privatization, one strand of scholarship conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization [@RN4543@; @RN2101].
 Of relevance to this chapter, public research universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753], who typically pay two- to three-times more than resident students.
-Another strand within the privatization literature conceptualizes privatization as a process whereby public institutions become more similar -- in terms of characteristics or behavior -- to for-profit or private non-profit organizations [@RN4543].
+A second strand within the privatization literature conceptualizes privatization as a process whereby public institutions become more similar -- in terms of characteristics or behavior -- to for-profit or private non-profit organizations [@RN4543].
 A weakness of this literature is that few empirical studies analyze public institutions on a behavior associated with private institutions.
 
-This chapter compares public research universities to selective private universities on a behavior -- recruiting visits to private high schools -- that is consistent with the traditional mission of selective private institutions and antithetical to the traditional mission of public research universities.
-Empirical analyses are organized around the following three research questions:
+Therefore, this chapter compares public research universities to selective private universities on the dimension of recruiting visits to private high schools, a behavior associated with the social reproduction orientation of selective private universities.
+Our primary goal is to learn about public research universities, using the behavior of private universities as a benchmark to develop more thoughtful insights about public research universities.
+We analyze recruiting visits made in 2017 calendar year by a sample of 15 public research universities, 14 selective private universities, and 12 selective private liberal arts colleges.
+
+Because little is known about recruiting at private high schools by public universities, we conduct descriptive analyses that seek to identify basic patterns and relationships.
+Because a recruiting visit to a private high school is an indicator of a relationship between two actors, we also utilize social network methods in order to compare the recruiting networks of public universities to those of private universities.
+Analyses are informed by the following three research questions:
 
@@
 1. To what extent do public research universities and private universities visit overlapping sets of private high schools?
+
+SHORT PARAGRAPH GIVING OUTLINE OF CHAPTER
 
@@
 <!--[SHOULD WE TRY TO ADD SOME CONCRETE NUMBERS ON $ SPENDING AT PARTICULAR UNIVERSITIES?]-->
+
+INSERT FIGURE \@ref(fig:em-funnel) ABOUT HERE
 
@@
 
-<!-- QUESTIONS ABOUT THE RNL 2020 COST OF RECRUITING AN UNDERGRADUATE STUDENT REPORT, FIGURE 9
+<!--
 
@@
 
-@RN3519 and Khan [-@RN4321;-@RN4407] are centrally important to our study because they analyze relationships between college admissions counselors and high school guidance counselors.
-@RN3519, an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of visits.
+@RN3519, an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of off-campus recruiting visits.
 Stevens [-@RN3519, p.
@@
 
+<!--
+
+@RN3519 and Khan [-@RN4321;-@RN4407] are centrally important to our study because they analyze relationships between college admissions counselors and high school guidance counselors.
+
+-->
+
+Although not about recruiting visits per se, Khan [-@RN4321;-@RN4407] is centrally important for our study because he lays out a conceptual explanation of why colleges and private high schools develop relationships with one another (i.e., what is each trying to obtain from the other).
 @RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p.
@@
 Colleges also want a class composed of "interesting characters" whose curricular and extracurricular strengths meet the needs of important campus constituents (e.g., academic majors, the athletic department, clubs, etc.).
-Private high schools want to send _all_ students to the best college possible.
+Elite private high schools want to send _all_ students to the best college possible.
 Here, high school guidance counselors face "the pressure of making sure their school seems worth it – that \ldots paying some $40,000+, really does aid students in the college process" [@RN4321, p.
@@
 
-Even in the absence of horsetrading, maintaining strong relationships is mutually important for the college and for the high school.
-The college admissions counselor and the high school guidance counselor need to tell one another "their story" and relay that story to constituents [@RN3519].
-The college admissions counselor explains why the college/university is a "special place" that high school students should want to attend.
-The guidance counselor explains why the high school is a special place, that even students with lower grades have outstanding extracurricular strengths that will benefit the college.
+### Conceptualizing visits as an indicator of a relationship
 
-To summarize, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
+@RN3519 and Khan [-@RN4321;-@RN4407] suggest that strong relationships are mutually important for the college and for the private high school.
 Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another.
-In the absence of strong relationships, it is less likely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
-Building on these findings, we reason that the presence of a recruiting visit between a college and a high school is an indicator that the college and the high school have a relationship.
-First, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school.
+Without a strong relationship, it unlikely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
+Even in the absence of horsetrading described by @RN4407, relationships enable the college admissions counselor and the high school guidance counselor to tell one another "their story" and relay that story to constituents [@RN3519].
+The college admissions counselor explains why the college/university is a "special place" that high school students should want to attend [@RN3519].
+The guidance counselor explains why the high school is a special place, that even students with lower grades have outstanding extracurricular strengths that will benefit the college [@RN4321].
+
+The presence of a recruiting visit between a college and a private high school is an indicator that the college and the high school have a relationship.
+From an empirical perspective, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
+From a logical perspective, we argue that, first, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school.
 Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
 Third, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls).
+
+Conceptualizing a recruiting visit as an indicator of a relationship between a college and a high school motivates the use of social network methods, which analyze the network defined by "network ties" (i.e., visits) between actors (colleges and high schools).
+Prior research has not used social network methods to analyze recruiting visits from colleges to high schools.
+Analyzing the network of recruiting visits to high schools enables us to investigate the extent to which public research universities are visiting similar sets of private high schools as private colleges and universities, and also the extent to which they are visiting the same private high schools.
+In turn, we hope these analyses yield novel insights to scholarship on the privatization of public higher education.
+
+# Data and Methods
 
@@
 <!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->
-
-Our analyses to date have focused only on visits by public research universities<!--[CITE]-->.
-We found that most public research universities in our sample made more out-of-state than in-state recruiting visits.
-The exceptions were UC Berkeley, UC Irvine, and North Carolina State University, three institutions with relatively generous state appropriations and the only three public universities in our sample that faced strong nonresident enrollment caps.
-Across all universities, out-of-state visits systematically targeted affluent, predominantly white schools and communities, usually within populous metropolitan areas.
-Most public universities also made a disproportionate number of out-of-state visits to private high schools, which tend to be more affluent and white.
-<!--In addition, analyses of in-state visits found that public high schools in affluent communities were more likely to receive a visit, but this relationship was modest compared to the income disparity between visited and not visited out-of-state public schools.
-Furthermore, in-state visits did not consistently indicate preferences for majority white high schools or for private high schools.-->
-
-These findings motivated the goal of this chapter to investigate off-campus recruiting visits to private high schools.
-Public research universities have the mission of providing social mobility, yet their large number of out-of-state visits to private high schools are making them more similar to private institutions.
-Figures \@ref(fig:event-count-figure-pubu) and \@ref(fig:event-count-figure-privu) show the number of off-campus recruiting visits by public and private colleges/universities in our sample, respectively.
-A disproportionate number of out-of-state private high school visits can be seen for both public and private institutions.
-In this chapter, we will answer the research questions: Which types of private high schools receive visits from which types of colleges and universities?
-Additionally, to what extent were visits by a college/university to a private high school more likely if the two organizations were similar to one another on key characteristics?
-Our analyses focus on the characteristics of academic reputation, geographic region, religious affiliation, and racial composition.
 

### 2021-06-07 text/tables_figures_june_2021.Rmd
add draft tables/figures

---
title: 'Recruiting Chapter'
author: 
  - Ozan Jaquette
  - Crystal Han
  - Irma Castaneda
bibliography: ./../other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
    toc: FALSE
csl: ./../other/apa.csl
urlcolor: blue
header-includes:
  - \usepackage{pdflscape}
  - \usepackage{geometry}
  - \usepackage{floatrow}
  - \floatsetup{capposition=top}
---

```{r setup, include=FALSE}
library(knitr)
library(bookdown)

# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
library(kableExtra)
library(tidyverse)
library(gridExtra)
library(scales)

knitr::opts_chunk$set(echo = F, message = F)

data_dir <- file.path('..', 'data')
tables_dir <- file.path('..', 'assets', 'tables')
figures_dir <- file.path('..', 'assets', 'figures')

univ_sample_df <- readRDS(file.path(data_dir, 'univ_sample.RDS')) %>%
  arrange(desc(classification), rank)
events_df <- readRDS(file.path(data_dir, 'events_data.RDS'))

pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
```

# University characteristics

```{r}
univ_sample <- univ_sample_df %>% 
  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)

kable(univ_sample %>% arrange(desc(classification), rank)) %>%
  collapse_rows(columns = 1, latex_hline = 'major', valign = 'middle') %>%
  kable_styling(latex_options = 'scale_down')
```

# RQ1

```{r}
events_count <- events_df %>%
  mutate(event_type = case_when(
    event_type %in% c('pub_hs', 'priv_hs') ~ event_type,
    event_type == 'cc' & event_loc == 'instate' ~ event_type,
    TRUE ~ 'other'
  )) %>%
  select(univ_abbrev, event_loc, event_type) %>% 
  group_by(univ_abbrev, event_loc, event_type) %>% 
  summarise(count = n())

kable(events_count[order(match(events_count$univ_abbrev, univ_sample_df$univ_abbrev)), ], longtable = TRUE) %>%
  kable_styling(font_size = 7.1, latex_options = c('repeat_header'))
```

## Number of events by type, in-state vs. out-of-state

- `events_count_pubu.pdf`
- `events_count_privu.pdf`
- `events_count_privc.pdf`

```{r}
include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
include_graphics(file.path(figures_dir, 'events_count_privc.pdf'))
```

\newpage

## Number of events by public vs. private HS

- `events_hs_count_pubu.pdf`
- `events_hs_count_privu.pdf`
- `events_hs_count_privc.pdf`

```{r}
include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
include_graphics(file.path(figures_dir, 'events_hs_count_privc.pdf'))
```

\newpage

## Actual vs. proportional visited HS

- Below shows actual/proportional numbers for all vs. out-of-state HS visited
- Numbers differ from above plots because above shows event counts (some HS can be visited multiple times) whereas below numbers count each HS once (no matter how many times they're visited)
- % private is generally higher for out-of-state. If we include all HS (both in and out) the % actual private is usually lowered, as seen below

```{r}
for (i in 1:nrow(univ_sample_df)) {
  print(univ_sample_df[[i, 'univ_abbrev']])
  uid <- univ_sample_df[[i, 'univ_id']]
  ust <- univ_sample_df[[i, 'state_code']]

  visited_pub_hs <- (events_df %>% filter(univ_id == uid, event_type == 'pub_hs'))$school_id %>% unique()
  visited_pub_state <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs))$state_code %>% unique()
  universe_pub_hs <- (pubhs_universe_df %>% filter(state_code %in% visited_pub_state))$ncessch %>% unique()

  visited_pub_state_out <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs, state_code != ust))$state_code %>% unique()
  visited_pub_hs_out <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs, state_code != ust))$ncessch %>% unique()
  universe_pub_hs_out <- (pubhs_universe_df %>% filter(state_code %in% visited_pub_state_out))$ncessch %>% unique()

  visited_priv_hs <- (events_df %>% filter(univ_id == uid, event_type == 'priv_hs'))$school_id %>% unique()
  visited_priv_state <- (privhs_universe_df %>% filter(school_id %in% visited_priv_hs))$state_code %>% unique()
  universe_priv_hs <- (privhs_universe_df %>% filter(state_code %in% visited_priv_state))$school_id %>% unique()

  visited_priv_state_out <- (privhs_universe_df %>% filter(school_id %in% visited_priv_hs, state_code != ust))$state_code %>% unique()
  visited_priv_hs_out <- (privhs_universe_df %>% filter(school_id %in% visited_priv_hs, state_code != ust))$school_id %>% unique()
  universe_priv_hs_out <- (privhs_universe_df %>% filter(state_code %in% visited_priv_state_out))$school_id %>% unique()

  visited_hs <- c(visited_pub_hs, visited_priv_hs)
  visited_hs_out <- c(visited_pub_hs_out, visited_priv_hs_out)

  universe_hs <- c(universe_pub_hs, universe_priv_hs)
  universe_hs_out <- c(universe_pub_hs_out, universe_priv_hs_out)

  writeLines(str_c('Total HS visited (unique): ', length(visited_hs)))
  writeLines(str_c('  % private HS (actual): ', round(length(visited_priv_hs) / length(visited_hs) * 100, 1)))
  writeLines(str_c('  % private HS (proportional): ', round(length(universe_priv_hs) / length(universe_hs) * 100, 1)))

  writeLines(str_c('Total out-of-state HS visited (unique): ', length(visited_hs_out)))
  writeLines(str_c('  % private HS (actual): ', round(length(visited_priv_hs_out) / length(visited_hs_out) * 100, 1)))
  writeLines(str_c('  % private HS (proportional): ', round(length(universe_priv_hs_out) / length(universe_hs_out) * 100, 1)))
}
```

\newpage

# RQ2

## Characteristics of visited private HS

- `ego_network_region_pubu_privu_privc.pdf`
- `ego_network_religion_pubu_privu_privc.pdf`
- `ego_network_race_pubu_privu_privc.pdf`
- `ego_network_rank_pubu_privu_privc.pdf`
- `ego_network_enroll_pubu_privu_privc.pdf`

```{r}
include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu_privc.pdf'))
include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu_privc.pdf'))
include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu_privc.pdf'))
include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu_privc.pdf'))
include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privu_privc.pdf'))
```

\newpage

# RQ3

### 2021-06-07 scripts/create_tables_figures.R

@@ -2,10 +2,12 @@ library(tidyverse)
 library(gridExtra)
 
 
+# File paths
 data_dir <- file.path('.', 'data')
 tables_dir <- file.path('.', 'assets', 'tables')
 figures_dir <- file.path('.', 'assets', 'figures')
 
+# Characteristic variables
 region_values <- c('northeast', 'midwest', 'south', 'west')
 region_keys <- c('Northeast', 'Midwest', 'South', 'West')
 region_title <- 'Region'
@@ -36,13 +38,18 @@ var_labels <- c(region_title, religion_title, race_title, ranking_title, enroll_
 var_values <- list(region_values, religion_values, race_values, ranking_values, enroll_values)
 var_keys <- list(region_keys, religion_keys, race_keys, ranking_keys, enroll_keys)
 
+# Load data
+univ_sample_df <- readRDS(file.path(data_dir, 'univ_sample.RDS')) %>% arrange(desc(classification), rank)
 
-## ------------------------------
-## PLOT USING EGO IGRAPH OBJECTS
-## ------------------------------
+univ_public_research <- (univ_sample_df %>% filter(classification == 'public_research'))$univ_abbrev
+univ_private_national <- (univ_sample_df %>% filter(classification == 'private_national'))$univ_abbrev
+univ_private_libarts <- (univ_sample_df %>% filter(classification == 'private_libarts'))$univ_abbrev
 
-universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
-visited_df <- readRDS(file.path(data_dir, 'privhs_visited.RDS'))
+pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
+events_df <- readRDS(file.path(data_dir, 'events_data.RDS'))
+
+privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
+privhs_visited_df <- readRDS(file.path(data_dir, 'privhs_visited.RDS'))
 
 ego_df <- readRDS(file.path(tables_dir, 'table_ego_all.RDS')) %>% 
   mutate(
@@ -54,16 +61,195 @@ ego_df <- readRDS(file.path(tables_dir, 'table_ego_all.RDS')) %>%
   )
 
 
+## -------------------
+## SAVE PLOT FUNCTION
+## -------------------
+
+# FUNCTION: save_plot(graph_object, plot_name, <paper>, <mar>, <mai>)
[…]

### 2021-06-08 text/front_end_june_2021.Rmd
created revised draft of front end

@@
       - \usepackage{floatrow}
+      - \usepackage{setspace}
+      - \doublespacing
       - \floatsetup{capposition=top}
+fontsize: 12pt
 ---
@@
 
-1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by private universities?
-1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by private universities?
-1. To what extent do public research universities and private universities visit overlapping sets of private high schools?
+1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
+1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
 
@@
 
-### Conceptualizing visits as an indicator of a relationship
+### Visits as an indicator of a social relation
 
@@
 
+# Social network analysis concepts
+
+Having conceptualized a recruiting visit as an indicator of a social relation, this section introduces basic concepts from social network analysis and motivate the research questions that guide empirical analyses.
+
+A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "network ties" or "edges" between these actors.
+"One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
+Similarly, the social network of Twitter consists of handles (vertices) who are connected to one another by following or being followed.
+
+Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
+For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
+The most commonly analyzed two-mode network in social networks literature is a corporate board-director network  [e.g., @RN4663].
+These networks consists of directors (mode 1) and organizational boards (mode 2) and a particular director shares an edge with a particular organizational board if they sit on that board.
+Similarly, our recruiting visit data form a two-mode network, consisting of private high schools (mode 1) and college (mode 2).
+An off-campus recruiting visit from a college/university to a private high school is the "edge" that connects two particular vertices.
+In this network, edges can only occur between vertices of a different type; that is a college can visit a high school, but colleges cannot visit other colleges and high schools cannot receive visits from other high schools.
+
+To reduce complexity, two-mode network graphs are often analyzed as one-mode networks [@RN2457;@RN4663].
+Our two-mode college-school network can be transformed into a one-mode college network in which each vertex is a college/university and two colleges share an edge if both colleges visited at least one high school in common.
+The *weight* of an edge indicates the number of high schools that both colleges visited.
+For example, if there are 200 private high schools that received a visit from both Notre Dame and Villanova, the weight of the edge between Notre Dame and Villanova is 200.
+
+## RQ1: Degree centrality
+
+<!-- 
+In social network analysis, *centrality* is a notion of how important or prominent or "in the middle of things"
+*centrality* refers to the importance or prominence of an actor/vertex in a social network [CITE].
+-->
+
+In social network analysis, *centrality* refers to the importance or prominence or "being in the middle of things" of an actor/vertex in a social network [CITE].
+Many alternative measures of centrality have been developed.
+All measures agree that centrality is an actor/vertex-level construct (e.g., each college in our network will have a centrality value, regardless of which centrality measure we use).
+However, different measures of centrality are based on different theoretical conceptualizations -- for example, being directly connected to the most actors versus being the intermediary between otherwise disconnected actors -- and are operationalized using different mathematical algorithms.
+
+The simplest measure of centrality, *degree centrality* measures the number of edges directly connected to a vertex.
+For each college in our network, degree centrality is simply the number of different private high schools visited by the college.
+For each high school in our network, degree centrality is simply the number of colleges in our network that visited the high school.
+Social network theory conceptualizes degree centrality as a measure of "local" centrality, capturing the number of direct connections for each actor/vertex.
+For our empirical context, we conceive of degree centrality as a measure of scale of the number of private high schools a college visits and, equivalently, the number of private high schools we observe haging a social relation with each college.
+Given that we conceptualize visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges/universities, we are interested in comparing how scale differs between public and private colleges/universities.
+This interest motivates research question 1, "how does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?" We answer this research question by comparing degree centrality across universities.
+
+<!-- 
+Social network theory conceptualizes degree centrality as a measure of "local" centrality; it captures the number of direct connections but it does not capture the extent to which an actor/vertex is indirectly connected to others or whether an actor is connected to highly-connected others.
+-->
+
+Degree is a limited measure of centrality in that only identifies direct connections.
+By contrast, *k-path centrality* centrality measures the extent to which an actor/vertex is indirectly connected to others, *betweenness centrality* measures the extent to which a vertex is an intermediary between otherwise disconnected groups of actors, and *eigenvector centrality* measures the extent to which a vertex is connected to highly connected others.
+Betweenness centrality tends to be relevant for empirical contexts (e.g., which manager gets credit for an idea) where an actor who occupies a position between groups can benefit by being a broker of information/ideas [@RN975].
+By contrast, this chapter is more concerned with whether a particular college tends to have indirect connections with some colleges but not others, and what is the subset of high schools this group of colleges tends to visit.
+Research question 3, motivated below, explores these ideas.
+
+## RQ2: Ego networks and homophily
+
+Because the data structure of networks is complicated, a useful first step is to analyze "ego networks" rather than the entire social network.
+An "ego" is a single "focal" node (e.g., The University of Notre Dame).
+An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" (p.
+XXX)<!-- [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ]-->.
+For example, the University of Notre Dame ego network consists of all private high schools that received at least one visit from Notre Dame.
+Additionally, for each high school visited by Notre Dame, the ego network may include all colleges/universities in our sample that also visited the high school.
+This chapter analyzes recruiting visits to private high schools by 41 colleges and universities, which we can think of as 41 ego networks.
+
+A common finding in social networks research is that actors are more likely to form connections with actors who are are similar to them [@RN1722].
+Said differently, ego networks are biased towards "homophily" rather than "heterophily." Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be friends on Facebook if they have similar political ideologies).
+Heterophily, the opposite of homophily, is when pairs of connected vertices have different characteristics from one another.
+
+In our analyses of recruiting visits from colleges to private high schools, we are interested in the existence of homophily versus heterophily for two reasons.
+First, prior scholarship suggests that private colleges and private high schools are more likely to have a relationship when they share common ideologies or view themselves as belonging to the same echelon [@RN3519; @RN4321;@RN4407].
+Second, with respect to our substantive interest the behavior of public research universities, the characteristics of visited private high schools have consequences for subsequent enrollment composition of public research universities.
+Therefore, we are interested in whether universities tend to visit high schools that are similar to them on certain characteristics.
+Additionally, we are interested in whether public research universities favor high schools with certain characteristics, independent of homophily.
+These interests motivate research question 2, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by private universities?"
+
+Decisions about which particular characteristics to analyze were driven by substantive considerations and data limitations.
+In particular, we analyzed geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
+We analyze geographic region because, for most colleges and universities, enrollment demand is likely to be stronger at high schools in the same geographic region, but nationally prestigious colleges and universities may experience high demand throughout the country.
+We analyze religious affiliation because private colleges are more likely to have a relationship with private high schools with a similar religious affiliation.
+Although public universities are formally secular, we are interested in whether particular public universities tend to target religiously affiliated private high schools.
+We analyze academic reputation based on the idea that more highly ranked colleges are likely to target highly ranked private high schools.
+Racial composition is of substantive interest because the racial composition of visited high schools has consequences for the rational composition of colleges and universities.
+Given our interests in social reproduction versus social mobility, we would also analyze tuition price and household income, but these data are not avalable for private high schools.
+
+## RQ3: Network similarity and community detection
+
+This chapter conceptualizes recruiting visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges and universities.
+We are interested in how similar the recruiting networks of public research universities are to those of private colleges and universities, thereby motivating research question 3: to what extent do public research universities and private universities visit overlapping sets of private high schools?
+This research question is addressed, simultaneously, through the use of network graphs and by allocating each college/university to a "community" cluster.
+
+Network graphs show vertices as nodes and edges as lines connecting two nodes.
+Conceptually, we think of nodes as repelling one another and edges as pulling nodes together.
+Therefore, nodes that share few connections are located apart and nodes that share many connections are located close together.
+Nodes that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while nodes that are relatively disconnected are located at the periphery of the graph.
+In the analyses below, we graph the one-mode college network, using relative proximity of nodes to convey whether a pair colleges have a similar network structure.
+
+We also address research question 3 by using cluster analysis to identify colleges/universities that share common network structure.
+Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
+Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
+We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits
+
 # Data and Methods
+
+## Data
 
@@
 These institutions are excluded from the analyses.
-Our final analysis sample consists of 17 public research universities, 13 private research universities, and 12 private liberal arts colleges.
+Our final analysis sample consists of 15 public research universities, 14 private research universities, and 12 private liberal arts colleges.
 <!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->
@@
 ADD TABLE OF UNIVERSITY CHARACTERISTICS HERE
+
+## Methods
+
+# Results
+
+## Research question 1: scale of visits
+
+Research question 1 asks, how does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
+This question can be answered by counting the number of visits to private high schools, which equivalent to calculating degree centrality for each university.
+In addition to scale, we are also interested in the relative scale of visits to private high schools.
+That is, the number of visits to private high schools as a proportion of all off-campus recruiting visits, or as a proportion of all recruiting visits to high schools.
+Appendix Figures X and X show the number of visits by "type" (public high school, private high school, community college, other), respectively, for public research universities and selective private universities.
+Figures X and X show the number of visits to private high schools and public high schools, respectively, for public research universities and selective private universities, with separate bars for in-state and out-of-state visits.
+
+INSERT FIGURE X AND FIGURE X ABOUT HERE
+
+## Research question 2: characteristics of visited schools
+
+TEXT
+
+## Research question 3: overlapping network structure
+
+TEXT
 

### 2021-06-08 text/manuscript_june_2021.Rmd
started full manuscript rmd

--- 2021-06-08 text/front_end_june_2021.Rmd
@@
 
+# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
 library(kableExtra)
@@
 library(gridExtra)
+library(scales)
+
+knitr::opts_chunk$set(echo = F, message = F)
+
+data_dir <- file.path('..', 'data')
+tables_dir <- file.path('..', 'assets', 'tables')
+figures_dir <- file.path('..', 'assets', 'figures')
+
+univ_sample_df <- readRDS(file.path(data_dir, 'univ_sample.RDS')) %>%
+  arrange(desc(classification), rank)
+events_df <- readRDS(file.path(data_dir, 'events_data.RDS'))
+
+pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
+privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
 ```
@@
 That is, the number of visits to private high schools as a proportion of all off-campus recruiting visits, or as a proportion of all recruiting visits to high schools.
-Appendix Figures X and X show the number of visits by "type" (public high school, private high school, community college, other), respectively, for public research universities and selective private universities.
-Figures X and X show the number of visits to private high schools and public high schools, respectively, for public research universities and selective private universities, with separate bars for in-state and out-of-state visits.
+Appendix Figures \@ref(fig:events-count-pubu) and \@ref(fig:events-count-privu) show the number of visits by "type" (public high school, private high school, community college, other), respectively, for public research universities and selective private universities.
+Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools, respectively, for public research universities and selective private universities, with separate bars for in-state and out-of-state visits.
 
-INSERT FIGURE X AND FIGURE X ABOUT HERE
+INSERT FIGURE \@ref(fig:events-hs-count-pubu) AND FIGURE \@ref(fig:events-hs-count-privu) ABOUT HERE
 
@@
 
+\newpage
+
 ```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%"}
@@
 ```
+
+\newpage
+
+```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
+include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
+```
+
+\newpage
+
+```{r events-hs-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
+include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
+```
+
+# Appendix
+
+```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
+include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
+```
+
+\newpage
+
+```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
+include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
+```

### 2021-06-09 text/manuscript_june_2021.Rmd
started writing results section

@@
 knitr::opts_chunk$set(echo = F, message = F)
+
+knitr::knit_hooks$set(inline = function(x) {   if(!is.numeric(x)){     x   }else{    prettyNum(round(x,2), big.mark=",")    } })
 
@@
 
-Decisions about which particular characteristics to analyze were driven by substantive considerations and data limitations.
-In particular, we analyzed geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
+Decisions about which private school characteristics to analyze were informed by prior research [e.g., @RN4504; @RN4321; @RN3519; @RN4588; @RN4724].
+In particular, @RN4504 used data from several national surveys to analyze long-term trends in private school enrollment by family income.
+The percentage of American (elementary school) students attending private school declined from 15% in the mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
+With respect to family income, the private school enrollment rate of high-income families (around 17%) and low-income families (around 4%) remained stable over time, but the enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
+These declines were substantially driven by declines in the number of students attending Catholic school, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
+Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
+With respect to race, in 2013, 11% of white students attended private school compared to 5% of Black students, and 3% of Hispanic students.
+However, for high income families, rates of private school enrollment do not differ substantially across race.
+In the South, there has been a long-term increase in private school enrollment, driven by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsetarian private schools by high-income families.
+
+Based on these findings and logical argument (and also data limitations), our analyses focus on the following private school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
 We analyze geographic region because, for most colleges and universities, enrollment demand is likely to be stronger at high schools in the same geographic region, but nationally prestigious colleges and universities may experience high demand throughout the country.
@@
 That is, the number of visits to private high schools as a proportion of all off-campus recruiting visits, or as a proportion of all recruiting visits to high schools.
+
 Appendix Figures \@ref(fig:events-count-pubu) and \@ref(fig:events-count-privu) show the number of visits by "type" (public high school, private high school, community college, other), respectively, for public research universities and selective private universities.
-Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools, respectively, for public research universities and selective private universities, with separate bars for in-state and out-of-state visits.
+On average, the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample conducted `r round((events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()), digits = 0)` off-campus recruiting events in 2017, ranging from a low of `r events_df %>% filter(univ_id == '139959') %>% count() %>% as.numeric()` for the University of Georgia to a high of `r events_df %>% filter(univ_id == '100751') %>% count() %>% as.numeric()` for the University of Alabama.
+By contrast, the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample conducted an average of `r round((events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()), digits = 0)` events, ranging from a low of `r events_df %>% filter(univ_id == '186867') %>% count() %>% as.numeric()` by Stevens Institute of Technology (located in Hoboken, NJ) to a high of `r events_df %>% filter(univ_id == '239105') %>% count() %>% as.numeric()` to Marquette University (located in Milwaukee, WI).
+Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs','priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())*100, digits=1)`% of visits were to a public or private high school, whereas for selective private universities `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('pub_hs','priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())*100, digits=1)`% of all visits were to a public or private high school.
+The lower percentage for public research universities is because many public research universities made a substantial number of visits to community colleges whereas private universities did not.
+
+Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools for for public research universities (Figure \@ref(fig:events-hs-count-pubu)) and selective private universities (Figure \@ref(fig:events-hs-count-privu)), with separate bars for in-state and out-of-state visits.
+Only three of the 15 public research Universities -- UC-Berkeley, UC-San Diego, and UC-Riverside -- made more in-state than out-of-state high school visits.
+Notably, the University of California voluntarily adopted a nonresident enrollment cap in 2017, following pressure from state legislators who had issued a bill to cap nonresident enrollment.
+Of the 14 selective private universities in our sample, only Baylor University (Waco, TX) made more in-state than out-of-state high school visits.
 
@@
 
+With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of `r events_df %>% filter(univ_id == '110671', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by UC-Riverside to a high of `r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by the University of Alabama (which accounted for `r round((events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)` of all visits to private schools by public research universities in our sample), with the median university, The University of Pittsburgh, making `r events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()` visits.
+Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of private high school visits were to out-of-state schools while `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of public high school visits were to out-of-state schools.
+This result is consistent with the notion that public research universities placed more value on out-of-state private high school students than in-state private high school students because out-of-state students generate substantially more tuition revenue.
+
+For selective private universities, the number of visits to private high schools ranged from a low of `r events_df %>% filter(univ_id == '186867', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` by Stevens Institute of Technology to a high of `r events_df %>% filter(univ_id == '152080', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` by Notre Dame, with the median universities -- Boston College and Northwestern University -- visiting `r events_df %>% filter(univ_id == '164924', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` and `r events_df %>% filter(univ_id == '147767', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` private high schools, respectively.
+Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities.
+That said, several public research universities in our sample -- University of Colorado-Boulder (`r events_df %>% filter(univ_id == '126614', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), University of South Carolina (`r events_df %>% filter(univ_id == '218663', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), and University of Alabama  (`r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
+
+The relative scale of visits to private high schools -- defined as private high school visits as a percentage of all high school visits -- also tended to be substantially higher at selective private universities than at public research universities.
+Across all selective private universities in our sample, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of high school visits were to private high schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
+However, the relative emphasis on private high schools was a bit closer for out-of-state visits; across all selective private universities, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% out-of-state high school visits were to private schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
+
+Although selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools.
+
+- DISCUSS TABLE COMPARING ACTUAL TO PROPORTIONAL VISITS; main point is that while private universities visit private high schools at a higher rate than public research universities, both groups visit private high schools at a higher rate than they do public high schools; note the exceptions to this statement and note that public research universities that are closer to the behavior of private universities (e.g., university of Georgia)
+
+```{r, eval = FALSE, include = FALSE}
+events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count(univ_abbrev) %>% arrange(n)
+
+events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count(univ_abbrev) %>% arrange(n)
+
+237/543*100 # Georgia
+381/1008*100 # CU Boulder
+461/1362*100 # U. South Carolina
+983/3410*100 # U. Alabama
+
+# private
+round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)
+
+# private out of state
+round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)
+
+# public
+round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)
+
+# public, out of state
+round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)
+```
+
+```{r, eval = FALSE, include = FALSE}
+
+events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n)
+
+events_df %>% filter(univ_id == '186867', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()
+
+events_df %>% filter(univ_id == '152080', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()
+
+events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()
+
+# number of visits to private schools by public research universities
+events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n)
+
+round((events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)
+
+events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()/univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()
+
+events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n)
+
+events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()
+```
+
+```{r, eval = FALSE, include = FALSE}
+
+# percentage of visits that were out-of-state
+
+# private high school visits
+round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)
+
+# public high school visits
+round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric())*100, digits=1)
+
+events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric()
+events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric()
+```
+
 ## Research question 2: characteristics of visited schools
 
-TEXT
+Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privu) address research question 2, how do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+
+Figure \@ref(fig:region-pubu-privu) shows the geographic region of visited private high schools.
+With respect to the private high school universe, there are more schools located in the South than any other region, consisting with the finding from @RN4504 about the long-term growth in private school enrollment in the South.
+START HERE THURSDAY
+
+RN4504
+
+high schools visited by universities in our sample. visited private high schools,
+
+Figure \@ref(fig:region-pubu-privu) shows the geographic region of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel).
+
+INSERT FIGURE \@ref(fig:region-pubu-privu) ABOUT HERE
+
+FOR RACE; CAN TALK A BIT ABOUT FINDINGS FROM PURDY AND LAWRENCE GRAHAM BASICALLY SAYING THAT RICH BLACK STUDENTS STARTED GOING TO THE BEST OF THE BEST TYPE PRIVATE SCHOOLS ONCE THEY WERE ALLOWED TO [@RN4588; @RN4724]
 
@@
 
+\newpage
+
+```{r region-pubu-privu, echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
+```
+
+\newpage
+
+```{r religion-pubu-privu, echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
+```
+
+\newpage
+
+```{r enroll-pubu-privu, echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privu.pdf'))
+```
+
+\newpage
+
+```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school rank of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
+```
+
+\newpage
+
+```{r race-pubu-privu, echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
+```
+
 # Appendix

### 2021-06-09 scripts/network_recruiting_analysis.R

@@ -561,6 +561,7 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
     edge.color = 'lightgrey',
     #coords = coords_kk, # starting positions for vertices
     layout = layout(network, coords = coords_kk),
+    #layout=layout_with_fr(network, coords = coords_kk),
     margin = margin
   )
 }

### 2021-06-11 text/tables_figures_june_2021.Rmd
add 1-mode plots

@@
 # RQ3
+
+## 1-mode plots
+
+- `plot_1mode_pubu.pdf`
+- `plot_1mode_privu.pdf`
+- `plot_1mode_privc.pdf`
+- `plot_1mode_u.pdf`, `plot_1mode_u_k5.pdf`
+- `plot_1mode_all.pdf`, `plot_1mode_all_k5.pdf`, `plot_1mode_all_k6.pdf`
+
+```{r}
+include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))
+include_graphics(file.path(figures_dir, 'plot_1mode_privu.pdf'))
+include_graphics(file.path(figures_dir, 'plot_1mode_privc.pdf'))
+
+include_graphics(file.path(figures_dir, 'plot_1mode_u.pdf'))
+include_graphics(file.path(figures_dir, 'plot_1mode_u_k5.pdf'))
+
+include_graphics(file.path(figures_dir, 'plot_1mode_all.pdf'))
+include_graphics(file.path(figures_dir, 'plot_1mode_all_k5.pdf'))
+include_graphics(file.path(figures_dir, 'plot_1mode_all_k6.pdf'))
+```

### 2021-06-11 text/manuscript_june_2021.Rmd
draft changes results section

@@
       - \floatsetup{capposition=top}
-fontsize: 12pt
+fontsize: 11pt
 ---
@@
 privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
+
+ego_df <- readRDS(file.path(tables_dir, 'table_ego_all.RDS')) %>% 
+  mutate(
+    univ_region = str_split(characteristics, '\\|', simplify = T)[,1],
+    univ_religion = str_split(characteristics, '\\|', simplify = T)[,2],
+    univ_race = round(as.numeric(str_split(characteristics, '\\|', simplify = T)[,3]), 1),
+    univ_rank = as.numeric(str_split(characteristics, '\\|', simplify = T)[,4]),
+    univ_enroll = format(as.numeric(str_split(characteristics, '\\|', simplify = T)[,5]), big.mark = ',')
+  )
 ```
@@
 
-ADD TABLE OF UNIVERSITY CHARACTERISTICS HERE
+INSERT TABLE \@ref(tab:sample-characteristics) ABOUT HERE
+
+Table \@ref(tab:sample-characteristics) shows selected characteristics for universities in our analysis sample.
+Given that we collected recruiting data for private universities ranked in the top 100 of US News and World Report, one concern is whether it makes sense to compare public research universities not ranked in the top 100 to private universities ranked in the top 100.
+However, the columns in Table \@ref(tab:sample-characteristics) for 25th and 75th percentile SAT score of enrolled freshmen suggest that private universities ranked lower than 75 have test score ranges that are fairly similar to public research universities not ranked in the top 100.
+The five public research universities ranked 124 or below have score ranges that are modestly lower, particularly the University of Nebraska-Lincoln, but remain comparable to private universities ranked 75 to 100.
+One exception is that Stevens Institute of Technology (rank 80) has substantially higher test scores.
+
+CRYSTAL - ADD ONE BRIEF PARAGRAPH LISTING THE DIFFERENT SECONDARY DATA SOURCES WE USED
 
@@
 - DISCUSS TABLE COMPARING ACTUAL TO PROPORTIONAL VISITS; main point is that while private universities visit private high schools at a higher rate than public research universities, both groups visit private high schools at a higher rate than they do public high schools; note the exceptions to this statement and note that public research universities that are closer to the behavior of private universities (e.g., university of Georgia)
+
+## Research question 2: characteristics of visited schools
+
+Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privu) address research question 2, how do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+
+Figure \@ref(fig:region-pubu-privu) shows the geographic region -- Northeast, Midwest, South, and West -- of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel).
+Scholarship on the relationship between geographic proximity and student demand tends to find that nationally prestigious universities enjoy strong demand across the nation, while less prestigious universities rely primarily on demand from students located nearby [e.g., @RN2133].
+The visit patterns for private universities are consistent with this finding; less prestiguous universities tended to focus on private high schools in their home region, while more prestigious universities tended to visit many private high schools outside their home region.
+Similarly, scholarship on student demand for out-of-state public universities finds that most public universities rely on demand from out-of-state students living in nearby states [@RN2536; @RN2535; @RN2546].
+Most public research universities in our sample visited a disproportionate number of private high schools in their home geographic region.
+UC-Berkeley and CU Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.
+
+INSERT FIGURE \@ref(fig:region-pubu-privu) ABOUT HERE
+
+In the universe of all private high schools (top row of Figure \@ref(fig:region-pubu-privu)), there are more schools located in the South than any other geographic region, consistent with the finding from @RN4504 about the long-term growth in private school enrollment in the South.
+Universities not located in the South tended to visit more private high schools in the South than any other region, except their home region.
+This finding emerged for both the public universities and private universities in our sample.
+
+Figure \@ref(fig:religion-pubu-privu) shows the religious affiliation -- Catholic, Christian, Nonsectarian, and Other -- of visited private high schools.
+The results for selective private universities (bottom panel) follow expectations: Nonsetarian universities tended to visit a higher proportion of nonsectarian private high schools; Catholic universities visited a higher proportion of Catholic high schools; and Christian universities tended to visit a relatively higher share of Christian high schools.
+
+INSERT FIGURE \@ref(fig:religion-pubu-privu) ABOUT HERE
+
+Results for public research universities (top panel) are more interesting.
+Despite being nonsectarian, the majority of public research universities visited a high share of religiously affiliated private high schools, particularly Catholic schools.
+Surprisingly, Catholic schools represented at least 40% of private high school visits for `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'public') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample.
+By contrast, Catholic schools represented at least 40% of visits for only `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'private') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample (the four Catholic universities and also Texas Christian University and Stevens Institute of Technology).
+For public research universities, the emphasis on visiting Catholic and Christian high schools rather than nonsectarian private high schools tended to be stronger at less prestigious institutions.
+
+Figure \@ref(fig:rank-pubu-privu) shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools.
+For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visted a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.
+A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.
+
+INSERT FIGURE \@ref(fig:rank-pubu-privu) ABOUT HERE
+
+A similar pattend emerged for the public research universities in our sample; more highly ranked universities tended to visit a higher share of higly rated private high schools than lower ranked universities.
+In comparison to the private universities in our sample, the public universities in our sample tended to visit a higher share of private high schools that were not highly rated.
+To a great extent, this finding is merely a consequence of our sampling strategy; we attempted to collected recruiting visit data from all public research universities but we only collected recruiting visit data from private universities ranked in the top 100 of US News and World Report.
+That said, the finding that public research universities visited a large share of low-rated private high schools is consistent with the idea that many public research universities visit private high schools in search of full-pay students rather than academic superstars.
+
+Figure \@ref(fig:enroll-pubu-privu) shows the 12th grade enrollment of visited private high schools.
+Compared to the universe of private high schools, the universities in our sample tended to visit schools that enrolled more 12th graders.
+Generally, the findings were pretty similar across universities public and private universities; for must universities, more than half of private school visits were to schools that enrolled at least 100 12th graders.
+However, public universities tended to visit a slightly larger share of high schools with fewer than 50 12th graders and private universities tended to visit a higher share of high schools with 12th grade enrollment of 50-100.
+
+INSERT FIGURES \@ref(fig:enroll-pubu-privu) AND \@ref(fig:enroll-pubu-privu) [the one for public high schools] ABOUT HERE
+
+Figure X shows the 12th grade enrollment of visited private high schools to the 12th grade enrollment of visited public high schools for the public research universities in our sample.
+DISCUSS RESULTS; MAIN TAKEAWAY IS THAT, COMPARED TO THE PUBLICH HIGH SCHOOLS THEY VISIT, PUBLIC UNIVERSITIES SEEM TO BE WILLING TO VISIT PRIVATE SCHOOLS THAT ENROLL FAR FEWER 12TH GRADERS.
+
+Figure \@ref(fig:race-pubu-privu) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited private high schools.
+Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups.
+For about 70% [CRYSTAL - CHECK THIS] of schools in the universe of private high schools (top row of Figure \@ref(fig:race-pubu-privu)), Black/Latinx/Native students comprise less than 20% of enrolled students.
+Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would enroll relatively few Black/Latinx/Native students.
+Figure \@ref(fig:race-pubu-privu) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
+For public universities, exceptions to this finding were were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.
+For private universities, Marquette was the only exception to this finding.
+
+Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495].
+Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students [@RN4724].
+Therefore, universities may visit predominantly white private high schools in search of non-white students.
+Once concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.
+
+INSERT FIGURE \@ref(fig:race-pubu-privu) ABOUT HERE
+
+Figure X compares the racial composition of private high schools visited by public research universities to the racial composition of public high schools visited by these universities.
+[TAKEAWAY: the private high schools visited are much less racially diverse that the public high schools they visit, so recruiting aggresively from private schools may shift the racial composition of public research universities away from black/latinx/native]
+
+## Research question 3: overlapping network structure
+
+Research question 3 asks, to what extent do public research universities and selective private universities visit overlapping sets of private high schools?
+In contrast to RQ1 and RQ2, answering RQ3 requires social network analysis techniques.
+
+Appendix X describes how we constructed social network data.
+Briefly, we began by constructing a two-mode social network of visits to private high schools (mode 1) by universities (mode 2).
+Each university and each private high school is a "vertex." A visit from a university to a school is an "edge." Because large two-mode networks like our school-university network are difficult to visualize, two-mode networks are often analyzed as one-mode networks [@RN2457;@RN4663].
+We transformed our two-mode school-university network into a one-mode university network in which each university is a vertex and two universities share an edge if both universities visited at least one high school in common.
+The *weight* of an edge indicates the number of high schools that both universities visited.
+For example, if there are 200 private high schools that received a visit from both Notre Dame and Villanova, the weight of the edge between Notre Dame and Villanova is 200.
+We created three separate one-mode university networks: a public university network; a private university network; a public and private university network.
+
+We answer research question 3 by, first, analyzing overlap in the recruiting network of public universities (the public university network), second, analyzing overlap in the network of private universities (the private university network), and third, analyzing overlap amongst public and private universities (the public and private university network).
+
+### Public university network
+
+text
+
+### Private university network
+
+text
+
+### Public and private university network
 
@@
 
+ego_df %>% glimpse()
+
+ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40) %>% count(control)
+
+ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'public') %>% count() %>% as.numeric()
 # percentage of visits that were out-of-state
@@
 
-## Research question 2: characteristics of visited schools
-
-Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privu) address research question 2, how do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
-
-Figure \@ref(fig:region-pubu-privu) shows the geographic region of visited private high schools.
-With respect to the private high school universe, there are more schools located in the South than any other region, consisting with the finding from @RN4504 about the long-term growth in private school enrollment in the South.
-START HERE THURSDAY
-
-RN4504
-
-high schools visited by universities in our sample. visited private high schools,
-
-Figure \@ref(fig:region-pubu-privu) shows the geographic region of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel).
-
-INSERT FIGURE \@ref(fig:region-pubu-privu) ABOUT HERE
-
-FOR RACE; CAN TALK A BIT ABOUT FINDINGS FROM PURDY AND LAWRENCE GRAHAM BASICALLY SAYING THAT RICH BLACK STUDENTS STARTED GOING TO THE BEST OF THE BEST TYPE PRIVATE SCHOOLS ONCE THEY WERE ALLOWED TO [@RN4588; @RN4724]
-
-## Research question 3: overlapping network structure
-
-TEXT
-
 # References
@@
 <!-- TABLES -->
+
+# Social network data appendix
+
+A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "network ties" or "edges" between these actors.
+"One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
+"Two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
+Data on recruiting visits by universities to high schools yields a two-mode network, in which an edge -- a recruiting visit -- occurs between a high school (mode 1) and a university (mode 2).
+
+**Constructing two-mode network** We describe construction of social network data with reference to "corporate board-director" networks -- the most commonly analyzed two-mode network -- which consist of directors (mode 1) who serve on organizational boards (mode 2).
+In our school-university two-mode network, the vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visits made between the two (e.g., high school $i$ shares an edge with university $j$ if high school $i$ receives at least one visit from university $j$).
+Visits can only occur between a school-university pair (not a school-school pair or a university-university pair).
+This (weighted) network can be represented as a school-by-university matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 universities) in which matrix cell $a_{i,j}$ identifies the number of visits  high school $i$ received from university $j$.
+<!--[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
+UNWEIGHTED SOMEWHERE]-->
+
+**Transforming two-mode network to one-mode networks** Two-mode networks are often analyzed as one-mode networks [@RN2457].
+@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" (p.
+XXX).
+Thus, a two-mode board-director network can be transformed into two one-mode networks.
+A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ serve on three boards together).
+Similarly, a one-mode board network is created based on a board-by-board matrix in which two boards share an edge if a director sits on both boards and matrix cell $a_{i,j}$ identifies the number of directors that serve on both board $i$ and board $j$.
+
+Following this approach, we create a one-mode high school network in which two private high schools share an edge if they both receive a visit by the same university.
+Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of universities that visited both school $i$ and school $j$<!-- [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
+Similarly, we create a one-mode university network in which two universities share an edge if both universities visited the same high school.
+Cell $c_{i,j}$ of the university-by-university matrix $C$ indicates the number of private high schools that received at least one visit from both university $i$ and university $j$.
+
+The social network analyses presented in this chapter -- particularly for research question 3 -- are primarily based on analysis of one-mode university networks.
+We created separate one-mode university networks for: public universities; private universities; both public and private universities.
 
@@
 
+\newpage
+
+```{r sample-characteristics}
+univ_sample <- univ_sample_df %>% 
+  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)
+
+kable(univ_sample %>% arrange(desc(classification), rank), caption = "Characteristics of universities in analysis sample") %>%
+  collapse_rows(columns = 1, latex_hline = 'major', valign = 'middle') %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
 <!-- FIGURES -->
@@
 \newpage
+
+\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
 
@@
 
-```{r enroll-pubu-privu, echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privu.pdf'))
-```
-
-\newpage
-
 ```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school rank of visited private high schools"}
@@
 
-```{r race-pubu-privu, echo = FALSE, fig.cap = "Racial composition of visited private high schools"}
+```{r enroll-pubu-privu, echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privu.pdf'))
+```
+
+```{r race-pubu-privu, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools"}
 include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
@@
 
-# Appendix
+```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
+```
+
+```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private universities, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
+```
+
+```{r plot-1mode-u-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster, five clusters"}
+knitr::include_graphics('./../assets/figures/plot_1mode_u_k5.pdf')
+```
 

### 2021-06-11 text/tables_figures_june_2021.Rmd
add 1-mode tables

@@
 ```
+
+\newpage
+
+## 1-mode tables
+
+- `table_1mode_pubu.RDS`
+- `table_1mode_privu.RDS`
+- `table_1mode_privc.RDS`
+
+Notes:
+
+- Each .RDS stores a list containing a counts matrix (`onemode_df`) and percent matrix (`onemode_pct_df`)
+- Some observations for the public university matrix and its corresponding 1-mode plot above
+  - U of Alabama has a lot more visits to private HS than the rest and is in its own cluster as seen from plot
+  - U of S.Carolina and CU Boulder are in a cluster together, and if we look at each of their columns in the pct matrix, they do have the most in common w/ each other (besides Alabama)
+  - UNL, UC Riverside, and Stony Brook actually have very little commonly visited HS, but ended up being in the same cluster as seen from the plot.
+They do have the fewest number of private HS visits, so less likely to have visits in common w/ other univs.
+As seen from the plot, their vertices are located very far apart from each other and have no direct edges connecting them.
+
+\newpage
+
+\newgeometry{top=0.5cm, left=0in, right=0cm, bottom=0.5cm}
+
+\begin{landscape}
+
+```{r}
+table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
+
+kable(table_1mode_pubu$onemode_df, caption = 'Public universities count matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(c(1, 15), width = '8.5em') %>% 
+  column_spec(2:13, width = '7em') %>% 
+  column_spec(c(14, 16), width = '6em')
+
+kable(table_1mode_pubu$onemode_pct_df, caption = 'Public universities percent matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(c(1, 15), width = '8.5em') %>% 
+  column_spec(2:13, width = '7em') %>% 
+  column_spec(c(14, 16), width = '6em')
+
+table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
+
+kable(table_1mode_privu$onemode_df, caption = 'Private universities count matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(1, width = '8.5em') %>%
+  column_spec(2:15, width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em')
+
+kable(table_1mode_privu$onemode_pct_df, caption = 'Private universities percent matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(1, width = '8.5em') %>%
+  column_spec(2:15, width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em')
+
+table_1mode_privc <- readRDS(file = file.path(tables_dir, 'table_1mode_privc.RDS'))
+
+kable(table_1mode_privc$onemode_df, caption = 'Private colleges count matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(1, width = '8.5em') %>%
+  column_spec(2:13, width = '7em') %>% 
+  column_spec(11, width = '6em')
+
+kable(table_1mode_privc$onemode_pct_df, caption = 'Private colleges percent matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(1, width = '8.5em') %>%
+  column_spec(2:13, width = '7em') %>% 
+  column_spec(11, width = '6em')
+```
+
+\end{landscape}

### 2021-06-11 scripts/network_recruiting_analysis.R

@@ -62,19 +62,19 @@ source(file = file.path(scripts_dir, 'create_igraph_objects.R'))
 
 region_values <- c('northeast', 'midwest', 'south', 'west')
 region_keys <- c('Northeast', 'Midwest', 'South', 'West')
-region_title <- 'geographic region'
+region_title <- 'Region'
 
 religion_values <- c('catholic', 'christian', 'nonsectarian', 'other')
 religion_keys <- c('Catholic', 'Christian', 'Nonsectarian', 'Other')
-religion_title <- 'religious affiliation'
+religion_title <- 'Religion'
 
 race_values <- c('c1_lt10', 'c2_10to20', 'c3_20to50', 'c4_50+')
 race_keys <- c('LT 10%', '10-20%', '20-50%', 'GT 50%')
-race_title <- 'percent black, latinx, or native'
+race_title <- '% Black/Latinx/Native'
 
 ranking_values <- c('c1_top200', 'c2_A+', 'c3_A', 'c4_ltA')
 ranking_keys <- c('Rank top 200', 'A+', 'A', 'A- or below')
-ranking_title <- 'academic reputation'
+ranking_title <- 'Ranking'
 
 enroll_values <- c('c1_lt50', 'c2_50to100', 'c3_100to150', 'c4_gt150')
 enroll_keys <- c('LT 50', '50-100', '100-150', 'GT 150')
@@ -228,12 +228,12 @@ plot_ego_graph(egos_psi_privu, '160755', characteristic = 'pct_blacklatinxnative
 plot_ego_graph(egos_psi_privu, '160755', characteristic = 'rank_cat2', values = ranking_values, keys = ranking_keys, title = ranking_title, graph_order = 1)
 
 # Villanova + religion
-save_plot(plot_ego_graph(egos_psi_privu, '216597', characteristic = 'religion', values = religion_values, keys = religion_keys, title = '', graph_order = 'both'),
-          plot_name = 'villanova_religion.pdf')
+# save_plot(plot_ego_graph(egos_psi_privu, '216597', characteristic = 'religion', values = religion_values, keys = religion_keys, title = '', graph_order = 'both'),
+#           plot_name = 'villanova_religion.pdf')
 
 # Emory + region
[…]

### 2021-06-11 text/manuscript_june_2021.Rmd
draft changes

@@
 We are interested in how similar the recruiting networks of public research universities are to those of private colleges and universities, thereby motivating research question 3: to what extent do public research universities and private universities visit overlapping sets of private high schools?
-This research question is addressed, simultaneously, through the use of network graphs and by allocating each college/university to a "community" cluster.
 
-Network graphs show vertices as nodes and edges as lines connecting two nodes.
-Conceptually, we think of nodes as repelling one another and edges as pulling nodes together.
-Therefore, nodes that share few connections are located apart and nodes that share many connections are located close together.
-Nodes that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while nodes that are relatively disconnected are located at the periphery of the graph.
-In the analyses below, we graph the one-mode college network, using relative proximity of nodes to convey whether a pair colleges have a similar network structure.
-
-We also address research question 3 by using cluster analysis to identify colleges/universities that share common network structure.
-Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
-Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
-We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits
+We address RQ3 by graphing the recruiting network and by identifying "clusters" of universities that have similar recruiting networks.
+First, network graphs show vertices (e.g., universities) as circles, with vertices that share many connections located close together and vertices that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph.
+In addition to network graphs, network scholarship often uses cluster analysis methodologies to identify vertices that share common structure, based purely on patterns of network ties.
 
@@
 
-text
+Tables \@ref(tab:pubu-count-matrix) and \@ref(tab:pubu-percent-matrix) provides a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
+Table \@ref(tab:pubu-count-matrix) shows, for each pair of public universities (e.g., University of Alabama and University of South Caroline,  the number of high schools that were visited by both universities.
+For example, column 1 shows that of the X different private high schools visited by the University of Alabama, the University of California also visited X of these high schools.
+Table \@ref(tab:pubu-percent-matrix) shows overlap in high schools visited in terms of percent rather than count.
+For example, of the X private high schools visited by CU Boulder, the University of Alabama visited X% of these high schools and the University of South Carolina visited X% of these high schools.
+
+INSERT TABLE \@ref(tab:pubu-count-matrix) AND TABLE \@ref(tab:pubu-percent-matrix) ABOUT HERE
+
+ADD PARAGRAPH THAT SUBSTANTIVELY INTERPRETS BIG PICTURE FINDINGS FROM THESE TABLES.
+
+```{r, eval = FALSE, include = FALSE}
+table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
+table_1mode_pubu %>% glimpse()
+```
+
+DESCRIBE HOW TO READ TABLE AND WHAT THE RESULTS SHOW
+
+INSERT TABLE X ABOUT HERE
+
+Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network.
+Generally -- whether graphing one-mode or two-mode networks -- network graphs show vertices as circles and edges as lines connecting pairs of vertices.
+In our one-mode public university network, each circle represents a public university and two universities share an edge -- represented by a dotted line -- if both universities visit at least one high school in common.
+
+For our one-mode public
+
+We address RQ3 by graphing the recruiting network and by identifying "clusters" of universities that have similar recruiting networks.
+First, network graphs show vertices (e.g., universities) as circles, with vertices that share many connections located close together and vertices that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph.
+In addition to network graphs, network scholarship often uses cluster analysis methodologies to identify vertices that share common structure, based purely on patterns of network ties.
+
+Network graphs show vertices as nodes and edges as lines connecting two nodes.
+Conceptually, we think of nodes as repelling one another and edges as pulling nodes together.
+Therefore, nodes that share few connections are located apart and nodes that share many connections are located close together.
+Nodes that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while nodes that are relatively disconnected are located at the periphery of the graph.
+In the analyses below, we graph the one-mode college network, using relative proximity of nodes to convey whether a pair colleges have a similar network structure.
+
+We also address research question 3 by using cluster analysis to identify colleges/universities that share common network structure.
+Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
+Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
+We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits
+
+INSERT FIGURE \@ref(fig:plot-1mode-pubu) ABOUT HERE
 
@@
 
-text
+INSERT TABLE \@ref(tab:privu-percent-matrix) ABOUT HERE
+
+INSERT FIGURE \@ref(fig:plot-1mode-privu) ABOUT HERE
 
 ### Public and private university network
+
+INSERT FIGURE \@ref(fig:plot-1mode-u-k5) ABOUT HERE
 
@@
 
-<!-- TABLES -->
+\newpage
 
@@
 
+<!-- TABLES -->
+
 \newpage
@@
 
-\newpage
+\clearpage
 
@@
 
+\clearpage
+
+```{r pubu-count-matrix}
+table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
+
+kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(c(1, 15), width = '8.5em') %>% 
+  column_spec(2:13, width = '7em') %>% 
+  column_spec(c(14, 16), width = '6em')
+```
+
+```{r pubu-percent-matrix}
+kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(c(1, 15), width = '8.5em') %>% 
+  column_spec(2:13, width = '7em') %>% 
+  column_spec(c(14, 16), width = '6em')
+
+```
+
+\clearpage
+
+```{r privu-count-matrix, eval=FALSE, include=FALSE}
+
+table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
+
+kable(table_1mode_privu$onemode_df, caption = 'Private universities count matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(1, width = '8.5em') %>%
+  column_spec(2:15, width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em')
+```
+
+```{r privu-percent-matrix}
+
+table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
+
+kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(1, width = '8.5em') %>%
+  column_spec(2:15, width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em')
+
+```
+
 <!-- FIGURES -->
 
-\newpage
+\clearpage
 

### 2021-06-11 scripts/network_recruiting_analysis.R

@@ -554,7 +554,7 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
     vertex.frame.color = 'lightgray',
     vertex.shape = 'circle',
     vertex.size = vertex_size,
-    edge.lty = 3,
+    edge.lty = 1, # 0 and “blank” mean no edges, 1 and “solid” are for solid lines, the other possible values are: 2 (“dashed”), 3 (“dotted”), 4 (“dotdash”), 5 (“longdash”), 6 (“twodash”).
     #edge.lty = 0.5,
     edge.width = log(as.numeric(E(network)$weight)/10),
     #edge.width = 1,
@@ -567,7 +567,9 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
 }
 
 # Usage
-# plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 4)
+plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 4)
+plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 4)
+plot_1mode_graph(g_2mode_u, mode = 'psi', c_analysis = 'hclust', k = 5, colors = c('lightblue', 'green', 'violet', 'yellow','coral'))
 
 # Private univs
 save_plot(plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 4),
@@ -582,10 +584,6 @@ save_plot(plot_1mode_graph(g_2mode_privc, mode = 'psi', c_analysis = 'hclust', k
 save_plot(plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 4),
           plot_name = 'plot_1mode_pubu.pdf')
 
-
-# Public univs, out-of-state
-# save_plot(plot_1mode_graph(g_2mode_pubu, mode = 'psi', pubu_visits = 'outofstate', c_analysis = 'hclust', k = 4),
-#           plot_name = 'plot_1mode_pubu_outst.pdf')
 
 # private and public universities
 save_plot(plot_1mode_graph(g_2mode_u, mode = 'psi', c_analysis = 'hclust', k = 4),

### 2021-06-12 text/manuscript_june_2021.Rmd
your side

@@
 
+The University of Alabama -- and to a lesser extent the University of South Carolina and CU-Boulder -- is omnipresent in the private high schools visited by the other public research universities in our sample, except the University of Nebraska-Lincoln.
+For the remaining universities, Figure \@ref(tab:pubu-percent-matrix) suggests several clusters of universities.
+For example, UMass-Amherst, Suny Stonybrook and Rutgers tend to visit many of the same high schools, as do University of Arkansas and the University of Kansas.
+
 ADD PARAGRAPH THAT SUBSTANTIVELY INTERPRETS BIG PICTURE FINDINGS FROM THESE TABLES.
@@
 
-DESCRIBE HOW TO READ TABLE AND WHAT THE RESULTS SHOW
-
-INSERT TABLE X ABOUT HERE
+INSERT TABLE \@ref(fig:plot-1mode-pubu) ABOUT HERE
 
@@
 Generally -- whether graphing one-mode or two-mode networks -- network graphs show vertices as circles and edges as lines connecting pairs of vertices.
-In our one-mode public university network, each circle represents a public university and two universities share an edge -- represented by a dotted line -- if both universities visit at least one high school in common.
-
-For our one-mode public
-
-We address RQ3 by graphing the recruiting network and by identifying "clusters" of universities that have similar recruiting networks.
-First, network graphs show vertices (e.g., universities) as circles, with vertices that share many connections located close together and vertices that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph.
-In addition to network graphs, network scholarship often uses cluster analysis methodologies to identify vertices that share common structure, based purely on patterns of network ties.
-
-Network graphs show vertices as nodes and edges as lines connecting two nodes.
-Conceptually, we think of nodes as repelling one another and edges as pulling nodes together.
-Therefore, nodes that share few connections are located apart and nodes that share many connections are located close together.
-Nodes that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while nodes that are relatively disconnected are located at the periphery of the graph.
-In the analyses below, we graph the one-mode college network, using relative proximity of nodes to convey whether a pair colleges have a similar network structure.
-
-We also address research question 3 by using cluster analysis to identify colleges/universities that share common network structure.
-Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
-Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
-We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits
+In our one-mode public university network, each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common.
+The width of a solid line between universities indicates the number of high schools both universities visited.
+Finally, the shape of each university vertex is determined by cluster analysis, which we specified to allocate each university to one of four groups, based purely on network patterns.
 
 INSERT FIGURE \@ref(fig:plot-1mode-pubu) ABOUT HERE
+
+Figure \@ref(fig:plot-1mode-pubu) shows three universities in the cneter of the recruiting network, the University of Alabama -- a cluster unto itesf -- and the University of South Carolina and CU-Boulder.
+By contrast, the University of Nebraska-Lincoln, UC-Riverside, and SUNY-Stonybrook are on the periphery of the network.
+These three universities are members of the same community cluster, despite not visiting any high schools in common.
+Between this most peripheral and the most central of universities, lies a cluster of 9 universities, consisting largely of universities that enoll relatively few out-of-state students but are actively seeking more.
 

### 2021-06-12 text/manuscript_june_2021.Rmd
results

@@
 The width of a solid line between universities indicates the number of high schools both universities visited.
+Conceptually, we think of nodes as repelling one another and edges as pulling nodes together.
+Therefore, nodes that share few connections are located apart and nodes that share many connections are located close together.
+Nodes that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while nodes that are relatively disconnected are located at the periphery of the graph.
+
 Finally, the shape of each university vertex is determined by cluster analysis, which we specified to allocate each university to one of four groups, based purely on network patterns.
+
+In the analyses below, we graph the one-mode college network, using relative proximity of nodes to convey whether a pair colleges have a similar network structure
 
@@
 INSERT FIGURE \@ref(fig:plot-1mode-privu) ABOUT HERE
+
+NOTE THAT MARQUETTE IS PERIPHERAL DESPITE MAKING A LARGE NUMBER OF VISITS, SUGGESTING THAT THEY VISIT A DIFFERENT SET OF HIGH SCHOOLS THAN MOST UNIVERSITIES
 

### 2021-06-14 text/tables_figures_june_2021.Rmd
update 1-mode tables

@@
   kable_styling(latex_options = 'scale_down') %>%
-  column_spec(c(1, 15), width = '8.5em') %>% 
+  column_spec(c(1, 14), width = '8.5em') %>% 
   column_spec(2:13, width = '7em') %>% 
-  column_spec(c(14, 16), width = '6em')
+  column_spec(c(15, 16), width = '6em')
 
@@
   kable_styling(latex_options = 'scale_down') %>%
-  column_spec(1, width = '8.5em') %>%
-  column_spec(2:15, width = '7em') %>% 
+  column_spec(c(1, 14, 15), width = '8.5em') %>%
+  column_spec(2:11, width = '7em') %>% 
   column_spec(c(4:6, 10, 12, 13), width = '6em')

### 2021-06-14 scripts/network_recruiting_analysis.R

@@ -619,9 +619,20 @@ save_plot(plot_1mode_graph(g_2mode, mode = 'psi', c_analysis = 'hclust', k = 6, 
 ## TABLE OF MATRIX OF NUMBER OF PRIVATE HIGH SCHOOLS VISITED IN COMMON
 ## ---------------------------
 
-create_1mode_table <- function(onemode_network) {
+privhs_events_unique <- privhs_events %>%
+  left_join(univ_info %>% select(univ_id, univ_abbrev, classification), by = 'univ_id') %>% 
+  group_by(classification, univ_id, univ_abbrev) %>% 
+  summarise(count = n_distinct(school_id)) %>% 
+  arrange(classification, desc(count))
+
+create_1mode_table <- function(onemode_network, univ_type) {
   
-  vertex_attr(graph=onemode_network, name='name') <- str_c(vertex_attr(graph=onemode_network, name='school_name'), ' (N=', vertex_attr(graph=onemode_network, name='privhs_visits_tot'), ')')
+  privhs_events_unique_df <- privhs_events_unique %>% filter(classification == univ_type)
+  
+  # Get N = number of unique private HS visited by each univ (order univ same way as igraph)
+  num_unique_privhs_visited <- privhs_events_unique_df[match(vertex_attr(graph=onemode_network, name='name'), privhs_events_unique_df$univ_id), ]$count
+
+  vertex_attr(graph=onemode_network, name='name') <- str_c(vertex_attr(graph=onemode_network, name='school_name'), ' (N=', num_unique_privhs_visited, ')')
 
   onemode_matrix <- as_adjacency_matrix(
     graph = onemode_network,
@@ -632,10 +643,18 @@ create_1mode_table <- function(onemode_network) {
   )
   
   # Sort by number of visits
-  univs_order_by_privhs_visits_tot <- (igraph::as_data_frame(onemode_network, 'vertices') %>% arrange(desc(privhs_visits_tot)))$name
-  onemode_df <- as.data.frame(onemode_matrix[univs_order_by_privhs_visits_tot, univs_order_by_privhs_visits_tot])
+  g_df <- igraph::as_data_frame(onemode_network, 'vertices')
+  univs_order_by_privhs <- g_df[match(privhs_events_unique_df$univ_abbrev, g_df$school_name),]$name 
+  onemode_df <- as.data.frame(onemode_matrix[univs_order_by_privhs, univs_order_by_privhs])
   
[…]

### 2021-06-14 scripts/ccd_data_saving.R
save race vars for public HS data

@@ -133,23 +133,77 @@ for (i in names(ccd_membership)) {
 
 # Pivot table (33369 obs.)
 ccd_membership_by_grade <- ccd_membership %>%
-  filter(grade %in% c('Grade 9', 'Grade 10', 'Grade 11', 'Grade 12', 'Grade 13'), total_indicator == 'Subtotal 4 - By Grade') %>%  # filter by 'Category Set A - By Race/Ethnicity; Sex; Grade' if want to further break down by race
+  filter(grade %in% c('Grade 9', 'Grade 10', 'Grade 11', 'Grade 12', 'Grade 13'), total_indicator == 'Subtotal 4 - By Grade') %>%
   select(ncessch, grade, student_count) %>%
-  mutate(grade = recode(grade,
-                        'Grade 9' = 'g09',
-                        'Grade 10' = 'g10',
-                        'Grade 11' = 'g11',
-                        'Grade 12' = 'g12',
-                        'Grade 13' = 'g13')
-         ) %>% 
+  mutate(
+    grade = recode(grade,
+                   'Grade 9' = 'g09',
+                   'Grade 10' = 'g10',
+                   'Grade 11' = 'g11',
+                   'Grade 12' = 'g12',
+                   'Grade 13' = 'g13')
+    ) %>% 
   pivot_wider(names_from = grade, values_from = student_count) %>%
   rowwise() %>% 
   mutate(total_students = sum(g09, g10, g11, g12, g13, na.rm = T))
 
+# Pivot table (33369 obs.)
+ccd_membership_by_race <- ccd_membership %>%
+  filter(grade %in% c('Grade 9', 'Grade 10', 'Grade 11', 'Grade 12', 'Grade 13'), total_indicator == 'Category Set A - By Race/Ethnicity; Sex; Grade') %>%
+  mutate(
+    grade = recode(grade,
+                   'Grade 9' = 'g09',
+                   'Grade 10' = 'g10',
+                   'Grade 11' = 'g11',
+                   'Grade 12' = 'g12',
+                   'Grade 13' = 'g13'),
+    race_ethnicity = recode(race_ethnicity,
+                            'American Indian or Alaska Native' = 'amerindian',
+                            'Asian' = 'asian',
+                            'Black or African American' = 'black',
+                            'Hispanic/Latino' = 'hispanic',
+                            'Native Hawaiian or Other Pacific Islander' = 'nativehawaii',
[…]

### 2021-06-14 scripts/create_igraph_objects.R

@@ -33,7 +33,16 @@ univ_info <- read.csv('./data/univ_data.csv', header = TRUE, na.strings = '', st
 
 # Public HS data from CCD
 pubhs_data_1718 <- readRDS('./data/ccd_1718.RDS')
-pubhs_data_1415 <- read.csv('./data/meta_high_school_public.csv', header = TRUE, na.strings = c('', 'NA', 'NULL'), stringsAsFactors = FALSE, colClasses = c('ncessch' = 'character'))  # original set used for merging
+pubhs_data_1415 <- read.csv('./data/meta_high_school_public.csv', header = TRUE, na.strings = c('', 'NA', 'NULL'), stringsAsFactors = FALSE, colClasses = c('ncessch' = 'character')) %>%  # original set used for merging
+  mutate(  # total_students = wh + am + as + hi + bl + hp + tr (each is sum of 9-12 grades)
+    pct_amerindian = am / total_students * 100,
+    pct_asian = as / total_students * 100,
+    pct_black = bl / total_students * 100,
+    pct_hispanic = hi / total_students * 100,
+    pct_nativehawaii = hp / total_students * 100,
+    pct_tworaces = tr / total_students * 100,
+    pct_white = wh / total_students * 100
+  )
 
 # Private HS data from PSS
 privhs_data_1718 <- readRDS('./data/pss_1718.RDS')
@@ -93,7 +102,7 @@ events_data <- events_data %>% filter(!(pid %in% c(34938, 44224, 33941, 25637)),
 table(events_data$event_type, useNA = 'always')
 
 
-# Clean up events data (drop visits to HS not meeting criteria - 45533 to 41054 obs)
+# Clean up events data (drop visits to HS not meeting criteria - 45533 to 44660 obs)
 events_df <- events_data %>% 
   select(univ_id, univ_state, event_type, school_id, event_state, event_loc)
 
@@ -137,14 +146,14 @@ ccd_missing_ncessch <- setdiff(events_df$school_id[events_df$event_type == 'pub_
 ccd_meet_criteria_1718 <- pubhs_data_1718 %>%
   filter(g_12_offered == 'Yes', g12 >= 10, virtual %in% c('NOTVIRTUAL', 'SUPPVIRTUAL'), fipst < 60, updated_status %in% c('1', '3', '8')) %>% 
[…]

### 2021-06-14 scripts/create_tables_figures.R
update format of hs count plot

@@ -134,7 +134,7 @@ save_plot(plot_event_count(univ_private_libarts, in_lim = 250, out_lim = 900), '
 ## NUMBER OF PUBLIC VS PRIVATE HS VISITS
 ## --------------------------------------
 
-plot_hs_count <- function(univ_sample, out_lim = 0, vjust = 1.5) {
+plot_hs_count <- function(univ_sample, in_lim = 0, out_lim = 0, vjust = 1.5) {
   sub_events_count <- events_count %>% filter(univ_abbrev %in% univ_sample)
   sub_events_count$univ_abbrev <- factor(sub_events_count$univ_abbrev, levels = rev(univ_sample))
   
@@ -145,16 +145,18 @@ plot_hs_count <- function(univ_sample, out_lim = 0, vjust = 1.5) {
     pivot_wider(names_from = event_type, values_from = count) %>% 
     mutate(
       tot_hs = priv_hs + pub_hs,
-      pct_priv = round(priv_hs / tot_hs * 100, 1),
-      label_text = str_c(tot_hs, ' (', pct_priv, '% priv)')
+      pct_priv = round(priv_hs / tot_hs * 100),
+      label_text_cnt = tot_hs,
+      label_text_pct = str_c(pct_priv, '% priv')
     )
   
   sub_events_outofstate_pct <- sub_events_outofstate %>%
     pivot_wider(names_from = event_type, values_from = count) %>% 
     mutate(
       tot_hs = priv_hs + pub_hs,
-      pct_priv = round(priv_hs / tot_hs * 100, 1),
-      label_text = str_c(tot_hs, ' (', pct_priv, '% priv)')
+      pct_priv = round(priv_hs / tot_hs * 100),
+      label_text_cnt = tot_hs,
+      label_text_pct = str_c(pct_priv, '% priv')
     )
   
   ggplot() +
@@ -164,7 +166,10 @@ plot_hs_count <- function(univ_sample, out_lim = 0, vjust = 1.5) {
              position = 'stack', 
              width = 0.35) +
     geom_text(data = sub_events_instate_pct,
-              aes(x = univ_abbrev, y = tot_hs, label = label_text),
+              aes(x = univ_abbrev, y = in_lim, label = str_c('In-state (N=', label_text_cnt, ')')),
+              hjust = 0, size = 2.5) +
+    geom_text(data = sub_events_instate_pct,
+              aes(x = univ_abbrev, y = tot_hs + 5, label = label_text_pct),
[…]

### 2021-06-14 text/tables_figures_june_2021.Rmd
add pubu hs visits characteristics plots

@@
 
+## Characteristics of visited private HS vs. public HS
+
+- `ego_network_enroll_pubu_privhs_pubhs.pdf`
+- `ego_network_race_pubu_privhs_pubhs.pdf`
+
+```{r}
+include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privhs_pubhs.pdf'))
+include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
+```
+
+\newpage
+
 # RQ3
@@
 - Each .RDS stores a list containing a counts matrix (`onemode_df`) and percent matrix (`onemode_pct_df`)
+- The numbers in matrix and the N=X count on top are for unique HS (not re-counting multiple visits to same HS)
 - Some observations for the public university matrix and its corresponding 1-mode plot above

### 2021-06-14 scripts/create_igraph_objects.R

@@ -166,7 +166,7 @@ pubhs_data %>% group_by(year) %>% count()  # 20756 from 2017-18, 53 from 2014-15
 events_df <- events_df %>% filter(event_type != 'pub_hs' | school_id %in% pubhs_data$ncessch)
 table(events_df$event_type, useNA = 'always')
 
-# Add race categorical variables to public HS data
+# Add race & enroll categorical variables to public HS data
 pubhs_data <- pubhs_data %>% mutate(
   pct_white_cat = case_when(
     pct_white < 50 ~ 'c1_lt50',
@@ -180,6 +180,18 @@ pubhs_data <- pubhs_data %>% mutate(
     pct_blacklatinxnative < 20 ~ 'c2_10to20',
     pct_blacklatinxnative < 50 ~ 'c3_20to50',
     pct_blacklatinxnative >= 50 ~ 'c4_50+'
+  ),
+  enroll_cat1 = case_when(
+    g12<50  ~ 'c1_lt50',
+    g12>=50 & g12<100  ~ 'c2_50to100',
+    g12>=100 & g12<150  ~ 'c3_100to150',
+    g12>=150  ~ 'c4_gt150'
+  ),
+  enroll_cat2 = case_when(
+    g12<100  ~ 'c1_lt100',
+    g12>=100 & g12<150  ~ 'c2_100to150',
+    g12>=150 & g12<200  ~ 'c3_150to200',
+    g12>=200  ~ 'c4_gt200'
   )
 )
 

### 2021-06-14 scripts/create_tables_figures.R

@@ -45,8 +45,10 @@ univ_public_research <- (univ_sample_df %>% filter(classification == 'public_res
 univ_private_national <- (univ_sample_df %>% filter(classification == 'private_national'))$univ_abbrev
 univ_private_libarts <- (univ_sample_df %>% filter(classification == 'private_libarts'))$univ_abbrev
 
-pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
 events_df <- readRDS(file.path(data_dir, 'events_data.RDS'))
+
+pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
+pubhs_visited_df <- pubhs_universe_df %>% filter(ncessch %in% events_df$school_id)
 
 privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
 privhs_visited_df <- readRDS(file.path(data_dir, 'privhs_visited.RDS'))
@@ -248,7 +250,70 @@ for (i in 1:nrow(univ_sample_df)) {
 ## CHARACTERISTICS OF PRIVATE HS VISITED BY UNIVERSITIES
 ## ------------------------------------------------------
 
-plot_characteristic <- function(plot_type, var_name, label, characteristic, label_text, control = 'public', type = 'univ') {
+# Ego tables for private HS visits currently show % for unique private HS (does not recount multiple visits to same HS)
+# View(events_df %>% filter(event_type == 'priv_hs', univ_id == '152080') %>% left_join(privhs_universe_df, by = 'school_id') %>% group_by(region) %>% summarise(count = n_distinct(school_id)) %>% mutate(pct = count / sum(count)))
+
+plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic, label_text, control = 'public', type = 'univ') {
+  
+  sub_df_visited <- pubhs_visited_df %>% group_by(get(var_name)) %>% 
+    summarize(`Public HS, 1+ visit` = n()) %>% 
+    pivot_longer(cols = 'Public HS, 1+ visit',
+                 names_to = 'universe',
+                 values_to = 'value')
+  names(sub_df_visited) <- c('key', 'univ_name', 'value')
+  
+  sub_df_universe <- pubhs_universe_df %>% group_by(get(var_name)) %>% 
+    summarize(`Public HS, universe` = n()) %>% 
[…]

### 2021-06-14 text/manuscript_june_2021.Rmd
draft changes

--- 2021-06-11 text/manuscript_june_2021.Rmd
@@
 
-INSERT FIGURES \@ref(fig:enroll-pubu-privu) AND \@ref(fig:enroll-pubu-privu) [the one for public high schools] ABOUT HERE
+INSERT FIGURES \@ref(fig:enroll-pubu-privu) AND \@ref(fig:enroll-pubu-privhs-pubhs) ABOUT HERE
 
-Figure X shows the 12th grade enrollment of visited private high schools to the 12th grade enrollment of visited public high schools for the public research universities in our sample.
+Figure \@ref(fig:enroll-pubu-privhs-pubhs) shows the 12th grade enrollment of visited private high schools to the 12th grade enrollment of visited public high schools for the public research universities in our sample.
 DISCUSS RESULTS; MAIN TAKEAWAY IS THAT, COMPARED TO THE PUBLICH HIGH SCHOOLS THEY VISIT, PUBLIC UNIVERSITIES SEEM TO BE WILLING TO VISIT PRIVATE SCHOOLS THAT ENROLL FAR FEWER 12TH GRADERS.
@@
 
+INSERT FIGURE \@ref(fig:race-pubu-privu) ABOUT HERE
+
 Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495].
@@
 
-INSERT FIGURE \@ref(fig:race-pubu-privu) ABOUT HERE
+INSERT FIGURE \@ref(fig:race-pubu-privhs-pubhs) ABOUT HERE
 
-Figure X compares the racial composition of private high schools visited by public research universities to the racial composition of public high schools visited by these universities.
+Figure \@ref(fig:race-pubu-privhs-pubhs) compares the racial composition of private high schools visited by public research universities to the racial composition of public high schools visited by these universities.
 [TAKEAWAY: the private high schools visited are much less racially diverse that the public high schools they visit, so recruiting aggresively from private schools may shift the racial composition of public research universities away from black/latinx/native]
@@
 Tables \@ref(tab:pubu-count-matrix) and \@ref(tab:pubu-percent-matrix) provides a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
-Table \@ref(tab:pubu-count-matrix) shows, for each pair of public universities (e.g., University of Alabama and University of South Caroline,  the number of high schools that were visited by both universities.
-For example, column 1 shows that of the X different private high schools visited by the University of Alabama, the University of California also visited X of these high schools.
+Table \@ref(tab:pubu-count-matrix) shows -- for each pair of public universities -- the number of high schools that were visited by both universities.
+For example, column 1 shows that of the 759 different private high schools that the University of Alabama visited, the University of South Carolina visited 284 of these schools and CU-Boulder visited 210 of these schools.
 Table \@ref(tab:pubu-percent-matrix) shows overlap in high schools visited in terms of percent rather than count.
-For example, of the X private high schools visited by CU Boulder, the University of Alabama visited X% of these high schools and the University of South Carolina visited X% of these high schools.
+For example, Column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7% of these high schools and CU-Boulder visited 39.1% of these high schools.
 
@@
 
-ADD PARAGRAPH THAT SUBSTANTIVELY INTERPRETS BIG PICTURE FINDINGS FROM THESE TABLES.
+One finding from Table \@ref(tab:pubu-percent-matrix) is that the University of Alabama is is omnipresent in the set of private high schools visited by most other public research universities in the sample, particularly universities located in the South.
+For the remaining universities, Figure \@ref(tab:pubu-percent-matrix) suggests several clusters of universities.
+For example, UMass-Amherst, Suny Stonybrook and Rutgers tend to visit many of the same high schools, as do University of Arkansas and the University of Kansas.
 
@@
 table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
-table_1mode_pubu %>% glimpse()
+table_1mode_pubu$onemode_pct_df %>% glimpse()
+table_1mode_pubu$onemode_pct_df
+
+table_1mode_pubu$onemode_pct_df %>% filter(row.names(table_1mode_pubu$onemode_pct_df) %in% c('CU Boulder'))
+
+table_1mode_pubu$onemode_pct_df %>% attributes()
+
+table_1mode_pubu$onemode_pct_df %>% select(`U of Alabama (N=759)`) %>% str()
+table_1mode_pubu$onemode_pct_df %>% select(`U of Alabama (N=759)`) %>% attributes()
 ```
 
-DESCRIBE HOW TO READ TABLE AND WHAT THE RESULTS SHOW
-
-INSERT TABLE X ABOUT HERE
-
+Network graphs are useful for showing which universities have similar private high school recruiting newtworks.
 Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network.
-Generally -- whether graphing one-mode or two-mode networks -- network graphs show vertices as circles and edges as lines connecting pairs of vertices.
-In our one-mode public university network, each circle represents a public university and two universities share an edge -- represented by a dotted line -- if both universities visit at least one high school in common.
-
-For our one-mode public
-
-We address RQ3 by graphing the recruiting network and by identifying "clusters" of universities that have similar recruiting networks.
-First, network graphs show vertices (e.g., universities) as circles, with vertices that share many connections located close together and vertices that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph.
-In addition to network graphs, network scholarship often uses cluster analysis methodologies to identify vertices that share common structure, based purely on patterns of network ties.
-
-Network graphs show vertices as nodes and edges as lines connecting two nodes.
-Conceptually, we think of nodes as repelling one another and edges as pulling nodes together.
+Whether graphing one-mode or two-mode networks, network graphs show vertices as circles and edges as lines connecting pairs of vertices.
+In Figure \@ref(fig:plot-1mode-pubu),each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common.
+The width of the line between two universities indicates the number of high schools both universities visited, as identified in Tables \@ref(tab:pubu-count-matrix).
+Conceptually, we think of vertices as repelling one another and edges as pulling vertices together [@RN4725].
 Therefore, nodes that share few connections are located apart and nodes that share many connections are located close together.
-Nodes that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while nodes that are relatively disconnected are located at the periphery of the graph.
-In the analyses below, we graph the one-mode college network, using relative proximity of nodes to convey whether a pair colleges have a similar network structure.
-
-We also address research question 3 by using cluster analysis to identify colleges/universities that share common network structure.
-Many social network analyses utilize data-driven "community detection" algorithms to categorize vertices into a small number of groups (or cluster) based purely on patterns of network ties.
-Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
-We performed hierarchical cluster analysis to allocate colleges and universities into clusters based on their private high schools visits
+Vertices that are highly connected -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, vertices nodes that are relatively disconnected are located at the periphery of the graph.
 
@@
 
+Figure \@ref(fig:plot-1mode-pubu) shows the University of Alabama, University of South Carolina, and CU-Boulder at the center of the recruiting network.
+The University of Nebraska-Lincoln, SUNY Stony Brook and UC-Riverside are located on the periphery, and the remaining universities are in-between.
+Universities that share many direct (i.e., visit many of the same schools) or indirect edges tend to be located close together, for example University of Kansas and University of Arkansas, University of Geogia and UC-Berkeley.
+
+To better answer research question 3, we augment the network graphs by using cluster analysis to identify universities that share common network structure.
+Social network.
+Referred to as "community detection" in the literature, social network methodologists have developed many alternative algorithms to categorized vertices into a small number of groups (or clusters) based purely on patterns of network ties [@RN4725].
+Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
+We performed hierarchical cluster analysis to allocate universities into clusters, directing the algorithm to identify four groups.
+
+The shape of each university vertex in Figure \@ref(fig:plot-1mode-pubu) is determined by this cluster analysis.
+These clusters are largely consistent with physical layout of vertices in Figure \@ref(fig:plot-1mode-pubu).
+The University of Alabama is a cluster unto itself.
+The University of South Carolina and CU-Boulder form a cluster.
+The third cluster consists of nine universities (Arkansas, Kansas, Cincinnati, San Diego, Rutgers, Amherst, Pitt, Berkeley, and Georgia).
+Finally, the fourth cluster -- Nebraska-Lincoln, UC-Riverside, and SUNY-Stony Brook -- consists of universities that are all peripheral to the network but do not visit any high schools in common.
+
 ### Private university network
+
+Table \@ref(tab:privu-percent-matrix) and Figure \@ref(fig:plot-1mode-privu) show overlap in private high schools visited by the selective private universities in our sample.
+The networks of private universities tend to have more overlap than the network of public research universities (above).
+This is demonstrated tabularly by the higher percentages in Table \@ref(tab:privu-percent-matrix) compared to Table \@ref(tab:pubu-percent-matrix) and graphically by the thicker lines connecting universities in Figure \@ref(fig:plot-1mode-privu) compared to Figure \@ref(fig:plot-1mode-pubu).
 
@@
 
+The three most central universities in Figure \@ref(fig:plot-1mode-privu) are the universities which visited the greatest number of different private high schools, identified in parentheses: Notre Dame (625), Villanova (563), and SMU (550).
+Visually, the second tier of centrality includes TCU (435), Tulane (430), Northwestern (377), and Boston College (339).
+These results are fairly consistent with the four clusters identified by cluster analysis, in which Notre Dame and SMU are both clusters unto themselves, and Villanova is part of the third cluster which also includes Northwestern, Boston College, Tulane, and TCU.
+
+With respect to the periphery of the network -- Baylor (237), Stevens Institute (160), Marquette (331), and Case Western (228) --  Baylor visits a higher number of conservative Chrisitan high schools than any other university (see Figure \@ref(fig:religion-pubu-privu)).
+It is notable that Marquette is in the periphery despite visiting a higher number of schools than more centrally located universities (e.g., Emory), suggesting that Marquette visits many schools that are visited by few other private universities in our sample.
+
+The universities located close to one another in Figure \@ref(fig:plot-1mode-privu) tend to share relgious affiliation and/or be located in the same geographic region.
+For example, the majority of Catholic universities are located close to one another and the majority of Midwest universities are located close to one another.
+Interestingly, two of the three Christian universities -- TCU and SMU -- are located closer much closer to the Catholic universities Notre Dame and Northwestern than they are to Baylor, suggesting that Baylor visits a different set of conservative Christian high schools than TCU and SMU.
+
 ### Public and private university network
+
+Figure \@ref(fig:plot-1mode-u) shows overlap in private high schools visited amongst all 29 private and public universities in the sample, with the cluster analysis algorithm specified to identify five groups.
+
+Two clusters -- consisting of 10 universities -- emerge as the most central.
+The first cluster, consisting of four universities (with number of unique private high schools visited in parentheses), is the University of Alabama (759), Notre Dame (625), Villanova (563), and SMU (550).
+These four universities visited more private high schools than all other universities in our sample.
+[COMMENT ON NUMBER OF SCHOOLS IN COMMON].
+With respect to the characteristics of private high schools visited, these universities made a relatively large share of visits at Catholic schools, at schools in the South (less so for Notre Dame), and at low-ranked schools (less so for SMU).
+
+The second most central cluster, consisting of six universities, is the University of South Carolina (396), Northwestern (377), TCU (435), Tulane (430), CU-Boulder (362), and Boston College (339).
+With respect to characteristics of private high schools visited, these universities made a relatively large share of visits at schools in the South (less so for Boston College), and a large share of visits to Catholic and nonsectarian schools (except many visits to Christian schools by TCU), and tended to visit higher private schools than universities in the first cluster.
+
+An important substantive takeaway is that the most central universities in the network consist of a mix of private (seven universities) and public (three universities).
+When we restrict the cluster analysis to identify four groups (not shown) rather than five groups, these 10 universities become one group.
+Thus, with respect to which private high schools they visit, the seven private universities in this group seem to have more in common with the three public universities in the group than the do with other private universities in our sample.
+Similarly, the three public universities in the group seem to have more in common with the seven private universities than they do with other public universities in our sample.
+
+The third cluster consists of 5 private universities -- Emory(), Case Western (), Tufts, University of Denver, Marquette (X) -- and 2 public universities -- UMass Amherst () and University of Georgia ().
+By contrast, the fourth cluster consists of consists of 7 public universities -- UC-Berkeley, UC San Diego, University of Pittsburgh, Rutgers, University of Cincinnati, University of Kansas, and University of Arkansas -- and 2 private universities -- Baylor () and Stevens Institute of Technology ().
+While the third cluster contains more private universities than public and the fourth cluster contains more public universities than private, it is interesting that clusters did not emerge based soley on private/public.
+The only cluster that does not contain both public and private unviersities is the cluster five -- -- which consists of universities visit relatively few private high schools a
+
+BIG PICTURE TAKEWAY: WITH EXCEPTION OF MOST PERIPHERAL CLUSTER, ALL THE CLUSTERS CONTAIN BOTH PUBLIC AND PRIVATE UNIVERSTIES
+
+- for majority of clusters, cluster includes both public and private universities, suggesting a great deal of overlap across public and private universities in terms of which private high schools they target.
+
+ Northwestern (377), TCU (435), Tulane (430), Boston College (339)
+
+ Notre Dame (625), Villanova (563), and SMU (550). Visually, the second tier of centrality includes TCU (435), Tulane (430), Northwestern (377), and Boston College (339).
+
+Big picture findings:
+
+- most central clusters
+  - if k = 5 clusters, two most central clusters: 
+    - University of Alabama, Notre Dame, Villanova, and SMU
+    - University of South Carolina, Northwestern, TCU, Tulane, CU-Boulder, and Boston College.
+  - if K= 4 clusters
+    - U. Alabama, Notre Dame, Villanova, SMU, U South Carilona, Northwestern, TCU, Tulane, CU-Boulder, Boston College
+
+  - 
+most central in graph:
+
+- Bama, Notre Dame
+
+, directing the algorithm to identify four groups.
 
@@
 
+\newpage
+
+```{r enroll-pubu-privhs-pubhs, echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools vs. public high schools, public research universities"}
+include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privhs_pubhs.pdf'))
+
+```
+
+\newpage
+
 ```{r race-pubu-privu, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools"}
 include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
+```
+
+\newpage
+
+```{r race-pubu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools vs.
+public high schools, public research universities"}
+include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
 ```

### 2021-06-14 scripts/network_recruiting_analysis.R

@@ -569,6 +569,8 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
 # Usage
 plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 4)
 plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 4)
+
+plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 5, colors = c('lightblue', 'green', 'violet', 'yellow','coral'))
 plot_1mode_graph(g_2mode_u, mode = 'psi', c_analysis = 'hclust', k = 5, colors = c('lightblue', 'green', 'violet', 'yellow','coral'))
 
 # Private univs

### 2021-06-15 scripts/create_tables_figures.R
update hs count graph

@@ -140,6 +140,73 @@ plot_hs_count <- function(univ_sample, in_lim = 0, out_lim = 0, vjust = 1.5) {
   sub_events_count <- events_count %>% filter(univ_abbrev %in% univ_sample)
   sub_events_count$univ_abbrev <- factor(sub_events_count$univ_abbrev, levels = rev(univ_sample))
   
+  sub_events_privhs <- subset(sub_events_count, event_type == 'priv_hs')
+  sub_events_pubhs <- subset(sub_events_count, event_type == 'pub_hs')
+  
+  sub_events_privhs_pct <- sub_events_privhs %>%
+    pivot_wider(names_from = event_loc, values_from = count) %>% 
+    mutate(
+      tot_hs = instate + outofstate,
+      pct_outofstate = round(outofstate / tot_hs * 100),
+      label_text_cnt = tot_hs,
+      label_text_pct = str_c(pct_outofstate, '% outofstate')
+    )
+  
+  sub_events_pubhs_pct <- sub_events_pubhs %>%
+    pivot_wider(names_from = event_loc, values_from = count) %>% 
+    mutate(
+      tot_hs = instate + outofstate,
+      pct_outofstate = round(outofstate / tot_hs * 100),
+      label_text_cnt = tot_hs,
+      label_text_pct = str_c(pct_outofstate, '% outofstate')
+    )
+  
+  ggplot() +
+    geom_bar(data = sub_events_privhs, 
+             mapping = aes(x = univ_abbrev, y = count, fill = event_loc), 
+             stat = 'identity', 
+             position = 'stack', 
+             width = 0.35) +
+    geom_text(data = sub_events_privhs_pct,
+              aes(x = univ_abbrev, y = in_lim, label = str_c('Private HS (N=', label_text_cnt, ')')),
+              hjust = 0, size = 2.5) +
+    geom_text(data = sub_events_privhs_pct,
+              aes(x = univ_abbrev, y = tot_hs + 5, label = label_text_pct),
+              hjust = 0, size = 2.5) +
+    geom_bar(data = sub_events_pubhs, 
+             mapping = aes(x = as.numeric(univ_abbrev) - 0.4, y = count, fill = event_loc), 
+             stat = 'identity', 
+             position = 'stack', 
+             width = 0.35) +
+    geom_text(data = sub_events_pubhs_pct,
[…]

### 2021-06-15 text/manuscript_june_2021.Rmd
draft changes results

@@
 
-```{r, eval = FALSE, include = FALSE}
-table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
-table_1mode_pubu$onemode_pct_df %>% glimpse()
-table_1mode_pubu$onemode_pct_df
-
-table_1mode_pubu$onemode_pct_df %>% filter(row.names(table_1mode_pubu$onemode_pct_df) %in% c('CU Boulder'))
-
-table_1mode_pubu$onemode_pct_df %>% attributes()
-
-table_1mode_pubu$onemode_pct_df %>% select(`U of Alabama (N=759)`) %>% str()
-table_1mode_pubu$onemode_pct_df %>% select(`U of Alabama (N=759)`) %>% attributes()
-```
-
 Network graphs are useful for showing which universities have similar private high school recruiting newtworks.
@@
 The University of Nebraska-Lincoln, SUNY Stony Brook and UC-Riverside are located on the periphery, and the remaining universities are in-between.
-Universities that share many direct (i.e., visit many of the same schools) or indirect edges tend to be located close together, for example University of Kansas and University of Arkansas, University of Geogia and UC-Berkeley.
+Universities that share many direct (i.e., visit many of the same schools) or indirect edges tend to be located close together, for example University of Kansas and University of Arkansas.
 
-To better answer research question 3, we augment the network graphs by using cluster analysis to identify universities that share common network structure.
-Social network.
-Referred to as "community detection" in the literature, social network methodologists have developed many alternative algorithms to categorized vertices into a small number of groups (or clusters) based purely on patterns of network ties [@RN4725].
-Generally, groups are chosen to maximize the number of within-group ties while minimizing ties between members of different groups.
-We performed hierarchical cluster analysis to allocate universities into clusters, directing the algorithm to identify four groups.
+To better answer research question 3, we augment the network graphs by using cluster analysis methods -- referred to as "community detection" in the network analysis literature -- to identify groups of universities that share common network structure.
+Broadly speaking, the goal of commmunity detection is to identify "subsets of vertices that demonstrate a ‘cohesiveness’ with respect to the underlying relational patterns" [@RN4725, p.
+59], where a "cohesive subset" means a "subset of vertices that (i) are well connected among themselves, and at the same time (ii) are relatively well separated from the remaining vertices"  [@RN4725, p.
+59].
+In particular, we utilize that "cluster fast and greedy" approach developed by @RN4725, which is a variation of hierarchical cluster analysis that starts with a large number of groups and adds individual vertices to a group when doing so contributes to a cohesive subset.
 
-The shape of each university vertex in Figure \@ref(fig:plot-1mode-pubu) is determined by this cluster analysis.
-These clusters are largely consistent with physical layout of vertices in Figure \@ref(fig:plot-1mode-pubu).
-The University of Alabama is a cluster unto itself.
-The University of South Carolina and CU-Boulder form a cluster.
-The third cluster consists of nine universities (Arkansas, Kansas, Cincinnati, San Diego, Rutgers, Amherst, Pitt, Berkeley, and Georgia).
-Finally, the fourth cluster -- Nebraska-Lincoln, UC-Riverside, and SUNY-Stony Brook -- consists of universities that are all peripheral to the network but do not visit any high schools in common.
+In Figure \@ref(fig:plot-1mode-pubu), the shape of each university vertex is based on implementing this cluster fast and greedy approach with the specification that the algorithm identify four groups.
+The largest group consists of eight universities (U.
+Alabama, U.
+Arkanasas, U.
+Kansas, Nebraska-Lincoln, U.
+Georgia, U.
+South Carolina, CU-Boulder, U.
+Cincinnati).
+With the exception of CU-Boulder, these universities were located in the South and the Midwest.
+Most of these universities made a relatively high share of visits in the South.
+The next largest cluster -- UMass Amherst, University of Pittsburgh, Rutgers, and SUNY Stony Brook -- consisted of universities that were mostly located in the Northeast and visited a large share of high schools in the Northeast.
+UC-Berkeley and UC-San Diego formed a two-university cluster and UC-Riverside -- which visited fewer private schools than any other public university -- was a cluster unto itself.
 
@@
 
-The three most central universities in Figure \@ref(fig:plot-1mode-privu) are the universities which visited the greatest number of different private high schools, identified in parentheses: Notre Dame (625), Villanova (563), and SMU (550).
-Visually, the second tier of centrality includes TCU (435), Tulane (430), Northwestern (377), and Boston College (339).
-These results are fairly consistent with the four clusters identified by cluster analysis, in which Notre Dame and SMU are both clusters unto themselves, and Villanova is part of the third cluster which also includes Northwestern, Boston College, Tulane, and TCU.
+Whereas applying cluster analysis to public universities (Figure \@ref(fig:plot-1mode-pubu)) yielded three clusters that contained multiple universities, the application of cluster analysis to private universities (Figure \@ref(fig:plot-1mode-privu)) yielded a single cluster that contained 11 universities and three clusters that contained one university each.
+As suggested above, a likely explanation for this difference is that the majority of private universities had substantial overlap in the sets of private high schools visited whereas public universities tended to have substanital overlap with some public universities but not others.
 
-With respect to the periphery of the network -- Baylor (237), Stevens Institute (160), Marquette (331), and Case Western (228) --  Baylor visits a higher number of conservative Chrisitan high schools than any other university (see Figure \@ref(fig:religion-pubu-privu)).
+Visually, the most central universities in Figure \@ref(fig:plot-1mode-privu) tended to be universities that visited a large number of schools (number of unique private high schools visited in parentheses): Villanova (563), SMU (550), Notre Dame (625), Northwestern (377), Tulane (430), Boston College (339).
+The periphery of the network included Baylor (237), Stevens Institute (160), Marquette (331), and Case Western (228).
+Baylor visited a higher number of conservative Chrisitan high schools than any other university (see Figure \@ref(fig:religion-pubu-privu)).
 It is notable that Marquette is in the periphery despite visiting a higher number of schools than more centrally located universities (e.g., Emory), suggesting that Marquette visits many schools that are visited by few other private universities in our sample.
@@
 
-Figure \@ref(fig:plot-1mode-u) shows overlap in private high schools visited amongst all 29 private and public universities in the sample, with the cluster analysis algorithm specified to identify five groups.
+Figure \@ref(fig:plot-1mode-u) shows overlap in private high schools visited amongst all 29 private and public universities in the sample.
+We discuss centrality, clusters, and proximity of vertices to one another.
 
-Two clusters -- consisting of 10 universities -- emerge as the most central.
-The first cluster, consisting of four universities (with number of unique private high schools visited in parentheses), is the University of Alabama (759), Notre Dame (625), Villanova (563), and SMU (550).
-These four universities visited more private high schools than all other universities in our sample.
-[COMMENT ON NUMBER OF SCHOOLS IN COMMON].
-With respect to the characteristics of private high schools visited, these universities made a relatively large share of visits at Catholic schools, at schools in the South (less so for Notre Dame), and at low-ranked schools (less so for SMU).
+Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities that visited a large number of high schools (number of unique private high schools visited in parentheses), for example, University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), Northwestern (377), University of South Carolina (396) and CU-Boulder (362), and Boston College (339).
+Notably, while the majority of universities located near the center of Figure are private, three are public.
 
-The second most central cluster, consisting of six universities, is the University of South Carolina (396), Northwestern (377), TCU (435), Tulane (430), CU-Boulder (362), and Boston College (339).
-With respect to characteristics of private high schools visited, these universities made a relatively large share of visits at schools in the South (less so for Boston College), and a large share of visits to Catholic and nonsectarian schools (except many visits to Christian schools by TCU), and tended to visit higher private schools than universities in the first cluster.
+The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and/or characteristics of the private schools they visit -- of geographic location, religious affiliation, and academic reputation, but less so to institutional control (public vs.
+private).
+For example, the cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities that visited a relatively large share of Christian high schools.
+Second, the cluster of 13 universities -- including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley -- largely consists of universities more highly ranked universities, universities located in the Midwest or West, and Catholic universities.
+Third, the five university cluster -- Rutgers, Stevens Institute of Technology, UMass Amherst, University of Pittsburgh -- consists of universities with strong ties to the Northeast.
 
-An important substantive takeaway is that the most central universities in the network consist of a mix of private (seven universities) and public (three universities).
-When we restrict the cluster analysis to identify four groups (not shown) rather than five groups, these 10 universities become one group.
-Thus, with respect to which private high schools they visit, the seven private universities in this group seem to have more in common with the three public universities in the group than the do with other private universities in our sample.
-Similarly, the three public universities in the group seem to have more in common with the seven private universities than they do with other public universities in our sample.
+Proximity of vertices to one another also appeared to be more connected to religious affiliation, geoggraphic location, and academic reputation.
+Universities with a cmmon religious affiliation (e.g., Notre Dame, Villanova, Marquette, Boston College) tend to be close to one another.
+However, the University of Alabama, which visited a high share of Catholic schools and Christian schools is simultaneously close to catholic universities and to the Christian universities TCU and SMU.
+Similarly, the University of South Carolina, which visited a relatively high share of Christian schools, is close to TCU and SMU.
+CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located close to one another in Figure \@ref(fig:plot-1mode-u) and are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit.
 
-The third cluster consists of 5 private universities -- Emory(), Case Western (), Tufts, University of Denver, Marquette (X) -- and 2 public universities -- UMass Amherst () and University of Georgia ().
-By contrast, the fourth cluster consists of consists of 7 public universities -- UC-Berkeley, UC San Diego, University of Pittsburgh, Rutgers, University of Cincinnati, University of Kansas, and University of Arkansas -- and 2 private universities -- Baylor () and Stevens Institute of Technology ().
-While the third cluster contains more private universities than public and the fourth cluster contains more public universities than private, it is interesting that clusters did not emerge based soley on private/public.
-The only cluster that does not contain both public and private unviersities is the cluster five -- -- which consists of universities visit relatively few private high schools a
+These analyses of the private and public university network provide the most direct assessment of research question 3.
+With respect to centrality, the identification of clusters, and the proximity of vertices, we find substantial overlap in the sets of private schools visited by public universities and private universities.
+This overlap does not suggest uniformity across public and private universities.
+Rather, there exist several groups of public and private universities -- which can be defined by cluster analysis or more loosely by proximity -- that have more in common with one another than they do with other universities of the same institutional control.
 
-BIG PICTURE TAKEWAY: WITH EXCEPTION OF MOST PERIPHERAL CLUSTER, ALL THE CLUSTERS CONTAIN BOTH PUBLIC AND PRIVATE UNIVERSTIES
+```{r, eval = FALSE, include = FALSE}
+table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
+table_1mode_pubu$onemode_pct_df %>% glimpse()
+table_1mode_pubu$onemode_pct_df
 
-- for majority of clusters, cluster includes both public and private universities, suggesting a great deal of overlap across public and private universities in terms of which private high schools they target.
+table_1mode_pubu$onemode_pct_df %>% filter(row.names(table_1mode_pubu$onemode_pct_df) %in% c('CU Boulder'))
 
- Northwestern (377), TCU (435), Tulane (430), Boston College (339)
+table_1mode_pubu$onemode_pct_df %>% attributes()
 
- Notre Dame (625), Villanova (563), and SMU (550). Visually, the second tier of centrality includes TCU (435), Tulane (430), Northwestern (377), and Boston College (339).
-
-Big picture findings:
-
-- most central clusters
-  - if k = 5 clusters, two most central clusters: 
-    - University of Alabama, Notre Dame, Villanova, and SMU
-    - University of South Carolina, Northwestern, TCU, Tulane, CU-Boulder, and Boston College.
-  - if K= 4 clusters
-    - U. Alabama, Notre Dame, Villanova, SMU, U South Carilona, Northwestern, TCU, Tulane, CU-Boulder, Boston College
-
-  - 
-most central in graph:
-
-- Bama, Notre Dame
-
-, directing the algorithm to identify four groups.
-
-INSERT FIGURE \@ref(fig:plot-1mode-u-k5) ABOUT HERE
+table_1mode_pubu$onemode_pct_df %>% select(`U of Alabama (N=759)`) %>% str()
+table_1mode_pubu$onemode_pct_df %>% select(`U of Alabama (N=759)`) %>% attributes()
+```
 
@@
 
-```{r plot-1mode-u-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster, five clusters"}
-knitr::include_graphics('./../assets/figures/plot_1mode_u_k5.pdf')
+```{r plot-1mode-u-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
 ```

### 2021-06-15 scripts/network_recruiting_analysis.R

@@ -296,7 +296,7 @@ create_hclust <- function(twomode_network, mode, dist_method = 'euclidean', hclu
 create_hclust(twomode_network = g_2mode, mode = 'psi', k = 4, plot_tree = TRUE)
 create_hclust(twomode_network = g_2mode, mode = 'psi', k = 4) %>% table()
 
-
+create_hclust(twomode_network = g_2mode_pubu, mode = 'psi', k = 4, plot_tree = TRUE)
 # FUNCTION: create_fast_greedy(twomode_network, mode, <no>, <steps>, <plot_tree>)
   # twomode_network: 2-mode object
   # mode: cluster HS or univs (hs, psi)
@@ -566,32 +566,50 @@ plot_1mode_graph <- function(twomode_network, mode, c_analysis, k = NULL, h = NU
   )
 }
 
-# Usage
-plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 4)
-plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 4)
+#### Usage
+  # privu
+    plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 4)
+    plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'fast', no = 4)
+    plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'fast', no = 5, colors = c('lightblue', 'green', 'violet', 'yellow','coral'))
+    plot_1mode_graph(g_2mode_privu, mode = 'psi', c_analysis = 'hclust', k = 6, colors = c('lightblue', 'green', 'violet', 'yellow','coral','pink'))
+    
+  # public
+    plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'hclust', k = 4)
+    plot_1mode_graph(g_2mode_pubu, mode = 'psi', c_analysis = 'fast', no = 4)
 
+  # u
+    plot_1mode_graph(g_2mode_u, mode = 'psi', c_analysis = 'hclust', k = 5, colors = c('lightblue', 'green', 'violet', 'yellow','coral'))
+    plot_1mode_graph(g_2mode_u, mode = 'psi', c_analysis = 'fast', no = 4)
[…]

### 2021-06-16 scripts/create_tables_figures.R
change 1+ visit to weighed universe for HS characteristics plot

@@ -336,6 +336,13 @@ plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic
                  values_to = 'value')
   names(sub_df_universe) <- c('key', 'univ_name', 'value')
   
+  sub_df_universe_weighed <- pubhs_universe_df %>% group_by(get(var_name)) %>% 
+    summarize(`Public HS, universe (wt)` = sum(g12, na.rm = T)) %>% 
+    pivot_longer(cols = 'Public HS, universe (wt)',
+                 names_to = 'universe',
+                 values_to = 'value')
+  names(sub_df_universe_weighed) <- c('key', 'univ_name', 'value')
+  
   sub_ego_df <- ego_df %>% filter(control == !!control, type == !!type) %>% 
     mutate(univ_name = str_c(univ_name, ' (', get(str_c('univ_', plot_type)), ')'))
   
@@ -347,7 +354,7 @@ plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic
     summarise(count = n_distinct(school_id))
   names(sub_df_univs) <- c('key', 'univ_name', 'value')
   
-  sub_df <- bind_rows(sub_df_universe, sub_df_visited, sub_df_univs) %>% filter(!is.na(key))
+  sub_df <- bind_rows(sub_df_universe, sub_df_universe_weighed, sub_df_univs) %>% filter(!is.na(key))
   
   # sort univs first by characteristic if region or religion, then by ranking
   if (plot_type %in% c('region', 'religion')) {
@@ -356,7 +363,7 @@ plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic
     univ_order <- (sub_ego_df[order(sub_ego_df$univ_rank), ])$univ_name
   }
   
-  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(c('Public HS, universe', 'Public HS, 1+ visit', univ_order)))
+  sub_df$univ_name <- factor(sub_df$univ_name, levels = rev(c('Public HS, universe', 'Public HS, universe (wt)', univ_order)))
   sub_df$key <- factor(sub_df$key, levels = characteristic)
   
   ggplot(sub_df, aes(fill = key, y = value, x = univ_name)) + 
@@ -396,6 +403,13 @@ plot_characteristic_privhs <- function(plot_type, var_name, label, characteristi
                  values_to = 'value')
[…]

### 2021-06-16 text/tables_figures_june_2021.Rmd
add actual vs proportional HS plots

@@
 - % private is generally higher for out-of-state. If we include all HS (both in and out) the % actual private is usually lowered, as seen below
+- The plots are for all HS visits (not just out-of-state)
+  - `events_hs_actual_proportional_pubu.pdf`
+  - `events_hs_actual_proportional_privu.pdf`
+  - `events_hs_actual_proportional_privc.pdf`
 
@@
 }
+
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privc.pdf'))
 ```

### 2021-06-16 scripts/create_tables_figures.R

@@ -276,41 +276,134 @@ table(events_df$univ_id)
 pubhs_universe_df %>% nrow()
 privhs_universe_df %>% nrow()
 
-for (i in 1:nrow(univ_sample_df)) {
-  print(univ_sample_df[[i, 'univ_abbrev']])
-  uid <- univ_sample_df[[i, 'univ_id']]
-  ust <- univ_sample_df[[i, 'state_code']]
+
+plot_actual_proportional <- function(univ_sample, in_lim = 0, out_lim = 0, vjust = 1.5) {
   
-  visited_pub_hs <- (events_df %>% filter(univ_id == uid, event_type == 'pub_hs'))$school_id %>% unique()
-  visited_pub_state <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs))$state_code %>% unique()
-  universe_pub_hs <- (pubhs_universe_df %>% filter(state_code %in% visited_pub_state))$ncessch %>% unique()
+  sub_df_actual <- data.frame(
+    univ_abbrev = character(),
+    event_type = character(),
+    count = numeric(0),
+    stringsAsFactors=FALSE
+  )
   
-  visited_pub_state_out <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs, state_code != ust))$state_code %>% unique()
-  visited_pub_hs_out <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs, state_code != ust))$ncessch %>% unique()
-  universe_pub_hs_out <- (pubhs_universe_df %>% filter(state_code %in% visited_pub_state_out))$ncessch %>% unique()
+  sub_df_proportional <- data.frame(
+    univ_abbrev = character(),
+    event_type = character(),
+    count = numeric(0),
+    stringsAsFactors=FALSE
+  )
   
-  visited_priv_hs <- (events_df %>% filter(univ_id == uid, event_type == 'priv_hs'))$school_id %>% unique()
-  visited_priv_state <- (privhs_universe_df %>% filter(school_id %in% visited_priv_hs))$state_code %>% unique()
-  universe_priv_hs <- (privhs_universe_df %>% filter(state_code %in% visited_priv_state))$school_id %>% unique()
+  i <- 1
   
-  visited_priv_state_out <- (privhs_universe_df %>% filter(school_id %in% visited_priv_hs, state_code != ust))$state_code %>% unique()
[…]

### 2021-06-16 text/tables_figures_june_2021.Rmd
update actual proportional graphs to total num of visits instead of unique hs

@@
 - Below shows actual/proportional numbers for all vs. out-of-state HS visited
-- Numbers differ from above plots because above shows event counts (some HS can be visited multiple times) whereas below numbers count each HS once (no matter how many times they're visited)
 - % private is generally higher for out-of-state. If we include all HS (both in and out) the % actual private is usually lowered, as seen below
@@
 
-  visited_pub_hs <- (events_df %>% filter(univ_id == uid, event_type == 'pub_hs'))$school_id %>% unique()
+  visited_pub_hs <- (events_df %>% filter(univ_id == uid, event_type == 'pub_hs'))$school_id
   visited_pub_state <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs))$state_code %>% unique()
@@
 
-  visited_priv_hs <- (events_df %>% filter(univ_id == uid, event_type == 'priv_hs'))$school_id %>% unique()
+  visited_priv_hs <- (events_df %>% filter(univ_id == uid, event_type == 'priv_hs'))$school_id
   visited_priv_state <- (privhs_universe_df %>% filter(school_id %in% visited_priv_hs))$state_code %>% unique()

### 2021-06-16 scripts/create_tables_figures.R

@@ -300,7 +300,7 @@ plot_actual_proportional <- function(univ_sample, in_lim = 0, out_lim = 0, vjust
     uid <- (univ_sample_df %>% filter(univ_abbrev == uab))$univ_id
     ust <- (univ_sample_df %>% filter(univ_abbrev == uab))$state_code
     
-    visited_pub_hs <- (events_df %>% filter(univ_id == uid, event_type == 'pub_hs'))$school_id %>% unique()
+    visited_pub_hs <- (events_df %>% filter(univ_id == uid, event_type == 'pub_hs'))$school_id
     visited_pub_state <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs))$state_code %>% unique()
     universe_pub_hs <- (pubhs_universe_df %>% filter(state_code %in% visited_pub_state))$ncessch %>% unique()
     
@@ -308,7 +308,7 @@ plot_actual_proportional <- function(univ_sample, in_lim = 0, out_lim = 0, vjust
     visited_pub_hs_out <- (pubhs_universe_df %>% filter(ncessch %in% visited_pub_hs, state_code != ust))$ncessch %>% unique()
     universe_pub_hs_out <- (pubhs_universe_df %>% filter(state_code %in% visited_pub_state_out))$ncessch %>% unique()
     
-    visited_priv_hs <- (events_df %>% filter(univ_id == uid, event_type == 'priv_hs'))$school_id %>% unique()
+    visited_priv_hs <- (events_df %>% filter(univ_id == uid, event_type == 'priv_hs'))$school_id
     visited_priv_state <- (privhs_universe_df %>% filter(school_id %in% visited_priv_hs))$state_code %>% unique()
     universe_priv_hs <- (privhs_universe_df %>% filter(state_code %in% visited_priv_state))$school_id %>% unique()
     
@@ -401,9 +401,9 @@ plot_actual_proportional <- function(univ_sample, in_lim = 0, out_lim = 0, vjust
 }
 
 
-save_plot(plot_actual_proportional(univ_public_research, in_lim = -500, out_lim = 2800), 'events_hs_actual_proportional_pubu.pdf')
-save_plot(plot_actual_proportional(univ_private_national, in_lim = -200, out_lim = 1100), 'events_hs_actual_proportional_privu.pdf')
-save_plot(plot_actual_proportional(univ_private_libarts, in_lim = -200, out_lim = 850), 'events_hs_actual_proportional_privc.pdf')
[…]

### 2021-06-16 scripts/create_tables_figures.R
add alt version of HS characteristics graphs for instate/outofstate public HS

@@ -413,7 +413,7 @@ save_plot(plot_actual_proportional(univ_private_libarts, in_lim = -200, out_lim 
 # Ego tables for private HS visits currently show % for unique private HS (does not recount multiple visits to same HS)
 # View(events_df %>% filter(event_type == 'priv_hs', univ_id == '152080') %>% left_join(privhs_universe_df, by = 'school_id') %>% group_by(region) %>% summarise(count = n_distinct(school_id)) %>% mutate(pct = count / sum(count)))
 
-plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic, label_text, control = 'public', type = 'univ') {
+plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic, label_text, control = 'public', type = 'univ', loc = c('instate', 'outofstate')) {
   
   sub_df_visited <- pubhs_visited_df %>% group_by(get(var_name)) %>% 
     summarize(`Public HS, 1+ visit` = n()) %>% 
@@ -440,7 +440,7 @@ plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic
     mutate(univ_name = str_c(univ_name, ' (', get(str_c('univ_', plot_type)), ')'))
   
   sub_df_univs <- events_df %>%
-    filter(event_type == 'pub_hs') %>%
+    filter(event_type == 'pub_hs', event_loc %in% loc) %>%
     right_join(sub_ego_df %>% select(univ_id, univ_name), by = 'univ_id') %>% 
     left_join(pubhs_universe_df, by = c('school_id' = 'ncessch')) %>%
     group_by(get(var_name), univ_name) %>%
@@ -575,6 +575,16 @@ par(mar = c(0, 0, 0, 0) + 0.1, mai = c(0, 0, 0, 0))
 grid.arrange(a, b, nrow = 2, ncol = 1)
 dev.off()
 
+# pubu to pubhs (separated by instate/outofstate) + privhs (enroll)
+a <- plot_characteristic_privhs('enroll', enroll_var, enroll_title, enroll_values, enroll_keys)
+b <- plot_characteristic_pubhs('enroll', enroll_var, enroll_title, enroll_values, enroll_keys, loc = 'instate')
[…]

### 2021-06-16 text/manuscript_june_2021.Rmd
draft changes manuscript

@@
 Although selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools.
+Figure \@ref(fig:actual-proportional-pubu) (public universities) and Figure \@ref(fig:actual-proportional-privu) (private universities) show the actual number of private school visits compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.
+Figure \@ref(fig:actual-proportional-pubu) shows the actual number of private school visits exceeded the proportional number of private school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
+For UC-Berkeley, private school visits represented X% of all high school visits but would have represented Y% had UC-Berkeley visited public and private schools at the same rate.
+For the University of Georgia, which represented the extreme for public universities, private school visits represented X% of all high school visits but would have represented Y% had the university visited public and private schools at the same rate.
+Figure \@ref(fig:actual-proportional-privu) shows that this disparity between actual versus proportional visits was much greater for private universities than public universities.
+Catholic universities made the most disproportionate number of private high school visits.
+For Notre Dame, private school visits represented X% of actual visits high school visits but would have represented Y% of proportional visits.
 
-- DISCUSS TABLE COMPARING ACTUAL TO PROPORTIONAL VISITS; main point is that while private universities visit private high schools at a higher rate than public research universities, both groups visit private high schools at a higher rate than they do public high schools; note the exceptions to this statement and note that public research universities that are closer to the behavior of private universities (e.g., university of Georgia)
+INSERT FIGURE \@ref(fig:actual-proportional-pubu) AND FIGURE \@ref(fig:actual-proportional-privu) ABOUT HERE
 
@@
 
+# Discussion
+
+## Summary
+
+This chapter analyzes recruiting visits to private high schools, which were made during the 2017 calendar year, for a convenience sample of 15 public research universities and 14 private universities ranked in the top 100 of US News National Universities.
+Our goal was to learn about public research universities, by analyzing their behavior and comparing their behavior to that of selective private universities.
+
+Research question 1 asks about the scale of visits to private high schools.
+All private universities in our sample made a disproportionate number of visits to private high schools (Figure X) and, for about half of these universities, visits to private high schools represented about 50% or more of all high school visits.
+For most public research universities in our sample, the scale and relative scale -- as a percentage of all HS visits -- of visits to private high schools was smaller than that of most selective private universities.
+However, X of the 15 public universities visited a disproportionate number of private high schools (Figure X) and that vast majority of these private school visits were to out-of-state private schools.
+Additionally, several public research universities -- University of Alabama, CU-Boulder, University of South Caroline -- visited private high schools at a scale that exceeded most private universities.
+Moreover, X of
+
+Research question 2 asks about the characteristics of visited private high schools.
+We analyzed geographic region, religious affiliation, high school rank, 12th grade enrollment, and racial composition.
+Bot public and private universities in our sample tended to make disproportionate number of visits in their home geographic region, with highly ranked universities making more visits to schools in other regions.
+The majority of universities -- even those located outside the south --  visited a large number of private schools located in the south.
+Unsurprisingly, sectarian private universities made a large share of visits to private high schools of a similar religious affiliation.
+Given that public universities are nonsectarian organizations, a surprising finding is that the majority of public universities in our sample made a large share of visits to Catholic or Christian private schools.
+
+With the exception of UC-Berkeley and UC-San Diego, the academic rating of private schools visited by public universities was lower than the rating of those visited by most private universities.
+This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked as a top 100 National University by US News.
+Nevertheless, the large number of visits to low-rated private schools by public universities, combined with the fact that that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private schools primarily in search of full-pay students rather than academic superstars.
+
+Across the universe of private high schools, most schools enroll relatively few students who identify as Black, Latinx, or Native.
+For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools.
+By contrast, the public high schools visited by public universities tended to enroll a much higher share students who identify as Black, Latinx, or Native.
+
+Research question 3 asks about overlap in the private school recruiting networks of public and private universities.
+Within the sample of public universities, we observed substantial overlap and variation in recruiting networks.
+For example, the recruiting networks of the the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass Amherst and Rutgers, which share substantial overlap with one another.
+Across the entire sample of public and private universities, we also observed substantial overlap and variation in recruiting networks.
+Whether we are categorizing universities by cluster analysis or by proximity on the network graph, we observe several different subsets of universities.
+Each of these subsets is associated with a different approach to private school visits and -- with the exception of a couple outliers like UC-Riverside and SUNY Stony Brook -- each of these subsets contains both public and private universities.
+
+## Privatization of Public Research Universities
+
+These findings contribute new insights about the privatization of public research universities.
+A weakness of the scholarly literature on privatization is that few studies compare public and private universities with respect to a behavior that is associated with private universities.
+
+We conceptualize recruiting visits to private schools as a behavior that is consistent with the social reproduction orientation of selective private universities and contrary to the historic social mobility mission associated with public research universties.
+In making large-scale visits to out-of-state private high schools, we argue that public research universities are mimicking the behavior selective private universities in order to compete for students that have been traditionally targeted by private universities.
+Our rationale for this statement is that selective private universities have been recruiting heavily from private schools for a long time [CITE].
+By contrast, the pursuit of out-of-state students is a relatively new phenomenon for most public research universities.
+
+Although our analyses cannot yield insight about the extent to the population of public research universities are visiting private schools (because we have a convenience sample rather than a random sample), we can make statements about variation in how public universities in our sample went about visiting private schools.
+At one end of the spectrum -- represented by UC-Riverside and SUNY Stony Brook -- some public research universities are not engaging in recruiting visits to private schools.
+For those public universities that make a substantial number of private school visits, we see substantial variation in the scale of visits and the characteristics of schools they target.
+Similarly, we see variation in the scale and characteristics of private schools visited by private universities.
+Several different groups emerge, with each group associated with a different broad approach to private schools and each group containing some mix of public and private universities.
+
+Therefore, when making decisions about scale of private school visits and which schools to visit, public research universities seem to be mimicking the behavior of particular kinds of private universities.
+For examle BAMA AND NOTRE DAME
+
 # References
@@
 
+```{r actual-proportional-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
+```
+
+\clearpage
+
+```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, private universities"}
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
+```
+
+\clearpage
+
 ```{r region-pubu-privu, echo = FALSE, fig.cap = "Geographic region of visited private high schools"}

### 2021-06-16 text/tables_figures_june_2021.Rmd
add 1-mode matrix tables by cluster for public + private universities

@@
   column_spec(11, width = '6em')
+
+table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
+
+kable(table_1mode_u$clusters_df[order(match(table_1mode_u$clusters_df$univ_abbrev, rownames(table_1mode_u$onemode_df))), ], caption = 'Clusters for public and private universities')
+
+cluster_1 <- c(13, 17, 21, 26, 27)
+cluster_2 <- c(2, 3, 6, 8, 9, 10, 11, 12, 14, 15, 20, 22, 23)
+cluster_3 <- c(1, 4, 5, 7, 16, 18, 19, 24, 25, 28)
+cluster_4 <- 29
+
+kable(table_1mode_u$onemode_df[cluster_1, cluster_1], caption = 'Public and private universities count matrix (cluster 1)') %>%
+  kable_styling(latex_options = 'scale_down')
+
+kable(table_1mode_u$onemode_pct_df[cluster_1, cluster_1], caption = 'Public and private universities percent matrix (cluster 1)') %>%
+  kable_styling(latex_options = 'scale_down')
+
+kable(table_1mode_u$onemode_df[cluster_2, cluster_2], caption = 'Public and private universities count matrix (cluster 2)') %>%
+  kable_styling(latex_options = 'scale_down')
+
+kable(table_1mode_u$onemode_pct_df[cluster_2, cluster_2], caption = 'Public and private universities percent matrix (cluster 2)') %>%
+  kable_styling(latex_options = 'scale_down')
+
+kable(table_1mode_u$onemode_df[cluster_3, cluster_3], caption = 'Public and private universities count matrix (cluster 3)') %>%
+  kable_styling(latex_options = 'scale_down')
+
+kable(table_1mode_u$onemode_pct_df[cluster_3, cluster_3], caption = 'Public and private universities percent matrix (cluster 3)') %>%
+  kable_styling(latex_options = 'scale_down')
+
 ```

### 2021-06-16 scripts/network_recruiting_analysis.R

@@ -643,11 +643,11 @@ privhs_events_unique <- privhs_events %>%
   left_join(univ_info %>% select(univ_id, univ_abbrev, classification), by = 'univ_id') %>% 
   group_by(classification, univ_id, univ_abbrev) %>% 
   summarise(count = n_distinct(school_id)) %>% 
-  arrange(classification, desc(count))
+  arrange(desc(count))
 
 create_1mode_table <- function(onemode_network, univ_type) {
   
-  privhs_events_unique_df <- privhs_events_unique %>% filter(classification == univ_type)
+  privhs_events_unique_df <- privhs_events_unique %>% filter(classification %in% univ_type)
   
   # Get N = number of unique private HS visited by each univ (order univ same way as igraph)
   num_unique_privhs_visited <- privhs_events_unique_df[match(vertex_attr(graph=onemode_network, name='name'), privhs_events_unique_df$univ_id), ]$count
@@ -713,6 +713,19 @@ saveRDS(table_1mode_privu, file = './assets/tables/table_1mode_privu.RDS')
 # Private colleges
 table_1mode_privc <- create_1mode_table(g_1mode_privc_psi, 'private_libarts')
 saveRDS(table_1mode_privc, file = './assets/tables/table_1mode_privc.RDS')
+
+# Public and private universities
+table_1mode_u <- create_1mode_table(g_1mode_u_psi, c('public_research', 'private_national'))
+
+intersect((privhs_events %>% filter(univ_id == '100751'))$school_id, (privhs_events %>% filter(univ_id == '152080'))$school_id) %>% length()  # 326 private HS are the same between U of Alabama & Notre Dame (unique)
+
+clusters_u <- create_fast_greedy(twomode_network = g_2mode_u, mode = 'psi', no = 4, plot_tree = F)
+get_cluster <- Vectorize(function(u) clusters_u[[u]])
+
+clusters_df <- univ_info %>% filter(classification != 'private_libarts') %>% select(univ_abbrev, classification, univ_id) %>% mutate(cluster = get_cluster(univ_id)) %>% arrange(cluster)
+table_1mode_u$clusters_df <- clusters_df
+
+saveRDS(table_1mode_u, file = './assets/tables/table_1mode_u.RDS')
 
 
 ## ------------------------------

### 2021-06-18 text/manuscript_june_2021.Rmd
finished rough draft

@@
       - \usepackage{setspace}
-      - \doublespacing
+      #- \doublespacing
       - \floatsetup{capposition=top}
@@
 
-Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools for for public research universities (Figure \@ref(fig:events-hs-count-pubu)) and selective private universities (Figure \@ref(fig:events-hs-count-privu)), with separate bars for in-state and out-of-state visits.
+[CRYSTAL - REVISE TEXT IN THIS PARAGRAPH AND MAYBE THE NEXT TO REFLECT CHANGES WE MADE TO THIS FIGURE] Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools for public research universities (Figure \@ref(fig:events-hs-count-pubu)) and selective private universities (Figure \@ref(fig:events-hs-count-privu)), with separate bars for in-state and out-of-state visits.
 Only three of the 15 public research Universities -- UC-Berkeley, UC-San Diego, and UC-Riverside -- made more in-state than out-of-state high school visits.
@@
 Figure \@ref(fig:plot-1mode-u) shows overlap in private high schools visited amongst all 29 private and public universities in the sample.
-We discuss centrality, clusters, and proximity of vertices to one another.
 
-Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities that visited a large number of high schools (number of unique private high schools visited in parentheses), for example, University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), Northwestern (377), University of South Carolina (396) and CU-Boulder (362), and Boston College (339).
+The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and characteristics of the schools they visit -- of geographic location, religious affiliation, academic reputation, and also institutional control.
+The cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities that visited a relatively large share of Christian high schools.
+Second, the cluster of 13 universities -- including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley -- largely consists of universities more highly ranked universities, universities located in the Midwest or West, and Catholic universities.
+Third, the five university cluster -- Rutgers, Stevens Institute of Technology, UMass Amherst, University of Pittsburgh -- largely consists of public universities with with strong ties to the Northeast.
+
+INSERT FIGURE \@ref(fig:plot-1mode-u) ABOUT HERE
+
+<!--
+
+Tables \@ref(tab:u-cluster1-percent-matrix), \@ref(tab:u-cluster2-percent-matrix), and \@ref(tab:u-cluster3-percent-matrix) show overlap in the percent of private high schools 
+INSERT TABLE \@ref(tab:u-cluster1-percent-matrix) TABLE \@ref(tab:u-cluster2-percent-matrix) AND TABLE \@ref(tab:u-cluster3-percent-matrix) ABOUT HERE
+-->
+
+Universities located near the center of Figure \@ref(fig:plot-1mode-u) do not all belong to the same cluster and, more broadly, universities located close to one another do not all belong to the same cluster.
+Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities with the highest degree centrality -- i.e., that visited most schools visited.
+The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses) University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), Northwestern (377), University of South Carolina (396), and CU-Boulder (362).
 Notably, while the majority of universities located near the center of Figure are private, three are public.
 
-The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and/or characteristics of the private schools they visit -- of geographic location, religious affiliation, and academic reputation, but less so to institutional control (public vs.
-private).
-For example, the cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities that visited a relatively large share of Christian high schools.
-Second, the cluster of 13 universities -- including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley -- largely consists of universities more highly ranked universities, universities located in the Midwest or West, and Catholic universities.
-Third, the five university cluster -- Rutgers, Stevens Institute of Technology, UMass Amherst, University of Pittsburgh -- consists of universities with strong ties to the Northeast.
-
-Proximity of vertices to one another also appeared to be more connected to religious affiliation, geoggraphic location, and academic reputation.
-Universities with a cmmon religious affiliation (e.g., Notre Dame, Villanova, Marquette, Boston College) tend to be close to one another.
+Proximity of vertices to one another in Figure \@ref(fig:plot-1mode-u) appeared to be more connected to religious affiliation, geoggraphic location, and academic reputation.
+Universities with a common religious affiliation (e.g., Notre Dame, Villanova, Marquette, Boston College) tend to be close to one another.
 However, the University of Alabama, which visited a high share of Catholic schools and Christian schools is simultaneously close to catholic universities and to the Christian universities TCU and SMU.
 Similarly, the University of South Carolina, which visited a relatively high share of Christian schools, is close to TCU and SMU.
-CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located close to one another in Figure \@ref(fig:plot-1mode-u) and are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit.
+CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located close to one another in Figure \@ref(fig:plot-1mode-u).
+These three universities are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit.
+
+Finally, Table \@ref(tab:privu-percent-visited-by-pubu-matrix) shows, for each private university, the percent of schools that were also visited by each public university.
+This table shows the extent to which public universities were competing at private schools targeted by private universities.
+For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.5% of these schools.
+Similarly, CU-Boulder visited 46.4 of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
+The University of Arkansas competed heavily at schools visited by Baylor, Rutgers and UMass Amherst competed heavily at schools visited by Stevens Institute of Technology, while UC Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
+
+INSERT TABLE \@ref(tab:privu-percent-visited-by-pubu-matrix) ABOUT HERE
 
 These analyses of the private and public university network provide the most direct assessment of research question 3.
-With respect to centrality, the identification of clusters, and the proximity of vertices, we find substantial overlap in the sets of private schools visited by public universities and private universities.
+Considering the identification of clusters, centrality, and proximity of vertices, we find substantial overlap in the sets of private schools visited by public universities and private universities.
 This overlap does not suggest uniformity across public and private universities.
@@
 Whether we are categorizing universities by cluster analysis or by proximity on the network graph, we observe several different subsets of universities.
-Each of these subsets is associated with a different approach to private school visits and -- with the exception of a couple outliers like UC-Riverside and SUNY Stony Brook -- each of these subsets contains both public and private universities.
+Each of these subsets is associated with a different approach to private school visits and -- with the exception of a few universities like UC-Riverside and SUNY Stony Brook -- each of these subsets contained both public and private universities.
 
@@
 These findings contribute new insights about the privatization of public research universities.
-A weakness of the scholarly literature on privatization is that few studies compare public and private universities with respect to a behavior that is associated with private universities.
+A weakness of the scholarly literature on privatization is that few studies compare public and private universities with respect to a behavior that is associated with private universities [@RN4543].
+We conceptualize recruiting visits to private schools as a behavior that is consistent with the social reproduction orientation of selective private universities and contrary to the historic social mobility mission associated with public research universties.
+Although we cannot make statements about the population of public research universities (ours is a convenience sample rather than a random sample), we can describe variation in how the public universities in our sample went about visiting private schools.
 
-We conceptualize recruiting visits to private schools as a behavior that is consistent with the social reproduction orientation of selective private universities and contrary to the historic social mobility mission associated with public research universties.
+At one end of the continuum lie public research universities that do not play the game, for example UC-Riverside and SUNY Stony Brook, visiting private schools at a lower rate than public schools (Figure \@ref(fig:actual-proportional-pubu)).
+For public universities that visited a substantial number of private schools, we observe substantial variation in the scale of visits and the characteristics of schools they target.
+While all private universities in our sample visited private schools at a much higher rate than public schools, we also see substantial variation amongst private universities in the scale and characteristics of private school visits.
+Amongst the network of public and private universities, Figure \@ref(fig:plot-1mode-u) shows that three clusters emerge -- each containing some mix of public and private universities.
+The universities within a cluster some overlap in the kinds of schools visited (e.g., TCU and University of South Carilina), but also share substantial overlap with particular universities in different clusters (e.g., Tufts and University of Pittsburgh).
+
 In making large-scale visits to out-of-state private high schools, we argue that public research universities are mimicking the behavior selective private universities in order to compete for students that have been traditionally targeted by private universities.
-Our rationale for this statement is that selective private universities have been recruiting heavily from private schools for a long time [CITE].
+Our rationale for this statement is that selective private universities have been recruiting heavily from private schools for a long time [@RN4642; @RN1565; @RN4407].
 By contrast, the pursuit of out-of-state students is a relatively new phenomenon for most public research universities.
 
-Although our analyses cannot yield insight about the extent to the population of public research universities are visiting private schools (because we have a convenience sample rather than a random sample), we can make statements about variation in how public universities in our sample went about visiting private schools.
-At one end of the spectrum -- represented by UC-Riverside and SUNY Stony Brook -- some public research universities are not engaging in recruiting visits to private schools.
-For those public universities that make a substantial number of private school visits, we see substantial variation in the scale of visits and the characteristics of schools they target.
-Similarly, we see variation in the scale and characteristics of private schools visited by private universities.
-Several different groups emerge, with each group associated with a different broad approach to private schools and each group containing some mix of public and private universities.
+When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
+Several public universities seem to be competing directly for students targeted by a particular private university.
+For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory.
+We reason UC-Berkeley is competing directly for students because all four universities are in the same broad echelon of prestige.
+Other potential examples of direct competition include the University of Georgia targeting schools visited by Emory, SMU, TCU, and Tulane, or the University of Arkansas targeting schools visited by Baylor.
 
-Therefore, when making decisions about scale of private school visits and which schools to visit, public research universities seem to be mimicking the behavior of particular kinds of private universities.
-For examle BAMA AND NOTRE DAME
+However, public universities that made the greatest number of private school visits seemed to be targeting lower-achieving students at private schools targeted by particular private universities.
+For example, the University of Alabama visited 52.2% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools.
+Given the differences in academic prestige between, the University of Alabama may not be competing for the same students as Notre Dame.
+Instead, they found a niche by targeting Catholic school students of a similar economic echelon, who have lower academic achievement, and want to attend a football powerhouse.
+Additionally, CU-Boulder visited 42.4% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
+Similarly, the University of South Carolina competes heavily at schools targeted by Emory, SMU, TCU, and Tulane.
+
+Finally, all public universities that visited a substantial number of private schools tended to visit schools that enrolled few Black, Latinx, or Native students.
+This finding is substantially driven by the fact that the national universe of private schools tend to enroll a much lower share of Black, Latinx, or Native students than the universe of public schools.
+However, the the set of schools visited by the public universities in our sample enrolled fewer Black, Latinx, and Native students than the universe of private schools.
+Although we do not have data on household income, it is likely that the majority of students are wealthy at the private schools visited by public universities in our sample.
+
+Therefore, while public universities playing the private school game differ in terms of the set of school they target, they all seem to be targeting schools that enroll mostly affluent students and few students who identify as Black, Latinx, or Native.
+To the extent that these recruiting efforts yield dividends in terms of incoming freshmen, playing the private school game is likely to change the enrollment composition of public research universities in ways that run contrary to racial and socioeconomic diversity.
 
@@
 
+\begin{landscape}
+
 ```{r pubu-count-matrix}
@@
 
+\clearpage
+
+```{r u-cluster1-percent-matrix, include=FALSE}
+table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
+
+#kable(table_1mode_u$clusters_df[order(match(table_1mode_u$clusters_df$univ_abbrev, rownames(table_1mode_u$onemode_df))), ], caption = 'Clusters for public and private universities')
+
+cluster_1 <- c(1, 4, 5, 7, 16, 18, 19, 24, 25, 28)
+cluster_2 <- c(2, 3, 6, 8, 9, 10, 11, 12, 14, 15, 20, 22, 23)
+cluster_3 <- c(13, 17, 21, 26, 27)
+cluster_4 <- 29
+
+kable(table_1mode_u$onemode_pct_df[cluster_1, cluster_1], caption = 'Public and private universities percent matrix (cluster 1)') %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r u-cluster2-percent-matrix, eval=FALSE}
+kable(table_1mode_u$onemode_pct_df[cluster_2, cluster_2], caption = 'Public and private universities percent matrix (cluster 2)') %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r u-cluster3-percent-matrix, eval=FALSE}
+kable(table_1mode_u$onemode_pct_df[cluster_3, cluster_3], caption = 'Public and private universities percent matrix (cluster 3)') %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r u-top-percent-matrix, eval=FALSE}
+kable(table_1mode_u$onemode_pct_df[c(1,2,3,4,5,6,7,8,9),c(1,2,3,4,5,6,7,8,9)], caption = 'Public and private universities, highest degree centrality') %>%
+  kable_styling(latex_options = 'scale_down')
+```
+
+```{r privu-percent-visited-by-pubu-matrix}
+kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  #column_spec(1, width = '8.5em') %>%
+  column_spec(2:15, width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em')
+```
+
+\end{landscape}
+
+\restoregeometry
+
 <!-- FIGURES -->
@@
 \newpage
-
-\newgeometry{top=1in, left=0cm, right=0cm, bottom=0cm}
 
@@
 
-```{r plot-1mode-u-k5, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
+```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
 knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')

### 2021-06-26 text/manuscript_june_2021.Rmd
copy-edit draft

@@
   - Crystal Han
-  - Irma Castaneda
+  - Irma Castañeda
 bibliography: ./../other/burd_recruiting_chapter.bib
@@
 Prior to the pandemic, admissions counselors from colleges and universities traveled to local high schools each year in order to meet prospective students and maintain relationships with guidance counselors at feeder schools [@RN3519].
-@RN4721 analyzed off-campus recruitiving visits made in 2017 by 15 public research universities.
+@RN4721 analyzed off-campus recruiting visits made in 2017 by 15 public research universities.
 Surprisingly, 12 of the 15 universities made more visits to *out-of-state* high schools than *in-state* high schools.
@@
 
+<!--
+Note: The data for this book chapter will be slightly different due to using 2017-18 CCD data plus modified criteria (no longer excluding HS w/ certain school types) - but % is still similar
+
+UC Berkeley: 171 (42%) of 404 out-of-state HS visits are to private schools
+CU Boulder: 381 (38%) of 1008 out-of-state HS visits are to private schools
+-->
+
 Whereas @RN4721 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
@@
 The mission of selective private colleges and universities is more squarely associated with social reproduction rather than social mobility.
-Historically, these institutions depend on patronage from philanthropic interests -- in connection with business and religious interests -- and depend from wealthy households who provide tuition revenue and donations [@RN4517].
+Historically, these institutions depend on patronage from philanthropic interests -- in connection with business and religious interests -- and on wealthy households who provide tuition revenue and donations [@RN4517].
 In turn, selective private institutions contribute to social reproduction by providing access to their patrons.
 The "Chetty" data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile [@RN4722; @RN4723].
-A significant caveat is that religiously affiliated universities may prioritize enrollment opportunities for students of the same faith regardless of wealth, but even here the mission is to benefit families from a particular cultural status group [CITE].
+A significant caveat is that religiously affiliated universities may prioritize enrollment opportunities for students of the same faith regardless of wealth, but even here the mission is to benefit families from a particular cultural status group.
+<!-- [CITE] -->
 
@@
 Public research universities are designated the unique responsibility of educating the future civic, professional, and business leaders of the state.
-Quoting 19th century University of Michigan President James Angell, these institutions contribute to social mobility by providing “an uncommon education for the common man” [as cited in @RN3608, p.
+Quoting 19th century University of Michigan President James Angell, these institutions contribute to social mobility by providing "an uncommon education for the common man" [as cited in @RN3608, p.
 279] who could not afford tuition at elite private institutions.
@@
 Recruiting visits to private high schools are consistent with the social reproduction mission of selective private universities, regardless of whether the university is targeting a particular high school because of its academic reputation, religious affiliation, or the affluence of its student body.
-By contrast, for public research universities, visits to private high schools -- particularly out-of-state schools -- are antithetical to mission of social mobility for high-achieving, low-income state residents.
+By contrast, for public research universities, visits to private high schools -- particularly out-of-state schools -- are antithetical to the mission of social mobility for high-achieving, low-income state residents.
 
 Analyses of recruiting visits to private high schools can contribute novel insights about the "privatization" of public research universities.
-Within the scholarly literature on privatization, one strand of scholarship conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization [@RN4543@; @RN2101].
+Within the scholarly literature on privatization, one strand of scholarship conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization [@RN4543; @RN2101].
 Of relevance to this chapter, public research universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753], who typically pay two- to three-times more than resident students.
@@
 Our primary goal is to learn about public research universities, using the behavior of private universities as a benchmark to develop more thoughtful insights about public research universities.
-We analyze recruiting visits made in 2017 calendar year by a sample of 15 public research universities, 14 selective private universities, and 12 selective private liberal arts colleges.
+We analyze recruiting visits made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
+<!-- and 12 selective private liberal arts colleges.
+-->
 
 Because little is known about recruiting at private high schools by public universities, we conduct descriptive analyses that seek to identify basic patterns and relationships.
-Because a recruiting visit to a private high school is an indicator of a relationship between two actors, we also utilize social network methods in order to compare the recruiting networks of public universities to those of private universities.
+Because a recruiting visit to the same private high school is an indicator of a relationship between two actors, we also utilize social network methods in order to compare the recruiting networks of public universities to those of private universities.
 Analyses are informed by the following three research questions:
@@
 
-SHORT PARAGRAPH GIVING OUTLINE OF CHAPTER
+<!-- SHORT PARAGRAPH GIVING OUTLINE OF CHAPTER -->
 
@@
 
-## Situating Off-Campus Recruiting Within Enrollment Management
+## Situating off-campus recruiting within enrollment management
 
@@
 Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411]<!--[CITE OTHER]-->.
-Given the the rise in "stealth applicants" who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.
+Given the rise in "stealth applicants" who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.
 
@@
 
-## Empirical Scholarship from Sociology
+## Empirical scholarship from sociology
 
@@
 
-Empirical academic scholarship on off-campus recruiting is mostly limited to a modest number of sociological case studies, which typically analyze off-campus recruiting as part of a broader analysis of enrollment management [e.g., @RN4324; @RN3519; @RN4538; @RN4520; @RN4407].
+Empirical academic scholarship on off-campus recruiting is mostly limited to a modest number of sociological case studies, which typically analyze off-campus recruiting as part of a broader analysis of enrollment management [e.g., @RN4538; @RN4324; @RN3519; @RN4520; @RN4407].
 @RN4324 analyzes visits from the perspective of students at two racially and socioeconomically diverse public high schools.
 @RN4324 found that high school visits -- including college fairs, instant decision events, and small-group representative visits -- influenced where students applied and where they enrolled.
-This finding was strongest for first-generation students and under-represented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college" (p.
-XXX) This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and made them feel wanted.
+This finding was strongest for first-generation students and underrepresented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college" (p.
+XXX).
+This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and made them feel wanted.
 For example, @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more" (p.
 XXX).
-By contrast, affluent students with college educated parents were less taken by such overtures and more concerned with college prestige.
-
-@RN3519, an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of off-campus recruiting visits.
+By contrast, affluent students with college-educated parents were less taken by such overtures and more concerned with college prestige.
+
+@RN3519, in an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of off-campus recruiting visits.
 Stevens [-@RN3519, p.
@@
 The College tended to visit the same "feeder" schools year after year because recruiting depends on long-term relationships with high schools.
-The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and had the resources and motivation to host a successful visit.
+The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and have the resources and motivation to host a successful visit.
 Whereas @RN4402 highlights the effect of recruiting visits on inquiries and enrollees, findings from @RN3519 suggest that the College may have valued recruiting visits primarily as a means of maintaining relationships with guidance counselors.
-From this perspective, recruiting visits may affect outcomes such as inquiries, applications, and matriculation through their affect on high school guidance counselors.
+From this perspective, recruiting visits may affect outcomes such as inquiries, applications, and matriculation through their effect on high school guidance counselors.
 The logic is that a guidance counselor who views a college favorably will steer students to the college.
@@
 The college "might stop taking these telephone calls and ignore the information provided.
-They may even start accepting fewer students from the school, thinking it is less than an honest" [@RN4321, p.
+They may even start accepting fewer students from the school, thinking it is less than an honest place" [@RN4321, p.
 106].
@@
 Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another.
-Without a strong relationship, it unlikely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
-Even in the absence of horsetrading described by @RN4407, relationships enable the college admissions counselor and the high school guidance counselor to tell one another "their story" and relay that story to constituents [@RN3519].
+Without a strong relationship, it is unlikely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
+Even in the absence of the horsetrading described by @RN4407, relationships enable the college admissions counselor and the high school guidance counselor to tell one another "their story" and relay that story to constituents [@RN3519].
 The college admissions counselor explains why the college/university is a "special place" that high school students should want to attend [@RN3519].
@@
 
-Having conceptualized a recruiting visit as an indicator of a social relation, this section introduces basic concepts from social network analysis and motivate the research questions that guide empirical analyses.
+Having conceptualized a recruiting visit as an indicator of a social relation, this section introduces basic concepts from social network analysis and motivates the research questions that guide empirical analyses.
 
@@
 
-Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
+Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network, each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
 For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
 The most commonly analyzed two-mode network in social networks literature is a corporate board-director network  [e.g., @RN4663].
-These networks consists of directors (mode 1) and organizational boards (mode 2) and a particular director shares an edge with a particular organizational board if they sit on that board.
-Similarly, our recruiting visit data form a two-mode network, consisting of private high schools (mode 1) and college (mode 2).
+These networks consist of directors (mode 1) and organizational boards (mode 2), and a particular director shares an edge with a particular organizational board if they sit on that board.
+Similarly, our recruiting visit data form a two-mode network, consisting of private high schools (mode 1) and colleges (mode 2).
 An off-campus recruiting visit from a college/university to a private high school is the "edge" that connects two particular vertices.
-In this network, edges can only occur between vertices of a different type; that is a college can visit a high school, but colleges cannot visit other colleges and high schools cannot receive visits from other high schools.
+In this network, edges can only occur between vertices of a different type; that is, a college can visit a high school, but colleges cannot visit other colleges and high schools cannot receive visits from other high schools.
 
@@
 
-In social network analysis, *centrality* refers to the importance or prominence or "being in the middle of things" of an actor/vertex in a social network [CITE].
-Many alternative measures of centrality have been developed.
+In social network analysis, *centrality* refers to the importance or prominence or "being in the middle of things" of an actor/vertex in a social network.<!--[CITE]--> Many alternative measures of centrality have been developed.
 All measures agree that centrality is an actor/vertex-level construct (e.g., each college in our network will have a centrality value, regardless of which centrality measure we use).
@@
 The simplest measure of centrality, *degree centrality* measures the number of edges directly connected to a vertex.
-For each college in our network, degree centrality is simply the number of different private high schools visited by the college.
-For each high school in our network, degree centrality is simply the number of colleges in our network that visited the high school.
+For each college in our two-mode network, degree centrality is simply the number of different private high schools visited by the college.
+For each high school in our network, degree centrality is the number of colleges in our network that visited the high school.
 Social network theory conceptualizes degree centrality as a measure of "local" centrality, capturing the number of direct connections for each actor/vertex.
-For our empirical context, we conceive of degree centrality as a measure of scale of the number of private high schools a college visits and, equivalently, the number of private high schools we observe haging a social relation with each college.
+For our empirical context, we conceive of degree centrality as a measure of scale of the number of private high schools a college visits and, equivalently, the number of private high schools we observe having a social relation with each college.
 Given that we conceptualize visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges/universities, we are interested in comparing how scale differs between public and private colleges/universities.
-This interest motivates research question 1, "how does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?" We answer this research question by comparing degree centrality across universities.
+This interest motivates research question 1, "How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?" We answer this research question by comparing degree centrality across universities.
 
@@
 
-Degree is a limited measure of centrality in that only identifies direct connections.
-By contrast, *k-path centrality* centrality measures the extent to which an actor/vertex is indirectly connected to others, *betweenness centrality* measures the extent to which a vertex is an intermediary between otherwise disconnected groups of actors, and *eigenvector centrality* measures the extent to which a vertex is connected to highly connected others.
+Degree is a limited measure of centrality in that it only identifies direct connections.
+By contrast, *k-path centrality* measures the extent to which an actor/vertex is indirectly connected to others, *betweenness centrality* measures the extent to which a vertex is an intermediary between otherwise disconnected groups of actors, and *eigenvector centrality* measures the extent to which a vertex is connected to highly-connected others.
 Betweenness centrality tends to be relevant for empirical contexts (e.g., which manager gets credit for an idea) where an actor who occupies a position between groups can benefit by being a broker of information/ideas [@RN975].
@@
 
-A common finding in social networks research is that actors are more likely to form connections with actors who are are similar to them [@RN1722].
+A common finding in social networks research is that actors are more likely to form connections with actors who are similar to them [@RN1722].
 Said differently, ego networks are biased towards "homophily" rather than "heterophily." Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be friends on Facebook if they have similar political ideologies).
@@
 First, prior scholarship suggests that private colleges and private high schools are more likely to have a relationship when they share common ideologies or view themselves as belonging to the same echelon [@RN3519; @RN4321;@RN4407].
-Second, with respect to our substantive interest the behavior of public research universities, the characteristics of visited private high schools have consequences for subsequent enrollment composition of public research universities.
+Second, with respect to our substantive interest in the behavior of public research universities, the characteristics of visited private high schools have consequences for subsequent enrollment compositions of public research universities.
 Therefore, we are interested in whether universities tend to visit high schools that are similar to them on certain characteristics.
@@
 
-Decisions about which private school characteristics to analyze were informed by prior research [e.g., @RN4504; @RN4321; @RN3519; @RN4588; @RN4724].
+Decisions about which private school characteristics to analyze were informed by prior research [e.g., @RN4724; @RN4504; @RN4321; @RN3519; @RN4588].
 In particular, @RN4504 used data from several national surveys to analyze long-term trends in private school enrollment by family income.
@@
 With respect to family income, the private school enrollment rate of high-income families (around 17%) and low-income families (around 4%) remained stable over time, but the enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
-These declines were substantially driven by declines in the number of students attending Catholic school, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
+These declines were substantially driven by declines in the number of students attending Catholic schools, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
 Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
@@
 However, for high income families, rates of private school enrollment do not differ substantially across race.
-In the South, there has been a long-term increase in private school enrollment, driven by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsetarian private schools by high-income families.
+In the South, there has been a long-term increase in private school enrollment, driven by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsectarian private schools by high-income families.
 
@@
 We analyze academic reputation based on the idea that more highly ranked colleges are likely to target highly ranked private high schools.
-Racial composition is of substantive interest because the racial composition of visited high schools has consequences for the rational composition of colleges and universities.
-Given our interests in social reproduction versus social mobility, we would also analyze tuition price and household income, but these data are not avalable for private high schools.
+Racial composition is of substantive interest because the racial composition of visited high schools has consequences for the racial composition of colleges and universities.
+Given our interests in social reproduction versus social mobility, we would also analyze tuition price and household income, but these data are not available for private high schools.
 
@@
 This chapter conceptualizes recruiting visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges and universities.
-We are interested in how similar the recruiting networks of public research universities are to those of private colleges and universities, thereby motivating research question 3: to what extent do public research universities and private universities visit overlapping sets of private high schools?
+We are interested in how similar the recruiting networks of public research universities are to those of private colleges and universities, thereby motivating research question 3, "To what extent do public research universities and private universities visit overlapping sets of private high schools?"
 
@@
 
-# Data and Methods
-
-## Data
+# Data and methods
 
 Our broader project collected data on off-campus recruiting visits made by a convenience sample of colleges and universities during the 2017 calendar year.
-The data collection sample comes from three different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102); all private universities in the top 100 of U.S.
-News and World Report National Universities rankings (N=58); and all private colleges in the top 50 of U.S.
-News and World Report Liberal Arts Colleges rankings (N=47).
-For each of these institutions, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits.
+The data collection sample comes from two different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), and all private universities in the top 100 of U.S.
+News and World Report National Universities rankings (N=58).
+<!-- and all private colleges in the top 50 of U.S.
+News and World Report Liberal Arts Colleges rankings (N=47).-->For each of these institutions, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits.
 For institutions that posted such pages, we scraped the pages once per week throughout 2017.
-Many colleges and university only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
+Many colleges and universities only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
 These institutions are excluded from the analyses.
-Our final analysis sample consists of 15 public research universities, 14 private research universities, and 12 private liberal arts colleges.
-<!--[MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->
+Our final analysis sample consists of 15 public research universities and 14 private research universities.
+<!--12 private liberal arts colleges [MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->
 
@@
 
-Table \@ref(tab:sample-characteristics) shows selected characteristics for universities in our analysis sample.
-Given that we collected recruiting data for private universities ranked in the top 100 of US News and World Report, one concern is whether it makes sense to compare public research universities not ranked in the top 100 to private universities ranked in the top 100.
+Table \@ref(tab:sample-characteristics) shows selected characteristics for the universities in our analysis sample.
+Given that we collected recruiting data for private universities ranked in the top 100 of U.S.
+News and World Report, one concern is whether it makes sense to compare public research universities not ranked in the top 100 to private universities ranked in the top 100.
 However, the columns in Table \@ref(tab:sample-characteristics) for 25th and 75th percentile SAT score of enrolled freshmen suggest that private universities ranked lower than 75 have test score ranges that are fairly similar to public research universities not ranked in the top 100.
@@
 
-CRYSTAL - ADD ONE BRIEF PARAGRAPH LISTING THE DIFFERENT SECONDARY DATA SOURCES WE USED
-
-## Methods
+The data on university characteristics come from the 2017 Integrated Postsecondary Education Data System (IPEDS) and 2020 Best Colleges ranking by U.S.
+News & World Report.
+For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.^[For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small amount of schools.] Only high schools that enroll at least 10 12th grade students, is not primarily a virtual school, and is located in the 50 U.S.
+states, the District of Columbia, or land regulated by the Bureau of Indian Affairs is included in our analysis.
 
@@
 
-## Research question 1: scale of visits
-
-Research question 1 asks, how does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
-This question can be answered by counting the number of visits to private high schools, which equivalent to calculating degree centrality for each university.
+## RQ1: Scale of visits
+
+Research question 1 asks, "How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?" This question can be answered by counting the number of visits to private high schools, which is equivalent to calculating the degree centrality for each university.
 In addition to scale, we are also interested in the relative scale of visits to private high schools.
@@
 
-Appendix Figures \@ref(fig:events-count-pubu) and \@ref(fig:events-count-privu) show the number of visits by "type" (public high school, private high school, community college, other), respectively, for public research universities and selective private universities.
+Appendix Figures \@ref(fig:events-count-pubu) and \@ref(fig:events-count-privu) show the number of visits by "type" (public high school, private high school, community college, other) for public research universities and selective private universities, respectively.
 On average, the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample conducted `r round((events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()), digits = 0)` off-campus recruiting events in 2017, ranging from a low of `r events_df %>% filter(univ_id == '139959') %>% count() %>% as.numeric()` for the University of Georgia to a high of `r events_df %>% filter(univ_id == '100751') %>% count() %>% as.numeric()` for the University of Alabama.
-By contrast, the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample conducted an average of `r round((events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()), digits = 0)` events, ranging from a low of `r events_df %>% filter(univ_id == '186867') %>% count() %>% as.numeric()` by Stevens Institute of Technology (located in Hoboken, NJ) to a high of `r events_df %>% filter(univ_id == '239105') %>% count() %>% as.numeric()` to Marquette University (located in Milwaukee, WI).
+By contrast, the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample conducted an average of `r round((events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()), digits = 0)` events, ranging from a low of `r events_df %>% filter(univ_id == '186867') %>% count() %>% as.numeric()` by Stevens Institute of Technology (located in Hoboken, NJ) to a high of `r events_df %>% filter(univ_id == '239105') %>% count() %>% as.numeric()` by Marquette University (located in Milwaukee, WI).
 Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs','priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())*100, digits=1)`% of visits were to a public or private high school, whereas for selective private universities `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('pub_hs','priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())*100, digits=1)`% of all visits were to a public or private high school.
@@
 
-[CRYSTAL - REVISE TEXT IN THIS PARAGRAPH AND MAYBE THE NEXT TO REFLECT CHANGES WE MADE TO THIS FIGURE] Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools for public research universities (Figure \@ref(fig:events-hs-count-pubu)) and selective private universities (Figure \@ref(fig:events-hs-count-privu)), with separate bars for in-state and out-of-state visits.
-Only three of the 15 public research Universities -- UC-Berkeley, UC-San Diego, and UC-Riverside -- made more in-state than out-of-state high school visits.
+Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools for public research universities (Figure \@ref(fig:events-hs-count-pubu)) and selective private universities (Figure \@ref(fig:events-hs-count-privu)), with each bar shaded by percent in-state versus out-of-state visits.
+Only three of the 15 public research universities -- UC-Berkeley, UC-San Diego, and UC-Riverside -- made more in-state than out-of-state total high school visits.
 Notably, the University of California voluntarily adopted a nonresident enrollment cap in 2017, following pressure from state legislators who had issued a bill to cap nonresident enrollment.
-Of the 14 selective private universities in our sample, only Baylor University (Waco, TX) made more in-state than out-of-state high school visits.
+Of the 14 selective private universities in our sample, only Baylor University (Waco, TX) made more in-state than out-of-state total high school visits.
 
@@
 
-With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of `r events_df %>% filter(univ_id == '110671', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by UC-Riverside to a high of `r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by the University of Alabama (which accounted for `r round((events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)` of all visits to private schools by public research universities in our sample), with the median university, The University of Pittsburgh, making `r events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()` visits.
+With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of `r events_df %>% filter(univ_id == '110671', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by UC-Riverside to a high of `r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by the University of Alabama (which accounted for `r round((events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of all visits to private schools by public research universities in our sample), with the median university, The University of Pittsburgh, making `r events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()` visits.
 Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of private high school visits were to out-of-state schools while `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of public high school visits were to out-of-state schools.
@@
 Across all selective private universities in our sample, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of high school visits were to private high schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
-However, the relative emphasis on private high schools was a bit closer for out-of-state visits; across all selective private universities, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% out-of-state high school visits were to private schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
-
-Although selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools.
-Figure \@ref(fig:actual-proportional-pubu) (public universities) and Figure \@ref(fig:actual-proportional-privu) (private universities) show the actual number of private school visits compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.
-Figure \@ref(fig:actual-proportional-pubu) shows the actual number of private school visits exceeded the proportional number of private school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
-For UC-Berkeley, private school visits represented X% of all high school visits but would have represented Y% had UC-Berkeley visited public and private schools at the same rate.
-For the University of Georgia, which represented the extreme for public universities, private school visits represented X% of all high school visits but would have represented Y% had the university visited public and private schools at the same rate.
+Although, the relative emphasis on private high schools was a bit closer for out-of-state visits; across all selective private universities, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% of out-of-state high school visits were to private schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
+
+Even though selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools.
+Figure \@ref(fig:actual-proportional-pubu) (public universities) and Figure \@ref(fig:actual-proportional-privu) (private universities) show the actual number of private school visits made compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.^[When calculating the hypothetical, proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university.
+Our rationale for this decision is that it is unhelpful to include schools in states that the university ignored entirely.] Figure \@ref(fig:actual-proportional-pubu) shows that the actual number of private school visits exceeded the proportional number of private school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
+For UC-Berkeley, private school visits represented 27% of all high school visits but would have represented 19% had UC-Berkeley visited public and private schools at the same rate.
+For the University of Georgia, which represented the extreme for public universities, private school visits represented 37% of all high school visits but would have represented 19% had the university visited public and private schools at the same rate.
 Figure \@ref(fig:actual-proportional-privu) shows that this disparity between actual versus proportional visits was much greater for private universities than public universities.
 Catholic universities made the most disproportionate number of private high school visits.
-For Notre Dame, private school visits represented X% of actual visits high school visits but would have represented Y% of proportional visits.
+For Notre Dame, private school visits represented 63% of actual high school visits but would have represented 18% of proportional visits.
 
@@
 
-## Research question 2: characteristics of visited schools
-
-Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privu) address research question 2, how do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+## RQ2: Characteristics of visited schools
+
+Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privhs-pubhs) address research question 2, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?"
 
@@
 Scholarship on the relationship between geographic proximity and student demand tends to find that nationally prestigious universities enjoy strong demand across the nation, while less prestigious universities rely primarily on demand from students located nearby [e.g., @RN2133].
-The visit patterns for private universities are consistent with this finding; less prestiguous universities tended to focus on private high schools in their home region, while more prestigious universities tended to visit many private high schools outside their home region.
+The visit patterns for private universities are consistent with this finding; less prestigious universities tended to focus on private high schools in their home region, while more prestigious universities tended to visit many private high schools outside their home region.
 Similarly, scholarship on student demand for out-of-state public universities finds that most public universities rely on demand from out-of-state students living in nearby states [@RN2536; @RN2535; @RN2546].
@@
 Figure \@ref(fig:religion-pubu-privu) shows the religious affiliation -- Catholic, Christian, Nonsectarian, and Other -- of visited private high schools.
-The results for selective private universities (bottom panel) follow expectations: Nonsetarian universities tended to visit a higher proportion of nonsectarian private high schools; Catholic universities visited a higher proportion of Catholic high schools; and Christian universities tended to visit a relatively higher share of Christian high schools.
+The results for selective private universities (bottom panel) follow our expectations: Nonsectarian universities tended to visit a higher proportion of nonsectarian private high schools; Catholic universities visited a higher proportion of Catholic high schools; and Christian universities tended to visit a relatively higher share of Christian high schools.
 
@@
 Figure \@ref(fig:rank-pubu-privu) shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools.
-For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visted a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.
+For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visited a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.
 A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.
@@
 
-A similar pattend emerged for the public research universities in our sample; more highly ranked universities tended to visit a higher share of higly rated private high schools than lower ranked universities.
+A similar pattern emerged for the public research universities in our sample; more highly ranked universities tended to visit a higher share of highly rated private high schools than lower ranked universities.
 In comparison to the private universities in our sample, the public universities in our sample tended to visit a higher share of private high schools that were not highly rated.
-To a great extent, this finding is merely a consequence of our sampling strategy; we attempted to collected recruiting visit data from all public research universities but we only collected recruiting visit data from private universities ranked in the top 100 of US News and World Report.
+To a great extent, this finding is merely a consequence of our sampling strategy; we attempted to collect recruiting visit data from all public research universities but we only collected recruiting visit data from private universities ranked in the top 100 of U.S.
+News and World Report.
 That said, the finding that public research universities visited a large share of low-rated private high schools is consistent with the idea that many public research universities visit private high schools in search of full-pay students rather than academic superstars.
@@
 Compared to the universe of private high schools, the universities in our sample tended to visit schools that enrolled more 12th graders.
-Generally, the findings were pretty similar across universities public and private universities; for must universities, more than half of private school visits were to schools that enrolled at least 100 12th graders.
+Generally, the findings were pretty similar across public and private universities; for most universities, more than half of private school visits were to schools that enrolled at least 100 12th graders.
 However, public universities tended to visit a slightly larger share of high schools with fewer than 50 12th graders and private universities tended to visit a higher share of high schools with 12th grade enrollment of 50-100.
@@
 
-Figure \@ref(fig:enroll-pubu-privhs-pubhs) shows the 12th grade enrollment of visited private high schools to the 12th grade enrollment of visited public high schools for the public research universities in our sample.
-DISCUSS RESULTS; MAIN TAKEAWAY IS THAT, COMPARED TO THE PUBLICH HIGH SCHOOLS THEY VISIT, PUBLIC UNIVERSITIES SEEM TO BE WILLING TO VISIT PRIVATE SCHOOLS THAT ENROLL FAR FEWER 12TH GRADERS.
+Figure \@ref(fig:enroll-pubu-privhs-pubhs) shows the 12th grade enrollment of visited private high schools as well as the 12th grade enrollment of visited public high schools for the public research universities in our sample.
+As seen, a large majority of public high school visits for all 15 universities were to schools with more than 150 12th graders enrolled (bottom panel).
+By contrast, most of the visited private schools tended to have fewer than 150 12th graders enrolled.
+Although this is somewhat to be expected, as public high schools tend to be larger in size than private schools (top rows of Figure \@ref(fig:enroll-pubu-privhs-pubhs)), there still appears to be a disproportionate amount of smaller private high schools visited compared to smaller public high schools.
+This suggests that the public universities in our sample were willing to take the time to visit private schools, even when they enroll far fewer 12th graders.
 
@@
 Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups.
-For about 70% [CRYSTAL - CHECK THIS] of schools in the universe of private high schools (top row of Figure \@ref(fig:race-pubu-privu)), Black/Latinx/Native students comprise less than 20% of enrolled students.
-Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would enroll relatively few Black/Latinx/Native students.
+For over 65%<!--0.6632124--> of schools in the universe of private high schools (top row of Figure \@ref(fig:race-pubu-privu)), Black/Latinx/Native students comprise less than 20% of enrolled students.
+Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
 Figure \@ref(fig:race-pubu-privu) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
-For public universities, exceptions to this finding were were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.
+For public universities, exceptions to this finding were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.
 For private universities, Marquette was the only exception to this finding.
@@
 Therefore, universities may visit predominantly white private high schools in search of non-white students.
-Once concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.
+One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.
 
@@
 Figure \@ref(fig:race-pubu-privhs-pubhs) compares the racial composition of private high schools visited by public research universities to the racial composition of public high schools visited by these universities.
-[TAKEAWAY: the private high schools visited are much less racially diverse that the public high schools they visit, so recruiting aggresively from private schools may shift the racial composition of public research universities away from black/latinx/native]
-
-## Research question 3: overlapping network structure
-
-Research question 3 asks, to what extent do public research universities and selective private universities visit overlapping sets of private high schools?
-In contrast to RQ1 and RQ2, answering RQ3 requires social network analysis techniques.
+Looking at the universe of high schools (top rows of Figure \@ref(fig:race-pubu-privhs-pubhs)), we see that public high schools tend to be more racially diverse than private schools.
+This is reflected in the racial composition of visited schools as well, where the set of visited public high schools generally enroll more Black/Latinx/Native students than the visited private schools for the public research universities in our sample.
+Unfortunately though, a majority of these public universities tended to visit private high schools at a higher rate than public high schools, as seen earlier in Figure \@ref(fig:actual-proportional-pubu).
+This disproportionate emphasis on private school visits may shift the racial composition of public universities away from Black/Latinx/Native students.
+
+## RQ3: Overlapping network structure
+
+Research question 3 asks, "To what extent do public research universities and selective private universities visit overlapping sets of private high schools?" In contrast to RQ1 and RQ2, answering RQ3 requires social network analysis techniques.
 
@@
 
-We answer research question 3 by, first, analyzing overlap in the recruiting network of public universities (the public university network), second, analyzing overlap in the network of private universities (the private university network), and third, analyzing overlap amongst public and private universities (the public and private university network).
+We answer research question 3 by: first, analyzing overlap in the recruiting network of public universities (the public university network); second, analyzing overlap in the network of private universities (the private university network); and third, analyzing overlap amongst public and private universities (the public and private university network).
 
@@
 
-Tables \@ref(tab:pubu-count-matrix) and \@ref(tab:pubu-percent-matrix) provides a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
+Tables \@ref(tab:pubu-count-matrix) and \@ref(tab:pubu-percent-matrix) provide a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
 Table \@ref(tab:pubu-count-matrix) shows -- for each pair of public universities -- the number of high schools that were visited by both universities.
@@
 Table \@ref(tab:pubu-percent-matrix) shows overlap in high schools visited in terms of percent rather than count.
-For example, Column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7% of these high schools and CU-Boulder visited 39.1% of these high schools.
+For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7% of these high schools and CU-Boulder visited 39.1% of these high schools.
 
@@
 
-One finding from Table \@ref(tab:pubu-percent-matrix) is that the University of Alabama is is omnipresent in the set of private high schools visited by most other public research universities in the sample, particularly universities located in the South.
-For the remaining universities, Figure \@ref(tab:pubu-percent-matrix) suggests several clusters of universities.
-For example, UMass-Amherst, Suny Stonybrook and Rutgers tend to visit many of the same high schools, as do University of Arkansas and the University of Kansas.
-
-Network graphs are useful for showing which universities have similar private high school recruiting newtworks.
+One finding from Table \@ref(tab:pubu-percent-matrix) is that the University of Alabama is omnipresent in the set of private high schools visited by most other public research universities in the sample, particularly universities located in the South.
+For the remaining universities, Table \@ref(tab:pubu-percent-matrix) suggests several clusters of universities.
+For example, UMass-Amherst, SUNY Stony Brook, and Rutgers tend to visit many of the same high schools, as do the University of Arkansas and the University of Kansas.
+
+Network graphs are useful for showing which universities have similar private high school recruiting networks.
 Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network.
 Whether graphing one-mode or two-mode networks, network graphs show vertices as circles and edges as lines connecting pairs of vertices.
-In Figure \@ref(fig:plot-1mode-pubu),each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common.
-The width of the line between two universities indicates the number of high schools both universities visited, as identified in Tables \@ref(tab:pubu-count-matrix).
+In Figure \@ref(fig:plot-1mode-pubu), each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common.
+The width of the line between two universities indicates the number of high schools both universities visited, as identified in Table \@ref(tab:pubu-count-matrix).
 Conceptually, we think of vertices as repelling one another and edges as pulling vertices together [@RN4725].
-Therefore, nodes that share few connections are located apart and nodes that share many connections are located close together.
-Vertices that are highly connected -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, vertices nodes that are relatively disconnected are located at the periphery of the graph.
+Therefore, vertices that share few connections are located apart and those that share many connections are located close together.
+Vertices that are highly connected -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while vertices that are relatively disconnected are located at the periphery of the graph.
 
@@
 Figure \@ref(fig:plot-1mode-pubu) shows the University of Alabama, University of South Carolina, and CU-Boulder at the center of the recruiting network.
-The University of Nebraska-Lincoln, SUNY Stony Brook and UC-Riverside are located on the periphery, and the remaining universities are in-between.
+The University of Nebraska-Lincoln, SUNY Stony Brook, and UC-Riverside are located on the periphery, and the remaining universities are in between.
 Universities that share many direct (i.e., visit many of the same schools) or indirect edges tend to be located close together, for example University of Kansas and University of Arkansas.
@@
 To better answer research question 3, we augment the network graphs by using cluster analysis methods -- referred to as "community detection" in the network analysis literature -- to identify groups of universities that share common network structure.
-Broadly speaking, the goal of commmunity detection is to identify "subsets of vertices that demonstrate a ‘cohesiveness’ with respect to the underlying relational patterns" [@RN4725, p.
+Broadly speaking, the goal of community detection is to identify "subsets of vertices that demonstrate a ‘cohesiveness’ with respect to the underlying relational patterns" [@RN4725, p.
 59], where a "cohesive subset" means a "subset of vertices that (i) are well connected among themselves, and at the same time (ii) are relatively well separated from the remaining vertices"  [@RN4725, p.
@@
 
-In Figure \@ref(fig:plot-1mode-pubu), the shape of each university vertex is based on implementing this cluster fast and greedy approach with the specification that the algorithm identify four groups.
+In Figure \@ref(fig:plot-1mode-pubu), the shape of each university vertex is based on implementing this cluster fast and greedy approach with the specification that the algorithm should identify four groups.
 The largest group consists of eight universities (U.
 Alabama, U.
-Arkanasas, U.
+Arkansas, U.
 Kansas, Nebraska-Lincoln, U.
@@
 Whereas applying cluster analysis to public universities (Figure \@ref(fig:plot-1mode-pubu)) yielded three clusters that contained multiple universities, the application of cluster analysis to private universities (Figure \@ref(fig:plot-1mode-privu)) yielded a single cluster that contained 11 universities and three clusters that contained one university each.
-As suggested above, a likely explanation for this difference is that the majority of private universities had substantial overlap in the sets of private high schools visited whereas public universities tended to have substanital overlap with some public universities but not others.
+As suggested above, a likely explanation for this difference is that the majority of private universities had substantial overlap in the sets of private high schools visited whereas public universities tended to have substantial overlap with some public universities but not others.
 
@@
 The periphery of the network included Baylor (237), Stevens Institute (160), Marquette (331), and Case Western (228).
-Baylor visited a higher number of conservative Chrisitan high schools than any other university (see Figure \@ref(fig:religion-pubu-privu)).
+Baylor visited a higher number of conservative Christian high schools than any other university (see Figure \@ref(fig:religion-pubu-privu)).
 It is notable that Marquette is in the periphery despite visiting a higher number of schools than more centrally located universities (e.g., Emory), suggesting that Marquette visits many schools that are visited by few other private universities in our sample.
 
-The universities located close to one another in Figure \@ref(fig:plot-1mode-privu) tend to share relgious affiliation and/or be located in the same geographic region.
+The universities located close to one another in Figure \@ref(fig:plot-1mode-privu) tend to share religious affiliation and/or be located in the same geographic region.
 For example, the majority of Catholic universities are located close to one another and the majority of Midwest universities are located close to one another.
-Interestingly, two of the three Christian universities -- TCU and SMU -- are located closer much closer to the Catholic universities Notre Dame and Northwestern than they are to Baylor, suggesting that Baylor visits a different set of conservative Christian high schools than TCU and SMU.
+Interestingly, two of the three Christian universities -- TCU and SMU -- are located much closer to the Catholic universities Notre Dame and Northwestern than they are to Baylor, suggesting that Baylor visits a different set of conservative Christian high schools than TCU and SMU.
 
@@
 The cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities that visited a relatively large share of Christian high schools.
-Second, the cluster of 13 universities -- including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley -- largely consists of universities more highly ranked universities, universities located in the Midwest or West, and Catholic universities.
-Third, the five university cluster -- Rutgers, Stevens Institute of Technology, UMass Amherst, University of Pittsburgh -- largely consists of public universities with with strong ties to the Northeast.
+Second, the cluster of 13 universities -- including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley -- largely consists of more highly ranked universities, universities located in the Midwest or West, and Catholic universities.
+Third, the five university cluster -- Rutgers, Stevens Institute of Technology, UMass Amherst, University of Pittsburgh, SUNY Stony Brook -- largely consists of public universities with strong ties to the Northeast.
 
@@
 Universities located near the center of Figure \@ref(fig:plot-1mode-u) do not all belong to the same cluster and, more broadly, universities located close to one another do not all belong to the same cluster.
-Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities with the highest degree centrality -- i.e., that visited most schools visited.
-The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses) University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), Northwestern (377), University of South Carolina (396), and CU-Boulder (362).
-Notably, while the majority of universities located near the center of Figure are private, three are public.
-
-Proximity of vertices to one another in Figure \@ref(fig:plot-1mode-u) appeared to be more connected to religious affiliation, geoggraphic location, and academic reputation.
+Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities with the highest degree centrality (i.e., those that visited the most schools).
+The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), Northwestern (377), University of South Carolina (396), and CU-Boulder (362).
+Notably, while the majority of universities located near the center of Figure \@ref(fig:plot-1mode-u) are private, three are public.
+
+Proximity of vertices to one another in Figure \@ref(fig:plot-1mode-u) appeared to be more connected to religious affiliation, geographic location, and academic reputation.
 Universities with a common religious affiliation (e.g., Notre Dame, Villanova, Marquette, Boston College) tend to be close to one another.
-However, the University of Alabama, which visited a high share of Catholic schools and Christian schools is simultaneously close to catholic universities and to the Christian universities TCU and SMU.
+However, the University of Alabama, which visited a high share of Catholic schools and Christian schools is simultaneously close to Catholic universities and to the Christian universities TCU and SMU.
 Similarly, the University of South Carolina, which visited a relatively high share of Christian schools, is close to TCU and SMU.
@@
 Similarly, CU-Boulder visited 46.4 of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
-The University of Arkansas competed heavily at schools visited by Baylor, Rutgers and UMass Amherst competed heavily at schools visited by Stevens Institute of Technology, while UC Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
+The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
 
@@
 
-This chapter analyzes recruiting visits to private high schools, which were made during the 2017 calendar year, for a convenience sample of 15 public research universities and 14 private universities ranked in the top 100 of US News National Universities.
-Our goal was to learn about public research universities, by analyzing their behavior and comparing their behavior to that of selective private universities.
+This chapter analyzes recruiting visits to private high schools, which were made during the 2017 calendar year, for a convenience sample of 15 public research universities and 14 private universities ranked in the top 100 of U.S.
+News and World Report National Universities rankings.
+Our goal was to learn about public research universities by analyzing their behavior and comparing their behavior to that of selective private universities.
 
 Research question 1 asks about the scale of visits to private high schools.
-All private universities in our sample made a disproportionate number of visits to private high schools (Figure X) and, for about half of these universities, visits to private high schools represented about 50% or more of all high school visits.
-For most public research universities in our sample, the scale and relative scale -- as a percentage of all HS visits -- of visits to private high schools was smaller than that of most selective private universities.
-However, X of the 15 public universities visited a disproportionate number of private high schools (Figure X) and that vast majority of these private school visits were to out-of-state private schools.
-Additionally, several public research universities -- University of Alabama, CU-Boulder, University of South Caroline -- visited private high schools at a scale that exceeded most private universities.
-Moreover, X of
+All private universities in our sample made a disproportionate number of visits to private high schools (Figure \@ref(fig:actual-proportional-privu)) and, for about half of these universities, visits to private high schools represented about 50% or more of all high school visits.
+For most public research universities in our sample, the scale and relative scale -- as a percentage of all HS visits -- of visits to private high schools were smaller than that of most selective private universities.
+However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \@ref(fig:actual-proportional-pubu)) and that vast majority of these private school visits were to out-of-state private schools.
+Additionally, several public research universities -- University of Alabama, CU-Boulder, University of South Carolina -- visited private high schools at a scale that exceeded most private universities.
 
 Research question 2 asks about the characteristics of visited private high schools.
-We analyzed geographic region, religious affiliation, high school rank, 12th grade enrollment, and racial composition.
-Bot public and private universities in our sample tended to make disproportionate number of visits in their home geographic region, with highly ranked universities making more visits to schools in other regions.
-The majority of universities -- even those located outside the south --  visited a large number of private schools located in the south.
+We analyzed geographic region, religious affiliation, high school ranking, 12th grade enrollment, and racial composition.
+Both public and private universities in our sample tended to make a disproportionate number of visits in their home geographic region, with highly ranked universities making more visits to schools in other regions.
+The majority of universities -- even those located outside the South --  visited a large number of private schools located in the South.
 Unsurprisingly, sectarian private universities made a large share of visits to private high schools of a similar religious affiliation.
@@
 With the exception of UC-Berkeley and UC-San Diego, the academic rating of private schools visited by public universities was lower than the rating of those visited by most private universities.
-This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked as a top 100 National University by US News.
-Nevertheless, the large number of visits to low-rated private schools by public universities, combined with the fact that that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private schools primarily in search of full-pay students rather than academic superstars.
+This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked as a top 100 National University by U.S.
+News.
+Nevertheless, the large number of visits to low-rated private schools by public universities, combined with the fact that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private schools primarily in search of full-pay students rather than academic superstars.
 
@@
 For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools.
-By contrast, the public high schools visited by public universities tended to enroll a much higher share students who identify as Black, Latinx, or Native.
+By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.
 
@@
 Within the sample of public universities, we observed substantial overlap and variation in recruiting networks.
-For example, the recruiting networks of the the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass Amherst and Rutgers, which share substantial overlap with one another.
+For example, the recruiting networks of the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass Amherst and Rutgers, which share substantial overlap with one another.
 Across the entire sample of public and private universities, we also observed substantial overlap and variation in recruiting networks.
@@
 
-## Privatization of Public Research Universities
+## Privatization of public research universities
 
@@
 A weakness of the scholarly literature on privatization is that few studies compare public and private universities with respect to a behavior that is associated with private universities [@RN4543].
-We conceptualize recruiting visits to private schools as a behavior that is consistent with the social reproduction orientation of selective private universities and contrary to the historic social mobility mission associated with public research universties.
+We conceptualize recruiting visits to private schools as a behavior that is consistent with the social reproduction orientation of selective private universities and contrary to the historic social mobility mission associated with public research universities.
 Although we cannot make statements about the population of public research universities (ours is a convenience sample rather than a random sample), we can describe variation in how the public universities in our sample went about visiting private schools.
@@
 Amongst the network of public and private universities, Figure \@ref(fig:plot-1mode-u) shows that three clusters emerge -- each containing some mix of public and private universities.
-The universities within a cluster some overlap in the kinds of schools visited (e.g., TCU and University of South Carilina), but also share substantial overlap with particular universities in different clusters (e.g., Tufts and University of Pittsburgh).
-
-In making large-scale visits to out-of-state private high schools, we argue that public research universities are mimicking the behavior selective private universities in order to compete for students that have been traditionally targeted by private universities.
+The universities within a cluster have some overlap in the kinds of schools visited (e.g., TCU and University of South Carolina), but also share substantial overlap with particular universities in different clusters (e.g., Tufts and University of Pittsburgh).
+
+In making large-scale visits to out-of-state private high schools, we argue that public research universities are mimicking the behavior of selective private universities in order to compete for students that have been traditionally targeted by private universities.
 Our rationale for this statement is that selective private universities have been recruiting heavily from private schools for a long time [@RN4642; @RN1565; @RN4407].
@@
 Several public universities seem to be competing directly for students targeted by a particular private university.
-For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory.
+For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory (Figure \@ref(tab:privu-percent-visited-by-pubu-matrix)).
 We reason UC-Berkeley is competing directly for students because all four universities are in the same broad echelon of prestige.
@@
 For example, the University of Alabama visited 52.2% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools.
-Given the differences in academic prestige between, the University of Alabama may not be competing for the same students as Notre Dame.
+Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame.
 Instead, they found a niche by targeting Catholic school students of a similar economic echelon, who have lower academic achievement, and want to attend a football powerhouse.
@@
 Finally, all public universities that visited a substantial number of private schools tended to visit schools that enrolled few Black, Latinx, or Native students.
-This finding is substantially driven by the fact that the national universe of private schools tend to enroll a much lower share of Black, Latinx, or Native students than the universe of public schools.
-However, the the set of schools visited by the public universities in our sample enrolled fewer Black, Latinx, and Native students than the universe of private schools.
+This finding is substantially driven by the fact that the national universe of private schools tends to enroll a much lower share of Black, Latinx, or Native students than the universe of public schools.
+However, the set of schools visited by the public universities in our sample enrolled fewer Black, Latinx, and Native students than the universe of private schools.
 Although we do not have data on household income, it is likely that the majority of students are wealthy at the private schools visited by public universities in our sample.
 
-Therefore, while public universities playing the private school game differ in terms of the set of school they target, they all seem to be targeting schools that enroll mostly affluent students and few students who identify as Black, Latinx, or Native.
+Therefore, while public universities playing the private school game differ in terms of the set of schools they target, they all seem to be targeting schools that enroll mostly affluent students and few students who identify as Black, Latinx, or Native.
 To the extent that these recruiting efforts yield dividends in terms of incoming freshmen, playing the private school game is likely to change the enrollment composition of public research universities in ways that run contrary to racial and socioeconomic diversity.
@@
 
-**Constructing two-mode network** We describe construction of social network data with reference to "corporate board-director" networks -- the most commonly analyzed two-mode network -- which consist of directors (mode 1) who serve on organizational boards (mode 2).
-In our school-university two-mode network, the vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visits made between the two (e.g., high school $i$ shares an edge with university $j$ if high school $i$ receives at least one visit from university $j$).
+**Constructing two-mode network**.
+We describe construction of social network data with reference to "corporate board-director" networks -- the most commonly analyzed two-mode network -- which consist of directors (mode 1) who serve on organizational boards (mode 2).
+In our school-university two-mode network, the vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visit made between the two (e.g., high school $i$ shares an edge with university $j$ if high school $i$ receives at least one visit from university $j$).
 Visits can only occur between a school-university pair (not a school-school pair or a university-university pair).
@@
 
-**Transforming two-mode network to one-mode networks** Two-mode networks are often analyzed as one-mode networks [@RN2457].
+**Transforming two-mode network to one-mode networks**.
+Two-mode networks are often analyzed as one-mode networks [@RN2457].
 @RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" (p.
@@
 
+rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)
+
 kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix') %>%
   kable_styling(latex_options = 'scale_down') %>%
-  column_spec(c(1, 15), width = '8.5em') %>% 
+  column_spec(c(1), width = '13em') %>% 
+  column_spec(c(14), width = '8.5em') %>% 
   column_spec(2:13, width = '7em') %>% 
-  column_spec(c(14, 16), width = '6em')
+  column_spec(c(7, 9, 15, 16), width = '6em')
 ```
@@
 ```{r pubu-percent-matrix}
+rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)
+
 kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix') %>%
   kable_styling(latex_options = 'scale_down') %>%
-  column_spec(c(1, 15), width = '8.5em') %>% 
+  column_spec(c(1), width = '13em') %>% 
+  column_spec(c(14), width = '8.5em') %>% 
   column_spec(2:13, width = '7em') %>% 
-  column_spec(c(14, 16), width = '6em')
+  column_spec(c(7, 9, 15, 16), width = '6em')
 
@@
 
+rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)
+
 kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix') %>%
   kable_styling(latex_options = 'scale_down') %>%
-  column_spec(1, width = '8.5em') %>%
+  column_spec(1, width = '13em') %>%
   column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em')
+  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
+  column_spec(14:15, width = '8.5em')
 
@@
 ```{r privu-percent-visited-by-pubu-matrix}
+rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
+
 kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities') %>%
@@
   column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em')
+  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
+  column_spec(14:15, width = '8.5em')
 ```
@@
 
-```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, private universities"}
+```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
 include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
@@
 
-```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school rank of visited private high schools"}
+```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school ranking of visited private high schools"}
 include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))

### 2021-10-15 text/manuscript_june_2021.Rmd
changed title

@@
 ---
-title: "Recruiting Chapter"
+title: "The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities"
 author: 

### 2023-07-25 text/manuscript_rihe.Rmd
added rihe manuscript

--- 2021-06-26 text/manuscript_june_2021.Rmd
@@
 ---
-title: "Recruiting Chapter"
-author: 
-  - Ozan Jaquette
-  - Crystal Han
-  - Irma Castañeda
+title: "The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities"
+#author: 
+#  - Ozan Jaquette
+#  - Crystal Han
+#  - Irma Castañeda
 bibliography: ./../other/burd_recruiting_chapter.bib
@@
     toc: FALSE
+    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
 csl: ./../other/apa.csl
@@
       - \floatsetup{capposition=top}
-fontsize: 11pt
+fontsize: 12pt
 ---
@@
 
+\setstretch{1.5}
+
+ABSTRACT
+
+Few empirical analyses of privatization compare public and private universities on a behavior associated with private universities.
+This manuscript analyzes off-campus recruiting visits to private high schools, which were made in 2017 by a convenience sample of 15 public research universities and 14 selective, private universities.
+Sociological scholarship on the relationship between high schools and universities conceives of off-campus recruiting visits as an indicator of a social relation.
+Therefore, we utilize social network concepts and methods to compare the recruiting networks of public and private universities.
+With respect to scale (research question 1), most public research universities in our sample made a disproportionate number of visits to private (out-of-state) high schools, though not as many as private universities.
+With respect to characteristics of visited schools (RQ2), both public and private universities tended to visit predominantly white schools in their home geographic region and the South.
+Public universities tended to visit lower ranked private high schools than private universities.
+Surprisingly, several public research universities visited sectarian private high schools at a rate similar to sectarian private universities.
+With respect to overlap (RQ3), descriptive statistics and community detection methods revealed substantial overlap in the recruiting networks of public and private universities.
+
+\newpage
+
 # Introduction
 
+In the early twenty-first century, "privatization" received substantial attention from scholars of higher education [e.g., @RN921; @RN2101; @RN1118; @RN1577; @RN2111].
+@RN4543 argue that scholarship on privatization waned because of a lack of conceptual and empirical clarity.
+One strand of scholarship conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources.
+Public research universities responded, for example, by pursuing research commercialization and nonresident tuition revenue, and donative resources [e.g., @RN3753; @RN2101; @RN1644].
+A second strand within the privatization literature conceptualizes privatization as a process whereby public institutions become more similar -- in terms of characteristics or behavior -- to for-profit or private non-profit organizations [@RN4543].
+A weakness of this literature is that few empirical studies analyze public institutions on a behavior associated with private institutions.
+Moreover, few studies directly compare public and private institutions on the same behavioral dimension.
+
+We argue that scholarship on recruiting behavior can shed light on the extent to which public universities are engaging in behaviors associated with private universities.
+Admissions counselors from colleges and universities visit local high schools in order to meet prospective students and maintain relationships with guidance counselors at feeder schools [@RN3519].
+@RN4758 analyzed off-campus recruiting visits made in 2017 by 15 public research universities, finding that 12 of these universities made more visits to *out-of-state* high schools than *in-state* high schools.
+These out-of-state visits focused on public schools in affluent, predominantly white communities.
+Whereas @RN4758 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
+More specifically, we investigate how visits to private high schools by public research universities compare to visits to private high schools by selective private universities.
+
+Our focus on recruiting visits to private high schools is motivated by seminal scholarship within the sociology of education.
+Sociologist Max Weber is credited for the insight that education has a "dual character," on one hand, serving *social mobility* by redistributing access to privileged positions and, on the other, serving *social reproduction* by granting privileged families disproportionate access to the educational institutions that confer pathways to privileged positions [@RN2377; @RN1133].
+
+The mission of selective private colleges and universities is more squarely associated with social reproduction rather than social mobility.
+Historically, these institutions depend on patronage from philanthropic interests -- in connection with business and religious interests -- and on wealthy households who provide tuition revenue and donations [@RN4517].
+In turn, selective private institutions contribute to social reproduction by providing access to their patrons.
+The "Chetty" data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile [@RN4722; @RN4723].
+A significant caveat is that religiously affiliated universities may prioritize enrollment opportunities for students of the same faith regardless of wealth, but even here the mission is to benefit families from a particular cultural status group [@RN4517].
+
+The traditional, albeit mythologized, public good mission of public research universities is tied to social mobility and development of the state [@RN2269; @RN921].
+Public research universities are designated the unique responsibility of educating the future civic, professional, and business leaders of the state.
+Quoting 19th century University of Michigan President James Angell, these institutions contribute to social mobility by providing "an uncommon education for the common man" [as cited in @RN3608, p.
+279] who could not afford tuition at elite private institutions.
+
+We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction.
+Recruiting visits to private high schools are consistent with the social reproduction mission of selective private universities, regardless of whether the university is targeting a particular high school because of its academic reputation, religious affiliation, or the affluence of its student body.
+By contrast, for public research universities, visits to private high schools -- particularly out-of-state schools -- are antithetical to the mission of social mobility for high-achieving, low-income state residents.
+
+This manuscript compares public research universities to selective private universities on the dimension of recruiting visits to private high schools, a behavior associated with the social reproduction orientation of selective private universities.
+Our primary goal is to learn about public research universities, using the behavior of private universities as a benchmark to develop more thoughtful insights about public research universities.
+We analyze recruiting visits made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
+<!-- and 12 selective private liberal arts colleges. -->
+
+<!--
+Note: The data for this book chapter will be slightly different due to using 2017-18 CCD data plus modified criteria (no longer excluding HS w/ certain school types) - but % is still similar
+
+UC Berkeley: 171 (42%) of 404 out-of-state HS visits are to private schools
+CU Boulder: 381 (38%) of 1008 out-of-state HS visits are to private schools
+-->
+
+Little is known about recruiting at private high schools by public universities.
+Therefore, we conduct descriptive analyses that seek to identify basic patterns and relationships.
+Because a recruiting visit to the same private high school is an indicator of a relationship between two actors, we also utilize social network methods in order to compare the recruiting networks of public universities to those of private universities.
+Analyses are informed by the following three research questions:
+
+1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
+1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
+
+The remainder of the manuscript is organized as follows.
+First, we situate off-campus recruiting visits within the broader process of recruiting students and we review scholarship on the relationship between high schools and universities, focusing on scholarship from sociology.
+This literature motivates off-campus recruiting visits as an indicator of a social relation.
+Second, we introduce concepts from social network analysis and motivate empirical research questions.
+Third, we describe data and methods.
+Fourth, we present results.
+Finally, we discuss implications for scholarship.
+
+<!-- SHORT PARAGRAPH GIVING OUTLINE OF CHAPTER -->
+
+<!--  ORIGINAL INTRODUCTION
+
 Prior to the pandemic, admissions counselors from colleges and universities traveled to local high schools each year in order to meet prospective students and maintain relationships with guidance counselors at feeder schools [@RN3519].
-@RN4721 analyzed off-campus recruiting visits made in 2017 by 15 public research universities.
+@RN4758 analyzed off-campus recruiting visits made in 2017 by 15 public research universities.
 Surprisingly, 12 of the 15 universities made more visits to *out-of-state* high schools than *in-state* high schools.
@@
 
-<!--
-Note: The data for this book chapter will be slightly different due to using 2017-18 CCD data plus modified criteria (no longer excluding HS w/ certain school types) - but % is still similar
-
-UC Berkeley: 171 (42%) of 404 out-of-state HS visits are to private schools
-CU Boulder: 381 (38%) of 1008 out-of-state HS visits are to private schools
--->
-
-Whereas @RN4721 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
+Whereas @RN4758 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
 More specifically, we investigate how visits to private high schools by public research universities compare to visits to private high schools by selective private universities.
@@
 A significant caveat is that religiously affiliated universities may prioritize enrollment opportunities for students of the same faith regardless of wealth, but even here the mission is to benefit families from a particular cultural status group.
-<!-- [CITE] -->
 
@@
 A weakness of this literature is that few empirical studies analyze public institutions on a behavior associated with private institutions.
+[FURTHER, FEW STUDIES COMPARE THE BEHAVIOR OF PUBLIC UNIVERSITIES TO THAT OF PRIVATE UNIVERSITIES ON THAT BEHAVIOR.]
 
@@
 We analyze recruiting visits made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
-<!-- and 12 selective private liberal arts colleges.
--->
 
@@
 
-<!-- SHORT PARAGRAPH GIVING OUTLINE OF CHAPTER -->
+-->
 
@@
 For institutions that posted such pages, we scraped the pages once per week throughout 2017.
-Many colleges and universities only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
+Many colleges and universities only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits fto high schools).
 These institutions are excluded from the analyses.
@@
 
+## Social network methods
+
+Analyses consist of simple descriptive statistics and descriptive social network analyses.
+
+A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "network ties" or "edges" between these actors.
+"One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
+"Two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
+Data on recruiting visits by universities to high schools yields a two-mode network, in which an edge -- a recruiting visit -- occurs between a high school (mode 1) and a university (mode 2).
+
+**Constructing two-mode network**.
+We describe construction of social network data with reference to "corporate board-director" networks -- the most commonly analyzed two-mode network -- which consist of directors (mode 1) who serve on organizational boards (mode 2).
+In our school-university two-mode network, the vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visit made between the two (e.g., high school $i$ shares an edge with university $j$ if high school $i$ receives at least one visit from university $j$).
+Visits can only occur between a school-university pair (not a school-school pair or a university-university pair).
+This (weighted) network can be represented as a school-by-university matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 universities) in which matrix cell $a_{i,j}$ identifies the number of visits  high school $i$ received from university $j$.
+<!--[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
+UNWEIGHTED SOMEWHERE]-->
+
+**Transforming two-mode network to one-mode networks**.
+Two-mode networks are often analyzed as one-mode networks [@RN2457].
+@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" (p.
+XXX).
+Thus, a two-mode board-director network can be transformed into two one-mode networks.
+A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ serve on three boards together).
+Similarly, a one-mode board network is created based on a board-by-board matrix in which two boards share an edge if a director sits on both boards and matrix cell $a_{i,j}$ identifies the number of directors that serve on both board $i$ and board $j$.
+
+Following this approach, we create a one-mode high school network in which two private high schools share an edge if they both receive a visit by the same university.
+Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of universities that visited both school $i$ and school $j$<!-- [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
+Similarly, we create a one-mode university network in which two universities share an edge if both universities visited the same high school.
+Cell $c_{i,j}$ of the university-by-university matrix $C$ indicates the number of private high schools that received at least one visit from both university $i$ and university $j$.
+
+The social network analyses presented in this chapter -- particularly for research question 3 -- are primarily based on analysis of one-mode university networks.
+We created separate one-mode university networks for: public universities; private universities; both public and private universities.
+
 # Results
@@
 
-Appendix Figures \@ref(fig:events-count-pubu) and \@ref(fig:events-count-privu) show the number of visits by "type" (public high school, private high school, community college, other) for public research universities and selective private universities, respectively.
+Figures \@ref(fig:events-count-pubu) and \@ref(fig:events-count-privu) show the number of visits by "type" (public high school, private high school, community college, other) for public research universities and selective private universities, respectively.
 On average, the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample conducted `r round((events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()), digits = 0)` off-campus recruiting events in 2017, ranging from a low of `r events_df %>% filter(univ_id == '139959') %>% count() %>% as.numeric()` for the University of Georgia to a high of `r events_df %>% filter(univ_id == '100751') %>% count() %>% as.numeric()` for the University of Alabama.
@@
 
-Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools for public research universities (Figure \@ref(fig:events-hs-count-pubu)) and selective private universities (Figure \@ref(fig:events-hs-count-privu)), with each bar shaded by percent in-state versus out-of-state visits.
+Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) address RQ1 directly by showing the number of visits to private high schools and public high schools for public research universities (Figure \@ref(fig:events-hs-count-pubu)) and selective private universities (Figure \@ref(fig:events-hs-count-privu)), with each bar shaded by percent in-state versus out-of-state visits.
 Only three of the 15 public research universities -- UC-Berkeley, UC-San Diego, and UC-Riverside -- made more in-state than out-of-state total high school visits.
@@
 
-Appendix X describes how we constructed social network data.
-Briefly, we began by constructing a two-mode social network of visits to private high schools (mode 1) by universities (mode 2).
+As described in the methods section, we began by constructing a two-mode social network of visits to private high schools (mode 1) by universities (mode 2).
 Each university and each private high school is a "vertex." A visit from a university to a school is an "edge." Because large two-mode networks like our school-university network are difficult to visualize, two-mode networks are often analyzed as one-mode networks [@RN2457;@RN4663].
@@
 
+# Conflict of Interest Statement
+
+All authors declare that they have no conflicts of interest.
+
+\singlespacing
+
 # References
@@
 <div id="refs"></div>
-
-\newpage
-
-# Social network data appendix
-
-A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "network ties" or "edges" between these actors.
-"One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
-"Two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
-Data on recruiting visits by universities to high schools yields a two-mode network, in which an edge -- a recruiting visit -- occurs between a high school (mode 1) and a university (mode 2).
-
-**Constructing two-mode network**.
-We describe construction of social network data with reference to "corporate board-director" networks -- the most commonly analyzed two-mode network -- which consist of directors (mode 1) who serve on organizational boards (mode 2).
-In our school-university two-mode network, the vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visit made between the two (e.g., high school $i$ shares an edge with university $j$ if high school $i$ receives at least one visit from university $j$).
-Visits can only occur between a school-university pair (not a school-school pair or a university-university pair).
-This (weighted) network can be represented as a school-by-university matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 universities) in which matrix cell $a_{i,j}$ identifies the number of visits  high school $i$ received from university $j$.
-<!--[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
-UNWEIGHTED SOMEWHERE]-->
-
-**Transforming two-mode network to one-mode networks**.
-Two-mode networks are often analyzed as one-mode networks [@RN2457].
-@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" (p.
-XXX).
-Thus, a two-mode board-director network can be transformed into two one-mode networks.
-A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ serve on three boards together).
-Similarly, a one-mode board network is created based on a board-by-board matrix in which two boards share an edge if a director sits on both boards and matrix cell $a_{i,j}$ identifies the number of directors that serve on both board $i$ and board $j$.
-
-Following this approach, we create a one-mode high school network in which two private high schools share an edge if they both receive a visit by the same university.
-Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of universities that visited both school $i$ and school $j$<!-- [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
-Similarly, we create a one-mode university network in which two universities share an edge if both universities visited the same high school.
-Cell $c_{i,j}$ of the university-by-university matrix $C$ indicates the number of private high schools that received at least one visit from both university $i$ and university $j$.
-
-The social network analyses presented in this chapter -- particularly for research question 3 -- are primarily based on analysis of one-mode university networks.
-We created separate one-mode university networks for: public universities; private universities; both public and private universities.
 
@@
 
+```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
+include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
+```
+
+\newpage
+
+```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
+include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
+```
+
+\newpage
+
 ```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
@@
 ```
-
-```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
-include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
-```
-
-\newpage
-
-```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
-include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
-```

### 2023-07-25 text/working/manuscript_rihe_v1.Rmd
added rihe manuscript

--- 2021-06-26 text/manuscript_june_2021.Rmd
@@
 
+\setstretch{1.5}
+
 # Introduction
 
+Analyses of recruiting visits to private high schools can contribute novel insights about the "privatization" of public research universities.
+
+Within the scholarly literature on privatization, one strand of scholarship conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization [@RN4543; @RN2101].
+Of relevance to this chapter, public research universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753], who typically pay two- to three-times more than resident students.
+A second strand within the privatization literature conceptualizes privatization as a process whereby public institutions become more similar -- in terms of characteristics or behavior -- to for-profit or private non-profit organizations [@RN4543].
+A weakness of this literature is that few empirical studies analyze public institutions on a behavior associated with private institutions.
+[FURTHER, FEW STUDIES COMPARE THE BEHAVIOR OF PUBLIC UNIVERSITIES TO THAT OF PRIVATE UNIVERSITIES ON THAT BEHAVIOR.]
+
+Therefore, this chapter compares public research universities to selective private universities on the dimension of recruiting visits to private high schools, a behavior associated with the social reproduction orientation of selective private universities.
+Our primary goal is to learn about public research universities, using the behavior of private universities as a benchmark to develop more thoughtful insights about public research universities.
+We analyze recruiting visits made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
+<!-- and 12 selective private liberal arts colleges.
+-->
+
 Prior to the pandemic, admissions counselors from colleges and universities traveled to local high schools each year in order to meet prospective students and maintain relationships with guidance counselors at feeder schools [@RN3519].
-@RN4721 analyzed off-campus recruiting visits made in 2017 by 15 public research universities.
+@RN4758 analyzed off-campus recruiting visits made in 2017 by 15 public research universities.
 Surprisingly, 12 of the 15 universities made more visits to *out-of-state* high schools than *in-state* high schools.
@@
 
-Whereas @RN4721 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
+Whereas @RN4758 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
 More specifically, we investigate how visits to private high schools by public research universities compare to visits to private high schools by selective private universities.
@@
 
+Little is known about recruiting at private high schools by public universities.
+Therefore, we conduct descriptive analyses that seek to identify basic patterns and relationships.
+Because a recruiting visit to the same private high school is an indicator of a relationship between two actors, we also utilize social network methods in order to compare the recruiting networks of public universities to those of private universities.
+Analyses are informed by the following three research questions:
+
+1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
+1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
+
+<!-- SHORT PARAGRAPH GIVING OUTLINE OF CHAPTER -->
+
+<!--  ORIGINAL INTRODUCTION
+
+Prior to the pandemic, admissions counselors from colleges and universities traveled to local high schools each year in order to meet prospective students and maintain relationships with guidance counselors at feeder schools [@RN3519].
+@RN4758 analyzed off-campus recruiting visits made in 2017 by 15 public research universities.
+Surprisingly, 12 of the 15 universities made more visits to *out-of-state* high schools than *in-state* high schools.
+These out-of-state visits focused on public schools in affluent, predominantly white communities.
+Additionally, most public research universities in our sample made a disproportionate number of visits to out-of-state private high schools.
+For the University of California-Berkeley, for example, 155 (43%) of the 360 out-of-state high school visits were to private high schools.
+For the University of Colorado-Boulder, 321 (36%) of the 901 out-of-state high school visits were to private high schools.
+
+Whereas @RN4758 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
+More specifically, we investigate how visits to private high schools by public research universities compare to visits to private high schools by selective private universities.
+
+## Social mobility, social reproduction, and privatization
+
+The sociologist Max Weber is credited for the insight that education has a "dual character," on one hand, serving *social mobility* by redistributing access to privileged positions and, on the other, serving *social reproduction* by granting privileged families disproportionate access to the educational institutions that confer pathways to privileged positions [@RN2377].
+
+The mission of selective private colleges and universities is more squarely associated with social reproduction rather than social mobility.
+Historically, these institutions depend on patronage from philanthropic interests -- in connection with business and religious interests -- and on wealthy households who provide tuition revenue and donations [@RN4517].
+In turn, selective private institutions contribute to social reproduction by providing access to their patrons.
+The "Chetty" data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile [@RN4722; @RN4723].
+A significant caveat is that religiously affiliated universities may prioritize enrollment opportunities for students of the same faith regardless of wealth, but even here the mission is to benefit families from a particular cultural status group.
+
+The traditional, albeit mythologized, public good mission of public research universities is tied to social mobility and development of the state [@RN2269; @RN921].
+Public research universities are designated the unique responsibility of educating the future civic, professional, and business leaders of the state.
+Quoting 19th century University of Michigan President James Angell, these institutions contribute to social mobility by providing "an uncommon education for the common man" [as cited in @RN3608, p.
+279] who could not afford tuition at elite private institutions.
+
+We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction.
+Recruiting visits to private high schools are consistent with the social reproduction mission of selective private universities, regardless of whether the university is targeting a particular high school because of its academic reputation, religious affiliation, or the affluence of its student body.
+By contrast, for public research universities, visits to private high schools -- particularly out-of-state schools -- are antithetical to the mission of social mobility for high-achieving, low-income state residents.
+
 Analyses of recruiting visits to private high schools can contribute novel insights about the "privatization" of public research universities.
@@
 
+\pagebreak
+\singlespacing
+
 # References

### 2023-08-29 r_r/front_end.Rmd
started revising lit review

--- 2021-06-26 text/manuscript_june_2021.Rmd
@@
 
+\setstretch{1.5}
+
+ABSTRACT
+
+Few empirical analyses of privatization compare public and private universities on a behavior associated with private universities.
+This manuscript analyzes off-campus recruiting visits to private high schools, which were made in 2017 by a convenience sample of 15 public research universities and 14 selective, private universities.
+Sociological scholarship on the relationship between high schools and universities conceives of off-campus recruiting visits as an indicator of a social relation.
+Therefore, we utilize social network concepts and methods to compare the recruiting networks of public and private universities.
+With respect to scale (research question 1), most public research universities in our sample made a disproportionate number of visits to private (out-of-state) high schools, though not as many as private universities.
+With respect to characteristics of visited schools (RQ2), both public and private universities tended to visit predominantly white schools in their home geographic region and the South.
+Public universities tended to visit lower ranked private high schools than private universities.
+Surprisingly, several public research universities visited sectarian private high schools at a rate similar to sectarian private universities.
+With respect to overlap (RQ3), descriptive statistics and community detection methods revealed substantial overlap in the recruiting networks of public and private universities.
+
+\newpage
+
 # Introduction
 
-Prior to the pandemic, admissions counselors from colleges and universities traveled to local high schools each year in order to meet prospective students and maintain relationships with guidance counselors at feeder schools [@RN3519].
-@RN4721 analyzed off-campus recruiting visits made in 2017 by 15 public research universities.
-Surprisingly, 12 of the 15 universities made more visits to *out-of-state* high schools than *in-state* high schools.
+BLAH BLAH BLAH
+
+# Literature Review
+
+## Scholarship on Nonresident Enrollment
+
+We situate this study vis-a-vis scholarship on nonresident enrollment at public research universities, which lies within the broader literature on "privatization" [CITE].
+Against the backdrop of many states disinvesting in higher education, the privatization literature examines the ways that public universities start behaving like private universities by emphasizing revenue generation and the pursuit of prestige in research and enrollment management behaviors.
+The so-called "iron triangle" of enrollment management states that universities pursue the three broad enrollment goals of access, academic profile, and revenue generation [CITE].
+"Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve tradeoffs with other goals.
+Scholarship on privatization expressed concern that the public research universities were emphasizing tuition revenue and rankings and deemphasizing access for state residents.
+
+@RN3753 draw from resource dependence theory to conceptualize the relationship between state appropriations and nonresident enrollment.
+Organizations are dependent on external resources that are important for organizational survival/stability and cannot be easily replaced.
+Public universities depend on state appropriations but these funds became increasingly uncertain in the 1980s and 1990s [@RN2271].
+Resource dependence theory states that one response to resource decline or uncertainty is to seek alternative, substitute resources [CITE].
+Tuition revenue is a potential substitute for state appropriations.
+Most states cap resident tuition price, but not nonresident tuition price.
+Therefore, @RN3753 argued that public universities have a financial incentive to grow nonresident enrollment in response to declines in state appropriations.
+Analyzing panel data from 2002-03 to 2012-13, @RN3753 found that a 10% decline in state appropriations was associated with a 2.7% increase in nonresident enrollment at all public universities and a 5.0% increase in nonresident enrollment at research-extensive universities.
+
+Other studies of nonresident enrollment examine university enrollment composition.
+Using data from NPSAS 2011-12, @RN3685 show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients and are less likely to be Black or LatinX.
+Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and LatinX students.
+@RN4290 examine whether growth in the number of nonresident students causes resident enrollment to decline.
+They find that nonresident enrollment "crowds out" resident enrollment at prestigious public research universities, but not at less prestigious public research universities.
+
+How did public research universities go about attracting all these nonresident students.
+One mechanism is financial aid.
+@RN2535 shows that nonresident students are less sensitive to sticker price than resident students.
+Because nonresident prospects may be considering several options -- in-state, out-of-state, public, private -- they are sensitive to the generosity of institutional aid offers [CITE].
+For example, @RN3762 analyze the effect of a University of Iowa institutional merit aid program for nonresident admits that offered higher awards for admits with higher academic achievement.
+Regression discontinuity analyses found that the program increased the probability of enrollment, particularly for high achieving students.
+These results suggest that high-achieving nonresident students face many good opportunities and require substantial institutional aid to be convinced to enroll.
+
+Earlier in the "enrollment funnel," universities utilize marketing and recruiting interventions to attract nonresident applicants.
+One widely utilized intervention is off-campus recruiting visits by admissions counselors to local high schools.
+@RN3519 found that colleges value this visits as a means of meeting prospective students and maintaining relationships with guidance counselors at feeder schools.
+@RN4758 analyzed off-campus recruiting visits by 15 public research universities, finding that 12 of these universities made more visits to out-of-state
+high schools than in-state high schools.
 These out-of-state visits focused on public schools in affluent, predominantly white communities.
-Additionally, most public research universities in our sample made a disproportionate number of visits to out-of-state private high schools.
-For the University of California-Berkeley, for example, 155 (43%) of the 360 out-of-state high school visits were to private high schools.
-For the University of Colorado-Boulder, 321 (36%) of the 901 out-of-state high school visits were to private high schools.
+Although @RN4758 focused on visits to public high schools, they noted a surprising number of visits to out-of-state private high schools.
+However, we know little about this private school visits, for example, which sorts of schools are they visiting and at what scale.
 
-<!--
-Note: The data for this book chapter will be slightly different due to using 2017-18 CCD data plus modified criteria (no longer excluding HS w/ certain school types) - but % is still similar
+## Scholarship on Linkages Between Private Schools and Colleges
 
-UC Berkeley: 171 (42%) of 404 out-of-state HS visits are to private schools
-CU Boulder: 381 (38%) of 1008 out-of-state HS visits are to private schools
--->
+A separate thread of scholarship analyzes linkages between private schools and colleges. Nationwide, dddd
 
-Whereas @RN4721 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
-More specifically, we investigate how visits to private high schools by public research universities compare to visits to private high schools by selective private universities.
-
-## Social mobility, social reproduction, and privatization
-
-The sociologist Max Weber is credited for the insight that education has a "dual character," on one hand, serving *social mobility* by redistributing access to privileged positions and, on the other, serving *social reproduction* by granting privileged families disproportionate access to the educational institutions that confer pathways to privileged positions [@RN2377].
-
-The mission of selective private colleges and universities is more squarely associated with social reproduction rather than social mobility.
-Historically, these institutions depend on patronage from philanthropic interests -- in connection with business and religious interests -- and on wealthy households who provide tuition revenue and donations [@RN4517].
-In turn, selective private institutions contribute to social reproduction by providing access to their patrons.
-The "Chetty" data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile [@RN4722; @RN4723].
-A significant caveat is that religiously affiliated universities may prioritize enrollment opportunities for students of the same faith regardless of wealth, but even here the mission is to benefit families from a particular cultural status group.
-<!-- [CITE] -->
-
-The traditional, albeit mythologized, public good mission of public research universities is tied to social mobility and development of the state [@RN2269; @RN921].
-Public research universities are designated the unique responsibility of educating the future civic, professional, and business leaders of the state.
-Quoting 19th century University of Michigan President James Angell, these institutions contribute to social mobility by providing "an uncommon education for the common man" [as cited in @RN3608, p.
-279] who could not afford tuition at elite private institutions.
-
-We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction.
-Recruiting visits to private high schools are consistent with the social reproduction mission of selective private universities, regardless of whether the university is targeting a particular high school because of its academic reputation, religious affiliation, or the affluence of its student body.
-By contrast, for public research universities, visits to private high schools -- particularly out-of-state schools -- are antithetical to the mission of social mobility for high-achieving, low-income state residents.
-
-Analyses of recruiting visits to private high schools can contribute novel insights about the "privatization" of public research universities.
-Within the scholarly literature on privatization, one strand of scholarship conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization [@RN4543; @RN2101].
-Of relevance to this chapter, public research universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753], who typically pay two- to three-times more than resident students.
-A second strand within the privatization literature conceptualizes privatization as a process whereby public institutions become more similar -- in terms of characteristics or behavior -- to for-profit or private non-profit organizations [@RN4543].
-A weakness of this literature is that few empirical studies analyze public institutions on a behavior associated with private institutions.
-
-Therefore, this chapter compares public research universities to selective private universities on the dimension of recruiting visits to private high schools, a behavior associated with the social reproduction orientation of selective private universities.
-Our primary goal is to learn about public research universities, using the behavior of private universities as a benchmark to develop more thoughtful insights about public research universities.
-We analyze recruiting visits made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
-<!-- and 12 selective private liberal arts colleges.
--->
-
-Because little is known about recruiting at private high schools by public universities, we conduct descriptive analyses that seek to identify basic patterns and relationships.
-Because a recruiting visit to the same private high school is an indicator of a relationship between two actors, we also utilize social network methods in order to compare the recruiting networks of public universities to those of private universities.
-Analyses are informed by the following three research questions:
-
-1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
-1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
-1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
-
-<!-- SHORT PARAGRAPH GIVING OUTLINE OF CHAPTER -->
-
-# What do we know about off-campus recruiting visits
-
-This section provides context for our analyses.
-First, we situate off-campus recruiting within the broader set of marketing and recruiting interventions in higher education and review what market research says about off-campus recruiting.
-Second, we review empirical scholarship from sociology that considers off-campus recruiting, emphasizing scholarship that considers the relational aspects of recruiting visits and scholarship that considers private high schools.
-
-## Situating off-campus recruiting within enrollment management
-
-The "enrollment funnel" -- depicted in Figure \@ref(fig:em-funnel) -- is a conceptual heuristic that identifies stages in the student recruitment process (prospects, inquiries, applicants, accepted applicants, and enrolled students).
-"Prospects" are "all the potential students you would want to attract to your institution" [@RN4322].
-"Inquiries" are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own.
-The enrollment management industry uses the enrollment funnel to inform marketing and recruiting interventions that target specific stages.
-Most scholarship on enrollment management focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [e.g., @RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948].
-By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664].
-<!--[SHOULD WE TRY TO ADD SOME CONCRETE NUMBERS ON $ SPENDING AT PARTICULAR UNIVERSITIES?]-->
-
-INSERT FIGURE \@ref(fig:em-funnel) ABOUT HERE
-
-Institutions identify undergraduate "prospects" by purchasing "student lists" -- containing contact, demographic, and academic achievement information -- from College Board, ACT, and other vendors.
-Universities control which prospects are contained within a list by filtering on criteria such as zip code, test scores, and high school GPA.
-Once prospects and inquiries are identified, they are targeted with remote and face-to-face recruiting interventions designed to solicit applications and deepen engagement.
-Remote recruiting interventions include postcards, brochures, emails, text messages, and targeted social media.
-Face-to-face recruiting interventions include on-campus visits by prospects and off-campus recruiting visits by admissions representatives to high schools, community colleges, college fairs, etc.
-Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411]<!--[CITE OTHER]-->.
-Given the rise in "stealth applicants" who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.
-
-What do we know about off-campus recruiting from previous research?
-As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practitioner-oriented publications.
-Market research describes off-campus recruiting visits as a means of identifying prospects and deepening engagement with prospects already being targeted through mail/email [@RN4323; @RN4402; @RN4664].
-
-@RN4402 documents the self-reported efficacy of marketing/recruiting interventions.
-For the median private 4-yr institution, off-campus visits were the second highest source of inquiries (after student list purchases), accounting for 17% of inquiries.
-Off-campus visits were tied with student list purchases as the highest source of enrollees, accounting for 18% of enrollees.
-For the median public institution, off-campus visits accounted for 19% of inquiries (second only to student list purchases) and accounted for 16% of enrollees (ranked third after stealth applicants and on-campus visits).
-
-With respect to expenditure, Table \@ref(tab:ug-recruit-budget), reproduced from @RN4664, shows the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.^[Table drawn directly from @RN4664 Figure 9, which is based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions.] The average public university spent 16% of its recruiting budget on off-campus recruiting visits, compared to 12% of its budget on purchasing student lists and 17% of its budget on "prospective student communications" (e.g., mail, email, text, social media) targeting prospects and inquiries.
-An emergent trend over the past decade -- partially a response to public universities seeking nonresident students -- has been the growth of "regional recruiters" who target specific metropolitan areas in the US and abroad [@RN4021].
-These regional recruiters may be college/university employees or they may be independent contractors who live in the metropolitan area they recruit.
-
-<!-- QUESTIONS ABOUT THE RNL 2020 COST OF RECRUITING AN UNDERGRADUATE STUDENT REPORT, FIGURE 9
-
-What does "recruitment publications" include?
-what does "prospective student communications" include?
-what does "event" include? can I assume this is on-campus events only cuz "travel" is a separate category?
-what does "web services and digital advertising" include? Does this include social media?
--->
-
-## Empirical scholarship from sociology
-
-<!--
-
-A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits [CITE].
-
--->
-
-Empirical academic scholarship on off-campus recruiting is mostly limited to a modest number of sociological case studies, which typically analyze off-campus recruiting as part of a broader analysis of enrollment management [e.g., @RN4538; @RN4324; @RN3519; @RN4520; @RN4407].
-@RN4324 analyzes visits from the perspective of students at two racially and socioeconomically diverse public high schools.
-@RN4324 found that high school visits -- including college fairs, instant decision events, and small-group representative visits -- influenced where students applied and where they enrolled.
-This finding was strongest for first-generation students and underrepresented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college" (p.
-XXX).
-This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and made them feel wanted.
-For example, @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more" (p.
-XXX).
-By contrast, affluent students with college-educated parents were less taken by such overtures and more concerned with college prestige.
-
-@RN3519, in an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of off-campus recruiting visits.
-Stevens [-@RN3519, p.
-54] states that "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide." Therefore, during the autumn "travel season," admissions officers visit selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
-53-54).
-The College tended to visit the same "feeder" schools year after year because recruiting depends on long-term relationships with high schools.
-The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and have the resources and motivation to host a successful visit.
-Whereas @RN4402 highlights the effect of recruiting visits on inquiries and enrollees, findings from @RN3519 suggest that the College may have valued recruiting visits primarily as a means of maintaining relationships with guidance counselors.
-From this perspective, recruiting visits may affect outcomes such as inquiries, applications, and matriculation through their effect on high school guidance counselors.
-The logic is that a guidance counselor who views a college favorably will steer students to the college.
-
-<!--
-
-@RN3519 and Khan [-@RN4321;-@RN4407] are centrally important to our study because they analyze relationships between college admissions counselors and high school guidance counselors.
-
--->
-
-Although not about recruiting visits per se, Khan [-@RN4321;-@RN4407] is centrally important for our study because he lays out a conceptual explanation of why colleges and private high schools develop relationships with one another (i.e., what is each trying to obtain from the other).
-@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p.
-98).
-The answer begins by considering the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors.
-Colleges want high-achieving students who can pay tuition and donate.
-They want low acceptance and high yield rates, which are important for rankings.
-Colleges also want a class composed of "interesting characters" whose curricular and extracurricular strengths meet the needs of important campus constituents (e.g., academic majors, the athletic department, clubs, etc.).
-Elite private high schools want to send _all_ students to the best college possible.
-Here, high school guidance counselors face "the pressure of making sure their school seems worth it – that \ldots paying some $40,000+, really does aid students in the college process" [@RN4321, p.
-105].
-
-The challenge faced by high school counselors at elite private schools is that "some of these students are slightly better than others.
-These students will likely get into more than one school -- but they can only attend one.
-And this will lower the chances of your 'second-best' students getting into top schools" [@RN4407, pp.
-173-174].
-"Luckily," Khan [-@RN4321, p.
-105] writes, "the problem for elite boarding schools matches up quite nicely with the problem faced by elite colleges." That is, although college admissions officers receive applications from many outstanding students,
-
-> These outstanding students will also be  outstanding to Princeton, Yale, Stanford, and everywhere else.
-How do you know the ones you pick will attend your school?
-You can't quite trust applicants, as they are all likely to tell you how much they want to go to your school.
-And if students you accept go somewhere else, there's not much you can do.
-But you can get better information -- information you want -- from their high school.
-And you can reward that school for good information and sanction it for bad information [@RN4407, p.
-173].
-
-<!--
-
- And you can reward that school for good information and sanction it for bad information [@RN4407, p. 173].
-
--->
-
-This desire by colleges for trustworthy information about applicant intentions creates an opportunity for high school counselors to advocate on behalf of their students.
-This opportunity depends on guidance counselors having personal relationships with university admissions offices and on having small enough caseloads to advocate for each student individually.
-
-To explain how high school counselors capitalize on this opportunity, @RN4407 describes two hypothetical students -- Susan and Billy -- who both apply to Harvard and Yale.
-Susan is a shoo-in at both universities, but wants to attend Harvard.
-Billy has a weaker academic record than most Ivy League students, but has strong extracurricular activities.
-The guidance counselor tells Harvard that Susan wants to attend Harvard.
-Next, he informs Yale that Susan will choose Harvard, but Billy loves Yale and has great "character" and extracurricular activities.
-In the end, Harvard rejects Billy and accepts Susan, thereby, decreasing acceptance rate and increasing yield.
-Yale rejects Susan and accepts Billy, thereby, also decreasing acceptance rate and increasing yield.
-
-The horsetrading described by @RN4407 depends on a relationship where the college can trust statements made by the high school counselor and vice-versa.
-This relationship is the product of repeated interactions over many years.
-A high school that makes false statements about applicant intentions faces consequences.
-The college "might stop taking these telephone calls and ignore the information provided.
-They may even start accepting fewer students from the school, thinking it is less than an honest place" [@RN4321, p.
-106].
-Because the college and the high school are mutually dependent, however, both "have an incentive to continue with a strong, honest relationship" [@RN4321, p.
-106].
-Although, such horsetrading may be less pervasive now than it was in prior decades and may be less common at non-elite private schools.
-Additionally, college admissions officers from public universities likely have less authority to engage in these tacit negotiations because admissions criteria at public universities face greater public scrutiny than admissions criteria at private colleges and universities.
-
-### Visits as an indicator of a social relation
-
-@RN3519 and Khan [-@RN4321;-@RN4407] suggest that strong relationships are mutually important for the college and for the private high school.
-Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another.
-Without a strong relationship, it is unlikely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
-Even in the absence of the horsetrading described by @RN4407, relationships enable the college admissions counselor and the high school guidance counselor to tell one another "their story" and relay that story to constituents [@RN3519].
-The college admissions counselor explains why the college/university is a "special place" that high school students should want to attend [@RN3519].
-The guidance counselor explains why the high school is a special place, that even students with lower grades have outstanding extracurricular strengths that will benefit the college [@RN4321].
-
-The presence of a recruiting visit between a college and a private high school is an indicator that the college and the high school have a relationship.
-From an empirical perspective, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
-From a logical perspective, we argue that, first, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school.
-Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
-Third, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls).
-
-Conceptualizing a recruiting visit as an indicator of a relationship between a college and a high school motivates the use of social network methods, which analyze the network defined by "network ties" (i.e., visits) between actors (colleges and high schools).
-Prior research has not used social network methods to analyze recruiting visits from colleges to high schools.
-Analyzing the network of recruiting visits to high schools enables us to investigate the extent to which public research universities are visiting similar sets of private high schools as private colleges and universities, and also the extent to which they are visiting the same private high schools.
-In turn, we hope these analyses yield novel insights to scholarship on the privatization of public higher education.
-
-# Social network analysis concepts
-
-Having conceptualized a recruiting visit as an indicator of a social relation, this section introduces basic concepts from social network analysis and motivates the research questions that guide empirical analyses.
-
-A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "network ties" or "edges" between these actors.
-"One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
-Similarly, the social network of Twitter consists of handles (vertices) who are connected to one another by following or being followed.
-
-Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network, each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
-For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
-The most commonly analyzed two-mode network in social networks literature is a corporate board-director network  [e.g., @RN4663].
-These networks consist of directors (mode 1) and organizational boards (mode 2), and a particular director shares an edge with a particular organizational board if they sit on that board.
-Similarly, our recruiting visit data form a two-mode network, consisting of private high schools (mode 1) and colleges (mode 2).
-An off-campus recruiting visit from a college/university to a private high school is the "edge" that connects two particular vertices.
-In this network, edges can only occur between vertices of a different type; that is, a college can visit a high school, but colleges cannot visit other colleges and high schools cannot receive visits from other high schools.
-
-To reduce complexity, two-mode network graphs are often analyzed as one-mode networks [@RN2457;@RN4663].
-Our two-mode college-school network can be transformed into a one-mode college network in which each vertex is a college/university and two colleges share an edge if both colleges visited at least one high school in common.
-The *weight* of an edge indicates the number of high schools that both colleges visited.
-For example, if there are 200 private high schools that received a visit from both Notre Dame and Villanova, the weight of the edge between Notre Dame and Villanova is 200.
-
-## RQ1: Degree centrality
-
-<!-- 
-In social network analysis, *centrality* is a notion of how important or prominent or "in the middle of things"
-*centrality* refers to the importance or prominence of an actor/vertex in a social network [CITE].
--->
-
-In social network analysis, *centrality* refers to the importance or prominence or "being in the middle of things" of an actor/vertex in a social network.<!--[CITE]--> Many alternative measures of centrality have been developed.
-All measures agree that centrality is an actor/vertex-level construct (e.g., each college in our network will have a centrality value, regardless of which centrality measure we use).
-However, different measures of centrality are based on different theoretical conceptualizations -- for example, being directly connected to the most actors versus being the intermediary between otherwise disconnected actors -- and are operationalized using different mathematical algorithms.
-
-The simplest measure of centrality, *degree centrality* measures the number of edges directly connected to a vertex.
-For each college in our two-mode network, degree centrality is simply the number of different private high schools visited by the college.
-For each high school in our network, degree centrality is the number of colleges in our network that visited the high school.
-Social network theory conceptualizes degree centrality as a measure of "local" centrality, capturing the number of direct connections for each actor/vertex.
-For our empirical context, we conceive of degree centrality as a measure of scale of the number of private high schools a college visits and, equivalently, the number of private high schools we observe having a social relation with each college.
-Given that we conceptualize visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges/universities, we are interested in comparing how scale differs between public and private colleges/universities.
-This interest motivates research question 1, "How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?" We answer this research question by comparing degree centrality across universities.
-
-<!-- 
-Social network theory conceptualizes degree centrality as a measure of "local" centrality; it captures the number of direct connections but it does not capture the extent to which an actor/vertex is indirectly connected to others or whether an actor is connected to highly-connected others.
--->
-
-Degree is a limited measure of centrality in that it only identifies direct connections.
-By contrast, *k-path centrality* measures the extent to which an actor/vertex is indirectly connected to others, *betweenness centrality* measures the extent to which a vertex is an intermediary between otherwise disconnected groups of actors, and *eigenvector centrality* measures the extent to which a vertex is connected to highly-connected others.
-Betweenness centrality tends to be relevant for empirical contexts (e.g., which manager gets credit for an idea) where an actor who occupies a position between groups can benefit by being a broker of information/ideas [@RN975].
-By contrast, this chapter is more concerned with whether a particular college tends to have indirect connections with some colleges but not others, and what is the subset of high schools this group of colleges tends to visit.
-Research question 3, motivated below, explores these ideas.
-
-## RQ2: Ego networks and homophily
-
-Because the data structure of networks is complicated, a useful first step is to analyze "ego networks" rather than the entire social network.
-An "ego" is a single "focal" node (e.g., The University of Notre Dame).
-An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" (p.
-XXX)<!-- [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ]-->.
-For example, the University of Notre Dame ego network consists of all private high schools that received at least one visit from Notre Dame.
-Additionally, for each high school visited by Notre Dame, the ego network may include all colleges/universities in our sample that also visited the high school.
-This chapter analyzes recruiting visits to private high schools by 41 colleges and universities, which we can think of as 41 ego networks.
-
-A common finding in social networks research is that actors are more likely to form connections with actors who are similar to them [@RN1722].
-Said differently, ego networks are biased towards "homophily" rather than "heterophily." Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be friends on Facebook if they have similar political ideologies).
-Heterophily, the opposite of homophily, is when pairs of connected vertices have different characteristics from one another.
-
-In our analyses of recruiting visits from colleges to private high schools, we are interested in the existence of homophily versus heterophily for two reasons.
-First, prior scholarship suggests that private colleges and private high schools are more likely to have a relationship when they share common ideologies or view themselves as belonging to the same echelon [@RN3519; @RN4321;@RN4407].
-Second, with respect to our substantive interest in the behavior of public research universities, the characteristics of visited private high schools have consequences for subsequent enrollment compositions of public research universities.
-Therefore, we are interested in whether universities tend to visit high schools that are similar to them on certain characteristics.
-Additionally, we are interested in whether public research universities favor high schools with certain characteristics, independent of homophily.
-These interests motivate research question 2, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by private universities?"
-
-Decisions about which private school characteristics to analyze were informed by prior research [e.g., @RN4724; @RN4504; @RN4321; @RN3519; @RN4588].
-In particular, @RN4504 used data from several national surveys to analyze long-term trends in private school enrollment by family income.
-The percentage of American (elementary school) students attending private school declined from 15% in the mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
-With respect to family income, the private school enrollment rate of high-income families (around 17%) and low-income families (around 4%) remained stable over time, but the enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
-These declines were substantially driven by declines in the number of students attending Catholic schools, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
+TEXT YOU WROTE ABOUT MURNANE AND REARDON
+In particular, Murnane & Reardon (2018) used data from several national surveys to analyze long-term trends in private school enrollment by family income.
+The percentage of American (elementary school) students attending private school declined from 15% in the With respect to family income, the private school enrollment rate of high-income families (around 17%) and low-income families (around 4%) remained stable over time, but the enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
+These declines were substantially driven by declines in the number of students attending Catholic
+schools, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
 Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
@@
 However, for high income families, rates of private school enrollment do not differ substantially across race.
-In the South, there has been a long-term increase in private school enrollment, driven by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsectarian private schools by high-income families.
+In the South, there has been a long-term increase in private school enrollment, driven
+by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsectarian private schools by high-income families.
+mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
 
-Based on these findings and logical argument (and also data limitations), our analyses focus on the following private school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
-We analyze geographic region because, for most colleges and universities, enrollment demand is likely to be stronger at high schools in the same geographic region, but nationally prestigious colleges and universities may experience high demand throughout the country.
-We analyze religious affiliation because private colleges are more likely to have a relationship with private high schools with a similar religious affiliation.
-Although public universities are formally secular, we are interested in whether particular public universities tend to target religiously affiliated private high schools.
-We analyze academic reputation based on the idea that more highly ranked colleges are likely to target highly ranked private high schools.
-Racial composition is of substantive interest because the racial composition of visited high schools has consequences for the racial composition of colleges and universities.
-Given our interests in social reproduction versus social mobility, we would also analyze tuition price and household income, but these data are not available for private high schools.
-
-## RQ3: Network similarity and community detection
-
-This chapter conceptualizes recruiting visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges and universities.
-We are interested in how similar the recruiting networks of public research universities are to those of private colleges and universities, thereby motivating research question 3, "To what extent do public research universities and private universities visit overlapping sets of private high schools?"
-
-We address RQ3 by graphing the recruiting network and by identifying "clusters" of universities that have similar recruiting networks.
-First, network graphs show vertices (e.g., universities) as circles, with vertices that share many connections located close together and vertices that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph.
-In addition to network graphs, network scholarship often uses cluster analysis methodologies to identify vertices that share common structure, based purely on patterns of network ties.
-
-# Data and methods
-
-Our broader project collected data on off-campus recruiting visits made by a convenience sample of colleges and universities during the 2017 calendar year.
-The data collection sample comes from two different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), and all private universities in the top 100 of U.S.
-News and World Report National Universities rankings (N=58).
-<!-- and all private colleges in the top 50 of U.S.
-News and World Report Liberal Arts Colleges rankings (N=47).-->For each of these institutions, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits.
-For institutions that posted such pages, we scraped the pages once per week throughout 2017.
-Many colleges and universities only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
-These institutions are excluded from the analyses.
-Our final analysis sample consists of 15 public research universities and 14 private research universities.
-<!--12 private liberal arts colleges [MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->
-
-INSERT TABLE \@ref(tab:sample-characteristics) ABOUT HERE
-
-Table \@ref(tab:sample-characteristics) shows selected characteristics for the universities in our analysis sample.
-Given that we collected recruiting data for private universities ranked in the top 100 of U.S.
-News and World Report, one concern is whether it makes sense to compare public research universities not ranked in the top 100 to private universities ranked in the top 100.
-However, the columns in Table \@ref(tab:sample-characteristics) for 25th and 75th percentile SAT score of enrolled freshmen suggest that private universities ranked lower than 75 have test score ranges that are fairly similar to public research universities not ranked in the top 100.
-The five public research universities ranked 124 or below have score ranges that are modestly lower, particularly the University of Nebraska-Lincoln, but remain comparable to private universities ranked 75 to 100.
-One exception is that Stevens Institute of Technology (rank 80) has substantially higher test scores.
-
-The data on university characteristics come from the 2017 Integrated Postsecondary Education Data System (IPEDS) and 2020 Best Colleges ranking by U.S.
-News & World Report.
-For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.^[For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small amount of schools.] Only high schools that enroll at least 10 12th grade students, is not primarily a virtual school, and is located in the 50 U.S.
-states, the District of Columbia, or land regulated by the Bureau of Indian Affairs is included in our analysis.
-
-# Results
-
-## RQ1: Scale of visits
-
-Research question 1 asks, "How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?" This question can be answered by counting the number of visits to private high schools, which is equivalent to calculating the degree centrality for each university.
-In addition to scale, we are also interested in the relative scale of visits to private high schools.
-That is, the number of visits to private high schools as a proportion of all off-campus recruiting visits, or as a proportion of all recruiting visits to high schools.
-
-Appendix Figures \@ref(fig:events-count-pubu) and \@ref(fig:events-count-privu) show the number of visits by "type" (public high school, private high school, community college, other) for public research universities and selective private universities, respectively.
-On average, the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample conducted `r round((events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()), digits = 0)` off-campus recruiting events in 2017, ranging from a low of `r events_df %>% filter(univ_id == '139959') %>% count() %>% as.numeric()` for the University of Georgia to a high of `r events_df %>% filter(univ_id == '100751') %>% count() %>% as.numeric()` for the University of Alabama.
-By contrast, the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample conducted an average of `r round((events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()), digits = 0)` events, ranging from a low of `r events_df %>% filter(univ_id == '186867') %>% count() %>% as.numeric()` by Stevens Institute of Technology (located in Hoboken, NJ) to a high of `r events_df %>% filter(univ_id == '239105') %>% count() %>% as.numeric()` by Marquette University (located in Milwaukee, WI).
-Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs','priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())*100, digits=1)`% of visits were to a public or private high school, whereas for selective private universities `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('pub_hs','priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())*100, digits=1)`% of all visits were to a public or private high school.
-The lower percentage for public research universities is because many public research universities made a substantial number of visits to community colleges whereas private universities did not.
-
-Figures \@ref(fig:events-hs-count-pubu) and \@ref(fig:events-hs-count-privu) show the number of visits to private high schools and public high schools for public research universities (Figure \@ref(fig:events-hs-count-pubu)) and selective private universities (Figure \@ref(fig:events-hs-count-privu)), with each bar shaded by percent in-state versus out-of-state visits.
-Only three of the 15 public research universities -- UC-Berkeley, UC-San Diego, and UC-Riverside -- made more in-state than out-of-state total high school visits.
-Notably, the University of California voluntarily adopted a nonresident enrollment cap in 2017, following pressure from state legislators who had issued a bill to cap nonresident enrollment.
-Of the 14 selective private universities in our sample, only Baylor University (Waco, TX) made more in-state than out-of-state total high school visits.
-
-INSERT FIGURE \@ref(fig:events-hs-count-pubu) AND FIGURE \@ref(fig:events-hs-count-privu) ABOUT HERE
-
-With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of `r events_df %>% filter(univ_id == '110671', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by UC-Riverside to a high of `r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by the University of Alabama (which accounted for `r round((events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of all visits to private schools by public research universities in our sample), with the median university, The University of Pittsburgh, making `r events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()` visits.
-Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of private high school visits were to out-of-state schools while `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of public high school visits were to out-of-state schools.
-This result is consistent with the notion that public research universities placed more value on out-of-state private high school students than in-state private high school students because out-of-state students generate substantially more tuition revenue.
-
-For selective private universities, the number of visits to private high schools ranged from a low of `r events_df %>% filter(univ_id == '186867', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` by Stevens Institute of Technology to a high of `r events_df %>% filter(univ_id == '152080', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` by Notre Dame, with the median universities -- Boston College and Northwestern University -- visiting `r events_df %>% filter(univ_id == '164924', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` and `r events_df %>% filter(univ_id == '147767', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` private high schools, respectively.
-Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities.
-That said, several public research universities in our sample -- University of Colorado-Boulder (`r events_df %>% filter(univ_id == '126614', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), University of South Carolina (`r events_df %>% filter(univ_id == '218663', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), and University of Alabama  (`r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
-
-The relative scale of visits to private high schools -- defined as private high school visits as a percentage of all high school visits -- also tended to be substantially higher at selective private universities than at public research universities.
-Across all selective private universities in our sample, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of high school visits were to private high schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
-Although, the relative emphasis on private high schools was a bit closer for out-of-state visits; across all selective private universities, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% of out-of-state high school visits were to private schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
-
-Even though selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools.
-Figure \@ref(fig:actual-proportional-pubu) (public universities) and Figure \@ref(fig:actual-proportional-privu) (private universities) show the actual number of private school visits made compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.^[When calculating the hypothetical, proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university.
-Our rationale for this decision is that it is unhelpful to include schools in states that the university ignored entirely.] Figure \@ref(fig:actual-proportional-pubu) shows that the actual number of private school visits exceeded the proportional number of private school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
-For UC-Berkeley, private school visits represented 27% of all high school visits but would have represented 19% had UC-Berkeley visited public and private schools at the same rate.
-For the University of Georgia, which represented the extreme for public universities, private school visits represented 37% of all high school visits but would have represented 19% had the university visited public and private schools at the same rate.
-Figure \@ref(fig:actual-proportional-privu) shows that this disparity between actual versus proportional visits was much greater for private universities than public universities.
-Catholic universities made the most disproportionate number of private high school visits.
-For Notre Dame, private school visits represented 63% of actual high school visits but would have represented 18% of proportional visits.
-
-INSERT FIGURE \@ref(fig:actual-proportional-pubu) AND FIGURE \@ref(fig:actual-proportional-privu) ABOUT HERE
-
-## RQ2: Characteristics of visited schools
-
-Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privhs-pubhs) address research question 2, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?"
-
-Figure \@ref(fig:region-pubu-privu) shows the geographic region -- Northeast, Midwest, South, and West -- of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel).
-Scholarship on the relationship between geographic proximity and student demand tends to find that nationally prestigious universities enjoy strong demand across the nation, while less prestigious universities rely primarily on demand from students located nearby [e.g., @RN2133].
-The visit patterns for private universities are consistent with this finding; less prestigious universities tended to focus on private high schools in their home region, while more prestigious universities tended to visit many private high schools outside their home region.
-Similarly, scholarship on student demand for out-of-state public universities finds that most public universities rely on demand from out-of-state students living in nearby states [@RN2536; @RN2535; @RN2546].
-Most public research universities in our sample visited a disproportionate number of private high schools in their home geographic region.
-UC-Berkeley and CU Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.
-
-INSERT FIGURE \@ref(fig:region-pubu-privu) ABOUT HERE
-
-In the universe of all private high schools (top row of Figure \@ref(fig:region-pubu-privu)), there are more schools located in the South than any other geographic region, consistent with the finding from @RN4504 about the long-term growth in private school enrollment in the South.
-Universities not located in the South tended to visit more private high schools in the South than any other region, except their home region.
-This finding emerged for both the public universities and private universities in our sample.
-
-Figure \@ref(fig:religion-pubu-privu) shows the religious affiliation -- Catholic, Christian, Nonsectarian, and Other -- of visited private high schools.
-The results for selective private universities (bottom panel) follow our expectations: Nonsectarian universities tended to visit a higher proportion of nonsectarian private high schools; Catholic universities visited a higher proportion of Catholic high schools; and Christian universities tended to visit a relatively higher share of Christian high schools.
-
-INSERT FIGURE \@ref(fig:religion-pubu-privu) ABOUT HERE
-
-Results for public research universities (top panel) are more interesting.
-Despite being nonsectarian, the majority of public research universities visited a high share of religiously affiliated private high schools, particularly Catholic schools.
-Surprisingly, Catholic schools represented at least 40% of private high school visits for `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'public') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample.
-By contrast, Catholic schools represented at least 40% of visits for only `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'private') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample (the four Catholic universities and also Texas Christian University and Stevens Institute of Technology).
-For public research universities, the emphasis on visiting Catholic and Christian high schools rather than nonsectarian private high schools tended to be stronger at less prestigious institutions.
-
-Figure \@ref(fig:rank-pubu-privu) shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools.
-For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visited a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.
-A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.
-
-INSERT FIGURE \@ref(fig:rank-pubu-privu) ABOUT HERE
-
-A similar pattern emerged for the public research universities in our sample; more highly ranked universities tended to visit a higher share of highly rated private high schools than lower ranked universities.
-In comparison to the private universities in our sample, the public universities in our sample tended to visit a higher share of private high schools that were not highly rated.
-To a great extent, this finding is merely a consequence of our sampling strategy; we attempted to collect recruiting visit data from all public research universities but we only collected recruiting visit data from private universities ranked in the top 100 of U.S.
-News and World Report.
-That said, the finding that public research universities visited a large share of low-rated private high schools is consistent with the idea that many public research universities visit private high schools in search of full-pay students rather than academic superstars.
-
-Figure \@ref(fig:enroll-pubu-privu) shows the 12th grade enrollment of visited private high schools.
-Compared to the universe of private high schools, the universities in our sample tended to visit schools that enrolled more 12th graders.
-Generally, the findings were pretty similar across public and private universities; for most universities, more than half of private school visits were to schools that enrolled at least 100 12th graders.
-However, public universities tended to visit a slightly larger share of high schools with fewer than 50 12th graders and private universities tended to visit a higher share of high schools with 12th grade enrollment of 50-100.
-
-INSERT FIGURES \@ref(fig:enroll-pubu-privu) AND \@ref(fig:enroll-pubu-privhs-pubhs) ABOUT HERE
-
-Figure \@ref(fig:enroll-pubu-privhs-pubhs) shows the 12th grade enrollment of visited private high schools as well as the 12th grade enrollment of visited public high schools for the public research universities in our sample.
-As seen, a large majority of public high school visits for all 15 universities were to schools with more than 150 12th graders enrolled (bottom panel).
-By contrast, most of the visited private schools tended to have fewer than 150 12th graders enrolled.
-Although this is somewhat to be expected, as public high schools tend to be larger in size than private schools (top rows of Figure \@ref(fig:enroll-pubu-privhs-pubhs)), there still appears to be a disproportionate amount of smaller private high schools visited compared to smaller public high schools.
-This suggests that the public universities in our sample were willing to take the time to visit private schools, even when they enroll far fewer 12th graders.
-
-Figure \@ref(fig:race-pubu-privu) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited private high schools.
-Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups.
-For over 65%<!--0.6632124--> of schools in the universe of private high schools (top row of Figure \@ref(fig:race-pubu-privu)), Black/Latinx/Native students comprise less than 20% of enrolled students.
-Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
-Figure \@ref(fig:race-pubu-privu) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
-For public universities, exceptions to this finding were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.
-For private universities, Marquette was the only exception to this finding.
-
-INSERT FIGURE \@ref(fig:race-pubu-privu) ABOUT HERE
-
-Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495].
-Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students [@RN4724].
-Therefore, universities may visit predominantly white private high schools in search of non-white students.
-One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.
-
-INSERT FIGURE \@ref(fig:race-pubu-privhs-pubhs) ABOUT HERE
-
-Figure \@ref(fig:race-pubu-privhs-pubhs) compares the racial composition of private high schools visited by public research universities to the racial composition of public high schools visited by these universities.
-Looking at the universe of high schools (top rows of Figure \@ref(fig:race-pubu-privhs-pubhs)), we see that public high schools tend to be more racially diverse than private schools.
-This is reflected in the racial composition of visited schools as well, where the set of visited public high schools generally enroll more Black/Latinx/Native students than the visited private schools for the public research universities in our sample.
-Unfortunately though, a majority of these public universities tended to visit private high schools at a higher rate than public high schools, as seen earlier in Figure \@ref(fig:actual-proportional-pubu).
-This disproportionate emphasis on private school visits may shift the racial composition of public universities away from Black/Latinx/Native students.
-
-## RQ3: Overlapping network structure
-
-Research question 3 asks, "To what extent do public research universities and selective private universities visit overlapping sets of private high schools?" In contrast to RQ1 and RQ2, answering RQ3 requires social network analysis techniques.
-
-Appendix X describes how we constructed social network data.
-Briefly, we began by constructing a two-mode social network of visits to private high schools (mode 1) by universities (mode 2).
-Each university and each private high school is a "vertex." A visit from a university to a school is an "edge." Because large two-mode networks like our school-university network are difficult to visualize, two-mode networks are often analyzed as one-mode networks [@RN2457;@RN4663].
-We transformed our two-mode school-university network into a one-mode university network in which each university is a vertex and two universities share an edge if both universities visited at least one high school in common.
-The *weight* of an edge indicates the number of high schools that both universities visited.
-For example, if there are 200 private high schools that received a visit from both Notre Dame and Villanova, the weight of the edge between Notre Dame and Villanova is 200.
-We created three separate one-mode university networks: a public university network; a private university network; a public and private university network.
-
-We answer research question 3 by: first, analyzing overlap in the recruiting network of public universities (the public university network); second, analyzing overlap in the network of private universities (the private university network); and third, analyzing overlap amongst public and private universities (the public and private university network).
-
-### Public university network
-
-Tables \@ref(tab:pubu-count-matrix) and \@ref(tab:pubu-percent-matrix) provide a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
-Table \@ref(tab:pubu-count-matrix) shows -- for each pair of public universities -- the number of high schools that were visited by both universities.
-For example, column 1 shows that of the 759 different private high schools that the University of Alabama visited, the University of South Carolina visited 284 of these schools and CU-Boulder visited 210 of these schools.
-Table \@ref(tab:pubu-percent-matrix) shows overlap in high schools visited in terms of percent rather than count.
-For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7% of these high schools and CU-Boulder visited 39.1% of these high schools.
-
-INSERT TABLE \@ref(tab:pubu-count-matrix) AND TABLE \@ref(tab:pubu-percent-matrix) ABOUT HERE
-
-One finding from Table \@ref(tab:pubu-percent-matrix) is that the University of Alabama is omnipresent in the set of private high schools visited by most other public research universities in the sample, particularly universities located in the South.
-For the remaining universities, Table \@ref(tab:pubu-percent-matrix) suggests several clusters of universities.
-For example, UMass-Amherst, SUNY Stony Brook, and Rutgers tend to visit many of the same high schools, as do the University of Arkansas and the University of Kansas.
-
-Network graphs are useful for showing which universities have similar private high school recruiting networks.
-Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network.
-Whether graphing one-mode or two-mode networks, network graphs show vertices as circles and edges as lines connecting pairs of vertices.
-In Figure \@ref(fig:plot-1mode-pubu), each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common.
-The width of the line between two universities indicates the number of high schools both universities visited, as identified in Table \@ref(tab:pubu-count-matrix).
-Conceptually, we think of vertices as repelling one another and edges as pulling vertices together [@RN4725].
-Therefore, vertices that share few connections are located apart and those that share many connections are located close together.
-Vertices that are highly connected -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while vertices that are relatively disconnected are located at the periphery of the graph.
-
-INSERT FIGURE \@ref(fig:plot-1mode-pubu) ABOUT HERE
-
-Figure \@ref(fig:plot-1mode-pubu) shows the University of Alabama, University of South Carolina, and CU-Boulder at the center of the recruiting network.
-The University of Nebraska-Lincoln, SUNY Stony Brook, and UC-Riverside are located on the periphery, and the remaining universities are in between.
-Universities that share many direct (i.e., visit many of the same schools) or indirect edges tend to be located close together, for example University of Kansas and University of Arkansas.
-
-To better answer research question 3, we augment the network graphs by using cluster analysis methods -- referred to as "community detection" in the network analysis literature -- to identify groups of universities that share common network structure.
-Broadly speaking, the goal of community detection is to identify "subsets of vertices that demonstrate a ‘cohesiveness’ with respect to the underlying relational patterns" [@RN4725, p.
-59], where a "cohesive subset" means a "subset of vertices that (i) are well connected among themselves, and at the same time (ii) are relatively well separated from the remaining vertices"  [@RN4725, p.
-59].
-In particular, we utilize that "cluster fast and greedy" approach developed by @RN4725, which is a variation of hierarchical cluster analysis that starts with a large number of groups and adds individual vertices to a group when doing so contributes to a cohesive subset.
-
-In Figure \@ref(fig:plot-1mode-pubu), the shape of each university vertex is based on implementing this cluster fast and greedy approach with the specification that the algorithm should identify four groups.
-The largest group consists of eight universities (U.
-Alabama, U.
-Arkansas, U.
-Kansas, Nebraska-Lincoln, U.
-Georgia, U.
-South Carolina, CU-Boulder, U.
-Cincinnati).
-With the exception of CU-Boulder, these universities were located in the South and the Midwest.
-Most of these universities made a relatively high share of visits in the South.
-The next largest cluster -- UMass Amherst, University of Pittsburgh, Rutgers, and SUNY Stony Brook -- consisted of universities that were mostly located in the Northeast and visited a large share of high schools in the Northeast.
-UC-Berkeley and UC-San Diego formed a two-university cluster and UC-Riverside -- which visited fewer private schools than any other public university -- was a cluster unto itself.
-
-### Private university network
-
-Table \@ref(tab:privu-percent-matrix) and Figure \@ref(fig:plot-1mode-privu) show overlap in private high schools visited by the selective private universities in our sample.
-The networks of private universities tend to have more overlap than the network of public research universities (above).
-This is demonstrated tabularly by the higher percentages in Table \@ref(tab:privu-percent-matrix) compared to Table \@ref(tab:pubu-percent-matrix) and graphically by the thicker lines connecting universities in Figure \@ref(fig:plot-1mode-privu) compared to Figure \@ref(fig:plot-1mode-pubu).
-
-INSERT TABLE \@ref(tab:privu-percent-matrix) ABOUT HERE
-
-INSERT FIGURE \@ref(fig:plot-1mode-privu) ABOUT HERE
-
-Whereas applying cluster analysis to public universities (Figure \@ref(fig:plot-1mode-pubu)) yielded three clusters that contained multiple universities, the application of cluster analysis to private universities (Figure \@ref(fig:plot-1mode-privu)) yielded a single cluster that contained 11 universities and three clusters that contained one university each.
-As suggested above, a likely explanation for this difference is that the majority of private universities had substantial overlap in the sets of private high schools visited whereas public universities tended to have substantial overlap with some public universities but not others.
-
-Visually, the most central universities in Figure \@ref(fig:plot-1mode-privu) tended to be universities that visited a large number of schools (number of unique private high schools visited in parentheses): Villanova (563), SMU (550), Notre Dame (625), Northwestern (377), Tulane (430), Boston College (339).
-The periphery of the network included Baylor (237), Stevens Institute (160), Marquette (331), and Case Western (228).
-Baylor visited a higher number of conservative Christian high schools than any other university (see Figure \@ref(fig:religion-pubu-privu)).
-It is notable that Marquette is in the periphery despite visiting a higher number of schools than more centrally located universities (e.g., Emory), suggesting that Marquette visits many schools that are visited by few other private universities in our sample.
-
-The universities located close to one another in Figure \@ref(fig:plot-1mode-privu) tend to share religious affiliation and/or be located in the same geographic region.
-For example, the majority of Catholic universities are located close to one another and the majority of Midwest universities are located close to one another.
-Interestingly, two of the three Christian universities -- TCU and SMU -- are located much closer to the Catholic universities Notre Dame and Northwestern than they are to Baylor, suggesting that Baylor visits a different set of conservative Christian high schools than TCU and SMU.
-
-### Public and private university network
-
-Figure \@ref(fig:plot-1mode-u) shows overlap in private high schools visited amongst all 29 private and public universities in the sample.
-
-The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and characteristics of the schools they visit -- of geographic location, religious affiliation, academic reputation, and also institutional control.
-The cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities that visited a relatively large share of Christian high schools.
-Second, the cluster of 13 universities -- including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley -- largely consists of more highly ranked universities, universities located in the Midwest or West, and Catholic universities.
-Third, the five university cluster -- Rutgers, Stevens Institute of Technology, UMass Amherst, University of Pittsburgh, SUNY Stony Brook -- largely consists of public universities with strong ties to the Northeast.
-
-INSERT FIGURE \@ref(fig:plot-1mode-u) ABOUT HERE
-
-<!--
-
-Tables \@ref(tab:u-cluster1-percent-matrix), \@ref(tab:u-cluster2-percent-matrix), and \@ref(tab:u-cluster3-percent-matrix) show overlap in the percent of private high schools 
-INSERT TABLE \@ref(tab:u-cluster1-percent-matrix) TABLE \@ref(tab:u-cluster2-percent-matrix) AND TABLE \@ref(tab:u-cluster3-percent-matrix) ABOUT HERE
--->
-
-Universities located near the center of Figure \@ref(fig:plot-1mode-u) do not all belong to the same cluster and, more broadly, universities located close to one another do not all belong to the same cluster.
-Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities with the highest degree centrality (i.e., those that visited the most schools).
-The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), Northwestern (377), University of South Carolina (396), and CU-Boulder (362).
-Notably, while the majority of universities located near the center of Figure \@ref(fig:plot-1mode-u) are private, three are public.
-
-Proximity of vertices to one another in Figure \@ref(fig:plot-1mode-u) appeared to be more connected to religious affiliation, geographic location, and academic reputation.
-Universities with a common religious affiliation (e.g., Notre Dame, Villanova, Marquette, Boston College) tend to be close to one another.
-However, the University of Alabama, which visited a high share of Catholic schools and Christian schools is simultaneously close to Catholic universities and to the Christian universities TCU and SMU.
-Similarly, the University of South Carolina, which visited a relatively high share of Christian schools, is close to TCU and SMU.
-CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located close to one another in Figure \@ref(fig:plot-1mode-u).
-These three universities are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit.
-
-Finally, Table \@ref(tab:privu-percent-visited-by-pubu-matrix) shows, for each private university, the percent of schools that were also visited by each public university.
-This table shows the extent to which public universities were competing at private schools targeted by private universities.
-For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.5% of these schools.
-Similarly, CU-Boulder visited 46.4 of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
-The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
-
-INSERT TABLE \@ref(tab:privu-percent-visited-by-pubu-matrix) ABOUT HERE
-
-These analyses of the private and public university network provide the most direct assessment of research question 3.
-Considering the identification of clusters, centrality, and proximity of vertices, we find substantial overlap in the sets of private schools visited by public universities and private universities.
-This overlap does not suggest uniformity across public and private universities.
-Rather, there exist several groups of public and private universities -- which can be defined by cluster analysis or more loosely by proximity -- that have more in common with one another than they do with other universities of the same institutional control.
-
-```{r, eval = FALSE, include = FALSE}
-table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
-table_1mode_pubu$onemode_pct_df %>% glimpse()
-table_1mode_pubu$onemode_pct_df
-
-table_1mode_pubu$onemode_pct_df %>% filter(row.names(table_1mode_pubu$onemode_pct_df) %in% c('CU Boulder'))
-
-table_1mode_pubu$onemode_pct_df %>% attributes()
-
-table_1mode_pubu$onemode_pct_df %>% select(`U of Alabama (N=759)`) %>% str()
-table_1mode_pubu$onemode_pct_df %>% select(`U of Alabama (N=759)`) %>% attributes()
-```
-
-```{r, eval = FALSE, include = FALSE}
-events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count(univ_abbrev) %>% arrange(n)
-
-events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count(univ_abbrev) %>% arrange(n)
-
-237/543*100 # Georgia
-381/1008*100 # CU Boulder
-461/1362*100 # U. South Carolina
-983/3410*100 # U. Alabama
-
-# private
-round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)
-
-# private out of state
-round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)
-
-# public
-round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)
-
-# public, out of state
-round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)
-```
-
-```{r, eval = FALSE, include = FALSE}
-
-events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n)
-
-events_df %>% filter(univ_id == '186867', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()
-
-events_df %>% filter(univ_id == '152080', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()
-
-events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()
-
-# number of visits to private schools by public research universities
-events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n)
-
-round((events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)
-
-events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()/univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()
-
-events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n)
-
-events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()
-```
-
-```{r, eval = FALSE, include = FALSE}
-
-ego_df %>% glimpse()
-
-ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40) %>% count(control)
-
-ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'public') %>% count() %>% as.numeric()
-# percentage of visits that were out-of-state
-
-# private high school visits
-round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)
-
-# public high school visits
-round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric())*100, digits=1)
-
-events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric()
-events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric()
-```
-
-# Discussion
-
-## Summary
-
-This chapter analyzes recruiting visits to private high schools, which were made during the 2017 calendar year, for a convenience sample of 15 public research universities and 14 private universities ranked in the top 100 of U.S.
-News and World Report National Universities rankings.
-Our goal was to learn about public research universities by analyzing their behavior and comparing their behavior to that of selective private universities.
-
-Research question 1 asks about the scale of visits to private high schools.
-All private universities in our sample made a disproportionate number of visits to private high schools (Figure \@ref(fig:actual-proportional-privu)) and, for about half of these universities, visits to private high schools represented about 50% or more of all high school visits.
-For most public research universities in our sample, the scale and relative scale -- as a percentage of all HS visits -- of visits to private high schools were smaller than that of most selective private universities.
-However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \@ref(fig:actual-proportional-pubu)) and that vast majority of these private school visits were to out-of-state private schools.
-Additionally, several public research universities -- University of Alabama, CU-Boulder, University of South Carolina -- visited private high schools at a scale that exceeded most private universities.
-
-Research question 2 asks about the characteristics of visited private high schools.
-We analyzed geographic region, religious affiliation, high school ranking, 12th grade enrollment, and racial composition.
-Both public and private universities in our sample tended to make a disproportionate number of visits in their home geographic region, with highly ranked universities making more visits to schools in other regions.
-The majority of universities -- even those located outside the South --  visited a large number of private schools located in the South.
-Unsurprisingly, sectarian private universities made a large share of visits to private high schools of a similar religious affiliation.
-Given that public universities are nonsectarian organizations, a surprising finding is that the majority of public universities in our sample made a large share of visits to Catholic or Christian private schools.
-
-With the exception of UC-Berkeley and UC-San Diego, the academic rating of private schools visited by public universities was lower than the rating of those visited by most private universities.
-This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked as a top 100 National University by U.S.
-News.
-Nevertheless, the large number of visits to low-rated private schools by public universities, combined with the fact that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private schools primarily in search of full-pay students rather than academic superstars.
-
-Across the universe of private high schools, most schools enroll relatively few students who identify as Black, Latinx, or Native.
-For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools.
-By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.
-
-Research question 3 asks about overlap in the private school recruiting networks of public and private universities.
-Within the sample of public universities, we observed substantial overlap and variation in recruiting networks.
-For example, the recruiting networks of the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass Amherst and Rutgers, which share substantial overlap with one another.
-Across the entire sample of public and private universities, we also observed substantial overlap and variation in recruiting networks.
-Whether we are categorizing universities by cluster analysis or by proximity on the network graph, we observe several different subsets of universities.
-Each of these subsets is associated with a different approach to private school visits and -- with the exception of a few universities like UC-Riverside and SUNY Stony Brook -- each of these subsets contained both public and private universities.
-
-## Privatization of public research universities
-
-These findings contribute new insights about the privatization of public research universities.
-A weakness of the scholarly literature on privatization is that few studies compare public and private universities with respect to a behavior that is associated with private universities [@RN4543].
-We conceptualize recruiting visits to private schools as a behavior that is consistent with the social reproduction orientation of selective private universities and contrary to the historic social mobility mission associated with public research universities.
-Although we cannot make statements about the population of public research universities (ours is a convenience sample rather than a random sample), we can describe variation in how the public universities in our sample went about visiting private schools.
-
-At one end of the continuum lie public research universities that do not play the game, for example UC-Riverside and SUNY Stony Brook, visiting private schools at a lower rate than public schools (Figure \@ref(fig:actual-proportional-pubu)).
-For public universities that visited a substantial number of private schools, we observe substantial variation in the scale of visits and the characteristics of schools they target.
-While all private universities in our sample visited private schools at a much higher rate than public schools, we also see substantial variation amongst private universities in the scale and characteristics of private school visits.
-Amongst the network of public and private universities, Figure \@ref(fig:plot-1mode-u) shows that three clusters emerge -- each containing some mix of public and private universities.
-The universities within a cluster have some overlap in the kinds of schools visited (e.g., TCU and University of South Carolina), but also share substantial overlap with particular universities in different clusters (e.g., Tufts and University of Pittsburgh).
-
-In making large-scale visits to out-of-state private high schools, we argue that public research universities are mimicking the behavior of selective private universities in order to compete for students that have been traditionally targeted by private universities.
-Our rationale for this statement is that selective private universities have been recruiting heavily from private schools for a long time [@RN4642; @RN1565; @RN4407].
-By contrast, the pursuit of out-of-state students is a relatively new phenomenon for most public research universities.
-
-When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
-Several public universities seem to be competing directly for students targeted by a particular private university.
-For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory (Figure \@ref(tab:privu-percent-visited-by-pubu-matrix)).
-We reason UC-Berkeley is competing directly for students because all four universities are in the same broad echelon of prestige.
-Other potential examples of direct competition include the University of Georgia targeting schools visited by Emory, SMU, TCU, and Tulane, or the University of Arkansas targeting schools visited by Baylor.
-
-However, public universities that made the greatest number of private school visits seemed to be targeting lower-achieving students at private schools targeted by particular private universities.
-For example, the University of Alabama visited 52.2% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools.
-Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame.
-Instead, they found a niche by targeting Catholic school students of a similar economic echelon, who have lower academic achievement, and want to attend a football powerhouse.
-Additionally, CU-Boulder visited 42.4% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
-Similarly, the University of South Carolina competes heavily at schools targeted by Emory, SMU, TCU, and Tulane.
-
-Finally, all public universities that visited a substantial number of private schools tended to visit schools that enrolled few Black, Latinx, or Native students.
-This finding is substantially driven by the fact that the national universe of private schools tends to enroll a much lower share of Black, Latinx, or Native students than the universe of public schools.
-However, the set of schools visited by the public universities in our sample enrolled fewer Black, Latinx, and Native students than the universe of private schools.
-Although we do not have data on household income, it is likely that the majority of students are wealthy at the private schools visited by public universities in our sample.
-
-Therefore, while public universities playing the private school game differ in terms of the set of schools they target, they all seem to be targeting schools that enroll mostly affluent students and few students who identify as Black, Latinx, or Native.
-To the extent that these recruiting efforts yield dividends in terms of incoming freshmen, playing the private school game is likely to change the enrollment composition of public research universities in ways that run contrary to racial and socioeconomic diversity.
-
-# References
-
-<div id="refs"></div>
-
-\newpage
-
-# Social network data appendix
-
-A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "network ties" or "edges" between these actors.
-"One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
-"Two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
-Data on recruiting visits by universities to high schools yields a two-mode network, in which an edge -- a recruiting visit -- occurs between a high school (mode 1) and a university (mode 2).
-
-**Constructing two-mode network**.
-We describe construction of social network data with reference to "corporate board-director" networks -- the most commonly analyzed two-mode network -- which consist of directors (mode 1) who serve on organizational boards (mode 2).
-In our school-university two-mode network, the vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visit made between the two (e.g., high school $i$ shares an edge with university $j$ if high school $i$ receives at least one visit from university $j$).
-Visits can only occur between a school-university pair (not a school-school pair or a university-university pair).
-This (weighted) network can be represented as a school-by-university matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 universities) in which matrix cell $a_{i,j}$ identifies the number of visits  high school $i$ received from university $j$.
-<!--[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
-UNWEIGHTED SOMEWHERE]-->
-
-**Transforming two-mode network to one-mode networks**.
-Two-mode networks are often analyzed as one-mode networks [@RN2457].
-@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" (p.
-XXX).
-Thus, a two-mode board-director network can be transformed into two one-mode networks.
-A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ serve on three boards together).
-Similarly, a one-mode board network is created based on a board-by-board matrix in which two boards share an edge if a director sits on both boards and matrix cell $a_{i,j}$ identifies the number of directors that serve on both board $i$ and board $j$.
-
-Following this approach, we create a one-mode high school network in which two private high schools share an edge if they both receive a visit by the same university.
-Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of universities that visited both school $i$ and school $j$<!-- [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
-Similarly, we create a one-mode university network in which two universities share an edge if both universities visited the same high school.
-Cell $c_{i,j}$ of the university-by-university matrix $C$ indicates the number of private high schools that received at least one visit from both university $i$ and university $j$.
-
-The social network analyses presented in this chapter -- particularly for research question 3 -- are primarily based on analysis of one-mode university networks.
-We created separate one-mode university networks for: public universities; private universities; both public and private universities.
-
-<!-- TABLES -->
-
-\newpage
-
-```{r ug-recruit-budget, echo=FALSE}
-pct_budget <- data.frame(
-  activity = c("Travel","Student search (purchased lists)","Prospective student communications","Events","Recruitment publications","Web services and digital advertising","Traditional advertising","International recruitment","Transfer recruitment","Other"),
-  private = c(17,14,13,12,11,11,6,5,4,8),
-  public = c(16,12,17,11,15,13,6,3,4,3)
-)
-
-#pct_budget
-#str(pct_budget)
-#attributes(pct_budget)
-kable(
-  x = pct_budget, 
-  col.names = c("Activity", "Private", "Public"),
-  caption = "Percentage of budget allocated to marketing/recruiting activities by private non-profit 4yr and public 4yr institutions"
-)
-#  <div id="refs"></div>
-```
-
-\clearpage
-
-```{r sample-characteristics}
-univ_sample <- univ_sample_df %>% 
-  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)
-
-kable(univ_sample %>% arrange(desc(classification), rank), caption = "Characteristics of universities in analysis sample") %>%
-  collapse_rows(columns = 1, latex_hline = 'major', valign = 'middle') %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-\clearpage
-
-\begin{landscape}
-
-```{r pubu-count-matrix}
-table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
-
-rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)
-
-kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(c(1), width = '13em') %>% 
-  column_spec(c(14), width = '8.5em') %>% 
-  column_spec(2:13, width = '7em') %>% 
-  column_spec(c(7, 9, 15, 16), width = '6em')
-```
-
-```{r pubu-percent-matrix}
-rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)
-
-kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(c(1), width = '13em') %>% 
-  column_spec(c(14), width = '8.5em') %>% 
-  column_spec(2:13, width = '7em') %>% 
-  column_spec(c(7, 9, 15, 16), width = '6em')
-
-```
-
-\clearpage
-
-```{r privu-count-matrix, eval=FALSE, include=FALSE}
-
-table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
-
-kable(table_1mode_privu$onemode_df, caption = 'Private universities count matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(1, width = '8.5em') %>%
-  column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em')
-```
-
-```{r privu-percent-matrix}
-
-table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
-
-rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)
-
-kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(1, width = '13em') %>%
-  column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
-  column_spec(14:15, width = '8.5em')
-
-```
-
-\clearpage
-
-```{r u-cluster1-percent-matrix, include=FALSE}
-table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
-
-#kable(table_1mode_u$clusters_df[order(match(table_1mode_u$clusters_df$univ_abbrev, rownames(table_1mode_u$onemode_df))), ], caption = 'Clusters for public and private universities')
-
-cluster_1 <- c(1, 4, 5, 7, 16, 18, 19, 24, 25, 28)
-cluster_2 <- c(2, 3, 6, 8, 9, 10, 11, 12, 14, 15, 20, 22, 23)
-cluster_3 <- c(13, 17, 21, 26, 27)
-cluster_4 <- 29
-
-kable(table_1mode_u$onemode_pct_df[cluster_1, cluster_1], caption = 'Public and private universities percent matrix (cluster 1)') %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r u-cluster2-percent-matrix, eval=FALSE}
-kable(table_1mode_u$onemode_pct_df[cluster_2, cluster_2], caption = 'Public and private universities percent matrix (cluster 2)') %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r u-cluster3-percent-matrix, eval=FALSE}
-kable(table_1mode_u$onemode_pct_df[cluster_3, cluster_3], caption = 'Public and private universities percent matrix (cluster 3)') %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r u-top-percent-matrix, eval=FALSE}
-kable(table_1mode_u$onemode_pct_df[c(1,2,3,4,5,6,7,8,9),c(1,2,3,4,5,6,7,8,9)], caption = 'Public and private universities, highest degree centrality') %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r privu-percent-visited-by-pubu-matrix}
-rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
-
-kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  #column_spec(1, width = '8.5em') %>%
-  column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
-  column_spec(14:15, width = '8.5em')
-```
-
-\end{landscape}
-
-\restoregeometry
-
-<!-- FIGURES -->
-
-\clearpage
-
-```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%"}
-knitr::include_graphics('./../assets/images/enrollment_funnel.png')
-#![The enrollment funnel](assets/images/enrollment_funnel.png)
-```
-
-\newpage
-
-```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
-include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
-```
-
-\newpage
-
-```{r events-hs-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
-include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
-```
-
-\newpage
-
-```{r actual-proportional-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
-include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
-```
-
-\clearpage
-
-```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
-include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
-```
-
-\clearpage
-
-```{r region-pubu-privu, echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r religion-pubu-privu, echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school ranking of visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r enroll-pubu-privu, echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r enroll-pubu-privhs-pubhs, echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools vs. public high schools, public research universities"}
-include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privhs_pubhs.pdf'))
-
-```
-
-\newpage
-
-```{r race-pubu-privu, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r race-pubu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools vs.
-public high schools, public research universities"}
-include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
-```
-
-```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
-```
-
-```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private universities, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
-```
-
-```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
-```
-
-```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
-include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
-```
-
-\newpage
-
-```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
-include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
-```
+- I think good to say that private schools make up about 9% of k-12 (or is it primary) enrollment
+The majority of research

### 2023-09-06 r_r/front_end.Rmd
draft changes front end

@@
 
-## Scholarship on Nonresident Enrollment
+## Nonresident Enrollment at Public Universities
 
+We stiuate this study vis-a-vis scholarship on enrollment management behavior by public research universities and particularly the pursuit of affluent nonresident students, a population also targeted by selective private universities.
+The so-called "iron triangle" of enrollment management states that universities pursue the broad enrollment goals of access, academic profile, and revenue generation [@RN3524].
+Historically, public research universities prioritize enrollment of high-performing state residents, often with an emphasis on social mobility for students who cannot afford private universities [@RN3608].
+By contrast, selective private universities typically prioritize academic profile and revenue generation, with funds generated from tuition and donation feeding the arms race for prestige [@RN3522; @RN1549].
+Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve trade-offs with other goals.
+@RN2772[p.
+221] state that “most enrollment management policies\ldots do not advance all three objectives; instead they lead to gains in some areas and declines in others.” In the 2000s, scholarship on privatization argued the public research universities were emphasizing tuition revenue and rankings and de-emphasizing access for state residents [@RN1577; @RN1118].
+<!-- PREVIOUS PARAGRAPH
 We situate this study vis-a-vis scholarship on nonresident enrollment at public research universities, which lies within the broader literature on "privatization" [CITE].
@@
 "Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve tradeoffs with other goals.
-Scholarship on privatization expressed concern that the public research universities were emphasizing tuition revenue and rankings and deemphasizing access for state residents.
+Scholarship on privatization expressed concern that the public research universities were emphasizing tuition revenue and rankings and deemphasizing access for state residents.-->
 
@@
 One mechanism is financial aid.
-@RN2535 shows that nonresident students are less sensitive to sticker price than resident students.
+Many public research universities have developed institutional aid policies for nonresident admits, typically offering larger awards for higher achieving students [@RN3762; @RN2287; @RN1791].<!--@RN2535 shows that nonresident students are less sensitive to sticker price than resident students.
 Because nonresident prospects may be considering several options -- in-state, out-of-state, public, private -- they are sensitive to the generosity of institutional aid offers [CITE].
@@
 These results suggest that high-achieving nonresident students face many good opportunities and require substantial institutional aid to be convinced to enroll.
+-->
 
@@
 One widely utilized intervention is off-campus recruiting visits by admissions counselors to local high schools.
-@RN3519 found that colleges value this visits as a means of meeting prospective students and maintaining relationships with guidance counselors at feeder schools.
-@RN4758 analyzed off-campus recruiting visits by 15 public research universities, finding that 12 of these universities made more visits to out-of-state
-high schools than in-state high schools.
+@RN4758 analyzed off-campus recruiting visits to public high schools by 15 public research universities.
+Recruiting visits to in-state high schools tended exhibit modest racial and socioeconomic bias.
+However, 12 of the 15 universities made more visits to out-of-state high schools than in-state high schools.
 These out-of-state visits focused on public schools in affluent, predominantly white communities.
-Although @RN4758 focused on visits to public high schools, they noted a surprising number of visits to out-of-state private high schools.
-However, we know little about this private school visits, for example, which sorts of schools are they visiting and at what scale.
+@RN4934 conducted geo-spatial analyses of out-of-state recruiting visits to Los Angeles and Dallas by four public research universities.
+She found that universities engage in "recruitment redlining -- the circuitous avoidance of predominantly Black and Latinx communities along recruiting visit paths" (p.
+X).
+Although @RN4758 and @RN4934 focused on visits to public high schools, they noted a surprising number of visits to out-of-state private high schools.
+<!-- However, we know little about this private school visits, for example, which sorts of schools are they visiting and at what scale. -->
 
-## Scholarship on Linkages Between Private Schools and Colleges
+## Linkages Between Private Schools and Private Universities
 
-A separate thread of scholarship analyzes linkages between private schools and colleges. Nationwide, dddd
+Disconnected from scholarship on nonresident enrollment at public universities, scholarship from economics and sociology analyzes linkages between private schools and colleges.
 
-TEXT YOU WROTE ABOUT MURNANE AND REARDON
-In particular, Murnane & Reardon (2018) used data from several national surveys to analyze long-term trends in private school enrollment by family income.
-The percentage of American (elementary school) students attending private school declined from 15% in the With respect to family income, the private school enrollment rate of high-income families (around 17%) and low-income families (around 4%) remained stable over time, but the enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
-These declines were substantially driven by declines in the number of students attending Catholic
-schools, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
-Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
+@RN4504<!-- use data from several national surveys to --> set the stage by analyzing long-term trends in private school enrollment.
+The percentage of American (elementary school) students attending private school declined from 15% in the mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
+With respect to family income, the private school enrollment rate of high-income families (around 17%) and low-income families (around 4%) remained stable over time, but the enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
+These declines were substantially driven by declines in the number of students attending Catholic schools, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
+However, as Catholic school enrollment has declined, Catholic school students tend to be more affluent than they were in prior decades.
+In the South, there has been a long-term increase in private school enrollment, driven by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsectarian private schools by high-income families.
 With respect to race, in 2013, 11% of white students attended private school compared to 5% of Black students, and 3% of Hispanic students.
-However, for high income families, rates of private school enrollment do not differ substantially across race.
-In the South, there has been a long-term increase in private school enrollment, driven
-by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsectarian private schools by high-income families.
-mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
+<!-- Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
+ However, for high income families, rates of private school enrollment do not differ substantially across race. -->
 
-- I think good to say that private schools make up about 9% of k-12 (or is it primary) enrollment
-The majority of research
+A robust empirical literature<!-- from sociology and economics  --> finds that attending private school positively affects college access and college selectivity [e.g.,] [@RN4642; @RN4596; @RN4634; @RN4599].
+Scholarship in the 1990s often focused on the effects of attending Catholic schools [@RN4937; @RN786; @RN4936; @RN4938; @RN4939].
+This is because Catholic schools enrolled the majority of private school students and because Catholic school students tended to be less affluent than those at other private schools.
+<!-- More recent scholarship tends to find that attending a nonsectarian private school has a larger effect on college access outcomes compared to Catholic schools [@RN4614;@RN4625].
+--> DESCRIPTIVE STATISTICS FROM HSLS ABOUT PRIVATE SCHOOLS AND SELECTIVE PRIVATE SCHOOLS.
+
+Scholarship has been particularly interested in the relationship between attending an elite private school and attending an elite private college [@RN4647; @RN4643; @RN4647; @RN4589].
+@RN4722 acquired unprecedented data -- application files and admissions decisions linked to income tax records  -- to investigate why high income families are over-represented at "Ivy Plus" colleges.
+Conditioning on SAT and ACT scores, applications from high-income families (top 1%) received the same academic rating as applications from lower-income families.
+However, applications from high-income families tended to receive higher non-academic ratings (extracurricular activities, leadership traits) then applications from lower-income families.
+In turn, the higher non-academic ratings for high-income applicants was driven by the fact that these students tended to attend elite private high schools that devote substantial resources to teacher recommendations and guidance counselor letters.
+
+Scholarship from sociology has examined organizational connections that catalyze the flow of students between private schools and selective private colleges [@RN4640; @RN4407; @RN4321; @RN3519].
+
+@RN3519 provides an ethnography of the admissions office at a highly selective (but not elite) private liberal arts college.
+The College is sensitive about its position in U.S.
+News Rankings and enrollment priorities tend to focus on academic profile and revenue generation.
+@RN3519 highlights the relational function of off-campus recruiting visits, stating that "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide" (p.
+54) Therefore, during the autumn "travel season," admissions officers visit selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
+53-54).
+The logic is that a guidance counselor who views a college favorably will steer students to the college.
+The College tended to visit the same "feeder" schools year after year because recruiting depends on long-term relationships with high schools.
+The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and have the resources and motivation to host a successful visit.
+<!-- Whereas @RN4402 highlights the effect of recruiting visits on inquiries and enrollees, findings from @RN3519 suggest that the College may have valued recruiting visits primarily as a means of maintaining relationships with guidance counselors.
+From this perspective, recruiting visits may affect outcomes such as inquiries, applications, and matriculation through their effect on high school guidance counselors.
+-->
+
+@RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p.
+98).
+Guidance counselors at elite private schools capitalize on the fact that college admissions offices value credible information about which applicants will accept or decline an admissions offer because colleges are sensitive to their acceptance and yield rates.
+This desire for credible intelligence creates an opportunity for high school counselors to advocate on behalf of their students.
+This opportunity depends on guidance counselors having personal relationships with university admissions offices and on having small enough caseloads to advocate for each student individually.
+Guidance counselors tell admissions counselors which highly-sought-after applicants are likely to decline an offer, while lobbying for an applicant who relatively weak academic credentials, but has "character," and extracurricular activities the college needs, and who is sure to matriculate.
+
+## Synthesis
+
+Our review of two literatures -- scholarship on nonresident enrollment by public research universities and scholarship on linkages between private schools and private colleges -- suggests an opportunity to bridge and contribute to both literatures.
+
+Historically, public universities received most of their revenue from state funding and enrollment goals prioritized opportunities for in-state students.
+As state funding became uncertain, public research universities began to prioritize tuition revenue and sought affluent, out-of-state students who paid high nonresident tuition price.
+Salazar et al shows that recruiting visits by public research universities out-of-state public schools in affluent, predominantly white communities.
+Resource dependence theory suggests that as public research universities become more tuition reliant, they will start behaving more like selective private universities in targeting private schools which tend to enroll affluent students that can to pay high tuition prices.
+However, prior research has not investigated visits to private schools.
+For example, which sorts of private schools are public research universities visiting and at what scale?
+
+The majority of scholarship on linkages between private high schools and private universities focuses on elite high schools and elite universities [CITE].
+We know much less about linkages between private schools and private universities that are selective but not elite.
+These universities are sensitive about their reputation.
+Despite being relatively affluent, they are much more resource constrained than Ivy Plus.
+Thus, they cannot pursue all enrollment goals with equal vigor.
+Prior research shows that selective but not elite colleges prioritize academic profile (as defined by US News Rankings) and tuition revenue, potentially at the expense of access.
+Many private high schools enroll students that satisfy both enrollment goals.
+However, prior scholarship provides little insight about which private schools have relationships with selective private universities.
+
+We argue that a recruiting visit from a university to a private high school is an indicator of a relationship.
+Empirically, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
+Logically, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school.
+Similarly, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
+Moreover, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls) between the organizations.
+Conceptualizing a recruiting visit as an indicator of a relationship between a college and a high school motivates the use of social network methods, which analyze the network defined by "network ties" (i.e., visits) between actors (universities and schools).
+
+Because nonresident enrollment is a relatively new phenomenon for most public research universities [CITE], visits to out-of-state private schools are encroachments on territory that was previously the domain of selective private universities and in-state public flagships.
+These visits suggest that public research universities are competing with selective private universities for private school students.
+This may be direct competition for the same student or vying to be the second choice for students who are rejected by their top choice.
+By analyzing the network of recruiting visits, we can determine the extent to which public research universities are visiting the same or similar sets of private high schools.
+These analyses provide a novel lens into the nature of competition between public research universities and selective private universities.
+They also yield insight about which student bodies these universities want to enroll.

### 2023-09-06 r_r/front_end.Rmd
draft

@@
 
-BLAH BLAH BLAH
+PX-PX: vignette of visits to a private high school.
+
+Theories of organizational behavior suggest that university recruiting behaviors -- those that require significant resource expenditure -- are indicators of organizational enrollment priorities.
+Large, complex organizations consist of several "technical levels" responsible for processing inputs and producing outputs and "managerial levels" responsible for directing the technical level and tending to demands from the external environment [@RN531; @RN959].
+The technical level cannot pursue multiple goals efficiently.
+Thus, organizations respond to external pressue to pursue multiple, competing goals goals by symbolically adopting some goals and substantively adopting others [@RN513].
+Under symbolic adoption, organizations adopt policies and structures that send signals to external constituents but do not affect resource allocation in the technical level.
+Under substantive adoption, organizations direct resources in the technical level towards achieving the goal.
+Off-campus recruiting visits by admissions officers to local high schools and college fairs was the top-ranked recruiting expenditure item for both public and private universities, according to @RN4664.
+Therefore, analyses of which schools a university visits -- and which schools they ignore -- can yield insights about university enrollment goals.
+
+@RN4758 analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
+the authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools.
+These out-of-state visits focused on affluent, predominantly white public schools.
+Set against the scholarship about declining state appropriations and growing nonresident enrollment [@RN3753; @RN3685], these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition price.
+
+A multidisciplinary literature on social stratification has analyzed relationship between private high schools and universities [CITE].
+This research observes strong linkages -- and flows of students -- between private high schools and selective private universities [CITE].
+To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on linkages between private schools and private universities.
+We argue that these two stories are connected because public research universities are increasingly targeting out-of-state private schools, which have historically been the domain of selective private universities.
+
+<!-- 
+This study compares recruiting visits to private high schools by public research universities and recruiting visits to private high schools by selective private universities. 
+We argue that recruiting visits are an indicator of enrollment goals -- the university wants to enroll some students from the school, the school wants some students to enroll at the university. 
+-->
+This study analyzes recruiting visits to private high schools made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
+@RN3519 finds that travel to local high schools is vital for maintaining relationships with guidance counselors at "feeder schools." We conceptualize recruiting visits as an indication the university and the school have a social relationship.
+This conceptualization motivates the use of social network methods, which analyze networks defined by "network ties" (i.e., visits) between actors (universities and schools).
+Comparing the recruiting networks of public researc universities and selective private universities yields novel insights about competition for students at schools that enroll affluent, "full-pay" students.
+Analyses are informed by three research questions:
+
+1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
+1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
+
+Both private and public universities in our sample made a disproportionate number of visits to private high schools.
+For public research universities, visited private schools were much more likely to be out-of-state than visited public schools.
+Although universities visited a large number of private schools in their home region, most universities also visited a large number of private schools in the South.
+Private schools that received visits were predominantly white.
+Although partially a function of our analysis sample, public universities tended to visit lower ranked private high schools than private universities.
+Surprisingly, several public universities visited sectarian private high schools at a rate similar to sectarian private universities.
+Network analyses revealed substantial overlap in the recruiting networks of public and private research universities.
+
+This manuscript is practically important because it provides insight about which schools universities view as "feeder schools" and -- to a limited extent -- the characteristics of students they want to enroll.
+Prior research finds that university recruiting efforts affect the enrollment decisions of students [CITE].
+In turn, the composition of enrolled students affects the campus culture experienced by students.
+Scholarship and the popular press reports that underrepresented minority students and low-income students at public flagship universities feel isolated amidst affluent, predominantly white student bodies.
+Racial and socioeconomic isolation negatively affects student development outcomes for isolated students and for the entire student body [CITE].
+State policymakers and institutional leaders should recognize that the enrollment composition at public research universities is not the consequence of exogenous student demand, but rather the consequence of recruiting efforts that seek to grow nonresident enrollment by systematically targeting affluent, predominantly white public high schools [@RN4758] and affluent, predominantly white private high schools.
+[NOTE: THESE IMPLICATIONS HAVE TO DO ABOUT TARGETING PRIVATE SCHOOLS BUT NOT TARGETING SAME SET OF SCHOOLS TARGETED BY SELECTIVE PRIVATE UNIVERSITIES]
+
+[PUT THIS IN THE DISCUSSION SECTION] Finally When both private and public universities are targeting private schools, competition for these students is likely to increase.
+This could be an explanation for why many private universities are struggling to meet enrollment goals
+
+student bodies that predonominantly affluent, white student bodies.
 

### 2023-09-11 r_r/front_end.Rmd
private hs data

@@
 
+\pagenumbering{roman}
 \newpage
+\pagenumbering{gobble}
+\pagenumbering{arabic}
 
@@
 
-PX-PX: vignette of visits to a private high school.
+Autumn is college visit season at Harpeth Hall, a non-sectarian private school for girls in Nashville, TN, founded in 1951.
+According to the 2020 *Best Private High Schools in America* by Niche, Harpeth is an "A+" school ranked 337 in the nation.
+Enrollment growth at Harpeth and the Nashville-area private school market mirror broader regional patterns, whereby “efforts by the courts to desegregate public schools in the South resulted in White flight to private schools” [@RN4504, p.
+14].
+In Fall 2017, about 85% of Harpeth students were white and less than 5% were Black or Latinx (Author calculations).
 
-Theories of organizational behavior suggest that university recruiting behaviors -- those that require significant resource expenditure -- are indicators of organizational enrollment priorities.
-Large, complex organizations consist of several "technical levels" responsible for processing inputs and producing outputs and "managerial levels" responsible for directing the technical level and tending to demands from the external environment [@RN531; @RN959].
-The technical level cannot pursue multiple goals efficiently.
-Thus, organizations respond to external pressue to pursue multiple, competing goals goals by symbolically adopting some goals and substantively adopting others [@RN513].
-Under symbolic adoption, organizations adopt policies and structures that send signals to external constituents but do not affect resource allocation in the technical level.
-Under substantive adoption, organizations direct resources in the technical level towards achieving the goal.
-Off-campus recruiting visits by admissions officers to local high schools and college fairs was the top-ranked recruiting expenditure item for both public and private universities, according to @RN4664.
+During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[NAME THE UNIVERSITIES].
+We are still trying to figure out what happened.
+
+From September 6th through October 17th, Harpeth received recruiting visits from 11 private universities (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denvor, Emory, Tulane, Baylor, Texas Christian University), and three private liberal arts colleges from our sample (Harvey Mudd, Scrips, and Sewanee, which visited twice).
+Harpeth also received visits from the University of Cincinatti, University of South Carolina, the University of Alabama, University of Arkansa, University of Georgia, and CU Boulder.
+
+Four miles northeast of Harpeth, next to Vanderbilt University, is the University School of Nashville.
+The University School is a nonsectarian, "A+" school, ranked 127th in the nation, and is more racially diverse than Harpeth (64% white, 11.5% Black, 3.5% Latinx, 10.0% Asian).
+From September 11th 2017 through October 18th, The University School received visits from the same 11 private universities that visited Harpeth (except Notre Dame visited and Baylor did not), five liberal arts colleges (Williams, Middlebury, Sewaneee, Scripps, and Harvey Mudd), but only two public research universities (University of Cincinatti, and CU Boulder).
+Four miles south of The University School lies Father Ryan High School, a predominantly white (86%, 7% Black or Latinx) Catholic school that received an "A" grade by Niche.
+In fall 2017, Father Ryan received visits from nine of the 14 private universities in our sample (including all the Catholic universities), just one liberal arts college (Sewanee), and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama.
+
+Theories of organizational behavior suggest that university recruiting behaviors -- those that require significant expenditure -- are indicators of organizational enrollment priorities.
+Large, public-facing organizations are beset by multiple, competing pressures from the external environment, but organizations have difficulty pursuing multiple goals [@RN531; @RN959].
+Thus, organizations respond by symbolically adopting some goals and substantively adopting others [@RN513].
+Under symbolic adoption, organizations adopt policies and structures that send signals to external constituents but do not substantively affect resource allocation inside the the "technical level" of the organization.^[Contingency theory states that organizations consist of "technical levels" responsible for processing inputs and producing outputs and "managerial levels" responsible for directing the technical level and tending to demands from the external environment [@RN531].
+The technical level achieves effectiveness by focusing on a small, stable set of goals.] Under substantive adoption, organizations direct resources in the technical level towards achieving the goal.
+Off-campus recruiting visits to local high schools and college fairs was the top-ranked recruiting expenditure item for both public and private universities, according to @RN4664.
 Therefore, analyses of which schools a university visits -- and which schools they ignore -- can yield insights about university enrollment goals.
@@
 
-A multidisciplinary literature on social stratification has analyzed relationship between private high schools and universities [CITE].
-This research observes strong linkages -- and flows of students -- between private high schools and selective private universities [CITE].
-To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on linkages between private schools and private universities.
-We argue that these two stories are connected because public research universities are increasingly targeting out-of-state private schools, which have historically been the domain of selective private universities.
+Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college [CITE].
+This research observes strong links -- and student flows -- between private high schools and selective private universities [CITE].
+To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between between private school and college.
+We argue that these two stories have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities.
 
@@
 This conceptualization motivates the use of social network methods, which analyze networks defined by "network ties" (i.e., visits) between actors (universities and schools).
-Comparing the recruiting networks of public researc universities and selective private universities yields novel insights about competition for students at schools that enroll affluent, "full-pay" students.
+Comparing the recruiting networks of public research universities and selective private universities yields novel insights about competition for students at schools that enroll affluent, "full-pay" students.
 Analyses are informed by three research questions:

### 2023-09-11 scripts/create_igraph_objects.R

@@ -230,6 +230,8 @@ privhs_df <- privhs_data %>% left_join(dplyr::union(
   ) %>%
   mutate(type = 'priv hs', control = 'private')
 
+# Save dataframes
+saveRDS(privhs_df, file = str_c('./data/privhs_universe.RDS'))
 
 # All NA/unmerged Niche data were checked and manually added if available. There are 33 known true NA's
 table((privhs_df %>% filter(ncessch %in% privhs_events$school_id))$overall_niche_letter_grade, useNA = 'always')

### 2023-09-11 scripts/network_recruiting_analysis.R

@@ -935,7 +935,6 @@ create_2mode_table <- function(twomode_network, race_var = 'pct_blacklatinxnativ
 }
 
 # Save tables
-# twomode_both <- create_2mode_table(g_2mode)
 # saveRDS(twomode_both$full_table, file = './assets/tables/table_2mode_both.RDS')
 # saveRDS(twomode_both$agg_table, file = './assets/tables/table_2mode_agg_both.RDS')
 # 

### 2023-09-11 scripts/vignette_lede_rihe.R

@@ -1,0 +1,90 @@
+library(igraph)
+library(tidyverse)
+
+options(max.print = 2000)
+
+
+# CODE TO RUN FIRST
+
+  # create_igraph_objects up through line 539, which creates the object g_2mode
+  # network_recruiting_analysis
+    # you might need to run lines 1 through 81 to create objects for categorical variables
+    # lines 891 through 935; creates two functions, including the function create_2mode_table
+
+  twomode_both <- create_2mode_table(g_2mode)
+  twomode_both[[1]] %>% str() # data frame
+
+  pick_schools_df <- twomode_both[[1]]
+  pick_schools_df %>% glimpse()
+  
+  pick_schools_df %>% filter(city == "DALLAS")
+  
+  pick_schools_df %>% filter(state_code == "TN")  %>% arrange(city,-degree)
+  
+  pick_schools_df %>% filter(state_code == "MO")
+  
+  
+  pick_schools_df %>% filter(state_code == "TX") %>% arrange(city,-degree)
+  
+#             name                                  school_name           city state_code region     religion pct_blacklatinxnative  ranking ranking_numeric degree closeness strength  
+#01296378 01296378                          HARPETH HALL SCHOOL      NASHVILLE         TN  south nonsectarian              5.660377       A+             337     21 0.4192007       24
+#A9300845 A9300845                      MONTGOMERY BELL ACADEMY      NASHVILLE         TN  south nonsectarian              8.984375       A+             260     20 0.3968744       25
+#01296764 01296764               UNIVERSITY SCHOOL OF NASHVILLE      NASHVILLE         TN  south nonsectarian             15.023474       A+             127     18 0.3845388       19
+#01294971 01294971                      FATHER RYAN HIGH SCHOOL      NASHVILLE         TN  south     catholic              7.768053        A              NA     15 0.4061448       18
+#01932509 01932509                           ST CECILIA ACADEMY      NASHVILLE         TN  south     catholic             20.077220        A              NA     15 0.4148753       16
+#02163165 02163165                        FRANKLIN ROAD ACADEMY      NASHVILLE         TN  south    christian             10.405405        A              NA     13 0.4007475       15
[…]

### 2023-09-28 r_r/front_end.Rmd
revising vignette lede

@@
 
+<!-- 
 Few empirical analyses of privatization compare public and private universities on a behavior associated with private universities.
@@
 With respect to overlap (RQ3), descriptive statistics and community detection methods revealed substantial overlap in the recruiting networks of public and private universities.
+-->
 
@@
 
-Autumn is college visit season at Harpeth Hall, a non-sectarian private school for girls in Nashville, TN, founded in 1951.
-According to the 2020 *Best Private High Schools in America* by Niche, Harpeth is an "A+" school ranked 337 in the nation.
-Enrollment growth at Harpeth and the Nashville-area private school market mirror broader regional patterns, whereby “efforts by the courts to desegregate public schools in the South resulted in White flight to private schools” [@RN4504, p.
+*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[NAME THE UNIVERSITIES] We are still trying to figure out what happened.*
+\bigskip
+
+Autumn is college recruiting visit season at Harpeth Hall, a non-sectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
+Founded in 1951, Harpeth is an "A+" school ranked 337 in the nation according to the 2020 *Best Private High Schools in America* by Niche.
+Enrollment patterns at Nashville-area private schools reflect broader regional patterns, whereby “efforts by the courts to desegregate public schools in the South resulted in White flight to private schools” [@RN4504, p.
 14].
@@
 
-During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[NAME THE UNIVERSITIES].
-We are still trying to figure out what happened.
+From September 6th through October 17th, Harpeth received recruiting visits from 11 private universitiesin our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denvor, Emory, Tulane, Baylor, Texas Christian University), and three private liberal arts colleges (Harvey Mudd, Scrips, and Sewanee).
+Previous scholarship observes strong connections between private schools and selective private universities [@RN3519; @RN4407].
+However, Harpeth also received visits from six out-of-state public research universities, the University of Cincinatti, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.
 
-From September 6th through October 17th, Harpeth received recruiting visits from 11 private universities (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denvor, Emory, Tulane, Baylor, Texas Christian University), and three private liberal arts colleges from our sample (Harvey Mudd, Scrips, and Sewanee, which visited twice).
-Harpeth also received visits from the University of Cincinatti, University of South Carolina, the University of Alabama, University of Arkansa, University of Georgia, and CU Boulder.
+The nonsectarian University School of Nashville was founded in 1975 and is located next door to Vanderbilt University.
+It is an "A+" school, ranked 127th in the nation, and is more racially diverse than Harpeth (64% white, 11.5% Black, 3.5% Latinx, 10.0% Asian).
+From September 11th 2017 through October 18th, the University School received visits from nearly the same set of 11 private universities that visited Harpeth (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinatti, CU Boulder).
 
-Four miles northeast of Harpeth, next to Vanderbilt University, is the University School of Nashville.
-The University School is a nonsectarian, "A+" school, ranked 127th in the nation, and is more racially diverse than Harpeth (64% white, 11.5% Black, 3.5% Latinx, 10.0% Asian).
-From September 11th 2017 through October 18th, The University School received visits from the same 11 private universities that visited Harpeth (except Notre Dame visited and Baylor did not), five liberal arts colleges (Williams, Middlebury, Sewaneee, Scripps, and Harvey Mudd), but only two public research universities (University of Cincinatti, and CU Boulder).
-Four miles south of The University School lies Father Ryan High School, a predominantly white (86%, 7% Black or Latinx) Catholic school that received an "A" grade by Niche.
-In fall 2017, Father Ryan received visits from nine of the 14 private universities in our sample (including all the Catholic universities), just one liberal arts college (Sewanee), and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama.
+Father Ryan High School is a Catholic school founded in 1925.
+Father Ryan is predominantly white (86%, 7% Black or Latinx) and received an "A" grade from Niche, meaning it is not ranked in the top 1,000 US private schools.
+In fall 2017, Father Ryan received visits from nine of the 14 private universities in our sample (including all the Catholic universities) and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama.
+Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from five private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University).
+It also received visits from the University of Cincinatti, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder.
+Christ Presbyterian Academy was founded in 1985 and 94% of its students are white.
 
@@
 -->
+
 This study analyzes recruiting visits to private high schools made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
-@RN3519 finds that travel to local high schools is vital for maintaining relationships with guidance counselors at "feeder schools." We conceptualize recruiting visits as an indication the university and the school have a social relationship.
+<!-- @RN3519 finds that travel to local high schools is vital for maintaining relationships with guidance counselors at "feeder schools."--> We conceptualize recruiting visits as an indication the university and the school have a social relationship.
 This conceptualization motivates the use of social network methods, which analyze networks defined by "network ties" (i.e., visits) between actors (universities and schools).
-Comparing the recruiting networks of public research universities and selective private universities yields novel insights about competition for students at schools that enroll affluent, "full-pay" students.
+Comparing the recruiting networks of public research universities and selective private universities yields novel insights about the competition for affluent, "full-pay" students.
 Analyses are informed by three research questions:
@@
 1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
+
+[KARINA STOP READING HERE]
 
@@
 We stiuate this study vis-a-vis scholarship on enrollment management behavior by public research universities and particularly the pursuit of affluent nonresident students, a population also targeted by selective private universities.
-The so-called "iron triangle" of enrollment management states that universities pursue the broad enrollment goals of access, academic profile, and revenue generation [@RN3524].
-Historically, public research universities prioritize enrollment of high-performing state residents, often with an emphasis on social mobility for students who cannot afford private universities [@RN3608].
-By contrast, selective private universities typically prioritize academic profile and revenue generation, with funds generated from tuition and donation feeding the arms race for prestige [@RN3522; @RN1549].
+The so-called "iron triangle" of enrollment management states that universities pursue the broad enrollment goals of access, academic profile, and revenue generation [@RN3524; @RN2772].
 Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve trade-offs with other goals.
 @RN2772[p.
-221] state that “most enrollment management policies\ldots do not advance all three objectives; instead they lead to gains in some areas and declines in others.” In the 2000s, scholarship on privatization argued the public research universities were emphasizing tuition revenue and rankings and de-emphasizing access for state residents [@RN1577; @RN1118].
+221] state that “most enrollment management policies\ldots do not advance all three objectives; instead they lead to gains in some areas and declines in others.” Scholarship argues that selective private universities prioritize academic profile and revenue generation, with funds generated from tuition and donation feeding the arms race for prestige [@RN3522; @RN1549; @RN3519].
+Historically, public research universities prioritize enrollment of high-performing state residents, often with an emphasis on social mobility for students who cannot afford private universities [@RN3608].
+However, scholarship on privatization argues the public research universities increasingly emphasizing tuition revenue and rankings and de-emphasize access for state residents [@RN1577; @RN1118].
+
 <!-- PREVIOUS PARAGRAPH
@@
 
-How did public research universities go about attracting all these nonresident students.
-One mechanism is financial aid.
+How did public research universities go about attracting all these nonresident students?
+One mechanism is financial aid, a lever to increase applications and affect matriculation decisions.
 Many public research universities have developed institutional aid policies for nonresident admits, typically offering larger awards for higher achieving students [@RN3762; @RN2287; @RN1791].<!--@RN2535 shows that nonresident students are less sensitive to sticker price than resident students.
@@
 
-Disconnected from scholarship on nonresident enrollment at public universities, scholarship from economics and sociology analyzes linkages between private schools and colleges.
+Separate from scholarship on nonresident enrollment at public universities, scholarship from economics and sociology analyzes linkages between private schools and colleges.
 
-@RN4504<!-- use data from several national surveys to --> set the stage by analyzing long-term trends in private school enrollment.
+@RN4504<!-- use data from several national surveys to --> set the stage by describing long-term trends in private school enrollment.
 The percentage of American (elementary school) students attending private school declined from 15% in the mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
-With respect to family income, the private school enrollment rate of high-income families (around 17%) and low-income families (around 4%) remained stable over time, but the enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
-These declines were substantially driven by declines in the number of students attending Catholic schools, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
-However, as Catholic school enrollment has declined, Catholic school students tend to be more affluent than they were in prior decades.
-In the South, there has been a long-term increase in private school enrollment, driven by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsectarian private schools by high-income families.
-With respect to race, in 2013, 11% of white students attended private school compared to 5% of Black students, and 3% of Hispanic students.
+The private school enrollment rate for high-income families and for low-income families has remained relatively stable over time at about 17% and 4%, respectively.
+The enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
+This decline was driven by shrinking Catholic school enrollment, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
+Morevoer, contemporary Catholic school students tend to be more affluent compared to prior decades.
+There has been a long-term increase in private school enrollment in the South, with middle-income families increasingly attending Christian schools and high-income families increasingly attending nonsectarian schools.
+With respect to race, 11% of white students attended private school in 2013, compared to 5% of Black students, and 3% of Hispanic students.
 <!-- Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
@@
 A robust empirical literature<!-- from sociology and economics  --> finds that attending private school positively affects college access and college selectivity [e.g.,] [@RN4642; @RN4596; @RN4634; @RN4599].
-Scholarship in the 1990s often focused on the effects of attending Catholic schools [@RN4937; @RN786; @RN4936; @RN4938; @RN4939].
-This is because Catholic schools enrolled the majority of private school students and because Catholic school students tended to be less affluent than those at other private schools.
-<!-- More recent scholarship tends to find that attending a nonsectarian private school has a larger effect on college access outcomes compared to Catholic schools [@RN4614;@RN4625].
---> DESCRIPTIVE STATISTICS FROM HSLS ABOUT PRIVATE SCHOOLS AND SELECTIVE PRIVATE SCHOOLS.
+Scholarship from the 1980s and 1990s focused on the effects of attending Catholic school [@RN4937; @RN786; @RN4936; @RN4938].
+More recent scholarship tends to find that attending a nonsectarian private school has larger effects on college access than attending a Catholic school [@RN4935; @RN4614;@RN4625].
 
-Scholarship has been particularly interested in the relationship between attending an elite private school and attending an elite private college [@RN4647; @RN4643; @RN4647; @RN4589].
-@RN4722 acquired unprecedented data -- application files and admissions decisions linked to income tax records  -- to investigate why high income families are over-represented at "Ivy Plus" colleges.
+The High School Longitudinal Survey of 2009 (HSLS) tracks the postsecondary destinations of students who were in ninth grade in 2009.
+Simple descriptive statistics are eye-opening (Author calculations).^[Analyses consist students who met the following conditions: completed the 2012 follow-up survey; obtained high school transcript data; and completed the 2016 followup survey.
+The survey weight variable used was W4W1W2W3STU.
+After weighting, these 14,020 (unweighted) students represent a population of 3.93 million U.S.
+ninth graders in 2009.
+Data on college rankings come from the 2020 U.S.
+News \& World Report *Best Colleges*.
+Data on high school control come from the HSLS school file and from the Private School Survey.] About 93% of students attended a public high school and 7% attended a private high school, including 3.6% attending a Catholic school, 1.6% attending a nonsectarian school, and 1.8% attending a Christian school.
+Of public high school students, 5.0% attending a public university ranked in the top 100 by US News and World Report (USNWR) and 1.9% attended a private university ranked in the top 100.
+Of private high school students, 10.9% attended a top 100 public university and 16.8% attended a top 100 private university.
+For Catholic school students, 12.8% attended a top 100 public university and 11.7% attended a top 100 private university, while for Christian schools these percentages were 8.2% and 8.2%, respectively.
+However, for nonsectarian private school students, 11.3% attended a top 100 public university and 39.8 percent attended a top 100 private university.
+Focusing on the institutional composition of private universities in USNWR top 100, 39.8% attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).
+
+Scholarship has been particularly interested in the relationship between attending a prestigious private school and attending an ultra selective university [@RN4647; @RN4643; @RN4647; @RN4589].
+@RN4935 acquired unprecedented data -- application files and admissions decisions linked to income tax records  -- to investigate why high income families are over-represented at "Ivy Plus" colleges.
 Conditioning on SAT and ACT scores, applications from high-income families (top 1%) received the same academic rating as applications from lower-income families.
-However, applications from high-income families tended to receive higher non-academic ratings (extracurricular activities, leadership traits) then applications from lower-income families.
+However, applications from high-income families received higher non-academic ratings (extracurricular activities, leadership traits) then applications from lower-income families.
 In turn, the higher non-academic ratings for high-income applicants was driven by the fact that these students tended to attend elite private high schools that devote substantial resources to teacher recommendations and guidance counselor letters.
@@
 Scholarship from sociology has examined organizational connections that catalyze the flow of students between private schools and selective private colleges [@RN4640; @RN4407; @RN4321; @RN3519].
-
-@RN3519 provides an ethnography of the admissions office at a highly selective (but not elite) private liberal arts college.
+@RN3519 provides an ethnography of the admissions office at a selective private liberal arts college.
 The College is sensitive about its position in U.S.
@@
 54) Therefore, during the autumn "travel season," admissions officers visit selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
-53-54).
-The logic is that a guidance counselor who views a college favorably will steer students to the college.
+53-54) because counselors who view a college favorably will steer students to that college.
 The College tended to visit the same "feeder" schools year after year because recruiting depends on long-term relationships with high schools.
-The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and have the resources and motivation to host a successful visit.
+The high schools they visited tend to be affluent schools -- in particular, private schools -- that possess the resources to host a successful visit and enroll high-achieving students who can afford tuition.
 <!-- Whereas @RN4402 highlights the effect of recruiting visits on inquiries and enrollees, findings from @RN3519 suggest that the College may have valued recruiting visits primarily as a means of maintaining relationships with guidance counselors.
@@
 98).
-Guidance counselors at elite private schools capitalize on the fact that college admissions offices value credible information about which applicants will accept or decline an admissions offer because colleges are sensitive to their acceptance and yield rates.
-This desire for credible intelligence creates an opportunity for high school counselors to advocate on behalf of their students.
-This opportunity depends on guidance counselors having personal relationships with university admissions offices and on having small enough caseloads to advocate for each student individually.
-Guidance counselors tell admissions counselors which highly-sought-after applicants are likely to decline an offer, while lobbying for an applicant who relatively weak academic credentials, but has "character," and extracurricular activities the college needs, and who is sure to matriculate.
+Guidance counselors at these schools capitalize on the fact that selective colleges are concerned about their acceptance and yield rates.
+Therefore, admissions offices value credible information about which applicants will accept or decline an admissions offer.
+This desire for intelligence creates an opportunity for high school counselors to advocate on behalf of their students.
+Guidance counselors tell admissions counselors which highly-sought-after applicants are likely to decline an offer, while lobbying for an applicant who has relatively weak academic credentials but is sure to matriculate and has "character" and extracurricular activities the university values.
+@RN4321 states that such horsetrading depends on guidance counselors having personal relationships with university admissions offices and on having small enough caseloads to advocate for each student individually.
 
@@
 
-Our review of two literatures -- scholarship on nonresident enrollment by public research universities and scholarship on linkages between private schools and private colleges -- suggests an opportunity to bridge and contribute to both literatures.
+Our review of two literatures -- (1) nonresident enrollment by public research universities and (2) linkages between private schools and private colleges -- suggests the opportunity to make a bridging contribution to both literatures.
 
-Historically, public universities received most of their revenue from state funding and enrollment goals prioritized opportunities for in-state students.
+Public universities historically received most of their revenue from state funding and enrollment goals prioritized opportunities for in-state students.
 As state funding became uncertain, public research universities began to prioritize tuition revenue and sought affluent, out-of-state students who paid high nonresident tuition price.
-Salazar et al shows that recruiting visits by public research universities out-of-state public schools in affluent, predominantly white communities.
+@RN4758 show that recruiting visits by public research universities targeted out-of-state public schools in affluent, predominantly white communities.
 Resource dependence theory suggests that as public research universities become more tuition reliant, they will start behaving more like selective private universities in targeting private schools which tend to enroll affluent students that can to pay high tuition prices.
@@
 
-The majority of scholarship on linkages between private high schools and private universities focuses on elite high schools and elite universities [CITE].
-We know much less about linkages between private schools and private universities that are selective but not elite.
-These universities are sensitive about their reputation.
-Despite being relatively affluent, they are much more resource constrained than Ivy Plus.
+Scholarship on linkages between private high schools and private universities often focuses on elite high schools and ultra selective universities [@RN1565; @RN4647; @RN4935].
+we know less about linkages between private schools and (merely) select private universities.
+These universities are self-consious about their reputation.
+Despite being relatively affluent, they are much more resource constrained than Ivy Plus universities.
 Thus, they cannot pursue all enrollment goals with equal vigor.
-Prior research shows that selective but not elite colleges prioritize academic profile (as defined by US News Rankings) and tuition revenue, potentially at the expense of access.
+Prior research shows that selective but not elite colleges prioritize academic profile and tuition revenue, potentially at the expense of access [CITE].
 Many private high schools enroll students that satisfy both enrollment goals.
-However, prior scholarship provides little insight about which private schools have relationships with selective private universities.
+Aside from the single-institution ethnography by @RN3519, prior scholarship provides little insight about which private schools have relationships with selective private universities.
 
-We argue that a recruiting visit from a university to a private high school is an indicator of a relationship.
+We argue that a recruiting visit from a university to a private high school is an indicator of a social relationship.
 Empirically, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
@@
 By analyzing the network of recruiting visits, we can determine the extent to which public research universities are visiting the same or similar sets of private high schools.
-These analyses provide a novel lens into the nature of competition between public research universities and selective private universities.
-They also yield insight about which student bodies these universities want to enroll.
+[IN CONTRAST TO LITERATURES THE TWO LITERATURES ABOVE] These analyses provide a novel lens into the nature of competition between public research universities and selective private universities.
+[ONE MORE SENTENCE TO SHARPEN THE BRIDGING CONTRIBUTION?]
+
+<!-- They also yield insight about which student bodies these universities want to enroll. -->

### 2023-09-28 scripts/vignette_lede_rihe.R

@@ -82,9 +82,16 @@ print_visits <- function(pss_id) {
   print_visits(pss_id = '01294971')
   
 
-# A tibble: 18 × 12
-   univ_name         school_id school_name             event_date religion enroll ranking ranking_numeric pct_white pct_black pct_hispanic pct_asian
-   <chr>             <chr>     <chr>                   <chr>      <chr>     <int> <chr>             <int>     <dbl>     <dbl>        <dbl>     <dbl>
- 
- 
+#01932509 01932509                           ST CECILIA ACADEMY      NASHVILLE         TN  south     catholic             20.077220        A              NA     15 0.4148753       16
+  print_visits(pss_id = '01932509')
+  
+#02163165 02163165                        FRANKLIN ROAD ACADEMY      NASHVILLE         TN  south    christian             10.405405        A              NA     13 0.4007475       15
+  print_visits(pss_id = '02163165')
+  
+#01296141 01296141                          THE ENSWORTH SCHOOL      NASHVILLE         TN  south nonsectarian             21.043324       A+             468     12 0.3983488       14
+  print_visits(pss_id = '01296141')
+  
+#A9106269 A9106269                  CHRIST PRESBYTERIAN ACADEMY      NASHVILLE         TN  south    christian              3.839590        A              NA     12 0.3928353       13
+ print_visits(pss_id = 'A9106269')
+  
  

### 2023-11-09 aefp_2024/aefp_2024_proposal_jaquette.Rmd
working on revisions

---
#title: "The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities"
#author: 
#  - Ozan Jaquette
#  - Crystal Han
#  - Irma Castañeda
bibliography: ./../other/burd_recruiting_chapter.bib
output: 
  bookdown::pdf_document2:
  #bookdown::word_document2:
    toc: FALSE
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
csl: ./../other/apa.csl
urlcolor: blue
always_allow_html: true
header-includes:
      - \usepackage{pdflscape}
      - \usepackage{geometry}
      - \usepackage{floatrow}
      - \usepackage{setspace}
      #- \doublespacing
      - \floatsetup{capposition=top}
fontsize: 12pt
---

```{r setup, include=FALSE}
library(knitr)
library(bookdown)

# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
library(kableExtra)
library(tidyverse)
library(gridExtra)
library(scales)

knitr::opts_chunk$set(echo = F, message = F)

knitr::knit_hooks$set(inline = function(x) {   if(!is.numeric(x)){     x   }else{    prettyNum(round(x,2), big.mark=",")    } })

data_dir <- file.path('..', 'data')
tables_dir <- file.path('..', 'assets', 'tables')
figures_dir <- file.path('..', 'assets', 'figures')

univ_sample_df <- readRDS(file.path(data_dir, 'univ_sample.RDS')) %>%
  arrange(desc(classification), rank)
events_df <- readRDS(file.path(data_dir, 'events_data.RDS'))

pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))

ego_df <- readRDS(file.path(tables_dir, 'table_ego_all.RDS')) %>% 
  mutate(
    univ_region = str_split(characteristics, '\\|', simplify = T)[,1],
    univ_religion = str_split(characteristics, '\\|', simplify = T)[,2],
    univ_race = round(as.numeric(str_split(characteristics, '\\|', simplify = T)[,3]), 1),
    univ_rank = as.numeric(str_split(characteristics, '\\|', simplify = T)[,4]),
    univ_enroll = format(as.numeric(str_split(characteristics, '\\|', simplify = T)[,5]), big.mark = ',')
  )
```

**The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities**

\medskip

*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities. We are still trying to figure out what happened.*
\medskip

<!-- 
Harpeth Hall is a non-sectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee. Harpeth is an "A+" school ranked 337 in the nation according to Niche. Founded in 1951, the racial composition of Harpeth reflects broader regional patterns, where “efforts by the courts to desegregate public schools in the South resulted in white flight to private schools” [@RN4504, p. 14]. In Fall 2017, about 85% of Harpeth students were white and less than 5% were Black or Latinx.
-->
**INTRODUCTION AND RESEARCH QUESTIONS**. Harpeth Hall is a non-sectarian private school for girls in Nashville, ranked 337 in the nation according to Niche private school rankings. From September 6th through October 17th, Harpeth received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University), and three private liberal arts colleges (Harvey Mudd, Scrips, and Sewanee). Previous scholarship observes strong connections between private schools and selective private universities [@RN3519; @RN4407]. However, Harpeth also received visits from six out-of-state public research universities, the University of Cincinnati, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.

Drawing from theories of organizational behavior [@RN531; @RN959; @RN531], recruiting behaviors that require significant expenditure are indicators of university enrollment priorities. According to @RN4664, off-campus recruiting visits were the top-ranked recruiting expenditure item for both public and private universities.

This study analyzes off-campus recruiting visits to private high schools from a convenience sample of 14 selective private universities and 15 public research universities. Recruiting visits indicate a social relationship, motivating social network analyses of network ties (visits) between actors (universities and schools). Analyses are informed by three research questions:
<!--

-->

1. How does the scale of visits to private schools by public research universities compare to the scale of visits to private schools by selective private universities?
1. How do the characteristics of private schools visited by public research universities compare to the characteristics of private schools visited by selective private universities?
1. To what extent do public and private universities visit overlapping sets of private schools?

Policy debates about college access are largely uninformed about recruiting.
This proposal speaks to the conference theme by informing researchers and policymakers how recruiting practice occurs "in the wild" within the college access ecosystem.

**LITERATURE REVIEW**. We bridge two disconnected literatures: (1) nonresident enrollment at public universities; and (2) linkages between private schools and private universities.

Public research universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753] and international students [@bound_international], who pay higher prices than residents. @RN3685 show that growth in the share of nonresident students is associated with declines in the share of Pell recipients and Black and LatinX students. Universities visit high schools to attract applicants and maintain relations with counselors. @RN4758 analyzed off-campus recruiting visits to public high schools by public research universities. Most universities made more visits to out-of-state high schools than in-state high schools. These out-of-state visits focused on affluent, predominantly white schools.

Scholarship from sociology and economics finds that private school attendance positively affects college access and college selectivity [@RN4614;@RN4625; @RN4599; @RN4936; @RN4938]. Descriptive statistics from the high school freshman class of 2009 indicate that 5.0% of public high school students attended a public university ranked in the top 100 by USNWR and 1.9% attended a top 100 private university (Author calculations based on HSLS). Of private school students, 10.9% attended a top 100 public university and 16.8% attended a top 100 private university. Of nonsectarian private school students, 11.3% attended a top 100 public university and 39.8% attended a top 100 private university.

@RN4935 find that students from elite private schools are overrepresented at elite universities because private school applicants receive higher ratings on non-academic components (e.g., extracurricular activities, teacher and guidance counselor recommendations). By contrast, scholarship from sociology highlights the mechanism of social relationships between private school guidance counselors and college admissions officers (e.g., making a phone call on behalf of an applicant) [@RN4407; @RN4647; @RN3519; @RN4640].

Although the literature on (1) nonresident enrollment and (2) the literature on linkages between private schools developed in isolation, they are both part of a broader story about the competition for affluent students. Historically, private schools were the domain of selective private universities. However, public research universities have an incentive to visit out-of-state private schools to find "full-pay" nonresident students. By analyzing the network of recruiting visits, we show whether public research universities and selective private universities are competing for students at similar sets of private schools.
<!-- 
 We also examine the characteristics of visited schools, which have implications for university enrollment composition.
-->

**METHODS**. We collected off-campus recruiting visit data in 2017 by web-scraping events from university admissions websites. The analysis sample for this study consists of 15 public research-extensive universities and 14 private universities ranked in the top 100 of US News National University rankings. We also incorporated secondary data from IPEDS, the American Community Survey, NCES Common Core of Data (public schools), and the Niche Best Private High Schools ranking.

Off-campus recruiting visits are the network tie that defines a two-mode social network between universities (mode 1) and private schools (mode 2). We construct the two-mode network and transform the two-mode network into several one-mode network objects. To answer research questions, we analyze these objects using simple descriptive statistics and cluster analysis methods, as shown below.

**RESULTS**. Results for RQ1 (scale of private school visits) are shown in Figures \@ref(fig:events-hs-count-pubu), \@ref(fig:events-hs-count-privu), \@ref(fig:actual-proportional-pubu), and \@ref(fig:actual-proportional-privu). Results for RQ2 (characteristics of visited private schools) are shown in Figures \@ref(fig:region-pubu-privu), \@ref(fig:religion-pubu-privu), \@ref(fig:rank-pubu-privu), \@ref(fig:race-pubu-privu), and \@ref(fig:race-pubu-privhs-pubhs). Results for RQ3 (overlap in visited schools) are shown in Table \@ref(tab:privu-percent-visited-by-pubu-matrix) and in Figure \@ref(fig:plot-1mode-u), which shows the one-mode public university network with universities categorized into groups based on "community detection" cluster analysis methods.

**SIGNIFICANCE**. Universities in our sample made a disproportionate number of visits to private schools. Most public universities in our sample -- even those not in the South -- made a large share of visits to the South. Visited private schools tend to be much whiter than visited public schools. We infer that university recruiting behavior disproportionately targets students at racially homogeneous high schools.

\newpage

# References

<div id="refs"></div>

\newpage

\clearpage

\begin{landscape}

```{r u-cluster1-percent-matrix, include=FALSE}
table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))

#kable(table_1mode_u$clusters_df[order(match(table_1mode_u$clusters_df$univ_abbrev, rownames(table_1mode_u$onemode_df))), ], caption = 'Clusters for public and private universities')

cluster_1 <- c(1, 4, 5, 7, 16, 18, 19, 24, 25, 28)
cluster_2 <- c(2, 3, 6, 8, 9, 10, 11, 12, 14, 15, 20, 22, 23)
cluster_3 <- c(13, 17, 21, 26, 27)
cluster_4 <- 29

kable(table_1mode_u$onemode_pct_df[cluster_1, cluster_1], caption = 'Public and private universities percent matrix (cluster 1)') %>%
  kable_styling(latex_options = 'scale_down')
```

```{r privu-percent-visited-by-pubu-matrix}
rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)

kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities') %>%
  kable_styling(latex_options = 'scale_down') %>%
  #column_spec(1, width = '8.5em') %>%
  column_spec(2:15, width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em')
```

\end{landscape}

\restoregeometry

\clearpage

\newpage

```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
```

\newpage

```{r events-hs-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
```

\newpage

```{r actual-proportional-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
```

\clearpage

```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
```

\clearpage

```{r region-pubu-privu, echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
```

\newpage

```{r religion-pubu-privu, echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
```

\newpage

```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school ranking of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
```

\newpage

```{r race-pubu-privu, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
```

\newpage

```{r race-pubu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools vs. public high schools, public research universities"}
include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
```

```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
```

### 2023-11-09 r_r/letter_to_reviewers.Rmd
working on revisions

---
#title: "Response to Editors and Reviewers"
#author: "ozan"
date: "`r Sys.Date()`"
output: pdf_document
bibliography: ./../other/burd_recruiting_chapter.bib
csl: ./../other/apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

XXXX X, 2023

Dear Editors,

We thank the Reviewers and the Editor for excellent, thoughtful, and detailed feedback. While the analyses have changed only modestly, the front end of the paper has changed tremendously, literally rewritten from scratch. I begin this letter by discussing the big changes in the manuscript, which I hope address many of the big concerns from Reviewer 2. Next, I address remaining reviewer concerns one by one.

# Big Changes to the Manuscript.

The original manuscript compared off-campus recruiting visits to private high schools by public research universities and selective private universities with the goal of contributing to scholarship on "privatization." The scholarly hook was that previous research stated that public universities were behaving more like private universities but empirical research had not compared public and private universities on a behavior associated with private universities. To set this hook, we made the strong argument that the historic mission of public universities is social mobility and the historic mission of selective private universities is social reproduction. Off-campus recruiting visits to private high schools is a behavior associated with the social production mission of selective private universities. Therefore, comparing public research and selective private universities on this behavior gives insight about the extent to which public research universities are behaving like private universities.

Reviewer 2 very helpfully pointed out several core flaws with assumptions, practical motivations, scholarly contribution, and practical significance of the manuscript. I view these flaws as distinct yet interconnected. First, Reviewer 2 found the assumptions about "mission" -- public research universities serve social mobility mission while selective private universities serve social reproduction -- to be overly simplistic generalizations that assume a homogeneous mission across very different organizations. Moreover, Reviewer 2 found the assumption that private universities serve the mission of social reproduction to be somewhat off-putting and dismissive. Second, in contrast to the emphasis on an idealized mission, Reviewer 2 encouraged the manuscript to consider a more practical reason for why public research universities would target private high schools, particularly around targeting high-paying students that generate substantial revenue. Third, with respect to scholarly contribution, Reviewer 2 questioned why comparing public and private universities on a behavior associated with private universities makes an important contribution to the privatization literature. We must admit that we agree with this concern. The "privatization" literature has been in decline for more than a decade. So it is not important to contribute to a literature that is no longer relevant. Fourth, Reviewer 2 is concerned that the original manuscript did not clearly state the practical implications of the findings.

We agree with all four of these core concerns by Reviewer 2. We sought to develop a revised manuscript that addressed all of these concerns. We concluded that targeted changes to particular parts of the front-end might address some but not all of these concerns. Therefore, we decided to completely destroy the original front end and create a new one. When the dust settled, we were happy to find that the original research questions -- and therefore the original analyses -- remained salient to the new front end.

We explain the structure of the revised manuscript, by drawing from the *Setting the Hook* article by @RN3515, which is my favorite article on the craft of scholarship. They write that "One hook involves using a provocative quotation or vignette to engage the reader in the intriguing and practical nature of their topic" (p. XX). Our revised introduction begins with a vignette describing off-campus recruiting visits to Harpeth Hall, a predominantly white "non-sectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee" (p. X). The vignette then moves to the nearby University School of Nashville, which is highly ranked nationally, and receives visits from the more elite private colleges and universities in our sample, but few public universities in our sample. Finally, nearby Father Ryan High School and Christ Presbyterian Academy are lower ranked, are overwhelmingly white and receive visits from few selective private universities in our sample but do receive visits from a substantial share of public research universities in our sample. This introduction relies on data collected for the study, previews some of the core findings, and we hope it "engage(s) the reader in the intriguing and practical nature of the topic" as @RN3515 say.

The revised literature review hopefully sets up a scholarly contribution while also doing a better job of describing the practical motivation for visits to private high schools by public universities. Following @RN3515, our literature review takes the approach of "entering two different conversations and bridging them" with the goal of making a contribution to each conversations while also showing that these two disparate conversations are both parts of a larger story. We first review scholarship on nonresident enrollment by public research universities. Reviewing this scholarship -- which we briefly preview in the introduction -- addresses a core concern from Reviewer 2 by identifying a strong practical motivation for public research universities to target out-of-state private school students (they tend to be affluent and can afford high prices and therefore generate desired tuition revenue). We also show that previous research about recruiting by public research universities has not investigated visits to private high schools.

Second, we review scholarship on linkages between private schools and private universities, we show that prior literature finds a strong relationship between private school attendance and college access and college selectivity. We also present descriptive statistics, which show a strong relationship between private school attendance and attending a selective private college or university. Whereas recent work from economists shows that private school applicants receive higher non-academic ratings than public school applicants [@RN4935], qualitative scholarship by sociologists highlights the importance of social relationships between private schools and selective private universities [@RN4407; @RN3519]. These social relationships are substantially maintained through face-to-face interactions between college admissions officers and high school guidance counselors. These interactions occur during off-campus recruiting visits, motivating the use of social network analyses. Although prior research highlights the importance of social networks between private schools and private universities, they haven't analyzed the social networks that emerge from off-campus visit patterns. Furthermore, we argue that scholarship by sociologists tends to focus on the relationship between elite private schools and elite universities, so we know less about the social networks of private universities that are selective but not elite.

We develop a "bridging" scholarly contribution by stating the these two literatures have been isolated from one another, but they are both parts of a broader story about the changing nature of school segregation and the competition for affluent students. As public universities seek affluent out-of-state students, they are attracted to out-of-state private schools. In doing so, public research universities are encroaching on what had primarily been the territory of private universities. Therefore, analyses of visits to private schools explore the extent to which public and private universities are competing for students at similar or distinct sets of schools, revealing insights about the competition for affluent students. Additionally, prior research shows that private school enrollment is whiter than public schools, that private school students have become more affluent in recent decades, and that private school enrollment has grown in the South as a consequence of "white flight" to private schools. "Thus, in recruiting from private schools, universities may be targeting student bodies that are more affluent and racially homogeneous than public schools. We investigate the characteristics – including geographic region and racial composition – of private schools being targeted by university admissions officers because these characteristics have downstream implications for the racial composition of university campuses"

Finally, we have revised the practical significance and implications to address concerns raised by Reviewer 2.

[WRITE THIS TEXT AFTER YOU REVISE THE DISCUSSION SECTION]

# Response to Reviewer 2

## Introduction and Overall Framing

> **Reviewer concern**. This paper examines the recruiting behaviors of a sample of public and private institutions in the U.S. This paper employs a unique dataset and uses descriptive techniques that are not commonly used in higher education literature. The paper is well-written and makes an interesting contribution to the literature. I do have a few suggestions, which I lay out below. Chiefly, as written, this paper lacks some practical grounding. The authors set up the paper by arguing that public and private institutions serve two different missions- one serves social reproduction and the other serves social mobility. They then argue that these priorities drive recruiting practices. While this is a useful way to frame behavior, I think the paper would benefit from an additional discussion about the practical benefits of recruiting students from private schools, especially for public institutions. One place to start is to consider how private and public-school students pay for college. Do private school students generate more revenue for the institution? This same feedback applies to the summary/conclusion section. While the authors do a good job talking through their findings, they did not discuss the implications of their findings for research, practice, or policy. As such, I left feeling like this paper had some interesting findings, but could not name any clear ways in which this paper makes a contribution to educators or education research. That being said, I do not think my ask is insurmountable by any means, therefore I recommend a revise and resubmit.

**Author response**: We wholeheartedly agree with these concern by Reviewer 2 and we are grateful to Reviewer 2 for raising these issues! As discussed above, the revised manuscript addresses these concerns about the practical benefits of recruiting students from private schools. We have also improved the discussion of implications for research and practice [REVISE AFTER YOU REWRITE THE DISCUSSION SECTION]

> **Reviewer concern**. I'm a bit off put by your blanket statement that private institutions prioritize social reproduction while public institutions prioritize social mobility. I understand that you're using this as a framework to set up your study, but some additional language qualifying these remarks would improve your argument. I can think of many examples where private institutions serve social mobility and where public institutions serve social reproduction. For example, we know that private institutions in many states are a vital path to a college degree for low-income students, as they can more easily discount the cost of attendance. Conversely, public institutions in some states do not give any aid to undocumented students. It might help to just note that we cannot fully capture colleges' priorities or sort them into these two buckets just based on their status as public or private, but that this framework is used to conceptualize behavior.

**Author response**: We agree with this reviewer concern. As discussed above, we have removed these statements from the revised manuscript.

> **Reviewer concern**. Your argument that the recruiting behavior of colleges at private secondary schools is an indicator of the social reproduction mission could use some strengthening. As school voucher programs become more common, it's possible that, by recruiting at private secondary schools, IHEs are reaching those who are high achieving, but less affluent. Is there any data that tracks the prevalence of voucher use in your sample over time? Do you have any descriptive data on the secondary schools in your sample that could speak to this? If not, it might be worth naming school vouchers as a recent(ish) trend and heading off concerns like mine.

**Author response**: We agree with this concern by Reviewer 2. Now that we have eliminated the "social reproduction" framing, the concern becomes less of an issue. Unfortunately, we do not know of data that speaks to the prevalence of voucher use at private high schools. That said, the revised literature review substantively cites the work of @RN4504, who find that private school enrollment by middle-income families has declined dramatically over the past three decades and this decline has been driven substantially by the decline in middle-income families enrolling at Catholic schools. Compared to three decades ago, the contemporary student population of private school students contains a higher proportion of affluent families.

> **Reviewer concern**. I have some reservations about this sentence: "By contrast, for public research universities, visits to private high schools - particularly out-of-state schools - are antithetical to the mission of social mobility for high-achieving, low-income state residents." (p. 3). Is it really the mission of public universities to serve high-achieving, low-income state residents? The emphasis on high-achieving, low-income students is where I take issue. I'd argue the mission is more generally to educate state residents and keep them within the borders of the state regardless of ability or SES.

**Author response**: We agree with his concern. The revised manuscript removes the idea that the mission of public universities is social mobility. As such, we no longer make the strong statement that the historic mission targets low-income state residents as the primary focus.

> **Reviewer concern**. I think what's missing in the introduction is a conversation about the practical advantages of recruiting students from private institutions from the university's perspective irrespective of "mission." Outside of reproducing or generating social mobility for its' patrons/stakeholders, why might an institution want to recruit from private secondary schools? I imagine that IHEs might want to do so because students who attend private secondary schools would be less likely to require need-based aid from the institution. Resource dependency theory would suggest that if recruiting high-paying students is critical to keeping the lights on, then institutions will try to get as many of these students in the door as possible. I think the conversation around the mission of the institutions is important; however, right now the grounding for the study feels very high-level and lacking some practical considerations.

**Author response**: We wholeheartedly agree with Reviewer 2 here. The previous manuscript's focus on some universally held historic "mission" for public vs. private universities was simultaneously simplistic and distracting. The revised manuscript focuses motivates the analysis based on the more practical idea that universities target private schools because these schools tend to enroll affluent students, who have greater ability to pay high tuition prices without substantial need-based aid.

> **Reviewer concern**. Similarly, I find myself craving some context around the broader implications for this study in the introduction. I think you start to get to this in your conversation around social reproduction, but it would help draw the reader in if you could lay out what the findings of this study could mean for policy and practice.]

**Author response**: REVISE THIS RESPONSE AFTER YOU HAVE WRITTEN THE DISCUSSION SECTION AND REVISED THE INTRODUCTION.

> **Reviewer concern**. "The "Chetty" data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile (Burd, 2017; Chetty, Friedman, Saez, Turner, & Yagan, 2020)." P. 3 Instead of saying "Chetty" data, can you be more descriptive here? This sentence assumes a lot of prior knowledge for the reader. "Data linking IRS records to …."

**Author response**: We agree with this recommendation. With that said, the revised paper no longer substantively references this data source.

## Section 2 [background and lit review]

> **Reviewer concern**. Is there any literature about the impacts of COVID on recruitment strategies? In particular, are in-person site visits to secondary schools more or less common than they were prior to 2020? Has there been any investment in virtual recruiting, such as zoom calls to schools? This kind of information will help enrich our understanding of the landscape of recruitment laid out in section 2.1.

**Author response**: The original manuscript had a level-1 section entitled "What do we know about off-campus recruiting?", which reviews market research about off-campus recruiting and published scholarship By contrast, the revised manuscript has a broader literature review section that reviews scholarshp from two literatures -- (1) nonresident enrollment by public universities and (2) linkages between private schools and private universities -- and bridges these two literatures. Therefore, this recommendation from Reviewer 2 is less relevant to the revised literature review structure.

[REVISE THIS TEXT AFTER YOU REVISE THE DISCUSSION SECTION]
Nevertheless, the question Reviewer 2 asks is very important; if off-campus recruiting visits became less prevalent following Covid, then the analyses do yield relevant insights about contemporary/future recruiting behavior by public research universities and selective private universities.

In the revised manuscript, the discussion section substantively describes information about off-campus recruiting events following Covid. In short, off-campus recruiting events are back and are viewed as vital to recruiting efforts. We put this text in the discussion section rather than the literature review because it complements text about recommendations for practice and this text fits lesss well with the revised literature review structure.

TEXT TEXT TEXT This recommendation is very relevant for the original manuscript, but a bit less relevant for the revised manuscript in that the previous lit review of "what do we know about off-campus recruiting" has been replaced by a much broader literature review which focuses on X, Y, Z. With that being said, the reviewer asks a good question here. We refer [IN FOOTNOTE?] the readers to REPORT X, Y, Z FROM RUFFALO NOEL LEVITZ WHICH SAYS BLAH BLAH BLAH. FROM EAB COUNSELOR REPORT Q16, "HOW DO YOU PREFER TO RECEIVE INFORMATION FROM COLLEGES"; FOR BOTH PUBLIC AND PRIVATE SCHOOLS, "HIGH SCHOOL VISITS BY COLLEGE REPRESENTATIVES" WERE THE HIGHEST RATED CHANNEL, ESPECIALLY FOR PRIVATE SCHOOL COUNSELORS. ALSO, VIRTUAL COUNSELOR EVENTS WERE QUITE LOW RATED. IMPLICATION, IN THE PURSUIT OF TRADITIONAL COLLEGE STUDENTS, THIS IS STILL A HAND-TO-HAND BUSINESS. ALSO THERE IS A BIT IN THE MARKETING RECRUITING PRACTICES FOR UNDERGRAD STUDENTS BY RUFFALO.

Cost of recruiting undergraduates report, 2022. Travel was 5th for publics. second for privates. Travel was top area of increased expenditure for publics and second top area of increase for privates, suggesting that they were going to increase travel following return from Covid.

## Section 3 (social network analysis concepts)

> **Reviewer concern**. It may help the reader understand network analysis concepts if the authors include some visualizations attached to their examples in the beginning of the section. This is especially true when the authors discuss the networks related to this study.

INCLUDE PICTURE OF EGO NETWORK? HAVE TO KEEP THIS PARSIMONIOUS BECAUSE OF PAGE LENGTH CONCERNS

> **Reviewer concern**. The authors rarely cite materials when explaining network analysis. Some citations would be helpful for those unfamiliar with the technique.

**Author response**: The revised discussion of social network concepts and analysis now includes relevant citations.

> **Reviewer concern**. On page 15, you lay out the different private school characteristics that are the focus of this study. I also wonder if the authors thought about looking at recruiting at private secondary schools in states neighboring the college in addition to the region analysis. I imagine that public institutions would have quite the incentive to recruit out-of-state students, as they are revenue generators for the institution. These institutions may target folks from surrounding states because a) it's cheaper to send a recruiter to a neighboring state rather than one in another region b) because the college likely has more name recognition in neighboring states than states in another region and c) if we believe that the purpose of public colleges' is to strengthen the state's economy by keeping highly educated workers in the state, it might follow that graduating students from neighboring states may be more likely to work in the college's state than graduating students who are much
further from home.

**Author response**: We agree with the point the Reviewer is making here and for all the reasons that Reviewer 1 lists. We experimented with doing an additional analysis of visits to neighboring states. However, we ultimately decided to not include this analysis in the revised manuscript. The two reasons are (1) the neighboring state analysis doesn't quite get at the underlying relationship between geographic proximity and recruiting visits/student demand and (2) the manuscript is already long so we decided to avoid including analyses that don't quite work.

The reason the neighboring state analysis doesn't quite work is exemplified by the University of Nebraska Lincoln (UNL). Nebraska does not share a border with Illinois but a huge proportion of their high school recruiting visits -- public and private -- are in Chicago. The same is true for the University of Arkanas and visits to Georgia (Atlanta), CU-Boulder and California and CU-Boulder and Chicago, and UC-Berkeley and visits to Washington (Seattle). To a huge degree, recruiting visits occur in major metropolitan areas, so the analysis you recommend bears fruit for universities in states that neighbor a state with a major metopolitan area (e.g., University of Alabama and Georgia, or University of Pittsburgh and New York).

We considered an alternative to your analysis that focuses on visits to metropolitan areas within some distance (e.g., 500 miles) from the University. But this analysis is also not clean because distances seem to be greater in the West (e.g., Denver to Los Angeles) than the east coast (e.g., Amherst MA to NYC). For these reasons, we opted to exclude those analyses even though we do agree with the basic logic the Reviewer lays out.

## Section 4 (data and methods)

> **Reviewer concern**. Can you walk us through why you used two different sources to choose colleges (Carnegie for publics and USNWR for privates)? If we want to examine samples of public and private colleges that are similar, wouldn't it make sense to use one classification method to pick schools? You get at this a little bit later, but I'd still like to know your logic.

**Author response**: The revised Data and Sample section states that "The rationale for different criteria for inclusion across different university types is because these criteria reflected the interests of a foundation that funded the data collection." We agree with Reviewer 1 that making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities. The revised manuscript now includes a Limitations subsection that describes this limitation and its consequences.

> **Reviewer concern**. What are the drawbacks of a convenience sample? The authors do a great job breaking down network analysis techniques, so I want to ensure that they aren't assuming knowledge elsewhere.

**Author response**: This is an excellent suggestion by Reviewer 1. The new Limitations section in the revised manuscript discusses the drawbacks of a convenience sample.

> **Reviewer concern**. How are you certain that the colleges in your final sample posted all of the recruiting events they hosted/took part in? Did you double-check with admissions offices?

**Author response**: We added text to the Data and Sample section to address this concern. For public research universities, we double checked with the admissions offices and issued formal public records requests if the university did not provide data.

> **Reviewer concern**. I would love to know what software/packages you used to scrape websites? This would be helpful for others who would like to build off your work.

**Author response**: The revised manuscript now states that we used Python to scrape admissions websites [CRYSTAL -- ADD WHICH PACKAGES WE USED]. Additionally, in case this is helpful to readers, the revised manuscript states that all analyses were conducted using *R* and network analyses were conducted using the *igraph* package. As an aside, we could have done the web-scraping in *R* too.

> **Reviewer concern**. I'd also like to know how the universities in your final sample compare the universities that were in your original sample. Of course, you aren't making any causal claims in your paper, but I do wonder where you think the reader should tread lightly when extrapolating the results to other institutions. In other words, is there anything special about your sample when compared to other colleges that may be driving the patters you're seeing?

ADD APPENDIX TABLE ABOUT THIS.

## Section 5 (results)

The results are well-organized and clear

**Author response**: Thank you! The results have been revised moderately to reflect analysis of recruiting in neighboring state and to reflect questions from Reviewer 1 (ADD/MODIFY TEXT ONCE YOU HAVE MADE THIS CHANGE)

## Section 6 (discussion)

> **Reviewer concern**. The authors state that "a weakness of the scholarly literature on privatization is that few studies compare public and private universities with respect to a behavior that is associated with private universities." Can the authors elaborate on why this weakness is important? In other words, help us understand why this gap in the literature deserves to be interrogated?

**Author response**: We agree with Reviewer 2 implied concern here that just because the privatization research did not address this topic, it is not clear that conducting this analysis makes a significant scholarly contribution because the privatization literature is less relevant than it was 10 years ago.

STATE THE SCHOLARLY CONTRIBUTION THE PRESENT ARTICLE DOES MAKE.

- TO THE NONRES LITERATURE/COMPARE THESE RESULTS TO RESULTS FROM AERJ ARTICLE. SAY THE CONTRIBUTION
- TO THE PRIVATE SCHOOL TO PRIVATE UNIVERSITY LINKAGES, SHOW WHAT ARE THE ORGS THAT UNIVERSITIES ESTABLISH TIES TO (E.G., ALONG RELIGIOUS LINES)
- WHAT IS THE BRIDGING CONTRIBUTION.

> **Reviewer concern**. The authors do a good job of summarizing their findings, but I'm, again, wanting a conversation about the implications of these findings for practice and future research. What do these findings mean for students? For admissions professionals? What are your thoughts on avenues for future research?

**Author response**: ADD TEXT

> **Reviewer concern**. Why do you think public universities are "playing the private school game?" This connects back to earlier suggestions about fleshing out the practical reasons why public institutions are targeting private schools students.

**Author response**: We agree with this concern. As described in the beginning of the letter, the revised manuscript is motivated by the idea that visiting private schools is motivated by the desire to find households that can pay high tuition prices without requiring substantial need-based institutional aid [NOTE TO SELF: NEED TO MAKE THIS RATIONALE MORE CLEAR FOR PRIVATE UNIVERSITIES].

# Response to Reviewer 1

> **Reviewer concern**. 1. It appears that the author has written a separate paper focusing on off-campus recruiting visits made by public research universities to public high schools. To enable a comprehensive comparison of off-campus recruiting behaviors between public and private universities, it is necessary to consider visits to both public and private high schools. At the very least, it would be beneficial to compare the findings of the earlier study with the results presented in this manuscript to identify any notable differences or similarities.

**Author response**: We agree with this suggestion. The revised literature review substantively reviews prior research we conducted about visits to public high schools by public research universities. The revised discussion section compares the results from this study to the previous study [REVISE ONCE YOU REVISE THE DISCUSSION SECTION]. WE FIND BLAH BLAH BLAH

> **Reviewer concern**. 2. The manuscript could benefit from some reduction in length without compromising its quality. For example, in section 2.2, instead of providing extensive descriptions of various studies, the author could reorient the focus of this section to highlight the specific contributions of these studies to the present research. Additionally, combining sections 3 and 4 and providing a concise description of the social network analysis in the Data and Methods section would enhance the overall readability and coherence of the paper.

**Author response**: We agree with these suggestions. The revised literature review avoids extensive discussion of any one publication. The revised literature review is focused on situating the contribution vis-a-vis two literatures, which we attempt to review efficiently in a way that highlights the contribution to each of these literatures and also the bridging contribution.

Additionally, we follow Reviewer 1's recommendation of removing the level-1 section "Social Network Analysis Concepts" text, and allocating this text to relevant sub-sections of the revised "Methods" section. This change reduces redundancy in text, helps to reduce word count, and results in a structure that we hope is easier for readers to digest. The revised organization of the level-1 Methods section is as follows: Data and sample; Constructing social networks; Analyses (which are described separately by research question)

> **Reviewer concern**. 3. The results section currently includes overly detailed and occasionally irrelevant information, making it challenging for readers to grasp the overall patterns and implications. In sections 5.3.1 and 5.3.2, the purpose of conducting network analysis within public and private universities is unclear. It is important to provide a clear rationale for analyzing these specific institutional types and explain how it contributes to understanding the differences in recruiting strategies. Additionally, some results seem specific to the sample of universities under study, and it would be valuable to provide broader insights into the disparities between public and private institutions.

WHAT REVIEWER IS ASKING:

- REMOVE ANALYSIS OF Figure 15: One-mode network for public institutions, colored by cluster TO THE APPENDIX
- REMOVE ANALYSIS OF Figure 16: One-mode network for private universities, colored by cluster TO THE APPENDIX
- REMOVE EXTENSIVE DISCUSSION OF INDIVIDUAL UNIVERSITIES;

> **Reviewer concern**. 4. The analysis conducted in section 5.3.3—which is central to this study—does not provide a clear indication of the differences or similarities between public and private institutions in terms of their recruiting strategies. However, the finding that certain groups of public and private universities have more in common with each other than with other universities of the same control suggests the possibility of confounding factors such as geographic proximity, rankings, etc. Incorporating an analysis of these confounding factors would strengthen the study and likely require additional data analysis.

SEEMS TO WANT ADDITIONAL ANALYSES TO ENGAGE W/ RQ3. I'M NOT SURE WHAT TO ADD HERE. COME BACK TO LATER.

> **Reviewer concern**. 5. The cross-sectional nature of the data limits the ability to draw conclusions about the direction of change in recruiting strategies between public and private institutions. This is especially significant given the convenient sample of institutions used in this study. These limitations should be discussed.

ADD LIMITATIONS SECTION. STATE LIMITATIONS OF CROSS-SECTIONAL NATURE OF DATA COLLECTION

### 2023-11-09 r_r/manuscript_rihe.Rmd
working on revisions

--- 2021-06-26 text/manuscript_june_2021.Rmd
@@
       - \usepackage{setspace}
+      - \usepackage{fancyhdr}
+      - \usepackage{titlesec}
       #- \doublespacing
       - \floatsetup{capposition=top}
-fontsize: 11pt
+      - \newcommand{\beginsupplement}{
+      - \setcounter{table}{0}  
+      - \renewcommand{\thetable}{S\arabic{table}} 
+      - \setcounter{figure}{0} 
+      - \renewcommand{\thefigure}{S\arabic{figure}}}
+fontsize: 12pt
 ---
@@
 
+\setstretch{1.5}
+
 # Introduction
 
-Prior to the pandemic, admissions counselors from colleges and universities traveled to local high schools each year in order to meet prospective students and maintain relationships with guidance counselors at feeder schools [@RN3519].
-@RN4721 analyzed off-campus recruiting visits made in 2017 by 15 public research universities.
-Surprisingly, 12 of the 15 universities made more visits to *out-of-state* high schools than *in-state* high schools.
+*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[NAME THE UNIVERSITIES] We are still trying to figure out what happened.*
+\bigskip
+
+Autumn is college recruiting visit season at Harpeth Hall, a non-sectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
+Founded in 1951, Harpeth is an "A+" school ranked 337 in the nation according to the 2020 *Best Private High Schools in America* by Niche.
+Enrollment patterns at Nashville-area private schools reflect broader regional patterns, whereby “efforts by the courts to desegregate public schools in the South resulted in White flight to private schools” [@RN4504, p.
+14].
+In Fall 2017, about 85% of Harpeth students were white and less than 5% were Black or Latinx (Author calculations).
+
+From September 6th through October 17th, Harpeth received recruiting visits from 11 private universitiesin our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denvor, Emory, Tulane, Baylor, Texas Christian University), and three private liberal arts colleges (Harvey Mudd, Scrips, and Sewanee).
+Previous scholarship observes strong connections between private schools and selective private universities [@RN3519; @RN4407].
+However, Harpeth also received visits from six out-of-state public research universities, the University of Cincinatti, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.
+
+The nonsectarian University School of Nashville was founded in 1975 and is located next door to Vanderbilt University.
+It is an "A+" school, ranked 127th in the nation, and is more racially diverse than Harpeth (64% white, 11.5% Black, 3.5% Latinx, 10.0% Asian).
+From September 11th 2017 through October 18th, the University School received visits from nearly the same set of 11 private universities that visited Harpeth (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinatti, CU Boulder).
+
+Father Ryan High School is a Catholic school founded in 1925.
+Father Ryan is predominantly white (86%, 7% Black or Latinx) and received an "A" grade from Niche, meaning it is not ranked in the top 1,000 US private schools.
+In fall 2017, Father Ryan received visits from nine of the 14 private universities in our sample (including all the Catholic universities) and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama.
+Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from five private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University).
+It also received visits from the University of Cincinatti, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder.
+Christ Presbyterian Academy was founded in 1985 and 94% of its students are white.
+
+Theories of organizational behavior suggest that university recruiting behaviors -- those that require significant expenditure -- are indicators of organizational enrollment priorities.
+Large, public-facing organizations are beset by multiple, competing pressures from the external environment, but organizations have difficulty pursuing multiple goals [@RN531; @RN959].
+Thus, organizations respond by symbolically adopting some goals and substantively adopting others [@RN513].
+Under symbolic adoption, organizations adopt policies and structures that send signals to external constituents but do not substantively affect resource allocation inside the the "technical level" of the organization.^[Contingency theory states that organizations consist of "technical levels" responsible for processing inputs and producing outputs and "managerial levels" responsible for directing the technical level and tending to demands from the external environment [@RN531].
+The technical level achieves effectiveness by focusing on a small, stable set of goals.] Under substantive adoption, organizations direct resources in the technical level towards achieving the goal.
+Off-campus recruiting visits to local high schools and college fairs was the top-ranked recruiting expenditure item for both public and private universities, according to @RN4664.
+Therefore, analyses of which schools a university visits -- and which schools they ignore -- can yield insights about university enrollment goals.
+
+@RN4758 analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
+the authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools.
+These out-of-state visits focused on affluent, predominantly white public schools.
+Set against the scholarship about declining state appropriations and growing nonresident enrollment [@RN3753; @RN3685], these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition price.
+
+Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college [CITE].
+This research observes strong links -- and student flows -- between private high schools and selective private universities [CITE].
+To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between between private school and college.
+We argue that these two stories have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities.
+
+<!-- 
+This study compares recruiting visits to private high schools by public research universities and recruiting visits to private high schools by selective private universities. 
+We argue that recruiting visits are an indicator of enrollment goals -- the university wants to enroll some students from the school, the school wants some students to enroll at the university. 
+-->
+
+This study analyzes recruiting visits to private high schools made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
+<!-- @RN3519 finds that travel to local high schools is vital for maintaining relationships with guidance counselors at "feeder schools."--> We conceptualize recruiting visits as an indication the university and the school have a social relationship.
+This conceptualization motivates the use of social network methods, which analyze networks defined by "network ties" (i.e., visits) between actors (universities and schools).
+Comparing the recruiting networks of public research universities and selective private universities yields novel insights about the competition for affluent, "full-pay" students.
+Analyses are informed by three research questions:
+
+1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
+    - ALTERNATIVE: How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?
+1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
+1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+
+Both private and public universities in our sample made a disproportionate number of visits to private high schools.
+For public research universities, visited private schools were much more likely to be out-of-state than visited public schools.
+Although universities visited a large number of private schools in their home region, most universities also visited a large number of private schools in the South.
+Private schools that received visits were predominantly white.
+Although partially a function of our analysis sample, public universities tended to visit lower ranked private high schools than private universities.
+Surprisingly, several public universities visited sectarian private high schools at a rate similar to sectarian private universities.
+Network analyses revealed substantial overlap in the recruiting networks of public and private research universities.
+
+This manuscript is practically important because it provides insight about which schools universities view as "feeder schools" and -- to a limited extent -- the characteristics of students they want to enroll.
+Prior research finds that university recruiting efforts affect the enrollment decisions of students [CITE].
+In turn, the composition of enrolled students affects the campus culture experienced by students.
+Scholarship and the popular press reports that underrepresented minority students and low-income students at public flagship universities feel isolated amidst affluent, predominantly white student bodies.
+Racial and socioeconomic isolation negatively affects student development outcomes for isolated students and for the entire student body [CITE].
+State policymakers and institutional leaders should recognize that the enrollment composition at public research universities is not the consequence of exogenous student demand, but rather the consequence of recruiting efforts that seek to grow nonresident enrollment by systematically targeting affluent, predominantly white public high schools [@RN4758] and affluent, predominantly white private high schools.
+[NOTE: THESE IMPLICATIONS HAVE TO DO ABOUT TARGETING PRIVATE SCHOOLS BUT NOT TARGETING SAME SET OF SCHOOLS TARGETED BY SELECTIVE PRIVATE UNIVERSITIES]
+
+[PUT THIS IN THE DISCUSSION SECTION] Finally When both private and public universities are targeting private schools, competition for these students is likely to increase.
+This could be an explanation for why many private universities are struggling to meet enrollment goals
+
+student bodies that predonominantly affluent, white student bodies.
+
+# Literature Review
+
+## Nonresident Enrollment at Public Universities
+
+We stiuate this study vis-a-vis scholarship on enrollment management behavior by public research universities and particularly the pursuit of affluent nonresident students, a population also targeted by selective private universities.
+The so-called "iron triangle" of enrollment management states that universities pursue the broad enrollment goals of access, academic profile, and revenue generation [@RN3524; @RN2772].
+Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve trade-offs with other goals.
+@RN2772[p.
+221] state that “most enrollment management policies\ldots do not advance all three objectives; instead they lead to gains in some areas and declines in others.” Scholarship argues that selective private universities prioritize academic profile and revenue generation, with funds generated from tuition and donation feeding the arms race for prestige [@RN3522; @RN1549; @RN3519].
+Historically, public research universities prioritize enrollment of high-performing state residents, often with an emphasis on social mobility for students who cannot afford private universities [@RN3608].
+However, scholarship on privatization argues the public research universities increasingly emphasizing tuition revenue and rankings and de-emphasize access for state residents [@RN1577; @RN1118].
+
+<!-- PREVIOUS PARAGRAPH
+We situate this study vis-a-vis scholarship on nonresident enrollment at public research universities, which lies within the broader literature on "privatization" [CITE].
+Against the backdrop of many states disinvesting in higher education, the privatization literature examines the ways that public universities start behaving like private universities by emphasizing revenue generation and the pursuit of prestige in research and enrollment management behaviors.
+The so-called "iron triangle" of enrollment management states that universities pursue the three broad enrollment goals of access, academic profile, and revenue generation [CITE].
+"Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve tradeoffs with other goals.
+Scholarship on privatization expressed concern that the public research universities were emphasizing tuition revenue and rankings and deemphasizing access for state residents.-->
+
+@RN3753 draw from resource dependence theory to conceptualize the relationship between state appropriations and nonresident enrollment.
+Organizations are dependent on external resources that are important for organizational survival/stability and cannot be easily replaced.
+Public universities depend on state appropriations but these funds became increasingly uncertain in the 1980s and 1990s [@RN2271].
+Resource dependence theory states that one response to resource decline or uncertainty is to seek alternative, substitute resources [CITE].
+Tuition revenue is a potential substitute for state appropriations.
+Most states cap resident tuition price, but not nonresident tuition price.
+Therefore, @RN3753 argued that public universities have a financial incentive to grow nonresident enrollment in response to declines in state appropriations.
+Analyzing panel data from 2002-03 to 2012-13, @RN3753 found that a 10% decline in state appropriations was associated with a 2.7% increase in nonresident enrollment at all public universities and a 5.0% increase in nonresident enrollment at research-extensive universities.
+
+Other studies of nonresident enrollment examine university enrollment composition.
+Using data from NPSAS 2011-12, @RN3685 show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients and are less likely to be Black or LatinX.
+Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and LatinX students.
+@RN4290 examine whether growth in the number of nonresident students causes resident enrollment to decline.
+They find that nonresident enrollment "crowds out" resident enrollment at prestigious public research universities, but not at less prestigious public research universities.
+
+How did public research universities go about attracting all these nonresident students?
+One mechanism is financial aid, a lever to increase applications and affect matriculation decisions.
+Many public research universities have developed institutional aid policies for nonresident admits, typically offering larger awards for higher achieving students [@RN3762; @RN2287; @RN1791].<!--@RN2535 shows that nonresident students are less sensitive to sticker price than resident students.
+Because nonresident prospects may be considering several options -- in-state, out-of-state, public, private -- they are sensitive to the generosity of institutional aid offers [CITE].
+For example, @RN3762 analyze the effect of a University of Iowa institutional merit aid program for nonresident admits that offered higher awards for admits with higher academic achievement.
+Regression discontinuity analyses found that the program increased the probability of enrollment, particularly for high achieving students.
+These results suggest that high-achieving nonresident students face many good opportunities and require substantial institutional aid to be convinced to enroll.
+-->
+
+Earlier in the "enrollment funnel," universities utilize marketing and recruiting interventions to attract nonresident applicants.
+One widely utilized intervention is off-campus recruiting visits by admissions counselors to local high schools.
+@RN4758 analyzed off-campus recruiting visits to public high schools by 15 public research universities.
+Recruiting visits to in-state high schools tended exhibit modest racial and socioeconomic bias.
+However, 12 of the 15 universities made more visits to out-of-state high schools than in-state high schools.
 These out-of-state visits focused on public schools in affluent, predominantly white communities.
-Additionally, most public research universities in our sample made a disproportionate number of visits to out-of-state private high schools.
-For the University of California-Berkeley, for example, 155 (43%) of the 360 out-of-state high school visits were to private high schools.
-For the University of Colorado-Boulder, 321 (36%) of the 901 out-of-state high school visits were to private high schools.
-
-<!--
-Note: The data for this book chapter will be slightly different due to using 2017-18 CCD data plus modified criteria (no longer excluding HS w/ certain school types) - but % is still similar
-
-UC Berkeley: 171 (42%) of 404 out-of-state HS visits are to private schools
-CU Boulder: 381 (38%) of 1008 out-of-state HS visits are to private schools
+@RN4934 conducted geo-spatial analyses of out-of-state recruiting visits to Los Angeles and Dallas by four public research universities.
+She found that universities engage in "recruitment redlining -- the circuitous avoidance of predominantly Black and Latinx communities along recruiting visit paths" (p.
+X).
+Although @RN4758 and @RN4934 focused on visits to public high schools, prior research has not considered visits to private schools by public research universities.
+For example, what is the scale of these visits and what are the characteristics of visited schools?
+
+## Linkages Between Private Schools and Private Universities
+
+Separate from scholarship on nonresident enrollment at public universities, scholarship from economics and sociology analyzes linkages between private schools and colleges.
+
+@RN4504<!-- use data from several national surveys to --> set the stage by describing long-term trends in private school enrollment.
+The percentage of American (elementary school) students attending private school declined from 15% in the mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
+The private school enrollment rate for high-income families and for low-income families has remained relatively stable over time at about 17% and 4%, respectively.
+The enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
+This decline was driven by shrinking Catholic school enrollment, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
+Moreover, contemporary Catholic school students tend to be more affluent compared to prior decades.
+There has been a long-term increase in private school enrollment in the South, with middle-income families increasingly attending Christian schools and high-income families increasingly attending nonsectarian schools.
+With respect to race, 11% of white students attended private school in 2013, compared to 5% of Black students, and 3% of Hispanic students.
+<!-- Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
+ However, for high income families, rates of private school enrollment do not differ substantially across race. -->
+
+A robust empirical literature<!-- from sociology and economics  --> finds that attending private school positively affects college access and college selectivity [e.g.,] [@RN4642; @RN4596; @RN4634; @RN4599].
+Scholarship from the 1980s and 1990s focused on the effects of attending Catholic school [@RN4937; @RN786; @RN4936; @RN4938].
+More recent scholarship tends to find that attending a nonsectarian private school has larger effects on college access than attending a Catholic school [@RN4935; @RN4614;@RN4625].
+
+The High School Longitudinal Survey of 2009 (HSLS) tracks the postsecondary destinations of students who were in ninth grade in 2009.
+Simple descriptive statistics are eye-opening (Author calculations).^[Analyses consist students who met the following conditions: completed the 2012 follow-up survey; obtained high school transcript data; and completed the 2016 followup survey.
+The survey weight variable used was W4W1W2W3STU.
+After weighting, these 14,020 (unweighted) students represent a population of 3.93 million U.S.
+ninth graders in 2009.
+Data on college rankings come from the 2020 U.S.
+News \& World Report *Best Colleges*.
+Data on high school control come from the HSLS school file and from the Private School Survey.] About 93% of students attended a public high school and 7% attended a private high school, including 3.6% attending a Catholic school, 1.6% attending a nonsectarian school, and 1.8% attending a Christian school.
+Of public high school students, 5.0% attending a public university ranked in the top 100 by US News and World Report (USNWR) and 1.9% attended a private university ranked in the top 100.
+Of private high school students, 10.9% attended a top 100 public university and 16.8% attended a top 100 private university.
+For Catholic school students, 12.8% attended a top 100 public university and 11.7% attended a top 100 private university, while for Christian schools these percentages were 8.2% and 8.2%, respectively.
+However, for nonsectarian private school students, 11.3% attended a top 100 public university and 39.8 percent attended a top 100 private university.
+Focusing on the institutional composition of private universities in USNWR top 100, 39.8% attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).
+
+Scholarship has been particularly interested in the relationship between attending a prestigious private school and attending an ultra selective university [@RN4647; @RN4643; @RN4647; @RN4589].
+@RN4935 acquired unprecedented data -- application files and admissions decisions linked to income tax records  -- to investigate why high income families are over-represented at "Ivy Plus" colleges.
+Conditioning on SAT and ACT scores, applications from high-income families (top 1%) received the same academic rating as applications from lower-income families.
+However, applications from high-income families received higher non-academic ratings (extracurricular activities, leadership traits) then applications from lower-income families.
+In turn, the higher non-academic ratings for high-income applicants was driven by the fact that these students tended to attend elite private high schools that devote substantial resources to teacher recommendations and guidance counselor letters.
+
+Scholarship from sociology has examined organizational connections that catalyze the flow of students between private schools and selective private colleges [@RN4640; @RN4407; @RN4321; @RN3519].
+@RN3519 provides an ethnography of the admissions office at a selective private liberal arts college.
+The College is sensitive about its position in U.S.
+News Rankings and enrollment priorities tend to focus on academic profile and revenue generation.
+@RN3519 highlights the relational function of off-campus recruiting visits, stating that "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide" (p.
+54) Therefore, during the autumn "travel season," admissions officers visit selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
+53-54) because counselors who view a college favorably will steer students to that college.
+The College tended to visit the same "feeder" schools year after year because recruiting depends on long-term relationships with high schools.
+The high schools they visited tend to be affluent schools -- in particular, private schools -- that possess the resources to host a successful visit and enroll high-achieving students who can afford tuition.
+<!-- Whereas @RN4402 highlights the effect of recruiting visits on inquiries and enrollees, findings from @RN3519 suggest that the College may have valued recruiting visits primarily as a means of maintaining relationships with guidance counselors.
+From this perspective, recruiting visits may affect outcomes such as inquiries, applications, and matriculation through their effect on high school guidance counselors.
 -->
 
-Whereas @RN4721 primarily analyzed visits to public high schools, this chapter focuses on visits to private high schools.
-More specifically, we investigate how visits to private high schools by public research universities compare to visits to private high schools by selective private universities.
-
-## Social mobility, social reproduction, and privatization
-
-The sociologist Max Weber is credited for the insight that education has a "dual character," on one hand, serving *social mobility* by redistributing access to privileged positions and, on the other, serving *social reproduction* by granting privileged families disproportionate access to the educational institutions that confer pathways to privileged positions [@RN2377].
-
-The mission of selective private colleges and universities is more squarely associated with social reproduction rather than social mobility.
-Historically, these institutions depend on patronage from philanthropic interests -- in connection with business and religious interests -- and on wealthy households who provide tuition revenue and donations [@RN4517].
-In turn, selective private institutions contribute to social reproduction by providing access to their patrons.
-The "Chetty" data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile [@RN4722; @RN4723].
-A significant caveat is that religiously affiliated universities may prioritize enrollment opportunities for students of the same faith regardless of wealth, but even here the mission is to benefit families from a particular cultural status group.
-<!-- [CITE] -->
-
-The traditional, albeit mythologized, public good mission of public research universities is tied to social mobility and development of the state [@RN2269; @RN921].
-Public research universities are designated the unique responsibility of educating the future civic, professional, and business leaders of the state.
-Quoting 19th century University of Michigan President James Angell, these institutions contribute to social mobility by providing "an uncommon education for the common man" [as cited in @RN3608, p.
-279] who could not afford tuition at elite private institutions.
-
-We argue that the recruiting behavior of colleges and universities is an indicator of organizational enrollment priorities and, in turn, the extent to which enrollment priorities serve social mobility or social reproduction.
-Recruiting visits to private high schools are consistent with the social reproduction mission of selective private universities, regardless of whether the university is targeting a particular high school because of its academic reputation, religious affiliation, or the affluence of its student body.
-By contrast, for public research universities, visits to private high schools -- particularly out-of-state schools -- are antithetical to the mission of social mobility for high-achieving, low-income state residents.
-
-Analyses of recruiting visits to private high schools can contribute novel insights about the "privatization" of public research universities.
-Within the scholarly literature on privatization, one strand of scholarship conceptualizes privatization as a process whereby declines in government funding cause public institutions to grow alternative revenue sources, particularly revenue from tuition and research commercialization [@RN4543; @RN2101].
-Of relevance to this chapter, public research universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753], who typically pay two- to three-times more than resident students.
-A second strand within the privatization literature conceptualizes privatization as a process whereby public institutions become more similar -- in terms of characteristics or behavior -- to for-profit or private non-profit organizations [@RN4543].
-A weakness of this literature is that few empirical studies analyze public institutions on a behavior associated with private institutions.
-
-Therefore, this chapter compares public research universities to selective private universities on the dimension of recruiting visits to private high schools, a behavior associated with the social reproduction orientation of selective private universities.
-Our primary goal is to learn about public research universities, using the behavior of private universities as a benchmark to develop more thoughtful insights about public research universities.
-We analyze recruiting visits made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities.
-<!-- and 12 selective private liberal arts colleges.
--->
-
-Because little is known about recruiting at private high schools by public universities, we conduct descriptive analyses that seek to identify basic patterns and relationships.
-Because a recruiting visit to the same private high school is an indicator of a relationship between two actors, we also utilize social network methods in order to compare the recruiting networks of public universities to those of private universities.
-Analyses are informed by the following three research questions:
-
-1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
-1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
-1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
-
-<!-- SHORT PARAGRAPH GIVING OUTLINE OF CHAPTER -->
-
-# What do we know about off-campus recruiting visits
-
-This section provides context for our analyses.
-First, we situate off-campus recruiting within the broader set of marketing and recruiting interventions in higher education and review what market research says about off-campus recruiting.
-Second, we review empirical scholarship from sociology that considers off-campus recruiting, emphasizing scholarship that considers the relational aspects of recruiting visits and scholarship that considers private high schools.
-
-## Situating off-campus recruiting within enrollment management
-
-The "enrollment funnel" -- depicted in Figure \@ref(fig:em-funnel) -- is a conceptual heuristic that identifies stages in the student recruitment process (prospects, inquiries, applicants, accepted applicants, and enrolled students).
-"Prospects" are "all the potential students you would want to attract to your institution" [@RN4322].
-"Inquiries" are prospects that contact the institution, including those who respond to a solicitation and those who reach out on their own.
-The enrollment management industry uses the enrollment funnel to inform marketing and recruiting interventions that target specific stages.
-Most scholarship on enrollment management focuses on the final stages of the enrollment funnel, specifically which applicants are admitted and the use of financial aid "leveraging" to convert admits to enrollees [e.g., @RN3536; @RN3544; @RN3523; @RN4131; @RN2241; @RN3564; @RN1948].
-By contrast, the enrollment management industry expends substantial resources on marketing/recruiting activities that target earlier stages of the enrollment funnel [@RN4664].
-<!--[SHOULD WE TRY TO ADD SOME CONCRETE NUMBERS ON $ SPENDING AT PARTICULAR UNIVERSITIES?]-->
-
-INSERT FIGURE \@ref(fig:em-funnel) ABOUT HERE
-
-Institutions identify undergraduate "prospects" by purchasing "student lists" -- containing contact, demographic, and academic achievement information -- from College Board, ACT, and other vendors.
-Universities control which prospects are contained within a list by filtering on criteria such as zip code, test scores, and high school GPA.
-Once prospects and inquiries are identified, they are targeted with remote and face-to-face recruiting interventions designed to solicit applications and deepen engagement.
-Remote recruiting interventions include postcards, brochures, emails, text messages, and targeted social media.
-Face-to-face recruiting interventions include on-campus visits by prospects and off-campus recruiting visits by admissions representatives to high schools, community colleges, college fairs, etc.
-Institutions utilize advertising (traditional and digital) and social media to solicit inquiries and to create positive "buzz" amongst prospects [@RN4411]<!--[CITE OTHER]-->.
-Given the rise in "stealth applicants" who do not inquire before applying (Dupaul & Harris, 2012), advertising and social media enables universities to tell their story to prospects who do not wish to be contacted.
-
-What do we know about off-campus recruiting from previous research?
-As is true for most aspects of enrollment management, much of what we know about off-campus recruiting comes from consulting firms (e.g., Ruffalo-Noel Levitz, EAB), professional associations (e.g., NACAC), and from practitioner-oriented publications.
-Market research describes off-campus recruiting visits as a means of identifying prospects and deepening engagement with prospects already being targeted through mail/email [@RN4323; @RN4402; @RN4664].
-
-@RN4402 documents the self-reported efficacy of marketing/recruiting interventions.
-For the median private 4-yr institution, off-campus visits were the second highest source of inquiries (after student list purchases), accounting for 17% of inquiries.
-Off-campus visits were tied with student list purchases as the highest source of enrollees, accounting for 18% of enrollees.
-For the median public institution, off-campus visits accounted for 19% of inquiries (second only to student list purchases) and accounted for 16% of enrollees (ranked third after stealth applicants and on-campus visits).
-
-With respect to expenditure, Table \@ref(tab:ug-recruit-budget), reproduced from @RN4664, shows the percentage of undergraduate recruitment budget allocated to different marketing and recruiting activities.^[Table drawn directly from @RN4664 Figure 9, which is based on a convenience sample of 45 four-year non-profit institutions and 21 four-year public institutions.] The average public university spent 16% of its recruiting budget on off-campus recruiting visits, compared to 12% of its budget on purchasing student lists and 17% of its budget on "prospective student communications" (e.g., mail, email, text, social media) targeting prospects and inquiries.
-An emergent trend over the past decade -- partially a response to public universities seeking nonresident students -- has been the growth of "regional recruiters" who target specific metropolitan areas in the US and abroad [@RN4021].
-These regional recruiters may be college/university employees or they may be independent contractors who live in the metropolitan area they recruit.
-
-<!-- QUESTIONS ABOUT THE RNL 2020 COST OF RECRUITING AN UNDERGRADUATE STUDENT REPORT, FIGURE 9
-
-What does "recruitment publications" include?
-what does "prospective student communications" include?
-what does "event" include? can I assume this is on-campus events only cuz "travel" is a separate category?
-what does "web services and digital advertising" include? Does this include social media?
--->
-
-## Empirical scholarship from sociology
-
-<!--
-
-A sociological case-study literature develops helpful insights about the mechanisms and functions of off-campus recruiting visits [CITE].
-
--->
-
-Empirical academic scholarship on off-campus recruiting is mostly limited to a modest number of sociological case studies, which typically analyze off-campus recruiting as part of a broader analysis of enrollment management [e.g., @RN4538; @RN4324; @RN3519; @RN4520; @RN4407].
-@RN4324 analyzes visits from the perspective of students at two racially and socioeconomically diverse public high schools.
-@RN4324 found that high school visits -- including college fairs, instant decision events, and small-group representative visits -- influenced where students applied and where they enrolled.
-This finding was strongest for first-generation students and underrepresented students of color, who often reported that "school counselors had low expectations for them and were too quick to suggest that they attend community college" (p.
-XXX).
-This trust vacuum created an opportunity for colleges because these students were drawn to colleges that connected with them and made them feel wanted.
-For example, @RN4324 describes a high-achieving, first-generation, African American student who was admitted by a highly selective liberal arts college but chose to attend a less selective college that "seemed to want him more" (p.
-XXX).
-By contrast, affluent students with college-educated parents were less taken by such overtures and more concerned with college prestige.
-
-@RN3519, in an ethnography of the admissions office at a selective private liberal arts college, highlights the relational function of off-campus recruiting visits.
-Stevens [-@RN3519, p.
-54] states that "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide." Therefore, during the autumn "travel season," admissions officers visit selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
-53-54).
-The College tended to visit the same "feeder" schools year after year because recruiting depends on long-term relationships with high schools.
-The high schools they visited tend to be affluent schools -- in particular, private schools -- that enroll high-achieving students who can afford tuition and have the resources and motivation to host a successful visit.
-Whereas @RN4402 highlights the effect of recruiting visits on inquiries and enrollees, findings from @RN3519 suggest that the College may have valued recruiting visits primarily as a means of maintaining relationships with guidance counselors.
-From this perspective, recruiting visits may affect outcomes such as inquiries, applications, and matriculation through their effect on high school guidance counselors.
-The logic is that a guidance counselor who views a college favorably will steer students to the college.
-
-<!--
-
-@RN3519 and Khan [-@RN4321;-@RN4407] are centrally important to our study because they analyze relationships between college admissions counselors and high school guidance counselors.
-
--->
-
-Although not about recruiting visits per se, Khan [-@RN4321;-@RN4407] is centrally important for our study because he lays out a conceptual explanation of why colleges and private high schools develop relationships with one another (i.e., what is each trying to obtain from the other).
 @RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p.
 98).
-The answer begins by considering the goals of colleges, which are represented by admissions officers, and the goals of private high schools, which are represented by guidance counselors.
-Colleges want high-achieving students who can pay tuition and donate.
-They want low acceptance and high yield rates, which are important for rankings.
-Colleges also want a class composed of "interesting characters" whose curricular and extracurricular strengths meet the needs of important campus constituents (e.g., academic majors, the athletic department, clubs, etc.).
-Elite private high schools want to send _all_ students to the best college possible.
-Here, high school guidance counselors face "the pressure of making sure their school seems worth it – that \ldots paying some $40,000+, really does aid students in the college process" [@RN4321, p.
-105].
-
-The challenge faced by high school counselors at elite private schools is that "some of these students are slightly better than others.
-These students will likely get into more than one school -- but they can only attend one.
-And this will lower the chances of your 'second-best' students getting into top schools" [@RN4407, pp.
-173-174].
-"Luckily," Khan [-@RN4321, p.
-105] writes, "the problem for elite boarding schools matches up quite nicely with the problem faced by elite colleges." That is, although college admissions officers receive applications from many outstanding students,
-
-> These outstanding students will also be  outstanding to Princeton, Yale, Stanford, and everywhere else.
-How do you know the ones you pick will attend your school?
-You can't quite trust applicants, as they are all likely to tell you how much they want to go to your school.
-And if students you accept go somewhere else, there's not much you can do.
-But you can get better information -- information you want -- from their high school.
-And you can reward that school for good information and sanction it for bad information [@RN4407, p.
-173].
-
-<!--
-
- And you can reward that school for good information and sanction it for bad information [@RN4407, p. 173].
-
--->
-
-This desire by colleges for trustworthy information about applicant intentions creates an opportunity for high school counselors to advocate on behalf of their students.
-This opportunity depends on guidance counselors having personal relationships with university admissions offices and on having small enough caseloads to advocate for each student individually.
-
-To explain how high school counselors capitalize on this opportunity, @RN4407 describes two hypothetical students -- Susan and Billy -- who both apply to Harvard and Yale.
-Susan is a shoo-in at both universities, but wants to attend Harvard.
-Billy has a weaker academic record than most Ivy League students, but has strong extracurricular activities.
-The guidance counselor tells Harvard that Susan wants to attend Harvard.
-Next, he informs Yale that Susan will choose Harvard, but Billy loves Yale and has great "character" and extracurricular activities.
-In the end, Harvard rejects Billy and accepts Susan, thereby, decreasing acceptance rate and increasing yield.
-Yale rejects Susan and accepts Billy, thereby, also decreasing acceptance rate and increasing yield.
-
-The horsetrading described by @RN4407 depends on a relationship where the college can trust statements made by the high school counselor and vice-versa.
-This relationship is the product of repeated interactions over many years.
-A high school that makes false statements about applicant intentions faces consequences.
-The college "might stop taking these telephone calls and ignore the information provided.
-They may even start accepting fewer students from the school, thinking it is less than an honest place" [@RN4321, p.
-106].
-Because the college and the high school are mutually dependent, however, both "have an incentive to continue with a strong, honest relationship" [@RN4321, p.
-106].
-Although, such horsetrading may be less pervasive now than it was in prior decades and may be less common at non-elite private schools.
-Additionally, college admissions officers from public universities likely have less authority to engage in these tacit negotiations because admissions criteria at public universities face greater public scrutiny than admissions criteria at private colleges and universities.
-
-### Visits as an indicator of a social relation
-
-@RN3519 and Khan [-@RN4321;-@RN4407] suggest that strong relationships are mutually important for the college and for the private high school.
-Strong relationships enable colleges and schools to negotiate and send trustworthy information to one another.
-Without a strong relationship, it is unlikely that a college admissions counselor will "take the call" of a high school guidance counselor [@RN4321; @RN4407].
-Even in the absence of the horsetrading described by @RN4407, relationships enable the college admissions counselor and the high school guidance counselor to tell one another "their story" and relay that story to constituents [@RN3519].
-The college admissions counselor explains why the college/university is a "special place" that high school students should want to attend [@RN3519].
-The guidance counselor explains why the high school is a special place, that even students with lower grades have outstanding extracurricular strengths that will benefit the college [@RN4321].
-
-The presence of a recruiting visit between a college and a private high school is an indicator that the college and the high school have a relationship.
-From an empirical perspective, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
-From a logical perspective, we argue that, first, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school.
-Second, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
-Third, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls).
-
-Conceptualizing a recruiting visit as an indicator of a relationship between a college and a high school motivates the use of social network methods, which analyze the network defined by "network ties" (i.e., visits) between actors (colleges and high schools).
-Prior research has not used social network methods to analyze recruiting visits from colleges to high schools.
-Analyzing the network of recruiting visits to high schools enables us to investigate the extent to which public research universities are visiting similar sets of private high schools as private colleges and universities, and also the extent to which they are visiting the same private high schools.
-In turn, we hope these analyses yield novel insights to scholarship on the privatization of public higher education.
-
-# Social network analysis concepts
-
-Having conceptualized a recruiting visit as an indicator of a social relation, this section introduces basic concepts from social network analysis and motivates the research questions that guide empirical analyses.
+Guidance counselors at these schools capitalize on the fact that selective colleges are concerned about their acceptance and yield rates.
+Therefore, admissions offices value credible information about which applicants will accept or decline an admissions offer.
+This desire for intelligence creates an opportunity for high school counselors to advocate on behalf of their students.
+Guidance counselors tell admissions counselors which highly-sought-after applicants are likely to decline an offer, while lobbying for an applicant who has relatively weak academic credentials but is sure to matriculate and has "character" and extracurricular activities the university values.
+@RN4321 states that such horsetrading depends on guidance counselors having sufficiently small caseloads to advocate for each student individually and on having personal relationships with university admissions officers.
+While @RN3519 and @RN4321 highlight the importance of social networks between private schools and private universities, prior research has not analyzed the social networks that emerge from off-campus visits.
+
+Additionally, scholarship on linkages between private high schools and private universities focuses on elite high schools and ultra selective universities [@RN1565; @RN4647; @RN4935; @RN4321].
+With the exception of the single-institution ethnography by @RN3519, we know less about linkages between private schools and private universities that are selective but not elite.
+These merely-selective universities are self-conscious about their reputation, and have fewer resources and weaker student demand compared to Ivy Plus universities.
+Analyses of off-campus recruiting visits provides novel insights about the schools and student populations these institutions target.
+
+## Synthesis
+
+We argue that a recruiting visit from a university to a private high school is an indicator of a social relationship.
+Empirically, @RN3519 finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school.
+Logically, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school.
+Similarly, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students.
+Moreover, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls) between the organizations.
+For example, @RN4895 reports that "calling after visits" was the most effective strategy for high school guidance counselor outreach for both private universities and public universities.
+Conceptualizing a recruiting visit as an indicator of a relationship between a college and a high school motivates the use of social network methods, which analyze the network defined by "network ties" (i.e., visits) between actors (universities and schools).
+
+Although the literature on nonresident enrollment developed in isolation from the literature on private school to private university linkages, both phenomena are part of a broader story about the changing nature of school segregation and the competition for affluent, traditional college students.
+Drawing from resource dependence theory, as public research universities become more reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices.
+While selective universities have long relied on enrollment from private schools [@RN3519; @RN4640], the pursuit of out-of-state private school students by public research universities is a recent phenomenon and thus an encroachment on the historic territory of selective private universities and in-state flagships.
+Speaking about this competition, an enrollment management consultant said, "'Everybody wants to go to the magic island of full pay students, but it’s rapidly shrinking real estate'" [@RN4911].
+By analyzing the network of recruiting visits, we show whether public research universities and selective private universities are competing for students at similar ets of private schools.
+This may be direct competition for the same student or vying to be the second choice for students who are rejected by their top choice.
+
+Private schools tend to be whiter and more racially segregated than public schools [CITE].
+Over the past three decades, middle-income enrollment at Catholic schools has declined and private school students have become more affluent.
+In the South, private school enrollment has grown as a consequence of "white flight" from public schools facing desegregation orders [@RN4504].
+Thus, in recruiting from private schools, universities may be targeting student bodies that are more affluent and racially homogeneous than public schools.
+We investigate the characteristics -- including geographic region and racial composition -- of private schools being targeted by university admissions officers because these characteristics have downstream implications for the racial composition of university campuses.
+
+# Methods
+
+# Data and sample
+
+This manuscript draws from a broader project in which we collected data about off-campus recruiting visits made during the 2017 calendar year by a convenience sample of colleges and universities.
+For universities in our data collection sample, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits.
+For institutions that posted such pages, we scraped the pages once per week throughout 2017.
+Web-scraping was conducted using the Python programming language [STATE WHICH PACKAGE?
+AND/OR SHOW LINK TO A SAMPLE SCRIPT?].
+Many universities in our data collection sample only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
+These institutions were excluded from the analysis sample.
+
+For public universities in our analysis sample, we assessed data quality of the web-scraped data by asking the enrollment/admissions office for these data.
+If a university denied or ignored our request, we issued a formal public records request.
+Of the 15 public universities analyzed in this study, we received requested data from 11 universities.
+For these 11 universities, web-scraped data was very similar to publicly requested data.
+For universities that sent us data, the analyses below use “requested” rather than “scraped” data because requested “requested” data tended to have more events.
+Broad patterns were similar across requested data versus scraped data, and results based on scraped data are available on request.
+@RN4758 describe data quality checks in greater detail.
+
+The data collection sample for the broader project consisted of: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), and all private universities in the top 100 of U.S.
+News and World Report National Universities rankings (N=58), and all private colleges in the top 50 of U.S.
+News and World Report Liberal Arts Colleges rankings (N=47).
+The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection.
+This article excludes private liberal arts colleges because having a third institutional type would substantially increase article length.
+The final analysis sample for this article consists of 15 public research universities and 14 private research universities that we believed posted all varieties of off-campus recruiting events on their admissions website.
+For these universities, we analyze recruiting visits to private high schools that meet the following criteria: enrolls at least 10 12th grade students, is not primarily a virtual school, and is located in the 50 U.S.
+states, the District of Columbia, or land regulated by the Bureau of Indian Affairs is included in our analysis.
+
+Our analysis sample of universities should be considered a convenience sample.
+Table \@ref(tab:sample-characteristics) shows selected characteristics for the universities in our analysis sample.
+Appendix Table X [CRYSTAL ADD] shows how our sample of universities compares to the populations they were drawn from.
+[ONE SENTENCE ABOUT REPRESENTATIVENESS COMPARED TO POPULATION]
+
+INSERT TABLE \@ref(tab:sample-characteristics) ABOUT HERE
+
+Analyses utilized several secondary data sources.
+The data on university characteristics come from the 2017 Integrated Postsecondary Education Data System (IPEDS) and 2020 Best Colleges ranking by U.S.
+News & World Report.
+For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.^[For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small amount of schools.]
+
+## Constructing Social Networks
 
@@
 
-Whereas "one-mode" networks consist of vertices of the same "type" (e.g., in a publication network, each vertex is an author), "two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
-For example, an actor-movie network consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
+**Two-mode networks**.
+"Two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type of actor/entity [@RN2457].
+For example, an actor-movie network -- for example, the so-called "Six Degrees of Kevin Bacon" -- consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
 The most commonly analyzed two-mode network in social networks literature is a corporate board-director network  [e.g., @RN4663].
 These networks consist of directors (mode 1) and organizational boards (mode 2), and a particular director shares an edge with a particular organizational board if they sit on that board.
-Similarly, our recruiting visit data form a two-mode network, consisting of private high schools (mode 1) and colleges (mode 2).
-An off-campus recruiting visit from a college/university to a private high school is the "edge" that connects two particular vertices.
-In this network, edges can only occur between vertices of a different type; that is, a college can visit a high school, but colleges cannot visit other colleges and high schools cannot receive visits from other high schools.
-
+
+Data about off-campus recruiting visits from universities to high schools form a two-mode network.
+The vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visit made between the two.
+High school $i$ shares an edge with university $j$ if high school $i$ receives at least one visit from university $j$.
+Visits can only occur between a school-university pair (not a school-school pair or a university-university pair).
+This (weighted) network can be represented as a school-by-university matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 universities) in which matrix cell $a_{i,j}$ identifies the number of visits  high school $i$ received from university $j$.
+REFER TO APPENDIX FIGURE THAT SHOWS ENTIRE 2-MODE NETWORK [CRYSTAL ADD FIGURE USING function plot_2mode_graph from network_recruiting_analysis.R]
+
+**Transforming two-mode to one-mode**.
 To reduce complexity, two-mode network graphs are often analyzed as one-mode networks [@RN2457;@RN4663].
-Our two-mode college-school network can be transformed into a one-mode college network in which each vertex is a college/university and two colleges share an edge if both colleges visited at least one high school in common.
-The *weight* of an edge indicates the number of high schools that both colleges visited.
-For example, if there are 200 private high schools that received a visit from both Notre Dame and Villanova, the weight of the edge between Notre Dame and Villanova is 200.
-
-## RQ1: Degree centrality
-
-<!-- 
-In social network analysis, *centrality* is a notion of how important or prominent or "in the middle of things"
-*centrality* refers to the importance or prominence of an actor/vertex in a social network [CITE].
--->
-
-In social network analysis, *centrality* refers to the importance or prominence or "being in the middle of things" of an actor/vertex in a social network.<!--[CITE]--> Many alternative measures of centrality have been developed.
+Our two-mode university-school network can be transformed into a one-mode university network in which each vertex is a university.
+Universities $i$ and $j$ share an edge if both universities visit at least one high school in common.
+Cell $a_{i,j}$ of the university-by-university matrix $A$ indicates the number of high schools that both universities visited.
+Cell $a_{i,j}$ is referred to as the *weight* of the edge between university $i$ and university $j$.
+For example, if there are 200 private high schools that received a visit from both Notre Dame (university $i$) and Villanova (university $j$), the weight of the edge between Notre Dame and Villanova is 200 ($a_{i,j}=200$).
+Following this approach we created a one-mode university matrix.
+
+We also created a one-mode high school network in which each vertex is a private high school.
+Private high schools $i$ and $j$ share an edge if at least one university visits both high schools.
+Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of universities that visited both school $i$ and school $j$.
+
+## Analyses
+
+Analyses consist of simple descriptive statistics and descriptive social network analyses. All analyses were conducted using *R* and network analyses were conducted using the *igraph* package.
+
+**RQ1: Degree centrality**.
+In social network analysis, *centrality* refers to the importance or prominence or "being in the middle of things" of an actor/vertex in a social network [@RN4725].<!--[CITE]--> Many alternative measures of centrality have been developed.
 All measures agree that centrality is an actor/vertex-level construct (e.g., each college in our network will have a centrality value, regardless of which centrality measure we use).
@@
 The simplest measure of centrality, *degree centrality* measures the number of edges directly connected to a vertex.
-For each college in our two-mode network, degree centrality is simply the number of different private high schools visited by the college.
+Social network theory conceptualizes degree centrality as a measure of "local" centrality, capturing the number of direct connections for each actor/vertex.
+For each university in our two-mode network, degree centrality is simply the number of different private high schools visited by the college.
 For each high school in our network, degree centrality is the number of colleges in our network that visited the high school.
-Social network theory conceptualizes degree centrality as a measure of "local" centrality, capturing the number of direct connections for each actor/vertex.
 For our empirical context, we conceive of degree centrality as a measure of scale of the number of private high schools a college visits and, equivalently, the number of private high schools we observe having a social relation with each college.
-Given that we conceptualize visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges/universities, we are interested in comparing how scale differs between public and private colleges/universities.
-This interest motivates research question 1, "How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?" We answer this research question by comparing degree centrality across universities.
+
+Research question 1 states, "How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?" We answer this research question by comparing degree centrality across universities, both within university type (public vs.
+private) and between university type.
+In order to discern the relative emphasis on private schools by each university, we also compare the number of recruiting visits to private schools to the number of visits to public schools.
 
@@
 Degree is a limited measure of centrality in that it only identifies direct connections.
-By contrast, *k-path centrality* measures the extent to which an actor/vertex is indirectly connected to others, *betweenness centrality* measures the extent to which a vertex is an intermediary between otherwise disconnected groups of actors, and *eigenvector centrality* measures the extent to which a vertex is connected to highly-connected others.
-Betweenness centrality tends to be relevant for empirical contexts (e.g., which manager gets credit for an idea) where an actor who occupies a position between groups can benefit by being a broker of information/ideas [@RN975].
+By contrast, *k-path centrality* measures the extent to which an actor/vertex is indirectly connected to others, *betweenness centrality* measures the extent to which a vertex is an intermediary between otherwise disconnected groups of actors, and *eigenvector centrality* measures the extent to which a vertex is connected to highly-connected others [@RN4725].
+Betweenness centrality tends to be relevant for empirical contexts (e.g., which manager gets credit for an idea) where an actor who occupies a position between groups can benefit by being a broker of information/ideas [@RN975; @RN4648].
 By contrast, this chapter is more concerned with whether a particular college tends to have indirect connections with some colleges but not others, and what is the subset of high schools this group of colleges tends to visit.
-Research question 3, motivated below, explores these ideas.
-
-## RQ2: Ego networks and homophily
-
-Because the data structure of networks is complicated, a useful first step is to analyze "ego networks" rather than the entire social network.
+Research question 2, motivated below, explores these ideas.
+
+**RQ2: Network similarity and community detection**.
+We are interested in similarities and differences in the recruiting networks of the public research universities and selective private universities in our sample.
+This interest motivates research question 3, "to what extent do public research universities and private universities visit overlapping sets of private high schools?"
+
+Following prior scholarship on two-mode networks [@RN4677; @RN4725], we address RQ3 by simultaneously graphing the one-mode university network and categorizing universities into distinct communities that have similar recruiting networks.
+In the resulting graph, vertices (universities) that share many connections are located close together and vertices that are "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph.
+Additionally, cluster analysis is used to identify vertices that share common structure, based purely on patterns of network ties, and vertices are assigned colors based on membership in a particular group.
+
+**RQ3: Ego networks and homophily**.
+Because the data structure of networks is complicated, it is often illuminating to analyze "ego networks" rather than the entire social network.
 An "ego" is a single "focal" node (e.g., The University of Notre Dame).
-An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" (p.
-XXX)<!-- [from http://www.analytictech.com/networks/egonet.htm#:~:text=Ego%20networks%20consist%20of%20a,form%20The%20human%20social%20network ]-->.
-For example, the University of Notre Dame ego network consists of all private high schools that received at least one visit from Notre Dame.
-Additionally, for each high school visited by Notre Dame, the ego network may include all colleges/universities in our sample that also visited the high school.
-This chapter analyzes recruiting visits to private high schools by 41 colleges and universities, which we can think of as 41 ego networks.
+An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" [@RN4953].
+An ego network of order 1 consists of the alters that are directly tied to the ego.
+The order 1 ego network for the University of Notre Dame consists of all private high schools that received at least one visit from Notre Dame.
+The order 2 ego network consists of all private schools that visited Notre Dame and all universities that visited the private high schools visited by Notre Dame.
+Figure \@ref(fig:nd-religion) shows the order 2 ego network for Notre Dame, with vertices colored by religious affiliation.
+Universities that are closer to Notre Dame visit more private high schools in common.
+[CRYSTAL - FIX ND GRAPH PLEASE]
+
+INSERT FIGURE \@ref(fig:nd-religion)
+
+Research question 3 asks, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by private universities?" To answer this question, we can think of the 15 public research universities and 14 selective private universities, which we can think of as 29 ego networks.
 
@@
 First, prior scholarship suggests that private colleges and private high schools are more likely to have a relationship when they share common ideologies or view themselves as belonging to the same echelon [@RN3519; @RN4321;@RN4407].
-Second, with respect to our substantive interest in the behavior of public research universities, the characteristics of visited private high schools have consequences for subsequent enrollment compositions of public research universities.
-Therefore, we are interested in whether universities tend to visit high schools that are similar to them on certain characteristics.
-Additionally, we are interested in whether public research universities favor high schools with certain characteristics, independent of homophily.
-These interests motivate research question 2, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by private universities?"
-
-Decisions about which private school characteristics to analyze were informed by prior research [e.g., @RN4724; @RN4504; @RN4321; @RN3519; @RN4588].
-In particular, @RN4504 used data from several national surveys to analyze long-term trends in private school enrollment by family income.
-The percentage of American (elementary school) students attending private school declined from 15% in the mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
-With respect to family income, the private school enrollment rate of high-income families (around 17%) and low-income families (around 4%) remained stable over time, but the enrollment rate for middle-income families declined from 12% in 1968 to 6% in 2013.
-These declines were substantially driven by declines in the number of students attending Catholic schools, which represented 89% of private school enrollment in 1965 and 42% of enrollment in 2013.
-Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
-With respect to race, in 2013, 11% of white students attended private school compared to 5% of Black students, and 3% of Hispanic students.
-However, for high income families, rates of private school enrollment do not differ substantially across race.
-In the South, there has been a long-term increase in private school enrollment, driven by growing enrollment in Christian private schools by middle-income families and growing enrollment in nonsectarian private schools by high-income families.
-
-Based on these findings and logical argument (and also data limitations), our analyses focus on the following private school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
+Second, similar to the colloquialism 'you are what you eat,' the characteristics of visited private high schools have subsequent consequences for the the enrollment composition of universities.
+
+Our analyses focus on the following private school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
+Decisions about which private school characteristics to analyze were informed by logical argument and by prior research [e.g., @RN4724; @RN4504; @RN4321; @RN3519; @RN4588].
 We analyze geographic region because, for most colleges and universities, enrollment demand is likely to be stronger at high schools in the same geographic region, but nationally prestigious colleges and universities may experience high demand throughout the country.
@@
 Racial composition is of substantive interest because the racial composition of visited high schools has consequences for the racial composition of colleges and universities.
-Given our interests in social reproduction versus social mobility, we would also analyze tuition price and household income, but these data are not available for private high schools.
-
-## RQ3: Network similarity and community detection
-
-This chapter conceptualizes recruiting visits to private high schools as a behavior consistent with the social reproduction orientation of selective private colleges and universities.
-We are interested in how similar the recruiting networks of public research universities are to those of private colleges and universities, thereby motivating research question 3, "To what extent do public research universities and private universities visit overlapping sets of private high schools?"
-
-We address RQ3 by graphing the recruiting network and by identifying "clusters" of universities that have similar recruiting networks.
-First, network graphs show vertices (e.g., universities) as circles, with vertices that share many connections located close together and vertices that are very "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph.
-In addition to network graphs, network scholarship often uses cluster analysis methodologies to identify vertices that share common structure, based purely on patterns of network ties.
-
-# Data and methods
-
-Our broader project collected data on off-campus recruiting visits made by a convenience sample of colleges and universities during the 2017 calendar year.
-The data collection sample comes from two different lists of postsecondary institutions: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), and all private universities in the top 100 of U.S.
+We would also like to analyze tuition price and household income, but these data are not available for private high schools.
+
+## Limitations
+
+This article faces several limitations.
+First, our data collection sample consisted of public research-extensive universities as defined by the 2000 Carnegie Classification (N=102) and all private universities in the top 100 of U.S.
 News and World Report National Universities rankings (N=58).
-<!-- and all private colleges in the top 50 of U.S.
-News and World Report Liberal Arts Colleges rankings (N=47).-->For each of these institutions, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits.
-For institutions that posted such pages, we scraped the pages once per week throughout 2017.
-Many colleges and universities only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
-These institutions are excluded from the analyses.
-Our final analysis sample consists of 15 public research universities and 14 private research universities.
-<!--12 private liberal arts colleges [MAYBE ADD TABLE/FIGURE OR APPENDIX TABLE/FIGURE ON CHARACTERISTICS OF INSTITUTIONS IN OUR SAMPLE?]-->
-
-INSERT TABLE \@ref(tab:sample-characteristics) ABOUT HERE
-
-Table \@ref(tab:sample-characteristics) shows selected characteristics for the universities in our analysis sample.
-Given that we collected recruiting data for private universities ranked in the top 100 of U.S.
-News and World Report, one concern is whether it makes sense to compare public research universities not ranked in the top 100 to private universities ranked in the top 100.
+Making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities.
+The process we used to define the data collection sample yielded a sample of public research universities with lower USNWR rankings than the analysis sample of selective private universities.
 However, the columns in Table \@ref(tab:sample-characteristics) for 25th and 75th percentile SAT score of enrolled freshmen suggest that private universities ranked lower than 75 have test score ranges that are fairly similar to public research universities not ranked in the top 100.
-The five public research universities ranked 124 or below have score ranges that are modestly lower, particularly the University of Nebraska-Lincoln, but remain comparable to private universities ranked 75 to 100.
-One exception is that Stevens Institute of Technology (rank 80) has substantially higher test scores.
-
-The data on university characteristics come from the 2017 Integrated Postsecondary Education Data System (IPEDS) and 2020 Best Colleges ranking by U.S.
-News & World Report.
-For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.^[For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small amount of schools.] Only high schools that enroll at least 10 12th grade students, is not primarily a virtual school, and is located in the 50 U.S.
-states, the District of Columbia, or land regulated by the Bureau of Indian Affairs is included in our analysis.
+
+A related limitation is that analysis sample consists of the subset of universities from the data collection sample that we believe posted all off-campus recruiting visits on their admissions website.
+This process for defining the analysis sample raises two concerns.
+First, including universities based on the completeness of recruiting events on their admissions website may yield an analysis sample that conducts more off-campus recruiting visits than the majority of the sample.
+Second -- and more broadly -- because our analysis sample is a convenience sample rather than a random sample, we cannot make inferences about the underlying populations of interest.
+This is an external validity concern.
+That said, we conceive of our research design as an exploratory comparative case study rather than a Large-N research design [@RN4116; @RN4011].
+From this perspective, we identify important variation in recruiting behavior but we cannot make strong claims about the prevalence of observed behaviors in the population.
 
@@
 
-## RQ2: Characteristics of visited schools
-
-Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privhs-pubhs) address research question 2, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?"
-
-Figure \@ref(fig:region-pubu-privu) shows the geographic region -- Northeast, Midwest, South, and West -- of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel).
-Scholarship on the relationship between geographic proximity and student demand tends to find that nationally prestigious universities enjoy strong demand across the nation, while less prestigious universities rely primarily on demand from students located nearby [e.g., @RN2133].
-The visit patterns for private universities are consistent with this finding; less prestigious universities tended to focus on private high schools in their home region, while more prestigious universities tended to visit many private high schools outside their home region.
-Similarly, scholarship on student demand for out-of-state public universities finds that most public universities rely on demand from out-of-state students living in nearby states [@RN2536; @RN2535; @RN2546].
-Most public research universities in our sample visited a disproportionate number of private high schools in their home geographic region.
-UC-Berkeley and CU Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.
-
-INSERT FIGURE \@ref(fig:region-pubu-privu) ABOUT HERE
-
-In the universe of all private high schools (top row of Figure \@ref(fig:region-pubu-privu)), there are more schools located in the South than any other geographic region, consistent with the finding from @RN4504 about the long-term growth in private school enrollment in the South.
-Universities not located in the South tended to visit more private high schools in the South than any other region, except their home region.
-This finding emerged for both the public universities and private universities in our sample.
-
-Figure \@ref(fig:religion-pubu-privu) shows the religious affiliation -- Catholic, Christian, Nonsectarian, and Other -- of visited private high schools.
-The results for selective private universities (bottom panel) follow our expectations: Nonsectarian universities tended to visit a higher proportion of nonsectarian private high schools; Catholic universities visited a higher proportion of Catholic high schools; and Christian universities tended to visit a relatively higher share of Christian high schools.
-
-INSERT FIGURE \@ref(fig:religion-pubu-privu) ABOUT HERE
-
-Results for public research universities (top panel) are more interesting.
-Despite being nonsectarian, the majority of public research universities visited a high share of religiously affiliated private high schools, particularly Catholic schools.
-Surprisingly, Catholic schools represented at least 40% of private high school visits for `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'public') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample.
-By contrast, Catholic schools represented at least 40% of visits for only `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'private') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample (the four Catholic universities and also Texas Christian University and Stevens Institute of Technology).
-For public research universities, the emphasis on visiting Catholic and Christian high schools rather than nonsectarian private high schools tended to be stronger at less prestigious institutions.
-
-Figure \@ref(fig:rank-pubu-privu) shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools.
-For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visited a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.
-A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.
-
-INSERT FIGURE \@ref(fig:rank-pubu-privu) ABOUT HERE
-
-A similar pattern emerged for the public research universities in our sample; more highly ranked universities tended to visit a higher share of highly rated private high schools than lower ranked universities.
-In comparison to the private universities in our sample, the public universities in our sample tended to visit a higher share of private high schools that were not highly rated.
-To a great extent, this finding is merely a consequence of our sampling strategy; we attempted to collect recruiting visit data from all public research universities but we only collected recruiting visit data from private universities ranked in the top 100 of U.S.
-News and World Report.
-That said, the finding that public research universities visited a large share of low-rated private high schools is consistent with the idea that many public research universities visit private high schools in search of full-pay students rather than academic superstars.
-
-Figure \@ref(fig:enroll-pubu-privu) shows the 12th grade enrollment of visited private high schools.
-Compared to the universe of private high schools, the universities in our sample tended to visit schools that enrolled more 12th graders.
-Generally, the findings were pretty similar across public and private universities; for most universities, more than half of private school visits were to schools that enrolled at least 100 12th graders.
-However, public universities tended to visit a slightly larger share of high schools with fewer than 50 12th graders and private universities tended to visit a higher share of high schools with 12th grade enrollment of 50-100.
-
-INSERT FIGURES \@ref(fig:enroll-pubu-privu) AND \@ref(fig:enroll-pubu-privhs-pubhs) ABOUT HERE
-
-Figure \@ref(fig:enroll-pubu-privhs-pubhs) shows the 12th grade enrollment of visited private high schools as well as the 12th grade enrollment of visited public high schools for the public research universities in our sample.
-As seen, a large majority of public high school visits for all 15 universities were to schools with more than 150 12th graders enrolled (bottom panel).
-By contrast, most of the visited private schools tended to have fewer than 150 12th graders enrolled.
-Although this is somewhat to be expected, as public high schools tend to be larger in size than private schools (top rows of Figure \@ref(fig:enroll-pubu-privhs-pubhs)), there still appears to be a disproportionate amount of smaller private high schools visited compared to smaller public high schools.
-This suggests that the public universities in our sample were willing to take the time to visit private schools, even when they enroll far fewer 12th graders.
-
-Figure \@ref(fig:race-pubu-privu) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited private high schools.
-Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups.
-For over 65%<!--0.6632124--> of schools in the universe of private high schools (top row of Figure \@ref(fig:race-pubu-privu)), Black/Latinx/Native students comprise less than 20% of enrolled students.
-Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
-Figure \@ref(fig:race-pubu-privu) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
-For public universities, exceptions to this finding were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.
-For private universities, Marquette was the only exception to this finding.
-
-INSERT FIGURE \@ref(fig:race-pubu-privu) ABOUT HERE
-
-Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495].
-Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students [@RN4724].
-Therefore, universities may visit predominantly white private high schools in search of non-white students.
-One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.
-
-INSERT FIGURE \@ref(fig:race-pubu-privhs-pubhs) ABOUT HERE
-
-Figure \@ref(fig:race-pubu-privhs-pubhs) compares the racial composition of private high schools visited by public research universities to the racial composition of public high schools visited by these universities.
-Looking at the universe of high schools (top rows of Figure \@ref(fig:race-pubu-privhs-pubhs)), we see that public high schools tend to be more racially diverse than private schools.
-This is reflected in the racial composition of visited schools as well, where the set of visited public high schools generally enroll more Black/Latinx/Native students than the visited private schools for the public research universities in our sample.
-Unfortunately though, a majority of these public universities tended to visit private high schools at a higher rate than public high schools, as seen earlier in Figure \@ref(fig:actual-proportional-pubu).
-This disproportionate emphasis on private school visits may shift the racial composition of public universities away from Black/Latinx/Native students.
-
 ## RQ3: Overlapping network structure
@@
 
+## RQ3: Characteristics of visited schools
+
+Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?"
+
+Figure \@ref(fig:region-pubu-privu) shows the geographic region -- Northeast, Midwest, South, and West -- of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel).
+Scholarship on the relationship between geographic proximity and student demand tends to find that nationally prestigious universities enjoy strong demand across the nation, while less prestigious universities rely primarily on demand from students located nearby [e.g., @RN2133].
+The visit patterns for private universities are consistent with this finding; less prestigious universities tended to focus on private high schools in their home region, while more prestigious universities tended to visit many private high schools outside their home region.
+Similarly, scholarship on student demand for out-of-state public universities finds that most public universities rely on demand from out-of-state students living in nearby states [@RN2536; @RN2535; @RN2546].
+Most public research universities in our sample visited a disproportionate number of private high schools in their home geographic region.
+UC-Berkeley and CU Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.
+
+INSERT FIGURE \@ref(fig:region-pubu-privu) ABOUT HERE
+
+In the universe of all private high schools (top row of Figure \@ref(fig:region-pubu-privu)), there are more schools located in the South than any other geographic region, consistent with the finding from @RN4504 about the long-term growth in private school enrollment in the South.
+Universities not located in the South tended to visit more private high schools in the South than any other region, except their home region.
+This finding emerged for both the public universities and private universities in our sample.
+
+Figure \@ref(fig:religion-pubu-privu) shows the religious affiliation -- Catholic, Christian, Nonsectarian, and Other -- of visited private high schools.
+The results for selective private universities (bottom panel) follow our expectations: Nonsectarian universities tended to visit a higher proportion of nonsectarian private high schools; Catholic universities visited a higher proportion of Catholic high schools; and Christian universities tended to visit a relatively higher share of Christian high schools.
+
+INSERT FIGURE \@ref(fig:religion-pubu-privu) ABOUT HERE
+
+Results for public research universities (top panel) are more interesting.
+Despite being nonsectarian, the majority of public research universities visited a high share of religiously affiliated private high schools, particularly Catholic schools.
+Surprisingly, Catholic schools represented at least 40% of private high school visits for `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'public') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample.
+By contrast, Catholic schools represented at least 40% of visits for only `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'private') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample (the four Catholic universities and also Texas Christian University and Stevens Institute of Technology).
+For public research universities, the emphasis on visiting Catholic and Christian high schools rather than nonsectarian private high schools tended to be stronger at less prestigious institutions.
+
+Figure \@ref(fig:rank-pubu-privu) shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools.
+For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visited a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.
+A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.
+
+INSERT FIGURE \@ref(fig:rank-pubu-privu) ABOUT HERE
+
+A similar pattern emerged for the public research universities in our sample; more highly ranked universities tended to visit a higher share of highly rated private high schools than lower ranked universities.
+In comparison to the private universities in our sample, the public universities in our sample tended to visit a higher share of private high schools that were not highly rated.
+To a great extent, this finding is merely a consequence of our sampling strategy; we attempted to collect recruiting visit data from all public research universities but we only collected recruiting visit data from private universities ranked in the top 100 of U.S.
+News and World Report.
+That said, the finding that public research universities visited a large share of low-rated private high schools is consistent with the idea that many public research universities visit private high schools in search of full-pay students rather than academic superstars.
+
+Figure \@ref(fig:enroll-pubu-privu) shows the 12th grade enrollment of visited private high schools.
+Compared to the universe of private high schools, the universities in our sample tended to visit schools that enrolled more 12th graders.
+Generally, the findings were pretty similar across public and private universities; for most universities, more than half of private school visits were to schools that enrolled at least 100 12th graders.
+However, public universities tended to visit a slightly larger share of high schools with fewer than 50 12th graders and private universities tended to visit a higher share of high schools with 12th grade enrollment of 50-100.
+
+INSERT FIGURES \@ref(fig:enroll-pubu-privu) AND \@ref(fig:enroll-pubu-privhs-pubhs) ABOUT HERE
+
+Figure \@ref(fig:enroll-pubu-privhs-pubhs) shows the 12th grade enrollment of visited private high schools as well as the 12th grade enrollment of visited public high schools for the public research universities in our sample.
+As seen, a large majority of public high school visits for all 15 universities were to schools with more than 150 12th graders enrolled (bottom panel).
+By contrast, most of the visited private schools tended to have fewer than 150 12th graders enrolled.
+Although this is somewhat to be expected, as public high schools tend to be larger in size than private schools (top rows of Figure \@ref(fig:enroll-pubu-privhs-pubhs)), there still appears to be a disproportionate amount of smaller private high schools visited compared to smaller public high schools.
+This suggests that the public universities in our sample were willing to take the time to visit private schools, even when they enroll far fewer 12th graders.
+
+Figure \@ref(fig:race-pubu-privu) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited private high schools.
+Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups.
+For over 65%<!--0.6632124--> of schools in the universe of private high schools (top row of Figure \@ref(fig:race-pubu-privu)), Black/Latinx/Native students comprise less than 20% of enrolled students.
+Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
+Figure \@ref(fig:race-pubu-privu) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
+For public universities, exceptions to this finding were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.
+For private universities, Marquette was the only exception to this finding.
+
+INSERT FIGURE \@ref(fig:race-pubu-privu) ABOUT HERE
+
+Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495].
+Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students [@RN4724].
+Therefore, universities may visit predominantly white private high schools in search of non-white students.
+One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.
+
+INSERT FIGURE \@ref(fig:race-pubu-privhs-pubhs) ABOUT HERE
+
+Figure \@ref(fig:race-pubu-privhs-pubhs) compares the racial composition of private high schools visited by public research universities to the racial composition of public high schools visited by these universities.
+Looking at the universe of high schools (top rows of Figure \@ref(fig:race-pubu-privhs-pubhs)), we see that public high schools tend to be more racially diverse than private schools.
+This is reflected in the racial composition of visited schools as well, where the set of visited public high schools generally enroll more Black/Latinx/Native students than the visited private schools for the public research universities in our sample.
+Unfortunately though, a majority of these public universities tended to visit private high schools at a higher rate than public high schools, as seen earlier in Figure \@ref(fig:actual-proportional-pubu).
+This disproportionate emphasis on private school visits may shift the racial composition of public universities away from Black/Latinx/Native students.
+
 # Discussion
@@
 
-\newpage
-
-# Social network data appendix
-
-A social network consists of a set of actors -- referred to as "vertices" -- and the connections -- referred to as "network ties" or "edges" between these actors.
-"One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
-"Two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type.
-Data on recruiting visits by universities to high schools yields a two-mode network, in which an edge -- a recruiting visit -- occurs between a high school (mode 1) and a university (mode 2).
-
-**Constructing two-mode network**.
-We describe construction of social network data with reference to "corporate board-director" networks -- the most commonly analyzed two-mode network -- which consist of directors (mode 1) who serve on organizational boards (mode 2).
-In our school-university two-mode network, the vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visit made between the two (e.g., high school $i$ shares an edge with university $j$ if high school $i$ receives at least one visit from university $j$).
-Visits can only occur between a school-university pair (not a school-school pair or a university-university pair).
-This (weighted) network can be represented as a school-by-university matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 universities) in which matrix cell $a_{i,j}$ identifies the number of visits  high school $i$ received from university $j$.
-<!--[SHOW AN EXCERPT OF THE TWO MODE ADJACENY MATRIX, LIKE 4 BY 3 OR SOMETHING] [DEFINE WEIGHTED VS.
-UNWEIGHTED SOMEWHERE]-->
-
-**Transforming two-mode network to one-mode networks**.
-Two-mode networks are often analyzed as one-mode networks [@RN2457].
-@RN4663 states that "overlapping groups such as boards of directors form a two-mode membership network in which one can conceive of directors as nodes [vertices] connected by a tie of common board membership, or boards as nodes connected by a tie of one or more shared directors" (p.
-XXX).
-Thus, a two-mode board-director network can be transformed into two one-mode networks.
-A weighted one-mode director network can be created as follows: create a director-by-director matrix (e.g., a $100 \times 100$ matrix if there are 100 directors in the network); two directors share an edge if they serve together on a board; matrix cell $a_{i,j}$ identifies the number of boards that include both director $i$ and director $j$ (e.g., $a_{i,j}=0$ if directors $i$ and $j$ do not serve on any of the same boards and $a_{i,j}=3$ if directors $i$ and $j$ serve on three boards together).
-Similarly, a one-mode board network is created based on a board-by-board matrix in which two boards share an edge if a director sits on both boards and matrix cell $a_{i,j}$ identifies the number of directors that serve on both board $i$ and board $j$.
-
-Following this approach, we create a one-mode high school network in which two private high schools share an edge if they both receive a visit by the same university.
-Cell $s_{i,j}$ of the school-by-school matrix $S$ indicates the number of universities that visited both school $i$ and school $j$<!-- [SHOW EXCERPT OF ONE-MODE SCHOOL BY SCHOOL MATRIX, LIKE 3 BY 3 OR SOMETHING]-->.
-Similarly, we create a one-mode university network in which two universities share an edge if both universities visited the same high school.
-Cell $c_{i,j}$ of the university-by-university matrix $C$ indicates the number of private high schools that received at least one visit from both university $i$ and university $j$.
-
-The social network analyses presented in this chapter -- particularly for research question 3 -- are primarily based on analysis of one-mode university networks.
-We created separate one-mode university networks for: public universities; private universities; both public and private universities.
-
 <!-- TABLES -->
 
-\newpage
-
-```{r ug-recruit-budget, echo=FALSE}
+```{r ug-recruit-budget, echo=FALSE, eval = FALSE, include = FALSE}
 pct_budget <- data.frame(
@@
 
+\newpage
 \clearpage
@@
 
+```{r pubu-percent-matrix}
+table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
+
+table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
+
+table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
+rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)
+
+rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)
+
+kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(c(1), width = '13em') %>% 
+  column_spec(c(14), width = '8.5em') %>% 
+  column_spec(2:13, width = '7em') %>% 
+  column_spec(c(7, 9, 15, 16), width = '6em')
+
+```
+
+```{r privu-percent-matrix}
+
+rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)
+
+kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  column_spec(1, width = '13em') %>%
+  column_spec(2:15, width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
+  column_spec(14:15, width = '8.5em')
+
+```
+
+\clearpage
+
+```{r privu-percent-visited-by-pubu-matrix}
+rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
+
+kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities') %>%
+  kable_styling(latex_options = 'scale_down') %>%
+  #column_spec(1, width = '8.5em') %>%
+  column_spec(2:15, width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
+  column_spec(14:15, width = '8.5em')
+```
+
+\end{landscape}
+
+\restoregeometry
+
+<!-- FIGURES -->
+
+```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%", include = FALSE, eval = FALSE}
+knitr::include_graphics('./../assets/images/enrollment_funnel.png')
+#![The enrollment funnel](assets/images/enrollment_funnel.png)
+```
+
+\clearpage
+\newpage
+
+```{r nd-religion, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Order 2 ego network of University of Notre Dame, vertices colored by religion"}
+include_graphics(file.path(figures_dir, 'nd_religtion.pdf'))
+```
+
+\newpage
+
+```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
+include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
+```
+
+\newpage
+
+```{r events-hs-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
+include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
+```
+
+\newpage
+
+```{r actual-proportional-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
+```
+
+\clearpage
+
+```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
+```
+
+\newpage
+
+```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
+```
+
+\clearpage
+
+```{r region-pubu-privu, echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
+```
+
+\newpage
+
+```{r religion-pubu-privu, echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
+```
+
+\newpage
+
+```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school ranking of visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
+```
+
+```{r race-pubu-privu, echo = FALSE, eval = FALSE, include = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools"}
+include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
+```
+
+\newpage
+
+```{r race-pubu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs.
+visited private high schools, public research universities"}
+include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
+```
+
+\newpage
+
+```{r race-privu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs.
+visited private high schools, selective private universities"}
+include_graphics(file.path(figures_dir, 'ego_network_race_privu_privhs_pubhs.pdf'))
+```
+
+\newpage
+\clearpage
+
+# Supplemental Online Appendix
+
+\pagenumbering{gobble}
+\pagenumbering{arabic}
+\renewcommand*{\thepage}{A\arabic{page}}
+\pagestyle{fancy}
+\setlength{\headheight}{15pt}
+
+\beginsupplement
+
 ```{r pubu-count-matrix}
-table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
-
-rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)
 
@@
 
-```{r pubu-percent-matrix}
-rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)
-
-kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(c(1), width = '13em') %>% 
-  column_spec(c(14), width = '8.5em') %>% 
-  column_spec(2:13, width = '7em') %>% 
-  column_spec(c(7, 9, 15, 16), width = '6em')
-
-```
-
-\clearpage
-
-```{r privu-count-matrix, eval=FALSE, include=FALSE}
+```{r privu-count-matrix}
 
@@
 
-kable(table_1mode_privu$onemode_df, caption = 'Private universities count matrix') %>%
+kable(table_1mode_privu$onemode_df, caption = 'One-mode private universities count matrix') %>%
   kable_styling(latex_options = 'scale_down') %>%
@@
 
-```{r privu-percent-matrix}
-
-table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
-
-rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)
-
-kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(1, width = '13em') %>%
-  column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
-  column_spec(14:15, width = '8.5em')
-
-```
-
 \clearpage
-
-```{r u-cluster1-percent-matrix, include=FALSE}
-table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
-
-#kable(table_1mode_u$clusters_df[order(match(table_1mode_u$clusters_df$univ_abbrev, rownames(table_1mode_u$onemode_df))), ], caption = 'Clusters for public and private universities')
-
-cluster_1 <- c(1, 4, 5, 7, 16, 18, 19, 24, 25, 28)
-cluster_2 <- c(2, 3, 6, 8, 9, 10, 11, 12, 14, 15, 20, 22, 23)
-cluster_3 <- c(13, 17, 21, 26, 27)
-cluster_4 <- 29
-
-kable(table_1mode_u$onemode_pct_df[cluster_1, cluster_1], caption = 'Public and private universities percent matrix (cluster 1)') %>%
-  kable_styling(latex_options = 'scale_down')
-```
 
@@
 
-```{r privu-percent-visited-by-pubu-matrix}
-rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
-
-kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  #column_spec(1, width = '8.5em') %>%
-  column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
-  column_spec(14:15, width = '8.5em')
-```
-
-\end{landscape}
-
-\restoregeometry
-
-<!-- FIGURES -->
-
-\clearpage
-
-```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%"}
-knitr::include_graphics('./../assets/images/enrollment_funnel.png')
-#![The enrollment funnel](assets/images/enrollment_funnel.png)
-```
-
-\newpage
-
-```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
-include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
-```
-
-\newpage
-
-```{r events-hs-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
-include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
-```
-
-\newpage
-
-```{r actual-proportional-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
-include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
-```
-
-\clearpage
-
-```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
-include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
-```
-
-\clearpage
-
-```{r region-pubu-privu, echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r religion-pubu-privu, echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school ranking of visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
+\newpage
+
+```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
+include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
+```
+
+\newpage
+
+```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
+include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
+```
+
+\newpage
+
+```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
+```
+
+```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private universities, colored by cluster"}
+knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
 ```
@@
 ```
-
-\newpage
-
-```{r race-pubu-privu, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r race-pubu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools vs.
-public high schools, public research universities"}
-include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
-```
-
-```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
-```
-
-```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private universities, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
-```
-
-```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
-```
-
-```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
-include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
-```
-
-\newpage
-
-```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
-include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
-```

### 2023-11-09 soc_of_ed/soc_of_ed_proposal_jaquette.Rmd
working on revisions

--- 2023-11-09 aefp_2024/aefp_2024_proposal_jaquette.Rmd
@@
 urlcolor: blue
-always_allow_html: true
 header-includes:
@@
 
-<!-- 
+**Introduction**.
 Harpeth Hall is a non-sectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
@@
 In Fall 2017, about 85% of Harpeth students were white and less than 5% were Black or Latinx.
--->
-**INTRODUCTION AND RESEARCH QUESTIONS**.
-Harpeth Hall is a non-sectarian private school for girls in Nashville, ranked 337 in the nation according to Niche private school rankings.
+
 From September 6th through October 17th, Harpeth received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University), and three private liberal arts colleges (Harvey Mudd, Scrips, and Sewanee).
@@
 
-Drawing from theories of organizational behavior [@RN531; @RN959; @RN531], recruiting behaviors that require significant expenditure are indicators of university enrollment priorities.
+Following the Supreme Court decision on race-conscious admissions, many universities have published statements about their commitment to diversity and racial justice.
+Talk is cheap.
+Drawing from theories of organizational behavior [@RN531; @RN959; @RN531], university recruiting behaviors that require significant expenditure are indicators of enrollment priorities.
 According to @RN4664, off-campus recruiting visits were the top-ranked recruiting expenditure item for both public and private universities.
+These visits leave a trail that problematizes the story told by university public relations efforts.
 
-This study analyzes off-campus recruiting visits to private high schools from a convenience sample of 14 selective private universities and 15 public research universities.
-Recruiting visits indicate a social relationship, motivating social network analyses of network ties (visits) between actors (universities and schools).
-Analyses are informed by three research questions:
+<!-- 
+Therefore, analyses of which schools a university visits -- and which schools they ignore -- can yield insights about university enrollment goals.
+What emerges is a story of white money and white privilege that flies in the face of  university public relations efforts.
+
+Comparing the recruiting networks of public research universities and selective private universities yields novel insights about the competition for affluent, "full-pay" students.  
+This research problematizes the story told by university public relations offices by analyzing off-campus recruiting visits to private high schools made by 14 selective private universities and 15 public research universities.
+
+Tell an untold story that flies in the face of the story that university public relations efforts tells us
+That the everyday recruiting practices of these universities actually serve the interests of white supremacy;
+-->
+This study analyzes off-campus recruiting visits to private high schools from a sample of 14 selective private universities and 15 public research universities.
+Recruiting visits indicate a social relationship, motivating social network analyses of network ties (visits) between actors (universities and schools): Analyses are informed by three research questions:
 <!--
@@
 1. How do the characteristics of private schools visited by public research universities compare to the characteristics of private schools visited by selective private universities?
-1. To what extent do public and private universities visit overlapping sets of private schools?
+1. To what extent do public and private univs visit overlapping sets of private schools?
+<!--
 
-Policy debates about college access are largely uninformed about recruiting.
-This proposal speaks to the conference theme by informing researchers and policymakers how recruiting practice occurs "in the wild" within the college access ecosystem.
+-->
 
-**LITERATURE REVIEW**. We bridge two disconnected literatures: (1) nonresident enrollment at public universities; and (2) linkages between private schools and private universities.
+**Literature Review**. We bridge two disconnected literatures: (1) nonresident enrollment at public universities; and (2) linkages between private schools and private universities.
+<!--
 
-Public research universities responded to declines in state appropriations by growing enrollment from nonresident students [@RN3753] and international students [@bound_international], who pay higher prices than residents.
-@RN3685 show that growth in the share of nonresident students is associated with declines in the share of Pell recipients and Black and LatinX students.
+-->
+
+@RN3753 found that public research universities responded to declines in state appropriations by growing enrollment from nonresident students, who pay higher prices than residents.
+@RN3685 shows that growth in the share of nonresident students is associated with declines in the share of Pell recipients and Black and LatinX students.
 Universities visit high schools to attract applicants and maintain relations with counselors.
@@
 
-Scholarship from sociology and economics finds that private school attendance positively affects college access and college selectivity [@RN4614;@RN4625; @RN4599; @RN4936; @RN4938].
-Descriptive statistics from the high school freshman class of 2009 indicate that 5.0% of public high school students attended a public university ranked in the top 100 by USNWR and 1.9% attended a top 100 private university (Author calculations based on HSLS).
-Of private school students, 10.9% attended a top 100 public university and 16.8% attended a top 100 private university.
-Of nonsectarian private school students, 11.3% attended a top 100 public university and 39.8% attended a top 100 private university.
+Scholarship from sociology has analyzed linkages between private schools and universities.
+Attending private school positively affects college access and college selectivity [e.g., @RN4642; @RN4614;@RN4625].
+Although recently discovered by economics [@RN4935], sociology has long observed a special relationship between elite private schools and elite universities [@RN4407; @RN4647; @RN3519; @RN4640].
+Moreover, sociology highlights the primacy of social relationships between elite schools and elite colleges.
 
-@RN4935 find that students from elite private schools are overrepresented at elite universities because private school applicants receive higher ratings on non-academic components (e.g., extracurricular activities, teacher and guidance counselor recommendations).
-By contrast, scholarship from sociology highlights the mechanism of social relationships between private school guidance counselors and college admissions officers (e.g., making a phone call on behalf of an applicant) [@RN4407; @RN4647; @RN3519; @RN4640].
-
-Although the literature on (1) nonresident enrollment and (2) the literature on linkages between private schools developed in isolation, they are both part of a broader story about the competition for affluent students.
+Although these two literatures developed in isolation, they are parts of a broader story about school segregation and the competition for affluent students.
+In recent decades, Catholic school enrollment by middle-income families declined in the Midwest and the Northeast [@RN4504].
+In the South, enrollment in Christian and nonsectarian private schools grew as a consequence of "white flight" from public schools.
 Historically, private schools were the domain of selective private universities.
 However, public research universities have an incentive to visit out-of-state private schools to find "full-pay" nonresident students.
-By analyzing the network of recruiting visits, we show whether public research universities and selective private universities are competing for students at similar sets of private schools.
+By analyzing the network of recruiting visits, we show whether public research universities and selective private universities are competing at similar sets of private schools.
 <!-- 
@@
 
-**METHODS**.
+**Methods**.
 We collected off-campus recruiting visit data in 2017 by web-scraping events from university admissions websites.
-The analysis sample for this study consists of 15 public research-extensive universities and 14 private universities ranked in the top 100 of US News National University rankings.
+The analysis sample for this study consists of 15 public research universities (research-extensive) and 14 private universities ranked in the top 100 of US News National University rankings.
 We also incorporated secondary data from IPEDS, the American Community Survey, NCES Common Core of Data (public schools), and the Niche Best Private High Schools ranking.
+Off-campus recruiting visits are the network tie that defines a two-mode social network between universities (mode 1) and private schools (mode 2).
+We construct the two-mode network, transform the two-mode network to several one-mode networks, and utilize descriptive statistics to analyze these objects.
 
-Off-campus recruiting visits are the network tie that defines a two-mode social network between universities (mode 1) and private schools (mode 2).
-We construct the two-mode network and transform the two-mode network into several one-mode network objects.
-To answer research questions, we analyze these objects using simple descriptive statistics and cluster analysis methods, as shown below.
-
-**RESULTS**.
-Results for RQ1 (scale of private school visits) are shown in Figures \@ref(fig:events-hs-count-pubu), \@ref(fig:events-hs-count-privu), \@ref(fig:actual-proportional-pubu), and \@ref(fig:actual-proportional-privu).
+**Results**.
+Results for RQ1 (scale of visits to private schools) are shown in Figures \@ref(fig:events-hs-count-pubu), \@ref(fig:events-hs-count-privu), \@ref(fig:actual-proportional-pubu), and \@ref(fig:actual-proportional-privu).
 Results for RQ2 (characteristics of visited private schools) are shown in Figures \@ref(fig:region-pubu-privu), \@ref(fig:religion-pubu-privu), \@ref(fig:rank-pubu-privu), \@ref(fig:race-pubu-privu), and \@ref(fig:race-pubu-privhs-pubhs).
@@
 
-**SIGNIFICANCE**.
+**Significance**.
 Universities in our sample made a disproportionate number of visits to private schools.
-Most public universities in our sample -- even those not in the South -- made a large share of visits to the South.
+In turn, the disproportionate enrollment of private school students at these universities may be the consequence of intentional recruiting rather than  exogenous student demand.
 Visited private schools tend to be much whiter than visited public schools.
-We infer that university recruiting behavior disproportionately targets students at racially homogeneous high schools.
+Most public universities in our sample -- even those not in the South -- made a large share of visits in the South.
+In contrast to stated commitments about racial diversity, university recruiting behavior implicitly targets households that sought racially homogenous high schools.
 
@@
 <div id="refs"></div>
+
+<!-- TABLES -->
 
@@
 \restoregeometry
+
+<!-- FIGURES -->
 

### 2023-11-09 scripts/create_tables_figures.R

@@ -586,13 +586,25 @@ grid.arrange(a, b, c, nrow = 3, ncol = 1)
 dev.off()
 
 # pubu to pubhs + privhs (race)
-a <- plot_characteristic_privhs('race', race_var, race_title, race_values, race_keys)
-b <- plot_characteristic_pubhs('race', race_var, race_title, race_values, race_keys)
+a <- plot_characteristic_pubhs('race', race_var, race_title, race_values, race_keys)
+b <- plot_characteristic_privhs('race', race_var, race_title, race_values, race_keys)
+
 
 pdf(file.path(figures_dir, str_c('ego_network_race_pubu_privhs_pubhs.pdf')))
 par(mar = c(0, 0, 0, 0) + 0.1, mai = c(0, 0, 0, 0))
 grid.arrange(a, b, nrow = 2, ncol = 1)
 dev.off()
+
+# privu to pubhs + privhs (race)
+a <- plot_characteristic_pubhs('race', race_var, race_title, race_values, race_keys, control = 'private', type = 'univ')
+b <- plot_characteristic_privhs('race', race_var, race_title, race_values, race_keys, control = 'private', type = 'univ')
+
+
+pdf(file.path(figures_dir, str_c('ego_network_race_privu_privhs_pubhs.pdf')))
+par(mar = c(0, 0, 0, 0) + 0.1, mai = c(0, 0, 0, 0))
+grid.arrange(a, b, nrow = 2, ncol = 1)
+dev.off()
+
 
 # pubu to pubhs (separated by instate/outofstate) + privhs (race)
 a <- plot_characteristic_privhs('race', race_var, race_title, race_values, race_keys)

### 2023-11-09 scripts/network_recruiting_analysis.R

@@ -214,6 +214,13 @@ plot_ego_graph(egos_psi_privu, '160755', graph_order = 1)
 plot_ego_graph(egos_psi_privu, '160755', graph_order = 2)
 plot_ego_graph(egos_psi_privu, '160755', graph_order = 'both')
 
+# Notre Dame 152080
+
+save_plot(
+  plot_ego_graph(egos_psi_u, '152080', characteristic = 'religion', values = religion_values, keys = religion_keys, 
+                 title = religion_title, graph_order = 'both', margin = -.3),
+  plot_name = 'nd_religtion.pdf')
+
 # Characteristics
 plot_ego_graph(egos_psi_privu, '160755', characteristic = 'region', values = region_values, keys = region_keys, title = region_title, graph_order = 1)
 plot_ego_graph(egos_psi_privu, '160755', characteristic = 'region', values = region_values, keys = region_keys, title = region_title, graph_order = 2)
@@ -439,9 +446,16 @@ plot_2mode_graph <- function(twomode_network, c_analysis, k = NULL, h = NULL, no
 }
 
 # Usage
-plot_2mode_graph(g_2mode, c_analysis = 'region', values = region_values, keys = region_keys)
+
+
+
+plot_2mode_graph(g_2mode_u, c_analysis = 'region', values = region_values, keys = region_keys, margin = -.8)
+plot_2mode_graph(g_2mode_u, c_analysis = 'region', values = region_values, keys = region_keys, layout = layout_with_fr, margin = -.7)
+plot_2mode_graph(g_2mode_u, c_analysis = 'region', values = region_values, keys = region_keys, layout = layout_with_kk, margin = -.6)
+
 plot_2mode_graph(g_2mode_privu, c_analysis = 'hclust', k = 4)
 plot_2mode_graph(g_2mode_pubu, c_analysis = 'fast', steps = 11, colors = c('red', 'orange', 'yellow', 'green', 'blue', 'purple'))
+
 
 # public and private universities
 

### 2023-11-13 r_r/manuscript_rihe.Rmd
working through revisions

@@
 
-## RQ3: Overlapping network structure
-
-Research question 3 asks, "To what extent do public research universities and selective private universities visit overlapping sets of private high schools?" In contrast to RQ1 and RQ2, answering RQ3 requires social network analysis techniques.
-
+## RQ2: Overlapping network structure
+
+Research question 2 asks, "To what extent do public research universities and selective private universities visit overlapping sets of private high schools?" Answering this question requires social network analysis techniques.
 As described in the methods section, we began by constructing a two-mode social network of visits to private high schools (mode 1) by universities (mode 2).
@@
 The *weight* of an edge indicates the number of high schools that both universities visited.
-For example, if there are 200 private high schools that received a visit from both Notre Dame and Villanova, the weight of the edge between Notre Dame and Villanova is 200.
+For example, Appendix Table \@ref(tab:pubu-count-matrix) shows the matrix of weights for the set of public research universities.
 We created three separate one-mode university networks: a public university network; a private university network; a public and private university network.
 
-We answer research question 3 by: first, analyzing overlap in the recruiting network of public universities (the public university network); second, analyzing overlap in the network of private universities (the private university network); and third, analyzing overlap amongst public and private universities (the public and private university network).
-
-### Public university network
-
-Tables \@ref(tab:pubu-count-matrix) and \@ref(tab:pubu-percent-matrix) provide a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
-Table \@ref(tab:pubu-count-matrix) shows -- for each pair of public universities -- the number of high schools that were visited by both universities.
-For example, column 1 shows that of the 759 different private high schools that the University of Alabama visited, the University of South Carolina visited 284 of these schools and CU-Boulder visited 210 of these schools.
-Table \@ref(tab:pubu-percent-matrix) shows overlap in high schools visited in terms of percent rather than count.
+We answer research question 2 by briefly describing tabular representations of overlap between the set of public research universities and overlap between the set of selective private universities.
+Next, we utilize tabular and graphical representations to describe ovelrap between the set of public and private universities in our sample.
+
+Table \@ref(tab:pubu-percent-matrix) provide a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
+For each public university (column), each cell of Table Table \@ref(tab:pubu-percent-matrix) shows number of visited high schools in common as a percent of the total number of high schools visited by the column university.
+This indicates the extent to which public universities were competing for students at the same set of private school.
 For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7% of these high schools and CU-Boulder visited 39.1% of these high schools.
-
-INSERT TABLE \@ref(tab:pubu-count-matrix) AND TABLE \@ref(tab:pubu-percent-matrix) ABOUT HERE
+Appendix Table \@ref(tab:pubu-count-matrix) shows counts rather than percents.
+
+INSERT TABLE \@ref(tab:pubu-percent-matrix) ABOUT HERE
 
@@
 For example, UMass-Amherst, SUNY Stony Brook, and Rutgers tend to visit many of the same high schools, as do the University of Arkansas and the University of Kansas.
+These descriptive findings suggest network structures based on geographic proximity.
+
+Table \@ref(tab:privu-percent-matrix) show overlap in private high schools visited by the selective private universities in our sample.
+Appendix Table \@ref(tab:privu-count-matrix) shows counts.
+The networks of private universities appear to have more overlap than the network of public research universities.
+This is demonstrated tabularly by the higher percentages in Table \@ref(tab:privu-percent-matrix) compared to Table \@ref(tab:pubu-percent-matrix).
+Private universities that share a high percent of visits tend to have the same religious affiliation and/or be located in the same geographic region.
+For example, the Catholic universities -- Notre Dame, Villanova, Boston College, and Marquette -- seem to visit many private high schools in common.
+
+INSERT TABLE \@ref(tab:privu-percent-matrix) ABOUT HERE
+
+Next, we examine overlap in a network that contains the 15 public universities and the 14 private universities.
+Table \@ref(tab:privu-percent-visited-by-pubu-matrix) shows, for each private university, the percent of schools that were also visited by each public university.
+This table shows the extent to which public universities were competing at private schools targeted by private universities.
+For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.5% of these schools.
+Similarly, CU-Boulder visited 46.4 of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
+The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
+[CRYSTAL ADDS THE TABLE: FOR PUBLIC UNIVERSITIES, THE PRECENT OF HIGH SCHOOLS VISITED BY PRIVATE UNIVERSITIES]
+
+INSERT TABLE \@ref(tab:privu-percent-visited-by-pubu-matrix) ABOUT HERE
 
 Network graphs are useful for showing which universities have similar private high school recruiting networks.
-Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network.
+Figure \@ref(fig:plot-1mode-u) graphs the one-mode network that consists of all 29 public and private universities in the sample (Appendix Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network and Appendix Figure \@ref(fig:plot-1mode-privu) graph the one-mode private university network).
+
 Whether graphing one-mode or two-mode networks, network graphs show vertices as circles and edges as lines connecting pairs of vertices.
-In Figure \@ref(fig:plot-1mode-pubu), each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common.
-The width of the line between two universities indicates the number of high schools both universities visited, as identified in Table \@ref(tab:pubu-count-matrix).
-Conceptually, we think of vertices as repelling one another and edges as pulling vertices together [@RN4725].
-Therefore, vertices that share few connections are located apart and those that share many connections are located close together.
-Vertices that are highly connected -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while vertices that are relatively disconnected are located at the periphery of the graph.
-
-INSERT FIGURE \@ref(fig:plot-1mode-pubu) ABOUT HERE
-
-Figure \@ref(fig:plot-1mode-pubu) shows the University of Alabama, University of South Carolina, and CU-Boulder at the center of the recruiting network.
-The University of Nebraska-Lincoln, SUNY Stony Brook, and UC-Riverside are located on the periphery, and the remaining universities are in between.
-Universities that share many direct (i.e., visit many of the same schools) or indirect edges tend to be located close together, for example University of Kansas and University of Arkansas.
-
-To better answer research question 3, we augment the network graphs by using cluster analysis methods -- referred to as "community detection" in the network analysis literature -- to identify groups of universities that share common network structure.
-Broadly speaking, the goal of community detection is to identify "subsets of vertices that demonstrate a ‘cohesiveness’ with respect to the underlying relational patterns" [@RN4725, p.
-59], where a "cohesive subset" means a "subset of vertices that (i) are well connected among themselves, and at the same time (ii) are relatively well separated from the remaining vertices"  [@RN4725, p.
-59].
-In particular, we utilize that "cluster fast and greedy" approach developed by @RN4725, which is a variation of hierarchical cluster analysis that starts with a large number of groups and adds individual vertices to a group when doing so contributes to a cohesive subset.
-
-In Figure \@ref(fig:plot-1mode-pubu), the shape of each university vertex is based on implementing this cluster fast and greedy approach with the specification that the algorithm should identify four groups.
-The largest group consists of eight universities (U.
-Alabama, U.
-Arkansas, U.
-Kansas, Nebraska-Lincoln, U.
-Georgia, U.
-South Carolina, CU-Boulder, U.
-Cincinnati).
-With the exception of CU-Boulder, these universities were located in the South and the Midwest.
-Most of these universities made a relatively high share of visits in the South.
-The next largest cluster -- UMass Amherst, University of Pittsburgh, Rutgers, and SUNY Stony Brook -- consisted of universities that were mostly located in the Northeast and visited a large share of high schools in the Northeast.
-UC-Berkeley and UC-San Diego formed a two-university cluster and UC-Riverside -- which visited fewer private schools than any other public university -- was a cluster unto itself.
-
-### Private university network
-
-Table \@ref(tab:privu-percent-matrix) and Figure \@ref(fig:plot-1mode-privu) show overlap in private high schools visited by the selective private universities in our sample.
-The networks of private universities tend to have more overlap than the network of public research universities (above).
-This is demonstrated tabularly by the higher percentages in Table \@ref(tab:privu-percent-matrix) compared to Table \@ref(tab:pubu-percent-matrix) and graphically by the thicker lines connecting universities in Figure \@ref(fig:plot-1mode-privu) compared to Figure \@ref(fig:plot-1mode-pubu).
-
-INSERT TABLE \@ref(tab:privu-percent-matrix) ABOUT HERE
-
-INSERT FIGURE \@ref(fig:plot-1mode-privu) ABOUT HERE
-
-Whereas applying cluster analysis to public universities (Figure \@ref(fig:plot-1mode-pubu)) yielded three clusters that contained multiple universities, the application of cluster analysis to private universities (Figure \@ref(fig:plot-1mode-privu)) yielded a single cluster that contained 11 universities and three clusters that contained one university each.
-As suggested above, a likely explanation for this difference is that the majority of private universities had substantial overlap in the sets of private high schools visited whereas public universities tended to have substantial overlap with some public universities but not others.
-
-Visually, the most central universities in Figure \@ref(fig:plot-1mode-privu) tended to be universities that visited a large number of schools (number of unique private high schools visited in parentheses): Villanova (563), SMU (550), Notre Dame (625), Northwestern (377), Tulane (430), Boston College (339).
-The periphery of the network included Baylor (237), Stevens Institute (160), Marquette (331), and Case Western (228).
-Baylor visited a higher number of conservative Christian high schools than any other university (see Figure \@ref(fig:religion-pubu-privu)).
-It is notable that Marquette is in the periphery despite visiting a higher number of schools than more centrally located universities (e.g., Emory), suggesting that Marquette visits many schools that are visited by few other private universities in our sample.
-
-The universities located close to one another in Figure \@ref(fig:plot-1mode-privu) tend to share religious affiliation and/or be located in the same geographic region.
-For example, the majority of Catholic universities are located close to one another and the majority of Midwest universities are located close to one another.
-Interestingly, two of the three Christian universities -- TCU and SMU -- are located much closer to the Catholic universities Notre Dame and Northwestern than they are to Baylor, suggesting that Baylor visits a different set of conservative Christian high schools than TCU and SMU.
-
-### Public and private university network
-
-Figure \@ref(fig:plot-1mode-u) shows overlap in private high schools visited amongst all 29 private and public universities in the sample.
-
-The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and characteristics of the schools they visit -- of geographic location, religious affiliation, academic reputation, and also institutional control.
-The cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities that visited a relatively large share of Christian high schools.
-Second, the cluster of 13 universities -- including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley -- largely consists of more highly ranked universities, universities located in the Midwest or West, and Catholic universities.
-Third, the five university cluster -- Rutgers, Stevens Institute of Technology, UMass Amherst, University of Pittsburgh, SUNY Stony Brook -- largely consists of public universities with strong ties to the Northeast.
+In Figure \@ref(fig:plot-1mode-u), each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common.
+The width of the line between two universities indicates the *weight* of the edge, defined as number of high schools both universities visited.
+Network methods conceive of vertices as repelling one another [@RN4725], like the "north pole" of two magnets.
+By contrast, edges shared between two vertices pull the two vertices together, like the north pole of one magnet being attracted to the south pole of another magnet.
+Because of these laws of repulsion and attraction, vertices that share few connections are located far apart while vertices that share many connections are located close together.
+Additionally, vertices that are highly connected -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while vertices that are relatively disconnected are located at the periphery of the graph.
 
@@
 
-<!--
-
-Tables \@ref(tab:u-cluster1-percent-matrix), \@ref(tab:u-cluster2-percent-matrix), and \@ref(tab:u-cluster3-percent-matrix) show overlap in the percent of private high schools 
-INSERT TABLE \@ref(tab:u-cluster1-percent-matrix) TABLE \@ref(tab:u-cluster2-percent-matrix) AND TABLE \@ref(tab:u-cluster3-percent-matrix) ABOUT HERE
--->
-
-Universities located near the center of Figure \@ref(fig:plot-1mode-u) do not all belong to the same cluster and, more broadly, universities located close to one another do not all belong to the same cluster.
 Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities with the highest degree centrality (i.e., those that visited the most schools).
@@
 Notably, while the majority of universities located near the center of Figure \@ref(fig:plot-1mode-u) are private, three are public.
+The most peripheral universities -- UC-Riverside,  SUNY Stony Brook, and University of Nebraska-Lincoln -- are all public.
 
@@
 CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located close to one another in Figure \@ref(fig:plot-1mode-u).
-These three universities are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit.
-
-Finally, Table \@ref(tab:privu-percent-visited-by-pubu-matrix) shows, for each private university, the percent of schools that were also visited by each public university.
-This table shows the extent to which public universities were competing at private schools targeted by private universities.
-For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.5% of these schools.
-Similarly, CU-Boulder visited 46.4 of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
-The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
-
-INSERT TABLE \@ref(tab:privu-percent-visited-by-pubu-matrix) ABOUT HERE
-
-These analyses of the private and public university network provide the most direct assessment of research question 3.
+These three universities are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit [HAVEN'T YET INTRODUCED THESE FIGURES].
+
+To better answer research question 2, we augment the network graphs by using cluster analysis methods -- referred to as "community detection" in the network analysis literature -- to identify groups of universities that share common network structure.
+Broadly speaking, the goal of community detection is to identify "subsets of vertices that demonstrate a ‘cohesiveness’ with respect to the underlying relational patterns" [@RN4725, p.
+59], where a "cohesive subset" means a "subset of vertices that (i) are well connected among themselves, and at the same time (ii) are relatively well separated from the remaining vertices"  [@RN4725, p.
+59].
+Therefore, universities in the same cluster have a relatively large number of direct and direct ties with other universities in the cluster and have relatively few direct and indirect ties with universities in other clusters.
+We utilize that "cluster fast and greedy" approach from @RN4725.
+This is a variation of hierarchical cluster analysis that starts with a large number of groups and adds individual vertices to a group when doing so contributes to a cohesive subset.
+
+In Figure \@ref(fig:plot-1mode-u), universities are allocated to groups based on the specification that the algorithm should identify four groups (we also experimented with three, five, and six groups).
+Universities located near the center of Figure \@ref(fig:plot-1mode-u) do not all belong to the same cluster and, more broadly, universities located close to one another do not all belong to the same cluster.
+Starting with the most peripheral group, UC-Riverside is a group unto itself.
+UC-Riverside only visited 100 private schools and about 70 of these were located in CA.
+Another group --- Rutgers, Stevens Institute of Technology, UMass-Amherst, SUNY-Stony Brook, and Pitt -- largely consists of public universities with strong ties to the Northeast.
+
+The remaining two groups are larger and include universities with greater network centrality.
+Additionally, these groups both contain a mix of public and private universities.
+The cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, University of Kansas, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities.
+While the federal government defines Nebraska and Kansas as part of the Midwest, Figure \@ref(fig:plot-1mode-u) suggests that the visit patterns of the University of Kansas and the University of Nebraska share more in common with Southern universities than they do with other universities in our sample.
+Finally, the largest and most centrally located cluster contains 13 universities, including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley.
+Compared to the overall sample, this group tends to be.
+This group largely consists of highly ranked universities, universities located in the Midwest or West, and Catholic universities.
+
+The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and characteristics of the schools they visit -- of geographic location, religious affiliation, academic reputation, and also institutional control.
 Considering the identification of clusters, centrality, and proximity of vertices, we find substantial overlap in the sets of private schools visited by public universities and private universities.
@@
 
-Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?"
-
-Figure \@ref(fig:region-pubu-privu) shows the geographic region -- Northeast, Midwest, South, and West -- of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel).
+Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?" Additionally, Appendix Figures \@ref(fig:enroll-pubu-privu) and \@ref(fig:enroll-pubu-privhs-pubhs) show the 12th grade enrollment size of visited high schools.
+
+Figure \@ref(fig:region-pubu-privu) shows the broad geographic region -- Northeast, Midwest, South, and West -- of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel).
 Scholarship on the relationship between geographic proximity and student demand tends to find that nationally prestigious universities enjoy strong demand across the nation, while less prestigious universities rely primarily on demand from students located nearby [e.g., @RN2133].
@@
 Figure \@ref(fig:rank-pubu-privu) shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools.
-For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visited a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.
-A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.
+For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visited a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.^[A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.]
 
@@
 News and World Report.
-That said, the finding that public research universities visited a large share of low-rated private high schools is consistent with the idea that many public research universities visit private high schools in search of full-pay students rather than academic superstars.
-
-Figure \@ref(fig:enroll-pubu-privu) shows the 12th grade enrollment of visited private high schools.
-Compared to the universe of private high schools, the universities in our sample tended to visit schools that enrolled more 12th graders.
-Generally, the findings were pretty similar across public and private universities; for most universities, more than half of private school visits were to schools that enrolled at least 100 12th graders.
-However, public universities tended to visit a slightly larger share of high schools with fewer than 50 12th graders and private universities tended to visit a higher share of high schools with 12th grade enrollment of 50-100.
-
-INSERT FIGURES \@ref(fig:enroll-pubu-privu) AND \@ref(fig:enroll-pubu-privhs-pubhs) ABOUT HERE
-
-Figure \@ref(fig:enroll-pubu-privhs-pubhs) shows the 12th grade enrollment of visited private high schools as well as the 12th grade enrollment of visited public high schools for the public research universities in our sample.
-As seen, a large majority of public high school visits for all 15 universities were to schools with more than 150 12th graders enrolled (bottom panel).
-By contrast, most of the visited private schools tended to have fewer than 150 12th graders enrolled.
-Although this is somewhat to be expected, as public high schools tend to be larger in size than private schools (top rows of Figure \@ref(fig:enroll-pubu-privhs-pubhs)), there still appears to be a disproportionate amount of smaller private high schools visited compared to smaller public high schools.
-This suggests that the public universities in our sample were willing to take the time to visit private schools, even when they enroll far fewer 12th graders.
-
-Figure \@ref(fig:race-pubu-privu) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited private high schools.
+That said, the finding that public research universities visited a large share of low-rated private high schools is consistent with the idea that many public research universities visit private high schools in search of full-pay students rather than high-achieving students.
+
+Figures \@ref(fig:race-pubu-privhs-pubhs) and \@ref(fig:race-privu-privhs-pubhs) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited high schools.
 Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups.
-For over 65%<!--0.6632124--> of schools in the universe of private high schools (top row of Figure \@ref(fig:race-pubu-privu)), Black/Latinx/Native students comprise less than 20% of enrolled students.
+The top row in the top panel of Figure \@ref(fig:race-pubu-privhs-pubhs) shows that the sum of Black, Latinx, and Native students comprise less than 20% of enrolled students in over over 65%<!--0.6632124--> of schools in private high school universe.
+At public high schools, Black/Latinx/Native students comprise less than 20% of enrolled students at less than 40% [CRYSTAL CHECK NUMBER] of all public schools.
+
+Figure \@ref(fig:race-pubu-privhs-pubhs) focuses on public universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel).
+START HERE TUESDAY.
+CONSISTENT WITH DIFFERENCES IN RACIAL COMPOSITION OF THE UNIVERSE OF PUBLIC VS.
+THE UNIVERSE OF PRIVATE, VISITED PRIVATE SCHOOLS TENDED TO ENROLL A MUCH LOWER SHARE OF BLACK/LATINX THAN VISITED PUBLIC SCHOOLS.
+
+This is reflected in the racial composition of visited schools as well, where the set of visited public high schools generally enroll more Black/Latinx/Native students than the visited private schools for the public research universities in our sample.
+Unfortunately though, a majority of these public universities tended to visit private high schools at a higher rate than public high schools, as seen earlier in Figure \@ref(fig:actual-proportional-pubu).
+This disproportionate emphasis on private school visits may shift the racial composition of public universities away from Black/Latinx/Native students.
+
 Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
+
 Figure \@ref(fig:race-pubu-privu) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
@@
 
-INSERT FIGURE \@ref(fig:race-pubu-privu) ABOUT HERE
+INSERT FIGURES \@ref(fig:race-pubu-privhs-pubhs) AND \@ref(fig:race-privu-privhs-pubhs) ABOUT HERE
 
@@
 
-INSERT FIGURE \@ref(fig:race-pubu-privhs-pubhs) ABOUT HERE
-
-Figure \@ref(fig:race-pubu-privhs-pubhs) compares the racial composition of private high schools visited by public research universities to the racial composition of public high schools visited by these universities.
-Looking at the universe of high schools (top rows of Figure \@ref(fig:race-pubu-privhs-pubhs)), we see that public high schools tend to be more racially diverse than private schools.
-This is reflected in the racial composition of visited schools as well, where the set of visited public high schools generally enroll more Black/Latinx/Native students than the visited private schools for the public research universities in our sample.
-Unfortunately though, a majority of these public universities tended to visit private high schools at a higher rate than public high schools, as seen earlier in Figure \@ref(fig:actual-proportional-pubu).
-This disproportionate emphasis on private school visits may shift the racial composition of public universities away from Black/Latinx/Native students.
+ADD ADDITIONAL SUBGROUP ANALYSES WITH CRYSTAL...?
+
+- look at racial composition of visited southern schools (public and private)
+- look at religious affiliation of visited southern schools?
+- look at racial composition of schools visited by some subset of universities?
+-
 

### 2023-11-13 scripts/create_tables_figures.R

@@ -586,9 +586,8 @@ grid.arrange(a, b, c, nrow = 3, ncol = 1)
 dev.off()
 
 # pubu to pubhs + privhs (race)
-a <- plot_characteristic_pubhs('race', race_var, race_title, race_values, race_keys)
-b <- plot_characteristic_privhs('race', race_var, race_title, race_values, race_keys)
-
+a <- plot_characteristic_privhs('race', race_var, race_title, race_values, race_keys)
+b <- plot_characteristic_pubhs('race', race_var, race_title, race_values, race_keys)
 
 pdf(file.path(figures_dir, str_c('ego_network_race_pubu_privhs_pubhs.pdf')))
 par(mar = c(0, 0, 0, 0) + 0.1, mai = c(0, 0, 0, 0))
@@ -596,9 +595,8 @@ grid.arrange(a, b, nrow = 2, ncol = 1)
 dev.off()
 
 # privu to pubhs + privhs (race)
-a <- plot_characteristic_pubhs('race', race_var, race_title, race_values, race_keys, control = 'private', type = 'univ')
-b <- plot_characteristic_privhs('race', race_var, race_title, race_values, race_keys, control = 'private', type = 'univ')
-
+a <- plot_characteristic_privhs('race', race_var, race_title, race_values, race_keys, control = 'private', type = 'univ')
+b <- plot_characteristic_pubhs('race', race_var, race_title, race_values, race_keys, control = 'private', type = 'univ')
 
 pdf(file.path(figures_dir, str_c('ego_network_race_privu_privhs_pubhs.pdf')))
 par(mar = c(0, 0, 0, 0) + 0.1, mai = c(0, 0, 0, 0))

### 2023-11-14 r_r/letter_to_reviewers.Rmd
revising results section

@@
 SEEMS TO WANT ADDITIONAL ANALYSES TO ENGAGE W/ RQ3. I'M NOT SURE WHAT TO ADD HERE. COME BACK TO LATER.
+SOLUTION: SAY THAT WE THINK THE AUTHOR IS MAKING A GOOD POINT.
+INCLUDE THIS POINT AS A LIMITATION.
+AND AN AREA WHERE FUTURE RESEARCH SHOULD PROBE.
+SAY THAT IF THE REVIEWER IS DEAD SET ON SOME ADDITIONAL ANALYSES, I WILL MAKE THIS HAPPEN.
+
+POTENTIAL ANALYSIS YOU THOUGHT THROUGH
+
+- WHAT ARE THE CHARACTERISTICS OF PRIVATE SCHOOLS VISITED BY PUBLIC UNIVERSITIES BUT NOT BY PRIVATE UNIVERSITIES 
+- REGRESSION ANALYSES; SEPARATE REGRESSION FOR EACH UNIVERSITY
 

### 2023-11-14 r_r/manuscript_rihe.Rmd
revising results section

@@
 At public high schools, Black/Latinx/Native students comprise less than 20% of enrolled students at less than 40% [CRYSTAL CHECK NUMBER] of all public schools.
+However, most public research universities and all selective private universities visited private high schools at a higher rate than public high schools, as seen earlier in Figures \@ref(fig:actual-proportional-pubu) and \@ref(fig:actual-proportional-privu).
+Even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
+Therefore, a disproportionate emphasis on visits to public schools may shift the racial composition of public universities away from Black/Latinx/Native students.
+
+INSERT FIGURES \@ref(fig:race-pubu-privhs-pubhs) AND \@ref(fig:race-privu-privhs-pubhs) ABOUT HERE
 
 Figure \@ref(fig:race-pubu-privhs-pubhs) focuses on public universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel).
-START HERE TUESDAY.
-CONSISTENT WITH DIFFERENCES IN RACIAL COMPOSITION OF THE UNIVERSE OF PUBLIC VS.
-THE UNIVERSE OF PRIVATE, VISITED PRIVATE SCHOOLS TENDED TO ENROLL A MUCH LOWER SHARE OF BLACK/LATINX THAN VISITED PUBLIC SCHOOLS.
-
-This is reflected in the racial composition of visited schools as well, where the set of visited public high schools generally enroll more Black/Latinx/Native students than the visited private schools for the public research universities in our sample.
-Unfortunately though, a majority of these public universities tended to visit private high schools at a higher rate than public high schools, as seen earlier in Figure \@ref(fig:actual-proportional-pubu).
-This disproportionate emphasis on private school visits may shift the racial composition of public universities away from Black/Latinx/Native students.
-
-Therefore, even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
-
-Figure \@ref(fig:race-pubu-privu) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
+For all public universities, the racial composition of visited public schools contain a much higher share of Black/Latinx/Native students than the racial composition of visited private schools.
+Figure \@ref(fig:race-pubu-privhs-pubhs) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
 For public universities, exceptions to this finding were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.
-For private universities, Marquette was the only exception to this finding.
-
-INSERT FIGURES \@ref(fig:race-pubu-privhs-pubhs) AND \@ref(fig:race-privu-privhs-pubhs) ABOUT HERE
+
+Figure \@ref(fig:race-privu-privhs-pubhs) focuses on selective private universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel).
+Results are very similar to those of public universities.
+Visited private schools enrolled a much lower share of Black/Latinx/Native students than visited public schools.
+For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75% of visited private schools enrolled less than 20% Black/Latinx/Native students.
 
@@
 Therefore, universities may visit predominantly white private high schools in search of non-white students.
-One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.
-
-ADD ADDITIONAL SUBGROUP ANALYSES WITH CRYSTAL...?
-
-- look at racial composition of visited southern schools (public and private)
+One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored [THIS PARAGRAPH SHOULD PROBABLY GO TO DISCUSSION].
+
+ADDITIONAL SUBGROUP ANALYSES
+
+- racial composition of visited southern schools (separat figures for public universities and private universities; top panel is visited private schools; bottom panel is visited public schools; universe is southern schools)
+
 - look at religious affiliation of visited southern schools?

### 2023-11-16 r_r/manuscript_rihe.Rmd
revising discussion

@@
 
-[PUT THIS IN THE DISCUSSION SECTION] Finally When both private and public universities are targeting private schools, competition for these students is likely to increase.
-This could be an explanation for why many private universities are struggling to meet enrollment goals
-
-student bodies that predonominantly affluent, white student bodies.
-
 # Literature Review
@@
 Visited private schools enrolled a much lower share of Black/Latinx/Native students than visited public schools.
-For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75% of visited private schools enrolled less than 20% Black/Latinx/Native students.
-
-Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495].
-Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students [@RN4724].
-Therefore, universities may visit predominantly white private high schools in search of non-white students.
-One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored [THIS PARAGRAPH SHOULD PROBABLY GO TO DISCUSSION].
+For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75% of visited private schools enrolled less than 20% Black/Latinx/Native students
 
@@
 
-Research question 2 asks about the characteristics of visited private high schools.
+Research question 2 asks about overlap in the private school recruiting networks of public and private universities.
+We observed substantial overlap and variation in recruiting networks of public universities.
+For example, the recruiting networks of the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass Amherst and Rutgers, which share substantial overlap with one another.
+Amongst the network of public and private universities, we observe substantial overlap and variation in recruiting networks.
+Figure \@ref(fig:plot-1mode-u) shows that three clusters emerge -- each containing some mix of public and private universities.
+The universities within a cluster have some overlap in the kinds of schools visited (e.g., TCU and University of South Carolina), but also share substantial overlap with particular universities in different clusters (e.g., Tufts and University of Pittsburgh).
+Whether we are categorizing universities by cluster analysis or by proximity on the network graph, we observe several different subsets of universities.
+Each of these subsets is associated with a different approach to private school visits and -- with the exception of a few universities like UC-Riverside and SUNY Stony Brook that don't play the private school game -- each of these subsets contained both public and private universities.
+
+Research question 3 asks about the characteristics of visited private high schools.
 We analyzed geographic region, religious affiliation, high school ranking, 12th grade enrollment, and racial composition.
@@
 For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools.
-By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.
-
-Research question 3 asks about overlap in the private school recruiting networks of public and private universities.
-Within the sample of public universities, we observed substantial overlap and variation in recruiting networks.
-For example, the recruiting networks of the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass Amherst and Rutgers, which share substantial overlap with one another.
-Across the entire sample of public and private universities, we also observed substantial overlap and variation in recruiting networks.
-Whether we are categorizing universities by cluster analysis or by proximity on the network graph, we observe several different subsets of universities.
-Each of these subsets is associated with a different approach to private school visits and -- with the exception of a few universities like UC-Riverside and SUNY Stony Brook -- each of these subsets contained both public and private universities.
-
-## Privatization of public research universities
-
-These findings contribute new insights about the privatization of public research universities.
-A weakness of the scholarly literature on privatization is that few studies compare public and private universities with respect to a behavior that is associated with private universities [@RN4543].
-We conceptualize recruiting visits to private schools as a behavior that is consistent with the social reproduction orientation of selective private universities and contrary to the historic social mobility mission associated with public research universities.
-Although we cannot make statements about the population of public research universities (ours is a convenience sample rather than a random sample), we can describe variation in how the public universities in our sample went about visiting private schools.
-
-At one end of the continuum lie public research universities that do not play the game, for example UC-Riverside and SUNY Stony Brook, visiting private schools at a lower rate than public schools (Figure \@ref(fig:actual-proportional-pubu)).
-For public universities that visited a substantial number of private schools, we observe substantial variation in the scale of visits and the characteristics of schools they target.
-While all private universities in our sample visited private schools at a much higher rate than public schools, we also see substantial variation amongst private universities in the scale and characteristics of private school visits.
-Amongst the network of public and private universities, Figure \@ref(fig:plot-1mode-u) shows that three clusters emerge -- each containing some mix of public and private universities.
-The universities within a cluster have some overlap in the kinds of schools visited (e.g., TCU and University of South Carolina), but also share substantial overlap with particular universities in different clusters (e.g., Tufts and University of Pittsburgh).
-
-In making large-scale visits to out-of-state private high schools, we argue that public research universities are mimicking the behavior of selective private universities in order to compete for students that have been traditionally targeted by private universities.
-Our rationale for this statement is that selective private universities have been recruiting heavily from private schools for a long time [@RN4642; @RN1565; @RN4407].
-By contrast, the pursuit of out-of-state students is a relatively new phenomenon for most public research universities.
-
+By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.n [ADD A SENTENCE OR TWO HERE]
+
+## Implications for Scholarship
+
+This study engages with two, previously disconnected literatures.
+Scholarship on nonresident enrollment observes that many public research universities began growing nonresident enrollment following declines in state appropriations [].
+Given that nonresident tuition price is often two- to three-times resident price, it is unsurprising that nonresident students tend to be more affluent than resident students, are less likely to be first-generation students, and are less likely to be Black or Latinx [CITE].
+Public research universities recruit nonresident students using institutional financial aid packages [CITE] and through recruiting interventions that target earlier stages in the enrollment funnel.
+Using nearly the same sample of 15 public research universities used in this study, Author (XXXX) found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools.
+Public research universities have a financial incentive to target private school students, who tend to come from affluent households able to pay nonresident tuition price without need-based aid.
+This study extends the literature on nonresident students by analyzing the scale of visits to private schools, the overlap and divergence in recruiting networks between public and private universities, and the characteristics of visited private schools.
+
+We also engage with scholarship on linkages between private schools and private universities, a linkage that sociologists have observed for many decades.
+Private school students comprise a disproportionate share of enrollment at selective private universities [CITE; AND AUTHOR CALCULATIONS].
+Practically, these linkages exist because private schools want to send their students to "good" universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profile and/or extracurricular activities.
+However, prior research tends to be focused on elite schools and universities [CITE KAHN; CHETTY; CHARTER+BARTER] and does not systematically analyzed connections between private schools and private universities that are selective, but not elite.
+This study extends the literature by investigating private school visits for a sample of 14 selective private universities that exhibit variation in geographic location, religious affiliation, and ranking.
+
+Our more important scholarly contribution is showing that these two separate stories are both parts of a broader narrative about the changing nature of competition for students from privileged schools and communities.
+Selective private universities have been recruiting  heavily from private schools for a long time [@RN4642; @RN3519; @RN4640].
+By contrast, the pursuit of out-of-state private school students by public research universities is a relatively new phenomenon and represents competition in the traditional hunting grounds of selective private universities.
+
+Our analyses shed light about the nature of this competition.
 When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
@@
 
-Finally, all public universities that visited a substantial number of private schools tended to visit schools that enrolled few Black, Latinx, or Native students.
-This finding is substantially driven by the fact that the national universe of private schools tends to enroll a much lower share of Black, Latinx, or Native students than the universe of public schools.
-However, the set of schools visited by the public universities in our sample enrolled fewer Black, Latinx, and Native students than the universe of private schools.
-Although we do not have data on household income, it is likely that the majority of students are wealthy at the private schools visited by public universities in our sample.
-
-Therefore, while public universities playing the private school game differ in terms of the set of schools they target, they all seem to be targeting schools that enroll mostly affluent students and few students who identify as Black, Latinx, or Native.
+While public universities playing the private school game differ in terms of the set of schools they target, they all seem to be targeting schools that enroll mostly affluent students and few students who identify as Black, Latinx, or Native.
 To the extent that these recruiting efforts yield dividends in terms of incoming freshmen, playing the private school game is likely to change the enrollment composition of public research universities in ways that run contrary to racial and socioeconomic diversity.
+
+## Implications for Practice
+
+Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the Covid pandemic.
+@RN4664 found that "travel" was the top-ranked top-ranked marketing/recruiting expenditure item for both public universities and private universities.
+During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events [CITE].
+Admissions counselors are now traveling again.
+@RN4896 found that travel was the fifth ranked expenditure item for public universities and the second ranked expenditure item for private universities.
+When asked about areas of future expenditure growth, travel was the top ranked item for public universities and the second ranked item for private universities @RN4896, suggesting that universities are increasing travel following the decline of the pandemic.
+
+Additionally, the EAB (XXXX) survey of high school counselors asked "how do you prefer to receive information from colleges?" High school visits by college representatives was the highest rated "channel" for both public school counselors and (especially) for private school counselors.
+By contrast, virtual visits by admissions representatives received low ratings by high school guidance counselors.
+Finally, @RN4895 asked universities to rank the most effective "outreach strategies for high school counselors." "Calling after visits" was deemed effective for 97% of private universities (the top strategy) and was deemed effective by 88% of public universities.
+What insights do we glean from these market research findings?
+In the era of mass marketing and data science, the pursuit of traditional college students from privileged schools and communities is still a hand-to-hand business and off-campus recruiting visits remain a vital means of recruiting these students.
+
+Considering the practical importance of off-campus recruiting visits, what are the practical implications of our research?
+Prior scholarly and market research [] shows that students are sensitive to recruiting interventions, including recruiting visits.
+This means that racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university.
+Our research on visits to public high schools [CITE] and this study on visits to private schools finds that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
+Some universities may publicly proclaim a commitment to social mobility and privately pursue an intentional recruiting strategy that targets affluent schools and communities.
+We offer practical guidance for universities that may be unintentionally implementing a recruiting strategy tied to social reproduction.
+
+Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools [e.g., @RN4495].
+Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students [@RN4724].
+Therefore, universities may visit predominantly white private high schools in search of non-white students.
+One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored
+
+In the aftermath of the Supreme Court decision on race conscious admissions, @RN4954 published a report titled *Strategies for Increasing Diversity and Opportunity in Higher Education.*  The report recommended that universities diversify the set of high schools they recruit from:
+
+>> Rather than recruiting primarily from private and public high schools composed of predominantly high-income students, institutions can expand and prioritize their outreach to high schools with substantial populations of low-income students and students of color.
+As part of expanding outreach, institutions can assign admissions recruiters to high schools from which they have not typically recruited to provide equal opportunity for all students
+
+We suspect that many universities may have incomplete knowledge about which schools they recruit from and how these schools compare to those they do not recruit from.
+Our rationale for this statement is that employee turnover in the enrollment management profession is quite high [CITE HOOVER] and many universities rely on expertise from third-party enrollment management consultancies [AUTHOR].
+Consistent with this idea, when issued public records requests to collect data on "student list" purchases from about 100 public universities [CITE], we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.
+
+For university leaders concerned about racial and socioeconomic equity in college access, we recommend conducting an internal audit of recruiting practices.
+How do the high schools and community colleges they visit differ racially, socioeconomically, and geographically from those they do not visit?
+How do the student list prospect profiles they purchase differ racially, socioeconomically, and geographically from those they do not purchase?
+We also recommend that students, faculty, and university stakeholders ask this question of the university president.
+It may be that the president is unaware and must ask the enrollment management office, which may begin a useful conversation.
+While universities may be aware of the composition of the schools they visit and the prospect profiles they purchase, we suspect that they may be less aware of how the composition of targeted schools/communities/students compares to the composition of not targeted schools/communities/students.
+If internal equity audits point to areas of inequity in recruiting behavior, university stakeholders can begin a discussion of how to address this issue.
 

### 2023-11-20 r_r/tables_and_figures.Rmd
update tables + figures

---
output:
  pdf_document:
    keep_tex: true
header-includes:
      - \newcommand{\beginsupplement}{
      - \setcounter{table}{0}  
      - \renewcommand{\thetable}{S\arabic{table}} 
      - \setcounter{figure}{0} 
      - \renewcommand{\thefigure}{S\arabic{figure}}}
---

\pagenumbering{gobble}
\begin{landscape}

```{r setup, include=FALSE}
library(knitr)
library(bookdown)

# https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_pdf.pdf
library(kableExtra)
library(tidyverse)
library(gridExtra)
library(scales)

knitr::opts_chunk$set(echo = F, message = F)

data_dir <- file.path('..', 'data')
tables_dir <- file.path('..', 'assets', 'tables')
figures_dir <- file.path('..', 'assets', 'figures')

univ_sample_df <- readRDS(file.path(data_dir, 'univ_sample.RDS')) %>%
  arrange(desc(classification), rank)
# events_df <- readRDS(file.path(data_dir, 'events_data.RDS'))
# 
# pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
# privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))

# ego_df <- readRDS(file.path(tables_dir, 'table_ego_all.RDS')) %>% 
#   mutate(
#     univ_region = str_split(characteristics, '\\|', simplify = T)[,1],
#     univ_religion = str_split(characteristics, '\\|', simplify = T)[,2],
#     univ_race = round(as.numeric(str_split(characteristics, '\\|', simplify = T)[,3]), 1),
#     univ_rank = as.numeric(str_split(characteristics, '\\|', simplify = T)[,4]),
#     univ_enroll = format(as.numeric(str_split(characteristics, '\\|', simplify = T)[,5]), big.mark = ',')
#   )
```

```{r sample-characteristics}
univ_sample <- univ_sample_df %>% 
  filter(classification != 'private_libarts') %>% 
  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal) %>% 
  mutate(
    classification = recode(
      classification,
      'public_research' = 'Public Research',
      'private_national' = 'Private National'
    ),
    satactcomp25 = format(round(satactcomp25), big.mark = ',', trim = T),
    satactcomp75 = format(round(satactcomp75), big.mark = ',', trim = T),
    tfuginst = str_c('\\$', format(round(tfuginst), big.mark = ',', trim = T)),
    tfugoutst = str_c('\\$', format(round(tfugoutst), big.mark = ',', trim = T)),
    ugftptfreshtot = format(round(ugftptfreshtot), big.mark = ',', trim = T),
    freshoutstpct = str_c(format(round(freshoutstpct * 100, 1), nsmall = 1), '\\%'),
    pgrnt_p = str_c(format(round(pgrnt_p, 1), nsmall = 1), '\\%'),
    pctfreshwh = str_c(format(round(pctfreshwh, 1), nsmall = 1), '\\%'),
    pctfreshbl = str_c(format(round(pctfreshbl, 1), nsmall = 1), '\\%'),
    pctfreshap = str_c(format(round(pctfreshap, 1), nsmall = 1), '\\%'),
    pctfreshhi = str_c(format(round(pctfreshhi, 1), nsmall = 1), '\\%'),
    pctfreshal = str_c(format(round(pctfreshal, 1), nsmall = 1), '\\%')
  ) %>% 
  arrange(desc(classification), rank)

names(univ_sample) <- c('Classification', 'University', 'Rank', '25th Percentile SAT/ACT Composite Score', '75th Percentile SAT/ACT Composite Score', 'In-State Tuition + Fees', 'Out-of-State Tuition + Fees', 'Total Enrolled Freshmen', 'Percent Out-of-State Freshmen', 'Percent Pell Recipients', 'Percent White Freshmen', 'Percent Black Freshmen', 'Percent Asian Freshmen', 'Percent Hispanic Freshmen', 'Percent International Freshmen')

kable(univ_sample, caption = "Characteristics of universities in analysis sample", booktabs = T, escape = F, align = 'c') %>%
  collapse_rows(columns = 1, latex_hline = 'major', valign = 'middle') %>%
  column_spec(c(2), width = '4.5cm', latex_valign = 'm') %>% 
  column_spec(c(3), width = '1.8cm', latex_valign = 'm') %>% 
  column_spec(c(4, 5), width = '3.8cm', latex_valign = 'm') %>% 
  column_spec(c(6, 8, 10:14), width = '2.4cm', latex_valign = 'm') %>% 
  column_spec(c(7), width = '2.7cm', latex_valign = 'm') %>% 
  column_spec(c(9, 15), width = '3cm', latex_valign = 'm') %>% 
  kable_styling(font_size = 13, latex_options = c('scale_down', 'hold_position'))
```

\clearpage

```{r sample-population-characteristics}
# Source: https://docs.google.com/spreadsheets/d/1e8lnU2YhJVigEYR55tc0pijsm52WKaEua8MNaYXTtM4
# Also in methodology: https://emraresearch.org/methodology

# 49 public research
pop_pubu <- c('151351', '171100', '180461', '188030', '199193', '147703', '204857', '207388', '214777', '186380', '149222', '196088', '196097', '204796', '100751', '197036', '164155', '104179', '106397', '110635', '110644', '110653', '110662', '110671', '110680', '201885', '126614', '129020', '139959', '141574', '225511', '142285', '155317', '161253', '163286', '166629', '170976', '181464', '187985', '199120', '215293', '217484', '218663', '230764', '234076', '236948', '230728', '234030', '172644')

# 49 private national
pop_privu <- c('194824', '139658', '190150', '223232', '212054', '193900', '166027', '144050', '130794', '243744', '166683', '198419', '215062', '162928', '182670', '110404', '147767', '217156', '190415', '227757', '152080', '186131', '221999', '131496', '164988', '160755', '213543', '135726', '216597', '228246', '191241', '186867', '131159', '228875', '239105', '127060', '122436', '207971', '179159', '168148', '164924', '195030', '179867', '201645', '197708', '199847', '211440', '121150', '123961')

sample_pubu <- (univ_sample_df %>% filter(classification == 'public_research'))$univ_id
sample_privu <- (univ_sample_df %>% filter(classification == 'private_national'))$univ_id

univ_pop <- read.csv(file.path(data_dir, 'ipeds_data.csv'), header = TRUE, na.strings = c('', 'NULL', 'NA'), stringsAsFactors = FALSE, colClasses = c('unitid' = 'character')) %>% as_tibble() %>%
  filter(endyear == 2017, unitid %in% c(pop_pubu, pop_privu, sample_pubu, sample_privu)) %>% 
  select(unitid, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_n, cohortsfaef, ugftptfreshwhmf, ugftptfreshblmf, ugftptfreshapmf, ugftptfreshhimf, ugftptfreshalmf, ugftptfreshmrmf, ugftptfreshnamf, ugftptfreshunmf, ugftptfreshasmf, ugftptfreshnhmf) %>% 
  mutate(
    pgrnt_p = pgrnt_n / cohortsfaef * 100,
    pctfreshwh = ugftptfreshwhmf / ugftptfreshtot * 100,
    pctfreshbl = ugftptfreshblmf / ugftptfreshtot * 100,
    pctfreshap = ugftptfreshapmf / ugftptfreshtot * 100,  # ap = as + nh
    pctfreshhi = ugftptfreshhimf / ugftptfreshtot * 100,
    pctfreshal = ugftptfreshalmf / ugftptfreshtot * 100,
    pctfreshmr = ugftptfreshmrmf / ugftptfreshtot * 100,
    pctfreshna = ugftptfreshnamf / ugftptfreshtot * 100,
    pctfreshun = ugftptfreshunmf / ugftptfreshtot * 100,
    pctfreshas = ugftptfreshasmf / ugftptfreshtot * 100,
    pctfreshnh = ugftptfreshnhmf / ugftptfreshtot * 100
  ) %>% 
  select(unitid, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)

format_data <- function(univ_ids) {
  apply(univ_pop %>% filter(unitid %in% univ_ids) %>% select(-unitid), 2, function(x) quantile(x, probs = c(0.25, 0.5, 0.75), na.rm = T)) %>% 
    as.data.frame() %>% 
    mutate(
      satactcomp25 = format(round(satactcomp25), big.mark = ',', trim = T),
      satactcomp75 = format(round(satactcomp75), big.mark = ',', trim = T),
      tfuginst = str_c('\\$', format(round(tfuginst), big.mark = ',', trim = T)),
      tfugoutst = str_c('\\$', format(round(tfugoutst), big.mark = ',', trim = T)),
      ugftptfreshtot = format(round(ugftptfreshtot), big.mark = ',', trim = T),
      freshoutstpct = str_c(format(round(freshoutstpct * 100, 1), nsmall = 1), '\\%'),
      pgrnt_p = str_c(format(round(pgrnt_p, 1), nsmall = 1), '\\%'),
      pctfreshwh = str_c(format(round(pctfreshwh, 1), nsmall = 1), '\\%'),
      pctfreshbl = str_c(format(round(pctfreshbl, 1), nsmall = 1), '\\%'),
      pctfreshap = str_c(format(round(pctfreshap, 1), nsmall = 1), '\\%'),
      pctfreshhi = str_c(format(round(pctfreshhi, 1), nsmall = 1), '\\%'),
      pctfreshal = str_c(format(round(pctfreshal, 1), nsmall = 1), '\\%')
    ) %>% 
    t()
}

univ_pop_df <- cbind(
  format_data(sample_pubu),
  format_data(pop_pubu),
  format_data(sample_privu),
  format_data(pop_privu)
)
rownames(univ_pop_df) <- c('25th Percentile SAT/ACT Composite Score', '75th Percentile SAT/ACT Composite Score', 'In-State Tuition + Fees', 'Out-of-State Tuition + Fees', 'Total Enrolled Freshmen', 'Percent Out-of-State Freshmen', 'Percent Pell Recipients', 'Percent White Freshmen', 'Percent Black Freshmen', 'Percent Asian Freshmen', 'Percent Hispanic Freshmen', 'Percent International Freshmen')
colnames(univ_pop_df) <- rep(c('25th percentile', '50th percentile', '75th percentile'), 4)

kable(univ_pop_df, caption = "Characteristics of universities in analysis sample compared to data collection sample", booktabs = T, escape = F, align = 'c', linesep = '') %>%
  add_header_above(header = c(' ' = 1, 'Analysis sample (N=15)' = 3, 'Data collection sample (N=49)' = 3, 'Analysis sample (N=14)' = 3, 'Data collection sample (N=49)' = 3)) %>%
  add_header_above(header = c(' ' = 1, 'Public research universities' = 6, 'Selective private universities' = 6)) %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

\clearpage

```{r pubu-percent-matrix}
table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)

kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(7, 9, 15), width = '5em') %>%
  column_spec(c(4, 12), width = '5.5em') %>%
  column_spec(c(6, 10, 16), width = '6em') %>%
  column_spec(c(2, 11, 13), width = '6.5em') %>%
  column_spec(c(3, 8), width = '7em') %>%
  column_spec(c(5), width = '7.5em') %>%
  column_spec(c(14), width = '8.8em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

```{r privu-percent-matrix}
table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)

kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

\clearpage

```{r privu-percent-visited-by-pubu-matrix}
table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)

kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down')
```

```{r pubu-percent-visited-by-privu-matrix}
table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)

kable(table_1mode_u$onemode_pct_df[c(2,3,4,5,6,8,10,11,12,14,15,19,20,26),c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29)], caption = 'For public universities, the percent of high schools visited by private universities', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(7, 9, 15), width = '5em') %>%
  column_spec(c(4, 12), width = '5.5em') %>%
  column_spec(c(6, 10, 16), width = '6em') %>%
  column_spec(c(2, 11, 13), width = '6.5em') %>%
  column_spec(c(3, 8), width = '7em') %>%
  column_spec(c(5), width = '7.5em') %>%
  column_spec(c(14), width = '8.8em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down')
```

\clearpage
\newpage

```{r nd-religion, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Order 2 ego network of University of Notre Dame, vertices colored by religion"}
include_graphics(file.path(figures_dir, 'nd_religion.pdf'))
```

\newpage

```{r events-hs-count-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits to public and private high schools by public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
```

\newpage

```{r events-hs-count-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
```

\newpage

```{r actual-proportional-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
```

\clearpage

```{r actual-proportional-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
```

\newpage

```{r plot-1mode-u, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_u.pdf'))
```

\clearpage

```{r region-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Geographic region of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
```

\newpage

```{r religion-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Religious affiliation of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
```

\newpage

```{r rank-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "High school ranking of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
```

\newpage

```{r race-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, public research universities"}
include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privhs_pubhs.pdf'))
```

\newpage

```{r race-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, selective private universities"}
include_graphics(file.path(figures_dir, 'ego_network_race_privu_privhs_pubhs.pdf'))
```

\beginsupplement
\clearpage
\newpage

```{r pubu-count-matrix}
rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)

kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(7, 9, 15), width = '5em') %>%
  column_spec(c(4, 12), width = '5.5em') %>%
  column_spec(c(6, 10, 16), width = '6em') %>%
  column_spec(c(2, 11, 13), width = '6.5em') %>%
  column_spec(c(3, 8), width = '7em') %>%
  column_spec(c(5), width = '7.5em') %>%
  column_spec(c(14), width = '8.8em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

```{r privu-count-matrix}
table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
rownames(table_1mode_privu$onemode_df) <- colnames(table_1mode_privu$onemode_df)

kable(table_1mode_privu$onemode_df, caption = 'One-mode private universities count matrix', booktabs = T, align = 'c', linesep = '') %>%
  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
  column_spec(14:15, width = '8.5em') %>%
  kable_styling(font_size = 13, latex_options = 'scale_down') 
```

\newpage

```{r events-count-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
```

\newpage

```{r events-count-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
```

\newpage

```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public institutions, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))
```

```{r plot-1mode-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for private universities, colored by cluster"}
knitr::include_graphics(file.path(figures_dir, 'plot_1mode_privu.pdf'))
```

\newpage

```{r enroll-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "12th grade enrollment of visited private high schools"}
include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privu.pdf'))
```

\newpage

```{r enroll-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "12th grade enrollment of visited private high schools vs. public high schools, public research universities"}
include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privhs_pubhs.pdf'))
```

\end{landscape}

\restoregeometry

### 2023-11-20 r_r/tables_and_figures.tex
update tables + figures

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\author{}
\date{\vspace{-2.5em}}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newcommand{\beginsupplement}{
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}

\pagenumbering{gobble}
\begin{landscape}

\begin{table}[!h]

\caption{\label{tab:sample-characteristics}Characteristics of universities in analysis sample}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{c>{\centering\arraybackslash}m{4.5cm}>{\centering\arraybackslash}m{1.8cm}>{\centering\arraybackslash}m{3.8cm}>{\centering\arraybackslash}m{3.8cm}>{\centering\arraybackslash}m{2.4cm}>{\centering\arraybackslash}m{2.7cm}>{\centering\arraybackslash}m{2.4cm}>{\centering\arraybackslash}m{3cm}>{\centering\arraybackslash}m{2.4cm}>{\centering\arraybackslash}m{2.4cm}>{\centering\arraybackslash}m{2.4cm}>{\centering\arraybackslash}m{2.4cm}>{\centering\arraybackslash}m{2.4cm}>{\centering\arraybackslash}m{3cm}}
\toprule
Classification & University & Rank & 25th Percentile SAT/ACT Composite Score & 75th Percentile SAT/ACT Composite Score & In-State Tuition + Fees & Out-of-State Tuition + Fees & Total Enrolled Freshmen & Percent Out-of-State Freshmen & Percent Pell Recipients & Percent White Freshmen & Percent Black Freshmen & Percent Asian Freshmen & Percent Hispanic Freshmen & Percent International Freshmen\\
\midrule
 & UC Berkeley & 22 & 1,316 & 1,527 & \$13,807 & \$41,076 & 6,252 & 24.4\% & 19.4\% & 25.6\% & 1.8\% & 42.7\% & 13.8\% & 9.3\%\\

 & UC San Diego & 35 & 1,193 & 1,455 & \$13,946 & \$41,215 & 5,748 & 26.5\% & 30.7\% & 15.5\% & 1.5\% & 34.4\% & 20.6\% & 21.6\%\\

 & U of Georgia & 47 & 1,165 & 1,360 & \$11,890 & \$30,502 & 5,433 & 12.3\% & 20.3\% & 68.0\% & 8.1\% & 12.4\% & 5.8\% & 1.6\%\\

 & U of Pitt & 58 & 1,202 & 1,395 & \$19,028 & \$30,414 & 5,644 & 30.6\% & 20.3\% & 68.5\% & 7.3\% & 9.3\% & 4.3\% & 3.6\%\\

 & Rutgers & 63 & 1,110 & 1,350 & \$14,689 & \$30,684 & 6,465 & 17.8\% & 27.0\% & 35.5\% & 6.0\% & 31.3\% & 12.1\% & 10.4\%\\

 & UMass Amherst & 66 & 1,135 & 1,332 & \$15,301 & \$32,914 & 4,679 & 26.9\% & 21.5\% & 61.0\% & 3.8\% & 12.5\% & 6.0\% & 8.1\%\\

 & UC Riverside & 88 & 956 & 1,200 & \$13,880 & \$41,150 & 5,358 & 2.2\% & 56.6\% & 10.1\% & 4.0\% & 31.1\% & 47.2\% & 2.5\%\\

 & SUNY Stony Brook & 88 & 1,163 & 1,373 & \$9,197 & \$26,817 & 2,934 & 25.8\% & 34.6\% & 27.8\% & 5.9\% & 28.8\% & 11.0\% & 16.5\%\\

 & CU Boulder & 103 & 1,126 & 1,331 & \$11,785 & \$35,852 & 6,421 & 47.2\% & 14.6\% & 66.3\% & 1.5\% & 5.6\% & 12.5\% & 7.5\%\\

 & U of S.Carolina & 118 & 1,135 & 1,321 & \$11,706 & \$31,562 & 5,110 & 53.2\% & 15.4\% & 82.1\% & 5.0\% & 3.0\% & 4.3\% & 1.2\%\\

 & U of Kansas & 124 & 1,070 & 1,300 & \$10,781 & \$26,503 & 4,233 & 42.8\% & 23.4\% & 72.1\% & 4.3\% & 4.5\% & 8.7\% & 4.6\%\\

 & UNL & 133 & 1,027 & 1,262 & \$8,725 & \$23,558 & 4,860 & 29.9\% & 23.9\% & 75.6\% & 3.1\% & 2.5\% & 7.2\% & 6.3\%\\

 & U of Alabama & 143 & 1,053 & 1,351 & \$10,701 & \$27,544 & 7,559 & 68.1\% & 17.0\% & 80.6\% & 8.0\% & 1.3\% & 5.3\% & 0.8\%\\

 & U of Cincinnati & 143 & 1,063 & 1,265 & \$11,242 & \$26,914 & 6,913 & 13.1\% & 26.7\% & 74.9\% & 9.0\% & 3.8\% & 3.5\% & 2.4\%\\

\multirow{-15}{*}{\centering\arraybackslash Public Research} & U of Arkansas & 160 & 1,057 & 1,283 & \$9,014 & \$23,678 & 4,972 & 51.0\% & 19.5\% & 78.7\% & 3.9\% & 2.6\% & 8.5\% & 1.0\%\\
\cmidrule{1-15}
 & Northwestern & 9 & 1,413 & 1,527 & \$51,975 & \$51,975 & 1,985 & 69.8\% & 17.8\% & 46.1\% & 5.0\% & 16.7\% & 13.6\% & 9.7\%\\

 & Notre Dame & 19 & 1,395 & 1,553 & \$50,780 & \$50,780 & 2,046 & 94.5\% & 11.9\% & 67.8\% & 4.5\% & 5.3\% & 10.7\% & 5.9\%\\

 & Emory & 21 & 1,313 & 1,481 & \$49,011 & \$49,011 & 1,358 & 85.5\% & 17.5\% & 40.9\% & 7.1\% & 18.8\% & 10.8\% & 16.1\%\\

 & Tufts & 30 & 1,375 & 1,515 & \$53,585 & \$53,585 & 1,336 & 80.2\% & 10.2\% & 54.9\% & 4.8\% & 13.4\% & 6.7\% & 11.4\%\\

 & Boston Coll. & 35 & 1,297 & 1,460 & \$52,426 & \$52,426 & 2,254 & 76.6\% & 12.8\% & 61.4\% & 2.8\% & 10.7\% & 11.1\% & 6.8\%\\

 & Tulane & 41 & 1,277 & 1,416 & \$52,134 & \$52,134 & 1,856 & 87.6\% & 7.8\% & 76.0\% & 4.3\% & 5.7\% & 5.8\% & 4.3\%\\

 & Case Western Res. & 42 & 1,314 & 1,501 & \$47,020 & \$47,020 & 1,265 & 75.7\% & 10.0\% & 48.1\% & 4.3\% & 19.6\% & 6.2\% & 15.6\%\\

 & Villanova & 53 & 1,280 & 1,420 & \$50,366 & \$50,366 & 1,678 & 83.1\% & 9.7\% & 76.0\% & 4.7\% & 5.5\% & 6.9\% & 1.5\%\\

 & SMU & 66 & 1,244 & 1,416 & \$51,467 & \$51,467 & 1,522 & 61.6\% & 10.2\% & 66.4\% & 5.6\% & 5.9\% & 11.0\% & 6.3\%\\

 & Baylor & 76 & 1,163 & 1,329 & \$42,931 & \$42,931 & 3,503 & 35.3\% & 17.4\% & 65.4\% & 6.2\% & 5.5\% & 15.3\% & 2.9\%\\

 & U of Denver & 80 & 1,166 & 1,359 & \$47,445 & \$47,445 & 1,399 & 67.5\% & 14.6\% & 73.5\% & 2.0\% & 4.3\% & 9.8\% & 5.6\%\\

 & TCU & 80 & 1,125 & 1,321 & \$43,610 & \$43,610 & 1,888 & 56.6\% & 11.2\% & 72.9\% & 4.7\% & 3.1\% & 13.3\% & 3.7\%\\

 & Stevens Ins. Tech & 80 & 1,274 & 1,447 & \$49,914 & \$49,914 & 737 & 38.8\% & 15.5\% & 65.4\% & 2.7\% & 14.7\% & 10.0\% & 4.6\%\\

\multirow{-14}{*}{\centering\arraybackslash Private National} & Marquette & 88 & 1,101 & 1,296 & \$39,318 & \$39,318 & 2,005 & 71.4\% & 19.0\% & 68.0\% & 4.9\% & 8.1\% & 13.3\% & 2.5\%\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\begin{table}

\caption{\label{tab:sample-population-characteristics}Characteristics of universities in analysis sample compared to data collection sample}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{lcccccccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Public research universities} & \multicolumn{6}{c}{Selective private universities} \\
\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Analysis sample (N=15)} & \multicolumn{3}{c}{Data collection sample (N=49)} & \multicolumn{3}{c}{Analysis sample (N=14)} & \multicolumn{3}{c}{Data collection sample (N=49)} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10} \cmidrule(l{3pt}r{3pt}){11-13}
  & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile\\
\midrule
25th Percentile SAT/ACT Composite Score & 1,060 & 1,126 & 1,164 & 985 & 1,083 & 1,169 & 1,185 & 1,278 & 1,314 & 1,212 & 1,313 & 1,402\\
75th Percentile SAT/ACT Composite Score & 1,292 & 1,332 & 1,366 & 1,219 & 1,307 & 1,376 & 1,373 & 1,433 & 1,496 & 1,411 & 1,481 & 1,549\\
In-State Tuition + Fees & \$10,741 & \$11,785 & \$13,913 & \$9,463 & \$11,547 & \$13,843 & \$47,126 & \$50,140 & \$51,848 & \$47,445 & \$50,394 & \$51,975\\
Out-of-State Tuition + Fees & \$26,866 & \$30,502 & \$34,383 & \$26,594 & \$30,414 & \$35,279 & \$47,126 & \$50,140 & \$51,848 & \$47,445 & \$50,394 & \$51,975\\
Total Enrolled Freshmen & 4,916 & 5,433 & 6,336 & 3,601 & 4,860 & 6,421 & 1,368 & 1,767 & 2,000 & 1,306 & 1,591 & 1,985\\
Percent Out-of-State Freshmen & 21.1\% & 26.9\% & 45.0\% & 16.7\% & 27.2\% & 42.8\% & 63.1\% & 73.6\% & 82.4\% & 66.4\% & 76.6\% & 87.6\%\\
Percent Pell Recipients & 19.5\% & 21.5\% & 26.8\% & 19.5\% & 23.9\% & 32.8\% & 10.2\% & 12.4\% & 16.9\% & 12.9\% & 14.3\% & 17.1\%\\
Percent White Freshmen & 31.6\% & 68.0\% & 75.2\% & 37.7\% & 62.7\% & 70.0\% & 56.5\% & 65.9\% & 71.7\% & 40.9\% & 49.3\% & 65.3\%\\
Percent Black Freshmen & 3.4\% & 4.3\% & 6.6\% & 2.2\% & 4.9\% & 7.6\% & 4.3\% & 4.7\% & 5.0\% & 4.1\% & 5.4\% & 7.1\%\\
Percent Asian Freshmen & 3.4\% & 9.3\% & 29.9\% & 3.2\% & 6.7\% & 16.2\% & 5.5\% & 7.0\% & 14.3\% & 7.7\% & 14.7\% & 19.6\%\\
Percent Hispanic Freshmen & 5.5\% & 8.5\% & 12.3\% & 6.4\% & 8.7\% & 13.4\% & 7.6\% & 10.7\% & 12.8\% & 9.0\% & 10.7\% & 13.3\%\\
Percent International Freshmen & 2.0\% & 4.6\% & 8.7\% & 1.6\% & 3.5\% & 8.7\% & 3.8\% & 5.7\% & 9.0\% & 6.3\% & 10.0\% & 11.6\%\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\begin{table}

\caption{\label{tab:pubu-percent-matrix}One-mode public university percent matrix}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{5.5em}>{\centering\arraybackslash}p{7.5em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{5.5em}>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{8.8em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{6em}}
\toprule
  & U of Alabama (N=759) & U of S.Carolina (N=396) & CU Boulder (N=362) & UMass Amherst (N=296) & U of Georgia (N=256) & Rutgers (N=255) & U of Cincinnati (N=243) & U of Pitt (N=222) & UC Berkeley (N=200) & UC San Diego (N=192) & U of Kansas (N=173) & U of Arkansas (N=163) & SUNY Stony Brook (N=119) & UNL (N=100) & UC Riverside (N=88)\\
\midrule
U of Alabama (N=759) & 100.0 & 71.7 & 58.0 & 50.3 & 66.0 & 47.1 & 51.0 & 56.3 & 56.0 & 52.1 & 53.8 & 61.3 & 36.1 & 31 & 38.6\\
U of S.Carolina (N=396) & 37.4 & 100.0 & 42.8 & 36.5 & 54.7 & 29.0 & 45.3 & 44.6 & 42.0 & 30.7 & 33.5 & 35.0 & 22.7 & 20 & 21.6\\
CU Boulder (N=362) & 27.7 & 39.1 & 100.0 & 38.9 & 34.4 & 29.8 & 28.4 & 41.4 & 38.5 & 51.0 & 42.8 & 31.3 & 17.6 & 25 & 31.8\\
UMass Amherst (N=296) & 19.6 & 27.3 & 31.8 & 100.0 & 22.3 & 36.5 & 11.1 & 25.2 & 22.5 & 29.7 & 10.4 & 8.6 & 47.9 & 4 & 20.5\\
U of Georgia (N=256) & 22.3 & 35.4 & 24.3 & 19.3 & 100.0 & 9.4 & 30.0 & 21.6 & 32.0 & 19.8 & 22.5 & 36.2 & 5.9 & 13 & 18.2\\
Rutgers (N=255) & 15.8 & 18.7 & 21.0 & 31.4 & 9.4 & 100.0 & 14.4 & 33.3 & 20.5 & 22.4 & 11.6 & 3.1 & 40.3 & 10 & 11.4\\
U of Cincinnati (N=243) & 16.3 & 27.8 & 19.1 & 9.1 & 28.5 & 13.7 & 100.0 & 25.2 & 16.5 & 12.5 & 16.8 & 22.7 & 4.2 & 18 & 9.1\\
U of Pitt (N=222) & 16.5 & 25.0 & 25.4 & 18.9 & 18.8 & 29.0 & 23.0 & 100.0 & 20.5 & 14.6 & 18.5 & 16.0 & 22.7 & 15 & 12.5\\
UC Berkeley (N=200) & 14.8 & 21.2 & 21.3 & 15.2 & 25.0 & 16.1 & 13.6 & 18.5 & 100.0 & 31.8 & 17.3 & 16.0 & 7.6 & 8 & 22.7\\
UC San Diego (N=192) & 13.2 & 14.9 & 27.1 & 19.3 & 14.8 & 16.9 & 9.9 & 12.6 & 30.5 & 100.0 & 16.8 & 13.5 & 9.2 & 3 & 39.8\\
U of Kansas (N=173) & 12.3 & 14.6 & 20.4 & 6.1 & 15.2 & 7.8 & 11.9 & 14.4 & 15.0 & 15.1 & 100.0 & 38.0 & 0.0 & 61 & 9.1\\
U of Arkansas (N=163) & 13.2 & 14.4 & 14.1 & 4.7 & 23.0 & 2.0 & 15.2 & 11.7 & 13.0 & 11.5 & 35.8 & 100.0 & 0.8 & 24 & 10.2\\
SUNY Stony Brook (N=119) & 5.7 & 6.8 & 5.8 & 19.3 & 2.7 & 18.8 & 2.1 & 12.2 & 4.5 & 5.7 & 0.0 & 0.6 & 100.0 & 0 & 4.5\\
UNL (N=100) & 4.1 & 5.1 & 6.9 & 1.4 & 5.1 & 3.9 & 7.4 & 6.8 & 4.0 & 1.6 & 35.3 & 14.7 & 0.0 & 100 & 0.0\\
UC Riverside (N=88) & 4.5 & 4.8 & 7.7 & 6.1 & 6.2 & 3.9 & 3.3 & 5.0 & 10.0 & 18.2 & 4.6 & 5.5 & 3.4 & 0 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}

\caption{\label{tab:privu-percent-matrix}One-mode private university percent matrix}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{8.5em}>{\centering\arraybackslash}p{8.5em}}
\toprule
  & Notre Dame (N=625) & Villanova (N=563) & SMU (N=550) & TCU (N=435) & Tulane (N=430) & Northwestern (N=377) & Boston Coll. (N=339) & Marquette (N=331) & Tufts (N=301) & U of Denver (N=279) & Emory (N=273) & Baylor (N=237) & Case Western Res. (N=228) & Stevens Ins. Tech (N=160)\\
\midrule
Notre Dame (N=625) & 100.0 & 60.0 & 53.3 & 58.2 & 51.9 & 59.4 & 69.3 & 69.8 & 58.8 & 58.8 & 53.1 & 41.8 & 58.3 & 49.4\\
Villanova (N=563) & 54.1 & 100.0 & 52.9 & 51.5 & 50.7 & 56.8 & 61.4 & 61.9 & 53.5 & 51.3 & 53.8 & 42.6 & 62.3 & 64.4\\
SMU (N=550) & 46.9 & 51.7 & 100.0 & 66.7 & 64.0 & 64.5 & 64.3 & 45.6 & 62.8 & 63.4 & 64.5 & 65.0 & 58.8 & 55.0\\
TCU (N=435) & 40.5 & 39.8 & 52.7 & 100.0 & 46.3 & 46.9 & 49.6 & 45.3 & 46.8 & 54.1 & 44.7 & 56.1 & 43.0 & 41.2\\
Tulane (N=430) & 35.7 & 38.7 & 50.0 & 45.7 & 100.0 & 58.1 & 51.0 & 31.1 & 63.1 & 50.9 & 52.4 & 33.3 & 57.5 & 35.0\\
Northwestern (N=377) & 35.8 & 38.0 & 44.2 & 40.7 & 50.9 & 100.0 & 50.7 & 34.4 & 56.1 & 49.8 & 46.9 & 31.6 & 53.5 & 34.4\\
Boston Coll. (N=339) & 37.6 & 36.9 & 39.6 & 38.6 & 40.2 & 45.6 & 100.0 & 40.2 & 52.5 & 48.4 & 41.4 & 27.0 & 43.9 & 37.5\\
Marquette (N=331) & 37.0 & 36.4 & 27.5 & 34.5 & 24.0 & 30.2 & 39.2 & 100.0 & 25.6 & 34.8 & 19.0 & 26.2 & 28.9 & 26.9\\
Tufts (N=301) & 28.3 & 28.6 & 34.4 & 32.4 & 44.2 & 44.8 & 46.6 & 23.3 & 100.0 & 40.9 & 42.9 & 21.9 & 47.4 & 41.2\\
U of Denver (N=279) & 26.2 & 25.4 & 32.2 & 34.7 & 33.0 & 36.9 & 39.8 & 29.3 & 37.9 & 100.0 & 30.0 & 24.1 & 31.6 & 27.5\\
Emory (N=273) & 23.2 & 26.1 & 32.0 & 28.0 & 33.3 & 34.0 & 33.3 & 15.7 & 38.9 & 29.4 & 100.0 & 16.5 & 43.0 & 26.2\\
Baylor (N=237) & 15.8 & 17.9 & 28.0 & 30.6 & 18.4 & 19.9 & 18.9 & 18.7 & 17.3 & 20.4 & 14.3 & 100.0 & 21.9 & 14.4\\
Case Western Res. (N=228) & 21.3 & 25.2 & 24.4 & 22.5 & 30.5 & 32.4 & 29.5 & 19.9 & 35.9 & 25.8 & 35.9 & 21.1 & 100.0 & 25.6\\
Stevens Ins. Tech (N=160) & 12.6 & 18.3 & 16.0 & 15.2 & 13.0 & 14.6 & 17.7 & 13.0 & 21.9 & 15.8 & 15.4 & 9.7 & 18.0 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\begin{table}

\caption{\label{tab:privu-percent-visited-by-pubu-matrix}For private universities, the percent of high schools visited by public universities}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{8.5em}>{\centering\arraybackslash}p{8.5em}}
\toprule
  & Notre Dame (N=625) & Villanova (N=563) & SMU (N=550) & TCU (N=435) & Tulane (N=430) & Northwestern (N=377) & Boston Coll. (N=339) & Marquette (N=331) & Tufts (N=301) & U of Denver (N=279) & Emory (N=273) & Baylor (N=237) & Case Western Res. (N=228) & Stevens Ins. Tech (N=160)\\
\midrule
U of Alabama (N=759) & 52.2 & 51.0 & 56.9 & 59.8 & 51.2 & 48.8 & 54.9 & 53.5 & 46.5 & 48.7 & 60.1 & 57.8 & 53.5 & 48.8\\
U of S.Carolina (N=396) & 30.7 & 36.2 & 40.5 & 43.9 & 37.0 & 36.1 & 35.7 & 31.1 & 35.2 & 35.5 & 44.0 & 38.8 & 34.6 & 36.9\\
CU Boulder (N=362) & 34.4 & 33.2 & 40.2 & 46.4 & 41.4 & 42.4 & 42.2 & 40.5 & 46.2 & 49.8 & 38.1 & 42.2 & 42.5 & 35.0\\
UMass Amherst (N=296) & 21.0 & 24.3 & 22.7 & 24.8 & 26.5 & 21.5 & 33.0 & 21.1 & 31.9 & 27.2 & 20.1 & 9.3 & 17.1 & 41.2\\
U of Georgia (N=256) & 17.9 & 22.7 & 28.4 & 27.8 & 27.7 & 27.3 & 21.8 & 13.3 & 23.6 & 17.2 & 32.2 & 32.5 & 20.2 & 20.0\\
Rutgers (N=255) & 19.0 & 22.9 & 14.0 & 16.8 & 15.8 & 16.4 & 20.4 & 16.9 & 17.3 & 16.5 & 17.2 & 7.6 & 20.2 & 41.9\\
U of Cincinnati (N=243) & 17.3 & 21.7 & 18.7 & 19.3 & 16.7 & 22.8 & 16.8 & 22.4 & 14.0 & 20.4 & 22.0 & 17.3 & 18.0 & 15.6\\
U of Pitt (N=222) & 20.5 & 27.5 & 18.0 & 18.9 & 19.1 & 19.6 & 20.1 & 19.0 & 21.3 & 15.8 & 17.2 & 15.6 & 27.2 & 30.6\\
UC Berkeley (N=200) & 16.3 & 19.0 & 21.1 & 21.4 & 24.4 & 27.9 & 21.8 & 13.9 & 28.9 & 19.7 & 27.8 & 16.0 & 27.2 & 17.5\\
UC San Diego (N=192) & 17.1 & 14.4 & 18.2 & 22.3 & 17.4 & 22.0 & 25.4 & 17.5 & 28.9 & 25.4 & 18.3 & 18.1 & 21.9 & 20.6\\
U of Kansas (N=173) & 14.4 & 15.1 & 16.2 & 20.7 & 13.5 & 17.0 & 15.0 & 27.2 & 12.0 & 24.7 & 10.3 & 23.2 & 16.2 & 7.5\\
U of Arkansas (N=163) & 8.8 & 11.5 & 19.6 & 19.8 & 15.8 & 13.3 & 9.4 & 13.6 & 10.0 & 14.3 & 10.6 & 35.4 & 15.4 & 8.1\\
SUNY Stony Brook (N=119) & 8.0 & 10.7 & 5.8 & 7.4 & 5.6 & 4.0 & 6.8 & 8.5 & 8.6 & 5.0 & 3.7 & 0.4 & 7.9 & 21.9\\
UNL (N=100) & 6.9 & 8.2 & 7.1 & 8.5 & 5.1 & 8.2 & 6.2 & 12.7 & 4.7 & 9.7 & 2.9 & 8.9 & 7.0 & 1.9\\
UC Riverside (N=88) & 5.6 & 5.0 & 4.9 & 6.7 & 5.6 & 7.4 & 6.8 & 5.1 & 8.0 & 6.1 & 4.0 & 7.6 & 6.6 & 3.8\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}

\caption{\label{tab:pubu-percent-visited-by-privu-matrix}For public universities, the percent of high schools visited by private universities}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{5.5em}>{\centering\arraybackslash}p{7.5em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{5.5em}>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{8.8em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{6em}}
\toprule
  & U of Alabama (N=759) & U of S.Carolina (N=396) & CU Boulder (N=362) & UMass Amherst (N=296) & U of Georgia (N=256) & Rutgers (N=255) & U of Cincinnati (N=243) & U of Pitt (N=222) & UC Berkeley (N=200) & UC San Diego (N=192) & U of Kansas (N=173) & U of Arkansas (N=163) & SUNY Stony Brook (N=119) & UNL (N=100) & UC Riverside (N=88)\\
\midrule
Notre Dame (N=625) & 43.0 & 48.5 & 59.4 & 44.3 & 43.8 & 46.7 & 44.4 & 57.7 & 51.0 & 55.7 & 52.0 & 33.7 & 42.0 & 43 & 39.8\\
Villanova (N=563) & 37.8 & 51.5 & 51.7 & 46.3 & 50.0 & 50.6 & 50.2 & 69.8 & 53.5 & 42.2 & 49.1 & 39.9 & 50.4 & 46 & 31.8\\
SMU (N=550) & 41.2 & 56.3 & 61.0 & 42.2 & 60.9 & 30.2 & 42.4 & 44.6 & 58.0 & 52.1 & 51.4 & 66.3 & 26.9 & 39 & 30.7\\
TCU (N=435) & 34.3 & 48.2 & 55.8 & 36.5 & 47.3 & 28.6 & 34.6 & 36.9 & 46.5 & 50.5 & 52.0 & 52.8 & 26.9 & 37 & 33.0\\
Tulane (N=430) & 29.0 & 40.2 & 49.2 & 38.5 & 46.5 & 26.7 & 29.6 & 36.9 & 52.5 & 39.1 & 33.5 & 41.7 & 20.2 & 22 & 27.3\\
Northwestern (N=377) & 24.2 & 34.3 & 44.2 & 27.4 & 40.2 & 24.3 & 35.4 & 33.3 & 52.5 & 43.2 & 37.0 & 30.7 & 12.6 & 31 & 31.8\\
Boston Coll. (N=339) & 24.5 & 30.6 & 39.5 & 37.8 & 28.9 & 27.1 & 23.5 & 30.6 & 37.0 & 44.8 & 29.5 & 19.6 & 19.3 & 21 & 26.1\\
Marquette (N=331) & 23.3 & 26.0 & 37.0 & 23.6 & 17.2 & 22.0 & 30.5 & 28.4 & 23.0 & 30.2 & 52.0 & 27.6 & 23.5 & 42 & 19.3\\
Tufts (N=301) & 18.4 & 26.8 & 38.4 & 32.4 & 27.7 & 20.4 & 17.3 & 28.8 & 43.5 & 45.3 & 20.8 & 18.4 & 21.8 & 14 & 27.3\\
U of Denver (N=279) & 17.9 & 25.0 & 38.4 & 25.7 & 18.8 & 18.0 & 23.5 & 19.8 & 27.5 & 37.0 & 39.9 & 24.5 & 11.8 & 27 & 19.3\\
Emory (N=273) & 21.6 & 30.3 & 28.7 & 18.6 & 34.4 & 18.4 & 24.7 & 21.2 & 38.0 & 26.0 & 16.2 & 17.8 & 8.4 & 8 & 12.5\\
Baylor (N=237) & 18.1 & 23.2 & 27.6 & 7.4 & 30.1 & 7.1 & 16.9 & 16.7 & 19.0 & 22.4 & 31.8 & 51.5 & 0.8 & 21 & 20.5\\
Case Western Res. (N=228) & 16.1 & 19.9 & 26.8 & 13.2 & 18.0 & 18.0 & 16.9 & 27.9 & 31.0 & 26.0 & 21.4 & 21.5 & 15.1 & 16 & 17.0\\
Stevens Ins. Tech (N=160) & 10.3 & 14.9 & 15.5 & 22.3 & 12.5 & 26.3 & 10.3 & 22.1 & 14.0 & 17.2 & 6.9 & 8.0 & 29.4 & 3 & 6.8\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage
\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/nd_religion}

}

\caption{Order 2 ego network of University of Notre Dame, vertices colored by religion}\label{fig:nd-religion}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_count_pubu}

}

\caption{Number of visits to public and private high schools by public research universities}\label{fig:events-hs-count-pubu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_count_privu}

}

\caption{Number of visits to public and private high schools by selective private universities}\label{fig:events-hs-count-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_actual_proportional_pubu}

}

\caption{Actual versus proportional number of private school visits, public research universities}\label{fig:actual-proportional-pubu}
\end{figure}

\clearpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_actual_proportional_privu}

}

\caption{Actual versus proportional number of private school visits, selective private universities}\label{fig:actual-proportional-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_u}

}

\caption{One-mode network for public and private universities, colored by cluster}\label{fig:plot-1mode-u}
\end{figure}

\clearpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_region_pubu_privu}

}

\caption{Geographic region of visited private high schools}\label{fig:region-pubu-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_religion_pubu_privu}

}

\caption{Religious affiliation of visited private high schools}\label{fig:religion-pubu-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_rank_pubu_privu}

}

\caption{High school ranking of visited private high schools}\label{fig:rank-pubu-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_race_pubu_privhs_pubhs}

}

\caption{Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, public research universities}\label{fig:race-pubu-privhs-pubhs}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_race_privu_privhs_pubhs}

}

\caption{Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, selective private universities}\label{fig:race-privu-privhs-pubhs}
\end{figure}

\beginsupplement
\clearpage
\newpage

\begin{table}

\caption{\label{tab:pubu-count-matrix}One-mode public university count matrix}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{5.5em}>{\centering\arraybackslash}p{7.5em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{5.5em}>{\centering\arraybackslash}p{6.5em}>{\centering\arraybackslash}p{8.8em}>{\centering\arraybackslash}p{5em}>{\centering\arraybackslash}p{6em}}
\toprule
  & U of Alabama (N=759) & U of S.Carolina (N=396) & CU Boulder (N=362) & UMass Amherst (N=296) & U of Georgia (N=256) & Rutgers (N=255) & U of Cincinnati (N=243) & U of Pitt (N=222) & UC Berkeley (N=200) & UC San Diego (N=192) & U of Kansas (N=173) & U of Arkansas (N=163) & SUNY Stony Brook (N=119) & UNL (N=100) & UC Riverside (N=88)\\
\midrule
U of Alabama (N=759) & 759 & 284 & 210 & 149 & 169 & 120 & 124 & 125 & 112 & 100 & 93 & 100 & 43 & 31 & 34\\
U of S.Carolina (N=396) & 284 & 396 & 155 & 108 & 140 & 74 & 110 & 99 & 84 & 59 & 58 & 57 & 27 & 20 & 19\\
CU Boulder (N=362) & 210 & 155 & 362 & 115 & 88 & 76 & 69 & 92 & 77 & 98 & 74 & 51 & 21 & 25 & 28\\
UMass Amherst (N=296) & 149 & 108 & 115 & 296 & 57 & 93 & 27 & 56 & 45 & 57 & 18 & 14 & 57 & 4 & 18\\
U of Georgia (N=256) & 169 & 140 & 88 & 57 & 256 & 24 & 73 & 48 & 64 & 38 & 39 & 59 & 7 & 13 & 16\\
Rutgers (N=255) & 120 & 74 & 76 & 93 & 24 & 255 & 35 & 74 & 41 & 43 & 20 & 5 & 48 & 10 & 10\\
U of Cincinnati (N=243) & 124 & 110 & 69 & 27 & 73 & 35 & 243 & 56 & 33 & 24 & 29 & 37 & 5 & 18 & 8\\
U of Pitt (N=222) & 125 & 99 & 92 & 56 & 48 & 74 & 56 & 222 & 41 & 28 & 32 & 26 & 27 & 15 & 11\\
UC Berkeley (N=200) & 112 & 84 & 77 & 45 & 64 & 41 & 33 & 41 & 200 & 61 & 30 & 26 & 9 & 8 & 20\\
UC San Diego (N=192) & 100 & 59 & 98 & 57 & 38 & 43 & 24 & 28 & 61 & 192 & 29 & 22 & 11 & 3 & 35\\
U of Kansas (N=173) & 93 & 58 & 74 & 18 & 39 & 20 & 29 & 32 & 30 & 29 & 173 & 62 & 0 & 61 & 8\\
U of Arkansas (N=163) & 100 & 57 & 51 & 14 & 59 & 5 & 37 & 26 & 26 & 22 & 62 & 163 & 1 & 24 & 9\\
SUNY Stony Brook (N=119) & 43 & 27 & 21 & 57 & 7 & 48 & 5 & 27 & 9 & 11 & 0 & 1 & 119 & 0 & 4\\
UNL (N=100) & 31 & 20 & 25 & 4 & 13 & 10 & 18 & 15 & 8 & 3 & 61 & 24 & 0 & 100 & 0\\
UC Riverside (N=88) & 34 & 19 & 28 & 18 & 16 & 10 & 8 & 11 & 20 & 35 & 8 & 9 & 4 & 0 & 88\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}

\caption{\label{tab:privu-count-matrix}One-mode private universities count matrix}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{7em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{8.5em}>{\centering\arraybackslash}p{8.5em}}
\toprule
  & Notre Dame (N=625) & Villanova (N=563) & SMU (N=550) & TCU (N=435) & Tulane (N=430) & Northwestern (N=377) & Boston Coll. (N=339) & Marquette (N=331) & Tufts (N=301) & U of Denver (N=279) & Emory (N=273) & Baylor (N=237) & Case Western Res. (N=228) & Stevens Ins. Tech (N=160)\\
\midrule
Notre Dame (N=625) & 625 & 338 & 293 & 253 & 223 & 224 & 235 & 231 & 177 & 164 & 145 & 99 & 133 & 79\\
Villanova (N=563) & 338 & 563 & 291 & 224 & 218 & 214 & 208 & 205 & 161 & 143 & 147 & 101 & 142 & 103\\
SMU (N=550) & 293 & 291 & 550 & 290 & 275 & 243 & 218 & 151 & 189 & 177 & 176 & 154 & 134 & 88\\
TCU (N=435) & 253 & 224 & 290 & 435 & 199 & 177 & 168 & 150 & 141 & 151 & 122 & 133 & 98 & 66\\
Tulane (N=430) & 223 & 218 & 275 & 199 & 430 & 219 & 173 & 103 & 190 & 142 & 143 & 79 & 131 & 56\\
Northwestern (N=377) & 224 & 214 & 243 & 177 & 219 & 377 & 172 & 114 & 169 & 139 & 128 & 75 & 122 & 55\\
Boston Coll. (N=339) & 235 & 208 & 218 & 168 & 173 & 172 & 339 & 133 & 158 & 135 & 113 & 64 & 100 & 60\\
Marquette (N=331) & 231 & 205 & 151 & 150 & 103 & 114 & 133 & 331 & 77 & 97 & 52 & 62 & 66 & 43\\
Tufts (N=301) & 177 & 161 & 189 & 141 & 190 & 169 & 158 & 77 & 301 & 114 & 117 & 52 & 108 & 66\\
U of Denver (N=279) & 164 & 143 & 177 & 151 & 142 & 139 & 135 & 97 & 114 & 279 & 82 & 57 & 72 & 44\\
Emory (N=273) & 145 & 147 & 176 & 122 & 143 & 128 & 113 & 52 & 117 & 82 & 273 & 39 & 98 & 42\\
Baylor (N=237) & 99 & 101 & 154 & 133 & 79 & 75 & 64 & 62 & 52 & 57 & 39 & 237 & 50 & 23\\
Case Western Res. (N=228) & 133 & 142 & 134 & 98 & 131 & 122 & 100 & 66 & 108 & 72 & 98 & 50 & 228 & 41\\
Stevens Ins. Tech (N=160) & 79 & 103 & 88 & 66 & 56 & 55 & 60 & 43 & 66 & 44 & 42 & 23 & 41 & 160\\
\bottomrule
\end{tabular}}
\end{table}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_pubu}

}

\caption{Number of visits by type and in-state vs. out-of-state, public research universities}\label{fig:events-count-pubu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_privu}

}

\caption{Number of visits by type and in-state vs. out-of-state, selective private universities}\label{fig:events-count-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_pubu}

}

\caption{One-mode network for public institutions, colored by cluster}\label{fig:plot-1mode-pubu}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_privu}

}

\caption{One-mode network for private universities, colored by cluster}\label{fig:plot-1mode-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_enroll_pubu_privu}

}

\caption{12th grade enrollment of visited private high schools}\label{fig:enroll-pubu-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_enroll_pubu_privhs_pubhs}

}

\caption{12th grade enrollment of visited private high schools vs. public high schools, public research universities}\label{fig:enroll-pubu-privhs-pubhs}
\end{figure}

\end{landscape}

\restoregeometry

\end{document}

### 2023-11-20 scripts/create_tables_figures.R

@@ -62,6 +62,8 @@ ego_df <- readRDS(file.path(tables_dir, 'table_ego_all.RDS')) %>%
     univ_enroll = format(as.numeric(str_split(characteristics, '\\|', simplify = T)[,5]), big.mark = ',')
   )
 
+color_palette <- c('#d1b38e', '#8eb9d1', '#b48ed1', '#afd18e')
+
 
 ## -------------------
 ## SAVE PLOT FUNCTION
@@ -98,24 +100,35 @@ events_count <- events_df %>%
   )) %>%
   select(univ_abbrev, event_loc, event_type) %>% 
   group_by(univ_abbrev, event_loc, event_type) %>% 
-  summarise(count = n())
+  summarise(count = n()) %>% 
+  ungroup()
 
 # View(events_count[order(match(events_count$univ_abbrev, univ_sample_df$univ_abbrev)), ])
 
 events_count$event_type <- factor(events_count$event_type, levels = c('pub_hs', 'priv_hs', 'cc', 'other'))
 events_count$univ_abbrev <- factor(events_count$univ_abbrev, levels = rev(univ_sample_df$univ_abbrev))
 
-plot_event_count <- function(univ_sample, in_lim = 0, out_lim = 0, hjust = 0.1) {
-  sub_events_count <- events_count %>% filter(univ_abbrev %in% univ_sample)
+plot_event_count <- function(univ_sample, in_lim = 0, out_lim = 0, hjust = 0.1, text_offset = 15) {
+  sub_events_count <- events_count %>% filter(univ_abbrev %in% univ_sample) %>% 
+    mutate(
+      event_type = recode_factor(
+        event_type,
+        'pub_hs' = 'Public HS',
+        'priv_hs' = 'Private HS',
+        'cc' = 'Community College',
+        'other' = 'Other'
+      )
+    )
   
   ggplot(sub_events_count, aes(univ_abbrev)) +
     geom_bar(data = subset(sub_events_count, event_loc == 'instate'), aes(y = -count, fill = event_type), stat = 'identity', position = position_stack(reverse = T), width = 0.5) +
     geom_bar(data = subset(sub_events_count, event_loc == 'outofstate'), aes(y = count, fill = event_type), stat = 'identity', position = position_stack(reverse = T), width = 0.5) +
     geom_hline(yintercept = 0, colour = 'grey90', linetype = 'dotted') +
[…]

### 2023-11-20 scripts/network_recruiting_analysis.R

@@ -94,7 +94,7 @@ enroll_title <- '12th grade enrollment'
 
 save_plot <- function(graph_object, plot_name, paper = 'a4r', mar = c(0, 0, 0, 0), mai = c(0, 0, 0, 0)) {
   
-  pdf(str_c('./assets/figures/', plot_name), paper = paper)
+  pdf(str_c('./assets/figures/', plot_name), paper = paper, width = 1600, height = 1200)
   par(mfrow = c(1, 1))
   par(mar = mar + 0.1, mai = mai)
   
@@ -121,7 +121,7 @@ save_plot <- function(graph_object, plot_name, paper = 'a4r', mar = c(0, 0, 0, 0
 
 # RETURNS: ego plot of the specified univ
 
-plot_ego_graph <- function(ego_networks, univ_id, characteristic = NULL, values = NULL, keys = NULL, colors = c('lightblue', 'lightgreen', 'violet', 'yellow'), title = as.character(univ_df[univ_df$school_id == univ_id, 'school_name']), graph_order = 'both', margin = 0.0) {
+plot_ego_graph <- function(ego_networks, univ_id, characteristic = NULL, values = NULL, keys = NULL, colors = c('lightblue', 'lightgreen', 'violet', 'yellow'), title = as.character(univ_df[univ_df$school_id == univ_id, 'school_name']), graph_order = 'both', margin = 0.0, offset_univs = c()) {
 
   network <- ego_networks[[univ_id]]
   
@@ -181,6 +181,10 @@ plot_ego_graph <- function(ego_networks, univ_id, characteristic = NULL, values 
     # vertex attributes
     vertex.shape = 'circle',
     vertex.label = if_else(V(network)$type, V(network)$school_name, ''),
+    vertex.label.cex = if_else(V(network)$name == univ_id, 1.2, 0.8),
+    vertex.label.color = if_else(V(network)$name == univ_id, 'black', adjustcolor('black', 0.6)),
+    vertex.label.dist = if_else(V(network)$name %in% offset_univs, 0.5, 0),
+    # vertex.label.degree = 0,  # default is -pi/4 (i.e., -45 deg)
     vertex.color = vertex_color,
     vertex.size = vertex_size,
     vertex.frame.color = 'lightgray',
@@ -189,18 +193,19 @@ plot_ego_graph <- function(ego_networks, univ_id, characteristic = NULL, values 
     edge.lty = edge_lty,
[…]

### 2023-12-07 r_r/manuscript_rihe_r_r.Rmd
revising intro, adding revised tables

--- 2023-11-16 r_r/manuscript_rihe.Rmd
@@
 *During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[NAME THE UNIVERSITIES] We are still trying to figure out what happened.*
+
 \bigskip
@@
 Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from five private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University).
-It also received visits from the University of Cincinatti, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder.
+It also received visits from the University of Cincinnati, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder.
 Christ Presbyterian Academy was founded in 1985 and 94% of its students are white.
@@
 @RN4758 analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
-the authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools.
+The authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools.
 These out-of-state visits focused on affluent, predominantly white public schools.
@@
 This research observes strong links -- and student flows -- between private high schools and selective private universities [CITE].
+Private schools enroll many students who can afford private university tuition.
 To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between between private school and college.
 We argue that these two stories have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities.
+Simply put, selective private universities and public research universities are increasingly competing for students from the same set of affluent households.
 
@@
 
-1. How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
-    - ALTERNATIVE: How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?
+<!--1. 
+How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?
+How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities? 
+-->
+
+1. How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?
 1. To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
-1. How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?
+1. What are the characteristics of private schools that receive visits from public research universities and selective private research universities in our sample?
 
@@
 For public research universities, visited private schools were much more likely to be out-of-state than visited public schools.
-Although universities visited a large number of private schools in their home region, most universities also visited a large number of private schools in the South.
-Private schools that received visits were predominantly white.
-Although partially a function of our analysis sample, public universities tended to visit lower ranked private high schools than private universities.
+Network analyses revealed substantial overlap in the recruiting networks of universities in our sample.
+For several public universities (e.g., University of Alabama, University of South Carolina) their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, Texas Christian University) than they did to other public universities in our sample.
+Results suggest that recruiting networks are substantially a function of geographic location.
+All universities visited a large number of private schools in their home region.
+However, most universities in our sample also visited a large number of private schools in the South.
+The private schools visited by public and private universities in our sample enrolled a much higher share of white students than the public schools visited by these universities.
 Surprisingly, several public universities visited sectarian private high schools at a rate similar to sectarian private universities.
-Network analyses revealed substantial overlap in the recruiting networks of public and private research universities.
-
-This manuscript is practically important because it provides insight about which schools universities view as "feeder schools" and -- to a limited extent -- the characteristics of students they want to enroll.
-Prior research finds that university recruiting efforts affect the enrollment decisions of students [CITE].
-In turn, the composition of enrolled students affects the campus culture experienced by students.
-Scholarship and the popular press reports that underrepresented minority students and low-income students at public flagship universities feel isolated amidst affluent, predominantly white student bodies.
-Racial and socioeconomic isolation negatively affects student development outcomes for isolated students and for the entire student body [CITE].
-State policymakers and institutional leaders should recognize that the enrollment composition at public research universities is not the consequence of exogenous student demand, but rather the consequence of recruiting efforts that seek to grow nonresident enrollment by systematically targeting affluent, predominantly white public high schools [@RN4758] and affluent, predominantly white private high schools.
-[NOTE: THESE IMPLICATIONS HAVE TO DO ABOUT TARGETING PRIVATE SCHOOLS BUT NOT TARGETING SAME SET OF SCHOOLS TARGETED BY SELECTIVE PRIVATE UNIVERSITIES]
+
+This manuscript yields practical implications for public and private universities concerned about racial and socioeconomic diversity.
+Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain the fundamental means of maintaining relationships with high school guidance counselors [CITE].
+Prior research shows that that students are sensitive to recruiting interventions, including off-campus recruiting visits.
+Therefore, which high schools a university chooses to visit will affect the subsequent enrollment composition of the university.
+In the aftermath of the Supreme Court decision on race conscious admissions, public and private universities are searching for ways to increase racial diversity without running afoul of the law.
+The U.S.
+Department of Education recommends that universities expand "outreach to high schools with substantial populations of low-income students and students of color" (CITE, PX X).
+Most public and private universities in our sample visited a disproportionate number of private schools and these private schools tended to enroll mostly white students.
+We recommend that universities concerned about racial diversity should conduct an internal equity audit of their recruiting practices, for example, comparing the racial and socioeconomic characteristics of schools they visit versus schools they do not visit.
 
@@
 
+An anecdote from @RN3519[p.
+73] highlights the allure that prestigious private schools and affluent private school students hold for selective private colleges.
+Stevens accompanied an admissions officer from the College on a visit to Corbett Academy, a prestigious school for girls.
+The admissions officer "said with a grin, 'We're not getting Corbett's finest.'" @RN3519 (p.
+73) writes that,
+
+> Corbett consistently sent its top performers to places like Berkeley and Stanford and the top of the Ivy League \ldots [Other colleges] in the College's own peer group only had a shot at girls nearer the middle of Corbett's class.
+Or below the middle.
+Still, by most standards this excellent school's modest achievers were very good admissions prospects, which was why we were visiting.
+Even Corbett's less fine would enter college well prepared academically, and their generally affluent famiies could absorb the College's full tuition and board cost with little, if any, financial aid."
+
 @RN4321 analyzed recruiting from the perspective of an elite private boarding school in order to understand "how such schools continue to get comparatively under-qualified students into top colleges and universities" (p.
@@
 \clearpage
+\begin{landscape}
 
@@
 univ_sample <- univ_sample_df %>% 
-  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)
-
-kable(univ_sample %>% arrange(desc(classification), rank), caption = "Characteristics of universities in analysis sample") %>%
+  filter(classification != 'private_libarts') %>% 
+  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal) %>% 
+  mutate(
+    classification = recode(
+      classification,
+      'public_research' = 'Public Research',
+      'private_national' = 'Private National'
+    ),
+    satactcomp25 = format(round(satactcomp25), big.mark = ',', trim = T),
+    satactcomp75 = format(round(satactcomp75), big.mark = ',', trim = T),
+    tfuginst = str_c('\\$', format(round(tfuginst), big.mark = ',', trim = T)),
+    tfugoutst = str_c('\\$', format(round(tfugoutst), big.mark = ',', trim = T)),
+    ugftptfreshtot = format(round(ugftptfreshtot), big.mark = ',', trim = T),
+    freshoutstpct = str_c(format(round(freshoutstpct * 100, 1), nsmall = 1), '\\%'),
+    pgrnt_p = str_c(format(round(pgrnt_p, 1), nsmall = 1), '\\%'),
+    pctfreshwh = str_c(format(round(pctfreshwh, 1), nsmall = 1), '\\%'),
+    pctfreshbl = str_c(format(round(pctfreshbl, 1), nsmall = 1), '\\%'),
+    pctfreshap = str_c(format(round(pctfreshap, 1), nsmall = 1), '\\%'),
+    pctfreshhi = str_c(format(round(pctfreshhi, 1), nsmall = 1), '\\%'),
+    pctfreshal = str_c(format(round(pctfreshal, 1), nsmall = 1), '\\%')
+  ) %>% 
+  arrange(desc(classification), rank)
+
+names(univ_sample) <- c('Classification', 'University', 'Rank', '25th Percentile SAT/ACT Composite Score', '75th Percentile SAT/ACT Composite Score', 'In-State Tuition + Fees', 'Out-of-State Tuition + Fees', 'Total Enrolled Freshmen', 'Percent Out-of-State Freshmen', 'Percent Pell Recipients', 'Percent White Freshmen', 'Percent Black Freshmen', 'Percent Asian Freshmen', 'Percent Hispanic Freshmen', 'Percent International Freshmen')
+
+kable(univ_sample, caption = "Characteristics of universities in analysis sample", booktabs = T, escape = F, align = 'c') %>%
   collapse_rows(columns = 1, latex_hline = 'major', valign = 'middle') %>%
-  kable_styling(latex_options = 'scale_down')
+  column_spec(c(2), width = '4.5cm', latex_valign = 'm') %>% 
+  column_spec(c(3), width = '1.8cm', latex_valign = 'm') %>% 
+  column_spec(c(4, 5), width = '3.8cm', latex_valign = 'm') %>% 
+  column_spec(c(6, 8, 10:14), width = '2.4cm', latex_valign = 'm') %>% 
+  column_spec(c(7), width = '2.7cm', latex_valign = 'm') %>% 
+  column_spec(c(9, 15), width = '3cm', latex_valign = 'm') %>% 
+  kable_styling(font_size = 13, latex_options = c('scale_down', 'hold_position'))
 ```
@@
 
-\begin{landscape}
+```{r sample-population-characteristics}
+# Source: https://docs.google.com/spreadsheets/d/1e8lnU2YhJVigEYR55tc0pijsm52WKaEua8MNaYXTtM4
+# Also in methodology: https://emraresearch.org/methodology
+
+# 49 public research
+pop_pubu <- c('151351', '171100', '180461', '188030', '199193', '147703', '204857', '207388', '214777', '186380', '149222', '196088', '196097', '204796', '100751', '197036', '164155', '104179', '106397', '110635', '110644', '110653', '110662', '110671', '110680', '201885', '126614', '129020', '139959', '141574', '225511', '142285', '155317', '161253', '163286', '166629', '170976', '181464', '187985', '199120', '215293', '217484', '218663', '230764', '234076', '236948', '230728', '234030', '172644')
+
+# 49 private national
+pop_privu <- c('194824', '139658', '190150', '223232', '212054', '193900', '166027', '144050', '130794', '243744', '166683', '198419', '215062', '162928', '182670', '110404', '147767', '217156', '190415', '227757', '152080', '186131', '221999', '131496', '164988', '160755', '213543', '135726', '216597', '228246', '191241', '186867', '131159', '228875', '239105', '127060', '122436', '207971', '179159', '168148', '164924', '195030', '179867', '201645', '197708', '199847', '211440', '121150', '123961')
+
+sample_pubu <- (univ_sample_df %>% filter(classification == 'public_research'))$univ_id
+sample_privu <- (univ_sample_df %>% filter(classification == 'private_national'))$univ_id
+
+univ_pop <- read.csv(file.path(data_dir, 'ipeds_data.csv'), header = TRUE, na.strings = c('', 'NULL', 'NA'), stringsAsFactors = FALSE, colClasses = c('unitid' = 'character')) %>% as_tibble() %>%
+  filter(endyear == 2017, unitid %in% c(pop_pubu, pop_privu, sample_pubu, sample_privu)) %>% 
+  select(unitid, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_n, cohortsfaef, ugftptfreshwhmf, ugftptfreshblmf, ugftptfreshapmf, ugftptfreshhimf, ugftptfreshalmf, ugftptfreshmrmf, ugftptfreshnamf, ugftptfreshunmf, ugftptfreshasmf, ugftptfreshnhmf) %>%
+  mutate(
+    pgrnt_p = pgrnt_n / cohortsfaef * 100,
+    pctfreshwh = ugftptfreshwhmf / ugftptfreshtot * 100,
+    pctfreshbl = ugftptfreshblmf / ugftptfreshtot * 100,
+    pctfreshap = ugftptfreshapmf / ugftptfreshtot * 100,  # ap = as + nh
+    pctfreshhi = ugftptfreshhimf / ugftptfreshtot * 100,
+    pctfreshal = ugftptfreshalmf / ugftptfreshtot * 100,
+    pctfreshmr = ugftptfreshmrmf / ugftptfreshtot * 100,
+    pctfreshna = ugftptfreshnamf / ugftptfreshtot * 100,
+    pctfreshun = ugftptfreshunmf / ugftptfreshtot * 100,
+    pctfreshas = ugftptfreshasmf / ugftptfreshtot * 100,
+    pctfreshnh = ugftptfreshnhmf / ugftptfreshtot * 100
+  ) %>% 
+  select(unitid, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)
+
+format_data <- function(univ_ids) {
+  apply(univ_pop %>% filter(unitid %in% univ_ids) %>% select(-unitid), 2, function(x) quantile(x, probs = c(0.25, 0.5, 0.75), na.rm = T)) %>% 
+    as.data.frame() %>% 
+    mutate(
+      satactcomp25 = format(round(satactcomp25), big.mark = ',', trim = T),
+      satactcomp75 = format(round(satactcomp75), big.mark = ',', trim = T),
+      tfuginst = str_c('\\$', format(round(tfuginst), big.mark = ',', trim = T)),
+      tfugoutst = str_c('\\$', format(round(tfugoutst), big.mark = ',', trim = T)),
+      ugftptfreshtot = format(round(ugftptfreshtot), big.mark = ',', trim = T),
+      freshoutstpct = str_c(format(round(freshoutstpct * 100, 1), nsmall = 1), '\\%'),
+      pgrnt_p = str_c(format(round(pgrnt_p, 1), nsmall = 1), '\\%'),
+      pctfreshwh = str_c(format(round(pctfreshwh, 1), nsmall = 1), '\\%'),
+      pctfreshbl = str_c(format(round(pctfreshbl, 1), nsmall = 1), '\\%'),
+      pctfreshap = str_c(format(round(pctfreshap, 1), nsmall = 1), '\\%'),
+      pctfreshhi = str_c(format(round(pctfreshhi, 1), nsmall = 1), '\\%'),
+      pctfreshal = str_c(format(round(pctfreshal, 1), nsmall = 1), '\\%')
+    ) %>% 
+    t()
+}
+
+univ_pop_df <- cbind(
+  format_data(sample_pubu),
+  format_data(pop_pubu),
+  format_data(sample_privu),
+  format_data(pop_privu)
+)
+rownames(univ_pop_df) <- c('25th Percentile SAT/ACT Composite Score', '75th Percentile SAT/ACT Composite Score', 'In-State Tuition + Fees', 'Out-of-State Tuition + Fees', 'Total Enrolled Freshmen', 'Percent Out-of-State Freshmen', 'Percent Pell Recipients', 'Percent White Freshmen', 'Percent Black Freshmen', 'Percent Asian Freshmen', 'Percent Hispanic Freshmen', 'Percent International Freshmen')
+colnames(univ_pop_df) <- rep(c('25th percentile', '50th percentile', '75th percentile'), 4)
+
+kable(univ_pop_df, caption = "Characteristics of universities in analysis sample compared to data collection sample", booktabs = T, escape = F, align = 'c', linesep = '') %>%
+  add_header_above(header = c(' ' = 1, 'Analysis sample (N=15)' = 3, 'Data collection sample (N=49)' = 3, 'Analysis sample (N=14)' = 3, 'Data collection sample (N=49)' = 3)) %>%
+  add_header_above(header = c(' ' = 1, 'Public research universities' = 6, 'Selective private universities' = 6)) %>%
+  kable_styling(font_size = 13, latex_options = 'scale_down') 
+```
+
+\clearpage
 
 ```{r pubu-percent-matrix}
+table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
+rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)
+
+kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix', booktabs = T, align = 'c', linesep = '') %>%
+  column_spec(c(7, 9, 15), width = '5em') %>%
+  column_spec(c(4, 12), width = '5.5em') %>%
+  column_spec(c(6, 10, 16), width = '6em') %>%
+  column_spec(c(2, 11, 13), width = '6.5em') %>%
+  column_spec(c(3, 8), width = '7em') %>%
+  column_spec(c(5), width = '7.5em') %>%
+  column_spec(c(14), width = '8.8em') %>%
+  kable_styling(font_size = 13, latex_options = 'scale_down') 
+```
+
+```{r privu-percent-matrix}
+table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
+rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)
+
+kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix', booktabs = T, align = 'c', linesep = '') %>%
+  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
+  column_spec(14:15, width = '8.5em') %>%
+  kable_styling(font_size = 13, latex_options = 'scale_down') 
+```
+
+\clearpage
+
+```{r privu-percent-visited-by-pubu-matrix}
 table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
-
-table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
-
-table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
-rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)
-
-rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)
-
-kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(c(1), width = '13em') %>% 
-  column_spec(c(14), width = '8.5em') %>% 
-  column_spec(2:13, width = '7em') %>% 
-  column_spec(c(7, 9, 15, 16), width = '6em')
-
-```
-
-```{r privu-percent-matrix}
-
-rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)
-
-kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(1, width = '13em') %>%
-  column_spec(2:15, width = '7em') %>% 
+rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
+
+kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities', booktabs = T, align = 'c', linesep = '') %>%
+  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
   column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
-  column_spec(14:15, width = '8.5em')
-
+  column_spec(14:15, width = '8.5em') %>%
+  kable_styling(font_size = 13, latex_options = 'scale_down')
+```
+
+```{r pubu-percent-visited-by-privu-matrix}
+table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
+rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
+
+kable(table_1mode_u$onemode_pct_df[c(2,3,4,5,6,8,10,11,12,14,15,19,20,26),c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29)], caption = 'For public universities, the percent of high schools visited by private universities', booktabs = T, align = 'c', linesep = '') %>%
+  column_spec(c(7, 9, 15), width = '5em') %>%
+  column_spec(c(4, 12), width = '5.5em') %>%
+  column_spec(c(6, 10, 16), width = '6em') %>%
+  column_spec(c(2, 11, 13), width = '6.5em') %>%
+  column_spec(c(3, 8), width = '7em') %>%
+  column_spec(c(5), width = '7.5em') %>%
+  column_spec(c(14), width = '8.8em') %>%
+  kable_styling(font_size = 13, latex_options = 'scale_down')
 ```
@@
 \clearpage
-
-```{r privu-percent-visited-by-pubu-matrix}
-rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
-
-kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  #column_spec(1, width = '8.5em') %>%
-  column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
-  column_spec(14:15, width = '8.5em')
-```
-
-\end{landscape}
-
-\restoregeometry
-
-<!-- FIGURES -->
-
-```{r em-funnel, echo = FALSE, fig.align = 'center', fig.cap = "The enrollment funnel", out.width = "70%", include = FALSE, eval = FALSE}
-knitr::include_graphics('./../assets/images/enrollment_funnel.png')
-#![The enrollment funnel](assets/images/enrollment_funnel.png)
+\newpage
+
+```{r nd-religion, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Order 2 ego network of University of Notre Dame, vertices colored by religion"}
+include_graphics(file.path(figures_dir, 'nd_religion.pdf'))
+```
+
+\newpage
+
+```{r events-hs-count-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits to public and private high schools by public research universities"}
+include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
+```
+
+\newpage
+
+```{r events-hs-count-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
+include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
+```
+
+\newpage
+
+```{r actual-proportional-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
 ```
@@
 \clearpage
-\newpage
-
-```{r nd-religion, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Order 2 ego network of University of Notre Dame, vertices colored by religion"}
-include_graphics(file.path(figures_dir, 'nd_religtion.pdf'))
-```
-
-\newpage
-
-```{r events-hs-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by public research universities"}
-include_graphics(file.path(figures_dir, 'events_hs_count_pubu.pdf'))
-```
-
-\newpage
-
-```{r events-hs-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits to public and private high schools by selective private universities"}
-include_graphics(file.path(figures_dir, 'events_hs_count_privu.pdf'))
-```
-
-\newpage
-
-```{r actual-proportional-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, public research universities"}
-include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_pubu.pdf'))
+
+```{r actual-proportional-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
+include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
+```
+
+\newpage
+
+```{r plot-1mode-u, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
+knitr::include_graphics(file.path(figures_dir, 'plot_1mode_u.pdf'))
 ```
@@
 
-```{r actual-proportional-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Actual versus proportional number of private school visits, selective private universities"}
-include_graphics(file.path(figures_dir, 'events_hs_actual_proportional_privu.pdf'))
-```
-
-\newpage
-
-```{r plot-1mode-u, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public and private universities, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_u.pdf')
-```
-
-\clearpage
-
-```{r region-pubu-privu, echo = FALSE, fig.cap = "Geographic region of visited private high schools"}
+```{r region-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Geographic region of visited private high schools"}
 include_graphics(file.path(figures_dir, 'ego_network_region_pubu_privu.pdf'))
@@
 
-```{r religion-pubu-privu, echo = FALSE, fig.cap = "Religious affiliation of visited private high schools"}
+```{r religion-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Religious affiliation of visited private high schools"}
 include_graphics(file.path(figures_dir, 'ego_network_religion_pubu_privu.pdf'))
@@
 
-```{r rank-pubu-privu, echo = FALSE, fig.cap = "High school ranking of visited private high schools"}
+```{r rank-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "High school ranking of visited private high schools"}
 include_graphics(file.path(figures_dir, 'ego_network_rank_pubu_privu.pdf'))
@@
 
-```{r race-pubu-privu, echo = FALSE, eval = FALSE, include = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited private high schools"}
-include_graphics(file.path(figures_dir, 'ego_network_race_pubu_privu.pdf'))
-```
-
-\newpage
-
-```{r race-pubu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs.
+\newpage
+
+```{r race-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs.
 visited private high schools, public research universities"}
@@
 
-```{r race-privu-privhs-pubhs, echo = FALSE, fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs.
+```{r race-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs.
 visited private high schools, selective private universities"}
@@
 
-\newpage
+\beginsupplement
 \clearpage
-
-# Supplemental Online Appendix
-
-\pagenumbering{gobble}
-\pagenumbering{arabic}
-\renewcommand*{\thepage}{A\arabic{page}}
-\pagestyle{fancy}
-\setlength{\headheight}{15pt}
-
-\beginsupplement
+\newpage
 
 ```{r pubu-count-matrix}
-
-kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(c(1), width = '13em') %>% 
-  column_spec(c(14), width = '8.5em') %>% 
-  column_spec(2:13, width = '7em') %>% 
-  column_spec(c(7, 9, 15, 16), width = '6em')
+rownames(table_1mode_pubu$onemode_df) <- colnames(table_1mode_pubu$onemode_df)
+
+kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix', booktabs = T, align = 'c', linesep = '') %>%
+  column_spec(c(7, 9, 15), width = '5em') %>%
+  column_spec(c(4, 12), width = '5.5em') %>%
+  column_spec(c(6, 10, 16), width = '6em') %>%
+  column_spec(c(2, 11, 13), width = '6.5em') %>%
+  column_spec(c(3, 8), width = '7em') %>%
+  column_spec(c(5), width = '7.5em') %>%
+  column_spec(c(14), width = '8.8em') %>%
+  kable_styling(font_size = 13, latex_options = 'scale_down') 
 ```
@@
 ```{r privu-count-matrix}
-
 table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
-
-kable(table_1mode_privu$onemode_df, caption = 'One-mode private universities count matrix') %>%
-  kable_styling(latex_options = 'scale_down') %>%
-  column_spec(1, width = '8.5em') %>%
-  column_spec(2:15, width = '7em') %>% 
-  column_spec(c(4:6, 10, 12, 13), width = '6em')
-```
-
-\clearpage
-
-```{r u-cluster2-percent-matrix, eval=FALSE}
-kable(table_1mode_u$onemode_pct_df[cluster_2, cluster_2], caption = 'Public and private universities percent matrix (cluster 2)') %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r u-cluster3-percent-matrix, eval=FALSE}
-kable(table_1mode_u$onemode_pct_df[cluster_3, cluster_3], caption = 'Public and private universities percent matrix (cluster 3)') %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-```{r u-top-percent-matrix, eval=FALSE}
-kable(table_1mode_u$onemode_pct_df[c(1,2,3,4,5,6,7,8,9),c(1,2,3,4,5,6,7,8,9)], caption = 'Public and private universities, highest degree centrality') %>%
-  kable_styling(latex_options = 'scale_down')
-```
-
-\newpage
-
-```{r events-count-pubu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
+rownames(table_1mode_privu$onemode_df) <- colnames(table_1mode_privu$onemode_df)
+
+kable(table_1mode_privu$onemode_df, caption = 'One-mode private universities count matrix', booktabs = T, align = 'c', linesep = '') %>%
+  column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
+  column_spec(c(4:6, 10, 12, 13), width = '6em') %>% 
+  column_spec(14:15, width = '8.5em') %>%
+  kable_styling(font_size = 13, latex_options = 'scale_down') 
+```
+
+\newpage
+
+```{r events-count-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
 include_graphics(file.path(figures_dir, 'events_count_pubu.pdf'))
@@
 
-```{r events-count-privu, echo = FALSE, fig.align = 'left', out.width = "125%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
+```{r events-count-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits by type and in-state vs. out-of-state, selective private universities"}
 include_graphics(file.path(figures_dir, 'events_count_privu.pdf'))
@@
 
-```{r plot-1mode-pubu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for public institutions, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_pubu.pdf')
-```
-
-```{r plot-1mode-privu, fig.align = 'center', echo = FALSE, out.width = "100%", fig.cap = "One-mode network for private universities, colored by cluster"}
-knitr::include_graphics('./../assets/figures/plot_1mode_privu.pdf')
-```
-
-\newpage
-
-```{r enroll-pubu-privu, echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools"}
+```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public institutions, colored by cluster"}
+knitr::include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))
+```
+
+```{r plot-1mode-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for private universities, colored by cluster"}
+knitr::include_graphics(file.path(figures_dir, 'plot_1mode_privu.pdf'))
+```
+
+\newpage
+
+```{r enroll-pubu-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "12th grade enrollment of visited private high schools"}
 include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privu.pdf'))
@@
 
-```{r enroll-pubu-privhs-pubhs, echo = FALSE, fig.cap = "12th grade enrollment of visited private high schools vs. public high schools, public research universities"}
+```{r enroll-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "12th grade enrollment of visited private high schools vs.
+public high schools, public research universities"}
 include_graphics(file.path(figures_dir, 'ego_network_enroll_pubu_privhs_pubhs.pdf'))
-
-```
+```
+
+\end{landscape}
+
+\restoregeometry

### 2023-12-07 r_r/letter_to_reviewers.Rmd
revising letter

@@
 While the analyses have changed only modestly, the front end of the paper has changed tremendously, literally rewritten from scratch.
-I begin this letter by discussing the big changes in the manuscript, which I hope address many of the big concerns from Reviewer 2.
+I begin this letter by describing the big changes in the manuscript, which I hope address many of the big concerns from Reviewer 2.
 Next, I address remaining reviewer concerns one by one.
@@
 The "privatization" literature has been in decline for more than a decade.
-So it is not important to contribute to a literature that is no longer relevant.
+It is not important to contribute to a literature that is no longer relevant.
 Fourth, Reviewer 2 is concerned that the original manuscript did not clearly state the practical implications of the findings.
@@
 "Thus, in recruiting from private schools, universities may be targeting student bodies that are more affluent and racially homogeneous than public schools.
-We investigate the characteristics – including geographic region and racial composition – of private schools being targeted by university admissions officers because these characteristics have downstream implications for the racial composition of university campuses"
+We investigate the characteristics – including geographic region and racial composition – of private schools being targeted by university admissions officers because these characteristics have downstream implications for the racial composition of university campuses."
 
-Finally, we have revised the practical significance and implications to address concerns raised by Reviewer 2.
+The research questions in the revised manuscript are very similar to the research questions from the original manuscript. Two specific changes:
 
-[WRITE THIS TEXT AFTER YOU REVISE THE DISCUSSION SECTION]
+1.
+First, we switched the order of RQ2 and RQ3.
+In the revised manuscript, overlap in recruiting network is RQ2 and characteristics of visited high schools is RQ3.
+Our rationale is that the characteristics of visited private high schools is the most climactic, substantively important set of results, so we wanted those to go last.
+Additionally, when thinking through the narrative story of the results, we thought it made more sense to identify overlap -- extent of overlap, which universities visiting similar sets of high schools -- and then examine the characteristics of visited high schools.
+1.
+Second, compared to the original manuscript, the revised manuscript research questions are worded in a way that places less emphasis on comparing public research universities to selective private universities.
+The original manuscript focused on whether public research universities behave like selective private universities.
+Here, comparison is central.
+The revised manuscript is based on the idea both public research universities and selective private universities are targeting the same (or similar) sets of predominantly affluent households.
+Although comparison remains important, the fundamental interest now becomes developing insights about the competition for students who attend private schools and which schools the universities in our sample are targeting.
+
+Finally, in the Discussion section, we have revised the practical significance and implications for colleges and universities to address concerns raised by Reviewer 2.
+The final paragraph of the revised introduction describes these implications succinctly:
+
+>This manuscript yields practical implications for public and private universities concerned about racial and socioeconomic diversity.
+Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors [@RN4896; @RN4895; @eab_nacac_counselor_2023].
+Prior research finds that that students are sensitive to recruiting interventions, including off-campus recruiting visits [@RN4324; @RN4402].
+Therefore, which high schools a university chooses to visit affect the subsequent enrollment composition of the university.
+In the aftermath of the Supreme Court decision on race conscious admissions, public and private universities are searching for ways to increase racial diversity without running afoul of the law.
+The @RN4954[p.
+9] recommends that universities expand "outreach to high schools with substantial populations of low-income students and students of color." Most public and private universities in our sample visited a disproportionate number of private schools and these private schools tended to enroll mostly white students.
+We recommend that universities concerned about racial diversity should conduct an internal equity audit of their recruiting practices, for example, comparing the racial and socioeconomic characteristics of schools they visit versus schools they do not visit.
 
@@
 As discussed above, the revised manuscript addresses these concerns about the practical benefits of recruiting students from private schools.
-We have also improved the discussion of implications for research and practice [REVISE AFTER YOU REWRITE THE DISCUSSION SECTION]
+We have also improved the discussion of implications for research and practice.
 
@@
 
-**Author response**: REVISE THIS RESPONSE AFTER YOU HAVE WRITTEN THE DISCUSSION SECTION AND REVISED THE INTRODUCTION.
+**Author response**: As stated above, the last paragraph of the revised introduction introduces practical implications.
+The Discussion section discusses these implications in greater detail.
+We focus on implications for universities rather than implications for policy because the implications for universities are clearer than the implications for policymakers.
 
@@
 
-[REVISE THIS TEXT AFTER YOU REVISE THE DISCUSSION SECTION]
 Nevertheless, the question Reviewer 2 asks is very important; if off-campus recruiting visits became less prevalent following Covid, then the analyses do yield relevant insights about contemporary/future recruiting behavior by public research universities and selective private universities.
@@
 In short, off-campus recruiting events are back and are viewed as vital to recruiting efforts.
-We put this text in the discussion section rather than the literature review because it complements text about recommendations for practice and this text fits lesss well with the revised literature review structure.
+We put this text in the discussion section rather than the literature review because it complements text about recommendations for practice and this text fits less well with the revised literature review structure.
+Here is the revised text that we placed at the beginning of the "implications for practice" sub-section of the Discussion section.
 
-TEXT TEXT TEXT This recommendation is very relevant for the original manuscript, but a bit less relevant for the revised manuscript in that the previous lit review of "what do we know about off-campus recruiting" has been replaced by a much broader literature review which focuses on X, Y, Z.
-With that being said, the reviewer asks a good question here.
-We refer [IN FOOTNOTE?] the readers to REPORT X, Y, Z FROM RUFFALO NOEL LEVITZ WHICH SAYS BLAH BLAH BLAH.
-FROM EAB COUNSELOR REPORT Q16, "HOW DO YOU PREFER TO RECEIVE INFORMATION FROM COLLEGES"; FOR BOTH PUBLIC AND PRIVATE SCHOOLS, "HIGH SCHOOL VISITS BY COLLEGE REPRESENTATIVES" WERE THE HIGHEST RATED CHANNEL, ESPECIALLY FOR PRIVATE SCHOOL COUNSELORS.
-ALSO, VIRTUAL COUNSELOR EVENTS WERE QUITE LOW RATED.
-IMPLICATION, IN THE PURSUIT OF TRADITIONAL COLLEGE STUDENTS, THIS IS STILL A HAND-TO-HAND BUSINESS.
-ALSO THERE IS A BIT IN THE MARKETING RECRUITING PRACTICES FOR UNDERGRAD STUDENTS BY RUFFALO.
+> Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the Covid pandemic.
+@RN4664 found that "travel" was the top-ranked top-ranked marketing/recruiting expenditure item for both public universities and private universities.
+During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events [@parents_covid_rnl].
+Admissions counselors are now traveling again.
+@RN4896 found that travel was the fifth ranked expenditure item for public universities and the second ranked expenditure item for private universities.
+When asked about areas of future expenditure growth, travel was the top ranked item for public universities and the second ranked item for private universities [@RN4896], suggesting that universities are increasing travel following the decline of the pandemic.
 
-Cost of recruiting undergraduates report, 2022.
-Travel was 5th for publics.
-second for privates.
-Travel was top area of increased expenditure for publics and second top area of increase for privates, suggesting that they were going to increase travel following return from Covid.
+> The @eab_nacac_counselor_2023 survey of high school counselors asked "how do you prefer to receive information from colleges?" High school visits by college representatives was by far the highest rated "channel" for private school counselors and was also the highest rated channel for public school counselors.
+By contrast, virtual visits by admissions representatives received low ratings by high school guidance counselors.
+Finally, @RN4895 asked universities to rank the most effective "outreach strategies for high school counselors." "Calling after visits" was deemed effective for 97% of private universities (the top strategy) and was deemed effective by 88% of public universities.
+What insights do we glean from these market research findings?
+In the era of mass marketing and data science, the pursuit of traditional college students from privileged schools and communities is still a hand-to-hand business and off-campus recruiting visits remain a vital means of recruiting these students.
 
@@
 
-INCLUDE PICTURE OF EGO NETWORK? HAVE TO KEEP THIS PARSIMONIOUS BECAUSE OF PAGE LENGTH CONCERNS
+**Author response**: We appreciate this concern and agree with the recommendation.
+We thought of several tables and figures that could help readers visualize some of the network concepts.
+However, we made the decision to exclude most of these because the manuscript is already quite long.
+The revised manuscript does include a visualization of the full two-mode recruiting network between universities and high schools (CRYSTAL STATE FIGURE NUMBER ONCE YOU ADD IT).
+The manuscript also includes a visualization of the ego network of University of Notre Dame (Figure 1), which is useful in explaining what are ego networks and their relationship with RQ3 (characteristics of high schools that reveive visits)
 
@@
 
-ADD APPENDIX TABLE ABOUT THIS.
+**Author response**: We agree with this suggestion.
+The revised manuscript now includes a table (Table 2) that compares the universities in the analysis sample to the relevant populations the analysis sample was drawn from.
 
@@
 **Author response**: Thank you!
-The results have been revised moderately to reflect analysis of recruiting in neighboring state and to reflect questions from Reviewer 1 (ADD/MODIFY TEXT ONCE YOU HAVE MADE THIS CHANGE)
 
@@
 
-STATE THE SCHOLARLY CONTRIBUTION THE PRESENT ARTICLE DOES MAKE.
+As stated above, the revised manuscript attempts to set up the scholarly contribution as bridging two previously disconnected literatures: (1) the literature on nonresident enrollment at public research universities; and (2) the literature on linkages between private schools and selective (private) universities.
 
-- TO THE NONRES LITERATURE/COMPARE THESE RESULTS TO RESULTS FROM AERJ ARTICLE. SAY THE CONTRIBUTION
-- TO THE PRIVATE SCHOOL TO PRIVATE UNIVERSITY LINKAGES, SHOW WHAT ARE THE ORGS THAT UNIVERSITIES ESTABLISH TIES TO (E.G., ALONG RELIGIOUS LINES)
-- WHAT IS THE BRIDGING CONTRIBUTION.
+In the "implications for scholarship" sub-section of the revised Discussion section, we discuss the contribution of this manuscript to the two respective literatures.
+Next, we argue that our broader/more important contribution is showing that these literatures are part of the same story and developing new insights about the competition privileged students.
+Here, I paste text from the revised manuscript:
+
+> Our more important scholarly contribution is showing that these two literatures are both parts of a broader story about the changing nature of competition for students from privileged schools and communities.
+Selective private universities have been recruiting heavily from private schools for a long time [@RN4642; @RN3519; @RN4640].
+By contrast, the pursuit of out-of-state private school students by public research universities is a relatively new phenomenon and represents competition in the traditional hunting grounds of selective private universities.
+
+> Our analyses shed light about the nature of this competition.
+When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
+Several public universities seem to be competing directly for students targeted by a particular private university.
+For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory (Figure \@ref(tab:privu-percent-visited-by-pubu-matrix)).
+We reason UC-Berkeley is competing directly for students because all four universities are in the same broad echelon of prestige.
+Other potential examples of direct competition include the University of Georgia targeting schools visited by Emory, SMU, TCU, and Tulane, or the University of Arkansas targeting schools visited by Baylor.
+
+> However, public universities that made the greatest number of private school visits seemed to be targeting lower-achieving students at private schools targeted by particular private universities.
+For example, the University of Alabama visited 52.2% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools.
+Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame.
+Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievement, and want to attend a football powerhouse.
+Additionally, CU-Boulder visited 42.4% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
+Similarly, the University of South Carolina competes heavily at schools targeted by Emory, SMU, TCU, and Tulane.
 
@@
 
-**Author response**: ADD TEXT
+**Author response**: ADD TEXT ON FRIDAY.
 

### 2023-12-07 r_r/manuscript_rihe_r_r.Rmd
revising letter

@@
 This manuscript yields practical implications for public and private universities concerned about racial and socioeconomic diversity.
-Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain the fundamental means of maintaining relationships with high school guidance counselors [CITE].
-Prior research shows that that students are sensitive to recruiting interventions, including off-campus recruiting visits.
-Therefore, which high schools a university chooses to visit will affect the subsequent enrollment composition of the university.
+Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors [@RN4896; @RN4895; @eab_nacac_counselor_2023].
+Prior research finds that that students are sensitive to recruiting interventions, including off-campus recruiting visits [@RN4324; @RN4402].
+Therefore, which high schools a university chooses to visit affect the subsequent enrollment composition of the university.
 In the aftermath of the Supreme Court decision on race conscious admissions, public and private universities are searching for ways to increase racial diversity without running afoul of the law.
-The U.S.
-Department of Education recommends that universities expand "outreach to high schools with substantial populations of low-income students and students of color" (CITE, PX X).
-Most public and private universities in our sample visited a disproportionate number of private schools and these private schools tended to enroll mostly white students.
+The @RN4954[p.
+9] recommends that universities expand "outreach to high schools with substantial populations of low-income students and students of color." Most public and private universities in our sample visited a disproportionate number of private schools and these private schools tended to enroll mostly white students.
 We recommend that universities concerned about racial diversity should conduct an internal equity audit of their recruiting practices, for example, comparing the racial and socioeconomic characteristics of schools they visit versus schools they do not visit.
@@
 Betweenness centrality tends to be relevant for empirical contexts (e.g., which manager gets credit for an idea) where an actor who occupies a position between groups can benefit by being a broker of information/ideas [@RN975; @RN4648].
-By contrast, this chapter is more concerned with whether a particular college tends to have indirect connections with some colleges but not others, and what is the subset of high schools this group of colleges tends to visit.
+By cont rast, this chapter is more concerned with whether a particular college tends to have indirect connections with some colleges but not others, and what is the subset of high schools this group of colleges tends to visit.
 Research question 2, motivated below, explores these ideas.
@@
 This study engages with two, previously disconnected literatures.
-Scholarship on nonresident enrollment observes that many public research universities began growing nonresident enrollment following declines in state appropriations [].
-Given that nonresident tuition price is often two- to three-times resident price, it is unsurprising that nonresident students tend to be more affluent than resident students, are less likely to be first-generation students, and are less likely to be Black or Latinx [CITE].
-Public research universities recruit nonresident students using institutional financial aid packages [CITE] and through recruiting interventions that target earlier stages in the enrollment funnel.
-Using nearly the same sample of 15 public research universities used in this study, Author (XXXX) found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools.
+Scholarship on nonresident enrollment observes that many public research universities began growing nonresident enrollment following declines in state appropriations [@RN3753].
+Given that nonresident tuition price is often two- to three-times resident price, it is unsurprising that nonresident students tend to be more affluent than resident students, are less likely to be first-generation students, and are less likely to be Black or Latinx [@RN3685].
+Public research universities recruit nonresident students using institutional financial aid packages [@RN3762] and through recruiting interventions that target earlier stages in the enrollment funnel.
+Using nearly the same sample of 15 public research universities used in this study, @RN4758 found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools.
 Public research universities have a financial incentive to target private school students, who tend to come from affluent households able to pay nonresident tuition price without need-based aid.
@@
 We also engage with scholarship on linkages between private schools and private universities, a linkage that sociologists have observed for many decades.
-Private school students comprise a disproportionate share of enrollment at selective private universities [CITE; AND AUTHOR CALCULATIONS].
-Practically, these linkages exist because private schools want to send their students to "good" universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profile and/or extracurricular activities.
-However, prior research tends to be focused on elite schools and universities [CITE KAHN; CHETTY; CHARTER+BARTER] and does not systematically analyzed connections between private schools and private universities that are selective, but not elite.
-This study extends the literature by investigating private school visits for a sample of 14 selective private universities that exhibit variation in geographic location, religious affiliation, and ranking.
-
-Our more important scholarly contribution is showing that these two separate stories are both parts of a broader narrative about the changing nature of competition for students from privileged schools and communities.
+Private school students comprise a disproportionate share of enrollment at selective private universities [Author calculations based on HSLS:2009].
+Practically, these linkages exist because private schools want to send their students to "good" universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profile and/or extracurricular activities [@RN3519].
+Prior research has often focused on linkages between elite private schools and elite universities [@RN4407; @RN4935; @RN4640].
+Whereas elite universities (e.g., Princeton, Stanford) experience strong student demand based on reputation, merely-selective private universities must incite demand by expending resources on recruiting.
+Prior research has not systematically analyzed connections between private schools and private universities that are selective, but not elite.
+Therefore, this study extends the literature by investigating private school visits for a sample of 14 selective private universities that exhibit variation in geographic location, religious affiliation, and ranking.
+
+Our more important scholarly contribution is showing that these two literatures are both parts of a broader story about the changing nature of competition for students from privileged schools and communities.
 Selective private universities have been recruiting heavily from private schools for a long time [@RN4642; @RN3519; @RN4640].
@@
 Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame.
-Instead, they found a niche by targeting Catholic school students of a similar economic echelon, who have lower academic achievement, and want to attend a football powerhouse.
+Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievement, and want to attend a football powerhouse.
 Additionally, CU-Boulder visited 42.4% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
@@
 @RN4664 found that "travel" was the top-ranked top-ranked marketing/recruiting expenditure item for both public universities and private universities.
-During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events [CITE].
+During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events [@parents_covid_rnl].
 Admissions counselors are now traveling again.
 @RN4896 found that travel was the fifth ranked expenditure item for public universities and the second ranked expenditure item for private universities.
-When asked about areas of future expenditure growth, travel was the top ranked item for public universities and the second ranked item for private universities @RN4896, suggesting that universities are increasing travel following the decline of the pandemic.
-
-Additionally, the EAB (XXXX) survey of high school counselors asked "how do you prefer to receive information from colleges?" High school visits by college representatives was the highest rated "channel" for both public school counselors and (especially) for private school counselors.
+When asked about areas of future expenditure growth, travel was the top ranked item for public universities and the second ranked item for private universities [@RN4896], suggesting that universities are increasing travel following the decline of the pandemic.
+
+The @eab_nacac_counselor_2023 survey of high school counselors asked "how do you prefer to receive information from colleges?" High school visits by college representatives was by far the highest rated "channel" for private school counselors and was also the highest rated channel for public school counselors.
 By contrast, virtual visits by admissions representatives received low ratings by high school guidance counselors.
@@
 Considering the practical importance of off-campus recruiting visits, what are the practical implications of our research?
-Prior scholarly and market research [] shows that students are sensitive to recruiting interventions, including recruiting visits.
-This means that racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university.
-Our research on visits to public high schools [CITE] and this study on visits to private schools finds that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
+Prior scholarly and market research shows that students are sensitive to recruiting interventions, including recruiting visits [@RN4324; @RN4402].
+Consequently, racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university.
+Our research on visits to public high schools [@RN4758] and this study on visits to private schools finds that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
 Some universities may publicly proclaim a commitment to social mobility and privately pursue an intentional recruiting strategy that targets affluent schools and communities.
-We offer practical guidance for universities that may be unintentionally implementing a recruiting strategy tied to social reproduction.
+We offer practical guidance for universities that may be unintentionally implementing a recruiting strategy that privileges the privileged.
 

### 2023-12-08 r_r/letter_to_reviewers.Rmd
finish reviewer letter

@@
 
-**Author response**: ADD TEXT ON FRIDAY.
+**Author response**: As stated previously, the revised manuscript discusses implications for student enrollment composition and university administrators (which we might think of senior administrators, high-level enrollment management administrators).
+We do not state implications that are explicitly for lower-level admissions professionals.
+Page limits were a consideration here.
+Additionally, based on our prior conversations with enrollment managers and admissions officers we believe that junior admissions professionals have limited discretion over which schools a university visits.
+However, if the Reviewer is adamant that the manuscript should be further revised to address implications for a particular group, we will gladly take this on in a subsequent revision.
 
@@
 **Author response**: We agree with this concern.
-As described in the beginning of the letter, the revised manuscript is motivated by the idea that visiting private schools is motivated by the desire to find households that can pay high tuition prices without requiring substantial need-based institutional aid [NOTE TO SELF: NEED TO MAKE THIS RATIONALE MORE CLEAR FOR PRIVATE UNIVERSITIES].
+As described in the beginning of the letter, the revised manuscript is motivated by the idea that visiting private schools is motivated by the desire to find households that can pay high tuition prices without requiring substantial need-based institutional aid.
 
@@
 The revised literature review substantively reviews prior research we conducted about visits to public high schools by public research universities.
-The revised discussion section compares the results from this study to the previous study [REVISE ONCE YOU REVISE THE DISCUSSION SECTION].
-WE FIND BLAH BLAH BLAH
+The revised discussion section discusses findings from the present study in relation to findings from the previous study.
 
@@
 
-WHAT REVIEWER IS ASKING:
-
-- REMOVE ANALYSIS OF Figure 15: One-mode network for public institutions, colored by cluster TO THE APPENDIX
-- REMOVE ANALYSIS OF Figure 16: One-mode network for private universities, colored by cluster TO THE APPENDIX
-- REMOVE EXTENSIVE DISCUSSION OF INDIVIDUAL UNIVERSITIES;
+**Author response**: We agree with these concerns.
+The revised manuscript removes the analyses of within public universities and within private universities (these figures are put into an appendix for readers who are interested).
+Additionally, we removed extensive discussion of individual institutions that is very specific to that institution.
+When describing and discussing findings we still refer to specific institutions as examples, but hopefully in a way that is consistent with what Reviewer 1 is asking for.
 
@@
 
-SEEMS TO WANT ADDITIONAL ANALYSES TO ENGAGE W/ RQ3. I'M NOT SURE WHAT TO ADD HERE. COME BACK TO LATER.
-SOLUTION: SAY THAT WE THINK THE AUTHOR IS MAKING A GOOD POINT.
-INCLUDE THIS POINT AS A LIMITATION.
-AND AN AREA WHERE FUTURE RESEARCH SHOULD PROBE.
-SAY THAT IF THE REVIEWER IS DEAD SET ON SOME ADDITIONAL ANALYSES, I WILL MAKE THIS HAPPEN.
+**Author response**: The reviewer is making a good point here.
+The one-mode network of university recruiting networks with universities colored by cluster indicates which universities are similar or disparate from one another in terms of private schools visited, as do the tabular counts of overlap (Tables 5 and 6).
+However, these results don't actually show how the recruiting strategies differ across/within public and private universities in terms of what sorts of private schools they visit.
+This limitation is one reason that we chose to switch the order of RQ2 and RQ3.
+In the revised manuscript, we show the analyses of network similarity and then we examine -- separately for each university -- the characteristics of private schools that receive visits.
+We hope this change helps address the concern.
+We considered subsequent analyses that would examine the characteristics of private schools that received visits from one set of universities but not another set of universities (e.g., schools visited by Midwestern private universities but not Midwestern puboic universities).
+There are many potential analyses that could be conducted here, and the choice of which analyses to include felt somewhat arbitrary.
+Therefore, we decided to exclude such analyses.
+Since comparison between public and private universities is less of a focus than the initial manuscript, we hope this omisssion is ok.
 
-POTENTIAL ANALYSIS YOU THOUGHT THROUGH
+We considered multiple regression analyses that would examine the characteristics of schools likely to receive a visit, while holding other variables constant.
+Such analyses would be run separately for each university, as we have done in our prior analysis of visits to public high schools by public research universities [@RN4758].
+Since these regression analyses would be conditional correlations rather than estimates of causal effects, we decided that they were not more preferable to the simple descriptive statistics.
+Therefore, we decided to exclude regression analyses because they would add to page length without necessarily providing greater insights.
 
-- WHAT ARE THE CHARACTERISTICS OF PRIVATE SCHOOLS VISITED BY PUBLIC UNIVERSITIES BUT NOT BY PRIVATE UNIVERSITIES 
-- REGRESSION ANALYSES; SEPARATE REGRESSION FOR EACH UNIVERSITY
+However, we did include a new analysis that examines the racial composition of schools in the South that received visits.
+We did this for both visits to private schools and visits to public schools.
+Our rationale for this comparison is that Universities in our sample tended to visit private schools in the South more than private schools in other regions (often this was true even for universities not located in the South).
+Additionally, over the last two decades, private school enrollment growth has been strongest in the South and scholars have argued that "white flight" from desegregated public schools is one reason for this enrollment growth [@RN4504].
+Therefore, we were interested in examining the racial composition of visited Southern private schools and how this compares to the racial composition of visited Southern public schools.
 
@@
 
-ADD LIMITATIONS SECTION. STATE LIMITATIONS OF CROSS-SECTIONAL NATURE OF DATA COLLECTION
+**Author response**: As stated above, we agree with the concern that our analysis sample is a convenience sample.
+The revised limitations section states this explicitly and discusses why this limitation undermines the external validity of our findings.
+We agree with Reviewer 1 that because we do not have longitudinal data, we cannot make strong claims about which university is mimicking which other university.
+We added this limitation to the Limitations section
+
+However, even without longitudinal data, we do feel comfortable making the claim that visiting large numbers of out-of-state private schools is a relatively new phenomenon for most public research universities.
+As stated in the revised "Synthesis" sub-section of the Literature Review section:
+
+> Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), Public research universities began substantially increasing nonresident enrollment en masse around 2005 [@RN3753].
+By contrast, selective private universities have long relied on enrollment from private schools [@RN3519; @RN4640].
+Therefore, the pursuit of out-of-state private school students by public research universities is relatively recent  encroachment on the historic territory of selective private universities and in-state flagships.

### 2023-12-08 r_r/manuscript_rihe_r_r.Rmd
finish reviewer letter

@@
 
-*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[NAME THE UNIVERSITIES] We are still trying to figure out what happened.*
+*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[CRYSTAL -- NAME ALL THE UNIVERSITIES] We are still trying to figure out what happened.*
 
@@
 
-Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college [CITE].
-This research observes strong links -- and student flows -- between private high schools and selective private universities [CITE].
-Private schools enroll many students who can afford private university tuition.
+Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college access [@RN4935; @RN4407; @RN1565; @RN786].
+This research observes strong links -- and student flows -- between private high schools and selective private universities.
+Private schools enroll many students who can afford private university tuition [@RN3519].
 To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between between private school and college.
@@
 All universities visited a large number of private schools in their home region.
-However, most universities in our sample also visited a large number of private schools in the South.
+However, most universities in our sample also visited a large number of private schools in the South, the region where private school enrollment has grown the most over the past three decades [@RN4504].
 The private schools visited by public and private universities in our sample enrolled a much higher share of white students than the public schools visited by these universities.
@@
 Public universities depend on state appropriations but these funds became increasingly uncertain in the 1980s and 1990s [@RN2271].
-Resource dependence theory states that one response to resource decline or uncertainty is to seek alternative, substitute resources [CITE].
+Resource dependence theory states that one response to resource decline or uncertainty is to seek alternative, substitute resources [@RN959].
 Tuition revenue is a potential substitute for state appropriations.
@@
 She found that universities engage in "recruitment redlining -- the circuitous avoidance of predominantly Black and Latinx communities along recruiting visit paths" (p.
-X).
+X) [CRYSTAL -- FIND PAGE NUMBER].
 Although @RN4758 and @RN4934 focused on visits to public high schools, prior research has not considered visits to private schools by public research universities.
@@
 
-A robust empirical literature<!-- from sociology and economics  --> finds that attending private school positively affects college access and college selectivity [e.g.,] [@RN4642; @RN4596; @RN4634; @RN4599].
+A robust empirical literature<!-- from sociology and economics  --> finds that attending private school positively affects college access and college selectivity [e.g., @RN4599; @RN4642; @RN4596; @RN4634].
 Scholarship from the 1980s and 1990s focused on the effects of attending Catholic school [@RN4937; @RN786; @RN4936; @RN4938].
@@
 Stevens accompanied an admissions officer from the College on a visit to Corbett Academy, a prestigious school for girls.
-The admissions officer "said with a grin, 'We're not getting Corbett's finest.'" @RN3519 (p.
-73) writes that,
+The admissions officer "said with a grin, 'We're not getting Corbett's finest.'" @RN3519[p.
+73] writes that,
 
@@
 Drawing from resource dependence theory, as public research universities become more reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices.
-While selective universities have long relied on enrollment from private schools [@RN3519; @RN4640], the pursuit of out-of-state private school students by public research universities is a recent phenomenon and thus an encroachment on the historic territory of selective private universities and in-state flagships.
+Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), Public research universities began substantially increasing nonresident enrollment en masse around 2005 [@RN3753].
+By contrast, selective private universities have long relied on enrollment from private schools [@RN3519; @RN4640].
+Therefore, the pursuit of out-of-state private school students by public research universities is relatively recent  encroachment on the historic territory of selective private universities and in-state flagships.
 Speaking about this competition, an enrollment management consultant said, "'Everybody wants to go to the magic island of full pay students, but it’s rapidly shrinking real estate'" [@RN4911].
@@
 
-Private schools tend to be whiter and more racially segregated than public schools [CITE].
-Over the past three decades, middle-income enrollment at Catholic schools has declined and private school students have become more affluent.
+Private schools tend to enroll a larger share of white students than public schools.^[Evidence for this claim can be seen in Figure \@ref(fig:race-pubu-privhs-pubhs)] Over the past three decades, middle-income enrollment at Catholic schools has declined and private school students have become more affluent.
 In the South, private school enrollment has grown as a consequence of "white flight" from public schools facing desegregation orders [@RN4504].
@@
 For institutions that posted such pages, we scraped the pages once per week throughout 2017.
-Web-scraping was conducted using the Python programming language [STATE WHICH PACKAGE?
+Web-scraping was conducted using the Python programming language [CRYSTAL -- STATE WHICH PYTHON PACKAGE?
 AND/OR SHOW LINK TO A SAMPLE SCRIPT?].
@@
 Table \@ref(tab:sample-characteristics) shows selected characteristics for the universities in our analysis sample.
-Appendix Table X [CRYSTAL ADD] shows how our sample of universities compares to the populations they were drawn from.
-[ONE SENTENCE ABOUT REPRESENTATIVENESS COMPARED TO POPULATION]
-
-INSERT TABLE \@ref(tab:sample-characteristics) ABOUT HERE
+Table \@ref(tab:sample-population-characteristics) shows that our analysis samples of public and private universities appear broadly similar to the populations they were drawn from.
+
+INSERT TABLES \@ref(tab:sample-characteristics) AND \@ref(tab:sample-population-characteristics) ABOUT HERE
 
@@
 This (weighted) network can be represented as a school-by-university matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 universities) in which matrix cell $a_{i,j}$ identifies the number of visits  high school $i$ received from university $j$.
-REFER TO APPENDIX FIGURE THAT SHOWS ENTIRE 2-MODE NETWORK [CRYSTAL ADD FIGURE USING function plot_2mode_graph from network_recruiting_analysis.R]
+CRYSTAL -- ADD SENTENCE THAT REFERS TO APPENDIX FIGURE THAT SHOWS ENTIRE 2-MODE NETWORK [CRYSTAL ADD FIGURE USING function plot_2mode_graph from network_recruiting_analysis.R]
 
@@
 Universities that are closer to Notre Dame visit more private high schools in common.
-[CRYSTAL - FIX ND GRAPH PLEASE]
 
@@
 From this perspective, we identify important variation in recruiting behavior but we cannot make strong claims about the prevalence of observed behaviors in the population.
+Additionally, because we lack longitudinal data about recruiting visits, we cannot make strong claims about which university is mimicking the recruiting behavior of which other university.
 
@@
 The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
-[CRYSTAL ADDS THE TABLE: FOR PUBLIC UNIVERSITIES, THE PRECENT OF HIGH SCHOOLS VISITED BY PRIVATE UNIVERSITIES]
 
@@
 CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located close to one another in Figure \@ref(fig:plot-1mode-u).
-These three universities are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit [HAVEN'T YET INTRODUCED THESE FIGURES].
+As discussed below, these three universities are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit.
 
@@
 UC-Riverside only visited 100 private schools and about 70 of these were located in CA.
-Another group --- Rutgers, Stevens Institute of Technology, UMass-Amherst, SUNY-Stony Brook, and Pitt -- largely consists of public universities with strong ties to the Northeast.
+Another group -- Rutgers, Stevens Institute of Technology, UMass-Amherst, SUNY-Stony Brook, and Pitt -- largely consists of public universities with strong ties to the Northeast.
 
@@
 
-ADDITIONAL SUBGROUP ANALYSES
-
-- racial composition of visited southern schools (separat figures for public universities and private universities; top panel is visited private schools; bottom panel is visited public schools; universe is southern schools)
-
-- look at religious affiliation of visited southern schools?
-- look at racial composition of schools visited by some subset of universities?
--
+CRYSTAL -- ADD THE NEW FIGURES I REQUESTED HERE
+
+- FIGURES: racial composition of visited southern schools (separat figures for public universities and private universities; top panel is visited private schools; bottom panel is visited public schools; universe is southern schools)
 
@@
 For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools.
-By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.n [ADD A SENTENCE OR TWO HERE]
+By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.
+[ADD A SENTENCE ABOUT RACIAL COMPOSITION OF VISITS TO SOUTH?]
 
@@
 We also engage with scholarship on linkages between private schools and private universities, a linkage that sociologists have observed for many decades.
-Private school students comprise a disproportionate share of enrollment at selective private universities [Author calculations based on HSLS:2009].
+Private school students comprise a disproportionate share of enrollment at selective private universities (Author calculations based on HSLS:2009).
 Practically, these linkages exist because private schools want to send their students to "good" universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profile and/or extracurricular activities [@RN3519].
@@
 We suspect that many universities may have incomplete knowledge about which schools they recruit from and how these schools compare to those they do not recruit from.
-Our rationale for this statement is that employee turnover in the enrollment management profession is quite high [CITE HOOVER] and many universities rely on expertise from third-party enrollment management consultancies [AUTHOR].
-Consistent with this idea, when issued public records requests to collect data on "student list" purchases from about 100 public universities [CITE], we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.
+Our rationale for this statement is that employee turnover in the enrollment management profession is quite high [CITE HOOVER] and many universities rely on expertise from third-party enrollment management consultancies [@list_biz].
+Consistent with this idea, when issued public records requests to collect data on "student list" purchases from about 100 public universities [@list_empirics], we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.
 

### 2023-12-08 r_r/manuscript_rihe_r_r.Rmd
add ref, write abstract

@@
 
+__ABSTRACT__
+
+Scholarship on nonresident enrollment by public research universities has developed in isolation from scholarship on linkages between private high schools and selective private universities.
+We argue that these literatures are part of a broader story about the competition for students from affluent schools and communities.
+This manuscript analyzes off-campus recruiting visits to private high schools made by a convenience sample of 15 public research universities and 14 selective private universities.
+An off-campus recruiting visit indicates a social relationship between a school and a university.
+Therefore, we utilize social network methods to examine the recruiting networks of public and private universities.
+With respect to scale (research question 1), universities in our sample made a disproportionate number of visits to private high schools.
+With respect to overlap (RQ2), simple network analyses and community detection methods reveal substantial overlap in the recruiting networks of public and private universities.
+RQ3 assesses the characteristics of visited schools.
+Both public and private universities tended to visit private schools in their home geographic region and also in the South, where private school enrollment growth has been strongest.
+Visited private schools enroll a much larger share of white students than visited public schools.
+Surprisingly, several public research universities visited sectarian private high schools at a rate similar to sectarian private universities.
+
+\pagenumbering{roman}
+\newpage
+\pagenumbering{gobble}
+\pagenumbering{arabic}
+
 # Introduction
@@
 We suspect that many universities may have incomplete knowledge about which schools they recruit from and how these schools compare to those they do not recruit from.
-Our rationale for this statement is that employee turnover in the enrollment management profession is quite high [CITE HOOVER] and many universities rely on expertise from third-party enrollment management consultancies [@list_biz].
+Our rationale for this statement is that employee turnover in the enrollment management profession is quite high [@em_burnout_hoover] and many universities rely on expertise from third-party enrollment management consultancies [@list_biz].
 Consistent with this idea, when issued public records requests to collect data on "student list" purchases from about 100 public universities [@list_empirics], we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.

### 2023-12-13 r_r/manuscript_rihe_r_r.Rmd
updates to manuscript

@@
 
-*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[CRYSTAL -- NAME ALL THE UNIVERSITIES] We are still trying to figure out what happened.*
+*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities (Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette), 12 selective private liberal arts colleges (Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College), and 15 public research universities (UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, University of Arkansas).
+We are still trying to figure out what happened.*
 
@@
 
-Autumn is college recruiting visit season at Harpeth Hall, a non-sectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
+Autumn is college recruiting visit season at Harpeth Hall, a nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
 Founded in 1951, Harpeth is an "A+" school ranked 337 in the nation according to the 2020 *Best Private High Schools in America* by Niche.
-Enrollment patterns at Nashville-area private schools reflect broader regional patterns, whereby “efforts by the courts to desegregate public schools in the South resulted in White flight to private schools” [@RN4504, p.
+Enrollment patterns at Nashville-area private schools reflect broader regional patterns, whereby "efforts by the courts to desegregate public schools in the South resulted in White flight to private schools" [@RN4504, p.
 14].
@@
 
-From September 6th through October 17th, Harpeth received recruiting visits from 11 private universitiesin our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denvor, Emory, Tulane, Baylor, Texas Christian University), and three private liberal arts colleges (Harvey Mudd, Scrips, and Sewanee).
+From September 6th through October 17th, Harpeth received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
 Previous scholarship observes strong connections between private schools and selective private universities [@RN3519; @RN4407].
-However, Harpeth also received visits from six out-of-state public research universities, the University of Cincinatti, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.
+However, Harpeth also received visits from six out-of-state public research universities, the University of Cincinnati, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.
 
@@
 It is an "A+" school, ranked 127th in the nation, and is more racially diverse than Harpeth (64% white, 11.5% Black, 3.5% Latinx, 10.0% Asian).
-From September 11th 2017 through October 18th, the University School received visits from nearly the same set of 11 private universities that visited Harpeth (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinatti, CU Boulder).
+From August 22nd 2017 through October 18th, the University School received visits from nearly the same set of 11 private universities that visited Harpeth (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinnati, CU Boulder).
 
 Father Ryan High School is a Catholic school founded in 1925.
-Father Ryan is predominantly white (86%, 7% Black or Latinx) and received an "A" grade from Niche, meaning it is not ranked in the top 1,000 US private schools.
-In fall 2017, Father Ryan received visits from nine of the 14 private universities in our sample (including all the Catholic universities) and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama.
-Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from five private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University).
+Father Ryan is predominantly white (86%, 7% Black or Latinx) and received an "A" grade from Niche, meaning it is not ranked in the top 1,000 U.S.
+private schools.
+In Fall 2017, Father Ryan received visits from eight of the 14 private universities in our sample (including three of the four Catholic universities)<!--Changed nine to eight - Marquette (Catholic, univ_id: 239105) did not visit Father Ryan (school_id: 01294971)--> and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama.
+Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from six private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University).
 It also received visits from the University of Cincinnati, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder.
@@
 Thus, organizations respond by symbolically adopting some goals and substantively adopting others [@RN513].
-Under symbolic adoption, organizations adopt policies and structures that send signals to external constituents but do not substantively affect resource allocation inside the the "technical level" of the organization.^[Contingency theory states that organizations consist of "technical levels" responsible for processing inputs and producing outputs and "managerial levels" responsible for directing the technical level and tending to demands from the external environment [@RN531].
+Under symbolic adoption, organizations adopt policies and structures that send signals to external constituents but do not substantively affect resource allocation inside the "technical level" of the organization.^[Contingency theory states that organizations consist of "technical levels" responsible for processing inputs and producing outputs and "managerial levels" responsible for directing the technical level and tending to demands from the external environment [@RN531].
 The technical level achieves effectiveness by focusing on a small, stable set of goals.] Under substantive adoption, organizations direct resources in the technical level towards achieving the goal.
@@
 These out-of-state visits focused on affluent, predominantly white public schools.
-Set against the scholarship about declining state appropriations and growing nonresident enrollment [@RN3753; @RN3685], these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition price.
+Set against the scholarship about declining state appropriations and growing nonresident enrollment [@RN3753; @RN3685], these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition prices.
 
@@
 Private schools enroll many students who can afford private university tuition [@RN3519].
-To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between between private school and college.
+To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between private schools and colleges.
 We argue that these two stories have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities.
@@
 Network analyses revealed substantial overlap in the recruiting networks of universities in our sample.
-For several public universities (e.g., University of Alabama, University of South Carolina) their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, Texas Christian University) than they did to other public universities in our sample.
+For several public universities (e.g., University of Alabama, University of South Carolina), their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, Texas Christian University) than they did to other public universities in our sample.
 Results suggest that recruiting networks are substantially a function of geographic location.
@@
 Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors [@RN4896; @RN4895; @eab_nacac_counselor_2023].
-Prior research finds that that students are sensitive to recruiting interventions, including off-campus recruiting visits [@RN4324; @RN4402].
-Therefore, which high schools a university chooses to visit affect the subsequent enrollment composition of the university.
-In the aftermath of the Supreme Court decision on race conscious admissions, public and private universities are searching for ways to increase racial diversity without running afoul of the law.
+Prior research finds that students are sensitive to recruiting interventions, including off-campus recruiting visits [@RN4324; @RN4402].
+Therefore, which high schools a university chooses to visit affects the subsequent enrollment composition of the university.
+In the aftermath of the Supreme Court decision on race-conscious admissions, public and private universities are searching for ways to increase racial diversity without running afoul of the law.
 The @RN4954[p.
@@
 
-We stiuate this study vis-a-vis scholarship on enrollment management behavior by public research universities and particularly the pursuit of affluent nonresident students, a population also targeted by selective private universities.
+We situate this study vis-a-vis scholarship on enrollment management behavior by public research universities and particularly the pursuit of affluent nonresident students, a population also targeted by selective private universities.
 The so-called "iron triangle" of enrollment management states that universities pursue the broad enrollment goals of access, academic profile, and revenue generation [@RN3524; @RN2772].
@@
 @RN2772[p.
-221] state that “most enrollment management policies\ldots do not advance all three objectives; instead they lead to gains in some areas and declines in others.” Scholarship argues that selective private universities prioritize academic profile and revenue generation, with funds generated from tuition and donation feeding the arms race for prestige [@RN3522; @RN1549; @RN3519].
+221] state that "most enrollment management policies\ldots do not advance all three objectives; instead they lead to gains in some areas and declines in others." Scholarship argues that selective private universities prioritize academic profile and revenue generation, with funds generated from tuition and donation feeding the arms race for prestige [@RN3522; @RN1549; @RN3519].
 Historically, public research universities prioritize enrollment of high-performing state residents, often with an emphasis on social mobility for students who cannot afford private universities [@RN3608].
-However, scholarship on privatization argues the public research universities increasingly emphasizing tuition revenue and rankings and de-emphasize access for state residents [@RN1577; @RN1118].
+However, scholarship on privatization argues that public research universities increasingly emphasize tuition revenue and rankings and de-emphasize access for state residents [@RN1577; @RN1118].
 
@@
 Tuition revenue is a potential substitute for state appropriations.
-Most states cap resident tuition price, but not nonresident tuition price.
+Most states cap resident tuition prices, but not nonresident tuition prices.
 Therefore, @RN3753 argued that public universities have a financial incentive to grow nonresident enrollment in response to declines in state appropriations.
@@
 Other studies of nonresident enrollment examine university enrollment composition.
-Using data from NPSAS 2011-12, @RN3685 show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients and are less likely to be Black or LatinX.
+Using data from NPSAS 2011-12, @RN3685 show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or LatinX.
 Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and LatinX students.
@@
 @RN4758 analyzed off-campus recruiting visits to public high schools by 15 public research universities.
-Recruiting visits to in-state high schools tended exhibit modest racial and socioeconomic bias.
+Recruiting visits to in-state high schools tended to exhibit modest racial and socioeconomic bias.
 However, 12 of the 15 universities made more visits to out-of-state high schools than in-state high schools.
 These out-of-state visits focused on public schools in affluent, predominantly white communities.
-@RN4934 conducted geo-spatial analyses of out-of-state recruiting visits to Los Angeles and Dallas by four public research universities.
+@RN4934 conducted geospatial analyses of out-of-state recruiting visits to Los Angeles and Dallas by four public research universities.
 She found that universities engage in "recruitment redlining -- the circuitous avoidance of predominantly Black and Latinx communities along recruiting visit paths" (p.
-X) [CRYSTAL -- FIND PAGE NUMBER].
-Although @RN4758 and @RN4934 focused on visits to public high schools, prior research has not considered visits to private schools by public research universities.
+X).<!--[CRYSTAL -- FIND PAGE NUMBER] TODO: I don't think I'm able to access the full version of the paper: https://doi.org/10.1080/00221546.2021.2004811--> Although @RN4758 and @RN4934 focused on visits to public high schools, prior research has not considered visits to private schools by public research universities.
 For example, what is the scale of these visits and what are the characteristics of visited schools?
@@
 @RN4504<!-- use data from several national surveys to --> set the stage by describing long-term trends in private school enrollment.
-The percentage of American (elementary school) students attending private school declined from 15% in the mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
+The percentage of American (elementary school) students attending private schools declined from 15% in the mid-1960s to 10% in the mid-1970s, and declined gradually from 11% in 1999 to 9% in 2015.
 The private school enrollment rate for high-income families and for low-income families has remained relatively stable over time at about 17% and 4%, respectively.
@@
 The High School Longitudinal Survey of 2009 (HSLS) tracks the postsecondary destinations of students who were in ninth grade in 2009.
-Simple descriptive statistics are eye-opening (Author calculations).^[Analyses consist students who met the following conditions: completed the 2012 follow-up survey; obtained high school transcript data; and completed the 2016 followup survey.
+Simple descriptive statistics are eye-opening (Author calculations).^[Analyses consist of students who met the following conditions: completed the 2012 follow-up survey; obtained high school transcript data; and completed the 2016 follow-up survey.
 The survey weight variable used was W4W1W2W3STU.
@@
 Data on high school control come from the HSLS school file and from the Private School Survey.] About 93% of students attended a public high school and 7% attended a private high school, including 3.6% attending a Catholic school, 1.6% attending a nonsectarian school, and 1.8% attending a Christian school.
-Of public high school students, 5.0% attending a public university ranked in the top 100 by US News and World Report (USNWR) and 1.9% attended a private university ranked in the top 100.
+Of public high school students, 5.0% attending a public university ranked in the top 100 by U.S.
+News and World Report (USNWR) and 1.9% attended a private university ranked in the top 100.
 Of private high school students, 10.9% attended a top 100 public university and 16.8% attended a top 100 private university.
-For Catholic school students, 12.8% attended a top 100 public university and 11.7% attended a top 100 private university, while for Christian schools these percentages were 8.2% and 8.2%, respectively.
-However, for nonsectarian private school students, 11.3% attended a top 100 public university and 39.8 percent attended a top 100 private university.
-Focusing on the institutional composition of private universities in USNWR top 100, 39.8% attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).
-
-Scholarship has been particularly interested in the relationship between attending a prestigious private school and attending an ultra selective university [@RN4647; @RN4643; @RN4647; @RN4589].
-@RN4935 acquired unprecedented data -- application files and admissions decisions linked to income tax records  -- to investigate why high income families are over-represented at "Ivy Plus" colleges.
+For Catholic school students, 12.8% attended a top 100 public university and 11.7% attended a top 100 private university, while for Christian schools these percentages were 8.2% and 8.2%<!--TODO: Want to double check they're both 8.2%?-->, respectively.
+However, for nonsectarian private school students, 11.3% attended a top 100 public university and 39.8% attended a top 100 private university.
+Focusing on the institutional composition of private universities in USNWR top 100, 39.8%<!--TODO: Want to double check this and the previous sentence are both 39.8%?--> attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).
+
+Scholarship has been particularly interested in the relationship between attending a prestigious private school and attending an ultra-selective university [@RN4647; @RN4643; @RN4647; @RN4589].
+@RN4935 acquired unprecedented data -- application files and admissions decisions linked to income tax records  -- to investigate why high-income families are over-represented at "Ivy Plus" colleges.
 Conditioning on SAT and ACT scores, applications from high-income families (top 1%) received the same academic rating as applications from lower-income families.
-However, applications from high-income families received higher non-academic ratings (extracurricular activities, leadership traits) then applications from lower-income families.
-In turn, the higher non-academic ratings for high-income applicants was driven by the fact that these students tended to attend elite private high schools that devote substantial resources to teacher recommendations and guidance counselor letters.
+However, applications from high-income families received higher non-academic ratings (extracurricular activities, leadership traits) than applications from lower-income families.
+In turn, the higher non-academic rating for high-income applicants was driven by the fact that these students tended to attend elite private high schools that devote substantial resources to teacher recommendations and guidance counselor letters.
 
@@
 @RN3519 provides an ethnography of the admissions office at a selective private liberal arts college.
-The College is sensitive about its position in U.S.
-News Rankings and enrollment priorities tend to focus on academic profile and revenue generation.
+The College is sensitive about its position in the U.S.
+News Rankings, and enrollment priorities tend to focus on academic profile and revenue generation.
 @RN3519 highlights the relational function of off-campus recruiting visits, stating that "the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide" (p.
-54) Therefore, during the autumn "travel season," admissions officers visit selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
+54).
+Therefore, during the autumn "travel season," admissions officers visit selected high schools across the country "to spread word of the institution and maintain relationships with guidance counselors" (p.
 53-54) because counselors who view a college favorably will steer students to that college.
@@
 Still, by most standards this excellent school's modest achievers were very good admissions prospects, which was why we were visiting.
-Even Corbett's less fine would enter college well prepared academically, and their generally affluent famiies could absorb the College's full tuition and board cost with little, if any, financial aid."
+Even Corbett's less fine would enter college well prepared academically, and their generally affluent families could absorb the College's full tuition and board cost with little, if any, financial aid.
 
@@
 
-Additionally, scholarship on linkages between private high schools and private universities focuses on elite high schools and ultra selective universities [@RN1565; @RN4647; @RN4935; @RN4321].
+Additionally, scholarship on linkages between private high schools and private universities focuses on elite high schools and ultra-selective universities [@RN1565; @RN4647; @RN4935; @RN4321].
 With the exception of the single-institution ethnography by @RN3519, we know less about linkages between private schools and private universities that are selective but not elite.
 These merely-selective universities are self-conscious about their reputation, and have fewer resources and weaker student demand compared to Ivy Plus universities.
-Analyses of off-campus recruiting visits provides novel insights about the schools and student populations these institutions target.
+Analyses of off-campus recruiting visits provide novel insights about the schools and student populations these institutions target.
 
@@
 Drawing from resource dependence theory, as public research universities become more reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices.
-Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), Public research universities began substantially increasing nonresident enrollment en masse around 2005 [@RN3753].
+Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), public research universities began substantially increasing nonresident enrollment en masse around 2005 [@RN3753].
 By contrast, selective private universities have long relied on enrollment from private schools [@RN3519; @RN4640].
-Therefore, the pursuit of out-of-state private school students by public research universities is relatively recent  encroachment on the historic territory of selective private universities and in-state flagships.
+Therefore, the pursuit of out-of-state private school students by public research universities is a relatively recent encroachment on the historic territory of selective private universities and in-state flagships.
 Speaking about this competition, an enrollment management consultant said, "'Everybody wants to go to the magic island of full pay students, but it’s rapidly shrinking real estate'" [@RN4911].
-By analyzing the network of recruiting visits, we show whether public research universities and selective private universities are competing for students at similar ets of private schools.
+By analyzing the network of recruiting visits, we show whether public research universities and selective private universities are competing for students at similar sets of private schools.
 This may be direct competition for the same student or vying to be the second choice for students who are rejected by their top choice.
 
-Private schools tend to enroll a larger share of white students than public schools.^[Evidence for this claim can be seen in Figure \@ref(fig:race-pubu-privhs-pubhs)] Over the past three decades, middle-income enrollment at Catholic schools has declined and private school students have become more affluent.
+Private schools tend to enroll a larger share of white students than public schools.^[Evidence for this claim can be seen in Figure \@ref(fig:race-pubu-privhs-pubhs).] Over the past three decades, middle-income enrollment at Catholic schools has declined and private school students have become more affluent.
 In the South, private school enrollment has grown as a consequence of "white flight" from public schools facing desegregation orders [@RN4504].
@@
 For institutions that posted such pages, we scraped the pages once per week throughout 2017.
-Web-scraping was conducted using the Python programming language [CRYSTAL -- STATE WHICH PYTHON PACKAGE?
-AND/OR SHOW LINK TO A SAMPLE SCRIPT?].
+Web-scraping was conducted using the Python programming language using the _requests_ library<!--[CRYSTAL -- STATE WHICH PYTHON PACKAGE?
+AND/OR SHOW LINK TO A SAMPLE SCRIPT?] TODO: Added the package used but not too sure if there's a simple way to show example...
+these (https://github.com/ksalazar3/recruitment-scraping/tree/master/universities) are univs w/ custom scripts but they're all passed to this main script (https://github.com/ksalazar3/recruitment-scraping/blob/master/scraper.py) that actually calls the requests library.
+Also, this GitHub repo is currently private.-->.
 Many universities in our data collection sample only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools).
@@
 
-For public universities in our analysis sample, we assessed data quality of the web-scraped data by asking the enrollment/admissions office for these data.
+For public universities in our analysis sample, we assessed the quality of the web-scraped data by asking the enrollment/admissions office for these data.
 If a university denied or ignored our request, we issued a formal public records request.
@@
 For these 11 universities, web-scraped data was very similar to publicly requested data.
-For universities that sent us data, the analyses below use “requested” rather than “scraped” data because requested “requested” data tended to have more events.
-Broad patterns were similar across requested data versus scraped data, and results based on scraped data are available on request.
+For universities that sent us data, the analyses below use "requested" rather than "scraped" data because requested data tended to have more events.
+Broad patterns were similar across requested data versus scraped data, and results based on scraped data are available upon request.
 @RN4758 describe data quality checks in greater detail.
 
-The data collection sample for the broader project consisted of: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), and all private universities in the top 100 of U.S.
+The data collection sample for the broader project consisted of: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), all private universities in the top 100 of U.S.
 News and World Report National Universities rankings (N=58), and all private colleges in the top 50 of U.S.
-News and World Report Liberal Arts Colleges rankings (N=47).
-The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection.
+News and World Report Liberal Arts Colleges rankings (N=47).<!--TODO: Confirm N's--> The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection.
 This article excludes private liberal arts colleges because having a third institutional type would substantially increase article length.
@@
 For these universities, we analyze recruiting visits to private high schools that meet the following criteria: enrolls at least 10 12th grade students, is not primarily a virtual school, and is located in the 50 U.S.
-states, the District of Columbia, or land regulated by the Bureau of Indian Affairs is included in our analysis.
+states, the District of Columbia, or land regulated by the Bureau of Indian Affairs.
 
@@
 News & World Report.
-For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.^[For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small amount of schools.]
+For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.^[For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small number of schools.]
 
@@
 "One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
-Similarly, the social network of Twitter consists of handles (vertices) who are connected to one another by following or being followed.
+Similarly, the social network of Twitter<!--TODO: Not sure if we should call this X now?
+haha--> consists of handles (vertices) who are connected to one another by following or being followed (edges).
 
@@
 "Two-mode" networks consist of vertices associated with one type of actor/entity having connections to vertices of another type of actor/entity [@RN2457].
-For example, an actor-movie network -- for example, the so-called "Six Degrees of Kevin Bacon" -- consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
+For example, an actor-movie network -- such as the so-called "Six Degrees of Kevin Bacon" -- consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie.
 The most commonly analyzed two-mode network in social networks literature is a corporate board-director network  [e.g., @RN4663].
@@
 This (weighted) network can be represented as a school-by-university matrix (e.g., a $500 \times 40$ matrix if our network contains 500 high schools and 40 universities) in which matrix cell $a_{i,j}$ identifies the number of visits high school $i$ received from university $j$.
-CRYSTAL -- ADD SENTENCE THAT REFERS TO APPENDIX FIGURE THAT SHOWS ENTIRE 2-MODE NETWORK [CRYSTAL ADD FIGURE USING function plot_2mode_graph from network_recruiting_analysis.R]
+This can also be visualized by a network graph of interconnected nodes.
+For example, Appendix Figure \@ref(fig:plot-2mode) shows the two-mode network graph of the 29 total universities in our analysis sample and all the private high schools they visited.
 
@@
 **RQ1: Degree centrality**.
-In social network analysis, *centrality* refers to the importance or prominence or "being in the middle of things" of an actor/vertex in a social network [@RN4725].<!--[CITE]--> Many alternative measures of centrality have been developed.
+In social network analysis, *centrality* refers to the importance or prominence or "being in the middle of things" of an actor/vertex in a social network [@RN4725].
+Many alternative measures of centrality have been developed.
 All measures agree that centrality is an actor/vertex-level construct (e.g., each college in our network will have a centrality value, regardless of which centrality measure we use).
@@
 For each high school in our network, degree centrality is the number of colleges in our network that visited the high school.
-For our empirical context, we conceive of degree centrality as a measure of scale of the number of private high schools a college visits and, equivalently, the number of private high schools we observe having a social relation with each college.
+For our empirical context, we conceive of degree centrality as a measure of the scale of private high school visits by a college, or equivalently, the number of private high schools we observe having a social relation with each college.
 
 Research question 1 states, "How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?" We answer this research question by comparing degree centrality across universities, both within university type (public vs.
-private) and between university type.
+private) and between university types.
 In order to discern the relative emphasis on private schools by each university, we also compare the number of recruiting visits to private schools to the number of visits to public schools.
@@
 Betweenness centrality tends to be relevant for empirical contexts (e.g., which manager gets credit for an idea) where an actor who occupies a position between groups can benefit by being a broker of information/ideas [@RN975; @RN4648].
-By cont rast, this chapter is more concerned with whether a particular college tends to have indirect connections with some colleges but not others, and what is the subset of high schools this group of colleges tends to visit.
+By contrast, this chapter is more concerned with whether a particular college tends to have indirect connections with some colleges but not others, and what is the subset of high schools this group of colleges tends to visit.
 Research question 2, motivated below, explores these ideas.
@@
 We are interested in similarities and differences in the recruiting networks of the public research universities and selective private universities in our sample.
-This interest motivates research question 3, "to what extent do public research universities and private universities visit overlapping sets of private high schools?"
-
-Following prior scholarship on two-mode networks [@RN4677; @RN4725], we address RQ3 by simultaneously graphing the one-mode university network and categorizing universities into distinct communities that have similar recruiting networks.
+This interest motivates research question 2, "to what extent do public research universities and private universities visit overlapping sets of private high schools?"
+
+Following prior scholarship on two-mode networks [@RN4677; @RN4725], we address RQ2 by simultaneously graphing the one-mode university network and categorizing universities into distinct communities that have similar recruiting networks.
 In the resulting graph, vertices (universities) that share many connections are located close together and vertices that are "central" -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph.
@@
 The order 1 ego network for the University of Notre Dame consists of all private high schools that received at least one visit from Notre Dame.
-The order 2 ego network consists of all private schools that visited Notre Dame and all universities that visited the private high schools visited by Notre Dame.
+The order 2 ego network consists of all private schools that were visited by Notre Dame and all universities that visited the private high schools visited by Notre Dame.
 Figure \@ref(fig:nd-religion) shows the order 2 ego network for Notre Dame, with vertices colored by religious affiliation.
@@
 
-A common finding in social networks research is that actors are more likely to form connections with actors who are similar to them [@RN1722].
+A common finding in social network research is that actors are more likely to form connections with actors who are similar to them [@RN1722].
 Said differently, ego networks are biased towards "homophily" rather than "heterophily." Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be friends on Facebook if they have similar political ideologies).
@@
 First, prior scholarship suggests that private colleges and private high schools are more likely to have a relationship when they share common ideologies or view themselves as belonging to the same echelon [@RN3519; @RN4321;@RN4407].
-Second, similar to the colloquialism 'you are what you eat,' the characteristics of visited private high schools have subsequent consequences for the the enrollment composition of universities.
+Second, similar to the colloquialism 'you are what you eat,' the characteristics of visited private high schools have subsequent consequences for the enrollment composition of universities.
 
@@
 
-A related limitation is that analysis sample consists of the subset of universities from the data collection sample that we believe posted all off-campus recruiting visits on their admissions website.
+A related limitation is that our analysis sample consists of the subset of universities from the data collection sample that we believe posted all off-campus recruiting visits on their admissions website.
 This process for defining the analysis sample raises two concerns.
@@
 Research question 1 asks, "How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?" This question can be answered by counting the number of visits to private high schools, which is equivalent to calculating the degree centrality for each university.
-In addition to scale, we are also interested in the relative scale of visits to private high schools.
+In addition, we are also interested in the relative scale of visits to private high schools as compared to other types of visits.
 That is, the number of visits to private high schools as a proportion of all off-campus recruiting visits, or as a proportion of all recruiting visits to high schools.
@@
 On average, the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample conducted `r round((events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()), digits = 0)` off-campus recruiting events in 2017, ranging from a low of `r events_df %>% filter(univ_id == '139959') %>% count() %>% as.numeric()` for the University of Georgia to a high of `r events_df %>% filter(univ_id == '100751') %>% count() %>% as.numeric()` for the University of Alabama.
-By contrast, the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample conducted an average of `r round((events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()), digits = 0)` events, ranging from a low of `r events_df %>% filter(univ_id == '186867') %>% count() %>% as.numeric()` by Stevens Institute of Technology (located in Hoboken, NJ) to a high of `r events_df %>% filter(univ_id == '239105') %>% count() %>% as.numeric()` by Marquette University (located in Milwaukee, WI).
+By contrast, the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample conducted an average of `r round((events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())/(univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()), digits = 0)` events, ranging from a low of `r events_df %>% filter(univ_id == '201645') %>% count() %>% as.numeric()` by Case Western Reserve (located in Cleveland, OH) to a high of `r events_df %>% filter(univ_id == '239105') %>% count() %>% as.numeric()` by Marquette University (located in Milwaukee, WI).
 Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs','priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric())*100, digits=1)`% of visits were to a public or private high school, whereas for selective private universities `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('pub_hs','priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric())*100, digits=1)`% of all visits were to a public or private high school.
@@
 Across all selective private universities in our sample, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of high school visits were to private high schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
-Although, the relative emphasis on private high schools was a bit closer for out-of-state visits; across all selective private universities, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% of out-of-state high school visits were to private schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
+Although, the relative emphasis on private high schools was slightly closer for out-of-state visits; across all selective private universities, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% of out-of-state high school visits were to private schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
 
 Even though selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools.
-Figure \@ref(fig:actual-proportional-pubu) (public universities) and Figure \@ref(fig:actual-proportional-privu) (private universities) show the actual number of private school visits made compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.^[When calculating the hypothetical, proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university.
+Figure \@ref(fig:actual-proportional-pubu) (public universities) and Figure \@ref(fig:actual-proportional-privu) (private universities) show the actual number of private school visits made compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.^[When calculating the hypothetical proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university.
 Our rationale for this decision is that it is unhelpful to include schools in states that the university ignored entirely.] Figure \@ref(fig:actual-proportional-pubu) shows that the actual number of private school visits exceeded the proportional number of private school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
@@
 
-We answer research question 2 by briefly describing tabular representations of overlap between the set of public research universities and overlap between the set of selective private universities.
-Next, we utilize tabular and graphical representations to describe ovelrap between the set of public and private universities in our sample.
-
-Table \@ref(tab:pubu-percent-matrix) provide a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
-For each public university (column), each cell of Table Table \@ref(tab:pubu-percent-matrix) shows number of visited high schools in common as a percent of the total number of high schools visited by the column university.
-This indicates the extent to which public universities were competing for students at the same set of private school.
+We answer research question 2 by briefly describing tabular representations of overlap within the set of public research universities and overlap within the set of selective private universities.
+Next, we utilize tabular and graphical representations to describe overlap between the set of public and private universities in our sample.
+
+Table \@ref(tab:pubu-percent-matrix) provides a tabular representation of the extent to which public universities visited overlapping sets of private high schools.
+For each public university (column), each cell of Table \@ref(tab:pubu-percent-matrix) shows the number of visited high schools in common with the row university as a percent of the total number of high schools visited by the column university.
+This indicates the extent to which public universities were competing for students at the same set of private schools.
 For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7% of these high schools and CU-Boulder visited 39.1% of these high schools.
-Appendix Table \@ref(tab:pubu-count-matrix) shows counts rather than percents.
+Appendix Table \@ref(tab:pubu-count-matrix) shows counts rather than percentages.
 
@@
 
-Table \@ref(tab:privu-percent-matrix) show overlap in private high schools visited by the selective private universities in our sample.
+Table \@ref(tab:privu-percent-matrix) shows overlap in private high schools visited by the selective private universities in our sample.
 Appendix Table \@ref(tab:privu-count-matrix) shows counts.
@@
 This is demonstrated tabularly by the higher percentages in Table \@ref(tab:privu-percent-matrix) compared to Table \@ref(tab:pubu-percent-matrix).
-Private universities that share a high percent of visits tend to have the same religious affiliation and/or be located in the same geographic region.
+Private universities that share a high percentage of visits tend to have the same religious affiliation and/or be located in the same geographic region.
 For example, the Catholic universities -- Notre Dame, Villanova, Boston College, and Marquette -- seem to visit many private high schools in common.
@@
 Next, we examine overlap in a network that contains the 15 public universities and the 14 private universities.
-Table \@ref(tab:privu-percent-visited-by-pubu-matrix) shows, for each private university, the percent of schools that were also visited by each public university.
+Table \@ref(tab:privu-percent-visited-by-pubu-matrix) shows, for each private university, the percentage of schools that were also visited by each public university.
 This table shows the extent to which public universities were competing at private schools targeted by private universities.
-For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.5% of these schools.
-Similarly, CU-Boulder visited 46.4 of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
-The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
+For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.2% of these schools.
+Similarly, CU-Boulder visited 46.4% of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
+The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass-Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
 
@@
 Network graphs are useful for showing which universities have similar private high school recruiting networks.
-Figure \@ref(fig:plot-1mode-u) graphs the one-mode network that consists of all 29 public and private universities in the sample (Appendix Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network and Appendix Figure \@ref(fig:plot-1mode-privu) graph the one-mode private university network).
+Figure \@ref(fig:plot-1mode-u) graphs the one-mode network that consists of all 29 public and private universities in the sample (Appendix Figure \@ref(fig:plot-1mode-pubu) graphs the one-mode public university network and Appendix Figure \@ref(fig:plot-1mode-privu) graphs the one-mode private university network).
 
 Whether graphing one-mode or two-mode networks, network graphs show vertices as circles and edges as lines connecting pairs of vertices.
-In Figure \@ref(fig:plot-1mode-u), each circle represents a public university and two universities share an edge -- represented by a solid line -- if both universities visit at least one high school in common.
-The width of the line between two universities indicates the *weight* of the edge, defined as number of high schools both universities visited.
+In Figure \@ref(fig:plot-1mode-u), each circle represents a public or private university and two universities share an edge -- represented by a solid line -- if both universities visited at least one high school in common.
+The width of the line between two universities indicates the *weight* of the edge, defined as the number of high schools both universities visited in common.
 Network methods conceive of vertices as repelling one another [@RN4725], like the "north pole" of two magnets.
@@
 Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities with the highest degree centrality (i.e., those that visited the most schools).
-The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), Northwestern (377), University of South Carolina (396), and CU-Boulder (362).
+The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), University of South Carolina (396), Northwestern (377), and CU-Boulder (362).
 Notably, while the majority of universities located near the center of Figure \@ref(fig:plot-1mode-u) are private, three are public.
@@
 Similarly, the University of South Carolina, which visited a relatively high share of Christian schools, is close to TCU and SMU.
-CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located close to one another in Figure \@ref(fig:plot-1mode-u).
+CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located fairly close to one another in Figure \@ref(fig:plot-1mode-u).
 As discussed below, these three universities are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit.
@@
 59].
-Therefore, universities in the same cluster have a relatively large number of direct and direct ties with other universities in the cluster and have relatively few direct and indirect ties with universities in other clusters.
+Therefore, universities in the same cluster have a relatively large number of direct and indirect ties with other universities in the cluster and have relatively few direct and indirect ties with universities in other clusters.
 We utilize that "cluster fast and greedy" approach from @RN4725.
@@
 
-In Figure \@ref(fig:plot-1mode-u), universities are allocated to groups based on the specification that the algorithm should identify four groups (we also experimented with three, five, and six groups).
+In Figure \@ref(fig:plot-1mode-u), universities are allocated to groups -- indicated by the color of the vertices -- based on the specification that the algorithm should identify four groups (we also experimented with three, five, and six groups).
 Universities located near the center of Figure \@ref(fig:plot-1mode-u) do not all belong to the same cluster and, more broadly, universities located close to one another do not all belong to the same cluster.
@@
 UC-Riverside only visited 100 private schools and about 70 of these were located in CA.
-Another group -- Rutgers, Stevens Institute of Technology, UMass-Amherst, SUNY-Stony Brook, and Pitt -- largely consists of public universities with strong ties to the Northeast.
+Another group -- Rutgers, Stevens Institute of Technology, UMass-Amherst, SUNY Stony Brook, and Pittsburgh -- largely consists of public universities with strong ties to the Northeast.
 
@@
 The cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, University of Kansas, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities.
-While the federal government defines Nebraska and Kansas as part of the Midwest, Figure \@ref(fig:plot-1mode-u) suggests that the visit patterns of the University of Kansas and the University of Nebraska share more in common with Southern universities than they do with other universities in our sample.
-Finally, the largest and most centrally located cluster contains 13 universities, including Notre Dame, Northwestern, Tulane, CU-Boulder, UC-Berkeley.
-Compared to the overall sample, this group tends to be.
-This group largely consists of highly ranked universities, universities located in the Midwest or West, and Catholic universities.
+While the federal government defines Nebraska and Kansas as part of the Midwest, Figure \@ref(fig:plot-1mode-u) suggests that the visit patterns of the University of Nebraska and the University of Kansas share more in common with Southern universities than they do with other universities in our sample.
+Finally, the largest and most centrally located cluster contains 13 universities, including Notre Dame, Northwestern, Tulane, CU-Boulder, and UC-Berkeley.
+Compared to the overall sample, this group largely consists of highly ranked universities, universities located in the Midwest or West, and Catholic universities.
 
@@
 
-Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-pubu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?" Additionally, Appendix Figures \@ref(fig:enroll-pubu-privu) and \@ref(fig:enroll-pubu-privhs-pubhs) show the 12th grade enrollment size of visited high schools.
+Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-comp-privu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?" Additionally, Appendix Figures \@ref(fig:enroll-pubu-privu) and \@ref(fig:enroll-pubu-privhs-pubhs) show the 12th grade enrollment size of visited high schools.
 
@@
 Most public research universities in our sample visited a disproportionate number of private high schools in their home geographic region.
-UC-Berkeley and CU Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.
+UC-Berkeley and CU-Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.
 
@@
 
-Figures \@ref(fig:race-pubu-privhs-pubhs) and \@ref(fig:race-privu-privhs-pubhs) shows the percentage of 12th graders who identify as Black, Latinx, or Native at visited high schools.
+Figures \@ref(fig:race-pubu-privhs-pubhs) and \@ref(fig:race-privu-privhs-pubhs) show the percentage of 12th graders who identify as Black, Latinx, or Native at visited high schools.
 Consistent with @RN4504, most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups.
-The top row in the top panel of Figure \@ref(fig:race-pubu-privhs-pubhs) shows that the sum of Black, Latinx, and Native students comprise less than 20% of enrolled students in over over 65%<!--0.6632124--> of schools in private high school universe.
-At public high schools, Black/Latinx/Native students comprise less than 20% of enrolled students at less than 40% [CRYSTAL CHECK NUMBER] of all public schools.
-However, most public research universities and all selective private universities visited private high schools at a higher rate than public high schools, as seen earlier in Figures \@ref(fig:actual-proportional-pubu) and \@ref(fig:actual-proportional-privu).
+The top row in the top panel of Figure \@ref(fig:race-pubu-privhs-pubhs) shows that the sum of Black, Latinx, and Native students comprise less than 20% of enrolled students in over 65%<!--0.6632124--> of schools in our private high school universe.
+At public high schools (bottom panel), Black/Latinx/Native students comprise less than 20% of enrolled students at around 40%<!--0.4087567--> of all public schools.
+However, most public research universities and all selective private universities visited private high schools at a higher rate than public high schools<!--TODO: I'm not too sure how to interpret "higher rate than public high schools" - should it be higher rate than proportional rate?
+Related, is the last sentence supposed to be "disproportionate emphasis on visits to" PRIVATE instead of "public schools"?-->, as seen earlier in Figures \@ref(fig:actual-proportional-pubu) and \@ref(fig:actual-proportional-privu).
 Even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
@@
 Figure \@ref(fig:race-pubu-privhs-pubhs) focuses on public universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel).
-For all public universities, the racial composition of visited public schools contain a much higher share of Black/Latinx/Native students than the racial composition of visited private schools.
+For all public universities, the racial composition of visited public schools contains a much higher share of Black/Latinx/Native students than the racial composition of visited private schools.
 Figure \@ref(fig:race-pubu-privhs-pubhs) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
@@
 Visited private schools enrolled a much lower share of Black/Latinx/Native students than visited public schools.
-For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75% of visited private schools enrolled less than 20% Black/Latinx/Native students
-
-CRYSTAL -- ADD THE NEW FIGURES I REQUESTED HERE
-
-- FIGURES: racial composition of visited southern schools (separat figures for public universities and private universities; top panel is visited private schools; bottom panel is visited public schools; universe is southern schools)
+For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75% of visited private schools enrolled less than 20% Black/Latinx/Native students.
+
+INSERT FIGURES \@ref(fig:race-comp-pubu-privhs-pubhs) AND \@ref(fig:race-comp-privu-privhs-pubhs) ABOUT HERE
 
@@
 We observed substantial overlap and variation in recruiting networks of public universities.
-For example, the recruiting networks of the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass Amherst and Rutgers, which share substantial overlap with one another.
+For example, the recruiting networks of the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass-Amherst and Rutgers, which share substantial overlap with one another.
 Amongst the network of public and private universities, we observe substantial overlap and variation in recruiting networks.
@@
 
+\newpage
+
+```{r race-comp-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs.
+visited private high schools in the South, public research universities"}
+include_graphics(file.path(figures_dir, 'race_comp_pubu_privhs_pubhs.pdf'))
+```
+
+\newpage
+
+```{r race-comp-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs.
+visited private high schools in the South, selective private universities"}
+include_graphics(file.path(figures_dir, 'race_comp_privu_privhs_pubhs.pdf'))
+```
+
 \beginsupplement
@@
 
+```{r plot-2mode, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Two-mode network for private high schools and all visiting universities, colored by cluster"}
+include_graphics(file.path(figures_dir, 'plot_2mode_u.pdf'))
+```
+
+\newpage
+
 ```{r events-count-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
@@
 
-```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public institutions, colored by cluster"}
+```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public research universities, colored by cluster"}
 knitr::include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))
@@
 
-```{r plot-1mode-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for private universities, colored by cluster"}
+```{r plot-1mode-privu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for selective private universities, colored by cluster"}
 knitr::include_graphics(file.path(figures_dir, 'plot_1mode_privu.pdf'))

### 2023-12-13 r_r/tables_and_figures.Rmd
updates to manuscript

@@
 
+```{r plot-2mode, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Two-mode network for private high schools and all visiting universities, colored by cluster"}
+include_graphics(file.path(figures_dir, 'plot_2mode_all.pdf'))
+```
+
+\newpage
+
 ```{r events-count-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Number of visits by type and in-state vs. out-of-state, public research universities"}
@@
 
-```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public institutions, colored by cluster"}
+```{r plot-1mode-pubu, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "One-mode network for public research institutions, colored by cluster"}
 knitr::include_graphics(file.path(figures_dir, 'plot_1mode_pubu.pdf'))

### 2023-12-13 r_r/tables_and_figures.tex
revising intro, adding revised tables
updates to manuscript

@@
 ]{article}
-\author{}
-\date{\vspace{-2.5em}}
-
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math}
+  \usepackage{unicode-math} % this also loads fontspec
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else
+  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics[width=2\linewidth]{../assets/figures/race_comp_pubu_privhs_pubhs}
+
+}
+
+\caption{Racial composition of students at visited public high schools vs. visited private high schools in the South, public research universities}\label{fig:race-comp-pubu-privhs-pubhs}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+
+{\centering \includegraphics[width=2\linewidth]{../assets/figures/race_comp_privu_privhs_pubhs}
+
+}
+
+\caption{Racial composition of students at visited public high schools vs. visited private high schools in the South, selective private universities}\label{fig:race-comp-privu-privhs-pubhs}
+\end{figure}
+
 \beginsupplement
@@
 
+{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_2mode_all}
+
+}
+
+\caption{Two-mode network for private high schools and all visiting universities, colored by cluster}\label{fig:plot-2mode}
+\end{figure}
+
+\newpage
+
+\begin{figure}
+
 {\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_pubu}
@@
 
-\caption{One-mode network for public institutions, colored by cluster}\label{fig:plot-1mode-pubu}
+\caption{One-mode network for public research institutions, colored by cluster}\label{fig:plot-1mode-pubu}
 \end{figure}
@@
 
-\caption{One-mode network for private universities, colored by cluster}\label{fig:plot-1mode-privu}
+\caption{One-mode network for selective private universities, colored by cluster}\label{fig:plot-1mode-privu}
 \end{figure}

### 2023-12-13 scripts/create_tables_figures.R

@@ -63,6 +63,7 @@ ego_df <- readRDS(file.path(tables_dir, 'table_ego_all.RDS')) %>%
   )
 
 color_palette <- c('#d1b38e', '#8eb9d1', '#b48ed1', '#afd18e')
+color_palette_2 <- c('#98abc5', '#8a89a6', '#7b6888', '#6b486b', '#a05d56', '#d0743c', '#ff8c00')
 
 
 ## -------------------
@@ -663,3 +664,129 @@ dev.off()
 # par(mar = c(0, 0, 0, 0) + 0.1, mai = c(0, 0, 0, 0))
 # grid.arrange(a, b, c, nrow = 3, ncol = 1)
 # dev.off()
+
+
+## --------------------------------------------------------
+## RACIAL COMPOSITION OF VISITED HIGH SCHOOLS IN THE SOUTH
+## --------------------------------------------------------
+
+southern_states <- c('AL', 'AR', 'DC', 'DE', 'FL', 'GA', 'KY', 'LA', 'MD', 'MS', 'NC', 'OK', 'SC', 'TN', 'TX', 'VA', 'WV')
+
+southern_pubhs <- pubhs_universe_df %>% 
+  filter(state_code %in% southern_states) %>% 
+  select(ncessch, g12, pct_white, pct_black, pct_hispanic, pct_asian, pct_amerindian, pct_nativehawaii, pct_tworaces) %>% 
+  mutate(
+    cnt_white = pct_white / 100 * g12,
+    cnt_black = pct_black / 100 * g12,
+    cnt_hispanic = pct_hispanic / 100 * g12,
+    cnt_asian = pct_asian / 100 * g12,
+    cnt_amerindian = pct_amerindian / 100 * g12,
+    cnt_nativehawaii = pct_nativehawaii / 100 * g12,
+    cnt_tworaces = pct_tworaces / 100 * g12
+  )
+
+southern_privhs <- privhs_universe_df %>% 
+  filter(state_code %in% southern_states) %>% 
+  select(school_id, enroll, pct_white, pct_black, pct_hispanic, pct_asian, pct_amerindian, pct_nativehawaii, pct_tworaces) %>% 
+  mutate(
+    cnt_white = pct_white / 100 * enroll,
+    cnt_black = pct_black / 100 * enroll,
+    cnt_hispanic = pct_hispanic / 100 * enroll,
+    cnt_asian = pct_asian / 100 * enroll,
[…]

### 2023-12-13 scripts/network_recruiting_analysis.R

@@ -92,9 +92,9 @@ enroll_title <- '12th grade enrollment'
   # mar: margin in lines (default: c(0, 0, 0, 0))
   # mai: margin in inches (default: c(0, 0, 0, 0))
 
-save_plot <- function(graph_object, plot_name, paper = 'a4r', mar = c(0, 0, 0, 0), mai = c(0, 0, 0, 0)) {
+save_plot <- function(graph_object, plot_name, paper = 'a4r', mar = c(0, 0, 0, 0), mai = c(0, 0, 0, 0), w = 1600, h = 1200) {
   
-  pdf(str_c('./assets/figures/', plot_name), paper = paper, width = 1600, height = 1200)
+  pdf(str_c('./assets/figures/', plot_name), paper = paper, w = 1600, h = 1200)
   par(mfrow = c(1, 1))
   par(mar = mar + 0.1, mai = mai)
   
@@ -426,6 +426,8 @@ plot_2mode_graph <- function(twomode_network, c_analysis, k = NULL, h = NULL, no
   plot(
     x = twomode_network, 
     vertex.label = if_else(V(twomode_network)$type, V(twomode_network)$school_name, ''),
+    vertex.label.cex = 0.6,
+    vertex.label.color = adjustcolor('black', 0.8),
     vertex.color = vertex_color,
     vertex.frame.color = 'lightgray',
     vertex.shape = 'circle',
@@ -470,7 +472,10 @@ plot_2mode_graph(g_2mode_pubu, c_analysis = 'fast', steps = 11, colors = c('red'
 # save_plot(plot_1mode_graph(g_2mode_u, mode = 'psi', c_analysis = 'hclust', k = 5, colors = c('lightblue', 'green', 'violet', 'yellow','coral')),
 #           plot_name = 'plot_1mode_u_k5.pdf')
 
-# Region characteristic
+save_plot(plot_2mode_graph(g_2mode_u, c_analysis = 'hclust', k = 4, margin = -0.6),
+          plot_name = 'plot_2mode_u.pdf')
+
+ # Region characteristic
 # save_plot(plot_2mode_graph(g_2mode, c_analysis = 'region', values = region_values, keys = region_keys, margin = -0.6),
 #           plot_name = 'plot_2mode_all_region.pdf')
 
@@ -487,10 +492,10 @@ plot_2mode_graph(g_2mode_pubu, c_analysis = 'fast', steps = 11, colors = c('red'
[…]

### 2023-12-15 r_r/letter_to_reviewers.Rmd
updates to manuscript

@@
 
-# Big Changes to the Manuscript.
+# Big Changes to the Manuscript
 
@@
 We sought to develop a revised manuscript that addressed all of these concerns.
-We concluded that targeted changes to particular parts of the front-end might address some but not all of these concerns.
+We concluded that targeted changes to particular parts of the front end might address some but not all of these concerns.
 Therefore, we decided to completely destroy the original front end and create a new one.
@@
 They write that "One hook involves using a provocative quotation or vignette to engage the reader in the intriguing and practical nature of their topic" (p.
-XX).
-Our revised introduction begins with a vignette describing off-campus recruiting visits to Harpeth Hall, a predominantly white "non-sectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee" (p.
-X).
+873)<!--https://journals.aom.org/doi/epdf/10.5465/amj.2011.4000-->.
+Our revised introduction begins with a vignette describing off-campus recruiting visits to Harpeth Hall, a predominantly white "nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee" (p.
+1).
 The vignette then moves to the nearby University School of Nashville, which is highly ranked nationally, and receives visits from the more elite private colleges and universities in our sample, but few public universities in our sample.
-Finally, nearby Father Ryan High School and Christ Presbyterian Academy are lower ranked, are overwhelmingly white and receive visits from few selective private universities in our sample but do receive visits from a substantial share of public research universities in our sample.
+Finally, nearby Father Ryan High School and Christ Presbyterian Academy are lower ranked, overwhelmingly white, and receive visits from few selective private universities in our sample but do receive visits from a substantial share of public research universities in our sample.
 This introduction relies on data collected for the study, previews some of the core findings, and we hope it "engage(s) the reader in the intriguing and practical nature of the topic" as @RN3515 say.
@@
 The revised literature review hopefully sets up a scholarly contribution while also doing a better job of describing the practical motivation for visits to private high schools by public universities.
-Following @RN3515, our literature review takes the approach of "entering two different conversations and bridging them" with the goal of making a contribution to each conversations while also showing that these two disparate conversations are both parts of a larger story.
+Following @RN3515, our literature review takes the approach of "entering two different conversations and bridging them" (p.
+874) with the goal of making a contribution to each conversation while also showing that these two disparate conversations are both parts of a larger story.
 We first review scholarship on nonresident enrollment by public research universities.
@@
 
-Second, we review scholarship on linkages between private schools and private universities, we show that prior literature finds a strong relationship between private school attendance and college access and college selectivity.
+Second, we review scholarship on linkages between private schools and private universities.
+We show that prior literature finds a strong relationship between private school attendance and college access and college selectivity.
 We also present descriptive statistics, which show a strong relationship between private school attendance and attending a selective private college or university.
@@
 
-We develop a "bridging" scholarly contribution by stating the these two literatures have been isolated from one another, but they are both parts of a broader story about the changing nature of school segregation and the competition for affluent students.
+We develop a "bridging" scholarly contribution by stating that these two literatures have been isolated from one another, but they are both parts of a broader story about the changing nature of school segregation and the competition for affluent students.
 As public universities seek affluent out-of-state students, they are attracted to out-of-state private schools.
@@
 "Thus, in recruiting from private schools, universities may be targeting student bodies that are more affluent and racially homogeneous than public schools.
-We investigate the characteristics – including geographic region and racial composition – of private schools being targeted by university admissions officers because these characteristics have downstream implications for the racial composition of university campuses."
+We investigate the characteristics -- including geographic region and racial composition -- of private schools being targeted by university admissions officers because these characteristics have downstream implications for the racial composition of university campuses" (p.
+12).
 
@@
 The original manuscript focused on whether public research universities behave like selective private universities.
-Here, comparison is central.
-The revised manuscript is based on the idea both public research universities and selective private universities are targeting the same (or similar) sets of predominantly affluent households.
+There, comparison is central.
+The revised manuscript is based on the idea that both public research universities and selective private universities are targeting the same (or similar) sets of predominantly affluent households.
 Although comparison remains important, the fundamental interest now becomes developing insights about the competition for students who attend private schools and which schools the universities in our sample are targeting.
@@
 
-**Author response**: We wholeheartedly agree with these concern by Reviewer 2 and we are grateful to Reviewer 2 for raising these issues!
+**Author response**: We wholeheartedly agree with these concerns by Reviewer 2 and we are grateful to Reviewer 2 for raising these issues!
 As discussed above, the revised manuscript addresses these concerns about the practical benefits of recruiting students from private schools.
@@
 
-**Author response**: We agree with his concern.
+**Author response**: We agree with this concern.
 The revised manuscript removes the idea that the mission of public universities is social mobility.
@@
 private universities was simultaneously simplistic and distracting.
-The revised manuscript focuses motivates the analysis based on the more practical idea that universities target private schools because these schools tend to enroll affluent students, who have greater ability to pay high tuition prices without substantial need-based aid.
+The revised manuscript motivates the analysis based on the more practical idea that universities target private schools because these schools tend to enroll affluent students, who have greater ability to pay high tuition prices without substantial need-based aid.
 
@@
 Similarly, I find myself craving some context around the broader implications for this study in the introduction.
-I think you start to get to this in your conversation around social reproduction, but it would help draw the reader in if you could lay out what the findings of this study could mean for policy and practice.]
+I think you start to get to this in your conversation around social reproduction, but it would help draw the reader in if you could lay out what the findings of this study could mean for policy and practice.
 
@@
 > **Reviewer concern**.
-"The "Chetty" data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile (Burd, 2017; Chetty, Friedman, Saez, Turner, & Yagan, 2020)." P.
+"The 'Chetty' data on parental income by college show that the overwhelming majority of students at selective private institutions have parental income in the top quintile (Burd, 2017; Chetty, Friedman, Saez, Turner, & Yagan, 2020)." P.
 3 Instead of saying "Chetty" data, can you be more descriptive here?
@@
 
-## Section 2 [background and lit review]
+## Section 2 (background and lit review)
 
@@
 
-**Author response**: The original manuscript had a level-1 section entitled "What do we know about off-campus recruiting?", which reviews market research about off-campus recruiting and published scholarship By contrast, the revised manuscript has a broader literature review section that reviews scholarshp from two literatures -- (1) nonresident enrollment by public universities and (2) linkages between private schools and private universities -- and bridges these two literatures.
+**Author response**: The original manuscript had a level-1 section entitled "What do we know about off-campus recruiting?", which reviews market research about off-campus recruiting and published scholarship.
+By contrast, the revised manuscript has a broader literature review section that reviews scholarship from two literatures -- (1) nonresident enrollment by public universities and (2) linkages between private schools and private universities -- and bridges these two literatures.
 Therefore, this recommendation from Reviewer 2 is less relevant to the revised literature review structure.
@@
 We put this text in the discussion section rather than the literature review because it complements text about recommendations for practice and this text fits less well with the revised literature review structure.
-Here is the revised text that we placed at the beginning of the "implications for practice" sub-section of the Discussion section.
+Here is the revised text that we placed at the beginning of the "Implications for Practice" sub-section of the Discussion section:
 
 > Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the Covid pandemic.
-@RN4664 found that "travel" was the top-ranked top-ranked marketing/recruiting expenditure item for both public universities and private universities.
+@RN4664 found that "travel" was the top-ranked marketing/recruiting expenditure item for both public universities and private universities.
 During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events [@parents_covid_rnl].
 Admissions counselors are now traveling again.
-@RN4896 found that travel was the fifth ranked expenditure item for public universities and the second ranked expenditure item for private universities.
-When asked about areas of future expenditure growth, travel was the top ranked item for public universities and the second ranked item for private universities [@RN4896], suggesting that universities are increasing travel following the decline of the pandemic.
+@RN4896 found that travel was the fifth-ranked expenditure item for public universities and the second-ranked expenditure item for private universities.
+When asked about areas of future expenditure growth, travel was the top-ranked item for public universities and the second-ranked item for private universities [@RN4896], suggesting that universities are increasing travel following the decline of the pandemic.
 
-> The @eab_nacac_counselor_2023 survey of high school counselors asked "how do you prefer to receive information from colleges?" High school visits by college representatives was by far the highest rated "channel" for private school counselors and was also the highest rated channel for public school counselors.
+> The @eab_nacac_counselor_2023 survey of high school counselors asked, "How do you prefer to receive information from colleges?" High school visits by college representatives was by far the highest rated "channel" for private school counselors and was also the highest rated channel for public school counselors.
 By contrast, virtual visits by admissions representatives received low ratings by high school guidance counselors.
@@
 What insights do we glean from these market research findings?
-In the era of mass marketing and data science, the pursuit of traditional college students from privileged schools and communities is still a hand-to-hand business and off-campus recruiting visits remain a vital means of recruiting these students.
+In the era of mass marketing and data science, the pursuit of traditional college students from privileged schools and communities is still a hand-to-hand business, and off-campus recruiting visits remain a vital means of recruiting these students.
 
@@
 However, we made the decision to exclude most of these because the manuscript is already quite long.
-The revised manuscript does include a visualization of the full two-mode recruiting network between universities and high schools (CRYSTAL STATE FIGURE NUMBER ONCE YOU ADD IT).
-The manuscript also includes a visualization of the ego network of University of Notre Dame (Figure 1), which is useful in explaining what are ego networks and their relationship with RQ3 (characteristics of high schools that reveive visits)
+The revised manuscript does include a visualization of the full two-mode recruiting network between universities and high schools (Appendix Figure 1).
+The manuscript also includes a visualization of the ego network of University of Notre Dame (Figure 1), which is useful in explaining what are ego networks and their relationship with RQ3 (characteristics of high schools that receive visits).
 
@@
 
-The reason the neighboring state analysis doesn't quite work is exemplified by the University of Nebraska Lincoln (UNL).
+The reason the neighboring state analysis doesn't quite work is exemplified by the University of Nebraska-Lincoln (UNL).
 Nebraska does not share a border with Illinois but a huge proportion of their high school recruiting visits -- public and private -- are in Chicago.
 The same is true for the University of Arkanas and visits to Georgia (Atlanta), CU-Boulder and California and CU-Boulder and Chicago, and UC-Berkeley and visits to Washington (Seattle).
-To a huge degree, recruiting visits occur in major metropolitan areas, so the analysis you recommend bears fruit for universities in states that neighbor a state with a major metopolitan area (e.g., University of Alabama and Georgia, or University of Pittsburgh and New York).
+To a huge degree, recruiting visits occur in major metropolitan areas, so the analysis you recommend bears fruit for universities in states that neighbor a state with a major metropolitan area (e.g., University of Alabama and Georgia, or University of Pittsburgh and New York).
 
 We considered an alternative to your analysis that focuses on visits to metropolitan areas within some distance (e.g., 500 miles) from the University.
-But this analysis is also not clean because distances seem to be greater in the West (e.g., Denver to Los Angeles) than the east coast (e.g., Amherst MA to NYC).
+But this analysis is also not clean because distances seem to be greater in the West (e.g., Denver to Los Angeles) than the East Coast (e.g., Amherst MA to NYC).
 For these reasons, we opted to exclude those analyses even though we do agree with the basic logic the Reviewer lays out.
@@
 
-**Author response**: The revised Data and Sample section states that "The rationale for different criteria for inclusion across different university types is because these criteria reflected the interests of a foundation that funded the data collection." We agree with Reviewer 1 that making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities.
+**Author response**: The revised Data and Sample section states that "The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection." We agree with Reviewer 1<!--TODO: Is this comment by Reviewer 1 or 2?
+This is under the level-1 section "Response to Reviewer 2"--> that making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities.
 The revised manuscript now includes a Limitations subsection that describes this limitation and its consequences.
@@
 
-**Author response**: This is an excellent suggestion by Reviewer 1. The new Limitations section in the revised manuscript discusses the drawbacks of a convenience sample.
+**Author response**: This is an excellent suggestion by Reviewer 1<!--TODO: Is this comment by Reviewer 1 or 2?
+This is under the level-1 section "Response to Reviewer 2"-->.
+The new Limitations section in the revised manuscript discusses the drawbacks of a convenience sample.
 
@@
 **Author response**: We added text to the Data and Sample section to address this concern.
-For public research universities, we double checked with the admissions offices and issued formal public records requests if the university did not provide data.
+For public research universities, we double-checked with the admissions offices and issued formal public records requests if the university did not provide data.
 
@@
 
-**Author response**: The revised manuscript now states that we used Python to scrape admissions websites [CRYSTAL -- ADD WHICH PACKAGES WE USED].
+**Author response**: The revised manuscript now states that we used Python to scrape admissions websites using the *requests* library.
 Additionally, in case this is helpful to readers, the revised manuscript states that all analyses were conducted using *R* and network analyses were conducted using the *igraph* package.
@@
 
-The results are well-organized and clear
+> **Reviewer comment**. The results are well-organized and clear
 
@@
 
-**Author response**: We agree with Reviewer 2 implied concern here that just because the privatization research did not address this topic, it is not clear that conducting this analysis makes a significant scholarly contribution because the privatization literature is less relevant than it was 10 years ago.
+**Author response**: We agree with Reviewer 2's implied concern here that just because the privatization research did not address this topic, it is not clear that conducting this analysis makes a significant scholarly contribution because the privatization literature is less relevant than it was 10 years ago.
 
@@
 
-In the "implications for scholarship" sub-section of the revised Discussion section, we discuss the contribution of this manuscript to the two respective literatures.
-Next, we argue that our broader/more important contribution is showing that these literatures are part of the same story and developing new insights about the competition privileged students.
+In the "Implications for Scholarship" sub-section of the revised Discussion section, we discuss the contribution of this manuscript to the two respective literatures.
+Next, we argue that our broader/more important contribution is showing that these literatures are part of the same story and developing new insights about the competition for privileged students.
 Here, I paste text from the revised manuscript:
@@
 
-> Our analyses shed light about the nature of this competition.
+> Our analyses shed light on the nature of this competition.
 When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
 Several public universities seem to be competing directly for students targeted by a particular private university.
-For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory (Figure \@ref(tab:privu-percent-visited-by-pubu-matrix)).
+For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory (Table 5).
 We reason UC-Berkeley is competing directly for students because all four universities are in the same broad echelon of prestige.
@@
 
-> However, public universities that made the greatest number of private school visits seemed to be targeting lower-achieving students at private schools targeted by particular private universities.
+> However, public universities that made the greatest number of private school visits seemed to be targeting the lower-achieving students at private schools targeted by particular private universities.
 For example, the University of Alabama visited 52.2% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools.
 Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame.
-Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievement, and want to attend a football powerhouse.
+Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievements, and want to attend a football powerhouse.
 Additionally, CU-Boulder visited 42.4% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
@@
 
-**Author response**: As stated previously, the revised manuscript discusses implications for student enrollment composition and university administrators (which we might think of senior administrators, high-level enrollment management administrators).
+**Author response**: As stated previously, the revised manuscript discusses implications for student enrollment composition and university administrators (which we might think of as senior administrators, high-level enrollment management administrators).
 We do not state implications that are explicitly for lower-level admissions professionals.
 Page limits were a consideration here.
-Additionally, based on our prior conversations with enrollment managers and admissions officers we believe that junior admissions professionals have limited discretion over which schools a university visits.
+Additionally, based on our prior conversations with enrollment managers and admissions officers, we believe that junior admissions professionals have limited discretion over which schools a university visits.
 However, if the Reviewer is adamant that the manuscript should be further revised to address implications for a particular group, we will gladly take this on in a subsequent revision.
@@
 This change reduces redundancy in text, helps to reduce word count, and results in a structure that we hope is easier for readers to digest.
-The revised organization of the level-1 Methods section is as follows: Data and sample; Constructing social networks; Analyses (which are described separately by research question)
+The revised organization of the level-1 Methods section is as follows: Data and Sample; Constructing Social Networks; Analyses (which are described separately by research question).
 
@@
 However, these results don't actually show how the recruiting strategies differ across/within public and private universities in terms of what sorts of private schools they visit.
-This limitation is one reason that we chose to switch the order of RQ2 and RQ3.
+This limitation is one reason why we chose to switch the order of RQ2 and RQ3.
 In the revised manuscript, we show the analyses of network similarity and then we examine -- separately for each university -- the characteristics of private schools that receive visits.
 We hope this change helps address the concern.
-We considered subsequent analyses that would examine the characteristics of private schools that received visits from one set of universities but not another set of universities (e.g., schools visited by Midwestern private universities but not Midwestern puboic universities).
+We considered subsequent analyses that would examine the characteristics of private schools that received visits from one set of universities but not another set of universities (e.g., schools visited by Midwestern private universities but not Midwestern pubic universities).
 There are many potential analyses that could be conducted here, and the choice of which analyses to include felt somewhat arbitrary.
 Therefore, we decided to exclude such analyses.
-Since comparison between public and private universities is less of a focus than the initial manuscript, we hope this omisssion is ok.
+Since comparison between public and private universities is less of a focus than the initial manuscript, we hope this omission is okay.
 
@@
 We did this for both visits to private schools and visits to public schools.
-Our rationale for this comparison is that Universities in our sample tended to visit private schools in the South more than private schools in other regions (often this was true even for universities not located in the South).
+Our rationale for this comparison is that universities in our sample tended to visit private schools in the South more than private schools in other regions (often this was true even for universities not located in the South).
 Additionally, over the last two decades, private school enrollment growth has been strongest in the South and scholars have argued that "white flight" from desegregated public schools is one reason for this enrollment growth [@RN4504].
@@
 **Author response**: As stated above, we agree with the concern that our analysis sample is a convenience sample.
-The revised limitations section states this explicitly and discusses why this limitation undermines the external validity of our findings.
+The revised Limitations section states this explicitly and discusses why this limitation undermines the external validity of our findings.
 We agree with Reviewer 1 that because we do not have longitudinal data, we cannot make strong claims about which university is mimicking which other university.
-We added this limitation to the Limitations section
+We added this limitation to the Limitations section.
 
@@
 
-> Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), Public research universities began substantially increasing nonresident enrollment en masse around 2005 [@RN3753].
+> Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), public research universities began substantially increasing nonresident enrollment en masse around 2005 [@RN3753].
 By contrast, selective private universities have long relied on enrollment from private schools [@RN3519; @RN4640].
-Therefore, the pursuit of out-of-state private school students by public research universities is relatively recent  encroachment on the historic territory of selective private universities and in-state flagships.
+Therefore, the pursuit of out-of-state private school students by public research universities is a relatively recent encroachment on the historic territory of selective private universities and in-state flagships.
+
+# References

### 2023-12-15 r_r/manuscript_rihe_r_r.Rmd
updates to manuscript

@@
 
-# Data and sample
+## Data and Sample
 
@@
 The data collection sample for the broader project consisted of: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), all private universities in the top 100 of U.S.
-News and World Report National Universities rankings (N=58), and all private colleges in the top 50 of U.S.
-News and World Report Liberal Arts Colleges rankings (N=47).<!--TODO: Confirm N's--> The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection.
+News and World Report National Universities rankings (N=57), and all private colleges in the top 50 of U.S.
+News and World Report Liberal Arts Colleges rankings (N=47).
+The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection.
 This article excludes private liberal arts colleges because having a third institutional type would substantially increase article length.
@@
 First, our data collection sample consisted of public research-extensive universities as defined by the 2000 Carnegie Classification (N=102) and all private universities in the top 100 of U.S.
-News and World Report National Universities rankings (N=58).
+News and World Report National Universities rankings (N=57).
 Making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities.
@@
 
-INSERT FIGURES \@ref(fig:race-comp-pubu-privhs-pubhs) AND \@ref(fig:race-comp-privu-privhs-pubhs) ABOUT HERE
+<!--TODO: Supplemental figures \@ref(fig:race-comp-pubu-privhs-pubhs) AND \@ref(fig:race-comp-privu-privhs-pubhs) are now moved to appenidix-->
 
@@
 For most public research universities in our sample, the scale and relative scale -- as a percentage of all HS visits -- of visits to private high schools were smaller than that of most selective private universities.
-However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \@ref(fig:actual-proportional-pubu)) and that vast majority of these private school visits were to out-of-state private schools.
+However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \@ref(fig:actual-proportional-pubu)) and the vast majority of these private school visits were to out-of-state private schools.
 Additionally, several public research universities -- University of Alabama, CU-Boulder, University of South Carolina -- visited private high schools at a scale that exceeded most private universities.
@@
 Research question 2 asks about overlap in the private school recruiting networks of public and private universities.
-We observed substantial overlap and variation in recruiting networks of public universities.
+We observed substantial overlap and variation in the recruiting networks of public universities.
 For example, the recruiting networks of the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass-Amherst and Rutgers, which share substantial overlap with one another.
@@
 
-With the exception of UC-Berkeley and UC-San Diego, the academic rating of private schools visited by public universities was lower than the rating of those visited by most private universities.
-This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked as a top 100 National University by U.S.
+With the exception of UC-Berkeley and UC-San Diego, the average academic rating of private schools visited by public universities was lower than the rating of those visited by most private universities.
+This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked in the top 100 National University by U.S.
 News.
@@
 By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.
-[ADD A SENTENCE ABOUT RACIAL COMPOSITION OF VISITS TO SOUTH?]
+<!--TODO: [ADD A SENTENCE ABOUT RACIAL COMPOSITION OF VISITS TO SOUTH?]-->
 
@@
 Using nearly the same sample of 15 public research universities used in this study, @RN4758 found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools.
-Public research universities have a financial incentive to target private school students, who tend to come from affluent households able to pay nonresident tuition price without need-based aid.
+Public research universities have a financial incentive to target private school students, who tend to come from affluent households that are able to pay nonresident tuition price without need-based aid.
 This study extends the literature on nonresident students by analyzing the scale of visits to private schools, the overlap and divergence in recruiting networks between public and private universities, and the characteristics of visited private schools.
@@
 Private school students comprise a disproportionate share of enrollment at selective private universities (Author calculations based on HSLS:2009).
-Practically, these linkages exist because private schools want to send their students to "good" universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profile and/or extracurricular activities [@RN3519].
+Practically, these linkages exist because private schools want to send their students to "good" universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profiles and/or extracurricular activities [@RN3519].
 Prior research has often focused on linkages between elite private schools and elite universities [@RN4407; @RN4935; @RN4640].
-Whereas elite universities (e.g., Princeton, Stanford) experience strong student demand based on reputation, merely-selective private universities must incite demand by expending resources on recruiting.
+Whereas elite universities (e.g., Princeton, Stanford) experience strong student demand based on reputation, merely selective private universities must incite demand by expending resources on recruiting.
 Prior research has not systematically analyzed connections between private schools and private universities that are selective, but not elite.
@@
 
-Our analyses shed light about the nature of this competition.
+Our analyses shed light on the nature of this competition.
 When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
 Several public universities seem to be competing directly for students targeted by a particular private university.
-For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory (Figure \@ref(tab:privu-percent-visited-by-pubu-matrix)).
+For example, UC-Berkeley visited 27.9% of the schools visited by Northwestern, 28.9% of the schools visited by Tufts, and 27.8% of the schools visited by Emory (Table \@ref(tab:privu-percent-visited-by-pubu-matrix)).
 We reason UC-Berkeley is competing directly for students because all four universities are in the same broad echelon of prestige.
@@
 
-However, public universities that made the greatest number of private school visits seemed to be targeting lower-achieving students at private schools targeted by particular private universities.
+However, public universities that made the greatest number of private school visits seemed to be targeting the lower-achieving students at private schools targeted by particular private universities.
 For example, the University of Alabama visited 52.2% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools.
 Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame.
-Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievement, and want to attend a football powerhouse.
+Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievements, and want to attend a football powerhouse.
 Additionally, CU-Boulder visited 42.4% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
@@
 Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the Covid pandemic.
-@RN4664 found that "travel" was the top-ranked top-ranked marketing/recruiting expenditure item for both public universities and private universities.
+@RN4664 found that "travel" was the top-ranked marketing/recruiting expenditure item for both public universities and private universities.
 During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events [@parents_covid_rnl].
 Admissions counselors are now traveling again.
-@RN4896 found that travel was the fifth ranked expenditure item for public universities and the second ranked expenditure item for private universities.
-When asked about areas of future expenditure growth, travel was the top ranked item for public universities and the second ranked item for private universities [@RN4896], suggesting that universities are increasing travel following the decline of the pandemic.
-
-The @eab_nacac_counselor_2023 survey of high school counselors asked "how do you prefer to receive information from colleges?" High school visits by college representatives was by far the highest rated "channel" for private school counselors and was also the highest rated channel for public school counselors.
+@RN4896 found that travel was the fifth-ranked expenditure item for public universities and the second-ranked expenditure item for private universities.
+When asked about areas of future expenditure growth, travel was the top-ranked item for public universities and the second-ranked item for private universities [@RN4896], suggesting that universities are increasing travel following the decline of the pandemic.
+
+The @eab_nacac_counselor_2023 survey of high school counselors asked, "How do you prefer to receive information from colleges?" High school visits by college representatives was by far the highest rated "channel" for private school counselors and was also the highest rated channel for public school counselors.
 By contrast, virtual visits by admissions representatives received low ratings by high school guidance counselors.
@@
 Prior scholarly and market research shows that students are sensitive to recruiting interventions, including recruiting visits [@RN4324; @RN4402].
-Consequently, racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university.
-Our research on visits to public high schools [@RN4758] and this study on visits to private schools finds that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
+Consequently, the racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university.
+Our research on visits to public high schools [@RN4758] and this study on visits to private schools find that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
 Some universities may publicly proclaim a commitment to social mobility and privately pursue an intentional recruiting strategy that targets affluent schools and communities.
@@
 Therefore, universities may visit predominantly white private high schools in search of non-white students.
-One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored
-
-In the aftermath of the Supreme Court decision on race conscious admissions, @RN4954 published a report titled *Strategies for Increasing Diversity and Opportunity in Higher Education.*  The report recommended that universities diversify the set of high schools they recruit from:
+One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.
+
+In the aftermath of the Supreme Court decision on race-conscious admissions, @RN4954 published a report titled *Strategies for Increasing Diversity and Opportunity in Higher Education.*  The report recommended that universities diversify the set of high schools they recruit from:
 
 >> Rather than recruiting primarily from private and public high schools composed of predominantly high-income students, institutions can expand and prioritize their outreach to high schools with substantial populations of low-income students and students of color.
-As part of expanding outreach, institutions can assign admissions recruiters to high schools from which they have not typically recruited to provide equal opportunity for all students
+As part of expanding outreach, institutions can assign admissions recruiters to high schools from which they have not typically recruited to provide equal opportunity for all students.
 
@@
 
-kable(univ_sample, caption = "Characteristics of universities in analysis sample", booktabs = T, escape = F, align = 'c') %>%
+kable(univ_sample, caption = "Characteristics of universities in analysis sample", booktabs = T, escape = F, align = c('l', 'l', rep('r', 13))) %>%
   collapse_rows(columns = 1, latex_hline = 'major', valign = 'middle') %>%
@@
   column_spec(c(9, 15), width = '3cm', latex_valign = 'm') %>% 
+  # row_spec(0, align = 'c') %>%
   kable_styling(font_size = 13, latex_options = c('scale_down', 'hold_position'))
@@
 # 49 public research
-pop_pubu <- c('151351', '171100', '180461', '188030', '199193', '147703', '204857', '207388', '214777', '186380', '149222', '196088', '196097', '204796', '100751', '197036', '164155', '104179', '106397', '110635', '110644', '110653', '110662', '110671', '110680', '201885', '126614', '129020', '139959', '141574', '225511', '142285', '155317', '161253', '163286', '166629', '170976', '181464', '187985', '199120', '215293', '217484', '218663', '230764', '234076', '236948', '230728', '234030', '172644')
+# pop_pubu <- c('151351', '171100', '180461', '188030', '199193', '147703', '204857', '207388', '214777', '186380', '149222', '196088', '196097', '204796', '100751', '197036', '164155', '104179', '106397', '110635', '110644', '110653', '110662', '110671', '110680', '201885', '126614', '129020', '139959', '141574', '225511', '142285', '155317', '161253', '163286', '166629', '170976', '181464', '187985', '199120', '215293', '217484', '218663', '230764', '234076', '236948', '230728', '234030', '172644')
 
 # 49 private national
-pop_privu <- c('194824', '139658', '190150', '223232', '212054', '193900', '166027', '144050', '130794', '243744', '166683', '198419', '215062', '162928', '182670', '110404', '147767', '217156', '190415', '227757', '152080', '186131', '221999', '131496', '164988', '160755', '213543', '135726', '216597', '228246', '191241', '186867', '131159', '228875', '239105', '127060', '122436', '207971', '179159', '168148', '164924', '195030', '179867', '201645', '197708', '199847', '211440', '121150', '123961')
+# pop_privu <- c('194824', '139658', '190150', '223232', '212054', '193900', '166027', '144050', '130794', '243744', '166683', '198419', '215062', '162928', '182670', '110404', '147767', '217156', '190415', '227757', '152080', '186131', '221999', '131496', '164988', '160755', '213543', '135726', '216597', '228246', '191241', '186867', '131159', '228875', '239105', '127060', '122436', '207971', '179159', '168148', '164924', '195030', '179867', '201645', '197708', '199847', '211440', '121150', '123961')
+
+library(readxl)
+cc2000_edition_data <- read_excel(file.path(data_dir, 'cc2000_edition_data.xls'), sheet = 'Data')
+pop_pubu <- (cc2000_edition_data %>% filter(`Control (text)` == 'Public', `CC2000 (text)` == 'Doctoral/Research Universities—Extensive'))$UNITID %>% as.character()
+
+usnews_rankings <- read_csv(file.path(data_dir, 'usnews_rankings.csv'), col_select = c('source', 'control', 'rank', 'univ_id'))
+pop_privu <- (usnews_rankings %>% filter(source == 'national-universities', control == 'private', rank <= 100))$univ_id %>% as.character()
 
@@
 
-kable(univ_pop_df, caption = "Characteristics of universities in analysis sample compared to data collection sample", booktabs = T, escape = F, align = 'c', linesep = '') %>%
-  add_header_above(header = c(' ' = 1, 'Analysis sample (N=15)' = 3, 'Data collection sample (N=49)' = 3, 'Analysis sample (N=14)' = 3, 'Data collection sample (N=49)' = 3)) %>%
+kable(univ_pop_df, caption = "Characteristics of universities in analysis sample compared to data collection sample", booktabs = T, escape = F, align = 'r', linesep = '') %>%
+  add_header_above(header = c(' ' = 1, 'Analysis sample (N=15)' = 3, 'Data collection sample (N=102)' = 3, 'Analysis sample (N=14)' = 3, 'Data collection sample (N=57)' = 3)) %>%
   add_header_above(header = c(' ' = 1, 'Public research universities' = 6, 'Selective private universities' = 6)) %>%
@@
 
-kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix', booktabs = T, align = 'c', linesep = '') %>%
+kable(table_1mode_pubu$onemode_pct_df, caption = 'One-mode public university percent matrix', booktabs = T, align = 'r', linesep = '') %>%
   column_spec(c(7, 9, 15), width = '5em') %>%
@@
   column_spec(c(14), width = '8.8em') %>%
+  row_spec(0, align = 'c') %>% 
   kable_styling(font_size = 13, latex_options = 'scale_down') 
@@
 
-kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix', booktabs = T, align = 'c', linesep = '') %>%
+kable(table_1mode_privu$onemode_pct_df, caption = 'One-mode private university percent matrix', booktabs = T, align = 'r', linesep = '') %>%
   column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
@@
   column_spec(14:15, width = '8.5em') %>%
+  row_spec(0, align = 'c') %>% 
   kable_styling(font_size = 13, latex_options = 'scale_down') 
@@
 
-kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities', booktabs = T, align = 'c', linesep = '') %>%
+kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], caption = 'For private universities, the percent of high schools visited by public universities', booktabs = T, align = 'r', linesep = '') %>%
   column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
@@
   column_spec(14:15, width = '8.5em') %>%
+  row_spec(0, align = 'c') %>% 
   kable_styling(font_size = 13, latex_options = 'scale_down')
@@
 
-kable(table_1mode_u$onemode_pct_df[c(2,3,4,5,6,8,10,11,12,14,15,19,20,26),c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29)], caption = 'For public universities, the percent of high schools visited by private universities', booktabs = T, align = 'c', linesep = '') %>%
+kable(table_1mode_u$onemode_pct_df[c(2,3,4,5,6,8,10,11,12,14,15,19,20,26),c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29)], caption = 'For public universities, the percent of high schools visited by private universities', booktabs = T, align = 'r', linesep = '') %>%
   column_spec(c(7, 9, 15), width = '5em') %>%
@@
   column_spec(c(14), width = '8.8em') %>%
+  row_spec(0, align = 'c') %>% 
   kable_styling(font_size = 13, latex_options = 'scale_down')
@@
 
-\newpage
-
-```{r race-comp-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs.
-visited private high schools in the South, public research universities"}
-include_graphics(file.path(figures_dir, 'race_comp_pubu_privhs_pubhs.pdf'))
-```
-
-\newpage
-
-```{r race-comp-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs.
-visited private high schools in the South, selective private universities"}
-include_graphics(file.path(figures_dir, 'race_comp_privu_privhs_pubhs.pdf'))
-```
-
 \beginsupplement
@@
 
-kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix', booktabs = T, align = 'c', linesep = '') %>%
+kable(table_1mode_pubu$onemode_df, caption = 'One-mode public university count matrix', booktabs = T, align = 'r', linesep = '') %>%
   column_spec(c(7, 9, 15), width = '5em') %>%
@@
 
-kable(table_1mode_privu$onemode_df, caption = 'One-mode private universities count matrix', booktabs = T, align = 'c', linesep = '') %>%
+kable(table_1mode_privu$onemode_df, caption = 'One-mode private universities count matrix', booktabs = T, align = 'r', linesep = '') %>%
   column_spec(c(2, 3, 7:9, 11), width = '7em') %>% 
@@
 
+\newpage
+
+```{r race-comp-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs.
+visited private high schools in the South, public research universities"}
+include_graphics(file.path(figures_dir, 'race_comp_pubu_privhs_pubhs.pdf'))
+```
+
+\newpage
+
+```{r race-comp-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs.
+visited private high schools in the South, selective private universities"}
+include_graphics(file.path(figures_dir, 'race_comp_privu_privhs_pubhs.pdf'))
+```
+
 \end{landscape}

### 2023-12-15 r_r/tables_and_figures.Rmd
updates to manuscript

@@
 kable(univ_pop_df, caption = "Characteristics of universities in analysis sample compared to data collection sample", booktabs = T, escape = F, align = 'c', linesep = '') %>%
-  add_header_above(header = c(' ' = 1, 'Analysis sample (N=15)' = 3, 'Data collection sample (N=49)' = 3, 'Analysis sample (N=14)' = 3, 'Data collection sample (N=49)' = 3)) %>%
+  add_header_above(header = c(' ' = 1, 'Analysis sample (N=15)' = 3, 'Data collection sample (N=102)' = 3, 'Analysis sample (N=14)' = 3, 'Data collection sample (N=57)' = 3)) %>%
   add_header_above(header = c(' ' = 1, 'Public research universities' = 6, 'Selective private universities' = 6)) %>%

### 2023-12-15 r_r/tables_and_figures.tex
updates to manuscript

@@
 \cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
-\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Analysis sample (N=15)} & \multicolumn{3}{c}{Data collection sample (N=49)} & \multicolumn{3}{c}{Analysis sample (N=14)} & \multicolumn{3}{c}{Data collection sample (N=49)} \\
+\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Analysis sample (N=15)} & \multicolumn{3}{c}{Data collection sample (N=102)} & \multicolumn{3}{c}{Analysis sample (N=14)} & \multicolumn{3}{c}{Data collection sample (N=57)} \\
 \cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10} \cmidrule(l{3pt}r{3pt}){11-13}
@@
 \midrule
-25th Percentile SAT/ACT Composite Score & 1,060 & 1,126 & 1,164 & 985 & 1,083 & 1,169 & 1,185 & 1,278 & 1,314 & 1,212 & 1,313 & 1,402\\
-75th Percentile SAT/ACT Composite Score & 1,292 & 1,332 & 1,366 & 1,219 & 1,307 & 1,376 & 1,373 & 1,433 & 1,496 & 1,411 & 1,481 & 1,549\\
-In-State Tuition + Fees & \$10,741 & \$11,785 & \$13,913 & \$9,463 & \$11,547 & \$13,843 & \$47,126 & \$50,140 & \$51,848 & \$47,445 & \$50,394 & \$51,975\\
-Out-of-State Tuition + Fees & \$26,866 & \$30,502 & \$34,383 & \$26,594 & \$30,414 & \$35,279 & \$47,126 & \$50,140 & \$51,848 & \$47,445 & \$50,394 & \$51,975\\
-Total Enrolled Freshmen & 4,916 & 5,433 & 6,336 & 3,601 & 4,860 & 6,421 & 1,368 & 1,767 & 2,000 & 1,306 & 1,591 & 1,985\\
-Percent Out-of-State Freshmen & 21.1\% & 26.9\% & 45.0\% & 16.7\% & 27.2\% & 42.8\% & 63.1\% & 73.6\% & 82.4\% & 66.4\% & 76.6\% & 87.6\%\\
-Percent Pell Recipients & 19.5\% & 21.5\% & 26.8\% & 19.5\% & 23.9\% & 32.8\% & 10.2\% & 12.4\% & 16.9\% & 12.9\% & 14.3\% & 17.1\%\\
-Percent White Freshmen & 31.6\% & 68.0\% & 75.2\% & 37.7\% & 62.7\% & 70.0\% & 56.5\% & 65.9\% & 71.7\% & 40.9\% & 49.3\% & 65.3\%\\
-Percent Black Freshmen & 3.4\% & 4.3\% & 6.6\% & 2.2\% & 4.9\% & 7.6\% & 4.3\% & 4.7\% & 5.0\% & 4.1\% & 5.4\% & 7.1\%\\
-Percent Asian Freshmen & 3.4\% & 9.3\% & 29.9\% & 3.2\% & 6.7\% & 16.2\% & 5.5\% & 7.0\% & 14.3\% & 7.7\% & 14.7\% & 19.6\%\\
-Percent Hispanic Freshmen & 5.5\% & 8.5\% & 12.3\% & 6.4\% & 8.7\% & 13.4\% & 7.6\% & 10.7\% & 12.8\% & 9.0\% & 10.7\% & 13.3\%\\
-Percent International Freshmen & 2.0\% & 4.6\% & 8.7\% & 1.6\% & 3.5\% & 8.7\% & 3.8\% & 5.7\% & 9.0\% & 6.3\% & 10.0\% & 11.6\%\\
+25th Percentile SAT/ACT Composite Score & 1,060 & 1,126 & 1,164 & 984 & 1,061 & 1,135 & 1,185 & 1,278 & 1,314 & 1,191 & 1,289 & 1,391\\
+75th Percentile SAT/ACT Composite Score & 1,292 & 1,332 & 1,366 & 1,204 & 1,282 & 1,350 & 1,373 & 1,433 & 1,496 & 1,375 & 1,472 & 1,542\\
+In-State Tuition + Fees & \$10,741 & \$11,785 & \$13,913 & \$9,100 & \$10,750 & \$13,322 & \$47,126 & \$50,140 & \$51,848 & \$47,020 & \$49,914 & \$51,661\\
+Out-of-State Tuition + Fees & \$26,866 & \$30,502 & \$34,383 & \$23,433 & \$27,589 & \$32,989 & \$47,126 & \$50,140 & \$51,848 & \$47,020 & \$49,914 & \$51,661\\
+Total Enrolled Freshmen & 4,916 & 5,433 & 6,336 & 3,416 & 4,528 & 5,850 & 1,368 & 1,767 & 2,000 & 1,305 & 1,585 & 2,005\\
+Percent Out-of-State Freshmen & 21.1\% & 26.9\% & 45.0\% & 15.4\% & 25.8\% & 39.8\% & 63.1\% & 73.6\% & 82.4\% & 66.4\% & 76.6\% & 87.6\%\\
+Percent Pell Recipients & 19.5\% & 21.5\% & 26.8\% & 20.3\% & 25.5\% & 33.3\% & 10.2\% & 12.4\% & 16.9\% & 12.8\% & 14.2\% & 16.5\%\\
+Percent White Freshmen & 31.6\% & 68.0\% & 75.2\% & 45.3\% & 61.7\% & 72.6\% & 56.5\% & 65.9\% & 71.7\% & 41.1\% & 49.3\% & 63.8\%\\
+Percent Black Freshmen & 3.4\% & 4.3\% & 6.6\% & 3.1\% & 5.6\% & 8.9\% & 4.3\% & 4.7\% & 5.0\% & 4.0\% & 5.3\% & 7.1\%\\
+Percent Asian Freshmen & 3.4\% & 9.3\% & 29.9\% & 3.1\% & 6.6\% & 13.2\% & 5.5\% & 7.0\% & 14.3\% & 5.9\% & 13.2\% & 18.8\%\\
+Percent Hispanic Freshmen & 5.5\% & 8.5\% & 12.3\% & 5.5\% & 8.6\% & 16.8\% & 7.6\% & 10.7\% & 12.8\% & 9.0\% & 10.7\% & 13.3\%\\
+Percent International Freshmen & 2.0\% & 4.6\% & 8.7\% & 1.6\% & 3.1\% & 7.1\% & 3.8\% & 5.7\% & 9.0\% & 6.0\% & 9.8\% & 12.3\%\\
 \bottomrule

### 2023-12-15 scripts/create_tables_figures.R

@@ -676,12 +676,15 @@ southern_pubhs <- pubhs_universe_df %>%
   filter(state_code %in% southern_states) %>% 
   select(ncessch, g12, pct_white, pct_black, pct_hispanic, pct_asian, pct_amerindian, pct_nativehawaii, pct_tworaces) %>% 
   mutate(
+    pct_native = pct_amerindian + pct_nativehawaii
+  ) %>% 
+  select(-pct_amerindian, -pct_nativehawaii) %>% 
+  mutate(
     cnt_white = pct_white / 100 * g12,
     cnt_black = pct_black / 100 * g12,
     cnt_hispanic = pct_hispanic / 100 * g12,
     cnt_asian = pct_asian / 100 * g12,
-    cnt_amerindian = pct_amerindian / 100 * g12,
-    cnt_nativehawaii = pct_nativehawaii / 100 * g12,
+    cnt_native = pct_native / 100 * g12,
     cnt_tworaces = pct_tworaces / 100 * g12
   )
 
@@ -689,12 +692,15 @@ southern_privhs <- privhs_universe_df %>%
   filter(state_code %in% southern_states) %>% 
   select(school_id, enroll, pct_white, pct_black, pct_hispanic, pct_asian, pct_amerindian, pct_nativehawaii, pct_tworaces) %>% 
   mutate(
+    pct_native = pct_amerindian + pct_nativehawaii
+  ) %>% 
+  select(-pct_amerindian, -pct_nativehawaii) %>% 
+  mutate(
     cnt_white = pct_white / 100 * enroll,
     cnt_black = pct_black / 100 * enroll,
     cnt_hispanic = pct_hispanic / 100 * enroll,
     cnt_asian = pct_asian / 100 * enroll,
-    cnt_amerindian = pct_amerindian / 100 * enroll,
-    cnt_nativehawaii = pct_nativehawaii / 100 * enroll,
+    cnt_native = pct_native / 100 * enroll,
     cnt_tworaces = pct_tworaces / 100 * enroll
   )
 
@@ -716,15 +722,18 @@ southern_privhs_comp$univ_abbrev <- c('Private HS, universe', 'Private HS, unive
 
 plot_racial_comp <- function(universe_df, schools_df, univ_type, hs_type) { 
   southern_comp <- schools_df %>% 
-    filter(classification == univ_type, event_type == hs_type, event_state %in% southern_states) %>% 
+    filter(classification == univ_type, event_type == hs_type, event_state %in% southern_states) %>%
+    mutate(
[…]

### 2023-12-15 r_r/manuscript_rihe_r_r.Rmd
privhs_df

@@
 She found that universities engage in "recruitment redlining -- the circuitous avoidance of predominantly Black and Latinx communities along recruiting visit paths" (p.
-X).<!--[CRYSTAL -- FIND PAGE NUMBER] TODO: I don't think I'm able to access the full version of the paper: https://doi.org/10.1080/00221546.2021.2004811--> Although @RN4758 and @RN4934 focused on visits to public high schools, prior research has not considered visits to private schools by public research universities.
+585).
+Although @RN4758 and @RN4934 focused on visits to public high schools, prior research has not considered visits to private schools by public research universities.
 For example, what is the scale of these visits and what are the characteristics of visited schools?
@@
 
-The data collection sample for the broader project consisted of: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), all private universities in the top 100 of U.S.
-News and World Report National Universities rankings (N=57), and all private colleges in the top 50 of U.S.
+The data collection sample for the broader project consisted of: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), all private universities in the top 100 of the 2020 U.S.
+News and World Report National Universities rankings (N=57), and all private colleges in the top 50 of the 2020 U.S.
 News and World Report Liberal Arts Colleges rankings (N=47).
@@
 "One-mode" networks consist of vertices of a "type." For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges).
-Similarly, the social network of Twitter<!--TODO: Not sure if we should call this X now?
-haha--> consists of handles (vertices) who are connected to one another by following or being followed (edges).
+Similarly, the social network of $X$ (formerly Twitter) consists of handles (vertices) who are connected to one another by following or being followed (edges).
 
@@
 At public high schools (bottom panel), Black/Latinx/Native students comprise less than 20% of enrolled students at around 40%<!--0.4087567--> of all public schools.
-However, most public research universities and all selective private universities visited private high schools at a higher rate than public high schools<!--TODO: I'm not too sure how to interpret "higher rate than public high schools" - should it be higher rate than proportional rate?
-Related, is the last sentence supposed to be "disproportionate emphasis on visits to" PRIVATE instead of "public schools"?-->, as seen earlier in Figures \@ref(fig:actual-proportional-pubu) and \@ref(fig:actual-proportional-privu).
+However, most public research universities (Figure \@ref(fig:actual-proportional-pubu)) and all selective private universities (Figure \@ref(fig:actual-proportional-privu)) visited a disproportionate number of private high schools compared to public high schools.
 Even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.

### 2023-12-15 r_r/letter_to_reviewers.Rmd
the longest yard

@@
 
-**Author response**: The revised Data and Sample section states that "The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection." We agree with Reviewer 1<!--TODO: Is this comment by Reviewer 1 or 2?
-This is under the level-1 section "Response to Reviewer 2"--> that making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities.
+**Author response**: The revised Data and Sample section states that "The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection." We agree with Reviewer 2 that making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities.
 The revised manuscript now includes a Limitations subsection that describes this limitation and its consequences.
@@
 
-**Author response**: This is an excellent suggestion by Reviewer 1<!--TODO: Is this comment by Reviewer 1 or 2?
-This is under the level-1 section "Response to Reviewer 2"-->.
-The new Limitations section in the revised manuscript discusses the drawbacks of a convenience sample.
+**Author response**: This is an excellent suggestion by Reviewer 2. The new Limitations section in the revised manuscript discusses the drawbacks of a convenience sample.
 

### 2023-12-15 r_r/manuscript_rihe_r_r.Rmd
the longest yard

@@
 For Catholic school students, 12.8% attended a top 100 public university and 11.7% attended a top 100 private university, while for Christian schools these percentages were 8.2% and 8.2%<!--TODO: Want to double check they're both 8.2%?-->, respectively.
-However, for nonsectarian private school students, 11.3% attended a top 100 public university and 39.8% attended a top 100 private university.
+However, for nonsectarian private school students, 11.3% attended a top 100 public university and an incredible 39.8% attended a top 100 private university.
+
 Focusing on the institutional composition of private universities in USNWR top 100, 39.8%<!--TODO: Want to double check this and the previous sentence are both 39.8%?--> attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).
@@
 
+Finally, Figure X examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample.
+Figure X does the same for selective private universities.
+These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest [@RN4504].
+For public research universities, Figure X shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools.
+This was true for all public universities in our sample, and particularly for UNIVERSITY X, Y, Z.
+Results for selective private universities in Figure X mirror the results for public research universities.
+Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits.
 <!--TODO: Supplemental figures \@ref(fig:race-comp-pubu-privhs-pubhs) AND \@ref(fig:race-comp-privu-privhs-pubhs) are now moved to appenidix-->
+INSERT FIGURES X AND X ABOUT HERE
 

### 2023-12-16 r_r/manuscript_rihe_r_r.Rmd
updates to figures

@@
 
-Figures \@ref(fig:region-pubu-privu) through \@ref(fig:race-comp-privu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?" Additionally, Appendix Figures \@ref(fig:enroll-pubu-privu) and \@ref(fig:enroll-pubu-privhs-pubhs) show the 12th grade enrollment size of visited high schools.
+Figures \@ref(fig:region-pubu-privu) through \@ref(fig:south-race-privu-privhs-pubhs) address research question 3, "How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?" Additionally, Appendix Figures \@ref(fig:enroll-pubu-privu) and \@ref(fig:enroll-pubu-privhs-pubhs) show the 12th grade enrollment size of visited high schools.
 
@@
 
-Finally, Figure X examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample.
-Figure X does the same for selective private universities.
+Finally, Figure \@ref(fig:south-race-pubu-privhs-pubhs) examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample.
+Figure \@ref(fig:south-race-privu-privhs-pubhs) does the same for selective private universities.
 These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest [@RN4504].
-For public research universities, Figure X shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools.
-This was true for all public universities in our sample, and particularly for UNIVERSITY X, Y, Z.
-Results for selective private universities in Figure X mirror the results for public research universities.
+For public research universities, Figure \@ref(fig:south-race-pubu-privhs-pubhs) shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools.
+This was true for most public universities in our sample, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati.
+A notable exception is SUNY Stony Brook, though this university only visited 12 private universities in the South.
+Results for selective private universities in Figure \@ref(fig:south-race-privu-privhs-pubhs) (with the exception of Marquette) mirror the results for public research universities.
 Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits.
-<!--TODO: Supplemental figures \@ref(fig:race-comp-pubu-privhs-pubhs) AND \@ref(fig:race-comp-privu-privhs-pubhs) are now moved to appenidix-->
-INSERT FIGURES X AND X ABOUT HERE
+Appendix Figures \@ref(fig:south-race-comp-pubu-privhs-pubhs) and \@ref(fig:south-race-comp-privu-privhs-pubhs) show the full racial composition of visited public and private schools in the South.
+
+INSERT FIGURES \@ref(fig:south-race-pubu-privhs-pubhs) AND \@ref(fig:south-race-privu-privhs-pubhs) ABOUT HERE
 
@@
 By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.
-<!--TODO: [ADD A SENTENCE ABOUT RACIAL COMPOSITION OF VISITS TO SOUTH?]-->
+This is true of the visits to schools in the South as well.
 
@@
 
+\newpage
+
+```{r south-race-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools in the South vs.
+visited private high schools in the South, public research universities"}
+include_graphics(file.path(figures_dir, 'south_race_pubu_privhs_pubhs.pdf'))
+```
+
+\newpage
+
+```{r south-race-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Percentage of students who identify as Black, Latinx, or Native at visited public high schools in the South vs.
+visited private high schools in the South, selective private universities"}
+include_graphics(file.path(figures_dir, 'south_race_privu_privhs_pubhs.pdf'))
+```
+
 \beginsupplement
@@
 
-```{r race-comp-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs.
+```{r south-race-comp-pubu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools in the South vs.
 visited private high schools in the South, public research universities"}
-include_graphics(file.path(figures_dir, 'race_comp_pubu_privhs_pubhs.pdf'))
-```
-
-\newpage
-
-```{r race-comp-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools vs.
+include_graphics(file.path(figures_dir, 'south_race_comp_pubu_privhs_pubhs.pdf'))
+```
+
+\newpage
+
+```{r south-race-comp-privu-privhs-pubhs, echo = FALSE, fig.align = 'center', out.width = "200%", fig.cap = "Racial composition of students at visited public high schools in the South vs.
 visited private high schools in the South, selective private universities"}
-include_graphics(file.path(figures_dir, 'race_comp_privu_privhs_pubhs.pdf'))
+include_graphics(file.path(figures_dir, 'south_race_comp_privu_privhs_pubhs.pdf'))
 ```

### 2023-12-16 scripts/create_tables_figures.R

@@ -464,7 +464,7 @@ unique_visited_schools <- events_df %>%
     values_fill = 0
   )
 
-plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic, label_text, control = 'public', type = 'univ', loc = c('instate', 'outofstate')) {
+plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic, label_text, control = 'public', type = 'univ', loc = c('instate', 'outofstate'), gg_title = '') {
   
   sub_df_visited <- pubhs_visited_df %>% group_by(get(var_name)) %>% 
     summarize(`Public HS, 1+ visit` = n()) %>% 
@@ -518,6 +518,7 @@ plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic
     scale_fill_manual(labels = label_text, values = color_palette) +
     scale_x_discrete(labels = function(x) str_wrap(x, width = 40)) +
     scale_y_continuous(labels = scales::percent, expand = c(0, 0, 0.05, 0)) +
+    ggtitle(gg_title) +
     theme(legend.position = 'top',
           legend.title = element_text(size = 6, face = 'bold'),
           legend.text = element_text(size = 6),
@@ -526,12 +527,12 @@ plot_characteristic_pubhs <- function(plot_type, var_name, label, characteristic
           legend.key.size = unit(0.3, 'cm'),
           panel.background = element_blank(),
           axis.ticks.y = element_blank(),
-          text = element_text(size = 8),
-          plot.title = element_text(color = 'white')) +
+          plot.title = element_text(size = 8, hjust = 0.45),
+          text = element_text(size = 8)) +
     coord_flip()
 }
 
-plot_characteristic_privhs <- function(plot_type, var_name, label, characteristic, label_text, control = 'public', type = 'univ') {
+plot_characteristic_privhs <- function(plot_type, var_name, label, characteristic, label_text, control = 'public', type = 'univ', gg_title = '') {
   
   sub_df_visited <- privhs_visited_df %>% group_by(get(var_name)) %>% 
     summarize(`Private HS, 1+ visit` = n()) %>% 
[…]

### 2023-12-21 r_r/manuscript_rihe_r_r.Rmd
submitted r&r mofogit add .git add .

@@
 
-*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities (Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette), 12 selective private liberal arts colleges (Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College), and 15 public research universities (UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, University of Arkansas).
-We are still trying to figure out what happened.*
+*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.] We are still trying to figure out what happened.*
 
@@
 For public research universities, Figure \@ref(fig:south-race-pubu-privhs-pubhs) shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools.
-This was true for most public universities in our sample, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati.
-A notable exception is SUNY Stony Brook, though this university only visited 12 private universities in the South.
-Results for selective private universities in Figure \@ref(fig:south-race-privu-privhs-pubhs) (with the exception of Marquette) mirror the results for public research universities.
+This was true for all universities in our sample that visited a substantial number of schools in the South, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati.
 Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits.
+Results for private universities in Figure \@ref(fig:south-race-privu-privhs-pubhs) are very similar, with Emory, Northwestern, and Case Western visiting private schools with a low share of Black/Latinx/Native students.
 Appendix Figures \@ref(fig:south-race-comp-pubu-privhs-pubhs) and \@ref(fig:south-race-comp-privu-privhs-pubhs) show the full racial composition of visited public and private schools in the South.
+For most universities that made a substantial number of visits in the South, white students comprised around 70% of total enrollment at visited private schools compared to around 40% at visited public schools.
 

### 2023-12-27 r_r/letter_to_reviewers.Rmd
submitted r&r mofogit add .git add .
trying to create word file

@@
 #author: "ozan"
-date: "`r Sys.Date()`"
-output: pdf_document
+#date: "`r Sys.Date()`"
+#output: pdf_document
+output: word_document
 bibliography: ./../other/burd_recruiting_chapter.bib
@@
 
-XXXX X, 2023
+December 20, 2023
 

### 2023-12-27 r_r/manuscript_rihe_r_r.Rmd
trying to create word file

@@
 output:
+  #bookdown::word_document2:
   bookdown::pdf_document2:
@@
     pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
+    keep_tex: true
 csl: ./../other/apa.csl
 urlcolor: blue
+#always_allow_html: true
 header-includes:

### 2023-12-27 r_r/manuscript_rihe_r_r.tex
trying to create word file

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  12pt,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{pdflscape}
\usepackage{geometry}
\usepackage{floatrow}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{titlesec}
\floatsetup{capposition=top}
\newcommand{\beginsupplement}{
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={blue},
  pdfcreator={LaTeX via pandoc}}

\title{The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities}
\author{}
\date{\vspace{-2.5em}}

\begin{document}
\maketitle

\setstretch{1.5}

\textbf{ABSTRACT}

Scholarship on nonresident enrollment by public research universities has developed in isolation from scholarship on linkages between private high schools and selective private universities. We argue that these literatures are part of a broader story about the competition for students from affluent schools and communities. This manuscript analyzes off-campus recruiting visits to private high schools made by a convenience sample of 15 public research universities and 14 selective private universities. An off-campus recruiting visit indicates a social relationship between a school and a university. Therefore, we utilize social network methods to examine the recruiting networks of public and private universities. With respect to scale (research question 1), universities in our sample made a disproportionate number of visits to private high schools. With respect to overlap (RQ2), simple network analyses and community detection methods reveal substantial overlap in the recruiting networks of public and private universities. RQ3 assesses the characteristics of visited schools. Both public and private universities tended to visit private schools in their home geographic region and also in the South, where private school enrollment growth has been strongest. Visited private schools enroll a much larger share of white students than visited public schools. Surprisingly, several public research universities visited sectarian private high schools at a rate similar to sectarian private universities.

\pagenumbering{roman}
\newpage
\pagenumbering{gobble}
\pagenumbering{arabic}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\emph{During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.\footnote{These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.} We are still trying to figure out what happened.}

\bigskip

Autumn is college recruiting visit season at Harpeth Hall, a nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee. Founded in 1951, Harpeth is an ``A+'' school ranked 337 in the nation according to the 2020 \emph{Best Private High Schools in America} by Niche. Enrollment patterns at Nashville-area private schools reflect broader regional patterns, whereby ``efforts by the courts to desegregate public schools in the South resulted in White flight to private schools'' (Murnane \& Reardon, 2018, p. 14). In Fall 2017, about 85\% of Harpeth students were white and less than 5\% were Black or Latinx (Author calculations).

From September 6th through October 17th, Harpeth received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee). Previous scholarship observes strong connections between private schools and selective private universities (Khan, 2011; Stevens, 2007). However, Harpeth also received visits from six out-of-state public research universities, the University of Cincinnati, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.

The nonsectarian University School of Nashville was founded in 1975 and is located next door to Vanderbilt University. It is an ``A+'' school, ranked 127th in the nation, and is more racially diverse than Harpeth (64\% white, 11.5\% Black, 3.5\% Latinx, 10.0\% Asian). From August 22nd 2017 through October 18th, the University School received visits from nearly the same set of 11 private universities that visited Harpeth (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinnati, CU Boulder).

Father Ryan High School is a Catholic school founded in 1925. Father Ryan is predominantly white (86\%, 7\% Black or Latinx) and received an ``A'' grade from Niche, meaning it is not ranked in the top 1,000 U.S. private schools. In Fall 2017, Father Ryan received visits from eight of the 14 private universities in our sample (including three of the four Catholic universities) and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama. Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from six private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University). It also received visits from the University of Cincinnati, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder. Christ Presbyterian Academy was founded in 1985 and 94\% of its students are white.

Theories of organizational behavior suggest that university recruiting behaviors -- those that require significant expenditure -- are indicators of organizational enrollment priorities. Large, public-facing organizations are beset by multiple, competing pressures from the external environment, but organizations have difficulty pursuing multiple goals (Pfeffer \& Salancik, 1978; Thompson, 1967). Thus, organizations respond by symbolically adopting some goals and substantively adopting others (Meyer \& Rowan, 1977). Under symbolic adoption, organizations adopt policies and structures that send signals to external constituents but do not substantively affect resource allocation inside the ``technical level'' of the organization.\footnote{Contingency theory states that organizations consist of ``technical levels'' responsible for processing inputs and producing outputs and ``managerial levels'' responsible for directing the technical level and tending to demands from the external environment (Thompson, 1967). The technical level achieves effectiveness by focusing on a small, stable set of goals.} Under substantive adoption, organizations direct resources in the technical level towards achieving the goal. Off-campus recruiting visits to local high schools and college fairs was the top-ranked recruiting expenditure item for both public and private universities, according to Ruffalo Noel-Levitz (2020a). Therefore, analyses of which schools a university visits -- and which schools they ignore -- can yield insights about university enrollment goals.

Author (XXXXa) analyzed recruiting visits to public high schools made by 15 public research universities in 2017. The authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools. These out-of-state visits focused on affluent, predominantly white public schools. Set against the scholarship about declining state appropriations and growing nonresident enrollment (Author, XXXXb, XXXXc), these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition prices.

Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990). This research observes strong links -- and student flows -- between private high schools and selective private universities. Private schools enroll many students who can afford private university tuition (Stevens, 2007). To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between private schools and colleges. We argue that these two stories have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities. Simply put, selective private universities and public research universities are increasingly competing for students from the same set of affluent households.

This study analyzes recruiting visits to private high schools made in the 2017 calendar year by a sample of 15 public research universities and 14 selective private universities. We conceptualize recruiting visits as an indication the university and the school have a social relationship. This conceptualization motivates the use of social network methods, which analyze networks defined by ``network ties'' (i.e., visits) between actors (universities and schools). Comparing the recruiting networks of public research universities and selective private universities yields novel insights about the competition for affluent, ``full-pay'' students. Analyses are informed by three research questions:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?
\item
  To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
\item
  What are the characteristics of private schools that receive visits from public research universities and selective private research universities in our sample?
\end{enumerate}

Both private and public universities in our sample made a disproportionate number of visits to private high schools. For public research universities, visited private schools were much more likely to be out-of-state than visited public schools. Network analyses revealed substantial overlap in the recruiting networks of universities in our sample. For several public universities (e.g., University of Alabama, University of South Carolina), their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, Texas Christian University) than they did to other public universities in our sample. Results suggest that recruiting networks are substantially a function of geographic location. All universities visited a large number of private schools in their home region. However, most universities in our sample also visited a large number of private schools in the South, the region where private school enrollment has grown the most over the past three decades (Murnane \& Reardon, 2018). The private schools visited by public and private universities in our sample enrolled a much higher share of white students than the public schools visited by these universities. Surprisingly, several public universities visited sectarian private high schools at a rate similar to sectarian private universities.

This manuscript yields practical implications for public and private universities concerned about racial and socioeconomic diversity. Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors (EAB \& NACAC, 2023; Ruffalo Noel-Levitz, 2022a, 2022b). Prior research finds that students are sensitive to recruiting interventions, including off-campus recruiting visits (Holland, 2019; Ruffalo Noel-Levitz, 2018). Therefore, which high schools a university chooses to visit affects the subsequent enrollment composition of the university. In the aftermath of the Supreme Court decision on race-conscious admissions, public and private universities are searching for ways to increase racial diversity without running afoul of the law. The U.S. Department of Education (2023, p. 9) recommends that universities expand ``outreach to high schools with substantial populations of low-income students and students of color.'' Most public and private universities in our sample visited a disproportionate number of private schools and these private schools tended to enroll mostly white students. We recommend that universities concerned about racial diversity should conduct an internal equity audit of their recruiting practices, for example, comparing the racial and socioeconomic characteristics of schools they visit versus schools they do not visit.

\hypertarget{literature-review}{%
\section{Literature Review}\label{literature-review}}

\hypertarget{nonresident-enrollment-at-public-universities}{%
\subsection{Nonresident Enrollment at Public Universities}\label{nonresident-enrollment-at-public-universities}}

We situate this study vis-a-vis scholarship on enrollment management behavior by public research universities and particularly the pursuit of affluent nonresident students, a population also targeted by selective private universities. The so-called ``iron triangle'' of enrollment management states that universities pursue the broad enrollment goals of access, academic profile, and revenue generation (Cheslock \& Kroc, 2012; DesJardins \& Bell, 2006). Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve trade-offs with other goals. Cheslock \& Kroc (2012, p. 221) state that ``most enrollment management policies\ldots do not advance all three objectives; instead they lead to gains in some areas and declines in others.'' Scholarship argues that selective private universities prioritize academic profile and revenue generation, with funds generated from tuition and donation feeding the arms race for prestige (Killgore, 2009; Stevens, 2007; Winston, 1999). Historically, public research universities prioritize enrollment of high-performing state residents, often with an emphasis on social mobility for students who cannot afford private universities (Rudolph, 1962). However, scholarship on privatization argues that public research universities increasingly emphasize tuition revenue and rankings and de-emphasize access for state residents (Priest \& St. John, 2006; Slaughter \& Rhoades, 2004).

Author (XXXXb) draw from resource dependence theory to conceptualize the relationship between state appropriations and nonresident enrollment. Organizations are dependent on external resources that are important for organizational survival/stability and cannot be easily replaced. Public universities depend on state appropriations but these funds became increasingly uncertain in the 1980s and 1990s (Delaney \& Doyle, 2011). Resource dependence theory states that one response to resource decline or uncertainty is to seek alternative, substitute resources (Pfeffer \& Salancik, 1978). Tuition revenue is a potential substitute for state appropriations. Most states cap resident tuition prices, but not nonresident tuition prices. Therefore, Author (XXXXb) argued that public universities have a financial incentive to grow nonresident enrollment in response to declines in state appropriations. Analyzing panel data from 2002-03 to 2012-13, Author (XXXXb) found that a 10\% decline in state appropriations was associated with a 2.7\% increase in nonresident enrollment at all public universities and a 5.0\% increase in nonresident enrollment at research-extensive universities.

Other studies of nonresident enrollment examine university enrollment composition. Using data from NPSAS 2011-12, Author (XXXXc) show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or LatinX. Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and LatinX students. Author (XXXXd) examine whether growth in the number of nonresident students causes resident enrollment to decline. They find that nonresident enrollment ``crowds out'' resident enrollment at prestigious public research universities, but not at less prestigious public research universities.

How did public research universities go about attracting all these nonresident students? One mechanism is financial aid, a lever to increase applications and affect matriculation decisions. Many public research universities have developed institutional aid policies for nonresident admits, typically offering larger awards for higher achieving students (Curs \& Singell, 2002, 2010; Leeds \& DesJardins, 2015).

Earlier in the ``enrollment funnel,'' universities utilize marketing and recruiting interventions to attract nonresident applicants. One widely utilized intervention is off-campus recruiting visits by admissions counselors to local high schools. Author (XXXXa) analyzed off-campus recruiting visits to public high schools by 15 public research universities. Recruiting visits to in-state high schools tended to exhibit modest racial and socioeconomic bias. However, 12 of the 15 universities made more visits to out-of-state high schools than in-state high schools. These out-of-state visits focused on public schools in affluent, predominantly white communities. Salazar (2022) conducted geospatial analyses of out-of-state recruiting visits to Los Angeles and Dallas by four public research universities. She found that universities engage in ``recruitment redlining -- the circuitous avoidance of predominantly Black and Latinx communities along recruiting visit paths'' (p.~585). Although Author (XXXXa) and Salazar (2022) focused on visits to public high schools, prior research has not considered visits to private schools by public research universities. For example, what is the scale of these visits and what are the characteristics of visited schools?

\hypertarget{linkages-between-private-schools-and-private-universities}{%
\subsection{Linkages Between Private Schools and Private Universities}\label{linkages-between-private-schools-and-private-universities}}

Separate from scholarship on nonresident enrollment at public universities, scholarship from economics and sociology analyzes linkages between private schools and colleges.

Murnane \& Reardon (2018) set the stage by describing long-term trends in private school enrollment. The percentage of American (elementary school) students attending private schools declined from 15\% in the mid-1960s to 10\% in the mid-1970s, and declined gradually from 11\% in 1999 to 9\% in 2015. The private school enrollment rate for high-income families and for low-income families has remained relatively stable over time at about 17\% and 4\%, respectively. The enrollment rate for middle-income families declined from 12\% in 1968 to 6\% in 2013. This decline was driven by shrinking Catholic school enrollment, which represented 89\% of private school enrollment in 1965 and 42\% of enrollment in 2013. Moreover, contemporary Catholic school students tend to be more affluent compared to prior decades. There has been a long-term increase in private school enrollment in the South, with middle-income families increasingly attending Christian schools and high-income families increasingly attending nonsectarian schools. With respect to race, 11\% of white students attended private school in 2013, compared to 5\% of Black students, and 3\% of Hispanic students.

A robust empirical literature finds that attending private school positively affects college access and college selectivity (e.g., Clark \& Del Bono, 2016; Falsey \& Heyns, 1984; Jerrim, Parker, Chmielewski, \& Anders, 2016; Persell, Catsambis, \& Cookson, 1992). Scholarship from the 1980s and 1990s focused on the effects of attending Catholic school (Bryk et al., 1993; Coleman \& Hoffer, 1987; Eide, Goldhaber, \& Showalter, 2004; Neal, 1997). More recent scholarship tends to find that attending a nonsectarian private school has larger effects on college access than attending a Catholic school (Chetty et al., 2023; Hill, 2008; Klugman, 2012).

The High School Longitudinal Survey of 2009 (HSLS) tracks the postsecondary destinations of students who were in ninth grade in 2009. Simple descriptive statistics are eye-opening (Author calculations).\footnote{Analyses consist of students who met the following conditions: completed the 2012 follow-up survey; obtained high school transcript data; and completed the 2016 follow-up survey. The survey weight variable used was W4W1W2W3STU. After weighting, these 14,020 (unweighted) students represent a population of 3.93 million U.S. ninth graders in 2009. Data on college rankings come from the 2020 U.S. News \& World Report \emph{Best Colleges}. Data on high school control come from the HSLS school file and from the Private School Survey.} About 93\% of students attended a public high school and 7\% attended a private high school, including 3.6\% attending a Catholic school, 1.6\% attending a nonsectarian school, and 1.8\% attending a Christian school. Of public high school students, 5.0\% attending a public university ranked in the top 100 by U.S. News and World Report (USNWR) and 1.9\% attended a private university ranked in the top 100. Of private high school students, 10.9\% attended a top 100 public university and 16.8\% attended a top 100 private university. For Catholic school students, 12.8\% attended a top 100 public university and 11.7\% attended a top 100 private university, while for Christian schools these percentages were 8.2\% and 8.2\%, respectively. However, for nonsectarian private school students, 11.3\% attended a top 100 public university and an incredible 39.8\% attended a top 100 private university.

Focusing on the institutional composition of private universities in USNWR top 100, 39.8\% attended a private high school (compared to 7\% of all high school students who attended a private high school) and 21.2\% attended a nonsectarian private high school (compared to 1.6\% of all high school students who attended a nonsectarian private high school).

Scholarship has been particularly interested in the relationship between attending a prestigious private school and attending an ultra-selective university (Cookson \& Persell, 1985, 1985; Levine, 1980; Reeves, Friedman, Rahal, \& Flemmen, 2017). Chetty et al. (2023) acquired unprecedented data -- application files and admissions decisions linked to income tax records -- to investigate why high-income families are over-represented at ``Ivy Plus'' colleges. Conditioning on SAT and ACT scores, applications from high-income families (top 1\%) received the same academic rating as applications from lower-income families. However, applications from high-income families received higher non-academic ratings (extracurricular activities, leadership traits) than applications from lower-income families. In turn, the higher non-academic rating for high-income applicants was driven by the fact that these students tended to attend elite private high schools that devote substantial resources to teacher recommendations and guidance counselor letters.

Scholarship from sociology has examined organizational connections that catalyze the flow of students between private schools and selective private colleges (Khan, 2010, 2011; Persell \& Cookson, 1985; Stevens, 2007). Stevens (2007) provides an ethnography of the admissions office at a selective private liberal arts college. The College is sensitive about its position in the U.S. News Rankings, and enrollment priorities tend to focus on academic profile and revenue generation. Stevens (2007) highlights the relational function of off-campus recruiting visits, stating that ``the College's reputation and the quality of its applicant pool are dependent upon its connections with high schools nationwide'' (p.~54). Therefore, during the autumn ``travel season,'' admissions officers visit selected high schools across the country ``to spread word of the institution and maintain relationships with guidance counselors'' (p.~53-54) because counselors who view a college favorably will steer students to that college. The College tended to visit the same ``feeder'' schools year after year because recruiting depends on long-term relationships with high schools. The high schools they visited tend to be affluent schools -- in particular, private schools -- that possess the resources to host a successful visit and enroll high-achieving students who can afford tuition.

An anecdote from Stevens (2007, p. 73) highlights the allure that prestigious private schools and affluent private school students hold for selective private colleges. Stevens accompanied an admissions officer from the College on a visit to Corbett Academy, a prestigious school for girls. The admissions officer ``said with a grin, `We're not getting Corbett's finest.'\,'' Stevens (2007, p. 73) writes that,

\begin{quote}
Corbett consistently sent its top performers to places like Berkeley and Stanford and the top of the Ivy League \ldots {[}Other colleges{]} in the College's own peer group only had a shot at girls nearer the middle of Corbett's class. Or below the middle. Still, by most standards this excellent school's modest achievers were very good admissions prospects, which was why we were visiting. Even Corbett's less fine would enter college well prepared academically, and their generally affluent families could absorb the College's full tuition and board cost with little, if any, financial aid.
\end{quote}

Khan (2010) analyzed recruiting from the perspective of an elite private boarding school in order to understand ``how such schools continue to get comparatively under-qualified students into top colleges and universities'' (p.~98). Guidance counselors at these schools capitalize on the fact that selective colleges are concerned about their acceptance and yield rates. Therefore, admissions offices value credible information about which applicants will accept or decline an admissions offer. This desire for intelligence creates an opportunity for high school counselors to advocate on behalf of their students. Guidance counselors tell admissions counselors which highly-sought-after applicants are likely to decline an offer, while lobbying for an applicant who has relatively weak academic credentials but is sure to matriculate and has ``character'' and extracurricular activities the university values. Khan (2010) states that such horsetrading depends on guidance counselors having sufficiently small caseloads to advocate for each student individually and on having personal relationships with university admissions officers. While Stevens (2007) and Khan (2010) highlight the importance of social networks between private schools and private universities, prior research has not analyzed the social networks that emerge from off-campus visits.

Additionally, scholarship on linkages between private high schools and private universities focuses on elite high schools and ultra-selective universities (Chetty et al., 2023; Cookson \& Persell, 1985; Khan, 2010; Kingston \& Lewis, 1990). With the exception of the single-institution ethnography by Stevens (2007), we know less about linkages between private schools and private universities that are selective but not elite. These merely-selective universities are self-conscious about their reputation, and have fewer resources and weaker student demand compared to Ivy Plus universities. Analyses of off-campus recruiting visits provide novel insights about the schools and student populations these institutions target.

\hypertarget{synthesis}{%
\subsection{Synthesis}\label{synthesis}}

We argue that a recruiting visit from a university to a private high school is an indicator of a social relationship. Empirically, Stevens (2007) finds that off-campus recruiting visits are important for the maintenance of strong relationships between a college and a high school. Logically, the fact that the college made the effort to visit suggests that the college wants to enroll students from the high school. Similarly, the fact that the high school hosted the visit suggests that the high school likely views the college as a desirable destination for some of its students. Moreover, the presence of the recruiting visit suggests the probability of additional interactions (e.g., phone calls) between the organizations. For example, Ruffalo Noel-Levitz (2022b) reports that ``calling after visits'' was the most effective strategy for high school guidance counselor outreach for both private universities and public universities. Conceptualizing a recruiting visit as an indicator of a relationship between a college and a high school motivates the use of social network methods, which analyze the network defined by ``network ties'' (i.e., visits) between actors (universities and schools).

Although the literature on nonresident enrollment developed in isolation from the literature on private school to private university linkages, both phenomena are part of a broader story about the changing nature of school segregation and the competition for affluent, traditional college students. Drawing from resource dependence theory, as public research universities become more reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices. Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), public research universities began substantially increasing nonresident enrollment en masse around 2005 (Author, XXXXb). By contrast, selective private universities have long relied on enrollment from private schools (Persell \& Cookson, 1985; Stevens, 2007). Therefore, the pursuit of out-of-state private school students by public research universities is a relatively recent encroachment on the historic territory of selective private universities and in-state flagships. Speaking about this competition, an enrollment management consultant said, ``\,`Everybody wants to go to the magic island of full pay students, but it's rapidly shrinking real estate'\,'' (Rivard, 2013). By analyzing the network of recruiting visits, we show whether public research universities and selective private universities are competing for students at similar sets of private schools. This may be direct competition for the same student or vying to be the second choice for students who are rejected by their top choice.

Private schools tend to enroll a larger share of white students than public schools.\footnote{Evidence for this claim can be seen in Figure \ref{fig:race-pubu-privhs-pubhs}.} Over the past three decades, middle-income enrollment at Catholic schools has declined and private school students have become more affluent. In the South, private school enrollment has grown as a consequence of ``white flight'' from public schools facing desegregation orders (Murnane \& Reardon, 2018). Thus, in recruiting from private schools, universities may be targeting student bodies that are more affluent and racially homogeneous than public schools. We investigate the characteristics -- including geographic region and racial composition -- of private schools being targeted by university admissions officers because these characteristics have downstream implications for the racial composition of university campuses.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{data-and-sample}{%
\subsection{Data and Sample}\label{data-and-sample}}

This manuscript draws from a broader project in which we collected data about off-campus recruiting visits made during the 2017 calendar year by a convenience sample of colleges and universities. For universities in our data collection sample, we investigated their admissions website for pages that posted their upcoming off-campus recruiting visits. For institutions that posted such pages, we scraped the pages once per week throughout 2017. Web-scraping was conducted using the Python programming language using the \emph{requests} library. Many universities in our data collection sample only posted certain kinds of events (e.g., hotel receptions and national college fairs) but not others (e.g., day-time visits to high schools). These institutions were excluded from the analysis sample.

For public universities in our analysis sample, we assessed the quality of the web-scraped data by asking the enrollment/admissions office for these data. If a university denied or ignored our request, we issued a formal public records request. Of the 15 public universities analyzed in this study, we received requested data from 11 universities. For these 11 universities, web-scraped data was very similar to publicly requested data. For universities that sent us data, the analyses below use ``requested'' rather than ``scraped'' data because requested data tended to have more events. Broad patterns were similar across requested data versus scraped data, and results based on scraped data are available upon request. Author (XXXXa) describe data quality checks in greater detail.

The data collection sample for the broader project consisted of: all public research-extensive universities as defined by the 2000 Carnegie Classification (N=102), all private universities in the top 100 of the 2020 U.S. News and World Report National Universities rankings (N=57), and all private colleges in the top 50 of the 2020 U.S. News and World Report Liberal Arts Colleges rankings (N=47). The rationale for different criteria for inclusion across different university types is because these criteria reflected the interest of a foundation that funded the data collection. This article excludes private liberal arts colleges because having a third institutional type would substantially increase article length. The final analysis sample for this article consists of 15 public research universities and 14 private research universities that we believed posted all varieties of off-campus recruiting events on their admissions website. For these universities, we analyze recruiting visits to private high schools that meet the following criteria: enrolls at least 10 12th grade students, is not primarily a virtual school, and is located in the 50 U.S. states, the District of Columbia, or land regulated by the Bureau of Indian Affairs.

Our analysis sample of universities should be considered a convenience sample. Table \ref{tab:sample-characteristics} shows selected characteristics for the universities in our analysis sample. Table \ref{tab:sample-population-characteristics} shows that our analysis samples of public and private universities appear broadly similar to the populations they were drawn from.

INSERT TABLES \ref{tab:sample-characteristics} AND \ref{tab:sample-population-characteristics} ABOUT HERE

Analyses utilized several secondary data sources. The data on university characteristics come from the 2017 Integrated Postsecondary Education Data System (IPEDS) and 2020 Best Colleges ranking by U.S. News \& World Report. For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.\footnote{For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small number of schools.}

\hypertarget{constructing-social-networks}{%
\subsection{Constructing Social Networks}\label{constructing-social-networks}}

A social network consists of a set of actors -- referred to as ``vertices'' -- and the connections -- referred to as ``network ties'' or ``edges'' between these actors. ``One-mode'' networks consist of vertices of a ``type.'' For example, the social network of Facebook consists of users (vertices) who are connected to one another via friendship ties (edges). Similarly, the social network of \(X\) (formerly Twitter) consists of handles (vertices) who are connected to one another by following or being followed (edges).

\textbf{Two-mode networks}. ``Two-mode'' networks consist of vertices associated with one type of actor/entity having connections to vertices of another type of actor/entity (Borgatti, 2008). For example, an actor-movie network -- such as the so-called ``Six Degrees of Kevin Bacon'' -- consists of actors (mode 1) who appear in movies (mode 2), and an actor shares an edge with a movie if the actor appears in the movie. The most commonly analyzed two-mode network in social networks literature is a corporate board-director network (e.g., Davis, Yoo, \& Baker, 2003). These networks consist of directors (mode 1) and organizational boards (mode 2), and a particular director shares an edge with a particular organizational board if they sit on that board.

Data about off-campus recruiting visits from universities to high schools form a two-mode network. The vertices are private high schools (mode 1) and universities (mode 2), and an edge is defined as an off-campus recruiting visit made between the two. High school \(i\) shares an edge with university \(j\) if high school \(i\) receives at least one visit from university \(j\). Visits can only occur between a school-university pair (not a school-school pair or a university-university pair). This (weighted) network can be represented as a school-by-university matrix (e.g., a \(500 \times 40\) matrix if our network contains 500 high schools and 40 universities) in which matrix cell \(a_{i,j}\) identifies the number of visits high school \(i\) received from university \(j\). This can also be visualized by a network graph of interconnected nodes. For example, Appendix Figure \ref{fig:plot-2mode} shows the two-mode network graph of the 29 total universities in our analysis sample and all the private high schools they visited.

\textbf{Transforming two-mode to one-mode}. To reduce complexity, two-mode network graphs are often analyzed as one-mode networks (Borgatti, 2008; Davis et al., 2003). Our two-mode university-school network can be transformed into a one-mode university network in which each vertex is a university. Universities \(i\) and \(j\) share an edge if both universities visit at least one high school in common. Cell \(a_{i,j}\) of the university-by-university matrix \(A\) indicates the number of high schools that both universities visited. Cell \(a_{i,j}\) is referred to as the \emph{weight} of the edge between university \(i\) and university \(j\). For example, if there are 200 private high schools that received a visit from both Notre Dame (university \(i\)) and Villanova (university \(j\)), the weight of the edge between Notre Dame and Villanova is 200 (\(a_{i,j}=200\)). Following this approach we created a one-mode university matrix.

We also created a one-mode high school network in which each vertex is a private high school. Private high schools \(i\) and \(j\) share an edge if at least one university visits both high schools. Cell \(s_{i,j}\) of the school-by-school matrix \(S\) indicates the number of universities that visited both school \(i\) and school \(j\).

\hypertarget{analyses}{%
\subsection{Analyses}\label{analyses}}

Analyses consist of simple descriptive statistics and descriptive social network analyses. All analyses were conducted using \emph{R} and network analyses were conducted using the \emph{igraph} package.

\textbf{RQ1: Degree centrality}. In social network analysis, \emph{centrality} refers to the importance or prominence or ``being in the middle of things'' of an actor/vertex in a social network (Kolaczyk \& Csárdi, 2020). Many alternative measures of centrality have been developed. All measures agree that centrality is an actor/vertex-level construct (e.g., each college in our network will have a centrality value, regardless of which centrality measure we use). However, different measures of centrality are based on different theoretical conceptualizations -- for example, being directly connected to the most actors versus being the intermediary between otherwise disconnected actors -- and are operationalized using different mathematical algorithms.

The simplest measure of centrality, \emph{degree centrality} measures the number of edges directly connected to a vertex. Social network theory conceptualizes degree centrality as a measure of ``local'' centrality, capturing the number of direct connections for each actor/vertex. For each university in our two-mode network, degree centrality is simply the number of different private high schools visited by the college. For each high school in our network, degree centrality is the number of colleges in our network that visited the high school. For our empirical context, we conceive of degree centrality as a measure of the scale of private high school visits by a college, or equivalently, the number of private high schools we observe having a social relation with each college.

Research question 1 states, ``How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?'' We answer this research question by comparing degree centrality across universities, both within university type (public vs.~private) and between university types. In order to discern the relative emphasis on private schools by each university, we also compare the number of recruiting visits to private schools to the number of visits to public schools.

Degree is a limited measure of centrality in that it only identifies direct connections. By contrast, \emph{k-path centrality} measures the extent to which an actor/vertex is indirectly connected to others, \emph{betweenness centrality} measures the extent to which a vertex is an intermediary between otherwise disconnected groups of actors, and \emph{eigenvector centrality} measures the extent to which a vertex is connected to highly-connected others (Kolaczyk \& Csárdi, 2020). Betweenness centrality tends to be relevant for empirical contexts (e.g., which manager gets credit for an idea) where an actor who occupies a position between groups can benefit by being a broker of information/ideas (Burt, 1992; Stone, 2018). By contrast, this chapter is more concerned with whether a particular college tends to have indirect connections with some colleges but not others, and what is the subset of high schools this group of colleges tends to visit. Research question 2, motivated below, explores these ideas.

\textbf{RQ2: Network similarity and community detection}. We are interested in similarities and differences in the recruiting networks of the public research universities and selective private universities in our sample. This interest motivates research question 2, ``to what extent do public research universities and private universities visit overlapping sets of private high schools?''

Following prior scholarship on two-mode networks (Clauset, Newman, \& Moore, 2004; Kolaczyk \& Csárdi, 2020), we address RQ2 by simultaneously graphing the one-mode university network and categorizing universities into distinct communities that have similar recruiting networks. In the resulting graph, vertices (universities) that share many connections are located close together and vertices that are ``central'' -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph. Additionally, cluster analysis is used to identify vertices that share common structure, based purely on patterns of network ties, and vertices are assigned colors based on membership in a particular group.

\textbf{RQ3: Ego networks and homophily}. Because the data structure of networks is complicated, it is often illuminating to analyze ``ego networks'' rather than the entire social network. An ``ego'' is a single ``focal'' node (e.g., The University of Notre Dame). An ego network consists ``of a focal node (`ego') and the nodes to whom ego is directly connected to (these are called `alters') plus the ties, if any, among the alters'' (Borgatti, 1998). An ego network of order 1 consists of the alters that are directly tied to the ego. The order 1 ego network for the University of Notre Dame consists of all private high schools that received at least one visit from Notre Dame. The order 2 ego network consists of all private schools that were visited by Notre Dame and all universities that visited the private high schools visited by Notre Dame. Figure \ref{fig:nd-religion} shows the order 2 ego network for Notre Dame, with vertices colored by religious affiliation. Universities that are closer to Notre Dame visit more private high schools in common.

INSERT FIGURE \ref{fig:nd-religion}

Research question 3 asks, ``How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by private universities?'' To answer this question, we can think of the 15 public research universities and 14 selective private universities, which we can think of as 29 ego networks.

A common finding in social network research is that actors are more likely to form connections with actors who are similar to them (McPherson, Smith-Lovin, \& Cook, 2001). Said differently, ego networks are biased towards ``homophily'' rather than ``heterophily.'' Homophily is the idea that two vertices are more likely to be connected if they have similar characteristics (e.g., two people are more likely to be friends on Facebook if they have similar political ideologies). Heterophily, the opposite of homophily, is when pairs of connected vertices have different characteristics from one another.

In our analyses of recruiting visits from colleges to private high schools, we are interested in the existence of homophily versus heterophily for two reasons. First, prior scholarship suggests that private colleges and private high schools are more likely to have a relationship when they share common ideologies or view themselves as belonging to the same echelon (Khan, 2010, 2011; Stevens, 2007). Second, similar to the colloquialism `you are what you eat,' the characteristics of visited private high schools have subsequent consequences for the enrollment composition of universities.

Our analyses focus on the following private school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size. Decisions about which private school characteristics to analyze were informed by logical argument and by prior research (e.g., Graham, 1999; Khan, 2010; Murnane \& Reardon, 2018; Purdy, 2018; Stevens, 2007). We analyze geographic region because, for most colleges and universities, enrollment demand is likely to be stronger at high schools in the same geographic region, but nationally prestigious colleges and universities may experience high demand throughout the country. We analyze religious affiliation because private colleges are more likely to have a relationship with private high schools with a similar religious affiliation. Although public universities are formally secular, we are interested in whether particular public universities tend to target religiously affiliated private high schools. We analyze academic reputation based on the idea that more highly ranked colleges are likely to target highly ranked private high schools. Racial composition is of substantive interest because the racial composition of visited high schools has consequences for the racial composition of colleges and universities. We would also like to analyze tuition price and household income, but these data are not available for private high schools.

\hypertarget{limitations}{%
\subsection{Limitations}\label{limitations}}

This article faces several limitations. First, our data collection sample consisted of public research-extensive universities as defined by the 2000 Carnegie Classification (N=102) and all private universities in the top 100 of U.S. News and World Report National Universities rankings (N=57). Making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities. The process we used to define the data collection sample yielded a sample of public research universities with lower USNWR rankings than the analysis sample of selective private universities. However, the columns in Table \ref{tab:sample-characteristics} for 25th and 75th percentile SAT score of enrolled freshmen suggest that private universities ranked lower than 75 have test score ranges that are fairly similar to public research universities not ranked in the top 100.

A related limitation is that our analysis sample consists of the subset of universities from the data collection sample that we believe posted all off-campus recruiting visits on their admissions website. This process for defining the analysis sample raises two concerns. First, including universities based on the completeness of recruiting events on their admissions website may yield an analysis sample that conducts more off-campus recruiting visits than the majority of the sample. Second -- and more broadly -- because our analysis sample is a convenience sample rather than a random sample, we cannot make inferences about the underlying populations of interest. This is an external validity concern. That said, we conceive of our research design as an exploratory comparative case study rather than a Large-N research design (Eisenhardt, 1989; Yin, 2009). From this perspective, we identify important variation in recruiting behavior but we cannot make strong claims about the prevalence of observed behaviors in the population. Additionally, because we lack longitudinal data about recruiting visits, we cannot make strong claims about which university is mimicking the recruiting behavior of which other university.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{rq1-scale-of-visits}{%
\subsection{RQ1: Scale of visits}\label{rq1-scale-of-visits}}

Research question 1 asks, ``How does the scale of visits to private high schools by public research universities compare to the scale of visits to private high schools by selective private universities?'' This question can be answered by counting the number of visits to private high schools, which is equivalent to calculating the degree centrality for each university. In addition, we are also interested in the relative scale of visits to private high schools as compared to other types of visits. That is, the number of visits to private high schools as a proportion of all off-campus recruiting visits, or as a proportion of all recruiting visits to high schools.

Appendix Figures \ref{fig:events-count-pubu} and \ref{fig:events-count-privu} show the number of visits by ``type'' (public high school, private high school, community college, other) for public research universities and selective private universities, respectively. On average, the 15 public research universities in our sample conducted 1,568 off-campus recruiting events in 2017, ranging from a low of 914 for the University of Georgia to a high of 4,466 for the University of Alabama. By contrast, the 14 selective private universities in our sample conducted an average of 959 events, ranging from a low of 477 by Case Western Reserve (located in Cleveland, OH) to a high of 1,432 by Marquette University (located in Milwaukee, WI). Across all public research universities, 81.3\% of visits were to a public or private high school, whereas for selective private universities 86.2\% of all visits were to a public or private high school. The lower percentage for public research universities is because many public research universities made a substantial number of visits to community colleges whereas private universities did not.

Figures \ref{fig:events-hs-count-pubu} and \ref{fig:events-hs-count-privu} address RQ1 directly by showing the number of visits to private high schools and public high schools for public research universities (Figure \ref{fig:events-hs-count-pubu}) and selective private universities (Figure \ref{fig:events-hs-count-privu}), with each bar shaded by percent in-state versus out-of-state visits. Only three of the 15 public research universities -- UC-Berkeley, UC-San Diego, and UC-Riverside -- made more in-state than out-of-state total high school visits. Notably, the University of California voluntarily adopted a nonresident enrollment cap in 2017, following pressure from state legislators who had issued a bill to cap nonresident enrollment. Of the 14 selective private universities in our sample, only Baylor University (Waco, TX) made more in-state than out-of-state total high school visits.

INSERT FIGURE \ref{fig:events-hs-count-pubu} AND FIGURE \ref{fig:events-hs-count-privu} ABOUT HERE

With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of 100 visits by UC-Riverside to a high of 1,039 visits by the University of Alabama (which accounted for 21.9\% of all visits to private schools by public research universities in our sample), with the median university, The University of Pittsburgh, making 267 visits. Across all public research universities, 83.2\% of private high school visits were to out-of-state schools while 64.4\% of public high school visits were to out-of-state schools. This result is consistent with the notion that public research universities placed more value on out-of-state private high school students than in-state private high school students because out-of-state students generate substantially more tuition revenue.

For selective private universities, the number of visits to private high schools ranged from a low of 181 by Stevens Institute of Technology to a high of 723 by Notre Dame, with the median universities -- Boston College and Northwestern University -- visiting 349 and 390 private high schools, respectively. Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities. That said, several public research universities in our sample -- University of Colorado-Boulder (402 visits), University of South Carolina (498 visits), and University of Alabama (1,039 visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.

The relative scale of visits to private high schools -- defined as private high school visits as a percentage of all high school visits -- also tended to be substantially higher at selective private universities than at public research universities. Across all selective private universities in our sample, 48.8\% of high school visits were to private high schools, compared to 24.8\% for public research universities. Although, the relative emphasis on private high schools was slightly closer for out-of-state visits; across all selective private universities, 52.9\% of out-of-state high school visits were to private schools, compared to 29.9\% for public research universities.

Even though selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools. Figure \ref{fig:actual-proportional-pubu} (public universities) and Figure \ref{fig:actual-proportional-privu} (private universities) show the actual number of private school visits made compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.\footnote{When calculating the hypothetical proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university. Our rationale for this decision is that it is unhelpful to include schools in states that the university ignored entirely.} Figure \ref{fig:actual-proportional-pubu} shows that the actual number of private school visits exceeded the proportional number of private school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook. For UC-Berkeley, private school visits represented 27\% of all high school visits but would have represented 19\% had UC-Berkeley visited public and private schools at the same rate. For the University of Georgia, which represented the extreme for public universities, private school visits represented 37\% of all high school visits but would have represented 19\% had the university visited public and private schools at the same rate. Figure \ref{fig:actual-proportional-privu} shows that this disparity between actual versus proportional visits was much greater for private universities than public universities. Catholic universities made the most disproportionate number of private high school visits. For Notre Dame, private school visits represented 63\% of actual high school visits but would have represented 18\% of proportional visits.

INSERT FIGURE \ref{fig:actual-proportional-pubu} AND FIGURE \ref{fig:actual-proportional-privu} ABOUT HERE

\hypertarget{rq2-overlapping-network-structure}{%
\subsection{RQ2: Overlapping network structure}\label{rq2-overlapping-network-structure}}

Research question 2 asks, ``To what extent do public research universities and selective private universities visit overlapping sets of private high schools?'' Answering this question requires social network analysis techniques. As described in the methods section, we began by constructing a two-mode social network of visits to private high schools (mode 1) by universities (mode 2). Each university and each private high school is a ``vertex.'' A visit from a university to a school is an ``edge.'' Because large two-mode networks like our school-university network are difficult to visualize, two-mode networks are often analyzed as one-mode networks (Borgatti, 2008; Davis et al., 2003). We transformed our two-mode school-university network into a one-mode university network in which each university is a vertex and two universities share an edge if both universities visited at least one high school in common. The \emph{weight} of an edge indicates the number of high schools that both universities visited. For example, Appendix Table \ref{tab:pubu-count-matrix} shows the matrix of weights for the set of public research universities. We created three separate one-mode university networks: a public university network; a private university network; a public and private university network.

We answer research question 2 by briefly describing tabular representations of overlap within the set of public research universities and overlap within the set of selective private universities. Next, we utilize tabular and graphical representations to describe overlap between the set of public and private universities in our sample.

Table \ref{tab:pubu-percent-matrix} provides a tabular representation of the extent to which public universities visited overlapping sets of private high schools. For each public university (column), each cell of Table \ref{tab:pubu-percent-matrix} shows the number of visited high schools in common with the row university as a percent of the total number of high schools visited by the column university. This indicates the extent to which public universities were competing for students at the same set of private schools. For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7\% of these high schools and CU-Boulder visited 39.1\% of these high schools. Appendix Table \ref{tab:pubu-count-matrix} shows counts rather than percentages.

INSERT TABLE \ref{tab:pubu-percent-matrix} ABOUT HERE

One finding from Table \ref{tab:pubu-percent-matrix} is that the University of Alabama is omnipresent in the set of private high schools visited by most other public research universities in the sample, particularly universities located in the South. For the remaining universities, Table \ref{tab:pubu-percent-matrix} suggests several clusters of universities. For example, UMass-Amherst, SUNY Stony Brook, and Rutgers tend to visit many of the same high schools, as do the University of Arkansas and the University of Kansas. These descriptive findings suggest network structures based on geographic proximity.

Table \ref{tab:privu-percent-matrix} shows overlap in private high schools visited by the selective private universities in our sample. Appendix Table \ref{tab:privu-count-matrix} shows counts. The networks of private universities appear to have more overlap than the network of public research universities. This is demonstrated tabularly by the higher percentages in Table \ref{tab:privu-percent-matrix} compared to Table \ref{tab:pubu-percent-matrix}. Private universities that share a high percentage of visits tend to have the same religious affiliation and/or be located in the same geographic region. For example, the Catholic universities -- Notre Dame, Villanova, Boston College, and Marquette -- seem to visit many private high schools in common.

INSERT TABLE \ref{tab:privu-percent-matrix} ABOUT HERE

Next, we examine overlap in a network that contains the 15 public universities and the 14 private universities. Table \ref{tab:privu-percent-visited-by-pubu-matrix} shows, for each private university, the percentage of schools that were also visited by each public university. This table shows the extent to which public universities were competing at private schools targeted by private universities. For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.2\% of these schools. Similarly, CU-Boulder visited 46.4\% of the 435 schools that TCU visited and 42.4\% of the 377 schools that Northwestern visited. The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass-Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.

INSERT TABLE \ref{tab:privu-percent-visited-by-pubu-matrix} ABOUT HERE

Network graphs are useful for showing which universities have similar private high school recruiting networks. Figure \ref{fig:plot-1mode-u} graphs the one-mode network that consists of all 29 public and private universities in the sample (Appendix Figure \ref{fig:plot-1mode-pubu} graphs the one-mode public university network and Appendix Figure \ref{fig:plot-1mode-privu} graphs the one-mode private university network).

Whether graphing one-mode or two-mode networks, network graphs show vertices as circles and edges as lines connecting pairs of vertices. In Figure \ref{fig:plot-1mode-u}, each circle represents a public or private university and two universities share an edge -- represented by a solid line -- if both universities visited at least one high school in common. The width of the line between two universities indicates the \emph{weight} of the edge, defined as the number of high schools both universities visited in common. Network methods conceive of vertices as repelling one another (Kolaczyk \& Csárdi, 2020), like the ``north pole'' of two magnets. By contrast, edges shared between two vertices pull the two vertices together, like the north pole of one magnet being attracted to the south pole of another magnet. Because of these laws of repulsion and attraction, vertices that share few connections are located far apart while vertices that share many connections are located close together. Additionally, vertices that are highly connected -- many direct and indirect connections to other nodes in the network -- are located near the center of the graph, while vertices that are relatively disconnected are located at the periphery of the graph.

INSERT FIGURE \ref{fig:plot-1mode-u} ABOUT HERE

Universities located near the center of Figure \ref{fig:plot-1mode-u} tended to be universities with the highest degree centrality (i.e., those that visited the most schools). The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), University of South Carolina (396), Northwestern (377), and CU-Boulder (362). Notably, while the majority of universities located near the center of Figure \ref{fig:plot-1mode-u} are private, three are public. The most peripheral universities -- UC-Riverside, SUNY Stony Brook, and University of Nebraska-Lincoln -- are all public.

Proximity of vertices to one another in Figure \ref{fig:plot-1mode-u} appeared to be more connected to religious affiliation, geographic location, and academic reputation. Universities with a common religious affiliation (e.g., Notre Dame, Villanova, Marquette, Boston College) tend to be close to one another. However, the University of Alabama, which visited a high share of Catholic schools and Christian schools is simultaneously close to Catholic universities and to the Christian universities TCU and SMU. Similarly, the University of South Carolina, which visited a relatively high share of Christian schools, is close to TCU and SMU. CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located fairly close to one another in Figure \ref{fig:plot-1mode-u}. As discussed below, these three universities are similar to one another with respect to the geographic location (Figure \ref{fig:region-pubu-privu}), religious affiliation (Figure \ref{fig:religion-pubu-privu}), and academic reputation (Figure \ref{fig:rank-pubu-privu}) of the private high schools they visit.

To better answer research question 2, we augment the network graphs by using cluster analysis methods -- referred to as ``community detection'' in the network analysis literature -- to identify groups of universities that share common network structure. Broadly speaking, the goal of community detection is to identify ``subsets of vertices that demonstrate a `cohesiveness' with respect to the underlying relational patterns'' (Kolaczyk \& Csárdi, 2020, p. 59), where a ``cohesive subset'' means a ``subset of vertices that (i) are well connected among themselves, and at the same time (ii) are relatively well separated from the remaining vertices'' (Kolaczyk \& Csárdi, 2020, p. 59). Therefore, universities in the same cluster have a relatively large number of direct and indirect ties with other universities in the cluster and have relatively few direct and indirect ties with universities in other clusters. We utilize that ``cluster fast and greedy'' approach from Kolaczyk \& Csárdi (2020). This is a variation of hierarchical cluster analysis that starts with a large number of groups and adds individual vertices to a group when doing so contributes to a cohesive subset.

In Figure \ref{fig:plot-1mode-u}, universities are allocated to groups -- indicated by the color of the vertices -- based on the specification that the algorithm should identify four groups (we also experimented with three, five, and six groups). Universities located near the center of Figure \ref{fig:plot-1mode-u} do not all belong to the same cluster and, more broadly, universities located close to one another do not all belong to the same cluster. Starting with the most peripheral group, UC-Riverside is a group unto itself. UC-Riverside only visited 100 private schools and about 70 of these were located in CA. Another group -- Rutgers, Stevens Institute of Technology, UMass-Amherst, SUNY Stony Brook, and Pittsburgh -- largely consists of public universities with strong ties to the Northeast.

The remaining two groups are larger and include universities with greater network centrality. Additionally, these groups both contain a mix of public and private universities. The cluster of 10 universities -- including the University of Alabama, TCU, SMU, Baylor, University of Kansas, and the University of South Carolina -- largely consists of universities in the South, and includes both private Christian universities and public universities. While the federal government defines Nebraska and Kansas as part of the Midwest, Figure \ref{fig:plot-1mode-u} suggests that the visit patterns of the University of Nebraska and the University of Kansas share more in common with Southern universities than they do with other universities in our sample. Finally, the largest and most centrally located cluster contains 13 universities, including Notre Dame, Northwestern, Tulane, CU-Boulder, and UC-Berkeley. Compared to the overall sample, this group largely consists of highly ranked universities, universities located in the Midwest or West, and Catholic universities.

The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and characteristics of the schools they visit -- of geographic location, religious affiliation, academic reputation, and also institutional control. Considering the identification of clusters, centrality, and proximity of vertices, we find substantial overlap in the sets of private schools visited by public universities and private universities. This overlap does not suggest uniformity across public and private universities. Rather, there exist several groups of public and private universities -- which can be defined by cluster analysis or more loosely by proximity -- that have more in common with one another than they do with other universities of the same institutional control.

\hypertarget{rq3-characteristics-of-visited-schools}{%
\subsection{RQ3: Characteristics of visited schools}\label{rq3-characteristics-of-visited-schools}}

Figures \ref{fig:region-pubu-privu} through \ref{fig:south-race-privu-privhs-pubhs} address research question 3, ``How do the characteristics of private high schools visited by public research universities compare to the characteristics of private high schools visited by selective private universities?'' Additionally, Appendix Figures \ref{fig:enroll-pubu-privu} and \ref{fig:enroll-pubu-privhs-pubhs} show the 12th grade enrollment size of visited high schools.

Figure \ref{fig:region-pubu-privu} shows the broad geographic region -- Northeast, Midwest, South, and West -- of visited private high schools, separately for public research universities (top panel) and selective private universities (bottom panel). Scholarship on the relationship between geographic proximity and student demand tends to find that nationally prestigious universities enjoy strong demand across the nation, while less prestigious universities rely primarily on demand from students located nearby (e.g., Hoxby, 1997). The visit patterns for private universities are consistent with this finding; less prestigious universities tended to focus on private high schools in their home region, while more prestigious universities tended to visit many private high schools outside their home region. Similarly, scholarship on student demand for out-of-state public universities finds that most public universities rely on demand from out-of-state students living in nearby states (Mak \& Moncur, 2003; Mixon \& Hsing, 1994; Zhang, 2007). Most public research universities in our sample visited a disproportionate number of private high schools in their home geographic region. UC-Berkeley and CU-Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.

INSERT FIGURE \ref{fig:region-pubu-privu} ABOUT HERE

In the universe of all private high schools (top row of Figure \ref{fig:region-pubu-privu}), there are more schools located in the South than any other geographic region, consistent with the finding from Murnane \& Reardon (2018) about the long-term growth in private school enrollment in the South. Universities not located in the South tended to visit more private high schools in the South than any other region, except their home region. This finding emerged for both the public universities and private universities in our sample.

Figure \ref{fig:religion-pubu-privu} shows the religious affiliation -- Catholic, Christian, Nonsectarian, and Other -- of visited private high schools. The results for selective private universities (bottom panel) follow our expectations: Nonsectarian universities tended to visit a higher proportion of nonsectarian private high schools; Catholic universities visited a higher proportion of Catholic high schools; and Christian universities tended to visit a relatively higher share of Christian high schools.

INSERT FIGURE \ref{fig:religion-pubu-privu} ABOUT HERE

Results for public research universities (top panel) are more interesting. Despite being nonsectarian, the majority of public research universities visited a high share of religiously affiliated private high schools, particularly Catholic schools. Surprisingly, Catholic schools represented at least 40\% of private high school visits for 10 of the 15 public research universities in our sample. By contrast, Catholic schools represented at least 40\% of visits for only 6 of the 14 selective private universities in our sample (the four Catholic universities and also Texas Christian University and Stevens Institute of Technology). For public research universities, the emphasis on visiting Catholic and Christian high schools rather than nonsectarian private high schools tended to be stronger at less prestigious institutions.

Figure \ref{fig:rank-pubu-privu} shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools. For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated ``A+'' whereas less prestigious universities visited a higher share of private high schools rated ``A'' or ``A- or below.'' Notre Dame University is a notable exception to this pattern.\footnote{A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.}

INSERT FIGURE \ref{fig:rank-pubu-privu} ABOUT HERE

A similar pattern emerged for the public research universities in our sample; more highly ranked universities tended to visit a higher share of highly rated private high schools than lower ranked universities. In comparison to the private universities in our sample, the public universities in our sample tended to visit a higher share of private high schools that were not highly rated. To a great extent, this finding is merely a consequence of our sampling strategy; we attempted to collect recruiting visit data from all public research universities but we only collected recruiting visit data from private universities ranked in the top 100 of U.S. News and World Report. That said, the finding that public research universities visited a large share of low-rated private high schools is consistent with the idea that many public research universities visit private high schools in search of full-pay students rather than high-achieving students.

Figures \ref{fig:race-pubu-privhs-pubhs} and \ref{fig:race-privu-privhs-pubhs} show the percentage of 12th graders who identify as Black, Latinx, or Native at visited high schools. Consistent with Murnane \& Reardon (2018), most private high schools enroll relatively few students from historically underrepresented race/ethnicity groups. The top row in the top panel of Figure \ref{fig:race-pubu-privhs-pubhs} shows that the sum of Black, Latinx, and Native students comprise less than 20\% of enrolled students in over 65\% of schools in our private high school universe. At public high schools (bottom panel), Black/Latinx/Native students comprise less than 20\% of enrolled students at around 40\% of all public schools. However, most public research universities (Figure \ref{fig:actual-proportional-pubu}) and all selective private universities (Figure \ref{fig:actual-proportional-privu}) visited a disproportionate number of private high schools compared to public high schools. Even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled. Therefore, a disproportionate emphasis on visits to public schools may shift the racial composition of public universities away from Black/Latinx/Native students.

INSERT FIGURES \ref{fig:race-pubu-privhs-pubhs} AND \ref{fig:race-privu-privhs-pubhs} ABOUT HERE

Figure \ref{fig:race-pubu-privhs-pubhs} focuses on public universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel). For all public universities, the racial composition of visited public schools contains a much higher share of Black/Latinx/Native students than the racial composition of visited private schools. Figure \ref{fig:race-pubu-privhs-pubhs} shows that for most universities in our sample, the set of visited private high schools enrolled \emph{fewer} Black/Latinx/Native students than the universe of private high schools. For public universities, exceptions to this finding were UC-San Diego, UC-Riverside, and -- to a lesser extent -- SUNY Stony Brook.

Figure \ref{fig:race-privu-privhs-pubhs} focuses on selective private universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel). Results are very similar to those of public universities. Visited private schools enrolled a much lower share of Black/Latinx/Native students than visited public schools. For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75\% of visited private schools enrolled less than 20\% Black/Latinx/Native students.

Finally, Figure \ref{fig:south-race-pubu-privhs-pubhs} examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample. Figure \ref{fig:south-race-privu-privhs-pubhs} does the same for selective private universities. These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest (Murnane \& Reardon, 2018). For public research universities, Figure \ref{fig:south-race-pubu-privhs-pubhs} shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools. This was true for all universities in our sample that visited a substantial number of schools in the South, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati. Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits. Results for private universities in Figure \ref{fig:south-race-privu-privhs-pubhs} are very similar, with Emory, Northwestern, and Case Western visiting private schools with a low share of Black/Latinx/Native students. Appendix Figures \ref{fig:south-race-comp-pubu-privhs-pubhs} and \ref{fig:south-race-comp-privu-privhs-pubhs} show the full racial composition of visited public and private schools in the South. For most universities that made a substantial number of visits in the South, white students comprised around 70\% of total enrollment at visited private schools compared to around 40\% at visited public schools.

INSERT FIGURES \ref{fig:south-race-pubu-privhs-pubhs} AND \ref{fig:south-race-privu-privhs-pubhs} ABOUT HERE

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{summary}{%
\subsection{Summary}\label{summary}}

This chapter analyzes recruiting visits to private high schools, which were made during the 2017 calendar year, for a convenience sample of 15 public research universities and 14 private universities ranked in the top 100 of U.S. News and World Report National Universities rankings. Our goal was to learn about public research universities by analyzing their behavior and comparing their behavior to that of selective private universities.

Research question 1 asks about the scale of visits to private high schools. All private universities in our sample made a disproportionate number of visits to private high schools (Figure \ref{fig:actual-proportional-privu}) and, for about half of these universities, visits to private high schools represented about 50\% or more of all high school visits. For most public research universities in our sample, the scale and relative scale -- as a percentage of all HS visits -- of visits to private high schools were smaller than that of most selective private universities. However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \ref{fig:actual-proportional-pubu}) and the vast majority of these private school visits were to out-of-state private schools. Additionally, several public research universities -- University of Alabama, CU-Boulder, University of South Carolina -- visited private high schools at a scale that exceeded most private universities.

Research question 2 asks about overlap in the private school recruiting networks of public and private universities. We observed substantial overlap and variation in the recruiting networks of public universities. For example, the recruiting networks of the University of Arkansas and the University of Kansas share substantial overlap and are very different from the recruiting networks of UMass-Amherst and Rutgers, which share substantial overlap with one another. Amongst the network of public and private universities, we observe substantial overlap and variation in recruiting networks. Figure \ref{fig:plot-1mode-u} shows that three clusters emerge -- each containing some mix of public and private universities. The universities within a cluster have some overlap in the kinds of schools visited (e.g., TCU and University of South Carolina), but also share substantial overlap with particular universities in different clusters (e.g., Tufts and University of Pittsburgh). Whether we are categorizing universities by cluster analysis or by proximity on the network graph, we observe several different subsets of universities. Each of these subsets is associated with a different approach to private school visits and -- with the exception of a few universities like UC-Riverside and SUNY Stony Brook that don't play the private school game -- each of these subsets contained both public and private universities.

Research question 3 asks about the characteristics of visited private high schools. We analyzed geographic region, religious affiliation, high school ranking, 12th grade enrollment, and racial composition. Both public and private universities in our sample tended to make a disproportionate number of visits in their home geographic region, with highly ranked universities making more visits to schools in other regions. The majority of universities -- even those located outside the South -- visited a large number of private schools located in the South. Unsurprisingly, sectarian private universities made a large share of visits to private high schools of a similar religious affiliation. Given that public universities are nonsectarian organizations, a surprising finding is that the majority of public universities in our sample made a large share of visits to Catholic or Christian private schools.

With the exception of UC-Berkeley and UC-San Diego, the average academic rating of private schools visited by public universities was lower than the rating of those visited by most private universities. This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked in the top 100 National University by U.S. News. Nevertheless, the large number of visits to low-rated private schools by public universities, combined with the fact that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private schools primarily in search of full-pay students rather than academic superstars.

Across the universe of private high schools, most schools enroll relatively few students who identify as Black, Latinx, or Native. For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools. By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native. This is true of the visits to schools in the South as well.

\hypertarget{implications-for-scholarship}{%
\subsection{Implications for Scholarship}\label{implications-for-scholarship}}

This study engages with two, previously disconnected literatures. Scholarship on nonresident enrollment observes that many public research universities began growing nonresident enrollment following declines in state appropriations (Author, XXXXb). Given that nonresident tuition price is often two- to three-times resident price, it is unsurprising that nonresident students tend to be more affluent than resident students, are less likely to be first-generation students, and are less likely to be Black or Latinx (Author, XXXXc). Public research universities recruit nonresident students using institutional financial aid packages (Leeds \& DesJardins, 2015) and through recruiting interventions that target earlier stages in the enrollment funnel. Using nearly the same sample of 15 public research universities used in this study, Author (XXXXa) found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools. Public research universities have a financial incentive to target private school students, who tend to come from affluent households that are able to pay nonresident tuition price without need-based aid. This study extends the literature on nonresident students by analyzing the scale of visits to private schools, the overlap and divergence in recruiting networks between public and private universities, and the characteristics of visited private schools.

We also engage with scholarship on linkages between private schools and private universities, a linkage that sociologists have observed for many decades. Private school students comprise a disproportionate share of enrollment at selective private universities (Author calculations based on HSLS:2009). Practically, these linkages exist because private schools want to send their students to ``good'' universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profiles and/or extracurricular activities (Stevens, 2007). Prior research has often focused on linkages between elite private schools and elite universities (Chetty et al., 2023; Khan, 2011; Persell \& Cookson, 1985). Whereas elite universities (e.g., Princeton, Stanford) experience strong student demand based on reputation, merely selective private universities must incite demand by expending resources on recruiting. Prior research has not systematically analyzed connections between private schools and private universities that are selective, but not elite. Therefore, this study extends the literature by investigating private school visits for a sample of 14 selective private universities that exhibit variation in geographic location, religious affiliation, and ranking.

Our more important scholarly contribution is showing that these two literatures are both parts of a broader story about the changing nature of competition for students from privileged schools and communities. Selective private universities have been recruiting heavily from private schools for a long time (Falsey \& Heyns, 1984; Persell \& Cookson, 1985; Stevens, 2007). By contrast, the pursuit of out-of-state private school students by public research universities is a relatively new phenomenon and represents competition in the traditional hunting grounds of selective private universities.

Our analyses shed light on the nature of this competition. When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large. Several public universities seem to be competing directly for students targeted by a particular private university. For example, UC-Berkeley visited 27.9\% of the schools visited by Northwestern, 28.9\% of the schools visited by Tufts, and 27.8\% of the schools visited by Emory (Table \ref{tab:privu-percent-visited-by-pubu-matrix}). We reason UC-Berkeley is competing directly for students because all four universities are in the same broad echelon of prestige. Other potential examples of direct competition include the University of Georgia targeting schools visited by Emory, SMU, TCU, and Tulane, or the University of Arkansas targeting schools visited by Baylor.

However, public universities that made the greatest number of private school visits seemed to be targeting the lower-achieving students at private schools targeted by particular private universities. For example, the University of Alabama visited 52.2\% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools. Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame. Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievements, and want to attend a football powerhouse. Additionally, CU-Boulder visited 42.4\% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern. Similarly, the University of South Carolina competes heavily at schools targeted by Emory, SMU, TCU, and Tulane.

While public universities playing the private school game differ in terms of the set of schools they target, they all seem to be targeting schools that enroll mostly affluent students and few students who identify as Black, Latinx, or Native. To the extent that these recruiting efforts yield dividends in terms of incoming freshmen, playing the private school game is likely to change the enrollment composition of public research universities in ways that run contrary to racial and socioeconomic diversity.

\hypertarget{implications-for-practice}{%
\subsection{Implications for Practice}\label{implications-for-practice}}

Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the Covid pandemic. Ruffalo Noel-Levitz (2020a) found that ``travel'' was the top-ranked marketing/recruiting expenditure item for both public universities and private universities. During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events (Ruffalo Noel-Levitz, 2020b). Admissions counselors are now traveling again. Ruffalo Noel-Levitz (2022a) found that travel was the fifth-ranked expenditure item for public universities and the second-ranked expenditure item for private universities. When asked about areas of future expenditure growth, travel was the top-ranked item for public universities and the second-ranked item for private universities (Ruffalo Noel-Levitz, 2022a), suggesting that universities are increasing travel following the decline of the pandemic.

The EAB \& NACAC (2023) survey of high school counselors asked, ``How do you prefer to receive information from colleges?'' High school visits by college representatives was by far the highest rated ``channel'' for private school counselors and was also the highest rated channel for public school counselors. By contrast, virtual visits by admissions representatives received low ratings by high school guidance counselors. Finally, Ruffalo Noel-Levitz (2022b) asked universities to rank the most effective ``outreach strategies for high school counselors.'' ``Calling after visits'' was deemed effective for 97\% of private universities (the top strategy) and was deemed effective by 88\% of public universities. What insights do we glean from these market research findings? In the era of mass marketing and data science, the pursuit of traditional college students from privileged schools and communities is still a hand-to-hand business, and off-campus recruiting visits remain a vital means of recruiting these students.

Considering the practical importance of off-campus recruiting visits, what are the practical implications of our research? Prior scholarly and market research shows that students are sensitive to recruiting interventions, including recruiting visits (Holland, 2019; Ruffalo Noel-Levitz, 2018). Consequently, the racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university. Our research on visits to public high schools (Author, XXXXa) and this study on visits to private schools find that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities. Some universities may publicly proclaim a commitment to social mobility and privately pursue an intentional recruiting strategy that targets affluent schools and communities. We offer practical guidance for universities that may be unintentionally implementing a recruiting strategy that privileges the privileged.

Several studies suggest that universities -- particularly elite private universities -- pursue racial diversity by recruiting non-white students who attend predominantly white private high schools (e.g., Jack, 2019). Additionally, scholarship that engages with enrollment in private schools by Black students suggests that many high-income Black families began sending their children to elite, predominantly white private schools once these schools were willing to enroll Black students (Graham, 1999). Therefore, universities may visit predominantly white private high schools in search of non-white students. One concern about this practice is that non-white students at elite private schools may be in high demand by many universities, but similarly achieving non-white students at predominantly non-white public schools might be ignored.

In the aftermath of the Supreme Court decision on race-conscious admissions, U.S. Department of Education (2023) published a report titled \emph{Strategies for Increasing Diversity and Opportunity in Higher Education.} The report recommended that universities diversify the set of high schools they recruit from:

\begin{quote}
\begin{quote}
Rather than recruiting primarily from private and public high schools composed of predominantly high-income students, institutions can expand and prioritize their outreach to high schools with substantial populations of low-income students and students of color. As part of expanding outreach, institutions can assign admissions recruiters to high schools from which they have not typically recruited to provide equal opportunity for all students.
\end{quote}
\end{quote}

We suspect that many universities may have incomplete knowledge about which schools they recruit from and how these schools compare to those they do not recruit from. Our rationale for this statement is that employee turnover in the enrollment management profession is quite high (Hoover, 2023) and many universities rely on expertise from third-party enrollment management consultancies (Author, XXXXe). Consistent with this idea, when issued public records requests to collect data on ``student list'' purchases from about 100 public universities (Author, XXXXf), we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.

For university leaders concerned about racial and socioeconomic equity in college access, we recommend conducting an internal audit of recruiting practices. How do the high schools and community colleges they visit differ racially, socioeconomically, and geographically from those they do not visit? How do the student list prospect profiles they purchase differ racially, socioeconomically, and geographically from those they do not purchase? We also recommend that students, faculty, and university stakeholders ask this question of the university president. It may be that the president is unaware and must ask the enrollment management office, which may begin a useful conversation. While universities may be aware of the composition of the schools they visit and the prospect profiles they purchase, we suspect that they may be less aware of how the composition of targeted schools/communities/students compares to the composition of not targeted schools/communities/students. If internal equity audits point to areas of inequity in recruiting behavior, university stakeholders can begin a discussion of how to address this issue.

\hypertarget{conflict-of-interest-statement}{%
\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}

All authors declare that they have no conflicts of interest.

\singlespacing

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-RN4758}{}}%
Author. (XXXXa).

\leavevmode\vadjust pre{\hypertarget{ref-list_biz}{}}%
Author. (XXXXe).

\leavevmode\vadjust pre{\hypertarget{ref-list_empirics}{}}%
Author. (XXXXf).

\leavevmode\vadjust pre{\hypertarget{ref-RN3753}{}}%
Author. (XXXXb).

\leavevmode\vadjust pre{\hypertarget{ref-RN3685}{}}%
Author. (XXXXc).

\leavevmode\vadjust pre{\hypertarget{ref-RN4290}{}}%
Author. (XXXXd).

\leavevmode\vadjust pre{\hypertarget{ref-RN4953}{}}%
Borgatti, S. P. (1998). Ego networks. Retrieved from \url{http://www.analytictech.com/networks/egonet.htm}

\leavevmode\vadjust pre{\hypertarget{ref-RN2457}{}}%
Borgatti, S. P. (2008). 2-mode concepts in social network analysis. In \emph{Encyclopedia of complexity and system science}.

\leavevmode\vadjust pre{\hypertarget{ref-RN786}{}}%
Bryk, A. S., Lee, V. E., \& Holland, P. B. (1993). \emph{Catholic schools and the common good}. Cambridge: Harvard University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN975}{}}%
Burt, R. S. (1992). \emph{Structural holes: The social structure of competition}. Cambridge, MA: Harvard University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN2772}{}}%
Cheslock, J. J., \& Kroc, R. (2012). Managing college enrollments. In R. Howard, B. Knight, \& G. McLaughlin (Eds.), \emph{The handbook for institutional researchers} (pp. 221--236). San Francisco, CA: Jossey-Bass.

\leavevmode\vadjust pre{\hypertarget{ref-RN4935}{}}%
Chetty, R., Deming, D. J., \& Friedman, J. N. (2023). Diversifying society's leaders? The causal effects of admission to highly selective private colleges. \emph{National Bureau of Economic Research Working Paper Series}, \emph{No. 31492}. \url{https://doi.org/10.3386/w31492}

\leavevmode\vadjust pre{\hypertarget{ref-RN4599}{}}%
Clark, D., \& Del Bono, E. (2016). The long-run effects of attending an elite school: Evidence from the united kingdom. \emph{American Economic Journal-Applied Economics}, \emph{8}(1), 150--176. \url{https://doi.org/10.1257/app.20130505}

\leavevmode\vadjust pre{\hypertarget{ref-RN4677}{}}%
Clauset, A., Newman, M. E. J., \& Moore, C. (2004). Finding community structure in very large networks. \emph{Physical Review E}, \emph{70}(6). \url{https://doi.org/10.1103/PhysRevE.70.066111}

\leavevmode\vadjust pre{\hypertarget{ref-RN4937}{}}%
Coleman, J. S., \& Hoffer, T. (1987). \emph{Public and private high schools: The impact of communities} (pp. xxviii, 254 p.). New York: Basic Books.

\leavevmode\vadjust pre{\hypertarget{ref-RN4647}{}}%
Cookson, P. W., \& Persell, C. H. (1985). \emph{Preparing for power : America's elite boarding schools} (pp. x, 260 p.). New York: Basic Books.

\leavevmode\vadjust pre{\hypertarget{ref-RN1791}{}}%
Curs, B. R., \& Singell, L. D. (2002). An analysis of the application and enrollment processes for in-state and out-of-state students at a large public university. \emph{Economics of Education Review}, \emph{21}(2), 111--124. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000173740100002}{\textless Go to ISI\textgreater://000173740100002}

\leavevmode\vadjust pre{\hypertarget{ref-RN2287}{}}%
Curs, B. R., \& Singell, L. D. (2010). Aim high or go low? Pricing strategies and enrollment effects when the net price elasticity varis with need and ability. \emph{Journal of Higher Education}, \emph{81}(4), 515--543.

\leavevmode\vadjust pre{\hypertarget{ref-RN4663}{}}%
Davis, G. F., Yoo, M., \& Baker, W. E. (2003). The small world of the american corporate elite, 1982-2001. \emph{Strategic Organization}, \emph{1}(3), 301--326. \url{https://doi.org/10.1177/14761270030013002}

\leavevmode\vadjust pre{\hypertarget{ref-RN2271}{}}%
Delaney, J. A., \& Doyle, W. R. (2011). State spending on higher education: Testing the balance wheel over time. \emph{Journal of Education Finance}, \emph{36}(4), 343--368. Journal Article.

\leavevmode\vadjust pre{\hypertarget{ref-RN3524}{}}%
DesJardins, S. L., \& Bell, A. (2006). Using economic concepts to inform enrollment management. \emph{New Directions for Institutional Research}, \emph{2006}(132), 59--74. \url{https://doi.org/10.1002/ir.196}

\leavevmode\vadjust pre{\hypertarget{ref-eab_nacac_counselor_2023}{}}%
EAB, \& NACAC. (2023). \emph{The counselor perspective: Insights from EAB's survey of high school counselors}. EAB. Retrieved from \url{https://www.nacacnet.org/wp-content/uploads/The-Counselor-Perspective-EAB-Survey.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-RN4936}{}}%
Eide, E. R., Goldhaber, D. D., \& Showalter, M. H. (2004). Does catholic high school attendance lead to attendance at a more selective college? \emph{Social Science Quarterly}, \emph{85}(5), 1335--1352. \url{https://doi.org/10.1111/j.0038-4941.2004.00279.x}

\leavevmode\vadjust pre{\hypertarget{ref-RN4116}{}}%
Eisenhardt, K. M. (1989). Building theories from case study research. \emph{Academy of Management Review}, \emph{14}(4), 532--550. \url{https://doi.org/10.2307/258557}

\leavevmode\vadjust pre{\hypertarget{ref-RN4642}{}}%
Falsey, B., \& Heyns, B. (1984). The college channel: Private and public schools reconsidered. \emph{Sociology of Education}, \emph{57}(2), 111--122. \url{https://doi.org/10.2307/2112633}

\leavevmode\vadjust pre{\hypertarget{ref-RN4724}{}}%
Graham, L. (1999). \emph{Our kind of people: Inside america's black upper class} (1st ed., pp. xii, 418 pages, 16 unnumbered pages of plates). New York: HarperCollins.

\leavevmode\vadjust pre{\hypertarget{ref-RN4625}{}}%
Hill, L. D. (2008). School strategies and the "college-linking" process: Reconsidering the effects of high schools on college enrollment. \emph{Sociology of Education}, \emph{81}(1), 53--76. Journal Article. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://WOS:000256634400003}{\textless Go to ISI\textgreater://WOS:000256634400003}

\leavevmode\vadjust pre{\hypertarget{ref-RN4324}{}}%
Holland, M. M. (2019). \emph{Divergent paths to college: Race, class, and inequality in high schools}. Rutgers University Press. \url{https://doi.org/10.36019/9780813590288}

\leavevmode\vadjust pre{\hypertarget{ref-em_burnout_hoover}{}}%
Hoover, E. (2023). A profession on the edge: Why enrollment leaders are wearing down, burning out, and leaving jobs they once loved. \emph{The Chronicle of Higher Education}, (April 5). Retrieved from \url{https://www.chronicle.com/article/a-profession-on-the-edge}

\leavevmode\vadjust pre{\hypertarget{ref-RN2133}{}}%
Hoxby, C. M. (1997). \emph{How the changing market structure of u.s. Higher education explains college tuition} (No. Working Paper 6323). National Bureau of Economic Research. Retrieved from \url{http://www.nber.org/papers/W6323.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-RN4495}{}}%
Jack, A. A. (2019). \emph{The privileged poor: How elite colleges are failing disadvantaged students} (p. 276). Cambridge, Massachusetts: Harvard University Press,. Retrieved from \href{Restricted\%20to\%20UCLA.\%20Limited\%20to\%20three\%20concurrent\%20users.\%20Try\%20again\%20later\%20if\%20unavailable.\%20http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&__char_set=utf8\&isbn=9780674239647}{Restricted to UCLA. Limited to three concurrent users. Try again later if unavailable. http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&\_\_char\_set=utf8\&isbn=9780674239647}

\leavevmode\vadjust pre{\hypertarget{ref-RN4596}{}}%
Jerrim, J., Parker, P. D., Chmielewski, A. K., \& Anders, J. (2016). Private schooling, educational transitions, and early labour market outcomes: Evidence from three anglophone countries. \emph{European Sociological Review}, \emph{32}(2), 280--294. \url{https://doi.org/10.1093/esr/jcv098}

\leavevmode\vadjust pre{\hypertarget{ref-RN4321}{}}%
Khan, S. R. (2010). \emph{Getting in: How elite schools play the college game} (pp. 97--113). Rowman \& Littlefield.

\leavevmode\vadjust pre{\hypertarget{ref-RN4407}{}}%
Khan, S. R. (2011). \emph{Privilege: The making of an adolescent elite at st. Paul's school} (pp. 232 pages). Princeton, N.J.: Princeton University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN3522}{}}%
Killgore, L. (2009). Merit and competition in selective college admissions. \emph{Review of Higher Education}, \emph{32}(4), 469--488. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://WOS:000266737500002}{\textless Go to ISI\textgreater://WOS:000266737500002}

\leavevmode\vadjust pre{\hypertarget{ref-RN1565}{}}%
Kingston, P. W., \& Lewis, L. S. (1990). \emph{The high-status track: Studies of elite schools and stratification} (pp. xxxiv, 261 p.). Albany: State University of New York Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN4614}{}}%
Klugman, J. (2012). How resource inequalities among high schools reproduce class advantages in college destinations. \emph{Research in Higher Education}, \emph{53}(8), 803--830. Journal Article. \url{https://doi.org/10.1007/s11162-012-9261-8}

\leavevmode\vadjust pre{\hypertarget{ref-RN4725}{}}%
Kolaczyk, E. D., \& Csárdi, G. (2020). \emph{Statistical analysis of network data with r} (2nd ed, p. 235). Cham: Springer,. \url{https://doi.org/10.1007/978-3-030-44129-6}

\leavevmode\vadjust pre{\hypertarget{ref-RN3762}{}}%
Leeds, D. M., \& DesJardins, S. L. (2015). The effect of merit aid on enrollment: A regression discontinuity analysis of iowa's national scholars award. \emph{Research in Higher Education}, \emph{56}(7), 471--495. \url{https://doi.org/10.1007/s11162-014-9359-2}

\leavevmode\vadjust pre{\hypertarget{ref-RN4643}{}}%
Levine, S. B. (1980). The rise of american boarding schools and the development of a national upper-class. \emph{Social Problems}, \emph{28}(1), 63--94. \url{https://doi.org/10.1525/sp.1980.28.1.03a00050}

\leavevmode\vadjust pre{\hypertarget{ref-RN2546}{}}%
Mak, J., \& Moncur, J. E. T. (2003). Interstate migration of college freshmen. \emph{Annals of Regional Science}, \emph{37}(4), 603--612. \url{https://doi.org/10.1007/s00168-003-0130-4}

\leavevmode\vadjust pre{\hypertarget{ref-RN1722}{}}%
McPherson, M., Smith-Lovin, L., \& Cook, J. M. (2001). Birds of a feather: Homophily in social networks. \emph{Annual Review of Sociology}, \emph{27}, 415--444. Journal Article. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000170748100017}{\textless Go to ISI\textgreater://000170748100017}

\leavevmode\vadjust pre{\hypertarget{ref-RN513}{}}%
Meyer, J. W., \& Rowan, B. (1977). Institutionalized organizations: Formal structure as myth and ceremony. \emph{The American Journal of Sociology}, \emph{83}(2), 340--363.

\leavevmode\vadjust pre{\hypertarget{ref-RN2536}{}}%
Mixon, F. G., \& Hsing, Y. (1994). The determinants of out-of-state enrollments in higher education: A tobit analysis. \emph{Economics of Education Review}, \emph{13}(4), 295--335.

\leavevmode\vadjust pre{\hypertarget{ref-RN4504}{}}%
Murnane, R. J., \& Reardon, S. F. (2018). Long-term trends in private school enrollments by family income. \emph{AERA Open}, \emph{4}(1), 1--24. \url{https://doi.org/10.1177/2332858417751355}

\leavevmode\vadjust pre{\hypertarget{ref-RN4938}{}}%
Neal, D. (1997). The effects of catholic secondary schooling on educational achievement. \emph{Journal of Labor Economics}, \emph{15}(1), 98--123. \url{https://doi.org/10.1086/209848}

\leavevmode\vadjust pre{\hypertarget{ref-RN4634}{}}%
Persell, C. H., Catsambis, S., \& Cookson, P. W. (1992). Differential asset conversion: Class and gendered pathways to selective colleges. \emph{Sociology of Education}, \emph{65}(3), 208--225. \url{https://doi.org/10.2307/2112809}

\leavevmode\vadjust pre{\hypertarget{ref-RN4640}{}}%
Persell, C. H., \& Cookson, P. W. (1985). Chartering and bartering: Elite education and social reproduction. \emph{Social Problems}, \emph{33}(2), 114--129. \url{https://doi.org/10.1525/sp.1985.33.2.03a00030}

\leavevmode\vadjust pre{\hypertarget{ref-RN959}{}}%
Pfeffer, J., \& Salancik, G. R. (1978). \emph{The external control of organizations: A resource dependence perspective} (pp. xiii, 300 p.). New York: Harper \& Row.

\leavevmode\vadjust pre{\hypertarget{ref-RN1577}{}}%
Priest, D. M., \& St. John, E. P. (2006). \emph{Privatization and public universities} (pp. 299 p.). Bloomington: Indiana University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN4588}{}}%
Purdy, M. A. (2018). \emph{Transforming the elite: Black students and the desegregation of private schools} (pp. 1--243). \url{https://doi.org/10.5149/northcarolina/9781469643496.001.0001}

\leavevmode\vadjust pre{\hypertarget{ref-RN4589}{}}%
Reeves, A., Friedman, S., Rahal, C., \& Flemmen, M. (2017). The decline and persistence of the old boy: Private schools and elite recruitment 1897 to 2016. \emph{American Sociological Review}, \emph{82}(6), 1139--1166. \url{https://doi.org/10.1177/0003122417735742}

\leavevmode\vadjust pre{\hypertarget{ref-RN4911}{}}%
Rivard, R. (2013). Micro-targeting students: Increasingly sophisticated data slicing tools are changing student recruitment. Who benefits? \emph{InsideHigherEd}, (Oct 24). Retrieved from \url{https://www.insidehighered.com/news/2013/10/24/political-campaign-style-targeting-comes-student-search?width=775\&height=500\&iframe=true}

\leavevmode\vadjust pre{\hypertarget{ref-RN3608}{}}%
Rudolph, F. (1962). \emph{The american college and university: A history} (1st ed., pp. 516 p.). New York: Alfred A. Knopf.

\leavevmode\vadjust pre{\hypertarget{ref-RN4402}{}}%
Ruffalo Noel-Levitz. (2018). \emph{2018 marketing and student recruitment report of effective practices}. Ruffalo Noel-Levitz. Retrieved from \url{http://learn.ruffalonl.com/rs/395-EOG-977/images/RNL_2018_Student_Recruitment_Marketing_Report_EM-19.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-RN4664}{}}%
Ruffalo Noel-Levitz. (2020a). \emph{2020 cost of recruiting an undergraduate student report} (Report). Ruffalo Noel-Levitz. Retrieved from \url{https://learn.ruffalonl.com/rs/395-EOG-977/images/2020_CostRecruiting_Report.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-parents_covid_rnl}{}}%
Ruffalo Noel-Levitz. (2020b). \emph{College planning and the perceptions of parents after covid-19}. Ruffalo Noel-Levitz. Retrieved from \url{https://www.ruffalonl.com/thank-you/download-college-planning-and-the-perceptions-of-parents-after-covid-19/}

\leavevmode\vadjust pre{\hypertarget{ref-RN4896}{}}%
Ruffalo Noel-Levitz. (2022a). \emph{2022 cost of recruiting an undergraduate student report}. Ruffalo Noel-Levitz. Retrieved from \url{https://www.ruffalonl.com/thank-you/download-the-2022-cost-of-recruiting-an-undergraduate-student-report/}

\leavevmode\vadjust pre{\hypertarget{ref-RN4895}{}}%
Ruffalo Noel-Levitz. (2022b). \emph{2022 marketing and recruitment practices for undergraduate students report}. Ruffalo Noel-Levitz. Retrieved from \url{https://www.ruffalonl.com/papers-research-higher-education-fundraising/marketing-and-recruitment-practices-for-undergraduate-students/}

\leavevmode\vadjust pre{\hypertarget{ref-RN4934}{}}%
Salazar, K. G. (2022). Recruitment redlining by public research universities in the los angeles and dallas metropolitan areas. \emph{The Journal of Higher Education}, \emph{93}(4), 585--621. \url{https://doi.org/10.1080/00221546.2021.2004811}

\leavevmode\vadjust pre{\hypertarget{ref-RN1118}{}}%
Slaughter, S., \& Rhoades, G. (2004). \emph{Academic capitalism and the new economy} (pp. xii, 370 p.). Baltimore: Johns Hopkins University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN3519}{}}%
Stevens, M. L. (2007). \emph{Creating a class: College admissions and the education of elites} (pp. 308 p.). Cambridge, MA: Harvard University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN4648}{}}%
Stone, T. (2018). Social network theory: A literature review for understanding innovation programs. Retrieved from \url{https://medium.com/swlh/social-network-theory-a-literature-review-for-understanding-innovation-programs-7f1c214e9a77}

\leavevmode\vadjust pre{\hypertarget{ref-RN531}{}}%
Thompson, J. D. (1967). \emph{Organizations in action}. New York: McGraw Hill.

\leavevmode\vadjust pre{\hypertarget{ref-RN4954}{}}%
U.S. Department of Education. (2023). \emph{Strategies for increasing diversity and opportunity in higher education}. U.S. Department of Education. Retrieved from \url{https://sites.ed.gov/ous/files/2023/09/Diversity-and-Opportunity-in-Higher-Education.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-RN1549}{}}%
Winston, G. C. (1999). Subsidies, hierarchy and peers: The awkward economics of higher education. \emph{Journal of Economic Perspectives}, \emph{13}(1), 13--36. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000078904300002}{\textless Go to ISI\textgreater://000078904300002}

\leavevmode\vadjust pre{\hypertarget{ref-RN4011}{}}%
Yin, R. K. (2009). \emph{Case study research: Design and methods} (4th ed., pp. xiv, 219 p.). Los Angeles: Sage Publications.

\leavevmode\vadjust pre{\hypertarget{ref-RN2535}{}}%
Zhang, L. A. (2007). Nonresident enrollment demand in public higher education: An analysis at national, state, and institutional levels. \emph{Review of Higher Education}, \emph{31}(1), 1--25. \url{https://doi.org/10.1353/rhe.2007.0057}

\leavevmode\vadjust pre{\hypertarget{ref-RN4758}{}}%
Author. (XXXXa).

\leavevmode\vadjust pre{\hypertarget{ref-list_biz}{}}%
Author. (XXXXe).

\leavevmode\vadjust pre{\hypertarget{ref-list_empirics}{}}%
Author. (XXXXf).

\leavevmode\vadjust pre{\hypertarget{ref-RN3753}{}}%
Author. (XXXXb).

\leavevmode\vadjust pre{\hypertarget{ref-RN3685}{}}%
Author. (XXXXc).

\leavevmode\vadjust pre{\hypertarget{ref-RN4290}{}}%
Author. (XXXXd).

\leavevmode\vadjust pre{\hypertarget{ref-RN4953}{}}%
Borgatti, S. P. (1998). Ego networks. Retrieved from \url{http://www.analytictech.com/networks/egonet.htm}

\leavevmode\vadjust pre{\hypertarget{ref-RN2457}{}}%
Borgatti, S. P. (2008). 2-mode concepts in social network analysis. In \emph{Encyclopedia of complexity and system science}.

\leavevmode\vadjust pre{\hypertarget{ref-RN786}{}}%
Bryk, A. S., Lee, V. E., \& Holland, P. B. (1993). \emph{Catholic schools and the common good}. Cambridge: Harvard University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN975}{}}%
Burt, R. S. (1992). \emph{Structural holes: The social structure of competition}. Cambridge, MA: Harvard University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN2772}{}}%
Cheslock, J. J., \& Kroc, R. (2012). Managing college enrollments. In R. Howard, B. Knight, \& G. McLaughlin (Eds.), \emph{The handbook for institutional researchers} (pp. 221--236). San Francisco, CA: Jossey-Bass.

\leavevmode\vadjust pre{\hypertarget{ref-RN4935}{}}%
Chetty, R., Deming, D. J., \& Friedman, J. N. (2023). Diversifying society's leaders? The causal effects of admission to highly selective private colleges. \emph{National Bureau of Economic Research Working Paper Series}, \emph{No. 31492}. \url{https://doi.org/10.3386/w31492}

\leavevmode\vadjust pre{\hypertarget{ref-RN4599}{}}%
Clark, D., \& Del Bono, E. (2016). The long-run effects of attending an elite school: Evidence from the united kingdom. \emph{American Economic Journal-Applied Economics}, \emph{8}(1), 150--176. \url{https://doi.org/10.1257/app.20130505}

\leavevmode\vadjust pre{\hypertarget{ref-RN4677}{}}%
Clauset, A., Newman, M. E. J., \& Moore, C. (2004). Finding community structure in very large networks. \emph{Physical Review E}, \emph{70}(6). \url{https://doi.org/10.1103/PhysRevE.70.066111}

\leavevmode\vadjust pre{\hypertarget{ref-RN4937}{}}%
Coleman, J. S., \& Hoffer, T. (1987). \emph{Public and private high schools: The impact of communities} (pp. xxviii, 254 p.). New York: Basic Books.

\leavevmode\vadjust pre{\hypertarget{ref-RN4647}{}}%
Cookson, P. W., \& Persell, C. H. (1985). \emph{Preparing for power : America's elite boarding schools} (pp. x, 260 p.). New York: Basic Books.

\leavevmode\vadjust pre{\hypertarget{ref-RN1791}{}}%
Curs, B. R., \& Singell, L. D. (2002). An analysis of the application and enrollment processes for in-state and out-of-state students at a large public university. \emph{Economics of Education Review}, \emph{21}(2), 111--124. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000173740100002}{\textless Go to ISI\textgreater://000173740100002}

\leavevmode\vadjust pre{\hypertarget{ref-RN2287}{}}%
Curs, B. R., \& Singell, L. D. (2010). Aim high or go low? Pricing strategies and enrollment effects when the net price elasticity varis with need and ability. \emph{Journal of Higher Education}, \emph{81}(4), 515--543.

\leavevmode\vadjust pre{\hypertarget{ref-RN4663}{}}%
Davis, G. F., Yoo, M., \& Baker, W. E. (2003). The small world of the american corporate elite, 1982-2001. \emph{Strategic Organization}, \emph{1}(3), 301--326. \url{https://doi.org/10.1177/14761270030013002}

\leavevmode\vadjust pre{\hypertarget{ref-RN2271}{}}%
Delaney, J. A., \& Doyle, W. R. (2011). State spending on higher education: Testing the balance wheel over time. \emph{Journal of Education Finance}, \emph{36}(4), 343--368. Journal Article.

\leavevmode\vadjust pre{\hypertarget{ref-RN3524}{}}%
DesJardins, S. L., \& Bell, A. (2006). Using economic concepts to inform enrollment management. \emph{New Directions for Institutional Research}, \emph{2006}(132), 59--74. \url{https://doi.org/10.1002/ir.196}

\leavevmode\vadjust pre{\hypertarget{ref-eab_nacac_counselor_2023}{}}%
EAB, \& NACAC. (2023). \emph{The counselor perspective: Insights from EAB's survey of high school counselors}. EAB. Retrieved from \url{https://www.nacacnet.org/wp-content/uploads/The-Counselor-Perspective-EAB-Survey.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-RN4936}{}}%
Eide, E. R., Goldhaber, D. D., \& Showalter, M. H. (2004). Does catholic high school attendance lead to attendance at a more selective college? \emph{Social Science Quarterly}, \emph{85}(5), 1335--1352. \url{https://doi.org/10.1111/j.0038-4941.2004.00279.x}

\leavevmode\vadjust pre{\hypertarget{ref-RN4116}{}}%
Eisenhardt, K. M. (1989). Building theories from case study research. \emph{Academy of Management Review}, \emph{14}(4), 532--550. \url{https://doi.org/10.2307/258557}

\leavevmode\vadjust pre{\hypertarget{ref-RN4642}{}}%
Falsey, B., \& Heyns, B. (1984). The college channel: Private and public schools reconsidered. \emph{Sociology of Education}, \emph{57}(2), 111--122. \url{https://doi.org/10.2307/2112633}

\leavevmode\vadjust pre{\hypertarget{ref-RN4724}{}}%
Graham, L. (1999). \emph{Our kind of people: Inside america's black upper class} (1st ed., pp. xii, 418 pages, 16 unnumbered pages of plates). New York: HarperCollins.

\leavevmode\vadjust pre{\hypertarget{ref-RN4625}{}}%
Hill, L. D. (2008). School strategies and the "college-linking" process: Reconsidering the effects of high schools on college enrollment. \emph{Sociology of Education}, \emph{81}(1), 53--76. Journal Article. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://WOS:000256634400003}{\textless Go to ISI\textgreater://WOS:000256634400003}

\leavevmode\vadjust pre{\hypertarget{ref-RN4324}{}}%
Holland, M. M. (2019). \emph{Divergent paths to college: Race, class, and inequality in high schools}. Rutgers University Press. \url{https://doi.org/10.36019/9780813590288}

\leavevmode\vadjust pre{\hypertarget{ref-em_burnout_hoover}{}}%
Hoover, E. (2023). A profession on the edge: Why enrollment leaders are wearing down, burning out, and leaving jobs they once loved. \emph{The Chronicle of Higher Education}, (April 5). Retrieved from \url{https://www.chronicle.com/article/a-profession-on-the-edge}

\leavevmode\vadjust pre{\hypertarget{ref-RN2133}{}}%
Hoxby, C. M. (1997). \emph{How the changing market structure of u.s. Higher education explains college tuition} (No. Working Paper 6323). National Bureau of Economic Research. Retrieved from \url{http://www.nber.org/papers/W6323.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-RN4495}{}}%
Jack, A. A. (2019). \emph{The privileged poor: How elite colleges are failing disadvantaged students} (p. 276). Cambridge, Massachusetts: Harvard University Press,. Retrieved from \href{Restricted\%20to\%20UCLA.\%20Limited\%20to\%20three\%20concurrent\%20users.\%20Try\%20again\%20later\%20if\%20unavailable.\%20http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&__char_set=utf8\&isbn=9780674239647}{Restricted to UCLA. Limited to three concurrent users. Try again later if unavailable. http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&\_\_char\_set=utf8\&isbn=9780674239647}

\leavevmode\vadjust pre{\hypertarget{ref-RN4596}{}}%
Jerrim, J., Parker, P. D., Chmielewski, A. K., \& Anders, J. (2016). Private schooling, educational transitions, and early labour market outcomes: Evidence from three anglophone countries. \emph{European Sociological Review}, \emph{32}(2), 280--294. \url{https://doi.org/10.1093/esr/jcv098}

\leavevmode\vadjust pre{\hypertarget{ref-RN4321}{}}%
Khan, S. R. (2010). \emph{Getting in: How elite schools play the college game} (pp. 97--113). Rowman \& Littlefield.

\leavevmode\vadjust pre{\hypertarget{ref-RN4407}{}}%
Khan, S. R. (2011). \emph{Privilege: The making of an adolescent elite at st. Paul's school} (pp. 232 pages). Princeton, N.J.: Princeton University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN3522}{}}%
Killgore, L. (2009). Merit and competition in selective college admissions. \emph{Review of Higher Education}, \emph{32}(4), 469--488. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://WOS:000266737500002}{\textless Go to ISI\textgreater://WOS:000266737500002}

\leavevmode\vadjust pre{\hypertarget{ref-RN1565}{}}%
Kingston, P. W., \& Lewis, L. S. (1990). \emph{The high-status track: Studies of elite schools and stratification} (pp. xxxiv, 261 p.). Albany: State University of New York Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN4614}{}}%
Klugman, J. (2012). How resource inequalities among high schools reproduce class advantages in college destinations. \emph{Research in Higher Education}, \emph{53}(8), 803--830. Journal Article. \url{https://doi.org/10.1007/s11162-012-9261-8}

\leavevmode\vadjust pre{\hypertarget{ref-RN4725}{}}%
Kolaczyk, E. D., \& Csárdi, G. (2020). \emph{Statistical analysis of network data with r} (2nd ed, p. 235). Cham: Springer,. \url{https://doi.org/10.1007/978-3-030-44129-6}

\leavevmode\vadjust pre{\hypertarget{ref-RN3762}{}}%
Leeds, D. M., \& DesJardins, S. L. (2015). The effect of merit aid on enrollment: A regression discontinuity analysis of iowa's national scholars award. \emph{Research in Higher Education}, \emph{56}(7), 471--495. \url{https://doi.org/10.1007/s11162-014-9359-2}

\leavevmode\vadjust pre{\hypertarget{ref-RN4643}{}}%
Levine, S. B. (1980). The rise of american boarding schools and the development of a national upper-class. \emph{Social Problems}, \emph{28}(1), 63--94. \url{https://doi.org/10.1525/sp.1980.28.1.03a00050}

\leavevmode\vadjust pre{\hypertarget{ref-RN2546}{}}%
Mak, J., \& Moncur, J. E. T. (2003). Interstate migration of college freshmen. \emph{Annals of Regional Science}, \emph{37}(4), 603--612. \url{https://doi.org/10.1007/s00168-003-0130-4}

\leavevmode\vadjust pre{\hypertarget{ref-RN1722}{}}%
McPherson, M., Smith-Lovin, L., \& Cook, J. M. (2001). Birds of a feather: Homophily in social networks. \emph{Annual Review of Sociology}, \emph{27}, 415--444. Journal Article. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000170748100017}{\textless Go to ISI\textgreater://000170748100017}

\leavevmode\vadjust pre{\hypertarget{ref-RN513}{}}%
Meyer, J. W., \& Rowan, B. (1977). Institutionalized organizations: Formal structure as myth and ceremony. \emph{The American Journal of Sociology}, \emph{83}(2), 340--363.

\leavevmode\vadjust pre{\hypertarget{ref-RN2536}{}}%
Mixon, F. G., \& Hsing, Y. (1994). The determinants of out-of-state enrollments in higher education: A tobit analysis. \emph{Economics of Education Review}, \emph{13}(4), 295--335.

\leavevmode\vadjust pre{\hypertarget{ref-RN4504}{}}%
Murnane, R. J., \& Reardon, S. F. (2018). Long-term trends in private school enrollments by family income. \emph{AERA Open}, \emph{4}(1), 1--24. \url{https://doi.org/10.1177/2332858417751355}

\leavevmode\vadjust pre{\hypertarget{ref-RN4938}{}}%
Neal, D. (1997). The effects of catholic secondary schooling on educational achievement. \emph{Journal of Labor Economics}, \emph{15}(1), 98--123. \url{https://doi.org/10.1086/209848}

\leavevmode\vadjust pre{\hypertarget{ref-RN4634}{}}%
Persell, C. H., Catsambis, S., \& Cookson, P. W. (1992). Differential asset conversion: Class and gendered pathways to selective colleges. \emph{Sociology of Education}, \emph{65}(3), 208--225. \url{https://doi.org/10.2307/2112809}

\leavevmode\vadjust pre{\hypertarget{ref-RN4640}{}}%
Persell, C. H., \& Cookson, P. W. (1985). Chartering and bartering: Elite education and social reproduction. \emph{Social Problems}, \emph{33}(2), 114--129. \url{https://doi.org/10.1525/sp.1985.33.2.03a00030}

\leavevmode\vadjust pre{\hypertarget{ref-RN959}{}}%
Pfeffer, J., \& Salancik, G. R. (1978). \emph{The external control of organizations: A resource dependence perspective} (pp. xiii, 300 p.). New York: Harper \& Row.

\leavevmode\vadjust pre{\hypertarget{ref-RN1577}{}}%
Priest, D. M., \& St. John, E. P. (2006). \emph{Privatization and public universities} (pp. 299 p.). Bloomington: Indiana University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN4588}{}}%
Purdy, M. A. (2018). \emph{Transforming the elite: Black students and the desegregation of private schools} (pp. 1--243). \url{https://doi.org/10.5149/northcarolina/9781469643496.001.0001}

\leavevmode\vadjust pre{\hypertarget{ref-RN4589}{}}%
Reeves, A., Friedman, S., Rahal, C., \& Flemmen, M. (2017). The decline and persistence of the old boy: Private schools and elite recruitment 1897 to 2016. \emph{American Sociological Review}, \emph{82}(6), 1139--1166. \url{https://doi.org/10.1177/0003122417735742}

\leavevmode\vadjust pre{\hypertarget{ref-RN4911}{}}%
Rivard, R. (2013). Micro-targeting students: Increasingly sophisticated data slicing tools are changing student recruitment. Who benefits? \emph{InsideHigherEd}, (Oct 24). Retrieved from \url{https://www.insidehighered.com/news/2013/10/24/political-campaign-style-targeting-comes-student-search?width=775\&height=500\&iframe=true}

\leavevmode\vadjust pre{\hypertarget{ref-RN3608}{}}%
Rudolph, F. (1962). \emph{The american college and university: A history} (1st ed., pp. 516 p.). New York: Alfred A. Knopf.

\leavevmode\vadjust pre{\hypertarget{ref-RN4402}{}}%
Ruffalo Noel-Levitz. (2018). \emph{2018 marketing and student recruitment report of effective practices}. Ruffalo Noel-Levitz. Retrieved from \url{http://learn.ruffalonl.com/rs/395-EOG-977/images/RNL_2018_Student_Recruitment_Marketing_Report_EM-19.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-RN4664}{}}%
Ruffalo Noel-Levitz. (2020a). \emph{2020 cost of recruiting an undergraduate student report} (Report). Ruffalo Noel-Levitz. Retrieved from \url{https://learn.ruffalonl.com/rs/395-EOG-977/images/2020_CostRecruiting_Report.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-parents_covid_rnl}{}}%
Ruffalo Noel-Levitz. (2020b). \emph{College planning and the perceptions of parents after covid-19}. Ruffalo Noel-Levitz. Retrieved from \url{https://www.ruffalonl.com/thank-you/download-college-planning-and-the-perceptions-of-parents-after-covid-19/}

\leavevmode\vadjust pre{\hypertarget{ref-RN4896}{}}%
Ruffalo Noel-Levitz. (2022a). \emph{2022 cost of recruiting an undergraduate student report}. Ruffalo Noel-Levitz. Retrieved from \url{https://www.ruffalonl.com/thank-you/download-the-2022-cost-of-recruiting-an-undergraduate-student-report/}

\leavevmode\vadjust pre{\hypertarget{ref-RN4895}{}}%
Ruffalo Noel-Levitz. (2022b). \emph{2022 marketing and recruitment practices for undergraduate students report}. Ruffalo Noel-Levitz. Retrieved from \url{https://www.ruffalonl.com/papers-research-higher-education-fundraising/marketing-and-recruitment-practices-for-undergraduate-students/}

\leavevmode\vadjust pre{\hypertarget{ref-RN4934}{}}%
Salazar, K. G. (2022). Recruitment redlining by public research universities in the los angeles and dallas metropolitan areas. \emph{The Journal of Higher Education}, \emph{93}(4), 585--621. \url{https://doi.org/10.1080/00221546.2021.2004811}

\leavevmode\vadjust pre{\hypertarget{ref-RN1118}{}}%
Slaughter, S., \& Rhoades, G. (2004). \emph{Academic capitalism and the new economy} (pp. xii, 370 p.). Baltimore: Johns Hopkins University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN3519}{}}%
Stevens, M. L. (2007). \emph{Creating a class: College admissions and the education of elites} (pp. 308 p.). Cambridge, MA: Harvard University Press.

\leavevmode\vadjust pre{\hypertarget{ref-RN4648}{}}%
Stone, T. (2018). Social network theory: A literature review for understanding innovation programs. Retrieved from \url{https://medium.com/swlh/social-network-theory-a-literature-review-for-understanding-innovation-programs-7f1c214e9a77}

\leavevmode\vadjust pre{\hypertarget{ref-RN531}{}}%
Thompson, J. D. (1967). \emph{Organizations in action}. New York: McGraw Hill.

\leavevmode\vadjust pre{\hypertarget{ref-RN4954}{}}%
U.S. Department of Education. (2023). \emph{Strategies for increasing diversity and opportunity in higher education}. U.S. Department of Education. Retrieved from \url{https://sites.ed.gov/ous/files/2023/09/Diversity-and-Opportunity-in-Higher-Education.pdf}

\leavevmode\vadjust pre{\hypertarget{ref-RN1549}{}}%
Winston, G. C. (1999). Subsidies, hierarchy and peers: The awkward economics of higher education. \emph{Journal of Economic Perspectives}, \emph{13}(1), 13--36. Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000078904300002}{\textless Go to ISI\textgreater://000078904300002}

\leavevmode\vadjust pre{\hypertarget{ref-RN4011}{}}%
Yin, R. K. (2009). \emph{Case study research: Design and methods} (4th ed., pp. xiv, 219 p.). Los Angeles: Sage Publications.

\leavevmode\vadjust pre{\hypertarget{ref-RN2535}{}}%
Zhang, L. A. (2007). Nonresident enrollment demand in public higher education: An analysis at national, state, and institutional levels. \emph{Review of Higher Education}, \emph{31}(1), 1--25. \url{https://doi.org/10.1353/rhe.2007.0057}

\end{CSLReferences}

\newpage
\clearpage
\begin{landscape}

\begin{table}[!h]

\caption{\label{tab:sample-characteristics}Characteristics of universities in analysis sample}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\raggedright\arraybackslash}m{4.5cm}>{\raggedleft\arraybackslash}m{1.8cm}>{\raggedleft\arraybackslash}m{3.8cm}>{\raggedleft\arraybackslash}m{3.8cm}>{\raggedleft\arraybackslash}m{2.4cm}>{\raggedleft\arraybackslash}m{2.7cm}>{\raggedleft\arraybackslash}m{2.4cm}>{\raggedleft\arraybackslash}m{3cm}>{\raggedleft\arraybackslash}m{2.4cm}>{\raggedleft\arraybackslash}m{2.4cm}>{\raggedleft\arraybackslash}m{2.4cm}>{\raggedleft\arraybackslash}m{2.4cm}>{\raggedleft\arraybackslash}m{2.4cm}>{\raggedleft\arraybackslash}m{3cm}}
\toprule
Classification & University & Rank & 25th Percentile SAT/ACT Composite Score & 75th Percentile SAT/ACT Composite Score & In-State Tuition + Fees & Out-of-State Tuition + Fees & Total Enrolled Freshmen & Percent Out-of-State Freshmen & Percent Pell Recipients & Percent White Freshmen & Percent Black Freshmen & Percent Asian Freshmen & Percent Hispanic Freshmen & Percent International Freshmen\\
\midrule
 & UC Berkeley & 22 & 1,316 & 1,527 & \$13,807 & \$41,076 & 6,252 & 24.4\% & 19.4\% & 25.6\% & 1.8\% & 42.7\% & 13.8\% & 9.3\%\\

 & UC San Diego & 35 & 1,193 & 1,455 & \$13,946 & \$41,215 & 5,748 & 26.5\% & 30.7\% & 15.5\% & 1.5\% & 34.4\% & 20.6\% & 21.6\%\\

 & U of Georgia & 47 & 1,165 & 1,360 & \$11,890 & \$30,502 & 5,433 & 12.3\% & 20.3\% & 68.0\% & 8.1\% & 12.4\% & 5.8\% & 1.6\%\\

 & U of Pitt & 58 & 1,202 & 1,395 & \$19,028 & \$30,414 & 5,644 & 30.6\% & 20.3\% & 68.5\% & 7.3\% & 9.3\% & 4.3\% & 3.6\%\\

 & Rutgers & 63 & 1,110 & 1,350 & \$14,689 & \$30,684 & 6,465 & 17.8\% & 27.0\% & 35.5\% & 6.0\% & 31.3\% & 12.1\% & 10.4\%\\

 & UMass Amherst & 66 & 1,135 & 1,332 & \$15,301 & \$32,914 & 4,679 & 26.9\% & 21.5\% & 61.0\% & 3.8\% & 12.5\% & 6.0\% & 8.1\%\\

 & UC Riverside & 88 & 956 & 1,200 & \$13,880 & \$41,150 & 5,358 & 2.2\% & 56.6\% & 10.1\% & 4.0\% & 31.1\% & 47.2\% & 2.5\%\\

 & SUNY Stony Brook & 88 & 1,163 & 1,373 & \$9,197 & \$26,817 & 2,934 & 25.8\% & 34.6\% & 27.8\% & 5.9\% & 28.8\% & 11.0\% & 16.5\%\\

 & CU Boulder & 103 & 1,126 & 1,331 & \$11,785 & \$35,852 & 6,421 & 47.2\% & 14.6\% & 66.3\% & 1.5\% & 5.6\% & 12.5\% & 7.5\%\\

 & U of S.Carolina & 118 & 1,135 & 1,321 & \$11,706 & \$31,562 & 5,110 & 53.2\% & 15.4\% & 82.1\% & 5.0\% & 3.0\% & 4.3\% & 1.2\%\\

 & U of Kansas & 124 & 1,070 & 1,300 & \$10,781 & \$26,503 & 4,233 & 42.8\% & 23.4\% & 72.1\% & 4.3\% & 4.5\% & 8.7\% & 4.6\%\\

 & UNL & 133 & 1,027 & 1,262 & \$8,725 & \$23,558 & 4,860 & 29.9\% & 23.9\% & 75.6\% & 3.1\% & 2.5\% & 7.2\% & 6.3\%\\

 & U of Alabama & 143 & 1,053 & 1,351 & \$10,701 & \$27,544 & 7,559 & 68.1\% & 17.0\% & 80.6\% & 8.0\% & 1.3\% & 5.3\% & 0.8\%\\

 & U of Cincinnati & 143 & 1,063 & 1,265 & \$11,242 & \$26,914 & 6,913 & 13.1\% & 26.7\% & 74.9\% & 9.0\% & 3.8\% & 3.5\% & 2.4\%\\

\multirow{-15}{*}{\raggedright\arraybackslash Public Research} & U of Arkansas & 160 & 1,057 & 1,283 & \$9,014 & \$23,678 & 4,972 & 51.0\% & 19.5\% & 78.7\% & 3.9\% & 2.6\% & 8.5\% & 1.0\%\\
\cmidrule{1-15}
 & Northwestern & 9 & 1,413 & 1,527 & \$51,975 & \$51,975 & 1,985 & 69.8\% & 17.8\% & 46.1\% & 5.0\% & 16.7\% & 13.6\% & 9.7\%\\

 & Notre Dame & 19 & 1,395 & 1,553 & \$50,780 & \$50,780 & 2,046 & 94.5\% & 11.9\% & 67.8\% & 4.5\% & 5.3\% & 10.7\% & 5.9\%\\

 & Emory & 21 & 1,313 & 1,481 & \$49,011 & \$49,011 & 1,358 & 85.5\% & 17.5\% & 40.9\% & 7.1\% & 18.8\% & 10.8\% & 16.1\%\\

 & Tufts & 30 & 1,375 & 1,515 & \$53,585 & \$53,585 & 1,336 & 80.2\% & 10.2\% & 54.9\% & 4.8\% & 13.4\% & 6.7\% & 11.4\%\\

 & Boston Coll. & 35 & 1,297 & 1,460 & \$52,426 & \$52,426 & 2,254 & 76.6\% & 12.8\% & 61.4\% & 2.8\% & 10.7\% & 11.1\% & 6.8\%\\

 & Tulane & 41 & 1,277 & 1,416 & \$52,134 & \$52,134 & 1,856 & 87.6\% & 7.8\% & 76.0\% & 4.3\% & 5.7\% & 5.8\% & 4.3\%\\

 & Case Western Res. & 42 & 1,314 & 1,501 & \$47,020 & \$47,020 & 1,265 & 75.7\% & 10.0\% & 48.1\% & 4.3\% & 19.6\% & 6.2\% & 15.6\%\\

 & Villanova & 53 & 1,280 & 1,420 & \$50,366 & \$50,366 & 1,678 & 83.1\% & 9.7\% & 76.0\% & 4.7\% & 5.5\% & 6.9\% & 1.5\%\\

 & SMU & 66 & 1,244 & 1,416 & \$51,467 & \$51,467 & 1,522 & 61.6\% & 10.2\% & 66.4\% & 5.6\% & 5.9\% & 11.0\% & 6.3\%\\

 & Baylor & 76 & 1,163 & 1,329 & \$42,931 & \$42,931 & 3,503 & 35.3\% & 17.4\% & 65.4\% & 6.2\% & 5.5\% & 15.3\% & 2.9\%\\

 & U of Denver & 80 & 1,166 & 1,359 & \$47,445 & \$47,445 & 1,399 & 67.5\% & 14.6\% & 73.5\% & 2.0\% & 4.3\% & 9.8\% & 5.6\%\\

 & TCU & 80 & 1,125 & 1,321 & \$43,610 & \$43,610 & 1,888 & 56.6\% & 11.2\% & 72.9\% & 4.7\% & 3.1\% & 13.3\% & 3.7\%\\

 & Stevens Ins. Tech & 80 & 1,274 & 1,447 & \$49,914 & \$49,914 & 737 & 38.8\% & 15.5\% & 65.4\% & 2.7\% & 14.7\% & 10.0\% & 4.6\%\\

\multirow{-14}{*}{\raggedright\arraybackslash Private National} & Marquette & 88 & 1,101 & 1,296 & \$39,318 & \$39,318 & 2,005 & 71.4\% & 19.0\% & 68.0\% & 4.9\% & 8.1\% & 13.3\% & 2.5\%\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\begin{table}

\caption{\label{tab:sample-population-characteristics}Characteristics of universities in analysis sample compared to data collection sample}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{lrrrrrrrrrrrr}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{6}{c}{Public research universities} & \multicolumn{6}{c}{Selective private universities} \\
\cmidrule(l{3pt}r{3pt}){2-7} \cmidrule(l{3pt}r{3pt}){8-13}
\multicolumn{1}{c}{ } & \multicolumn{3}{c}{Analysis sample (N=15)} & \multicolumn{3}{c}{Data collection sample (N=102)} & \multicolumn{3}{c}{Analysis sample (N=14)} & \multicolumn{3}{c}{Data collection sample (N=57)} \\
\cmidrule(l{3pt}r{3pt}){2-4} \cmidrule(l{3pt}r{3pt}){5-7} \cmidrule(l{3pt}r{3pt}){8-10} \cmidrule(l{3pt}r{3pt}){11-13}
  & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile & 25th percentile & 50th percentile & 75th percentile\\
\midrule
25th Percentile SAT/ACT Composite Score & 1,060 & 1,126 & 1,164 & 984 & 1,061 & 1,135 & 1,185 & 1,278 & 1,314 & 1,191 & 1,289 & 1,391\\
75th Percentile SAT/ACT Composite Score & 1,292 & 1,332 & 1,366 & 1,204 & 1,282 & 1,350 & 1,373 & 1,433 & 1,496 & 1,375 & 1,472 & 1,542\\
In-State Tuition + Fees & \$10,741 & \$11,785 & \$13,913 & \$9,100 & \$10,750 & \$13,322 & \$47,126 & \$50,140 & \$51,848 & \$47,020 & \$49,914 & \$51,661\\
Out-of-State Tuition + Fees & \$26,866 & \$30,502 & \$34,383 & \$23,433 & \$27,589 & \$32,989 & \$47,126 & \$50,140 & \$51,848 & \$47,020 & \$49,914 & \$51,661\\
Total Enrolled Freshmen & 4,916 & 5,433 & 6,336 & 3,416 & 4,528 & 5,850 & 1,368 & 1,767 & 2,000 & 1,305 & 1,585 & 2,005\\
Percent Out-of-State Freshmen & 21.1\% & 26.9\% & 45.0\% & 15.4\% & 25.8\% & 39.8\% & 63.1\% & 73.6\% & 82.4\% & 66.4\% & 76.6\% & 87.6\%\\
Percent Pell Recipients & 19.5\% & 21.5\% & 26.8\% & 20.3\% & 25.5\% & 33.3\% & 10.2\% & 12.4\% & 16.9\% & 12.8\% & 14.2\% & 16.5\%\\
Percent White Freshmen & 31.6\% & 68.0\% & 75.2\% & 45.3\% & 61.7\% & 72.6\% & 56.5\% & 65.9\% & 71.7\% & 41.1\% & 49.3\% & 63.8\%\\
Percent Black Freshmen & 3.4\% & 4.3\% & 6.6\% & 3.1\% & 5.6\% & 8.9\% & 4.3\% & 4.7\% & 5.0\% & 4.0\% & 5.3\% & 7.1\%\\
Percent Asian Freshmen & 3.4\% & 9.3\% & 29.9\% & 3.1\% & 6.6\% & 13.2\% & 5.5\% & 7.0\% & 14.3\% & 5.9\% & 13.2\% & 18.8\%\\
Percent Hispanic Freshmen & 5.5\% & 8.5\% & 12.3\% & 5.5\% & 8.6\% & 16.8\% & 7.6\% & 10.7\% & 12.8\% & 9.0\% & 10.7\% & 13.3\%\\
Percent International Freshmen & 2.0\% & 4.6\% & 8.7\% & 1.6\% & 3.1\% & 7.1\% & 3.8\% & 5.7\% & 9.0\% & 6.0\% & 9.8\% & 12.3\%\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\begin{table}

\caption{\label{tab:pubu-percent-matrix}One-mode public university percent matrix}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{5.5em}>{\raggedleft\arraybackslash}p{7.5em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{5.5em}>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{8.8em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{6em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{U of Alabama (N=759)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of S.Carolina (N=396)} & \multicolumn{1}{>{\centering\arraybackslash}p{5.5em}}{CU Boulder (N=362)} & \multicolumn{1}{>{\centering\arraybackslash}p{7.5em}}{UMass Amherst (N=296)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{U of Georgia (N=256)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{Rutgers (N=255)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of Cincinnati (N=243)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{U of Pitt (N=222)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{UC Berkeley (N=200)} & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{UC San Diego (N=192)} & \multicolumn{1}{>{\centering\arraybackslash}p{5.5em}}{U of Kansas (N=173)} & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{U of Arkansas (N=163)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.8em}}{SUNY Stony Brook (N=119)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{UNL (N=100)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{UC Riverside (N=88)}\\
\midrule
U of Alabama (N=759) & 100.0 & 71.7 & 58.0 & 50.3 & 66.0 & 47.1 & 51.0 & 56.3 & 56.0 & 52.1 & 53.8 & 61.3 & 36.1 & 31 & 38.6\\
U of S.Carolina (N=396) & 37.4 & 100.0 & 42.8 & 36.5 & 54.7 & 29.0 & 45.3 & 44.6 & 42.0 & 30.7 & 33.5 & 35.0 & 22.7 & 20 & 21.6\\
CU Boulder (N=362) & 27.7 & 39.1 & 100.0 & 38.9 & 34.4 & 29.8 & 28.4 & 41.4 & 38.5 & 51.0 & 42.8 & 31.3 & 17.6 & 25 & 31.8\\
UMass Amherst (N=296) & 19.6 & 27.3 & 31.8 & 100.0 & 22.3 & 36.5 & 11.1 & 25.2 & 22.5 & 29.7 & 10.4 & 8.6 & 47.9 & 4 & 20.5\\
U of Georgia (N=256) & 22.3 & 35.4 & 24.3 & 19.3 & 100.0 & 9.4 & 30.0 & 21.6 & 32.0 & 19.8 & 22.5 & 36.2 & 5.9 & 13 & 18.2\\
Rutgers (N=255) & 15.8 & 18.7 & 21.0 & 31.4 & 9.4 & 100.0 & 14.4 & 33.3 & 20.5 & 22.4 & 11.6 & 3.1 & 40.3 & 10 & 11.4\\
U of Cincinnati (N=243) & 16.3 & 27.8 & 19.1 & 9.1 & 28.5 & 13.7 & 100.0 & 25.2 & 16.5 & 12.5 & 16.8 & 22.7 & 4.2 & 18 & 9.1\\
U of Pitt (N=222) & 16.5 & 25.0 & 25.4 & 18.9 & 18.8 & 29.0 & 23.0 & 100.0 & 20.5 & 14.6 & 18.5 & 16.0 & 22.7 & 15 & 12.5\\
UC Berkeley (N=200) & 14.8 & 21.2 & 21.3 & 15.2 & 25.0 & 16.1 & 13.6 & 18.5 & 100.0 & 31.8 & 17.3 & 16.0 & 7.6 & 8 & 22.7\\
UC San Diego (N=192) & 13.2 & 14.9 & 27.1 & 19.3 & 14.8 & 16.9 & 9.9 & 12.6 & 30.5 & 100.0 & 16.8 & 13.5 & 9.2 & 3 & 39.8\\
U of Kansas (N=173) & 12.3 & 14.6 & 20.4 & 6.1 & 15.2 & 7.8 & 11.9 & 14.4 & 15.0 & 15.1 & 100.0 & 38.0 & 0.0 & 61 & 9.1\\
U of Arkansas (N=163) & 13.2 & 14.4 & 14.1 & 4.7 & 23.0 & 2.0 & 15.2 & 11.7 & 13.0 & 11.5 & 35.8 & 100.0 & 0.8 & 24 & 10.2\\
SUNY Stony Brook (N=119) & 5.7 & 6.8 & 5.8 & 19.3 & 2.7 & 18.8 & 2.1 & 12.2 & 4.5 & 5.7 & 0.0 & 0.6 & 100.0 & 0 & 4.5\\
UNL (N=100) & 4.1 & 5.1 & 6.9 & 1.4 & 5.1 & 3.9 & 7.4 & 6.8 & 4.0 & 1.6 & 35.3 & 14.7 & 0.0 & 100 & 0.0\\
UC Riverside (N=88) & 4.5 & 4.8 & 7.7 & 6.1 & 6.2 & 3.9 & 3.3 & 5.0 & 10.0 & 18.2 & 4.6 & 5.5 & 3.4 & 0 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}

\caption{\label{tab:privu-percent-matrix}One-mode private university percent matrix}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{8.5em}>{\raggedleft\arraybackslash}p{8.5em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Notre Dame (N=625)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Villanova (N=563)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{SMU (N=550)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{TCU (N=435)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Tulane (N=430)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Northwestern (N=377)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Boston Coll. (N=339)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Marquette (N=331)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Tufts (N=301)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of Denver (N=279)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Emory (N=273)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Baylor (N=237)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.5em}}{Case Western Res. (N=228)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.5em}}{Stevens Ins. Tech (N=160)}\\
\midrule
Notre Dame (N=625) & 100.0 & 60.0 & 53.3 & 58.2 & 51.9 & 59.4 & 69.3 & 69.8 & 58.8 & 58.8 & 53.1 & 41.8 & 58.3 & 49.4\\
Villanova (N=563) & 54.1 & 100.0 & 52.9 & 51.5 & 50.7 & 56.8 & 61.4 & 61.9 & 53.5 & 51.3 & 53.8 & 42.6 & 62.3 & 64.4\\
SMU (N=550) & 46.9 & 51.7 & 100.0 & 66.7 & 64.0 & 64.5 & 64.3 & 45.6 & 62.8 & 63.4 & 64.5 & 65.0 & 58.8 & 55.0\\
TCU (N=435) & 40.5 & 39.8 & 52.7 & 100.0 & 46.3 & 46.9 & 49.6 & 45.3 & 46.8 & 54.1 & 44.7 & 56.1 & 43.0 & 41.2\\
Tulane (N=430) & 35.7 & 38.7 & 50.0 & 45.7 & 100.0 & 58.1 & 51.0 & 31.1 & 63.1 & 50.9 & 52.4 & 33.3 & 57.5 & 35.0\\
Northwestern (N=377) & 35.8 & 38.0 & 44.2 & 40.7 & 50.9 & 100.0 & 50.7 & 34.4 & 56.1 & 49.8 & 46.9 & 31.6 & 53.5 & 34.4\\
Boston Coll. (N=339) & 37.6 & 36.9 & 39.6 & 38.6 & 40.2 & 45.6 & 100.0 & 40.2 & 52.5 & 48.4 & 41.4 & 27.0 & 43.9 & 37.5\\
Marquette (N=331) & 37.0 & 36.4 & 27.5 & 34.5 & 24.0 & 30.2 & 39.2 & 100.0 & 25.6 & 34.8 & 19.0 & 26.2 & 28.9 & 26.9\\
Tufts (N=301) & 28.3 & 28.6 & 34.4 & 32.4 & 44.2 & 44.8 & 46.6 & 23.3 & 100.0 & 40.9 & 42.9 & 21.9 & 47.4 & 41.2\\
U of Denver (N=279) & 26.2 & 25.4 & 32.2 & 34.7 & 33.0 & 36.9 & 39.8 & 29.3 & 37.9 & 100.0 & 30.0 & 24.1 & 31.6 & 27.5\\
Emory (N=273) & 23.2 & 26.1 & 32.0 & 28.0 & 33.3 & 34.0 & 33.3 & 15.7 & 38.9 & 29.4 & 100.0 & 16.5 & 43.0 & 26.2\\
Baylor (N=237) & 15.8 & 17.9 & 28.0 & 30.6 & 18.4 & 19.9 & 18.9 & 18.7 & 17.3 & 20.4 & 14.3 & 100.0 & 21.9 & 14.4\\
Case Western Res. (N=228) & 21.3 & 25.2 & 24.4 & 22.5 & 30.5 & 32.4 & 29.5 & 19.9 & 35.9 & 25.8 & 35.9 & 21.1 & 100.0 & 25.6\\
Stevens Ins. Tech (N=160) & 12.6 & 18.3 & 16.0 & 15.2 & 13.0 & 14.6 & 17.7 & 13.0 & 21.9 & 15.8 & 15.4 & 9.7 & 18.0 & 100.0\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage

\begin{table}

\caption{\label{tab:privu-percent-visited-by-pubu-matrix}For private universities, the percent of high schools visited by public universities}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{8.5em}>{\raggedleft\arraybackslash}p{8.5em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Notre Dame (N=625)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Villanova (N=563)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{SMU (N=550)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{TCU (N=435)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Tulane (N=430)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Northwestern (N=377)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Boston Coll. (N=339)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Marquette (N=331)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Tufts (N=301)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of Denver (N=279)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Emory (N=273)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Baylor (N=237)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.5em}}{Case Western Res. (N=228)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.5em}}{Stevens Ins. Tech (N=160)}\\
\midrule
U of Alabama (N=759) & 52.2 & 51.0 & 56.9 & 59.8 & 51.2 & 48.8 & 54.9 & 53.5 & 46.5 & 48.7 & 60.1 & 57.8 & 53.5 & 48.8\\
U of S.Carolina (N=396) & 30.7 & 36.2 & 40.5 & 43.9 & 37.0 & 36.1 & 35.7 & 31.1 & 35.2 & 35.5 & 44.0 & 38.8 & 34.6 & 36.9\\
CU Boulder (N=362) & 34.4 & 33.2 & 40.2 & 46.4 & 41.4 & 42.4 & 42.2 & 40.5 & 46.2 & 49.8 & 38.1 & 42.2 & 42.5 & 35.0\\
UMass Amherst (N=296) & 21.0 & 24.3 & 22.7 & 24.8 & 26.5 & 21.5 & 33.0 & 21.1 & 31.9 & 27.2 & 20.1 & 9.3 & 17.1 & 41.2\\
U of Georgia (N=256) & 17.9 & 22.7 & 28.4 & 27.8 & 27.7 & 27.3 & 21.8 & 13.3 & 23.6 & 17.2 & 32.2 & 32.5 & 20.2 & 20.0\\
Rutgers (N=255) & 19.0 & 22.9 & 14.0 & 16.8 & 15.8 & 16.4 & 20.4 & 16.9 & 17.3 & 16.5 & 17.2 & 7.6 & 20.2 & 41.9\\
U of Cincinnati (N=243) & 17.3 & 21.7 & 18.7 & 19.3 & 16.7 & 22.8 & 16.8 & 22.4 & 14.0 & 20.4 & 22.0 & 17.3 & 18.0 & 15.6\\
U of Pitt (N=222) & 20.5 & 27.5 & 18.0 & 18.9 & 19.1 & 19.6 & 20.1 & 19.0 & 21.3 & 15.8 & 17.2 & 15.6 & 27.2 & 30.6\\
UC Berkeley (N=200) & 16.3 & 19.0 & 21.1 & 21.4 & 24.4 & 27.9 & 21.8 & 13.9 & 28.9 & 19.7 & 27.8 & 16.0 & 27.2 & 17.5\\
UC San Diego (N=192) & 17.1 & 14.4 & 18.2 & 22.3 & 17.4 & 22.0 & 25.4 & 17.5 & 28.9 & 25.4 & 18.3 & 18.1 & 21.9 & 20.6\\
U of Kansas (N=173) & 14.4 & 15.1 & 16.2 & 20.7 & 13.5 & 17.0 & 15.0 & 27.2 & 12.0 & 24.7 & 10.3 & 23.2 & 16.2 & 7.5\\
U of Arkansas (N=163) & 8.8 & 11.5 & 19.6 & 19.8 & 15.8 & 13.3 & 9.4 & 13.6 & 10.0 & 14.3 & 10.6 & 35.4 & 15.4 & 8.1\\
SUNY Stony Brook (N=119) & 8.0 & 10.7 & 5.8 & 7.4 & 5.6 & 4.0 & 6.8 & 8.5 & 8.6 & 5.0 & 3.7 & 0.4 & 7.9 & 21.9\\
UNL (N=100) & 6.9 & 8.2 & 7.1 & 8.5 & 5.1 & 8.2 & 6.2 & 12.7 & 4.7 & 9.7 & 2.9 & 8.9 & 7.0 & 1.9\\
UC Riverside (N=88) & 5.6 & 5.0 & 4.9 & 6.7 & 5.6 & 7.4 & 6.8 & 5.1 & 8.0 & 6.1 & 4.0 & 7.6 & 6.6 & 3.8\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}

\caption{\label{tab:pubu-percent-visited-by-privu-matrix}For public universities, the percent of high schools visited by private universities}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{5.5em}>{\raggedleft\arraybackslash}p{7.5em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{5.5em}>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{8.8em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{6em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{U of Alabama (N=759)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of S.Carolina (N=396)} & \multicolumn{1}{>{\centering\arraybackslash}p{5.5em}}{CU Boulder (N=362)} & \multicolumn{1}{>{\centering\arraybackslash}p{7.5em}}{UMass Amherst (N=296)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{U of Georgia (N=256)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{Rutgers (N=255)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of Cincinnati (N=243)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{U of Pitt (N=222)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{UC Berkeley (N=200)} & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{UC San Diego (N=192)} & \multicolumn{1}{>{\centering\arraybackslash}p{5.5em}}{U of Kansas (N=173)} & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{U of Arkansas (N=163)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.8em}}{SUNY Stony Brook (N=119)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{UNL (N=100)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{UC Riverside (N=88)}\\
\midrule
Notre Dame (N=625) & 43.0 & 48.5 & 59.4 & 44.3 & 43.8 & 46.7 & 44.4 & 57.7 & 51.0 & 55.7 & 52.0 & 33.7 & 42.0 & 43 & 39.8\\
Villanova (N=563) & 37.8 & 51.5 & 51.7 & 46.3 & 50.0 & 50.6 & 50.2 & 69.8 & 53.5 & 42.2 & 49.1 & 39.9 & 50.4 & 46 & 31.8\\
SMU (N=550) & 41.2 & 56.3 & 61.0 & 42.2 & 60.9 & 30.2 & 42.4 & 44.6 & 58.0 & 52.1 & 51.4 & 66.3 & 26.9 & 39 & 30.7\\
TCU (N=435) & 34.3 & 48.2 & 55.8 & 36.5 & 47.3 & 28.6 & 34.6 & 36.9 & 46.5 & 50.5 & 52.0 & 52.8 & 26.9 & 37 & 33.0\\
Tulane (N=430) & 29.0 & 40.2 & 49.2 & 38.5 & 46.5 & 26.7 & 29.6 & 36.9 & 52.5 & 39.1 & 33.5 & 41.7 & 20.2 & 22 & 27.3\\
Northwestern (N=377) & 24.2 & 34.3 & 44.2 & 27.4 & 40.2 & 24.3 & 35.4 & 33.3 & 52.5 & 43.2 & 37.0 & 30.7 & 12.6 & 31 & 31.8\\
Boston Coll. (N=339) & 24.5 & 30.6 & 39.5 & 37.8 & 28.9 & 27.1 & 23.5 & 30.6 & 37.0 & 44.8 & 29.5 & 19.6 & 19.3 & 21 & 26.1\\
Marquette (N=331) & 23.3 & 26.0 & 37.0 & 23.6 & 17.2 & 22.0 & 30.5 & 28.4 & 23.0 & 30.2 & 52.0 & 27.6 & 23.5 & 42 & 19.3\\
Tufts (N=301) & 18.4 & 26.8 & 38.4 & 32.4 & 27.7 & 20.4 & 17.3 & 28.8 & 43.5 & 45.3 & 20.8 & 18.4 & 21.8 & 14 & 27.3\\
U of Denver (N=279) & 17.9 & 25.0 & 38.4 & 25.7 & 18.8 & 18.0 & 23.5 & 19.8 & 27.5 & 37.0 & 39.9 & 24.5 & 11.8 & 27 & 19.3\\
Emory (N=273) & 21.6 & 30.3 & 28.7 & 18.6 & 34.4 & 18.4 & 24.7 & 21.2 & 38.0 & 26.0 & 16.2 & 17.8 & 8.4 & 8 & 12.5\\
Baylor (N=237) & 18.1 & 23.2 & 27.6 & 7.4 & 30.1 & 7.1 & 16.9 & 16.7 & 19.0 & 22.4 & 31.8 & 51.5 & 0.8 & 21 & 20.5\\
Case Western Res. (N=228) & 16.1 & 19.9 & 26.8 & 13.2 & 18.0 & 18.0 & 16.9 & 27.9 & 31.0 & 26.0 & 21.4 & 21.5 & 15.1 & 16 & 17.0\\
Stevens Ins. Tech (N=160) & 10.3 & 14.9 & 15.5 & 22.3 & 12.5 & 26.3 & 10.3 & 22.1 & 14.0 & 17.2 & 6.9 & 8.0 & 29.4 & 3 & 6.8\\
\bottomrule
\end{tabular}}
\end{table}

\clearpage
\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/nd_religion}

}

\caption{Order 2 ego network of University of Notre Dame, vertices colored by religion}\label{fig:nd-religion}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_count_pubu}

}

\caption{Number of visits to public and private high schools by public research universities}\label{fig:events-hs-count-pubu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_count_privu}

}

\caption{Number of visits to public and private high schools by selective private universities}\label{fig:events-hs-count-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_actual_proportional_pubu}

}

\caption{Actual versus proportional number of private school visits, public research universities}\label{fig:actual-proportional-pubu}
\end{figure}

\clearpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_actual_proportional_privu}

}

\caption{Actual versus proportional number of private school visits, selective private universities}\label{fig:actual-proportional-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_u}

}

\caption{One-mode network for public and private universities, colored by cluster}\label{fig:plot-1mode-u}
\end{figure}

\clearpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_region_pubu_privu}

}

\caption{Geographic region of visited private high schools}\label{fig:region-pubu-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_religion_pubu_privu}

}

\caption{Religious affiliation of visited private high schools}\label{fig:religion-pubu-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_rank_pubu_privu}

}

\caption{High school ranking of visited private high schools}\label{fig:rank-pubu-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_race_pubu_privhs_pubhs}

}

\caption{Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, public research universities}\label{fig:race-pubu-privhs-pubhs}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_race_privu_privhs_pubhs}

}

\caption{Percentage of students who identify as Black, Latinx, or Native at visited public high schools vs. visited private high schools, selective private universities}\label{fig:race-privu-privhs-pubhs}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_pubu_privhs_pubhs}

}

\caption{Percentage of students who identify as Black, Latinx, or Native at visited public high schools in the South vs. visited private high schools in the South, public research universities}\label{fig:south-race-pubu-privhs-pubhs}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_privu_privhs_pubhs}

}

\caption{Percentage of students who identify as Black, Latinx, or Native at visited public high schools in the South vs. visited private high schools in the South, selective private universities}\label{fig:south-race-privu-privhs-pubhs}
\end{figure}

\beginsupplement
\clearpage
\newpage

\begin{table}

\caption{\label{tab:pubu-count-matrix}One-mode public university count matrix}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{5.5em}>{\raggedleft\arraybackslash}p{7.5em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{5.5em}>{\raggedleft\arraybackslash}p{6.5em}>{\raggedleft\arraybackslash}p{8.8em}>{\raggedleft\arraybackslash}p{5em}>{\raggedleft\arraybackslash}p{6em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{U of Alabama (N=759)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of S.Carolina (N=396)} & \multicolumn{1}{>{\centering\arraybackslash}p{5.5em}}{CU Boulder (N=362)} & \multicolumn{1}{>{\centering\arraybackslash}p{7.5em}}{UMass Amherst (N=296)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{U of Georgia (N=256)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{Rutgers (N=255)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of Cincinnati (N=243)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{U of Pitt (N=222)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{UC Berkeley (N=200)} & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{UC San Diego (N=192)} & \multicolumn{1}{>{\centering\arraybackslash}p{5.5em}}{U of Kansas (N=173)} & \multicolumn{1}{>{\centering\arraybackslash}p{6.5em}}{U of Arkansas (N=163)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.8em}}{SUNY Stony Brook (N=119)} & \multicolumn{1}{>{\centering\arraybackslash}p{5em}}{UNL (N=100)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{UC Riverside (N=88)}\\
\midrule
U of Alabama (N=759) & 759 & 284 & 210 & 149 & 169 & 120 & 124 & 125 & 112 & 100 & 93 & 100 & 43 & 31 & 34\\
U of S.Carolina (N=396) & 284 & 396 & 155 & 108 & 140 & 74 & 110 & 99 & 84 & 59 & 58 & 57 & 27 & 20 & 19\\
CU Boulder (N=362) & 210 & 155 & 362 & 115 & 88 & 76 & 69 & 92 & 77 & 98 & 74 & 51 & 21 & 25 & 28\\
UMass Amherst (N=296) & 149 & 108 & 115 & 296 & 57 & 93 & 27 & 56 & 45 & 57 & 18 & 14 & 57 & 4 & 18\\
U of Georgia (N=256) & 169 & 140 & 88 & 57 & 256 & 24 & 73 & 48 & 64 & 38 & 39 & 59 & 7 & 13 & 16\\
Rutgers (N=255) & 120 & 74 & 76 & 93 & 24 & 255 & 35 & 74 & 41 & 43 & 20 & 5 & 48 & 10 & 10\\
U of Cincinnati (N=243) & 124 & 110 & 69 & 27 & 73 & 35 & 243 & 56 & 33 & 24 & 29 & 37 & 5 & 18 & 8\\
U of Pitt (N=222) & 125 & 99 & 92 & 56 & 48 & 74 & 56 & 222 & 41 & 28 & 32 & 26 & 27 & 15 & 11\\
UC Berkeley (N=200) & 112 & 84 & 77 & 45 & 64 & 41 & 33 & 41 & 200 & 61 & 30 & 26 & 9 & 8 & 20\\
UC San Diego (N=192) & 100 & 59 & 98 & 57 & 38 & 43 & 24 & 28 & 61 & 192 & 29 & 22 & 11 & 3 & 35\\
U of Kansas (N=173) & 93 & 58 & 74 & 18 & 39 & 20 & 29 & 32 & 30 & 29 & 173 & 62 & 0 & 61 & 8\\
U of Arkansas (N=163) & 100 & 57 & 51 & 14 & 59 & 5 & 37 & 26 & 26 & 22 & 62 & 163 & 1 & 24 & 9\\
SUNY Stony Brook (N=119) & 43 & 27 & 21 & 57 & 7 & 48 & 5 & 27 & 9 & 11 & 0 & 1 & 119 & 0 & 4\\
UNL (N=100) & 31 & 20 & 25 & 4 & 13 & 10 & 18 & 15 & 8 & 3 & 61 & 24 & 0 & 100 & 0\\
UC Riverside (N=88) & 34 & 19 & 28 & 18 & 16 & 10 & 8 & 11 & 20 & 35 & 8 & 9 & 4 & 0 & 88\\
\bottomrule
\end{tabular}}
\end{table}

\begin{table}

\caption{\label{tab:privu-count-matrix}One-mode private universities count matrix}
\centering
\resizebox{\linewidth}{!}{
\fontsize{13}{15}\selectfont
\begin{tabular}[t]{l>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{7em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{6em}>{\raggedleft\arraybackslash}p{8.5em}>{\raggedleft\arraybackslash}p{8.5em}}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Notre Dame (N=625)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Villanova (N=563)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{SMU (N=550)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{TCU (N=435)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Tulane (N=430)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Northwestern (N=377)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Boston Coll. (N=339)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{Marquette (N=331)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Tufts (N=301)} & \multicolumn{1}{>{\centering\arraybackslash}p{7em}}{U of Denver (N=279)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Emory (N=273)} & \multicolumn{1}{>{\centering\arraybackslash}p{6em}}{Baylor (N=237)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.5em}}{Case Western Res. (N=228)} & \multicolumn{1}{>{\centering\arraybackslash}p{8.5em}}{Stevens Ins. Tech (N=160)}\\
\midrule
Notre Dame (N=625) & 625 & 338 & 293 & 253 & 223 & 224 & 235 & 231 & 177 & 164 & 145 & 99 & 133 & 79\\
Villanova (N=563) & 338 & 563 & 291 & 224 & 218 & 214 & 208 & 205 & 161 & 143 & 147 & 101 & 142 & 103\\
SMU (N=550) & 293 & 291 & 550 & 290 & 275 & 243 & 218 & 151 & 189 & 177 & 176 & 154 & 134 & 88\\
TCU (N=435) & 253 & 224 & 290 & 435 & 199 & 177 & 168 & 150 & 141 & 151 & 122 & 133 & 98 & 66\\
Tulane (N=430) & 223 & 218 & 275 & 199 & 430 & 219 & 173 & 103 & 190 & 142 & 143 & 79 & 131 & 56\\
Northwestern (N=377) & 224 & 214 & 243 & 177 & 219 & 377 & 172 & 114 & 169 & 139 & 128 & 75 & 122 & 55\\
Boston Coll. (N=339) & 235 & 208 & 218 & 168 & 173 & 172 & 339 & 133 & 158 & 135 & 113 & 64 & 100 & 60\\
Marquette (N=331) & 231 & 205 & 151 & 150 & 103 & 114 & 133 & 331 & 77 & 97 & 52 & 62 & 66 & 43\\
Tufts (N=301) & 177 & 161 & 189 & 141 & 190 & 169 & 158 & 77 & 301 & 114 & 117 & 52 & 108 & 66\\
U of Denver (N=279) & 164 & 143 & 177 & 151 & 142 & 139 & 135 & 97 & 114 & 279 & 82 & 57 & 72 & 44\\
Emory (N=273) & 145 & 147 & 176 & 122 & 143 & 128 & 113 & 52 & 117 & 82 & 273 & 39 & 98 & 42\\
Baylor (N=237) & 99 & 101 & 154 & 133 & 79 & 75 & 64 & 62 & 52 & 57 & 39 & 237 & 50 & 23\\
Case Western Res. (N=228) & 133 & 142 & 134 & 98 & 131 & 122 & 100 & 66 & 108 & 72 & 98 & 50 & 228 & 41\\
Stevens Ins. Tech (N=160) & 79 & 103 & 88 & 66 & 56 & 55 & 60 & 43 & 66 & 44 & 42 & 23 & 41 & 160\\
\bottomrule
\end{tabular}}
\end{table}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_2mode_u}

}

\caption{Two-mode network for private high schools and all visiting universities, colored by cluster}\label{fig:plot-2mode}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_pubu}

}

\caption{Number of visits by type and in-state vs. out-of-state, public research universities}\label{fig:events-count-pubu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_privu}

}

\caption{Number of visits by type and in-state vs. out-of-state, selective private universities}\label{fig:events-count-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_pubu}

}

\caption{One-mode network for public research universities, colored by cluster}\label{fig:plot-1mode-pubu}
\end{figure}

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_privu}

}

\caption{One-mode network for selective private universities, colored by cluster}\label{fig:plot-1mode-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_enroll_pubu_privu}

}

\caption{12th grade enrollment of visited private high schools}\label{fig:enroll-pubu-privu}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_enroll_pubu_privhs_pubhs}

}

\caption{12th grade enrollment of visited private high schools vs. public high schools, public research universities}\label{fig:enroll-pubu-privhs-pubhs}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_comp_pubu_privhs_pubhs}

}

\caption{Racial composition of students at visited public high schools in the South vs. visited private high schools in the South, public research universities}\label{fig:south-race-comp-pubu-privhs-pubhs}
\end{figure}

\newpage

\begin{figure}

{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_comp_privu_privhs_pubhs}

}

\caption{Racial composition of students at visited public high schools in the South vs. visited private high schools in the South, selective private universities}\label{fig:south-race-comp-privu-privhs-pubhs}
\end{figure}

\end{landscape}

\restoregeometry

\end{document}

### 2023-12-28 r_r/submission/manuscript_rihe_r_r.Rmd
add revision submission files

--- 2023-12-21 r_r/manuscript_rihe_r_r.Rmd
@@
 #  - Irma Castañeda
-bibliography: ./../other/burd_recruiting_chapter.bib
+bibliography: ../../other/burd_recruiting_chapter.bib
 output:
+  #bookdown::word_document2:
   bookdown::pdf_document2:
@@
     pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
-csl: ./../other/apa.csl
+    keep_tex: true
+csl: ../../other/apa.csl
 urlcolor: blue
+#always_allow_html: true
 header-includes:
@@
 
-data_dir <- file.path('..', 'data')
-tables_dir <- file.path('..', 'assets', 'tables')
-figures_dir <- file.path('..', 'assets', 'figures')
+data_dir <- file.path('..', '..', 'data')
+tables_dir <- file.path('..', 'tables')
+figures_dir <- file.path('.')
 

### 2023-12-28 r_r/submission/manuscript_rihe_r_r.tex
add revision submission files

--- 2023-12-27 r_r/manuscript_rihe_r_r.tex
@@
+%!TEX TS-program = xelatex
+
 % Options for packages loaded elsewhere
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/nd_religion}
+{\centering \includegraphics[width=2\linewidth]{./nd_religion}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_count_pubu}
+{\centering \includegraphics[width=2\linewidth]{./events_hs_count_pubu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_count_privu}
+{\centering \includegraphics[width=2\linewidth]{./events_hs_count_privu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_actual_proportional_pubu}
+{\centering \includegraphics[width=2\linewidth]{./events_hs_actual_proportional_pubu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_hs_actual_proportional_privu}
+{\centering \includegraphics[width=2\linewidth]{./events_hs_actual_proportional_privu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_u}
+{\centering \includegraphics[width=2\linewidth]{./plot_1mode_u}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_region_pubu_privu}
+{\centering \includegraphics[width=2\linewidth]{./ego_network_region_pubu_privu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_religion_pubu_privu}
+{\centering \includegraphics[width=2\linewidth]{./ego_network_religion_pubu_privu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_rank_pubu_privu}
+{\centering \includegraphics[width=2\linewidth]{./ego_network_rank_pubu_privu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_race_pubu_privhs_pubhs}
+{\centering \includegraphics[width=2\linewidth]{./ego_network_race_pubu_privhs_pubhs}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_race_privu_privhs_pubhs}
+{\centering \includegraphics[width=2\linewidth]{./ego_network_race_privu_privhs_pubhs}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_pubu_privhs_pubhs}
+{\centering \includegraphics[width=2\linewidth]{./south_race_pubu_privhs_pubhs}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_privu_privhs_pubhs}
+{\centering \includegraphics[width=2\linewidth]{./south_race_privu_privhs_pubhs}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_2mode_u}
+{\centering \includegraphics[width=2\linewidth]{./plot_2mode_u}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_pubu}
+{\centering \includegraphics[width=2\linewidth]{./events_count_pubu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/events_count_privu}
+{\centering \includegraphics[width=2\linewidth]{./events_count_privu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_pubu}
+{\centering \includegraphics[width=2\linewidth]{./plot_1mode_pubu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/plot_1mode_privu}
+{\centering \includegraphics[width=2\linewidth]{./plot_1mode_privu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_enroll_pubu_privu}
+{\centering \includegraphics[width=2\linewidth]{./ego_network_enroll_pubu_privu}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/ego_network_enroll_pubu_privhs_pubhs}
+{\centering \includegraphics[width=2\linewidth]{./ego_network_enroll_pubu_privhs_pubhs}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_comp_pubu_privhs_pubhs}
+{\centering \includegraphics[width=2\linewidth]{./south_race_comp_pubu_privhs_pubhs}
 
@@
 
-{\centering \includegraphics[width=2\linewidth]{../assets/figures/south_race_comp_privu_privhs_pubhs}
+{\centering \includegraphics[width=2\linewidth]{./south_race_comp_privu_privhs_pubhs}
 

### 2024-01-27 index.qmd
test qmd slides

---
title: Title
bibliography: ./other/burd_recruiting_chapter.bib
format:
  revealjs: 
    embed-resources: true
    theme: sky
    controls: true
    controls-layout: bottom-right
    controls-tutorial: true
    transition: slide
    background-transition: fade
    auto-stretch: false
include-in-header: ./assets/html/header.html
css: ./assets/css/style.css
---

## Slide w/ bullets
### Bullets can appear one at a time

<hr>

::: {.incremental}
- Bullet
- Bullet
- Bullet
:::

## Slide w/ 2 columns {.smaller}

:::: {.columns}

::: {.column width="40%"}
![](https://www.r-project.org/logo/Rlogo.png)
:::

::: {.column width="60%"}
Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
:::

::::

## Slide w/ image {.smaller}

![](https://quarto.org/quarto.png)

## Slide w/ ggplot image

```{r}
library(ggplot2)

# Create data
data <- data.frame(
  name=c("A","B","C","D","E") ,  
  value=c(3,12,5,18,45)
  )

# Barplot
ggplot(data, aes(x=name, y=value)) + 
  geom_bar(stat = "identity")
```

## Slide w/ table

```{r}
library(kableExtra)

kable_styling(kbl(data))
```

## Slide w/ citation

@RN4504 said blah...

Parenthetical citation [@RN4625].

---

Slide w/ no title

## References

### 2024-01-27 assets/js/script.js

@@ -1,0 +1,23 @@
+$(function() {
+
+  const modal = '<div class="modal"><span class="close">&times;</span><h3></h3><img /></div>';
+  
+  $('.slides section').prepend(modal);
+  
+  $('.slides section img').on('click', function() {
+    let src = $(this).attr('src');
+    
+    var $slide = $(this).closest('.slide');
+    $slide.find('.modal img').attr('src', src);
+    
+    $(this).closest('.slide').find('.modal').fadeIn();
+  });
+  
+  $('.close').on('click', function() {
+    $(this).closest('.slide').find('.modal').fadeOut();
+  });
+  
+  Reveal.addEventListener('slidechanged', function() {
+    $('.modal').fadeOut();
+  });
+});

### 2024-02-06 index.qmd
update slides

@@
   revealjs: 
-    embed-resources: true
-    theme: sky
+    theme: [default, ./assets/css/custom.scss]
     controls: true
@@
 include-in-header: ./assets/html/header.html
-css: ./assets/css/style.css
+# https://github.com/quarto-dev/quarto-cli/discussions/5853#discussioncomment-6126603
+# filters:
+#   - /path/to/relevel_headings.lua
 ---
 
-## Slide w/ bullets
-### Bullets can appear one at a time
+```{r setup, include = FALSE}
+library(tidyverse)
+library(kableExtra)  # For collapse_rows() to work: https://stackoverflow.com/a/67803915/6373540
+library(readxl)
+
+knitr::opts_chunk$set(echo = F, message = F)
+
+data_dir <- file.path('.', 'data')
+tables_dir <- file.path('.', 'assets', 'tables')
+figures_dir <- file.path('.', 'assets', 'figures')
+
+univ_sample_df <- readRDS(file.path(data_dir, 'univ_sample.RDS')) %>%
+  arrange(desc(classification), rank)
+events_df <- readRDS(file.path(data_dir, 'events_data.RDS'))
+
+pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
+privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
+
+ego_df <- readRDS(file.path(tables_dir, 'table_ego_all.RDS')) %>% 
+  mutate(
+    univ_region = str_split(characteristics, '\\|', simplify = T)[,1],
+    univ_religion = str_split(characteristics, '\\|', simplify = T)[,2],
+    univ_race = round(as.numeric(str_split(characteristics, '\\|', simplify = T)[,3]), 1),
+    univ_rank = as.numeric(str_split(characteristics, '\\|', simplify = T)[,4]),
+    univ_enroll = format(as.numeric(str_split(characteristics, '\\|', simplify = T)[,5]), big.mark = ',')
+  )
+```
+
+## Characteristics of universities in analysis sample
+
+<div class="table-wrapper" id="tbl-1">
+```{r sample-characteristics}
+univ_sample <- univ_sample_df %>% 
+  filter(classification != 'private_libarts') %>% 
+  select(classification, univ_abbrev, rank, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal) %>% 
+  mutate(
+    classification = recode(
+      classification,
+      'public_research' = 'Public Research',
+      'private_national' = 'Private National'
+    ),
+    satactcomp25 = format(round(satactcomp25), big.mark = ',', trim = T),
+    satactcomp75 = format(round(satactcomp75), big.mark = ',', trim = T),
+    tfuginst = str_c('$', format(round(tfuginst), big.mark = ',', trim = T)),
+    tfugoutst = str_c('$', format(round(tfugoutst), big.mark = ',', trim = T)),
+    ugftptfreshtot = format(round(ugftptfreshtot), big.mark = ',', trim = T),
+    freshoutstpct = str_c(format(round(freshoutstpct * 100, 1), nsmall = 1), '%'),
+    pgrnt_p = str_c(format(round(pgrnt_p, 1), nsmall = 1), '%'),
+    pctfreshwh = str_c(format(round(pctfreshwh, 1), nsmall = 1), '%'),
+    pctfreshbl = str_c(format(round(pctfreshbl, 1), nsmall = 1), '%'),
+    pctfreshap = str_c(format(round(pctfreshap, 1), nsmall = 1), '%'),
+    pctfreshhi = str_c(format(round(pctfreshhi, 1), nsmall = 1), '%'),
+    pctfreshal = str_c(format(round(pctfreshal, 1), nsmall = 1), '%')
+  ) %>% 
+  arrange(desc(classification), rank)
+
+names(univ_sample) <- c('Classification', 'University', 'Rank', '25th Percentile SAT/ACT Composite Score', '75th Percentile SAT/ACT Composite Score', 'In-State Tuition + Fees', 'Out-of-State Tuition + Fees', 'Total Enrolled Freshmen', 'Percent<br>Out-of-State Freshmen', 'Percent Pell Recipients', 'Percent White Freshmen', 'Percent Black Freshmen', 'Percent Asian Freshmen', 'Percent Hispanic Freshmen', 'Percent International Freshmen')
+
+kbl(univ_sample, align = c('l', 'l', rep('r', 13)), escape = F) %>% 
+  collapse_rows(columns = 1, valign = 'middle') %>% 
+  column_spec(4, width_min = '1.2in') %>% 
+  column_spec(6, width_min = '0.9in') %>% 
+  column_spec(8, width_min = '0.9in')
+```
+</div>
+
+## Characteristics of universities in analysis sample compared to data collection sample
+
+<div class="table-wrapper">
+```{r sample-population-characteristics}
+cc2000_edition_data <- read_excel(file.path(data_dir, 'cc2000_edition_data.xls'), sheet = 'Data')
+pop_pubu <- (cc2000_edition_data %>% filter(`Control (text)` == 'Public', `CC2000 (text)` == 'Doctoral/Research Universities—Extensive'))$UNITID %>% as.character()
+
+usnews_rankings <- read_csv(file.path(data_dir, 'usnews_rankings.csv'), col_select = c('source', 'control', 'rank', 'univ_id'))
+pop_privu <- (usnews_rankings %>% filter(source == 'national-universities', control == 'private', rank <= 100))$univ_id %>% as.character()
+
+sample_pubu <- (univ_sample_df %>% filter(classification == 'public_research'))$univ_id
+sample_privu <- (univ_sample_df %>% filter(classification == 'private_national'))$univ_id
+
+univ_pop <- read.csv(file.path(data_dir, 'ipeds_data.csv'), header = TRUE, na.strings = c('', 'NULL', 'NA'), stringsAsFactors = FALSE, colClasses = c('unitid' = 'character')) %>% as_tibble() %>%
+  filter(endyear == 2017, unitid %in% c(pop_pubu, pop_privu, sample_pubu, sample_privu)) %>% 
+  select(unitid, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_n, cohortsfaef, ugftptfreshwhmf, ugftptfreshblmf, ugftptfreshapmf, ugftptfreshhimf, ugftptfreshalmf, ugftptfreshmrmf, ugftptfreshnamf, ugftptfreshunmf, ugftptfreshasmf, ugftptfreshnhmf) %>%
+  mutate(
+    pgrnt_p = pgrnt_n / cohortsfaef * 100,
+    pctfreshwh = ugftptfreshwhmf / ugftptfreshtot * 100,
+    pctfreshbl = ugftptfreshblmf / ugftptfreshtot * 100,
+    pctfreshap = ugftptfreshapmf / ugftptfreshtot * 100,  # ap = as + nh
+    pctfreshhi = ugftptfreshhimf / ugftptfreshtot * 100,
+    pctfreshal = ugftptfreshalmf / ugftptfreshtot * 100,
+    pctfreshmr = ugftptfreshmrmf / ugftptfreshtot * 100,
+    pctfreshna = ugftptfreshnamf / ugftptfreshtot * 100,
+    pctfreshun = ugftptfreshunmf / ugftptfreshtot * 100,
+    pctfreshas = ugftptfreshasmf / ugftptfreshtot * 100,
+    pctfreshnh = ugftptfreshnhmf / ugftptfreshtot * 100
+  ) %>% 
+  select(unitid, satactcomp25, satactcomp75, tfuginst, tfugoutst, ugftptfreshtot, freshoutstpct, pgrnt_p, pctfreshwh, pctfreshbl, pctfreshap, pctfreshhi, pctfreshal)
+
+format_data <- function(univ_ids) {
+  apply(univ_pop %>% filter(unitid %in% univ_ids) %>% select(-unitid), 2, function(x) quantile(x, probs = c(0.25, 0.5, 0.75), na.rm = T)) %>% 
+    as.data.frame() %>% 
+    mutate(
+      satactcomp25 = format(round(satactcomp25), big.mark = ',', trim = T),
+      satactcomp75 = format(round(satactcomp75), big.mark = ',', trim = T),
+      tfuginst = str_c('$', format(round(tfuginst), big.mark = ',', trim = T)),
+      tfugoutst = str_c('$', format(round(tfugoutst), big.mark = ',', trim = T)),
+      ugftptfreshtot = format(round(ugftptfreshtot), big.mark = ',', trim = T),
+      freshoutstpct = str_c(format(round(freshoutstpct * 100, 1), nsmall = 1), '%'),
+      pgrnt_p = str_c(format(round(pgrnt_p, 1), nsmall = 1), '%'),
+      pctfreshwh = str_c(format(round(pctfreshwh, 1), nsmall = 1), '%'),
+      pctfreshbl = str_c(format(round(pctfreshbl, 1), nsmall = 1), '%'),
+      pctfreshap = str_c(format(round(pctfreshap, 1), nsmall = 1), '%'),
+      pctfreshhi = str_c(format(round(pctfreshhi, 1), nsmall = 1), '%'),
+      pctfreshal = str_c(format(round(pctfreshal, 1), nsmall = 1), '%')
+    ) %>% 
+    t()
+}
+
+univ_pop_df <- cbind(
+  format_data(sample_pubu),
+  format_data(pop_pubu),
+  format_data(sample_privu),
+  format_data(pop_privu)
+)
+rownames(univ_pop_df) <- c('25th Percentile SAT/ACT Composite Score', '75th Percentile SAT/ACT Composite Score', 'In-State Tuition + Fees', 'Out-of-State Tuition + Fees', 'Total Enrolled Freshmen', 'Percent Out-of-State Freshmen', 'Percent Pell Recipients', 'Percent White Freshmen', 'Percent Black Freshmen', 'Percent Asian Freshmen', 'Percent Hispanic Freshmen', 'Percent International Freshmen')
+colnames(univ_pop_df) <- rep(c('25th percentile', '50th percentile', '75th percentile'), 4)
+
+kbl(univ_pop_df, align = 'r', escape = F) %>%
+  add_header_above(header = c(' ' = 1, 'Analysis sample (N=15)' = 3, 'Data collection sample (N=102)' = 3, 'Analysis sample (N=14)' = 3, 'Data collection sample (N=57)' = 3)) %>%
+  add_header_above(header = c(' ' = 1, 'Public research universities' = 6, 'Selective private universities' = 6)) %>% 
+  column_spec(1, bold = T) %>%
+  column_spec(2:13, width_min = '0.9in')
+```
+</div>
+
+## One-mode public university percent matrix
+
+<div class="table-wrapper tbl-1mode">
+```{r pubu-percent-matrix}
+table_1mode_pubu <- readRDS(file = file.path(tables_dir, 'table_1mode_pubu.RDS'))
+rownames(table_1mode_pubu$onemode_pct_df) <- colnames(table_1mode_pubu$onemode_pct_df)
+
+names(table_1mode_pubu$onemode_pct_df) <- str_replace(names(table_1mode_pubu$onemode_pct_df), ' \\(', '<br>(')
+
+kable(table_1mode_pubu$onemode_pct_df, align = 'r', escape = F) %>%
+  column_spec(1, bold = T) %>% 
+  column_spec(2:16, width_min = '0.9in')
+```
+</div>
+
+## One-mode private university percent matrix
+
+<div class="table-wrapper tbl-1mode">
+```{r privu-percent-matrix}
+table_1mode_privu <- readRDS(file = file.path(tables_dir, 'table_1mode_privu.RDS'))
+rownames(table_1mode_privu$onemode_pct_df) <- colnames(table_1mode_privu$onemode_pct_df)
+
+names(table_1mode_privu$onemode_pct_df) <- str_replace(names(table_1mode_privu$onemode_pct_df), ' \\(', '<br>(')
+
+kable(table_1mode_privu$onemode_pct_df, align = 'r', escape = F) %>%
+  column_spec(1, bold = T) %>% 
+  column_spec(2:15, width_min = '0.9in')
+```
+</div>
+
+## For private universities, the percent of high schools visited by public universities
+
+<div class="table-wrapper tbl-1mode">
+```{r privu-percent-visited-by-pubu-matrix}
+table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
+rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
+
+names(table_1mode_u$onemode_pct_df) <- str_replace(names(table_1mode_u$onemode_pct_df), ' \\(', '<br>(')
+
+kable(table_1mode_u$onemode_pct_df[c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29),c(2,3,4,5,6,8,10,11,12,14,15,19,20,26)], align = 'r', escape = F) %>%
+  column_spec(1, bold = T) %>% 
+  column_spec(2:15, width_min = '0.9in')
+```
+</div>
+
+## For public universities, the percent of high schools visited by private universities
+
+<div class="table-wrapper tbl-1mode">
+```{r pubu-percent-visited-by-privu-matrix}
+kable(table_1mode_u$onemode_pct_df[c(2,3,4,5,6,8,10,11,12,14,15,19,20,26),c(1,7,9,13,16,17,18,21,22,23,24,25,27,28,29)], align = 'r', escape = F) %>%
+  column_spec(1, bold = T) %>% 
+  column_spec(2:16, width_min = '0.9in')
+```
+</div>
+
+## Order 2 ego network of University of Notre Dame
+
+![](/assets/figures/nd_religion.png)
+
+## Number of HS visits by public research universities
+
+![](/assets/figures/events_hs_count_pubu.png)
+
+## Number of HS visits by selective private universities
+
+![](/assets/figures/events_hs_count_privu.png)
+
+## Proportional HS visits by public research universities
+
+![](/assets/figures/events_hs_actual_proportional_pubu.png)
+
+## Proportional HS visits by selective private universities
+
+![](/assets/figures/events_hs_actual_proportional_privu.png)
+
+## One-mode network for all universities
+
+![](/assets/figures/plot_1mode_u.png)
+
+## Geographic region of visited private high schools
+
+![](/assets/figures/ego_network_region_pubu_privu.png)
+
+## Religious affiliation of visited private high schools
+
+![](/assets/figures/ego_network_religion_pubu_privu.png)
+
+## High school ranking of visited private high schools
+
+![](/assets/figures/ego_network_rank_pubu_privu.png)
+
+## Racial composition of visited HS, public universities
+
+![](/assets/figures/ego_network_race_pubu_privhs_pubhs.png)
+
+## Racial composition of visited HS, private universities
+
+![](/assets/figures/ego_network_race_privu_privhs_pubhs.png)
+
+## Racial composition in the South, public universities
+
+![](/assets/figures/south_race_pubu_privhs_pubhs.png)
+
+## Racial composition in the South, private universities
+
+![](/assets/figures/south_race_privu_privhs_pubhs.png)
+
+## Slide w/ citation
+### Subtitle
 
@@
 
-::: {.incremental}
-- Bullet
-- Bullet
-- Bullet
-:::
+Here's some text:
 
-## Slide w/ 2 columns {.smaller}
+- @RN4504 said blah...
+- Parenthetical citation [@RN4625].
+- **Bold** and _italic_ text
 
-:::: {.columns}
+More things:
 
-::: {.column width="40%"}
-![](https://www.r-project.org/logo/Rlogo.png)
-:::
-
-::: {.column width="60%"}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.
-Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
-:::
-
-::::
-
-## Slide w/ image {.smaller}
-
-![](https://quarto.org/quarto.png)
-
-## Slide w/ ggplot image
-
-```{r}
-library(ggplot2)
-
-# Create data
-data <- data.frame(
-  name=c("A","B","C","D","E") ,  
-  value=c(3,12,5,18,45)
-  )
-
-# Barplot
-ggplot(data, aes(x=name, y=value)) + 
-  geom_bar(stat = "identity")
-```
-
-## Slide w/ table
-
-```{r}
-library(kableExtra)
-
-kable_styling(kbl(data))
-```
-
-## Slide w/ citation
-
-@RN4504 said blah...
-
-Parenthetical citation [@RN4625].
-
----
-
-Slide w/ no title
+- Blah
 

### 2024-02-06 assets/js/script.js

@@ -1,6 +1,6 @@
 $(function() {
 
-  const modal = '<div class="modal"><span class="close">&times;</span><h3></h3><img /></div>';
+  const modal = '<div class="modal"><span class="close">&times;</span><img /></div>';
   
   $('.slides section').prepend(modal);
   
@@ -10,14 +10,17 @@ $(function() {
     var $slide = $(this).closest('.slide');
     $slide.find('.modal img').attr('src', src);
     
-    $(this).closest('.slide').find('.modal').fadeIn();
+    $(this).closest('.slide').find('.modal').fadeIn(600);
+    $(this).closest('.slide').find('p img').addClass('disabled');
   });
   
   $('.close').on('click', function() {
     $(this).closest('.slide').find('.modal').fadeOut();
+    $(this).closest('.slide').find('p img').removeClass('disabled');
   });
   
   Reveal.addEventListener('slidechanged', function() {
     $('.modal').fadeOut();
+    $('img').removeClass('disabled');
   });
 });

### 2024-02-06 index.qmd
update filepaths

@@
 
-![](/assets/figures/nd_religion.png)
+![](./assets/figures/nd_religion.png)
 
@@
 
-![](/assets/figures/events_hs_count_pubu.png)
+![](./assets/figures/events_hs_count_pubu.png)
 
@@
 
-![](/assets/figures/events_hs_count_privu.png)
+![](./assets/figures/events_hs_count_privu.png)
 
@@
 
-![](/assets/figures/events_hs_actual_proportional_pubu.png)
+![](./assets/figures/events_hs_actual_proportional_pubu.png)
 
@@
 
-![](/assets/figures/events_hs_actual_proportional_privu.png)
+![](./assets/figures/events_hs_actual_proportional_privu.png)
 
@@
 
-![](/assets/figures/plot_1mode_u.png)
+![](./assets/figures/plot_1mode_u.png)
 
@@
 
-![](/assets/figures/ego_network_region_pubu_privu.png)
+![](./assets/figures/ego_network_region_pubu_privu.png)
 
@@
 
-![](/assets/figures/ego_network_religion_pubu_privu.png)
+![](./assets/figures/ego_network_religion_pubu_privu.png)
 
@@
 
-![](/assets/figures/ego_network_rank_pubu_privu.png)
+![](./assets/figures/ego_network_rank_pubu_privu.png)
 
@@
 
-![](/assets/figures/ego_network_race_pubu_privhs_pubhs.png)
+![](./assets/figures/ego_network_race_pubu_privhs_pubhs.png)
 
@@
 
-![](/assets/figures/ego_network_race_privu_privhs_pubhs.png)
+![](./assets/figures/ego_network_race_privu_privhs_pubhs.png)
 
@@
 
-![](/assets/figures/south_race_pubu_privhs_pubhs.png)
+![](./assets/figures/south_race_pubu_privhs_pubhs.png)
 
@@
 
-![](/assets/figures/south_race_privu_privhs_pubhs.png)
+![](./assets/figures/south_race_privu_privhs_pubhs.png)
 

### 2024-02-09 index.qmd
freeze headers of table

@@
 
-<div class="table-wrapper">
+<div class="table-wrapper freeze-col">
 ```{r sample-population-characteristics}

### 2024-02-14 r_r/manuscript_rihe_r_r.Rmd
changed the introduction per reviewer 2

@@
 
-*During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.] We are still trying to figure out what happened.*
-
-\bigskip
-
-Autumn is college recruiting visit season at Harpeth Hall, a nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
+Autumn is college recruiting season at Harpeth Hall, a nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
 Founded in 1951, Harpeth is an "A+" school ranked 337 in the nation according to the 2020 *Best Private High Schools in America* by Niche.
@@
 
-From September 6th through October 17th, Harpeth received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
+During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.] From September 6th through October 17th, Harpeth Hall received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
 Previous scholarship observes strong connections between private schools and selective private universities [@RN3519; @RN4407].
@@
 
-Father Ryan High School is a Catholic school founded in 1925.
-Father Ryan is predominantly white (86%, 7% Black or Latinx) and received an "A" grade from Niche, meaning it is not ranked in the top 1,000 U.S.
+Christ Presbyterian Academy, located in the Forest Hills suburb southwest of Nashville, received an "A" grade from Niche, meaning it is not ranked in the top 1,000 U.S.
 private schools.
-In Fall 2017, Father Ryan received visits from eight of the 14 private universities in our sample (including three of the four Catholic universities)<!--Changed nine to eight - Marquette (Catholic, univ_id: 239105) did not visit Father Ryan (school_id: 01294971)--> and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama.
-Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from six private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University).
+In 2017, it received visits from six private universities in our sample (including the three Christian universities, Baylor, Texas Christian University, and Southern Methodist University).
 It also received visits from the University of Cincinnati, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder.
@@
 
+This paper analyzes the social networks revealed by recruiting visits from universities to private high schools.
 Theories of organizational behavior suggest that university recruiting behaviors -- those that require significant expenditure -- are indicators of organizational enrollment priorities.
-Large, public-facing organizations are beset by multiple, competing pressures from the external environment, but organizations have difficulty pursuing multiple goals [@RN531; @RN959].
+Public-facing organizations are beset by multiple, competing pressures from the external environment, but organizations have difficulty pursuing multiple goals [@RN531; @RN959].
 Thus, organizations respond by symbolically adopting some goals and substantively adopting others [@RN513].
@@
 
+We situate this study within scholarship on nonresident enrollment at public universities.
 @RN4758 analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
@@
 
-Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college access [@RN4935; @RN4407; @RN1565; @RN786].
+A separate, multidisciplinary literature has analyzed linkages betwen private school and college access [@RN4935; @RN4407; @RN1565; @RN786].
 This research observes strong links -- and student flows -- between private high schools and selective private universities.
@@
 To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between private schools and colleges.
-We argue that these two stories have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities.
+
+We argue that these two literatures have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities.
 Simply put, selective private universities and public research universities are increasingly competing for students from the same set of affluent households.
@@
 
-This manuscript yields practical implications for public and private universities concerned about racial and socioeconomic diversity.
+The results yield practical implications for public and private universities concerned about racial and socioeconomic diversity.
 Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors [@RN4896; @RN4895; @eab_nacac_counselor_2023].

### 2024-02-14 r_r/manuscript_rihe_r_r.tex
changed the introduction per reviewer 2

@@
 \setcounter{secnumdepth}{5}
+% definitions for citeproc citations
+\NewDocumentCommand\citeproctext{}{}
+\NewDocumentCommand\citeproc{mm}{%
+  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
+\makeatletter
+ % allow citations to break across lines
+ \let\@cite@ofmt\@firstofone
+ % avoid brackets around text for \cite:
+ \def\@biblabel#1{}
+ \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
+\makeatother
 \newlength{\cslhangindent}
@@
 \setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
+\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
+ {\begin{list}{}{%
+  \setlength{\itemindent}{0pt}
+  \setlength{\leftmargin}{0pt}
+  \setlength{\parsep}{0pt}
   % turn on hanging indent if param 1 is 1
   \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
+   \setlength{\leftmargin}{\cslhangindent}
+   \setlength{\itemindent}{-1\cslhangindent}
   \fi
   % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
+  \setlength{\itemsep}{#2\baselineskip}}}
+ {\end{list}}
 \usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\usepackage{bookmark}
 \IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-\emph{During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.\footnote{These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.} We are still trying to figure out what happened.}
-
-\bigskip
-
-Autumn is college recruiting visit season at Harpeth Hall, a nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
+\section{Introduction}\label{introduction}
+
+Autumn is college recruiting season at Harpeth Hall, a nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
 Founded in 1951, Harpeth is an ``A+'' school ranked 337 in the nation according to the 2020 \emph{Best Private High Schools in America} by Niche.
@@
 
-From September 6th through October 17th, Harpeth received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
+During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.\footnote{These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.} From September 6th through October 17th, Harpeth Hall received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
 Previous scholarship observes strong connections between private schools and selective private universities (Khan, 2011; Stevens, 2007).
@@
 
-Father Ryan High School is a Catholic school founded in 1925.
-Father Ryan is predominantly white (86\%, 7\% Black or Latinx) and received an ``A'' grade from Niche, meaning it is not ranked in the top 1,000 U.S.
+Christ Presbyterian Academy, located in the Forest Hills suburb southwest of Nashville, received an ``A'' grade from Niche, meaning it is not ranked in the top 1,000 U.S.
 private schools.
-In Fall 2017, Father Ryan received visits from eight of the 14 private universities in our sample (including three of the four Catholic universities) and the same six public universities that visited Harpeth Hall, including two visits by the University of Alabama.
-Meanwhile, Christ Presbyterian Academy -- also not ranked in the top 1,000 private schools -- received visits from six private universities in our sample (including the three Christian universities Baylor, Texas Christian University, and Southern Methodist University).
+In 2017, it received visits from six private universities in our sample (including the three Christian universities, Baylor, Texas Christian University, and Southern Methodist University).
 It also received visits from the University of Cincinnati, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder.
@@
 
+This paper analyzes the social networks revealed by recruiting visits from universities to private high schools.
 Theories of organizational behavior suggest that university recruiting behaviors -- those that require significant expenditure -- are indicators of organizational enrollment priorities.
-Large, public-facing organizations are beset by multiple, competing pressures from the external environment, but organizations have difficulty pursuing multiple goals (Pfeffer \& Salancik, 1978; Thompson, 1967).
+Public-facing organizations are beset by multiple, competing pressures from the external environment, but organizations have difficulty pursuing multiple goals (Pfeffer \& Salancik, 1978; Thompson, 1967).
 Thus, organizations respond by symbolically adopting some goals and substantively adopting others (Meyer \& Rowan, 1977).
@@
 
+We situate this study within scholarship on nonresident enrollment at public universities.
 Author (XXXXa) analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
@@
 
-Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990).
+A separate, multidisciplinary literature has analyzed linkages betwen private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990).
 This research observes strong links -- and student flows -- between private high schools and selective private universities.
@@
 
-This manuscript yields practical implications for public and private universities concerned about racial and socioeconomic diversity.
+The results yield practical implications for public and private universities concerned about racial and socioeconomic diversity.
 Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors (EAB \& NACAC, 2023; Ruffalo Noel-Levitz, 2022a, 2022b).
@@
 
-\hypertarget{literature-review}{%
-\section{Literature Review}\label{literature-review}}
-
-\hypertarget{nonresident-enrollment-at-public-universities}{%
-\subsection{Nonresident Enrollment at Public Universities}\label{nonresident-enrollment-at-public-universities}}
+\section{Literature Review}\label{literature-review}
+
+\subsection{Nonresident Enrollment at Public Universities}\label{nonresident-enrollment-at-public-universities}
 
@@
 
-\hypertarget{linkages-between-private-schools-and-private-universities}{%
-\subsection{Linkages Between Private Schools and Private Universities}\label{linkages-between-private-schools-and-private-universities}}
+\subsection{Linkages Between Private Schools and Private Universities}\label{linkages-between-private-schools-and-private-universities}
 
@@
 
-\hypertarget{synthesis}{%
-\subsection{Synthesis}\label{synthesis}}
+\subsection{Synthesis}\label{synthesis}
 
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{data-and-sample}{%
-\subsection{Data and Sample}\label{data-and-sample}}
+\section{Methods}\label{methods}
+
+\subsection{Data and Sample}\label{data-and-sample}
 
@@
 
-\hypertarget{constructing-social-networks}{%
-\subsection{Constructing Social Networks}\label{constructing-social-networks}}
+\subsection{Constructing Social Networks}\label{constructing-social-networks}
 
@@
 
-\hypertarget{analyses}{%
-\subsection{Analyses}\label{analyses}}
+\subsection{Analyses}\label{analyses}
 
@@
 
-\hypertarget{limitations}{%
-\subsection{Limitations}\label{limitations}}
+\subsection{Limitations}\label{limitations}
 
@@
 
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-\hypertarget{rq1-scale-of-visits}{%
-\subsection{RQ1: Scale of visits}\label{rq1-scale-of-visits}}
+\section{Results}\label{results}
+
+\subsection{RQ1: Scale of visits}\label{rq1-scale-of-visits}
 
@@
 
-\hypertarget{rq2-overlapping-network-structure}{%
-\subsection{RQ2: Overlapping network structure}\label{rq2-overlapping-network-structure}}
+\subsection{RQ2: Overlapping network structure}\label{rq2-overlapping-network-structure}
 
@@
 
-\hypertarget{rq3-characteristics-of-visited-schools}{%
-\subsection{RQ3: Characteristics of visited schools}\label{rq3-characteristics-of-visited-schools}}
+\subsection{RQ3: Characteristics of visited schools}\label{rq3-characteristics-of-visited-schools}
 
@@
 
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-\hypertarget{summary}{%
-\subsection{Summary}\label{summary}}
+\section{Discussion}\label{discussion}
+
+\subsection{Summary}\label{summary}
 
@@
 
-\hypertarget{implications-for-scholarship}{%
-\subsection{Implications for Scholarship}\label{implications-for-scholarship}}
+\subsection{Implications for Scholarship}\label{implications-for-scholarship}
 
@@
 
-\hypertarget{implications-for-practice}{%
-\subsection{Implications for Practice}\label{implications-for-practice}}
+\subsection{Implications for Practice}\label{implications-for-practice}
 
@@
 
-\hypertarget{conflict-of-interest-statement}{%
-\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}}
+\section{Conflict of Interest Statement}\label{conflict-of-interest-statement}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\hypertarget{refs}{}
+\section{References}\label{references}
+
+\phantomsection\label{refs}
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-RN4758}{}}%
+\bibitem[\citeproctext]{ref-RN4758}
 Author. (XXXXa).
 
-\leavevmode\vadjust pre{\hypertarget{ref-list_biz}{}}%
+\bibitem[\citeproctext]{ref-list_biz}
 Author. (XXXXe).
 
-\leavevmode\vadjust pre{\hypertarget{ref-list_empirics}{}}%
+\bibitem[\citeproctext]{ref-list_empirics}
 Author. (XXXXf).
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN3753}{}}%
+\bibitem[\citeproctext]{ref-RN3753}
 Author. (XXXXb).
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN3685}{}}%
+\bibitem[\citeproctext]{ref-RN3685}
 Author. (XXXXc).
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4290}{}}%
+\bibitem[\citeproctext]{ref-RN4290}
 Author. (XXXXd).
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4953}{}}%
+\bibitem[\citeproctext]{ref-RN4953}
 Borgatti, S. P. (1998). Ego networks. Retrieved from \url{http://www.analytictech.com/networks/egonet.htm}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2457}{}}%
+\bibitem[\citeproctext]{ref-RN2457}
 Borgatti, S. P. (2008). 2-mode concepts in social network analysis. In \emph{Encyclopedia of complexity and system science}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN786}{}}%
+\bibitem[\citeproctext]{ref-RN786}
 Bryk, A. S., Lee, V. E., \& Holland, P. B. (1993). \emph{Catholic schools and the common good}. Cambridge: Harvard University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN975}{}}%
+\bibitem[\citeproctext]{ref-RN975}
 Burt, R. S. (1992). \emph{Structural holes: The social structure of competition}. Cambridge, MA: Harvard University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2772}{}}%
+\bibitem[\citeproctext]{ref-RN2772}
 Cheslock, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4935}{}}%
+\bibitem[\citeproctext]{ref-RN4935}
 Chetty, R., Deming, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4599}{}}%
+\bibitem[\citeproctext]{ref-RN4599}
 Clark, D., \& Del Bono, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4677}{}}%
+\bibitem[\citeproctext]{ref-RN4677}
 Clauset, A., Newman, M. E. J., \& Moore, C. (2004). Finding community structure in very large networks. \emph{Physical Review E}, \emph{70}(6). \url{https://doi.org/10.1103/PhysRevE.70.066111}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4937}{}}%
+\bibitem[\citeproctext]{ref-RN4937}
 Coleman, J. S., \& Hoffer, T. (1987). \emph{Public and private high schools: The impact of communities} (pp. xxviii, 254 p.). New York: Basic Books.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4647}{}}%
+\bibitem[\citeproctext]{ref-RN4647}
 Cookson, P. W., \& Persell, C. H. (1985). \emph{Preparing for power : America's elite boarding schools} (pp. x, 260 p.). New York: Basic Books.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN1791}{}}%
+\bibitem[\citeproctext]{ref-RN1791}
 Curs, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2287}{}}%
+\bibitem[\citeproctext]{ref-RN2287}
 Curs, B.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4663}{}}%
+\bibitem[\citeproctext]{ref-RN4663}
 Davis, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2271}{}}%
+\bibitem[\citeproctext]{ref-RN2271}
 Delaney, J. A., \& Doyle, W. R. (2011). State spending on higher education: Testing the balance wheel over time. \emph{Journal of Education Finance}, \emph{36}(4), 343--368. Journal Article.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN3524}{}}%
+\bibitem[\citeproctext]{ref-RN3524}
 DesJardins, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-eab_nacac_counselor_2023}{}}%
+\bibitem[\citeproctext]{ref-eab_nacac_counselor_2023}
 EAB, \& NACAC.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4936}{}}%
+\bibitem[\citeproctext]{ref-RN4936}
 Eide, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4116}{}}%
+\bibitem[\citeproctext]{ref-RN4116}
 Eisenhardt, K. M. (1989). Building theories from case study research. \emph{Academy of Management Review}, \emph{14}(4), 532--550. \url{https://doi.org/10.2307/258557}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4642}{}}%
+\bibitem[\citeproctext]{ref-RN4642}
 Falsey, B., \& Heyns, B. (1984). The college channel: Private and public schools reconsidered. \emph{Sociology of Education}, \emph{57}(2), 111--122. \url{https://doi.org/10.2307/2112633}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4724}{}}%
+\bibitem[\citeproctext]{ref-RN4724}
 Graham, L. (1999). \emph{Our kind of people: Inside america's black upper class} (1st ed., pp. xii, 418 pages, 16 unnumbered pages of plates). New York: HarperCollins.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4625}{}}%
+\bibitem[\citeproctext]{ref-RN4625}
 Hill, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4324}{}}%
+\bibitem[\citeproctext]{ref-RN4324}
 Holland, M. M. (2019). \emph{Divergent paths to college: Race, class, and inequality in high schools}. Rutgers University Press. \url{https://doi.org/10.36019/9780813590288}
 
-\leavevmode\vadjust pre{\hypertarget{ref-em_burnout_hoover}{}}%
+\bibitem[\citeproctext]{ref-em_burnout_hoover}
 Hoover, E.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2133}{}}%
+\bibitem[\citeproctext]{ref-RN2133}
 Hoxby, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4495}{}}%
+\bibitem[\citeproctext]{ref-RN4495}
 Jack, A.
@@
 Cambridge, Massachusetts: Harvard University Press,.
-Retrieved from \href{Restricted\%20to\%20UCLA.\%20Limited\%20to\%20three\%20concurrent\%20users.\%20Try\%20again\%20later\%20if\%20unavailable.\%20http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&__char_set=utf8\&isbn=9780674239647}{Restricted to UCLA.
+Retrieved from \href{Restricted\%20to\%20UCLA.\%20Limited\%20to\%20three\%20concurrent\%20users.\%20Try\%20again\%20later\%20if\%20unavailable.\%20http://openurl.cdlib.org?sid=UCLA:CAT&genre=book&__char_set=utf8&isbn=9780674239647}{Restricted to UCLA.
 Limited to three concurrent users.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4596}{}}%
+\bibitem[\citeproctext]{ref-RN4596}
 Jerrim, J., Parker, P.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4321}{}}%
+\bibitem[\citeproctext]{ref-RN4321}
 Khan, S. R. (2010). \emph{Getting in: How elite schools play the college game} (pp. 97--113). Rowman \& Littlefield.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4407}{}}%
+\bibitem[\citeproctext]{ref-RN4407}
 Khan, S. R. (2011). \emph{Privilege: The making of an adolescent elite at st. Paul's school} (pp. 232 pages). Princeton, N.J.: Princeton University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN3522}{}}%
+\bibitem[\citeproctext]{ref-RN3522}
 Killgore, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN1565}{}}%
+\bibitem[\citeproctext]{ref-RN1565}
 Kingston, P. W., \& Lewis, L. S. (1990). \emph{The high-status track: Studies of elite schools and stratification} (pp. xxxiv, 261 p.). Albany: State University of New York Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4614}{}}%
+\bibitem[\citeproctext]{ref-RN4614}
 Klugman, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4725}{}}%
+\bibitem[\citeproctext]{ref-RN4725}
 Kolaczyk, E. D., \& Csárdi, G. (2020). \emph{Statistical analysis of network data with r} (2nd ed, p. 235). Cham: Springer,. \url{https://doi.org/10.1007/978-3-030-44129-6}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN3762}{}}%
+\bibitem[\citeproctext]{ref-RN3762}
 Leeds, D.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4643}{}}%
+\bibitem[\citeproctext]{ref-RN4643}
 Levine, S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2546}{}}%
+\bibitem[\citeproctext]{ref-RN2546}
 Mak, J., \& Moncur, J. E. T. (2003). Interstate migration of college freshmen. \emph{Annals of Regional Science}, \emph{37}(4), 603--612. \url{https://doi.org/10.1007/s00168-003-0130-4}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN1722}{}}%
+\bibitem[\citeproctext]{ref-RN1722}
 McPherson, M., Smith-Lovin, L., \& Cook, J.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN513}{}}%
+\bibitem[\citeproctext]{ref-RN513}
 Meyer, J. W., \& Rowan, B. (1977). Institutionalized organizations: Formal structure as myth and ceremony. \emph{The American Journal of Sociology}, \emph{83}(2), 340--363.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2536}{}}%
+\bibitem[\citeproctext]{ref-RN2536}
 Mixon, F. G., \& Hsing, Y. (1994). The determinants of out-of-state enrollments in higher education: A tobit analysis. \emph{Economics of Education Review}, \emph{13}(4), 295--335.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4504}{}}%
+\bibitem[\citeproctext]{ref-RN4504}
 Murnane, R. J., \& Reardon, S. F. (2018). Long-term trends in private school enrollments by family income. \emph{AERA Open}, \emph{4}(1), 1--24. \url{https://doi.org/10.1177/2332858417751355}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4938}{}}%
+\bibitem[\citeproctext]{ref-RN4938}
 Neal, D. (1997). The effects of catholic secondary schooling on educational achievement. \emph{Journal of Labor Economics}, \emph{15}(1), 98--123. \url{https://doi.org/10.1086/209848}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4634}{}}%
+\bibitem[\citeproctext]{ref-RN4634}
 Persell, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4640}{}}%
+\bibitem[\citeproctext]{ref-RN4640}
 Persell, C.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN959}{}}%
+\bibitem[\citeproctext]{ref-RN959}
 Pfeffer, J., \& Salancik, G. R. (1978). \emph{The external control of organizations: A resource dependence perspective} (pp. xiii, 300 p.). New York: Harper \& Row.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN1577}{}}%
+\bibitem[\citeproctext]{ref-RN1577}
 Priest, D. M., \& St. John, E. P. (2006). \emph{Privatization and public universities} (pp. 299 p.). Bloomington: Indiana University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4588}{}}%
+\bibitem[\citeproctext]{ref-RN4588}
 Purdy, M. A. (2018). \emph{Transforming the elite: Black students and the desegregation of private schools} (pp. 1--243). \url{https://doi.org/10.5149/northcarolina/9781469643496.001.0001}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4589}{}}%
+\bibitem[\citeproctext]{ref-RN4589}
 Reeves, A., Friedman, S., Rahal, C., \& Flemmen, M.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4911}{}}%
+\bibitem[\citeproctext]{ref-RN4911}
 Rivard, R.
@@
 \emph{InsideHigherEd}, (Oct 24).
-Retrieved from \url{https://www.insidehighered.com/news/2013/10/24/political-campaign-style-targeting-comes-student-search?width=775\&height=500\&iframe=true}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN3608}{}}%
+Retrieved from \url{https://www.insidehighered.com/news/2013/10/24/political-campaign-style-targeting-comes-student-search?width=775&height=500&iframe=true}
+
+\bibitem[\citeproctext]{ref-RN3608}
 Rudolph, F. (1962). \emph{The american college and university: A history} (1st ed., pp. 516 p.). New York: Alfred A. Knopf.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4402}{}}%
+\bibitem[\citeproctext]{ref-RN4402}
 Ruffalo Noel-Levitz.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4664}{}}%
+\bibitem[\citeproctext]{ref-RN4664}
 Ruffalo Noel-Levitz.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-parents_covid_rnl}{}}%
+\bibitem[\citeproctext]{ref-parents_covid_rnl}
 Ruffalo Noel-Levitz.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4896}{}}%
+\bibitem[\citeproctext]{ref-RN4896}
 Ruffalo Noel-Levitz.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4895}{}}%
+\bibitem[\citeproctext]{ref-RN4895}
 Ruffalo Noel-Levitz.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4934}{}}%
+\bibitem[\citeproctext]{ref-RN4934}
 Salazar, K.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN1118}{}}%
+\bibitem[\citeproctext]{ref-RN1118}
 Slaughter, S., \& Rhoades, G. (2004). \emph{Academic capitalism and the new economy} (pp. xii, 370 p.). Baltimore: Johns Hopkins University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN3519}{}}%
+\bibitem[\citeproctext]{ref-RN3519}
 Stevens, M. L. (2007). \emph{Creating a class: College admissions and the education of elites} (pp. 308 p.). Cambridge, MA: Harvard University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4648}{}}%
+\bibitem[\citeproctext]{ref-RN4648}
 Stone, T.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN531}{}}%
+\bibitem[\citeproctext]{ref-RN531}
 Thompson, J. D. (1967). \emph{Organizations in action}. New York: McGraw Hill.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4954}{}}%
+\bibitem[\citeproctext]{ref-RN4954}
 U.S.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN1549}{}}%
+\bibitem[\citeproctext]{ref-RN1549}
 Winston, G.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4011}{}}%
+\bibitem[\citeproctext]{ref-RN4011}
 Yin, R. K. (2009). \emph{Case study research: Design and methods} (4th ed., pp. xiv, 219 p.). Los Angeles: Sage Publications.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2535}{}}%
+\bibitem[\citeproctext]{ref-RN2535}
 Zhang, L.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4758}{}}%
+\bibitem[\citeproctext]{ref-RN4758}
 Author. (XXXXa).
 
-\leavevmode\vadjust pre{\hypertarget{ref-list_biz}{}}%
+\bibitem[\citeproctext]{ref-list_biz}
 Author. (XXXXe).
 
-\leavevmode\vadjust pre{\hypertarget{ref-list_empirics}{}}%
+\bibitem[\citeproctext]{ref-list_empirics}
 Author. (XXXXf).
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN3753}{}}%
+\bibitem[\citeproctext]{ref-RN3753}
 Author. (XXXXb).
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN3685}{}}%
+\bibitem[\citeproctext]{ref-RN3685}
 Author. (XXXXc).
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4290}{}}%
+\bibitem[\citeproctext]{ref-RN4290}
 Author. (XXXXd).
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN4953}{}}%
+\bibitem[\citeproctext]{ref-RN4953}
 Borgatti, S. P. (1998). Ego networks. Retrieved from \url{http://www.analytictech.com/networks/egonet.htm}
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2457}{}}%
+\bibitem[\citeproctext]{ref-RN2457}
 Borgatti, S. P. (2008). 2-mode concepts in social network analysis. In \emph{Encyclopedia of complexity and system science}.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN786}{}}%
+\bibitem[\citeproctext]{ref-RN786}
 Bryk, A. S., Lee, V. E., \& Holland, P. B. (1993). \emph{Catholic schools and the common good}. Cambridge: Harvard University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN975}{}}%
+\bibitem[\citeproctext]{ref-RN975}
 Burt, R. S. (1992). \emph{Structural holes: The social structure of competition}. Cambridge, MA: Harvard University Press.
 
-\leavevmode\vadjust pre{\hypertarget{ref-RN2772}{}}%
+\bibitem[\citeproctext]{ref-RN2772}
 Cheslock, J.

### 2024-02-15 r_r/submission/manuscript_rihe_r_r.Rmd
update submission for revision 2

@@
 data_dir <- file.path('..', '..', 'data')
-tables_dir <- file.path('..', 'tables')
+tables_dir <- file.path('..', '..', 'assets', 'tables')
 figures_dir <- file.path('.')
@@
 
-Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college access [@RN4935; @RN4407; @RN1565; @RN786].
+A separate, multidisciplinary literature has analyzed linkages between private school and college access [@RN4935; @RN4407; @RN1565; @RN786].
 This research observes strong links -- and student flows -- between private high schools and selective private universities.

### 2024-02-15 r_r/submission/manuscript_rihe_r_r.tex
update submission for revision 2

@@
 ]{article}
+\title{The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities}
+\author{}
+\date{\vspace{-2.5em}}
+
 \usepackage{amsmath,amssymb}
+\usepackage{lmodern}
 \usepackage{iftex}
@@
 \else % if luatex or xetex
-  \usepackage{unicode-math} % this also loads fontspec
+  \usepackage{unicode-math}
   \defaultfontfeatures{Scale=MatchLowercase}
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else
-  % xetex/luatex font selection
 \fi
@@
 \usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities},
+  colorlinks=true,
+  linkcolor={Maroon},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={blue},
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
@@
 \fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same}
-\hypersetup{
-  pdftitle={The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities},
-  colorlinks=true,
-  linkcolor={Maroon},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={blue},
-  pdfcreator={LaTeX via pandoc}}
-
-\title{The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities}
-\author{}
-\date{\vspace{-2.5em}}
 
@@
 
-\emph{During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.\footnote{These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.} We are still trying to figure out what happened.}
-
-\bigskip
-
-Autumn is college recruiting visit season at Harpeth Hall, a nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
+Autumn is college recruiting season at Harpeth Hall, a nonsectarian private school for girls located in the affluent Green Hills neighborhood of Nashville, Tennessee.
 Founded in 1951, Harpeth is an ``A+'' school ranked 337 in the nation according to the 2020 \emph{Best Private High Schools in America} by Niche.
@@
 
-Within scholarship on social mobility and social stratification, a multidisciplinary literature analyzes the relationship between private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990).
+A separate, multidisciplinary literature has analyzed linkages between private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990).
 This research observes strong links -- and student flows -- between private high schools and selective private universities.
@@
 \emph{Economics of Education Review}, \emph{21}(2), 111--124.
-Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000173740100002}{\textless Go to ISI\textgreater://000173740100002}
+Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://000173740100002}
 
@@
 Journal Article.
-Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://WOS:000256634400003}{\textless Go to ISI\textgreater://WOS:000256634400003}
+Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://WOS:000256634400003}
 
@@
 Cambridge, Massachusetts: Harvard University Press,.
-Retrieved from \href{Restricted\%20to\%20UCLA.\%20Limited\%20to\%20three\%20concurrent\%20users.\%20Try\%20again\%20later\%20if\%20unavailable.\%20http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&__char_set=utf8\&isbn=9780674239647}{Restricted to UCLA.
-Limited to three concurrent users.
-Try again later if unavailable.
-http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&\_\_char\_set=utf8\&isbn=9780674239647}
+Retrieved from \url{Restricted\%20to\%20UCLA.\%20Limited\%20to\%20three\%20concurrent\%20users.\%20Try\%20again\%20later\%20if\%20unavailable.\%20http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&__char_set=utf8\&isbn=9780674239647}
 
@@
 \emph{Review of Higher Education}, \emph{32}(4), 469--488.
-Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://WOS:000266737500002}{\textless Go to ISI\textgreater://WOS:000266737500002}
+Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://WOS:000266737500002}
 
@@
 Journal Article.
-Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000170748100017}{\textless Go to ISI\textgreater://000170748100017}
+Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://000170748100017}
 
@@
 \emph{Journal of Economic Perspectives}, \emph{13}(1), 13--36.
-Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000078904300002}{\textless Go to ISI\textgreater://000078904300002}
+Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://000078904300002}
 

### 2024-02-15 index.qmd
started revising soc of ed presentation

--- 2024-02-06 index.qmd
@@
 ---
-title: Title
+title: "The Private School Network"
+subtitle: "Recruiting Visits to Private High Schools by Public and Private Universities"
 bibliography: ./other/burd_recruiting_chapter.bib
@@
     auto-stretch: false
+    slide-level: 3
 include-in-header: ./assets/html/header.html
@@
 
-## Characteristics of universities in analysis sample
+# Motivation
 
-<div class="table-wrapper" id="tbl-1">
+### Motivation
+
+#### Off-campus recruiting visits to high schools in Nashville
+
+CRYSTAL: INSERT MAP HERE
+
+### Motivation
+
+-   Recruiting visit indicates university and school have social relationship
+-   Visits (edges) from university (mode 1) to high school (mode 2) yields a two-mode social network
+-   Comparing recruiting network of public research and selective private universities gives insight about competition for affluent students
+
+Research questions
+
+1.  How does the scale of visits to private high schools vary for the public research universities and selective private universities?
+2.  To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
+3.  What are the characteristics of private schools that receive visits from public research universities and selective private research universities?
+
+# Literature Review
+
+### Research on nonresident enrollment at public universities
+
+- Increase nonresident enrollment in response to declines in state funding  [@RN3753]
+- Nonresident students more affluent, less likely to be Black or Latinx [@RN3685]
+
+Interventions to attract nonresident students
+
+- Institutional financial aid [@RN3762]
+- Recruiting to solicit 'inquiries' and applications
+  - "Student list" purchases [@RN4985]
+  - Off-campus recruiting visits [@RN4758; @RN4934]
+    - Out-of state visits to public high schools focus on affluent public schools, avoid non-white communities
+
+### Research on links between private schools and private universities
+
+Studies find attending private school increases college access, selectivity
+
+- Public school students: 5% attend "top 100" public univ; 2% attend top 100 private univ (Author calculations from HSLS 2009)
+- Private school: 11% attend top 100 public; 17% attend top 100 private
+- Nonsectarian private: 11% attend top 100 public; 40% attend top 100 private
+
+Research from economics [@RN4935]
+
+- Rich students have higher non-academic ratings because they attend elite private schools (extracurricular activities, recommendations)
+
+Research from sociology highlights organizational linkages [@RN4935]
+
+### slide title
+#### slide sub-title
+
+<hr>
+
+Here's some text:
+
+-   @RN4504 said blah...
+-   Parenthetical citation [@RN4625].
+-   **Bold** and *italic* text
+
+More things:
+
+-   Blah
+
+# Methods
+
+## Data and Sample
+
+### Characteristics of universities in analysis sample
+
+::: {#tbl-1 .table-wrapper}
 ```{r sample-characteristics}
@@
 ```
-</div>
+:::
 
-## Characteristics of universities in analysis sample compared to data collection sample
+### Characteristics of universities in analysis sample compared to data collection sample
 
-<div class="table-wrapper">
+::: {.table-wrapper .freeze-col}
 ```{r sample-population-characteristics}
@@
 ```
-</div>
+:::
 
-## One-mode public university percent matrix
+## Constructing Social Networks
 
-<div class="table-wrapper tbl-1mode">
+## Analyses
+
+# Results
+
+## RQ1: Scale of Visits
+
+### Number of HS visits by public research universities
+
+![](./assets/figures/events_hs_count_pubu.png)
+
+### Number of HS visits by selective private universities
+
+![](./assets/figures/events_hs_count_privu.png)
+
+### Proportional HS visits by public research universities
+
+![](./assets/figures/events_hs_actual_proportional_pubu.png)
+
+### Proportional HS visits by selective private universities
+
+![](./assets/figures/events_hs_actual_proportional_privu.png)
+
+## RQ2: Overlap of Visits
+
+### One-mode percent matrix, all universities
+
+CRYSTAL: CREATE ONE-MODE PERCENT MATRIX FOR ALL UNIVERSITIES; FREEZING PANES FOR FIRST COLUMN AND FIRST ROW
+
+### One-mode network for all universities
+
+![](./assets/figures/plot_1mode_u.png)
+
+## RQ3: Characteristics of Visited Schools
+
+### Order 2 ego network of University of Notre Dame
+
+![](./assets/figures/nd_religion.png)
+
+### Geographic region of visited private high schools
+
+![](./assets/figures/ego_network_region_pubu_privu.png)
+
+### Religious affiliation of visited private high schools
+
+![](./assets/figures/ego_network_religion_pubu_privu.png)
+
+### Racial composition of visited HS, public universities
+
+![](./assets/figures/ego_network_race_pubu_privhs_pubhs.png)
+
+### Racial composition of visited HS, private universities
+
+![](./assets/figures/ego_network_race_privu_privhs_pubhs.png)
+
+### High school ranking of visited private high schools
+
+![](./assets/figures/ego_network_rank_pubu_privu.png)
+
+# Discussion
+
+### Slide w/ citation
+
+#### Subtitle
+
+<hr>
+
+Here's some text:
+
+-   @RN4504 said blah...
+-   Parenthetical citation [@RN4625].
+-   **Bold** and *italic* text
+
+More things:
+
+-   Blah
+
+### References
+
+::: {#refs}
+:::
+
+# Appendix
+
+## RQ1: Scale of Visits
+
+### All recruiting visits, public research universities
+
+![](./assets/figures/events_count_pubu.png)
+
+### All recruiting visits, public research universities
+
+![](./assets/figures/events_count_privu.png)
+
+## RQ2: Overlap of Visits
+
+### One-mode public university percent matrix
+
+::: {.table-wrapper .tbl-1mode}
 ```{r pubu-percent-matrix}
@@
 ```
-</div>
+:::
 
-## One-mode private university percent matrix
+### One-mode network, public universities
 
-<div class="table-wrapper tbl-1mode">
+![](./assets/figures/plot_1mode_pubu.png)
+
+### One-mode network, public universities
+
+![](./assets/figures/plot_1mode_privu.png)
+
+### One-mode private university percent matrix
+
+::: {.table-wrapper .tbl-1mode}
 ```{r privu-percent-matrix}
@@
 ```
-</div>
+:::
 
-## For private universities, the percent of high schools visited by public universities
+### For private universities, the percent of high schools visited by public universities
 
-<div class="table-wrapper tbl-1mode">
+::: {.table-wrapper .tbl-1mode}
 ```{r privu-percent-visited-by-pubu-matrix}
@@
 ```
-</div>
+:::
 
-## For public universities, the percent of high schools visited by private universities
+### For public universities, the percent of high schools visited by private universities
 
-<div class="table-wrapper tbl-1mode">
+::: {.table-wrapper .tbl-1mode}
 ```{r pubu-percent-visited-by-privu-matrix}
@@
 ```
-</div>
+:::
 
-## Order 2 ego network of University of Notre Dame
+## RQ3: Characteristics of Visited Schools
 
-![](./assets/figures/nd_religion.png)
-
-## Number of HS visits by public research universities
-
-![](./assets/figures/events_hs_count_pubu.png)
-
-## Number of HS visits by selective private universities
-
-![](./assets/figures/events_hs_count_privu.png)
-
-## Proportional HS visits by public research universities
-
-![](./assets/figures/events_hs_actual_proportional_pubu.png)
-
-## Proportional HS visits by selective private universities
-
-![](./assets/figures/events_hs_actual_proportional_privu.png)
-
-## One-mode network for all universities
-
-![](./assets/figures/plot_1mode_u.png)
-
-## Geographic region of visited private high schools
-
-![](./assets/figures/ego_network_region_pubu_privu.png)
-
-## Religious affiliation of visited private high schools
-
-![](./assets/figures/ego_network_religion_pubu_privu.png)
-
-## High school ranking of visited private high schools
-
-![](./assets/figures/ego_network_rank_pubu_privu.png)
-
-## Racial composition of visited HS, public universities
-
-![](./assets/figures/ego_network_race_pubu_privhs_pubhs.png)
-
-## Racial composition of visited HS, private universities
-
-![](./assets/figures/ego_network_race_privu_privhs_pubhs.png)
-
-## Racial composition in the South, public universities
+### Racial composition in the South, public universities
 
@@
 
-## Racial composition in the South, private universities
+### Racial composition in the South, private universities
 
 ![](./assets/figures/south_race_privu_privhs_pubhs.png)
-
-## Slide w/ citation
-### Subtitle
-
-<hr>
-
-Here's some text:
-
-- @RN4504 said blah...
-- Parenthetical citation [@RN4625].
-- **Bold** and _italic_ text
-
-More things:
-
-- Blah
-
-## References

### 2024-02-16 index.qmd
update tables

@@
   column_spec(4, width_min = '1.2in') %>% 
-  column_spec(6, width_min = '0.9in') %>% 
-  column_spec(8, width_min = '0.9in')
+  column_spec(6, width_min = '1in') %>% 
+  column_spec(8, width_min = '1in')
 ```
@@
 
-::: {.table-wrapper .freeze-col}
+::: {#tbl-2 .table-wrapper}
 ```{r sample-population-characteristics}
@@
 
-CRYSTAL: CREATE ONE-MODE PERCENT MATRIX FOR ALL UNIVERSITIES; FREEZING PANES FOR FIRST COLUMN AND FIRST ROW
+::: {.table-wrapper .tbl-1mode}
+```{r pubu-privu-1mode}
+table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
+rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
+
+names(table_1mode_u$onemode_pct_df) <- str_replace(names(table_1mode_u$onemode_pct_df), ' \\(', '<br>(')
+
+kable(table_1mode_u$onemode_pct_df, align = 'r', escape = F) %>%
+  column_spec(1, bold = T) %>% 
+  column_spec(2:30, width_min = '0.9in')
+```
+:::
 

### 2024-02-16 index.qmd
working through presentation

@@
 
-# Motivation
+# Introduction
 
-### Motivation
-
-#### Off-campus recruiting visits to high schools in Nashville
+### Off-campus recruiting visits to high schools in Nashville
 
@@
 
-### Motivation
+### Setup
 
--   Recruiting visit indicates university and school have social relationship
--   Visits (edges) from university (mode 1) to high school (mode 2) yields a two-mode social network
--   Comparing recruiting network of public research and selective private universities gives insight about competition for affluent students
+Recruiting visit indicates university and school have social relationship
+
+- The university wants to enroll some students from the school
+- The school wants to send some students to the university
+
+Visits from universities to schools yields a two-mode social network
+
+- "Edges" = visits; "Vertices" = schools (mode 1) and universities (mode 2)
 
@@
 
-### Research on nonresident enrollment at public universities
+### Literature Review
+#### Nonresident enrollment at public universities
 
@@
 
-- Institutional financial aid [@RN3762]
-- Recruiting to solicit 'inquiries' and applications
+- Institutional financial aid to convert admits [@RN3762]
+- Recruiting interventions at earlier stages of enrollment funnel
   - "Student list" purchases [@RN4985]
@@
 
-### Research on links between private schools and private universities
-
+### Literature Review
+#### Linkages between private schools and private universities
+<hr>
 Studies find attending private school increases college access, selectivity
@@
 - Public school students: 5% attend "top 100" public univ; 2% attend top 100 private univ (Author calculations from HSLS 2009)
-- Private school: 11% attend top 100 public; 17% attend top 100 private
-- Nonsectarian private: 11% attend top 100 public; 40% attend top 100 private
+- Private school: 11% `@` top 100 public; 17% `@` top 100 private
+- Nonsectarian private: 11% `@` top 100 public; 40% `@` top 100 private
 
-Research from economics [@RN4935]
+@RN4935 study Ivy Plus admissions decisions
 
-- Rich students have higher non-academic ratings because they attend elite private schools (extracurricular activities, recommendations)
+- Rich students have higher non-academic ratings because they attend elite private schools (extracurriculars, recommendations)
 
-Research from sociology highlights organizational linkages [@RN4935]
+Sociology highlights school-college organizational linkages
 
-### slide title
-#### slide sub-title
+- Visits maintain relations with counselors at feeder schools [@RN3519]
+- Private school counselors lobby for marginal candidates [@RN4407]
 
+### Literature Review
+#### Synthesis
 <hr>
+These two literatures have developed in isolation
 
-Here's some text:
+- Pursuing out-of-state private school students by public research univs encroaches on historic territory of selective private univs
 
--   @RN4504 said blah...
--   Parenthetical citation [@RN4625].
--   **Bold** and *italic* text
+Analyzing network of recruiting visits to private schools gives insight about competition for affluent students
 
-More things:
+- Public and private universities may be targeting similar sets of schools
+  - Direct competition or vying to be second choice for rejected applicant
 
--   Blah
+Private school students more likely to be affluent, white than public school students [@RN4504]
+
+- Competitive recruiting of private school students has downstream effects on racial and socioeconomic composition of colleges
 
@@
 
-## Data and Sample
+### Methods
+#### Data and Sample
+
+Data collection (see @RN4758)
+
+- 2017 off-campus recruiting visits scraped from univ admissions websites
+
+Data collection sample
+
+- Public "research-extensive" universities from 2000 Carnegie (N=102)
+- Private universities in top 100 of U.S. News *National Universities* (N=57)
+- Private colleges in top 50 of *National Liberal Arts Colleges* (N=47)
+
+Analysis sample: univs that posted complete recruiting visits on website
+
+- 15 public research, 14 private universities, 12 private liberal arts (omitted)
+
+Secondary data
+
+- IPEDS; CCD; Private School Survey; Niche *Best Private High Schools*
 
@@
 
-## Constructing Social Networks
+### Methods
+#### Constructing social networks
 
-## Analyses
+text
+- Transform two-mode network to one-mode university network showing number of schools visited by both university $i$ and university $j$
+
+### Methods
+#### Analyses by research question
+
+1.  How does the scale of visits to private high schools vary for the public research universities and selective private universities?
+    - Simple descriptive statistics
+
+\medskip
+
+2.  To what extent do public research universities and selective private universities visit overlapping sets of private high schools?
+    - Graph one-mode university network; universities allocated to categories based on cluster analysis
+
+\medskip
+
+3.  What are the characteristics of private schools that receive visits from public research universities and selective private research universities?
+    - Descriptive statistics of characteristics of university order-1 "ego network" (schools the university visited):
+      - Geographic region, religion, racial composition, academic reputation
 

### 2024-02-16 r_r/submission/manuscript_rihe_r_r.Rmd
working through presentation

@@
 Although the literature on nonresident enrollment developed in isolation from the literature on private school to private university linkages, both phenomena are part of a broader story about the changing nature of school segregation and the competition for affluent, traditional college students.
-Drawing from resource dependence theory, as public research universities become more reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices.
+Drawing from resource dependence theory, as public research universities become more tuition reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices.
 Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), public research universities began substantially increasing nonresident enrollment en masse around 2005 [@RN3753].

### 2024-02-19 scripts/acs_collect_via_API_tract.py
#12 add intro map

@@ -1,0 +1,84 @@
+import requests
+import json
+import csv
+import os
+
+
+# Doc: https://www.census.gov/data/developers/data-sets/acs-5year.2017.html
+# Variables: https://api.census.gov/data/2017/acs/acs5/variables.html
+# Geography: https://api.census.gov/data/2017/acs/acs5/geography.html
+
+
+def main():
+
+    col_names = ['tract_name',
+    
+                 # Population
+                 'pop_total', 'pop_total_25plus',
+
+                 # Median household income
+                 'median_household_income', 'median_inc_2544', 'median_inc_4564',
+    
+                 # Race and ethnicity
+                 'pop_white_m_15-17', 'pop_white_m_18-19', 'pop_white_f_15-17', 'pop_white_f_18-19',
+                 'pop_black_m_15-17', 'pop_black_m_18-19', 'pop_black_f_15-17', 'pop_black_f_18-19',
+                 'pop_amerindian_m_15-17', 'pop_amerindian_m_18-19', 'pop_amerindian_f_15-17', 'pop_amerindian_f_18-19',
+                 'pop_asian_m_15-17', 'pop_asian_m_18-19', 'pop_asian_f_15-17', 'pop_asian_f_18-19',
+                 'pop_nativehawaii_m_15-17', 'pop_nativehawaii_m_18-19', 'pop_nativehawaii_f_15-17', 'pop_nativehawaii_f_18-19',
+                 'pop_otherrace_m_15-17', 'pop_otherrace_m_18-19', 'pop_otherrace_f_15-17', 'pop_otherrace_f_18-19',
+                 'pop_tworaces_m_15-17', 'pop_tworaces_m_18-19', 'pop_tworaces_f_15-17', 'pop_tworaces_f_18-19',
+                 'pop_hispanic_m_15-17', 'pop_hispanic_m_18-19', 'pop_hispanic_f_15-17', 'pop_hispanic_f_18-19',
+                 
+                 'fips_state_code', 'fips_county_code', 'tract']  # last by default
+
+    var_names = ['NAME',
+    
+                 # Population
+                 'B01003_001E', 'B15003_001E',
+
+                 # Median household income
+                 'B19013_001E', 'B19049_003E', 'B19049_004E',
+    
+                 # Race and ethnicity
+                 'B01001H_006E', 'B01001H_007E', 'B01001H_021E', 'B01001H_022E',
[…]

### 2024-02-19 scripts/create_igraph_objects.R

@@ -104,7 +104,7 @@ table(events_data$event_type, useNA = 'always')
 
 # Clean up events data (drop visits to HS not meeting criteria - 45533 to 44660 obs)
 events_df <- events_data %>% 
-  select(univ_id, univ_state, event_type, school_id, event_state, event_loc)
+  select(univ_id, univ_state, event_type, school_id, event_date, event_state, event_loc)
 
 # Override school_id with updated 2017-18 PSS ID
 get_pss_override <- function(x) {

### 2024-02-19 scripts/intro_map.R

@@ -1,0 +1,227 @@
+library(tidyverse)
+library(leaflet)
+library(tigris)
+library(formattable)
+library(htmlwidgets)
+library(htmltools)
+
+
+output_dir <- file.path('.', 'assets', 'maps')
+imgs_dir <- file.path('.', 'assets', 'images')
+data_dir <- file.path('.', 'data')
+
+# Load school data
+ipeds_1718 <- readRDS(file.path(data_dir, 'ipeds_1718.RDS'))
+ccd_1718 <- readRDS(file.path(data_dir, 'ccd_1718.RDS'))
+# pss_1718 <- readRDS(file.path(data_dir, 'pss_1718.RDS'))
+
+pubhs_universe_df <- readRDS(file.path(data_dir, 'pubhs_universe.RDS'))
+privhs_universe_df <- readRDS(file.path(data_dir, 'privhs_universe.RDS'))
+
+univ_sample <- readRDS(file.path(data_dir, 'univ_sample.RDS'))
+events_data <- readRDS(file.path(data_dir, 'events_data.RDS'))
+
+# Harpeth Hall (01296378), est. 1951
+# University School of Nashville (01296764), est. 1975
+# Christ Presbyterian Academy (A9106269), est. 1985
+intro_schools <- c('01296378', '01296764', 'A9106269')
+
+visits_data <- events_data %>% 
+  filter(event_date > '2017-08-01') %>% 
+  distinct() %>% 
+  arrange(event_date) %>% 
+  mutate(
+    visit = str_c(univ_abbrev, ' (', event_date, ')')
+  ) %>% 
+  group_by(school_id, classification) %>%
+  summarise(
+    visit = paste(visit, collapse = '<br>')
+  ) %>% 
+  ungroup() %>% 
+  pivot_wider(
+    id_cols = school_id,
+    names_from = classification,
+    values_from = visit
+  )
+
+# https://www.zillow.com/browse/homes/tn/davidson-county/
[…]

### 2024-02-19 index.qmd
#12 add intro map
#14 add horizontal line for text slides

@@
 
-### Off-campus recruiting visits to high schools in Nashville
+### Off-campus recruiting visits to high schools in Nashville {.caption}
 
-CRYSTAL: INSERT MAP HERE
+<iframe src="./assets/maps/intro_map.html" width=100% height=100% allowtransparency="true"></iframe>
 
@@
 #### Linkages between private schools and private universities
-<hr>
+
 Studies find attending private school increases college access, selectivity
@@
 #### Synthesis
-<hr>
+
 These two literatures have developed in isolation
@@
 
-### Characteristics of universities in analysis sample
+### Characteristics of universities in analysis sample {.caption}
 
@@
   collapse_rows(columns = 1, valign = 'middle') %>% 
-  column_spec(4, width_min = '1.2in') %>% 
+  column_spec(4, width_min = '1.4in') %>% 
   column_spec(6, width_min = '1in') %>% 
@@
 
-### Characteristics of universities in analysis sample compared to data collection sample
+### Characteristics of universities in analysis sample compared to data collection sample {.caption}
 
@@
 
-### Number of HS visits by public research universities
+### Number of HS visits by public research universities {.caption}
 
@@
 
-### Number of HS visits by selective private universities
+### Number of HS visits by selective private universities {.caption}
 
@@
 
-### Proportional HS visits by public research universities
+### Proportional HS visits by public research universities {.caption}
 
@@
 
-### Proportional HS visits by selective private universities
+### Proportional HS visits by selective private universities {.caption}
 
@@
 
-### One-mode percent matrix, all universities
+### One-mode percent matrix, all universities {.caption}
 
@@
 
-### One-mode network for all universities
+### One-mode network for all universities {.caption}
 
@@
 
-### Order 2 ego network of University of Notre Dame
+### Order 2 ego network of University of Notre Dame {.caption}
 
@@
 
-### Geographic region of visited private high schools
+### Geographic region of visited private high schools {.caption}
 
@@
 
-### Religious affiliation of visited private high schools
+### Religious affiliation of visited private high schools {.caption}
 
@@
 
-### Racial composition of visited HS, public universities
+### Racial composition of visited HS, public universities {.caption}
 
@@
 
-### Racial composition of visited HS, private universities
+### Racial composition of visited HS, private universities {.caption}
 
@@
 
-### High school ranking of visited private high schools
+### High school ranking of visited private high schools {.caption}
 
@@
 #### Subtitle
-
-<hr>
 
@@
 
-### All recruiting visits, public research universities
+### All recruiting visits, public research universities {.caption}
 
@@
 
-### One-mode public university percent matrix
+### One-mode public university percent matrix {.caption}
 
@@
 
-### One-mode network, public universities
+### One-mode network, public universities {.caption}
 
@@
 
-### One-mode private university percent matrix
+### One-mode private university percent matrix {.caption}
 
@@
 
-### For private universities, the percent of high schools visited by public universities
+### For private universities, the percent of high schools visited by public universities {.caption}
 
@@
 
-### For public universities, the percent of high schools visited by private universities
+### For public universities, the percent of high schools visited by private universities {.caption}
 
@@
 
-### Racial composition in the South, public universities
+### Racial composition in the South, public universities {.caption}
 
@@
 
-### Racial composition in the South, private universities
+### Racial composition in the South, private universities {.caption}
 

### 2024-02-19 assets/js/script.js

@@ -19,6 +19,9 @@ $(function() {
     $(this).closest('.slide').find('p img').removeClass('disabled');
   });
   
+  $('<hr>').insertAfter('.reveal .slide h4');
+  $('<hr>').insertAfter('.reveal .slide:not(.caption) h3:not(:has(+ h4))');
+  
   Reveal.addEventListener('slidechanged', function() {
     $('.modal').fadeOut();
     $('img').removeClass('disabled');

### 2024-02-20 index.qmd
#13 add background options

@@
     slide-level: 3
+    template-partials:
+      - ./assets/html/title-slide.html
 include-in-header: ./assets/html/header.html

### 2024-02-20 assets/js/script.js

@@ -26,4 +26,8 @@ $(function() {
     $('.modal').fadeOut();
     $('img').removeClass('disabled');
   });
+  
+  $('.bg').on('click', function(e) {
+    $('.backgrounds').attr('class', 'backgrounds ' + $(this).attr('id'))
+  })
 });

### 2024-02-20 index.qmd
revised presentation

@@
 
+Construct two-mode network
+
+- "Edge" or "network tie" = off-campus recruiting vist
+- "Vertices” = schools $i$ (mode 1) and universities $j$ (mode 2)
 text
-- Transform two-mode network to one-mode university network showing number of schools visited by both university $i$ and university $j$
+- School-by-university matrix; cell $a_{i,j}$ shows number of visits school $i$ received from univ $j$
+
+Transform two-mode network into one-mode university network
+
+- university $i$ and university $j$ share an edge if they visit at least one high school in common
+- "Weight" of the edge is number of high schools visited by both $i$ and $j$
+
+### Visualizing two-mode recruiting network {.caption}
+
+![](./assets/figures/plot_2mode_u.png)
 
@@
 
-### Slide w/ citation
+### Discussion
 
-#### Subtitle
+Key findings (for analysis sample)
 
-Here's some text:
+- **RQ1**. Disproportionate number of visits to private schools
+- **RQ2**. Substantial overlap in recruiting networks of public and private univs
+- **RQ3**. For public univs, visit schools: in the South; Catholic/Christian; enrollment mostly white
 
--   @RN4504 said blah...
--   Parenthetical citation [@RN4625].
--   **Bold** and *italic* text
+Practical implications
 
-More things:
+- Universities should conduct an internal equity audit of recruiting practices
 
--   Blah
+Implications for scholarship
+
+- Selective private, public flagship compete for same affluent households
+- @RN4935 study Ivy Plus admissions; focuses on student/household behavior
+  - Ignore organizational linkages between privileged schools and univs
+  - These orgs interact to increase flow of students between one another
 

### 2024-02-20 r_r/submission/manuscript_rihe_r_r.Rmd
revised presentation

@@
 
-A separate, multidisciplinary literature has analyzed linkages between private school and college access [@RN4935; @RN4407; @RN1565; @RN786].
+A separate, multidisciplinary literature has analyzed linkages between private school and college access [@RN4935; @RN4407; @RN1565; @RN786; @RN3519].
 This research observes strong links -- and student flows -- between private high schools and selective private universities.
-Private schools enroll many students who can afford private university tuition [@RN3519].
 To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between private schools and colleges.

### 2024-02-21 index.qmd
copy-edit slides

@@
 
-Visits from universities to schools yields a two-mode social network
+Visits from universities to schools yield a two-mode social network
 
@@
 
-- Increase nonresident enrollment in response to declines in state funding  [@RN3753]
-- Nonresident students more affluent, less likely to be Black or Latinx [@RN3685]
+- Increased nonresident enrollment in response to declines in state funding  [@RN3753]
+- Nonresident students are more affluent, less likely to be Black or Latinx [@RN3685]
 
@@
   - Off-campus recruiting visits [@RN4758; @RN4934]
-    - Out-of state visits to public high schools focus on affluent public schools, avoid non-white communities
+    - Out-of-state visits to public high schools focus on affluent public schools, avoid non-white communities
 
@@
 
-- Public school students: 5% attend "top 100" public univ; 2% attend top 100 private univ (Author calculations from HSLS 2009)
-- Private school: 11% `@` top 100 public; 17% `@` top 100 private
-- Nonsectarian private: 11% `@` top 100 public; 40% `@` top 100 private
+- **Public school students**: 5% attend "top 100" public univ; 2% attend top 100 private univ (Author calculations from HSLS 2009)
+- **Private school**: 11% `@` top 100 public; 17% `@` top 100 private
+- **Nonsectarian private**: 11% `@` top 100 public; 40% `@` top 100 private
 
@@
 - Public and private universities may be targeting similar sets of schools
-  - Direct competition or vying to be second choice for rejected applicant
+  - Direct competition or vying to be second choice for rejected applicants
 
@@
 
-- "Edge" or "network tie" = off-campus recruiting vist
+- "Edge" or "network tie" = off-campus recruiting visit
 - "Vertices” = schools $i$ (mode 1) and universities $j$ (mode 2)
-text
 - School-by-university matrix; cell $a_{i,j}$ shows number of visits school $i$ received from univ $j$
@@
 
-- university $i$ and university $j$ share an edge if they visit at least one high school in common
-- "Weight" of the edge is number of high schools visited by both $i$ and $j$
+- university $j_1$ and university $j_2$ share an edge if they visit at least one high school in common
+- "Weight" of the edge is number of high schools visited by both $j_1$ and $j_2$
 
@@
 
-### All recruiting visits, public research universities {.caption}
+### All recruiting visits, public universities {.caption}
 
@@
 
-### All recruiting visits, public research universities {.caption}
+### All recruiting visits, private universities {.caption}
 
@@
 
-### One-mode network, public universities {.caption}
+### One-mode network, private universities {.caption}
 

### 2024-02-22 scripts/intro_map.R
#12 update intro map

@@ -44,16 +44,13 @@ visits_data <- events_data %>%
     values_from = visit
   )
 
-# https://www.zillow.com/browse/homes/tn/davidson-county/
-davidson_zips <- c('37013', '37211', '37027', '37115', '37221', '37207', '37086', '37076', '37209', '37217', '37072', '37214', '37138', '37205', '37206', '37215', '37203', '37216', '37212', '37208', '37204', '37210', '37218', '37080', '37220', '37189', '37143', '37248', '37245', '37228', '37247', '37237', '37213', '37201', '37219', '37232', '37246', '37243', '37249', '37202', '37011', '37024', '37070', '37116', '37222', '37227', '37224', '37229', '37230', '37235', '37234', '37236', '37240', '37238', '37242', '37241', '37244', '37250')
-
 pubhs_data <- pubhs_universe_df %>% 
-  left_join(ccd_1718 %>% select(ncessch, sch_name, lzip, latitude, longitude), by = 'ncessch') %>% 
-  filter(lzip %in% davidson_zips, !ncessch %in% c('470453001894', '470453001946', '470369001987')) %>% 
+  left_join(ccd_1718 %>% select(ncessch, sch_name, latitude, longitude), by = 'ncessch') %>% 
+  filter(state_code == 'TN') %>% 
   left_join(visits_data, by = c('ncessch' = 'school_id'))
 
 privhs_data <- privhs_universe_df %>% 
-  filter(zip_code %in% davidson_zips | ncessch == 'A1503590', !ncessch %in% c('A1703353', '01296403', '01296811', intro_schools)) %>% 
+  filter(state_code == 'TN') %>% 
   left_join(visits_data, by = c('ncessch' = 'school_id'))
 
 intro_schools_data <- privhs_universe_df %>% 
@@ -62,20 +59,21 @@ intro_schools_data <- privhs_universe_df %>%
 
 # Create marker popups
 pubhs_data$popup <- paste0(
-  '<div style="max-height: 400px; overflow-y: scroll;"><b>', pubhs_data$sch_name, '</b><br>',
+  '<div style="max-height: 400px; overflow-y: scroll;font-size: 15px;"><b>', pubhs_data$sch_name, '</b><br>',
   '<br>Grade 12 Enrollment: ', pubhs_data$g12,
   '<br>% White: ', sprintf('%.1f', pubhs_data$pct_white),
[…]

### 2024-02-22 index.qmd
#15 update title + level-1 slides

@@
 subtitle: "Recruiting Visits to Private High Schools by Public and Private Universities"
+author: ["Ozan Jaquette (UCLA)", "Crystal Han (NASA GeneLab)", "Irma Castañeda (MEF Associates)"]
 bibliography: ./other/burd_recruiting_chapter.bib

### 2024-02-22 assets/js/script.js
#16 add link to slides

@@ -1,8 +1,10 @@
 $(function() {
 
   const modal = '<div class="modal"><span class="close">&times;</span><img /></div>';
-  
   $('.slides section').prepend(modal);
+  
+  const link = '<a class="link" href="https://cyouh95.github.io/recruiting-chapter/">cyouh95.github.io/recruiting-chapter</a>';
+  $('.slides section.level3').prepend(link);
   
   $('.slides section img').on('click', function() {
     let src = $(this).attr('src');

### 2024-02-24 index.qmd
close #17

@@
 
-### One-mode percent matrix, all universities {.caption}
+### One-mode count matrix, all universities {.caption}
 
@@
 table_1mode_u <- readRDS(file = file.path(tables_dir, 'table_1mode_u.RDS'))
-rownames(table_1mode_u$onemode_pct_df) <- colnames(table_1mode_u$onemode_pct_df)
+rownames(table_1mode_u$onemode_df) <- colnames(table_1mode_u$onemode_df)
 
-names(table_1mode_u$onemode_pct_df) <- str_replace(names(table_1mode_u$onemode_pct_df), ' \\(', '<br>(')
+names(table_1mode_u$onemode_df) <- str_replace(names(table_1mode_u$onemode_df), ' \\(', '<br>(')
 
-kable(table_1mode_u$onemode_pct_df, align = 'r', escape = F) %>%
+kable(table_1mode_u$onemode_df, align = 'r', escape = F) %>%
   column_spec(1, bold = T) %>% 

### 2024-02-25 index.qmd
added Patricia Martin cite

@@
 - Recruiting interventions at earlier stages of enrollment funnel
-  - "Student list" purchases [@RN4985]
+  - "Student list" purchases [@list_biz; @RN4985]
   - Off-campus recruiting visits [@RN4758; @RN4934]

### 2024-02-28 r_r/submission/manuscript_rihe_r_r.tex
knit pdf

@@
-%!TEX TS-program = xelatex
-
 % Options for packages loaded elsewhere
@@
 ]{article}
-\title{The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities}
-\author{}
-\date{\vspace{-2.5em}}
-
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
 \usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities},
-  colorlinks=true,
-  linkcolor={Maroon},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={blue},
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
 \usepackage[margin=1in]{geometry}
@@
 \fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same}
+\hypersetup{
+  pdftitle={The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities},
+  colorlinks=true,
+  linkcolor={Maroon},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={blue},
+  pdfcreator={LaTeX via pandoc}}
+
+\title{The Private School Network: Recruiting Visits to Private High Schools by Public and Private Universities}
+\author{}
+\date{\vspace{-2.5em}}
 
@@
 We situate this study within scholarship on nonresident enrollment at public universities.
-Author (XXXXa) analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
+Salazar, Jaquette, \& Han (2021) analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
 The authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools.
 These out-of-state visits focused on affluent, predominantly white public schools.
-Set against the scholarship about declining state appropriations and growing nonresident enrollment (Author, XXXXb, XXXXc), these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition prices.
-
-A separate, multidisciplinary literature has analyzed linkages between private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990).
+Set against the scholarship about declining state appropriations and growing nonresident enrollment (Jaquette \& Curs, 2015; Jaquette, Curs, \& Posselt, 2016), these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition prices.
+
+A separate, multidisciplinary literature has analyzed linkages between private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990; Stevens, 2007).
 This research observes strong links -- and student flows -- between private high schools and selective private universities.
-Private schools enroll many students who can afford private university tuition (Stevens, 2007).
 To date, scholarship on nonresident enrollment by public universities has progressed in isolation from scholarship on links between private schools and colleges.
@@
 
-Author (XXXXb) draw from resource dependence theory to conceptualize the relationship between state appropriations and nonresident enrollment.
+Jaquette \& Curs (2015) draw from resource dependence theory to conceptualize the relationship between state appropriations and nonresident enrollment.
 Organizations are dependent on external resources that are important for organizational survival/stability and cannot be easily replaced.
@@
 Most states cap resident tuition prices, but not nonresident tuition prices.
-Therefore, Author (XXXXb) argued that public universities have a financial incentive to grow nonresident enrollment in response to declines in state appropriations.
-Analyzing panel data from 2002-03 to 2012-13, Author (XXXXb) found that a 10\% decline in state appropriations was associated with a 2.7\% increase in nonresident enrollment at all public universities and a 5.0\% increase in nonresident enrollment at research-extensive universities.
+Therefore, Jaquette \& Curs (2015) argued that public universities have a financial incentive to grow nonresident enrollment in response to declines in state appropriations.
+Analyzing panel data from 2002-03 to 2012-13, Jaquette \& Curs (2015) found that a 10\% decline in state appropriations was associated with a 2.7\% increase in nonresident enrollment at all public universities and a 5.0\% increase in nonresident enrollment at research-extensive universities.
 
 Other studies of nonresident enrollment examine university enrollment composition.
-Using data from NPSAS 2011-12, Author (XXXXc) show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or LatinX.
+Using data from NPSAS 2011-12, Jaquette et al.
+(2016) show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or LatinX.
 Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and LatinX students.
-Author (XXXXd) examine whether growth in the number of nonresident students causes resident enrollment to decline.
+Curs \& Jaquette (2017) examine whether growth in the number of nonresident students causes resident enrollment to decline.
 They find that nonresident enrollment ``crowds out'' resident enrollment at prestigious public research universities, but not at less prestigious public research universities.
@@
 One widely utilized intervention is off-campus recruiting visits by admissions counselors to local high schools.
-Author (XXXXa) analyzed off-campus recruiting visits to public high schools by 15 public research universities.
+Salazar et al.
+(2021) analyzed off-campus recruiting visits to public high schools by 15 public research universities.
 Recruiting visits to in-state high schools tended to exhibit modest racial and socioeconomic bias.
@@
 She found that universities engage in ``recruitment redlining -- the circuitous avoidance of predominantly Black and Latinx communities along recruiting visit paths'' (p.~585).
-Although Author (XXXXa) and Salazar (2022) focused on visits to public high schools, prior research has not considered visits to private schools by public research universities.
+Although Salazar et al.
+(2021) and Salazar (2022) focused on visits to public high schools, prior research has not considered visits to private schools by public research universities.
 For example, what is the scale of these visits and what are the characteristics of visited schools?
@@
 Although the literature on nonresident enrollment developed in isolation from the literature on private school to private university linkages, both phenomena are part of a broader story about the changing nature of school segregation and the competition for affluent, traditional college students.
-Drawing from resource dependence theory, as public research universities become more reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices.
-Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), public research universities began substantially increasing nonresident enrollment en masse around 2005 (Author, XXXXb).
+Drawing from resource dependence theory, as public research universities become more tuition reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices.
+Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), public research universities began substantially increasing nonresident enrollment en masse around 2005 (Jaquette \& Curs, 2015).
 By contrast, selective private universities have long relied on enrollment from private schools (Persell \& Cookson, 1985; Stevens, 2007).
@@
 Broad patterns were similar across requested data versus scraped data, and results based on scraped data are available upon request.
-Author (XXXXa) describe data quality checks in greater detail.
+Salazar et al.
+(2021) describe data quality checks in greater detail.
 
@@
 This study engages with two, previously disconnected literatures.
-Scholarship on nonresident enrollment observes that many public research universities began growing nonresident enrollment following declines in state appropriations (Author, XXXXb).
-Given that nonresident tuition price is often two- to three-times resident price, it is unsurprising that nonresident students tend to be more affluent than resident students, are less likely to be first-generation students, and are less likely to be Black or Latinx (Author, XXXXc).
+Scholarship on nonresident enrollment observes that many public research universities began growing nonresident enrollment following declines in state appropriations (Jaquette \& Curs, 2015).
+Given that nonresident tuition price is often two- to three-times resident price, it is unsurprising that nonresident students tend to be more affluent than resident students, are less likely to be first-generation students, and are less likely to be Black or Latinx (Jaquette et al., 2016).
 Public research universities recruit nonresident students using institutional financial aid packages (Leeds \& DesJardins, 2015) and through recruiting interventions that target earlier stages in the enrollment funnel.
-Using nearly the same sample of 15 public research universities used in this study, Author (XXXXa) found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools.
+Using nearly the same sample of 15 public research universities used in this study, Salazar et al.
+(2021) found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools.
 Public research universities have a financial incentive to target private school students, who tend to come from affluent households that are able to pay nonresident tuition price without need-based aid.
@@
 Consequently, the racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university.
-Our research on visits to public high schools (Author, XXXXa) and this study on visits to private schools find that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
+Our research on visits to public high schools (Salazar et al., 2021) and this study on visits to private schools find that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
 Some universities may publicly proclaim a commitment to social mobility and privately pursue an intentional recruiting strategy that targets affluent schools and communities.
@@
 We suspect that many universities may have incomplete knowledge about which schools they recruit from and how these schools compare to those they do not recruit from.
-Our rationale for this statement is that employee turnover in the enrollment management profession is quite high (Hoover, 2023) and many universities rely on expertise from third-party enrollment management consultancies (Author, XXXXe).
-Consistent with this idea, when issued public records requests to collect data on ``student list'' purchases from about 100 public universities (Author, XXXXf), we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.
+Our rationale for this statement is that employee turnover in the enrollment management profession is quite high (Hoover, 2023) and many universities rely on expertise from third-party enrollment management consultancies (Jaquette, Salazar, \& Martin, 2022).
+Consistent with this idea, when issued public records requests to collect data on ``student list'' purchases from about 100 public universities (Salazar, Jaquette, \& Han, 2022), we found that many public universities did not know who or how they purchased student lists, typically because the person who did this had left the university and/or the job was outsourced to a consultancy.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-RN4758}{}}%
-Author. (XXXXa).
-
-\leavevmode\vadjust pre{\hypertarget{ref-list_biz}{}}%
-Author. (XXXXe).
-
-\leavevmode\vadjust pre{\hypertarget{ref-list_empirics}{}}%
-Author. (XXXXf).
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN3753}{}}%
-Author. (XXXXb).
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN3685}{}}%
-Author. (XXXXc).
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN4290}{}}%
-Author. (XXXXd).
-
 \leavevmode\vadjust pre{\hypertarget{ref-RN4953}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-RN4290}{}}%
+Curs, B.
+R., \& Jaquette, O.
+(2017).
+Crowded out?
+The effect of nonresident enrollment on resident access to public research universities.
+\emph{Educational Evaluation and Policy Analysis}, \emph{39}(4), 644--669.
+Journal Article.
+\url{https://doi.org/10.3102/0162373717704719}
+
 \leavevmode\vadjust pre{\hypertarget{ref-RN1791}{}}%
@@
 \emph{Economics of Education Review}, \emph{21}(2), 111--124.
-Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://000173740100002}
+Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000173740100002}{\textless Go to ISI\textgreater://000173740100002}
 
@@
 Journal Article.
-Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://WOS:000256634400003}
+Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://WOS:000256634400003}{\textless Go to ISI\textgreater://WOS:000256634400003}
 
@@
 Cambridge, Massachusetts: Harvard University Press,.
-Retrieved from \url{Restricted\%20to\%20UCLA.\%20Limited\%20to\%20three\%20concurrent\%20users.\%20Try\%20again\%20later\%20if\%20unavailable.\%20http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&__char_set=utf8\&isbn=9780674239647}
+Retrieved from \href{Restricted\%20to\%20UCLA.\%20Limited\%20to\%20three\%20concurrent\%20users.\%20Try\%20again\%20later\%20if\%20unavailable.\%20http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&__char_set=utf8\&isbn=9780674239647}{Restricted to UCLA.
+Limited to three concurrent users.
+Try again later if unavailable.
+http://openurl.cdlib.org?sid=UCLA:CAT\&genre=book\&\_\_char\_set=utf8\&isbn=9780674239647}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RN3753}{}}%
+Jaquette, O., \& Curs, B.
+R.
+(2015).
+Creating the out-of-state university: Do public universities increase nonresident freshman enrollment in response to declining state appropriations?
+\emph{Research in Higher Education}, \emph{56}(6), 535--565.
+\url{https://doi.org/10.1007/s11162-015-9362-2}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RN3685}{}}%
+Jaquette, O., Curs, B.
+R., \& Posselt, J.
+R.
+(2016).
+Tuition rich, mission poor: Nonresident enrollment growth and the.
+\emph{Journal of Higher Education}, \emph{87}(5), 635--673.
+\url{https://doi.org/10.1353/jhe.2016.0025}
+
+\leavevmode\vadjust pre{\hypertarget{ref-list_biz}{}}%
+Jaquette, O., Salazar, K.
+G., \& Martin, P.
+(2022).
+\emph{The student list business: Primer and market dynamics}.
+The Institute for College Access; Success.
+Retrieved from \url{https://ticas.org/wp-content/uploads/2022/09/The-Student-List-Business_-Primer-and-Market-Dynamics.pdf}
 
@@
 \emph{Review of Higher Education}, \emph{32}(4), 469--488.
-Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://WOS:000266737500002}
+Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://WOS:000266737500002}{\textless Go to ISI\textgreater://WOS:000266737500002}
 
@@
 Journal Article.
-Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://000170748100017}
+Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000170748100017}{\textless Go to ISI\textgreater://000170748100017}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-RN4758}{}}%
+Salazar, K.
+G., Jaquette, O., \& Han, C.
+(2021).
+Coming soon to a neighborhood near you?
+Off-campus recruiting by public research universities.
+\emph{American Educational Research Journal}, \emph{58}(6), 1270--1314.
+\url{https://doi.org/10.3102/00028312211001810}
+
+\leavevmode\vadjust pre{\hypertarget{ref-list_empirics}{}}%
+Salazar, K.
+G., Jaquette, O., \& Han, C.
+(2022).
+\emph{Geodemographics of student list purchases: A first look}.
+The Institute for College Access; Success.
+Retrieved from \url{https://ticas.org/wp-content/uploads/2022/09/Geodemographics-of-Student-List-Purchases_A-First-Look.pdf}
+
 \leavevmode\vadjust pre{\hypertarget{ref-RN1118}{}}%
@@
 \emph{Journal of Economic Perspectives}, \emph{13}(1), 13--36.
-Retrieved from \url{\%3CGo\%20to\%20ISI\%3E://000078904300002}
+Retrieved from \href{\%3CGo\%20to\%20ISI\%3E://000078904300002}{\textless Go to ISI\textgreater://000078904300002}
 
@@
 \url{https://doi.org/10.1353/rhe.2007.0057}
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN4758}{}}%
-Author. (XXXXa).
-
-\leavevmode\vadjust pre{\hypertarget{ref-list_biz}{}}%
-Author. (XXXXe).
-
-\leavevmode\vadjust pre{\hypertarget{ref-list_empirics}{}}%
-Author. (XXXXf).
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN3753}{}}%
-Author. (XXXXb).
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN3685}{}}%
-Author. (XXXXc).
-
-\leavevmode\vadjust pre{\hypertarget{ref-RN4290}{}}%
-Author. (XXXXd).
 
@@
 \begin{table}[!h]
-
+\centering
 \caption{\label{tab:sample-characteristics}Characteristics of universities in analysis sample}
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \fontsize{13}{15}\selectfont
@@
 \begin{table}
-
+\centering
 \caption{\label{tab:sample-population-characteristics}Characteristics of universities in analysis sample compared to data collection sample}
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \fontsize{13}{15}\selectfont
@@
 \begin{table}
-
+\centering
 \caption{\label{tab:pubu-percent-matrix}One-mode public university percent matrix}
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \fontsize{13}{15}\selectfont
@@
 \begin{table}
-
+\centering
 \caption{\label{tab:privu-percent-matrix}One-mode private university percent matrix}
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \fontsize{13}{15}\selectfont
@@
 \begin{table}
-
+\centering
 \caption{\label{tab:privu-percent-visited-by-pubu-matrix}For private universities, the percent of high schools visited by public universities}
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \fontsize{13}{15}\selectfont
@@
 \begin{table}
-
+\centering
 \caption{\label{tab:pubu-percent-visited-by-privu-matrix}For public universities, the percent of high schools visited by private universities}
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \fontsize{13}{15}\selectfont
@@
 \begin{table}
-
+\centering
 \caption{\label{tab:pubu-count-matrix}One-mode public university count matrix}
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \fontsize{13}{15}\selectfont
@@
 \begin{table}
-
+\centering
 \caption{\label{tab:privu-count-matrix}One-mode private universities count matrix}
 \centering
-\resizebox{\linewidth}{!}{
+\resizebox{\ifdim\width>\linewidth\linewidth\else\width\fi}{!}{
 \fontsize{13}{15}\selectfont

### 2024-03-05 r_r/submission/manuscript_rihe_r_r.Rmd
copy edits abstract through methods

@@
 Therefore, we utilize social network methods to examine the recruiting networks of public and private universities.
-With respect to scale (research question 1), universities in our sample made a disproportionate number of visits to private high schools.
+With respect to scale (research question (RQ) 1), universities in our sample made a disproportionate number of visits to private high schools.
 With respect to overlap (RQ2), simple network analyses and community detection methods reveal substantial overlap in the recruiting networks of public and private universities.
@@
 14].
-In Fall 2017, about 85% of Harpeth students were white and less than 5% were Black or Latinx (Author calculations).
+In Fall 2017, about 85% of Harpeth Hall students were white and less than 5% were Black or Latinx (Author calculations).
 
@@
 Previous scholarship observes strong connections between private schools and selective private universities [@RN3519; @RN4407].
-However, Harpeth also received visits from six out-of-state public research universities, the University of Cincinnati, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.
+However, Harpeth Hall also received visits from six out-of-state public research universities, the University of Cincinnati, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.
 
 The nonsectarian University School of Nashville was founded in 1975 and is located next door to Vanderbilt University.
-It is an "A+" school, ranked 127th in the nation, and is more racially diverse than Harpeth (64% white, 11.5% Black, 3.5% Latinx, 10.0% Asian).
-From August 22nd 2017 through October 18th, the University School received visits from nearly the same set of 11 private universities that visited Harpeth (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinnati, CU Boulder).
+It is an "A+" school, ranked 127th in the nation, and is more racially diverse than Harpeth Hall (64% white, 11.5% Black, 3.5% Latinx, 10.0% Asian).
+From August 22nd 2017 through October 18th, the University School of Nashville received visits from nearly the same set of 11 private universities that visited Harpeth Hall (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinnati, CU Boulder).
 
@@
 The results yield practical implications for public and private universities concerned about racial and socioeconomic diversity.
-Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors [@RN4896; @RN4895; @eab_nacac_counselor_2023].
+Following the COVID-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors [@RN4896; @RN4895; @eab_nacac_counselor_2023].
 Prior research finds that students are sensitive to recruiting interventions, including off-campus recruiting visits [@RN4324; @RN4402].
@@
 The so-called "iron triangle" of enrollment management states that universities pursue the three broad enrollment goals of access, academic profile, and revenue generation [CITE].
-"Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve tradeoffs with other goals.
-Scholarship on privatization expressed concern that the public research universities were emphasizing tuition revenue and rankings and deemphasizing access for state residents.-->
+"Because resources are scarce, the imagery of the iron triangle suggests that the pursuit of one enrollment goal may involve trade-offs with other goals.
+Scholarship on privatization expressed concern that the public research universities were emphasizing tuition revenue and rankings and de-emphasizing access for state residents.-->
 
@@
 Other studies of nonresident enrollment examine university enrollment composition.
-Using data from NPSAS 2011-12, @RN3685 show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or LatinX.
-Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and LatinX students.
+Using data from NPSAS 2011-12, @RN3685 show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or Latinx.
+Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and Latinx students.
 @RN4290 examine whether growth in the number of nonresident students causes resident enrollment to decline.
@@
 There has been a long-term increase in private school enrollment in the South, with middle-income families increasingly attending Christian schools and high-income families increasingly attending nonsectarian schools.
-With respect to race, 11% of white students attended private school in 2013, compared to 5% of Black students, and 3% of Hispanic students.
+With respect to race, 11% of white students attended private school in 2013, compared to 5% of Black students and 3% of Hispanic students.
 <!-- Private school enrollment rates are higher for families located in urban areas than those in suburban areas.
@@
 Of public high school students, 5.0% attending a public university ranked in the top 100 by U.S.
-News and World Report (USNWR) and 1.9% attended a private university ranked in the top 100.
+News and World Report and 1.9% attended a private university ranked in the top 100.
 Of private high school students, 10.9% attended a top 100 public university and 16.8% attended a top 100 private university.
@@
 
-Focusing on the institutional composition of private universities in USNWR top 100, 39.8%<!--TODO: Want to double check this and the previous sentence are both 39.8%?--> attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).
+Focusing on the institutional composition of private universities in U.S.
+News and World Report's top 100, 39.8%<!--TODO: Want to double check this and the previous sentence are both 39.8%?--> attended a private high school (compared to 7% of all high school students who attended a private high school) and 21.2% attended a nonsectarian private high school (compared to 1.6% of all high school students who attended a nonsectarian private high school).
 
@@
 The data on university characteristics come from the 2017 Integrated Postsecondary Education Data System (IPEDS) and 2020 Best Colleges ranking by U.S.
-News & World Report.
+News and World Report.
 For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.^[For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small number of schools.]
@@
 Making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities.
-The process we used to define the data collection sample yielded a sample of public research universities with lower USNWR rankings than the analysis sample of selective private universities.
+The process we used to define the data collection sample yielded a sample of public research universities with lower U.S.
+News and World Report rankings than the analysis sample of selective private universities.
 However, the columns in Table \@ref(tab:sample-characteristics) for 25th and 75th percentile SAT score of enrolled freshmen suggest that private universities ranked lower than 75 have test score ranges that are fairly similar to public research universities not ranked in the top 100.

### 2024-03-05 r_r/submission/manuscript_rihe_r_r.tex
copy edits abstract through methods

@@
 14).
-In Fall 2017, about 85\% of Harpeth students were white and less than 5\% were Black or Latinx (Author calculations).
+In Fall 2017, about 85\% of Harpeth Hall students were white and less than 5\% were Black or Latinx (Author calculations).
 
@@
 Previous scholarship observes strong connections between private schools and selective private universities (Khan, 2011; Stevens, 2007).
-However, Harpeth also received visits from six out-of-state public research universities, the University of Cincinnati, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.
+However, Harpeth Hall also received visits from six out-of-state public research universities, the University of Cincinnati, University of South Carolina, the University of Alabama, University of Arkansas, University of Georgia, and CU Boulder.
 
 The nonsectarian University School of Nashville was founded in 1975 and is located next door to Vanderbilt University.
-It is an ``A+'' school, ranked 127th in the nation, and is more racially diverse than Harpeth (64\% white, 11.5\% Black, 3.5\% Latinx, 10.0\% Asian).
-From August 22nd 2017 through October 18th, the University School received visits from nearly the same set of 11 private universities that visited Harpeth (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinnati, CU Boulder).
+It is an ``A+'' school, ranked 127th in the nation, and is more racially diverse than Harpeth Hall (64\% white, 11.5\% Black, 3.5\% Latinx, 10.0\% Asian).
+From August 22nd 2017 through October 18th, the University School of Nashville received visits from nearly the same set of 11 private universities that visited Harpeth Hall (Notre Dame visited and Baylor did not) and five liberal arts colleges (including Williams and Middlebury), but only two public research universities from our sample (University of Cincinnati, CU Boulder).
 
@@
 The results yield practical implications for public and private universities concerned about racial and socioeconomic diversity.
-Following the Covid-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors (EAB \& NACAC, 2023; Ruffalo Noel-Levitz, 2022a, 2022b).
+Following the COVID-19 Pandemic, off-campus recruiting visits have bounced back because they remain a fundamental means of maintaining relationships with high school guidance counselors (EAB \& NACAC, 2023; Ruffalo Noel-Levitz, 2022a, 2022b).
 Prior research finds that students are sensitive to recruiting interventions, including off-campus recruiting visits (Holland, 2019; Ruffalo Noel-Levitz, 2018).
@@
 Using data from NPSAS 2011-12, Jaquette et al.
-(2016) show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or LatinX.
-Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and LatinX students.
+(2016) show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or Latinx.
+Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and Latinx students.
 Curs \& Jaquette (2017) examine whether growth in the number of nonresident students causes resident enrollment to decline.
@@
 There has been a long-term increase in private school enrollment in the South, with middle-income families increasingly attending Christian schools and high-income families increasingly attending nonsectarian schools.
-With respect to race, 11\% of white students attended private school in 2013, compared to 5\% of Black students, and 3\% of Hispanic students.
+With respect to race, 11\% of white students attended private school in 2013, compared to 5\% of Black students and 3\% of Hispanic students.
 
@@
 Of public high school students, 5.0\% attending a public university ranked in the top 100 by U.S.
-News and World Report (USNWR) and 1.9\% attended a private university ranked in the top 100.
+News and World Report and 1.9\% attended a private university ranked in the top 100.
 Of private high school students, 10.9\% attended a top 100 public university and 16.8\% attended a top 100 private university.
@@
 
-Focusing on the institutional composition of private universities in USNWR top 100, 39.8\% attended a private high school (compared to 7\% of all high school students who attended a private high school) and 21.2\% attended a nonsectarian private high school (compared to 1.6\% of all high school students who attended a nonsectarian private high school).
+Focusing on the institutional composition of private universities in U.S.
+News and World Report's top 100, 39.8\% attended a private high school (compared to 7\% of all high school students who attended a private high school) and 21.2\% attended a nonsectarian private high school (compared to 1.6\% of all high school students who attended a nonsectarian private high school).
 
@@
 The data on university characteristics come from the 2017 Integrated Postsecondary Education Data System (IPEDS) and 2020 Best Colleges ranking by U.S.
-News \& World Report.
+News and World Report.
 For the high schools in our analysis, we use secondary data from the 2017-18 NCES Common Core of Data (CCD) for public high schools, and the 2017-18 NCES Private School Universe Survey (PSS) and 2020 Best Private High Schools ranking by Niche for private high schools.\footnote{For both public and private high schools, we also used NCES data from previous years when the 2017-18 data was not available for a small number of schools.}
@@
 Making comparisons between public and private universities would be more appropriate if we used the same classification method to define the data collection sample for all universities.
-The process we used to define the data collection sample yielded a sample of public research universities with lower USNWR rankings than the analysis sample of selective private universities.
+The process we used to define the data collection sample yielded a sample of public research universities with lower U.S.
+News and World Report rankings than the analysis sample of selective private universities.
 However, the columns in Table \ref{tab:sample-characteristics} for 25th and 75th percentile SAT score of enrolled freshmen suggest that private universities ranked lower than 75 have test score ranges that are fairly similar to public research universities not ranked in the top 100.

### 2024-03-05 r_r/manuscript_rihe_r_r.tex

@@
 We situate this study within scholarship on nonresident enrollment at public universities.
-Author (XXXXa) analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
+Salazar, Jaquette, \& Han (2021) analyzed recruiting visits to public high schools made by 15 public research universities in 2017.
 The authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools.
 These out-of-state visits focused on affluent, predominantly white public schools.
-Set against the scholarship about declining state appropriations and growing nonresident enrollment (Author, XXXXb, XXXXc), these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition prices.
-
-A separate, multidisciplinary literature has analyzed linkages betwen private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990).
+Set against the scholarship about declining state appropriations and growing nonresident enrollment (Jaquette \& Curs, 2015; Jaquette, Curs, \& Posselt, 2016), these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition prices.
+
+A separate, multidisciplinary literature has analyzed linkages between private school and college access (Bryk, Lee, \& Holland, 1993; Chetty, Deming, \& Friedman, 2023; Khan, 2011; Kingston \& Lewis, 1990).
 This research observes strong links -- and student flows -- between private high schools and selective private universities.
@@
 Drawing from resource dependence theory, as public research universities become more reliant, they have a financial incentive to target out-of-state private schools, which tend to enroll affluent students that can pay high tuition prices.
-Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), public research universities began substantially increasing nonresident enrollment en masse around 2005 (Author, XXXXb).
+Although a handful of public research universities have relied on nonresident enrollment for many decades (e.g., University of Michigan, University of Delaware), public research universities began substantially increasing nonresident enrollment en masse around 2005 (Jaquette \& Curs, 2015).
 By contrast, selective private universities have long relied on enrollment from private schools (Persell \& Cookson, 1985; Stevens, 2007).
@@
 \begin{CSLReferences}{1}{0}
-\bibitem[\citeproctext]{ref-RN4758}
-Author. (XXXXa).
-
-\bibitem[\citeproctext]{ref-list_biz}
-Author. (XXXXe).
-
-\bibitem[\citeproctext]{ref-list_empirics}
-Author. (XXXXf).
-
-\bibitem[\citeproctext]{ref-RN3753}
-Author. (XXXXb).
-
-\bibitem[\citeproctext]{ref-RN3685}
-Author. (XXXXc).
-
-\bibitem[\citeproctext]{ref-RN4290}
-Author. (XXXXd).
-
 \bibitem[\citeproctext]{ref-RN4953}
@@
 
+\bibitem[\citeproctext]{ref-RN4290}
+Curs, B.
+R., \& Jaquette, O.
+(2017).
+Crowded out?
+The effect of nonresident enrollment on resident access to public research universities.
+\emph{Educational Evaluation and Policy Analysis}, \emph{39}(4), 644--669.
+Journal Article.
+\url{https://doi.org/10.3102/0162373717704719}
+
 \bibitem[\citeproctext]{ref-RN1791}
@@
 
+\bibitem[\citeproctext]{ref-RN3753}
+Jaquette, O., \& Curs, B.
+R.
+(2015).
+Creating the out-of-state university: Do public universities increase nonresident freshman enrollment in response to declining state appropriations?
+\emph{Research in Higher Education}, \emph{56}(6), 535--565.
+\url{https://doi.org/10.1007/s11162-015-9362-2}
+
+\bibitem[\citeproctext]{ref-RN3685}
+Jaquette, O., Curs, B.
+R., \& Posselt, J.
+R.
+(2016).
+Tuition rich, mission poor: Nonresident enrollment growth and the.
+\emph{Journal of Higher Education}, \emph{87}(5), 635--673.
+\url{https://doi.org/10.1353/jhe.2016.0025}
+
+\bibitem[\citeproctext]{ref-list_biz}
+Jaquette, O., Salazar, K.
+G., \& Martin, P.
+(2022).
+\emph{The student list business: Primer and market dynamics}.
+The Institute for College Access; Success.
+Retrieved from \url{https://ticas.org/wp-content/uploads/2022/09/The-Student-List-Business_-Primer-and-Market-Dynamics.pdf}
+
 \bibitem[\citeproctext]{ref-RN4596}
@@
 
+\bibitem[\citeproctext]{ref-RN4758}
+Salazar, K.
+G., Jaquette, O., \& Han, C.
+(2021).
+Coming soon to a neighborhood near you?
+Off-campus recruiting by public research universities.
+\emph{American Educational Research Journal}, \emph{58}(6), 1270--1314.
+\url{https://doi.org/10.3102/00028312211001810}
+
+\bibitem[\citeproctext]{ref-list_empirics}
+Salazar, K.
+G., Jaquette, O., \& Han, C.
+(2022).
+\emph{Geodemographics of student list purchases: A first look}.
+The Institute for College Access; Success.
+Retrieved from \url{https://ticas.org/wp-content/uploads/2022/09/Geodemographics-of-Student-List-Purchases_A-First-Look.pdf}
+
 \bibitem[\citeproctext]{ref-RN1118}
@@
 \url{https://doi.org/10.1353/rhe.2007.0057}
-
-\bibitem[\citeproctext]{ref-RN4758}
-Author. (XXXXa).
-
-\bibitem[\citeproctext]{ref-list_biz}
-Author. (XXXXe).
-
-\bibitem[\citeproctext]{ref-list_empirics}
-Author. (XXXXf).
-
-\bibitem[\citeproctext]{ref-RN3753}
-Author. (XXXXb).
-
-\bibitem[\citeproctext]{ref-RN3685}
-Author. (XXXXc).
-
-\bibitem[\citeproctext]{ref-RN4290}
-Author. (XXXXd).
 
@@
 \url{https://doi.org/10.1080/00221546.2021.2004811}
+
+\bibitem[\citeproctext]{ref-RN4758}
+Salazar, K.
+G., Jaquette, O., \& Han, C.
+(2021).
+Coming soon to a neighborhood near you?
+Off-campus recruiting by public research universities.
+\emph{American Educational Research Journal}, \emph{58}(6), 1270--1314.
+\url{https://doi.org/10.3102/00028312211001810}
+
+\bibitem[\citeproctext]{ref-list_empirics}
+Salazar, K.
+G., Jaquette, O., \& Han, C.
+(2022).
+\emph{Geodemographics of student list purchases: A first look}.
+The Institute for College Access; Success.
+Retrieved from \url{https://ticas.org/wp-content/uploads/2022/09/Geodemographics-of-Student-List-Purchases_A-First-Look.pdf}
 

### 2024-03-11 r_r/submission/manuscript_rihe_r_r.Rmd
copy editing manuscript 3.10.24

@@
 Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities.
-That said, several public research universities in our sample -- University of Colorado-Boulder (`r events_df %>% filter(univ_id == '126614', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), University of South Carolina (`r events_df %>% filter(univ_id == '218663', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), and University of Alabama  (`r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
+That said, several public research universities in our sample -- CU-Boulder (`r events_df %>% filter(univ_id == '126614', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), University of South Carolina (`r events_df %>% filter(univ_id == '218663', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), and University of Alabama (`r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
 
@@
 Appendix Table \@ref(tab:privu-count-matrix) shows counts.
-The networks of private universities appear to have more overlap than the network of public research universities.
+The networks of private universities appear to have more overlap than the networks of public research universities.
 This is demonstrated tabularly by the higher percentages in Table \@ref(tab:privu-percent-matrix) compared to Table \@ref(tab:pubu-percent-matrix).

### 2024-03-11 r_r/submission/manuscript_rihe_r_r.tex
copy editing manuscript 3.10.24

@@
 Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities.
-That said, several public research universities in our sample -- University of Colorado-Boulder (402 visits), University of South Carolina (498 visits), and University of Alabama (1,039 visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
+That said, several public research universities in our sample -- CU-Boulder (402 visits), University of South Carolina (498 visits), and University of Alabama (1,039 visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
 
@@
 Appendix Table \ref{tab:privu-count-matrix} shows counts.
-The networks of private universities appear to have more overlap than the network of public research universities.
+The networks of private universities appear to have more overlap than the networks of public research universities.
 This is demonstrated tabularly by the higher percentages in Table \ref{tab:privu-percent-matrix} compared to Table \ref{tab:pubu-percent-matrix}.

### 2024-03-31 manuscript/manuscript_rihe_r_r.Rmd
#18 remove files

--- 2024-03-11 r_r/submission/manuscript_rihe_r_r.Rmd
@@
 Therefore, we utilize social network methods to examine the recruiting networks of public and private universities.
-With respect to scale (research question (RQ) 1), universities in our sample made a disproportionate number of visits to private high schools.
+With respect to scale (research question 1), universities in our sample made a disproportionate number of visits to private high schools.
 With respect to overlap (RQ2), simple network analyses and community detection methods reveal substantial overlap in the recruiting networks of public and private universities.
 RQ3 assesses the characteristics of visited schools.
-Both public and private universities tended to visit private schools in their home geographic region and also in the South, where private school enrollment growth has been strongest.
-Visited private schools enroll a much larger share of white students than visited public schools.
+Both public and private universities tended to visit private high schools in their home geographic region and also in the South, where private school enrollment growth has been strongest.
+Visited private high schools enroll a much larger share of white students than visited public high schools.
 Surprisingly, several public research universities visited sectarian private high schools at a rate similar to sectarian private universities.
@@
 
-During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.] From September 6th through October 17th, Harpeth Hall received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
+During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.^[These institutions are: Northwestern University, University of Notre Dame, Emory University, Tufts University, Boston College, Tulane University, Case Western Reserve University, Villanova University, Southern Methodist University, Baylor University, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette University, Williams College, Swarthmore College, Middlebury College, Smith College, Harvey Mudd College, Colorado College, Macalester College, Scripps College, Oberlin College, Occidental College, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers University, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.] From September 6th through October 17th, Harpeth Hall received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, TCU, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
 Previous scholarship observes strong connections between private schools and selective private universities [@RN3519; @RN4407].
@@
 private schools.
-In 2017, it received visits from six private universities in our sample (including the three Christian universities, Baylor, Texas Christian University, and Southern Methodist University).
+In 2017, it received visits from six private universities in our sample (including the three Christian universities, Baylor, TCU, and Southern Methodist University).
 It also received visits from the University of Cincinnati, the University of South Carolina, the University of Alabama, University of Arkansas, and CU Boulder.
@@
 Off-campus recruiting visits to local high schools and college fairs was the top-ranked recruiting expenditure item for both public and private universities, according to @RN4664.
-Therefore, analyses of which schools a university visits -- and which schools they ignore -- can yield insights about university enrollment goals.
+Therefore, analyses of which high schools a university visits -- and which high schools they ignore -- can yield insights about university enrollment goals.
 
@@
 The authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools.
-These out-of-state visits focused on affluent, predominantly white public schools.
+These out-of-state visits focused on affluent, predominantly white public high schools.
 Set against the scholarship about declining state appropriations and growing nonresident enrollment [@RN3753; @RN3685], these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition prices.
@@
 
-We argue that these two literatures have become connected because public research universities increasingly target out-of-state private schools, schools that have been the domain of selective private universities.
+We argue that these two literatures have become connected because public research universities increasingly target out-of-state private high schools, schools that have been the domain of selective private universities.
 Simply put, selective private universities and public research universities are increasingly competing for students from the same set of affluent households.
@@
 Both private and public universities in our sample made a disproportionate number of visits to private high schools.
-For public research universities, visited private schools were much more likely to be out-of-state than visited public schools.
+For public research universities, visited private high schools were much more likely to be out-of-state than visited public high schools.
 Network analyses revealed substantial overlap in the recruiting networks of universities in our sample.
-For several public universities (e.g., University of Alabama, University of South Carolina), their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, Texas Christian University) than they did to other public universities in our sample.
+For several public universities (e.g., University of Alabama, University of South Carolina), their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, TCU) than they did to other public universities in our sample.
 Results suggest that recruiting networks are substantially a function of geographic location.
-All universities visited a large number of private schools in their home region.
-However, most universities in our sample also visited a large number of private schools in the South, the region where private school enrollment has grown the most over the past three decades [@RN4504].
-The private schools visited by public and private universities in our sample enrolled a much higher share of white students than the public schools visited by these universities.
+All universities visited a large number of private high schools in their home region.
+However, most universities in our sample also visited a large number of private high schools in the South, the region where private school enrollment has grown the most over the past three decades [@RN4504].
+The private high schools visited by public and private universities in our sample enrolled a much higher share of white students than the public high schools visited by these universities.
 Surprisingly, several public universities visited sectarian private high schools at a rate similar to sectarian private universities.
@@
 The @RN4954[p.
-9] recommends that universities expand "outreach to high schools with substantial populations of low-income students and students of color." Most public and private universities in our sample visited a disproportionate number of private schools and these private schools tended to enroll mostly white students.
+9] recommends that universities expand "outreach to high schools with substantial populations of low-income students and students of color." Most public and private universities in our sample visited a disproportionate number of private high schools and these private schools tended to enroll mostly white students.
 We recommend that universities concerned about racial diversity should conduct an internal equity audit of their recruiting practices, for example, comparing the racial and socioeconomic characteristics of schools they visit versus schools they do not visit.
@@
 Other studies of nonresident enrollment examine university enrollment composition.
-Using data from NPSAS 2011-12, @RN3685 show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or Latinx.
-Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and Latinx students.
+Using data from NPSAS 2011-12, @RN3685 show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell Grant recipients, and are less likely to be Black or Latinx.
+Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell Grant recipients and a decline in the share of Black and Latinx students.
 @RN4290 examine whether growth in the number of nonresident students causes resident enrollment to decline.
@@
 private) and between university types.
-In order to discern the relative emphasis on private schools by each university, we also compare the number of recruiting visits to private schools to the number of visits to public schools.
+In order to discern the relative emphasis on private high schools by each university, we also compare the number of recruiting visits to private high schools to the number of visits to public high schools.
 
@@
 Because the data structure of networks is complicated, it is often illuminating to analyze "ego networks" rather than the entire social network.
-An "ego" is a single "focal" node (e.g., The University of Notre Dame).
+An "ego" is a single "focal" node (e.g., Notre Dame).
 An ego network consists "of a focal node ('ego') and the nodes to whom ego is directly connected to (these are called 'alters') plus the ties, if any, among the alters" [@RN4953].
 An ego network of order 1 consists of the alters that are directly tied to the ego.
-The order 1 ego network for the University of Notre Dame consists of all private high schools that received at least one visit from Notre Dame.
+The order 1 ego network for Notre Dame consists of all private high schools that received at least one visit from Notre Dame.
 The order 2 ego network consists of all private schools that were visited by Notre Dame and all universities that visited the private high schools visited by Notre Dame.
@@
 
-Our analyses focus on the following private school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
-Decisions about which private school characteristics to analyze were informed by logical argument and by prior research [e.g., @RN4724; @RN4504; @RN4321; @RN3519; @RN4588].
+Our analyses focus on the following private high school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
+Decisions about which private high school characteristics to analyze were informed by logical argument and by prior research [e.g., @RN4724; @RN4504; @RN4321; @RN3519; @RN4588].
 We analyze geographic region because, for most colleges and universities, enrollment demand is likely to be stronger at high schools in the same geographic region, but nationally prestigious colleges and universities may experience high demand throughout the country.
@@
 
-With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of `r events_df %>% filter(univ_id == '110671', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by UC-Riverside to a high of `r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by the University of Alabama (which accounted for `r round((events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of all visits to private schools by public research universities in our sample), with the median university, The University of Pittsburgh, making `r events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()` visits.
-Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of private high school visits were to out-of-state schools while `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of public high school visits were to out-of-state schools.
+With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of `r events_df %>% filter(univ_id == '110671', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by UC-Riverside to a high of `r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits by the University of Alabama (which accounted for `r round((events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of all visits to private high schools by public research universities in our sample), with the median university, The University of Pittsburgh, making `r events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count(univ_abbrev) %>% arrange(n) %>% summarize(median = median(n)) %>% as.numeric()` visits.
+Across all public research universities, `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of private high school visits were to out-of-state high schools while `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of public high school visits were to out-of-state high schools.
 This result is consistent with the notion that public research universities placed more value on out-of-state private high school students than in-state private high school students because out-of-state students generate substantially more tuition revenue.
@@
 Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities.
-That said, several public research universities in our sample -- CU-Boulder (`r events_df %>% filter(univ_id == '126614', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), University of South Carolina (`r events_df %>% filter(univ_id == '218663', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), and University of Alabama (`r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
+That said, several public research universities in our sample -- CU Boulder (`r events_df %>% filter(univ_id == '126614', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), University of South Carolina (`r events_df %>% filter(univ_id == '218663', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits), and University of Alabama (`r events_df %>% filter(univ_id == '100751', event_type %in% c('priv_hs')) %>% count() %>% as.numeric()` visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
 
@@
 Across all selective private universities in our sample, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% of high school visits were to private high schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs')) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs')) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
-Although, the relative emphasis on private high schools was slightly closer for out-of-state visits; across all selective private universities, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% of out-of-state high school visits were to private schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
+Although, the relative emphasis on private high schools was slightly closer for out-of-state visits; across all selective private universities, `r round((events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'private_national', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% of out-of-state high school visits were to private high schools, compared to `r round((events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs'),univ_state != event_state) %>% count() %>% as.numeric())/(events_df %>% filter(classification == 'public_research', event_type %in% c('priv_hs','pub_hs'),univ_state != event_state) %>% count() %>% as.numeric())*100, digits=1)`% for public research universities.
 
 Even though selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools.
-Figure \@ref(fig:actual-proportional-pubu) (public universities) and Figure \@ref(fig:actual-proportional-privu) (private universities) show the actual number of private school visits made compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.^[When calculating the hypothetical proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university.
-Our rationale for this decision is that it is unhelpful to include schools in states that the university ignored entirely.] Figure \@ref(fig:actual-proportional-pubu) shows that the actual number of private school visits exceeded the proportional number of private school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
-For UC-Berkeley, private school visits represented 27% of all high school visits but would have represented 19% had UC-Berkeley visited public and private schools at the same rate.
-For the University of Georgia, which represented the extreme for public universities, private school visits represented 37% of all high school visits but would have represented 19% had the university visited public and private schools at the same rate.
+Figure \@ref(fig:actual-proportional-pubu) (public universities) and Figure \@ref(fig:actual-proportional-privu) (private universities) show the actual number of private high school visits made compared to the hypothetical number of private high school visits if each public and private high school in the nation had an equal probability of receiving a visit.^[When calculating the hypothetical proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university.
+Our rationale for this decision is that it is unhelpful to include schools in states that the university ignored entirely.] Figure \@ref(fig:actual-proportional-pubu) shows that the actual number of private high school visits exceeded the proportional number of private high school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
+For UC-Berkeley, private school visits represented 27% of all high school visits but would have represented 19% had UC-Berkeley visited public and private high schools at the same rate.
+For the University of Georgia, which represented the extreme for public universities, private high school visits represented 37% of all high school visits but would have represented 19% had the university visited public and private high schools at the same rate.
 Figure \@ref(fig:actual-proportional-privu) shows that this disparity between actual versus proportional visits was much greater for private universities than public universities.
 Catholic universities made the most disproportionate number of private high school visits.
-For Notre Dame, private school visits represented 63% of actual high school visits but would have represented 18% of proportional visits.
+For Notre Dame, private high school visits represented 63% of actual high school visits but would have represented 18% of proportional visits.
 
@@
 As described in the methods section, we began by constructing a two-mode social network of visits to private high schools (mode 1) by universities (mode 2).
-Each university and each private high school is a "vertex." A visit from a university to a school is an "edge." Because large two-mode networks like our school-university network are difficult to visualize, two-mode networks are often analyzed as one-mode networks [@RN2457;@RN4663].
+Each university and each private high school is a "vertex." A visit from a university to a high school is an "edge." Because large two-mode networks like our school-university network are difficult to visualize, two-mode networks are often analyzed as one-mode networks [@RN2457;@RN4663].
 We transformed our two-mode school-university network into a one-mode university network in which each university is a vertex and two universities share an edge if both universities visited at least one high school in common.
@@
 This indicates the extent to which public universities were competing for students at the same set of private schools.
-For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7% of these high schools and CU-Boulder visited 39.1% of these high schools.
+For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7% of these high schools and CU Boulder visited 39.1% of these high schools.
 Appendix Table \@ref(tab:pubu-count-matrix) shows counts rather than percentages.
@@
 Next, we examine overlap in a network that contains the 15 public universities and the 14 private universities.
-Table \@ref(tab:privu-percent-visited-by-pubu-matrix) shows, for each private university, the percentage of schools that were also visited by each public university.
-This table shows the extent to which public universities were competing at private schools targeted by private universities.
-For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.2% of these schools.
-Similarly, CU-Boulder visited 46.4% of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
+Table \@ref(tab:privu-percent-visited-by-pubu-matrix) shows, for each private university, the percentage of high schools that were also visited by each public university.
+This table shows the extent to which public universities were competing at private high schools targeted by private universities.
+For example, of the 625 private high schools visited by Notre Dame, the University of Alabama visited 52.2% of these schools.
+Similarly, CU Boulder visited 46.4% of the 435 schools that TCU visited and 42.4% of the 377 schools that Northwestern visited.
 The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass-Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
@@
 Universities located near the center of Figure \@ref(fig:plot-1mode-u) tended to be universities with the highest degree centrality (i.e., those that visited the most schools).
-The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), University of South Carolina (396), Northwestern (377), and CU-Boulder (362).
+The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), University of South Carolina (396), Northwestern (377), and CU Boulder (362).
 Notably, while the majority of universities located near the center of Figure \@ref(fig:plot-1mode-u) are private, three are public.
@@
 Similarly, the University of South Carolina, which visited a relatively high share of Christian schools, is close to TCU and SMU.
-CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located fairly close to one another in Figure \@ref(fig:plot-1mode-u).
+CU Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located fairly close to one another in Figure \@ref(fig:plot-1mode-u).
 As discussed below, these three universities are similar to one another with respect to the geographic location (Figure \@ref(fig:region-pubu-privu)), religious affiliation (Figure \@ref(fig:religion-pubu-privu)), and academic reputation (Figure \@ref(fig:rank-pubu-privu)) of the private high schools they visit.
@@
 Starting with the most peripheral group, UC-Riverside is a group unto itself.
-UC-Riverside only visited 100 private schools and about 70 of these were located in CA.
+UC-Riverside only visited 100 private high schools and about 70 of these were located in CA.
 Another group -- Rutgers, Stevens Institute of Technology, UMass-Amherst, SUNY Stony Brook, and Pittsburgh -- largely consists of public universities with strong ties to the Northeast.
@@
 While the federal government defines Nebraska and Kansas as part of the Midwest, Figure \@ref(fig:plot-1mode-u) suggests that the visit patterns of the University of Nebraska and the University of Kansas share more in common with Southern universities than they do with other universities in our sample.
-Finally, the largest and most centrally located cluster contains 13 universities, including Notre Dame, Northwestern, Tulane, CU-Boulder, and UC-Berkeley.
+Finally, the largest and most centrally located cluster contains 13 universities, including Notre Dame, Northwestern, Tulane, CU Boulder, and UC-Berkeley.
 Compared to the overall sample, this group largely consists of highly ranked universities, universities located in the Midwest or West, and Catholic universities.
@@
 The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and characteristics of the schools they visit -- of geographic location, religious affiliation, academic reputation, and also institutional control.
-Considering the identification of clusters, centrality, and proximity of vertices, we find substantial overlap in the sets of private schools visited by public universities and private universities.
+Considering the identification of clusters, centrality, and proximity of vertices, we find substantial overlap in the sets of private high  schools visited by public universities and private universities.
 This overlap does not suggest uniformity across public and private universities.
@@
 Most public research universities in our sample visited a disproportionate number of private high schools in their home geographic region.
-UC-Berkeley and CU-Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.
+UC-Berkeley and CU Boulder -- universities with strong national brand recognition -- visited a large number of private high schools outside their home region.
 
@@
 
-In the universe of all private high schools (top row of Figure \@ref(fig:region-pubu-privu)), there are more schools located in the South than any other geographic region, consistent with the finding from @RN4504 about the long-term growth in private school enrollment in the South.
+In the universe of all private high schools (top row of Figure \@ref(fig:region-pubu-privu)), there are more schools located in the South than any other geographic region, consistent with the finding from @RN4504 about the long-term growth in private high school enrollment in the South.
 Universities not located in the South tended to visit more private high schools in the South than any other region, except their home region.
@@
 Surprisingly, Catholic schools represented at least 40% of private high school visits for `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'public') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'public_research') %>% count() %>% as.numeric()` public research universities in our sample.
-By contrast, Catholic schools represented at least 40% of visits for only `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'private') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample (the four Catholic universities and also Texas Christian University and Stevens Institute of Technology).
+By contrast, Catholic schools represented at least 40% of visits for only `r ego_df %>% mutate(catholic2= as.numeric(str_replace(catholic,'%',''))) %>% filter(type == 'univ', catholic2>=40, control == 'private') %>% count() %>% as.numeric()` of the `r univ_sample_df %>% filter(classification == 'private_national') %>% count() %>% as.numeric()` selective private universities in our sample (the four Catholic universities and also TCU and Stevens Institute of Technology).
 For public research universities, the emphasis on visiting Catholic and Christian high schools rather than nonsectarian private high schools tended to be stronger at less prestigious institutions.
@@
 Figure \@ref(fig:rank-pubu-privu) shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools.
-For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visited a higher share of private high schools rated "A" or "A- or below." Notre Dame University is a notable exception to this pattern.^[A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.]
+For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated "A+" whereas less prestigious universities visited a higher share of private high schools rated "A" or "A- or below." Notre Dame is a notable exception to this pattern.^[A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.]
 
@@
 The top row in the top panel of Figure \@ref(fig:race-pubu-privhs-pubhs) shows that the sum of Black, Latinx, and Native students comprise less than 20% of enrolled students in over 65%<!--0.6632124--> of schools in our private high school universe.
-At public high schools (bottom panel), Black/Latinx/Native students comprise less than 20% of enrolled students at around 40%<!--0.4087567--> of all public schools.
+At public high schools (bottom panel), Black/Latinx/Native students comprise less than 20% of enrolled students at around 40%<!--0.4087567--> of all public high schools.
 However, most public research universities (Figure \@ref(fig:actual-proportional-pubu)) and all selective private universities (Figure \@ref(fig:actual-proportional-privu)) visited a disproportionate number of private high schools compared to public high schools.
 Even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
-Therefore, a disproportionate emphasis on visits to public schools may shift the racial composition of public universities away from Black/Latinx/Native students.
+Therefore, a disproportionate emphasis on visits to public high schools may shift the racial composition of public universities away from Black/Latinx/Native students.
 
@@
 Figure \@ref(fig:race-pubu-privhs-pubhs) focuses on public universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel).
-For all public universities, the racial composition of visited public schools contains a much higher share of Black/Latinx/Native students than the racial composition of visited private schools.
+For all public universities, the racial composition of visited public schools contains a much higher share of Black/Latinx/Native students than the racial composition of visited private high schools.
 Figure \@ref(fig:race-pubu-privhs-pubhs) shows that for most universities in our sample, the set of visited private high schools enrolled *fewer* Black/Latinx/Native students than the universe of private high schools.
@@
 Results are very similar to those of public universities.
-Visited private schools enrolled a much lower share of Black/Latinx/Native students than visited public schools.
-For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75% of visited private schools enrolled less than 20% Black/Latinx/Native students.
-
-Finally, Figure \@ref(fig:south-race-pubu-privhs-pubhs) examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample.
+Visited private high schools enrolled a much lower share of Black/Latinx/Native students than visited public high schools.
+For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75% of visited private high schools enrolled less than 20% Black/Latinx/Native students.
+
+Finally, Figure \@ref(fig:south-race-pubu-privhs-pubhs) examines the racial composition of private high schools visited in the South (upper panel) and the racial composition of public high schools visited in the South (lower panel) by public research universities in our sample.
 Figure \@ref(fig:south-race-privu-privhs-pubhs) does the same for selective private universities.
-These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest [@RN4504].
-For public research universities, Figure \@ref(fig:south-race-pubu-privhs-pubhs) shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools.
+These figures are motivated by the finding that many universities in our sample visited a large number of private high schools in the South, where private high school enrollment growth has been the strongest [@RN4504].
+For public research universities, Figure \@ref(fig:south-race-pubu-privhs-pubhs) shows that visited Southern private high schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public high schools.
 This was true for all universities in our sample that visited a substantial number of schools in the South, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati.
-Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits.
+Quite simply, the racial composition of Southern private high schools is dramatically different than the racial composition of Southern public high schools and these differences are also reflected in schools that received visits.
 Results for private universities in Figure \@ref(fig:south-race-privu-privhs-pubhs) are very similar, with Emory, Northwestern, and Case Western visiting private schools with a low share of Black/Latinx/Native students.
-Appendix Figures \@ref(fig:south-race-comp-pubu-privhs-pubhs) and \@ref(fig:south-race-comp-privu-privhs-pubhs) show the full racial composition of visited public and private schools in the South.
-For most universities that made a substantial number of visits in the South, white students comprised around 70% of total enrollment at visited private schools compared to around 40% at visited public schools.
+Appendix Figures \@ref(fig:south-race-comp-pubu-privhs-pubhs) and \@ref(fig:south-race-comp-privu-privhs-pubhs) show the full racial composition of visited public and private high schools in the South.
+For most universities that made a substantial number of visits in the South, white students comprised around 70% of total enrollment at visited private high schools compared to around 40% at visited public high schools.
 
@@
 For most public research universities in our sample, the scale and relative scale -- as a percentage of all HS visits -- of visits to private high schools were smaller than that of most selective private universities.
-However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \@ref(fig:actual-proportional-pubu)) and the vast majority of these private school visits were to out-of-state private schools.
-Additionally, several public research universities -- University of Alabama, CU-Boulder, University of South Carolina -- visited private high schools at a scale that exceeded most private universities.
-
-Research question 2 asks about overlap in the private school recruiting networks of public and private universities.
+However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \@ref(fig:actual-proportional-pubu)) and the vast majority of these private high school visits were to out-of-state private high schools.
+Additionally, several public research universities -- University of Alabama, CU Boulder, University of South Carolina -- visited private high schools at a scale that exceeded most private universities.
+
+Research question 2 asks about overlap in the private high school recruiting networks of public and private universities.
 We observed substantial overlap and variation in the recruiting networks of public universities.
@@
 Whether we are categorizing universities by cluster analysis or by proximity on the network graph, we observe several different subsets of universities.
-Each of these subsets is associated with a different approach to private school visits and -- with the exception of a few universities like UC-Riverside and SUNY Stony Brook that don't play the private school game -- each of these subsets contained both public and private universities.
+Each of these subsets is associated with a different approach to private high school visits and -- with the exception of a few universities like UC-Riverside and SUNY Stony Brook that don't play the private high school game -- each of these subsets contained both public and private universities.
 
@@
 Both public and private universities in our sample tended to make a disproportionate number of visits in their home geographic region, with highly ranked universities making more visits to schools in other regions.
-The majority of universities -- even those located outside the South --  visited a large number of private schools located in the South.
+The majority of universities -- even those located outside the South --  visited a large number of private high schools located in the South.
 Unsurprisingly, sectarian private universities made a large share of visits to private high schools of a similar religious affiliation.
-Given that public universities are nonsectarian organizations, a surprising finding is that the majority of public universities in our sample made a large share of visits to Catholic or Christian private schools.
-
-With the exception of UC-Berkeley and UC-San Diego, the average academic rating of private schools visited by public universities was lower than the rating of those visited by most private universities.
+Given that public universities are nonsectarian organizations, a surprising finding is that the majority of public universities in our sample made a large share of visits to Catholic or Christian private high schools.
+
+With the exception of UC-Berkeley and UC-San Diego, the average academic rating of private high schools visited by public universities was lower than the rating of those visited by most private universities.
 This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked in the top 100 National University by U.S.
-News.
-Nevertheless, the large number of visits to low-rated private schools by public universities, combined with the fact that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private schools primarily in search of full-pay students rather than academic superstars.
+News and World Report.
+Nevertheless, the large number of visits to low-rated private high schools by public universities, combined with the fact that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private high schools primarily in search of full-pay students rather than academic superstars.
 
 Across the universe of private high schools, most schools enroll relatively few students who identify as Black, Latinx, or Native.
-For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools.
+For the public and private universities in our sample, the set of visited private high schools enrolled fewer Black, Latinx, and Native students than the national universe of private high schools.
 By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.
@@
 Using nearly the same sample of 15 public research universities used in this study, @RN4758 found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools.
-Public research universities have a financial incentive to target private school students, who tend to come from affluent households that are able to pay nonresident tuition price without need-based aid.
-This study extends the literature on nonresident students by analyzing the scale of visits to private schools, the overlap and divergence in recruiting networks between public and private universities, and the characteristics of visited private schools.
-
-We also engage with scholarship on linkages between private schools and private universities, a linkage that sociologists have observed for many decades.
-Private school students comprise a disproportionate share of enrollment at selective private universities (Author calculations based on HSLS:2009).
-Practically, these linkages exist because private schools want to send their students to "good" universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profiles and/or extracurricular activities [@RN3519].
+Public research universities have a financial incentive to target private high school students, who tend to come from affluent households that are able to pay nonresident tuition price without need-based aid.
+This study extends the literature on nonresident students by analyzing the scale of visits to private high schools, the overlap and divergence in recruiting networks between public and private universities, and the characteristics of visited private high schools.
+
+We also engage with scholarship on linkages between private high schools and private universities, a linkage that sociologists have observed for many decades.
+Private high school students comprise a disproportionate share of enrollment at selective private universities (Author calculations based on HSLS:2009).
+Practically, these linkages exist because private high schools want to send their students to "good" universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profiles and/or extracurricular activities [@RN3519].
 Prior research has often focused on linkages between elite private schools and elite universities [@RN4407; @RN4935; @RN4640].
 Whereas elite universities (e.g., Princeton, Stanford) experience strong student demand based on reputation, merely selective private universities must incite demand by expending resources on recruiting.
-Prior research has not systematically analyzed connections between private schools and private universities that are selective, but not elite.
-Therefore, this study extends the literature by investigating private school visits for a sample of 14 selective private universities that exhibit variation in geographic location, religious affiliation, and ranking.
+Prior research has not systematically analyzed connections between private high schools and private universities that are selective, but not elite.
+Therefore, this study extends the literature by investigating private high school visits for a sample of 14 selective private universities that exhibit variation in geographic location, religious affiliation, and ranking.
 
@@
 Selective private universities have been recruiting heavily from private schools for a long time [@RN4642; @RN3519; @RN4640].
-By contrast, the pursuit of out-of-state private school students by public research universities is a relatively new phenomenon and represents competition in the traditional hunting grounds of selective private universities.
+By contrast, the pursuit of out-of-state private high school students by public research universities is a relatively new phenomenon and represents competition in the traditional hunting grounds of selective private universities.
 
 Our analyses shed light on the nature of this competition.
-When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
+When making decisions about which private high schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
 Several public universities seem to be competing directly for students targeted by a particular private university.
@@
 
-However, public universities that made the greatest number of private school visits seemed to be targeting the lower-achieving students at private schools targeted by particular private universities.
-For example, the University of Alabama visited 52.2% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools.
+However, public universities that made the greatest number of private high school visits seemed to be targeting the lower-achieving students at private high schools targeted by particular private universities.
+For example, the University of Alabama visited 52.2% of the 625 private high schools that Notre Dame visited, with most of the overlap at Catholic schools.
 Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame.
 Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievements, and want to attend a football powerhouse.
-Additionally, CU-Boulder visited 42.4% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
+Additionally, CU Boulder visited 42.4% of schools visited by Northwestern, which could be interpreted as CU Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
 Similarly, the University of South Carolina competes heavily at schools targeted by Emory, SMU, TCU, and Tulane.
@@
 
-Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the Covid pandemic.
+Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the COVID-19 pandemic.
 @RN4664 found that "travel" was the top-ranked marketing/recruiting expenditure item for both public universities and private universities.
-During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events [@parents_covid_rnl].
+During the height of COVID-19, off-campus recruiting visits ceased and were partially replaced by virtual counselor events [@parents_covid_rnl].
 Admissions counselors are now traveling again.
@@
 Consequently, the racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university.
-Our research on visits to public high schools [@RN4758] and this study on visits to private schools find that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
+Our research on visits to public high schools [@RN4758] and this study on visits to private high schools find that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
 Some universities may publicly proclaim a commitment to social mobility and privately pursue an intentional recruiting strategy that targets affluent schools and communities.

### 2024-03-31 manuscript/manuscript_rihe_r_r.tex
#18 remove files

--- 2024-03-11 r_r/submission/manuscript_rihe_r_r.tex
@@
 
-During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.\footnote{These institutions are: Northwestern, Notre Dame, Emory, Tufts, Boston College, Tulane, Case Western Reserve, Villanova, Southern Methodist University, Baylor, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette, Williams, Swarthmore, Middlebury, Smith, Harvey Mudd, Colorado College, Macalester, Scripps, Oberlin, Occidental, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.} From September 6th through October 17th, Harpeth Hall received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, Texas Christian University, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
+During the 2017 calendar year, we tracked off-campus recruiting visits made by 14 selective private universities, 12 selective private liberal arts colleges, and 15 public research universities.\footnote{These institutions are: Northwestern University, University of Notre Dame, Emory University, Tufts University, Boston College, Tulane University, Case Western Reserve University, Villanova University, Southern Methodist University, Baylor University, University of Denver, Texas Christian University, Stevens Institute of Technology, Marquette University, Williams College, Swarthmore College, Middlebury College, Smith College, Harvey Mudd College, Colorado College, Macalester College, Scripps College, Oberlin College, Occidental College, Sewanee, Connecticut College, UC-Berkeley, UC-San Diego, University of Georgia, University of Pittsburgh, Rutgers University, University of Massachusetts-Amherst, UC-Riverside, SUNY Stony Brook, University of Colorado-Boulder, University of South Carolina, University of Kansas, University of Nebraska-Lincoln, University of Alabama, University of Cincinnati, and University of Arkansas.} From September 6th through October 17th, Harpeth Hall received recruiting visits from 11 private universities in our sample (Northwestern, Boston College, Tufts, Villanova, Case Western Reserve, University of Denver, Emory, Tulane, Baylor, TCU, Southern Methodist University), and three private liberal arts colleges (Harvey Mudd, Scripps, and Sewanee).
 Previous scholarship observes strong connections between private schools and selective private universities (Khan, 2011; Stevens, 2007).
@@
 Off-campus recruiting visits to local high schools and college fairs was the top-ranked recruiting expenditure item for both public and private universities, according to Ruffalo Noel-Levitz (2020a).
-Therefore, analyses of which schools a university visits -- and which schools they ignore -- can yield insights about university enrollment goals.
+Therefore, analyses of which high schools a university visits -- and which high schools they ignore -- can yield insights about university enrollment goals.
 
@@
 The authors found that 12 of the 15 universities made more visits to out-of-state schools than in-state schools.
-These out-of-state visits focused on affluent, predominantly white public schools.
+These out-of-state visits focused on affluent, predominantly white public high schools.
 Set against the scholarship about declining state appropriations and growing nonresident enrollment (Jaquette \& Curs, 2015; Jaquette, Curs, \& Posselt, 2016), these results suggest that many public research universities prioritize enrollment from wealthy out-of-state students who can afford to pay nonresident tuition prices.
@@
 Both private and public universities in our sample made a disproportionate number of visits to private high schools.
-For public research universities, visited private schools were much more likely to be out-of-state than visited public schools.
+For public research universities, visited private high schools were much more likely to be out-of-state than visited public high schools.
 Network analyses revealed substantial overlap in the recruiting networks of universities in our sample.
-For several public universities (e.g., University of Alabama, University of South Carolina), their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, Texas Christian University) than they did to other public universities in our sample.
+For several public universities (e.g., University of Alabama, University of South Carolina), their recruiting networks had more similarity to private universities (e.g., Southern Methodist University, TCU) than they did to other public universities in our sample.
 Results suggest that recruiting networks are substantially a function of geographic location.
-All universities visited a large number of private schools in their home region.
-However, most universities in our sample also visited a large number of private schools in the South, the region where private school enrollment has grown the most over the past three decades (Murnane \& Reardon, 2018).
-The private schools visited by public and private universities in our sample enrolled a much higher share of white students than the public schools visited by these universities.
+All universities visited a large number of private high schools in their home region.
+However, most universities in our sample also visited a large number of private high schools in the South, the region where private school enrollment has grown the most over the past three decades (Murnane \& Reardon, 2018).
+The private high schools visited by public and private universities in our sample enrolled a much higher share of white students than the public high schools visited by these universities.
 Surprisingly, several public universities visited sectarian private high schools at a rate similar to sectarian private universities.
@@
 Department of Education (2023, p.
-9) recommends that universities expand ``outreach to high schools with substantial populations of low-income students and students of color.'' Most public and private universities in our sample visited a disproportionate number of private schools and these private schools tended to enroll mostly white students.
+9) recommends that universities expand ``outreach to high schools with substantial populations of low-income students and students of color.'' Most public and private universities in our sample visited a disproportionate number of private high schools and these private schools tended to enroll mostly white students.
 We recommend that universities concerned about racial diversity should conduct an internal equity audit of their recruiting practices, for example, comparing the racial and socioeconomic characteristics of schools they visit versus schools they do not visit.
@@
 Using data from NPSAS 2011-12, Jaquette et al.
-(2016) show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell recipients, and are less likely to be Black or Latinx.
-Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell recipients and a decline in the share of Black and Latinx students.
+(2016) show that compared to resident students at public research universities, nonresident students generate higher net tuition revenue, are more affluent, are less likely to be Pell Grant recipients, and are less likely to be Black or Latinx.
+Institution-level panel models reveal that growth in the share of nonresident students was associated with a decline in the share of Pell Grant recipients and a decline in the share of Black and Latinx students.
 Curs \& Jaquette (2017) examine whether growth in the number of nonresident students causes resident enrollment to decline.
@@
 Research question 1 states, ``How does the scale of visits to private high schools vary for the public research universities and selective private universities in our sample?'' We answer this research question by comparing degree centrality across universities, both within university type (public vs.~private) and between university types.
-In order to discern the relative emphasis on private schools by each university, we also compare the number of recruiting visits to private schools to the number of visits to public schools.
+In order to discern the relative emphasis on private high schools by each university, we also compare the number of recruiting visits to private high schools to the number of visits to public high schools.
 
@@
 Because the data structure of networks is complicated, it is often illuminating to analyze ``ego networks'' rather than the entire social network.
-An ``ego'' is a single ``focal'' node (e.g., The University of Notre Dame).
+An ``ego'' is a single ``focal'' node (e.g., Notre Dame).
 An ego network consists ``of a focal node (`ego') and the nodes to whom ego is directly connected to (these are called `alters') plus the ties, if any, among the alters'' (Borgatti, 1998).
 An ego network of order 1 consists of the alters that are directly tied to the ego.
-The order 1 ego network for the University of Notre Dame consists of all private high schools that received at least one visit from Notre Dame.
+The order 1 ego network for Notre Dame consists of all private high schools that received at least one visit from Notre Dame.
 The order 2 ego network consists of all private schools that were visited by Notre Dame and all universities that visited the private high schools visited by Notre Dame.
@@
 
-Our analyses focus on the following private school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
-Decisions about which private school characteristics to analyze were informed by logical argument and by prior research (e.g., Graham, 1999; Khan, 2010; Murnane \& Reardon, 2018; Purdy, 2018; Stevens, 2007).
+Our analyses focus on the following private high school characteristics: geographic region, religious affiliation, academic reputation, racial composition, and enrollment size.
+Decisions about which private high school characteristics to analyze were informed by logical argument and by prior research (e.g., Graham, 1999; Khan, 2010; Murnane \& Reardon, 2018; Purdy, 2018; Stevens, 2007).
 We analyze geographic region because, for most colleges and universities, enrollment demand is likely to be stronger at high schools in the same geographic region, but nationally prestigious colleges and universities may experience high demand throughout the country.
@@
 
-With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of 100 visits by UC-Riverside to a high of 1,039 visits by the University of Alabama (which accounted for 21.9\% of all visits to private schools by public research universities in our sample), with the median university, The University of Pittsburgh, making 267 visits.
-Across all public research universities, 83.2\% of private high school visits were to out-of-state schools while 64.4\% of public high school visits were to out-of-state schools.
+With respect to research question 1, the scale of visits to private high schools by public research universities ranged from a low of 100 visits by UC-Riverside to a high of 1,039 visits by the University of Alabama (which accounted for 21.9\% of all visits to private high schools by public research universities in our sample), with the median university, The University of Pittsburgh, making 267 visits.
+Across all public research universities, 83.2\% of private high school visits were to out-of-state high schools while 64.4\% of public high school visits were to out-of-state high schools.
 This result is consistent with the notion that public research universities placed more value on out-of-state private high school students than in-state private high school students because out-of-state students generate substantially more tuition revenue.
@@
 Thus, for the universities in our sample, the scale of visits to private high schools tended to be higher for selective private universities than public research universities.
-That said, several public research universities in our sample -- CU-Boulder (402 visits), University of South Carolina (498 visits), and University of Alabama (1,039 visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
+That said, several public research universities in our sample -- CU Boulder (402 visits), University of South Carolina (498 visits), and University of Alabama (1,039 visits) -- made a relatively high number of private high school visits even when compared to the selective private universities in our sample.
 
@@
 Across all selective private universities in our sample, 48.8\% of high school visits were to private high schools, compared to 24.8\% for public research universities.
-Although, the relative emphasis on private high schools was slightly closer for out-of-state visits; across all selective private universities, 52.9\% of out-of-state high school visits were to private schools, compared to 29.9\% for public research universities.
+Although, the relative emphasis on private high schools was slightly closer for out-of-state visits; across all selective private universities, 52.9\% of out-of-state high school visits were to private high schools, compared to 29.9\% for public research universities.
 
 Even though selective private universities tend to emphasize visits to private high schools more than public research universities, both groups visited private high schools at a much higher rate than public high schools.
-Figure \ref{fig:actual-proportional-pubu} (public universities) and Figure \ref{fig:actual-proportional-privu} (private universities) show the actual number of private school visits made compared to the hypothetical number of private school visits if each public and private high school in the nation had an equal probability of receiving a visit.\footnote{When calculating the hypothetical proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university.
-Our rationale for this decision is that it is unhelpful to include schools in states that the university ignored entirely.} Figure \ref{fig:actual-proportional-pubu} shows that the actual number of private school visits exceeded the proportional number of private school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
-For UC-Berkeley, private school visits represented 27\% of all high school visits but would have represented 19\% had UC-Berkeley visited public and private schools at the same rate.
-For the University of Georgia, which represented the extreme for public universities, private school visits represented 37\% of all high school visits but would have represented 19\% had the university visited public and private schools at the same rate.
+Figure \ref{fig:actual-proportional-pubu} (public universities) and Figure \ref{fig:actual-proportional-privu} (private universities) show the actual number of private high school visits made compared to the hypothetical number of private high school visits if each public and private high school in the nation had an equal probability of receiving a visit.\footnote{When calculating the hypothetical proportional number of visits for each university, we only consider high schools in states that received at least one visit to a public or private high school from that university.
+Our rationale for this decision is that it is unhelpful to include schools in states that the university ignored entirely.} Figure \ref{fig:actual-proportional-pubu} shows that the actual number of private high school visits exceeded the proportional number of private high school visits for 13 of the 15 public research universities in our sample, the exceptions being UC-Riverside and SUNY Stony Brook.
+For UC-Berkeley, private school visits represented 27\% of all high school visits but would have represented 19\% had UC-Berkeley visited public and private high schools at the same rate.
+For the University of Georgia, which represented the extreme for public universities, private high school visits represented 37\% of all high school visits but would have represented 19\% had the university visited public and private high schools at the same rate.
 Figure \ref{fig:actual-proportional-privu} shows that this disparity between actual versus proportional visits was much greater for private universities than public universities.
 Catholic universities made the most disproportionate number of private high school visits.
-For Notre Dame, private school visits represented 63\% of actual high school visits but would have represented 18\% of proportional visits.
+For Notre Dame, private high school visits represented 63\% of actual high school visits but would have represented 18\% of proportional visits.
 
@@
 As described in the methods section, we began by constructing a two-mode social network of visits to private high schools (mode 1) by universities (mode 2).
-Each university and each private high school is a ``vertex.'' A visit from a university to a school is an ``edge.'' Because large two-mode networks like our school-university network are difficult to visualize, two-mode networks are often analyzed as one-mode networks (Borgatti, 2008; Davis et al., 2003).
+Each university and each private high school is a ``vertex.'' A visit from a university to a high school is an ``edge.'' Because large two-mode networks like our school-university network are difficult to visualize, two-mode networks are often analyzed as one-mode networks (Borgatti, 2008; Davis et al., 2003).
 We transformed our two-mode school-university network into a one-mode university network in which each university is a vertex and two universities share an edge if both universities visited at least one high school in common.
@@
 This indicates the extent to which public universities were competing for students at the same set of private schools.
-For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7\% of these high schools and CU-Boulder visited 39.1\% of these high schools.
+For example, column 2 shows that of the 396 different private high schools visited by the University of South Carolina, the University of Alabama visited 71.7\% of these high schools and CU Boulder visited 39.1\% of these high schools.
 Appendix Table \ref{tab:pubu-count-matrix} shows counts rather than percentages.
@@
 Next, we examine overlap in a network that contains the 15 public universities and the 14 private universities.
-Table \ref{tab:privu-percent-visited-by-pubu-matrix} shows, for each private university, the percentage of schools that were also visited by each public university.
-This table shows the extent to which public universities were competing at private schools targeted by private universities.
-For example, of the 625 private schools visited by Notre Dame, the University of Alabama visited 52.2\% of these schools.
-Similarly, CU-Boulder visited 46.4\% of the 435 schools that TCU visited and 42.4\% of the 377 schools that Northwestern visited.
+Table \ref{tab:privu-percent-visited-by-pubu-matrix} shows, for each private university, the percentage of high schools that were also visited by each public university.
+This table shows the extent to which public universities were competing at private high schools targeted by private universities.
+For example, of the 625 private high schools visited by Notre Dame, the University of Alabama visited 52.2\% of these schools.
+Similarly, CU Boulder visited 46.4\% of the 435 schools that TCU visited and 42.4\% of the 377 schools that Northwestern visited.
 The University of Arkansas competed heavily at schools visited by Baylor; Rutgers and UMass-Amherst competed heavily at schools visited by Stevens Institute of Technology; and UC-Berkeley competed at schools visited by Northwestern, Tufts, and Emory.
@@
 Universities located near the center of Figure \ref{fig:plot-1mode-u} tended to be universities with the highest degree centrality (i.e., those that visited the most schools).
-The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), University of South Carolina (396), Northwestern (377), and CU-Boulder (362).
+The top nine universities in terms of degree centrality are (number of unique private high schools visited in parentheses): University of Alabama (759), Notre Dame (625), Villanova (563), SMU (550), TCU (435), Tulane (430), University of South Carolina (396), Northwestern (377), and CU Boulder (362).
 Notably, while the majority of universities located near the center of Figure \ref{fig:plot-1mode-u} are private, three are public.
@@
 Similarly, the University of South Carolina, which visited a relatively high share of Christian schools, is close to TCU and SMU.
-CU-Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located fairly close to one another in Figure \ref{fig:plot-1mode-u}.
+CU Boulder, Emory, and Northwestern -- three universities that differ from one another with respect to geographic location, religious affiliation, and institutional control -- are located fairly close to one another in Figure \ref{fig:plot-1mode-u}.
 As discussed below, these three universities are similar to one another with respect to the geographic location (Figure \ref{fig:region-pubu-privu}), religious affiliation (Figure \ref{fig:religion-pubu-privu}), and academic reputation (Figure \ref{fig:rank-pubu-privu}) of the private high schools they visit.
@@
 While the federal government defines Nebraska and Kansas as part of the Midwest, Figure \ref{fig:plot-1mode-u} suggests that the visit patterns of the University of Nebraska and the University of Kansas share more in common with Southern universities than they do with other universities in our sample.
-Finally, the largest and most centrally located cluster contains 13 universities, including Notre Dame, Northwestern, Tulane, CU-Boulder, and UC-Berkeley.
+Finally, the largest and most centrally located cluster contains 13 universities, including Notre Dame, Northwestern, Tulane, CU Boulder, and UC-Berkeley.
 Compared to the overall sample, this group largely consists of highly ranked universities, universities located in the Midwest or West, and Catholic universities.
@@
 The allocation of universities to clusters appears to be correlated with the characteristics -- university characteristics and characteristics of the schools they visit -- of geographic location, religious affiliation, academic reputation, and also institutional control.
-Considering the identification of clusters, centrality, and proximity of vertices, we find substantial overlap in the sets of private schools visited by public universities and private universities.
+Considering the identification of clusters, centrality, and proximity of vertices, we find substantial overlap in the sets of private high schools visited by public universities and private universities.
 This overlap does not suggest uniformity across public and private universities.
@@
 
-In the universe of all private high schools (top row of Figure \ref{fig:region-pubu-privu}), there are more schools located in the South than any other geographic region, consistent with the finding from Murnane \& Reardon (2018) about the long-term growth in private school enrollment in the South.
+In the universe of all private high schools (top row of Figure \ref{fig:region-pubu-privu}), there are more schools located in the South than any other geographic region, consistent with the finding from Murnane \& Reardon (2018) about the long-term growth in private high school enrollment in the South.
 Universities not located in the South tended to visit more private high schools in the South than any other region, except their home region.
@@
 Surprisingly, Catholic schools represented at least 40\% of private high school visits for 10 of the 15 public research universities in our sample.
-By contrast, Catholic schools represented at least 40\% of visits for only 6 of the 14 selective private universities in our sample (the four Catholic universities and also Texas Christian University and Stevens Institute of Technology).
+By contrast, Catholic schools represented at least 40\% of visits for only 6 of the 14 selective private universities in our sample (the four Catholic universities and also TCU and Stevens Institute of Technology).
 For public research universities, the emphasis on visiting Catholic and Christian high schools rather than nonsectarian private high schools tended to be stronger at less prestigious institutions.
@@
 Figure \ref{fig:rank-pubu-privu} shows the academic reputation -- defined by the Niche private high school ranking -- of visited private high schools.
-For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated ``A+'' whereas less prestigious universities visited a higher share of private high schools rated ``A'' or ``A- or below.'' Notre Dame University is a notable exception to this pattern.\footnote{A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.}
+For the private universities in our sample, we see the predictable pattern that more highly ranked universities tend to visit a higher share of private high schools that are ranked in the top 200 nationally or are rated ``A+'' whereas less prestigious universities visited a higher share of private high schools rated ``A'' or ``A- or below.'' Notre Dame is a notable exception to this pattern.\footnote{A potential explanation is that Notre Dame has developed a strategy of targeting the very top students at relatively less-prestigious Catholic high schools, believing that these students will choose Notre Dame because of its status as the preeminent Catholic University.}
 
@@
 The top row in the top panel of Figure \ref{fig:race-pubu-privhs-pubhs} shows that the sum of Black, Latinx, and Native students comprise less than 20\% of enrolled students in over 65\% of schools in our private high school universe.
-At public high schools (bottom panel), Black/Latinx/Native students comprise less than 20\% of enrolled students at around 40\% of all public schools.
+At public high schools (bottom panel), Black/Latinx/Native students comprise less than 20\% of enrolled students at around 40\% of all public high schools.
 However, most public research universities (Figure \ref{fig:actual-proportional-pubu}) and all selective private universities (Figure \ref{fig:actual-proportional-privu}) visited a disproportionate number of private high schools compared to public high schools.
 Even if universities visited schools with racial composition on par with the universe of private high schools, most visited schools would have relatively few Black/Latinx/Native students enrolled.
-Therefore, a disproportionate emphasis on visits to public schools may shift the racial composition of public universities away from Black/Latinx/Native students.
+Therefore, a disproportionate emphasis on visits to public high schools may shift the racial composition of public universities away from Black/Latinx/Native students.
 
@@
 Figure \ref{fig:race-pubu-privhs-pubhs} focuses on public universities, showing the racial composition of visited private high schools (top panel) to the racial composition of visited public high schools (bottom panel).
-For all public universities, the racial composition of visited public schools contains a much higher share of Black/Latinx/Native students than the racial composition of visited private schools.
+For all public universities, the racial composition of visited public schools contains a much higher share of Black/Latinx/Native students than the racial composition of visited private high schools.
 Figure \ref{fig:race-pubu-privhs-pubhs} shows that for most universities in our sample, the set of visited private high schools enrolled \emph{fewer} Black/Latinx/Native students than the universe of private high schools.
@@
 Results are very similar to those of public universities.
-Visited private schools enrolled a much lower share of Black/Latinx/Native students than visited public schools.
-For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75\% of visited private schools enrolled less than 20\% Black/Latinx/Native students.
-
-Finally, Figure \ref{fig:south-race-pubu-privhs-pubhs} examines the racial composition of private schools visited in the South (upper panel) and the racial composition of public schools visited in the South (lower panel) by public research universities in our sample.
+Visited private high schools enrolled a much lower share of Black/Latinx/Native students than visited public high schools.
+For Emory, Northwestern, Tufts, Tulane, Case Western Reserve, and University of Denver, at least 75\% of visited private high schools enrolled less than 20\% Black/Latinx/Native students.
+
+Finally, Figure \ref{fig:south-race-pubu-privhs-pubhs} examines the racial composition of private high schools visited in the South (upper panel) and the racial composition of public high schools visited in the South (lower panel) by public research universities in our sample.
 Figure \ref{fig:south-race-privu-privhs-pubhs} does the same for selective private universities.
-These figures are motivated by the finding that many universities in our sample visited a large number of private schools in the South, where private school enrollment growth has been the strongest (Murnane \& Reardon, 2018).
-For public research universities, Figure \ref{fig:south-race-pubu-privhs-pubhs} shows that visited Southern private schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public schools.
+These figures are motivated by the finding that many universities in our sample visited a large number of private high schools in the South, where private high school enrollment growth has been the strongest (Murnane \& Reardon, 2018).
+For public research universities, Figure \ref{fig:south-race-pubu-privhs-pubhs} shows that visited Southern private high schools tended to enroll dramatically lower shares of Black/Latinx/Native students than visited Southern public high schools.
 This was true for all universities in our sample that visited a substantial number of schools in the South, and particularly for the University of Georgia, University of South Carolina, and University of Cincinnati.
-Quite simply, the racial composition of Southern private schools is dramatically different than the racial composition of Southern public schools and these differences are also reflected in schools that received visits.
+Quite simply, the racial composition of Southern private high schools is dramatically different than the racial composition of Southern public high schools and these differences are also reflected in schools that received visits.
 Results for private universities in Figure \ref{fig:south-race-privu-privhs-pubhs} are very similar, with Emory, Northwestern, and Case Western visiting private schools with a low share of Black/Latinx/Native students.
-Appendix Figures \ref{fig:south-race-comp-pubu-privhs-pubhs} and \ref{fig:south-race-comp-privu-privhs-pubhs} show the full racial composition of visited public and private schools in the South.
-For most universities that made a substantial number of visits in the South, white students comprised around 70\% of total enrollment at visited private schools compared to around 40\% at visited public schools.
+Appendix Figures \ref{fig:south-race-comp-pubu-privhs-pubhs} and \ref{fig:south-race-comp-privu-privhs-pubhs} show the full racial composition of visited public and private high schools in the South.
+For most universities that made a substantial number of visits in the South, white students comprised around 70\% of total enrollment at visited private high schools compared to around 40\% at visited public high schools.
 
@@
 For most public research universities in our sample, the scale and relative scale -- as a percentage of all HS visits -- of visits to private high schools were smaller than that of most selective private universities.
-However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \ref{fig:actual-proportional-pubu}) and the vast majority of these private school visits were to out-of-state private schools.
-Additionally, several public research universities -- University of Alabama, CU-Boulder, University of South Carolina -- visited private high schools at a scale that exceeded most private universities.
-
-Research question 2 asks about overlap in the private school recruiting networks of public and private universities.
+However, 13 of the 15 public universities visited a disproportionate number of private high schools (Figure \ref{fig:actual-proportional-pubu}) and the vast majority of these private high school visits were to out-of-state private high schools.
+Additionally, several public research universities -- University of Alabama, CU Boulder, University of South Carolina -- visited private high schools at a scale that exceeded most private universities.
+
+Research question 2 asks about overlap in the private high school recruiting networks of public and private universities.
 We observed substantial overlap and variation in the recruiting networks of public universities.
@@
 Both public and private universities in our sample tended to make a disproportionate number of visits in their home geographic region, with highly ranked universities making more visits to schools in other regions.
-The majority of universities -- even those located outside the South -- visited a large number of private schools located in the South.
+The majority of universities -- even those located outside the South -- visited a large number of private high schools located in the South.
 Unsurprisingly, sectarian private universities made a large share of visits to private high schools of a similar religious affiliation.
-Given that public universities are nonsectarian organizations, a surprising finding is that the majority of public universities in our sample made a large share of visits to Catholic or Christian private schools.
-
-With the exception of UC-Berkeley and UC-San Diego, the average academic rating of private schools visited by public universities was lower than the rating of those visited by most private universities.
+Given that public universities are nonsectarian organizations, a surprising finding is that the majority of public universities in our sample made a large share of visits to Catholic or Christian private high schools.
+
+With the exception of UC-Berkeley and UC-San Diego, the average academic rating of private high schools visited by public universities was lower than the rating of those visited by most private universities.
 This finding is largely explained by our analysis sample, which included public research universities regardless of rank but only included private universities ranked in the top 100 National University by U.S.
-News.
-Nevertheless, the large number of visits to low-rated private schools by public universities, combined with the fact that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private schools primarily in search of full-pay students rather than academic superstars.
+News and World Report.
+Nevertheless, the large number of visits to low-rated private high schools by public universities, combined with the fact that the overwhelming majority of these visits were to out-of-state schools, is consistent with the idea that many public flagship universities visit private high schools primarily in search of full-pay students rather than academic superstars.
 
 Across the universe of private high schools, most schools enroll relatively few students who identify as Black, Latinx, or Native.
-For the public and private universities in our sample, the set of visited private schools enrolled fewer Black, Latinx, and Native students than the national universe of private schools.
+For the public and private universities in our sample, the set of visited private high schools enrolled fewer Black, Latinx, and Native students than the national universe of private high schools.
 By contrast, the public high schools visited by public universities tended to enroll a much higher share of students who identify as Black, Latinx, or Native.
@@
 (2021) found that 12 universities made more out-of-state visits than in-state visits and visits to out-of-state public high schools focused on affluent, predominantly white schools.
-Public research universities have a financial incentive to target private school students, who tend to come from affluent households that are able to pay nonresident tuition price without need-based aid.
-This study extends the literature on nonresident students by analyzing the scale of visits to private schools, the overlap and divergence in recruiting networks between public and private universities, and the characteristics of visited private schools.
-
-We also engage with scholarship on linkages between private schools and private universities, a linkage that sociologists have observed for many decades.
-Private school students comprise a disproportionate share of enrollment at selective private universities (Author calculations based on HSLS:2009).
-Practically, these linkages exist because private schools want to send their students to ``good'' universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profiles and/or extracurricular activities (Stevens, 2007).
+Public research universities have a financial incentive to target private high school students, who tend to come from affluent households that are able to pay nonresident tuition price without need-based aid.
+This study extends the literature on nonresident students by analyzing the scale of visits to private high schools, the overlap and divergence in recruiting networks between public and private universities, and the characteristics of visited private high schools.
+
+We also engage with scholarship on linkages between private high schools and private universities, a linkage that sociologists have observed for many decades.
+Private high school students comprise a disproportionate share of enrollment at selective private universities (Author calculations based on HSLS:2009).
+Practically, these linkages exist because private high schools want to send their students to ``good'' universities while selective private universities want to enroll students who can pay private university tuition and who have desired academic profiles and/or extracurricular activities (Stevens, 2007).
 Prior research has often focused on linkages between elite private schools and elite universities (Chetty et al., 2023; Khan, 2011; Persell \& Cookson, 1985).
 Whereas elite universities (e.g., Princeton, Stanford) experience strong student demand based on reputation, merely selective private universities must incite demand by expending resources on recruiting.
-Prior research has not systematically analyzed connections between private schools and private universities that are selective, but not elite.
-Therefore, this study extends the literature by investigating private school visits for a sample of 14 selective private universities that exhibit variation in geographic location, religious affiliation, and ranking.
+Prior research has not systematically analyzed connections between private high schools and private universities that are selective, but not elite.
+Therefore, this study extends the literature by investigating private high school visits for a sample of 14 selective private universities that exhibit variation in geographic location, religious affiliation, and ranking.
 
@@
 Selective private universities have been recruiting heavily from private schools for a long time (Falsey \& Heyns, 1984; Persell \& Cookson, 1985; Stevens, 2007).
-By contrast, the pursuit of out-of-state private school students by public research universities is a relatively new phenomenon and represents competition in the traditional hunting grounds of selective private universities.
+By contrast, the pursuit of out-of-state private high school students by public research universities is a relatively new phenomenon and represents competition in the traditional hunting grounds of selective private universities.
 
 Our analyses shed light on the nature of this competition.
-When making decisions about which private schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
+When making decisions about which private high schools to visit, public research universities seem to be mimicking the behavior of particular private universities rather than mimicking the behavior of private universities writ large.
 Several public universities seem to be competing directly for students targeted by a particular private university.
@@
 
-However, public universities that made the greatest number of private school visits seemed to be targeting the lower-achieving students at private schools targeted by particular private universities.
-For example, the University of Alabama visited 52.2\% of the 625 private schools that Notre Dame visited, with most of the overlap at Catholic schools.
+However, public universities that made the greatest number of private high school visits seemed to be targeting the lower-achieving students at private high schools targeted by particular private universities.
+For example, the University of Alabama visited 52.2\% of the 625 private high schools that Notre Dame visited, with most of the overlap at Catholic schools.
 Given the differences in academic prestige between them, the University of Alabama may not be competing for the same students as Notre Dame.
 Instead, they seem to be targeting Catholic school students of a similar economic echelon, who have lower academic achievements, and want to attend a football powerhouse.
-Additionally, CU-Boulder visited 42.4\% of schools visited by Northwestern, which could be interpreted as CU-Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
+Additionally, CU Boulder visited 42.4\% of schools visited by Northwestern, which could be interpreted as CU Boulder competing for lower-achieving students of a similar economic and cultural echelon at the schools targeted by Northwestern.
 Similarly, the University of South Carolina competes heavily at schools targeted by Emory, SMU, TCU, and Tulane.
@@
 
-Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the Covid pandemic.
+Market research suggests that off-campus recruiting visits will remain a vital means of connecting to students and guidance counselors, just as they were prior to the COVID-19 pandemic.
 Ruffalo Noel-Levitz (2020a) found that ``travel'' was the top-ranked marketing/recruiting expenditure item for both public universities and private universities.
-During the height of Covid, off-campus recruiting visits ceased and were partially replaced by virtual counselor events (Ruffalo Noel-Levitz, 2020b).
+During the height of COVID-19, off-campus recruiting visits ceased and were partially replaced by virtual counselor events (Ruffalo Noel-Levitz, 2020b).
 Admissions counselors are now traveling again.
@@
 Consequently, the racial and socioeconomic composition of the schools that a university chooses to visit affects the racial and socioeconomic composition of the university.
-Our research on visits to public high schools (Salazar et al., 2021) and this study on visits to private schools find that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
+Our research on visits to public high schools (Salazar et al., 2021) and this study on visits to private high schools find that our sample of public research universities and selective private universities tend to focus their recruiting efforts on affluent and predominantly white schools and communities.
 Some universities may publicly proclaim a commitment to social mobility and privately pursue an intentional recruiting strategy that targets affluent schools and communities.

### 2024-03-31 scripts/acs_collect_via_API_tract.py

@@ -58,7 +58,7 @@ def get_data(region, headings, cols):
     url = 'https://api.census.gov/data/2017/acs/acs5'
 
     params = {
-        'key': 'ab3870e2d20fc643fefe2e23361c8c2d40fbd0e1',
+        'key': 'API_KEY',
         'for': 'tract:*',
         'in': 'state:{}'.format(region),
         'get': cols

### 2024-03-31 scripts/ccd_data_cleaning.R

@@ -1,936 +1,0 @@
-#Following Data Cleaning Guidelines
-
-# install.packages("tidyverse")
-# install.packages("tidyr")
-# install.packages("readr")
-# install.packages("lubridate")
-# install.packages("stringr")
-# install.packages("kableExtra")
-# install.packages("labelled")
-# install.packages("haven")
-# install.packages("stargazer")
-# install.packages("Hmisc")
-# install.packages("sjlabelled")
-# install.packages("assertthat")
-# install.packages("dplyr")
-
-
-library(tidyverse)
-library(tidyr)
-library(readr)
-library(lubridate)
-library(stringr)
-library(kableExtra)
-library(labelled)
-library(haven) 
-library(stargazer)
-library(Hmisc)
-library(sjlabelled)
-library(assertthat)
-library(dplyr)
-
-###CCD Data
-##Loading & investigating data: CCD School Directory Data for 2017-2018
-#Check working directory
-getwd()
-setwd("/Users/irmacastaneda/Documents/UCLA/GSR/recruiting-chapter")
-
-#Loading Data; Starting with public high school data
-hs_directory <- read.csv('./data/archive/ccd_school_directory_1718.csv', header = TRUE, na.strings=c("","NA"), colClasses = c('SCHOOL_YEAR' = "character", 'FIPST' = 'character', 'STATENAME' = 'character', 'ST' = 'character', 'SCH_NAME' = 'character', 'LEA_NAME' = 'character', 'STATE_AGENCY_NO' = 'character', 'UNION' = 'character', 'ST_LEAID' = 'character', 'LEAID' = 'character', 'ST_SCHID' = 'character', 'NCESSCH' = 'character', 'SCHID' = 'character', 
-                                                                                                                      'MSTREET1' = 'character', 'MSTREET2' = 'character', 'MSTREET3' = 'character', 'MCITY' = 'character', 'MSTATE' = 'character', 'MZIP' = 'character', 'MZIP4' = 'character', 'LSTREET1' = 'character', 'LSTREET2' = 'character', 'LSTREET3'= 'character', 'LCITY' = 'character', 'LSTATE' = 'character', 'LZIP' = 'character', 'LZIP4' = 'character',
[…]

### 2024-03-31 scripts/ccd_data_saving_membership.R

@@ -1,123 +1,0 @@
-library(tidyverse)
-library(readxl)
-
-
-data_dir <- file.path('.', 'data')
-
-
-# Read in directory data and dictionary (102337 obs. of 65 variables)
-ccd_directory <- read.csv(file.path(data_dir, 'ccd_directory_1718.csv'), header = TRUE, na.strings = c('', 'NA'), stringsAsFactors = F,  colClasses = c('FIPST' = 'character', 'LEAID' = 'character', 'NCESSCH' = 'character', 'SCHID' = 'character', 'MZIP' = 'character', 'MZIP4' = 'character', 'LZIP' = 'character', 'LZIP4' = 'character', 'SY_STATUS' = 'character', 'UPDATED_STATUS' = 'character', 'SCH_TYPE' = 'character', 'STATE_AGENCY_NO' = 'character', 'UNION' = 'character'))
-
-# Turn variables to lowercase
-names(ccd_directory) <- tolower(names(ccd_directory))
-
-
-# Read in characteristics data and dictionary (99899 obs. of 20 variables)
-ccd_characteristics <- read.csv(file.path(data_dir, 'ccd_characteristics_1718.csv'), header = TRUE, na.strings = c('', 'NA'), stringsAsFactors = F,  colClasses = c('FIPST' = 'character', 'LEAID' = 'character', 'NCESSCH' = 'character', 'SCHID' = 'character', 'STATE_AGENCY_NO' = 'character', 'UNION' = 'character'))
-
-# Turn variables to lowercase
-names(ccd_characteristics) <- tolower(names(ccd_characteristics))
-
-# Add virtual variable
-table(ccd_characteristics$virtual)
-table(ccd_characteristics$virtual_text)
-
-ccd_characteristics <- ccd_characteristics %>%
-  mutate(is_virtual = case_when(
-    virtual == 'NOTVIRTUAL' ~ 0,
-    virtual == 'Not reported' ~ NA_real_,
-    TRUE ~ 1  # FULLVIRTUAL, FACEVIRTUAL, SUPPVIRTUAL
-  ))
-
-table(ccd_characteristics$is_virtual, useNA = 'always')
-
-# Filter duplicate variables from directory (10 remaining variables)
-ccd_characteristics <- ccd_characteristics %>% 
-  select(ncessch, setdiff(names(ccd_characteristics), names(ccd_directory)))
-
-
[…]

### 2024-03-31 scripts/chicken_scratch/create_igraph_objects.R

@@ -1,852 +1,0 @@
-################################################################################
-##
-## [ PROJ ] Recruiting chapter for Stephen Burd
-## [ FILE ] igraph_recruiting.R
-## [ AUTH ] Ozan, Crystal, Irma
-## [ INIT ] July 1, 2020
-##
-################################################################################
-
-# CLEAR MEMORY
-rm(list = ls())
-
-options(max.print=2000)
-
-## ---------------------------
-## libraries
-## ---------------------------
-
-library(igraph)
-library(tidyverse)
-library(Hmisc)
-library(labelled)
-library(haven)
-
-## ---------------------------
-## Read in csv data; load R data
-## ---------------------------
-
-
-# read in hs data; has data on both publics and privates
-  #hs_data <- read.csv('./data/hs_data.csv', header = TRUE, na.strings='', colClasses = c('school_type' = 'character', 'ncessch' = 'character', 'state_code' = 'character', 'zip_code' = 'character'))
-  #hs_data %>% count(school_type)
-
-# read in zip_code level data
-  zip_data <- read.csv('./data/zip_to_state.csv', header = TRUE, na.strings='', colClasses = c('state_code' = 'character', 'zip_name' = 'character', 'zip_code' = 'character'))
-
-# merge hs school-level data to zipcode-level data  
-  #data <- full_join(hs_data, zip_data, by = 'zip_code')
-  
-# load 2017-2018 PSS data
-  load(file = "./data/pss_1718.RData")
-  class(privatehs)
-  glimpse(privatehs)
-  
-  #remove variables we definitely won't use
-  privatehs <- privatehs %>% select(-starts_with("rep"),-starts_with("f_"))
-  
-    #privatehs %>% var_label() # variable labels
-    #privatehs %>% val_labels() # variable labels
-  
-  # university data  
-
-#read in data on visits by universities; one obs per university-event
-
-  #events <- read.csv('./data/events_data.csv', header = TRUE, na.strings='', colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character'))
-  events <- read.csv('./data/events_data_2020-07-27.csv', header = TRUE, na.strings='', colClasses = c('univ_id' = 'character', 'univ_id_req' = 'character', 'school_id' = 'character')) %>% as_tibble()
-
-
-
-# Create data frame of events at private high schoools
-  privhs_events <- events %>% filter(event_type == "priv_hs") %>% 
[…]

### 2024-03-31 scripts/chicken_scratch/figuring-out-how-to-do-cluster_fast_and_greedy.R

@@ -1,114 +1,0 @@
-library(igraph)
-library(tidyverse)
-
-options(max.print=2000)
-## -------------
-## LOAD OBJECTS
-## -------------
-
-# Run create_igraph_objects.R
-scripts_dir <- file.path('.', 'scripts')
-source(file = file.path(scripts_dir, 'create_igraph_objects.R'))
-
-
-
-library(ape)  
-
-#bipartite.projection(g_2mode_privu)[["proj2"]] %>% cluster_fast_greedy() %>% membership()
-
-vertex_attr_names(bipartite.projection(g_2mode)[["proj2"]])
-
-edge_attr_names(bipartite.projection(g_2mode)[["proj2"]])
-edge_attr_names(g_1mode_psi)
-
-ecount(bipartite.projection(g_2mode)[["proj2"]])
-ecount(g_1mode_psi)
-
-
-as_adjacency_matrix(
-  graph = bipartite.projection(g_2mode)[["proj2"]],  # creates one-mode object w/ mode = universities
-  sparse = FALSE, 
-  attr = 'weight'
-)
-affil_1mode_psi %>% str()
-
-
-E(bipartite.projection(g_2mode)[["proj2"]])$weight
-E(g_1mode_psi)$weight
-
-bipartite.projection(g_2mode)[["proj2"]]
-
-c_obj <- cluster_fast_greedy(
-  graph = bipartite.projection(g_2mode)[["proj2"]],
-  merges = TRUE,
-  modularity = TRUE,
-  membership = TRUE,
-  weights = E(bipartite.projection(g_2mode)[["proj2"]])$weight
-)
-
-c_obj %>% membership()
-
-
-# investigating communities object
-c_2mode <- bipartite.projection(g_2mode)[["proj2"]] %>% cluster_fast_greedy() 
-c_2mode %>% membership() %>% table()
-c_2mode %>% str()
-
-c_2mode$merges %>% str()
-c_2mode$modularity %>% str()
-
-c_2mode %>% str()
-c_2mode %>% class()
-
-c_2mode %>% cut_at(steps = 41) %>% table()
-
-bipartite.projection(g_2mode_pubu)[["proj2"]] %>% cluster_fast_greedy() %>% cut_at(steps = 16) %>% table()
-
-cut_2mode <- c_2mode %>% cut_at(no = 2)
-cut_2mode %>% str()
-
-
[…]

### 2024-03-31 scripts/chicken_scratch/figuring-out-how-to-do-hierarchical-cluster-analysis.R

@@ -1,229 +1,0 @@
-library(igraph)
-library(tidyverse)
-
-options(max.print=2000)
-## -------------
-## LOAD OBJECTS
-## -------------
-
-# Run create_igraph_objects.R
-scripts_dir <- file.path('.', 'scripts')
-source(file = file.path(scripts_dir, 'create_igraph_objects.R'))
-
-
-
-## ------------------------------
-## PLAYING WITH COMMUNITY DETECTION
-## ------------------------------
-
-g_2mode
-
-# function igraph::as_incidence_matrix "This function can return a sparse or dense incidence matrix of a bipartite network. The incidence matrix is an n times m matrix, n and m are the number of vertices of the two kinds."
-as_incidence_matrix(
-  graph = g_2mode,
-  types = NULL,
-  attr = NULL,
-  names = TRUE,
-  sparse = FALSE
-) %>% str()
-
-# creates data frame where each observation is a college/university and each variable is a high school ID
-df_temp_univ <- as_incidence_matrix(
-  graph = g_2mode,
-  types = NULL,
-  attr = NULL,
-  names = TRUE,
-  sparse = FALSE
-) %>% t() %>% as.data.frame(
-  row.names = NULL, 
-  optional = FALSE,
-  make.names = TRUE,
-  stringsAsFactors = FALSE
-)
-
-df_temp_univ %>% dim() # 43 obs, 1742 variables
-
-# try performing principal component analysis on object
-pca_univ <- prcomp(
-  x = df_temp_univ, 
-  retx = TRUE, # a logical value indicating whether the rotated variables should be returned. default TRUE
-  center = TRUE, # a logical value indicating whether the variables should be shifted to be zero centered. default TRUE. Alternately, a vector of length equal the number of columns of x can be supplied. The value is passed to scale.
-  scale. = TRUE, # a logical value indicating whether the variables should be scaled to have unit variance before the analysis takes place. The default is FALSE for consistency with S, but in general scaling is advisable
-  tol = NULL, # a value indicating the magnitude below which components should be omitted. (Components are omitted if their standard deviations are less than or equal to tol times the standard deviation of the first component.) With the default null setting, no components are omitted (unless rank. is specified less than min(dim(x)).)
[…]

### 2024-03-31 scripts/chicken_scratch/igraph_ego_network_chicken_scratch.R

@@ -1,254 +1,0 @@
-################################################################################
-##
-## [ PROJ ] Recruiting chapter for Stephen Burd
-## [ FILE ] igraph_recruiting.R
-## [ AUTH ] Ozan, Crystal, Irma
-## [ INIT ] July 1, 2020
-##
-################################################################################
-
-# CLEAR MEMORY
-rm(list = ls())
-
-options(max.print=2000)
-
-## ---------------------------
-## libraries
-## ---------------------------
-
-library(igraph)
-library(tidyverse)
-library(Hmisc)
-library(labelled)
-library(haven) 
-
-
-
-      summary(E(egos_psi[[2]])$order)
-      print(edge_attr_names(egos_psi[[43]]))
-      edge_attr_names(egos_psi[[43]])
-      
-      print(table(E(egos_psi[[2]])$order))
-      
-      E(egos_psi[[i]])$order <- if_else(str_detect(string = attr(x = E(ego_uarkansas), which = "vnames"), pattern ="106397"),1,2)      
-      
-      str(attr(x = E(ego_uarkansas), which = "vnames"))
-      
-      str_detect(string = attr(x = E(egos_psi[[2]]), which = "vnames"), pattern =names(egos_psi)[[2]])
-      
-      summary(str_detect(string = attr(x = E(egos_psi[[2]]), which = "vnames"), pattern =names(egos_psi)[[2]]))
-      summary(str_detect(string = attr(x = E(egos_psi[[2]]), which = "vnames"), pattern ="106397"))
-      
-      class(E(egos_psi[[2]]))
-      
-      names(egos_psi)[[2]]
-      str(names(egos_psi)[[2]])
-      
-  # Create separate object for u arkansas ego network
-    ego_uarkansas <- egos_psi[["106397"]]
-
-    # see if you can create an edge attribute that is order of the network
-      ego_uarkansas
-      vcount(ego_uarkansas)
-      ecount(ego_uarkansas)
-      as.integer(E(ego_uarkansas))
-      str(E(ego_uarkansas))
-      
-      attr(x = E(ego_uarkansas), which = "vnames")
-      str(attr(x = E(ego_uarkansas), which = "vnames"))
-      #edge where the attribute name of the edge contains "100751"
-
[…]

### 2024-03-31 scripts/chicken_scratch/igraph_recruiting_practice_oj.R

@@ -1,2036 +1,0 @@
-
-
-################################################################################
-##
-## [ PROJ ] < Burd recruiting chapter >
-## [ FILE ] < igraph_recruiting_practice_oj.R >
-## [ AUTH ] < Ozan Jaquette / ozanj >
-## [ INIT ] < 9/4/2020 >
-##
-################################################################################
-
-rm(list = ls())
-
-options(max.print=9999)
-
-## ---------------------------
-## libraries
-## ---------------------------
-
-library(igraph)
-library(tidyverse)
-library(Hmisc)
-
-## ---------------------------
-## directory paths
-## ---------------------------
-
-getwd()
-list.files()
-
-data_dir <- file.path(".", "data")
-scripts_dir <- file.path(".", "scripts")
-
-
-## ---------------------------
-## Run script that creates igraph objects
-## ---------------------------
-
-#file.path(scripts_dir,"create_igraph_objects.R")
-source(file = file.path(scripts_dir,"create_igraph_objects.R"))
-
-###########################
-###########################
-
-## ---------------------------
-## Practice network visualization
-## ---------------------------
-
-# resources I am drawing from:
-  # Bipartite/Two-Mode Networks in igraph by Phil Murphy & Brendan Knapp
-    # https://rpubs.com/pjmurphy/317838
-  # ?plot.igraph
-  # igraph manual on plotting
-    # ?igraph.plotting
-
-
-# igraph approaches for visualization
-    # ?plot.igraph
-    # igraph manual on plotting
-      # ?igraph.plotting
-
-# syntax for plot.igraph:
-  # plot(x, axes = FALSE, add = FALSE, xlim = c(-1, 1), ylim = c(-1, 1), mark.groups = list(), mark.shape = 1/2,
-    #mark.col = rainbow(length(mark.groups), alpha = 0.3),mark.border = rainbow(length(mark.groups), alpha = 1), mark.expand = 15, ...)
-
-# Three ways to give values to the parameters of the plot functions
-  # 1. supply named arguments to the plotting commands
-  # 2. assign vertex, edge, and graph attributes to the graph
-    # The second way is to assign vertex, edge and graph attributes to the graph. These attributes have no prefix, ie. the color of the vertices is taken from the color vertex attribute and the color of the edges from the color edge attribute. 
-  # 3. igraph_options
[…]

### 2024-03-31 scripts/chicken_scratch/network_recruiting_analysis_scratch.R

@@ -1,433 +1,0 @@
-################################################################################
-##
-## [ PROJ ] < Burd recruiting chapter >
-## [ FILE ] < network_recruiting_analysis.R >
-## [ AUTH ] < Ozan Jaquette / ozanj >
-## [ INIT ] < 9/4/2020 >
-##
-################################################################################
-
-rm(list = ls())
-
-options(max.print=9999)
-
-## ---------------------------
-## libraries
-## ---------------------------
-
-library(igraph)
-library(tidyverse)
-library(Hmisc)
-
-## ---------------------------
-## directory paths
-## ---------------------------
-
-getwd()
-list.files()
-
-data_dir <- file.path(".", "data")
-scripts_dir <- file.path(".", "scripts")
-
-
-## ---------------------------
-## Run script that creates igraph objects
-## ---------------------------
-
-#file.path(scripts_dir,"create_igraph_objects.R")
-source(file = file.path(scripts_dir,"create_igraph_objects.R"))
-
-# save one of the igraph objects for use as an example in rclass1
-#g_2mode_privu
-
-save(g_2mode_privu, file = "data/g_2mode_privu.rda")
-
-#g_2mode_privu
-#rm(g_2mode_privu)
-#load("data/g_2mode_privu.rda")
-
-## ---------------------------
-## Visits by private colleges and universities to private high schools
-## ---------------------------
-
-# objects wi will potentially use for analyses
-
-  g_2mode_privu # 2-mode object, only visits by private colleges and universities
-  g_1mode_hs_privu # 1 mode object, nodes = private high schools that received at least one visit from a private college/university
-  g_1mode_psi_privu  # 1 mode object, nodes = private colleges/universities
-  
-  egos_psi_privu %>% length() # object that has one element per ego network for each private university
-    # egos_psi_privu[["139658"]] # emory university
-
-  egos_hs_privu %>% length() # object that has one element per ego network for each private high school
-  
-
-  # plotting ego network of emory university
-    plot.igraph(
-      x = egos_psi_privu[["139658"]], # egos_psi[["106397"]] = uarkansas
-      #vertex.label = "",
[…]

### 2024-03-31 scripts/chicken_scratch/network_recruiting_analysis_v1.R

@@ -1,876 +1,0 @@
-library(igraph)
-library(tidyverse)
-
-options(max.print=2000)
-## -------------
-## LOAD OBJECTS
-## -------------
-
-# Run create_igraph_objects.R
-scripts_dir <- file.path('.', 'scripts')
-source(file = file.path(scripts_dir, 'create_igraph_objects.R'))
-
-# Summary of objects (1742 private HS + 43 univs = 1785 vertices total)
-  # 2-mode igraph objects
-    # g_2mode (1785 vertices + 11034 edges)
-    # g_2mode_privu (1356 vertices + 7310 edges)
-    # g_2mode_pubu (1481 vertices + 3724 edges)
-  # 1-mode igraph objects [HS]
-    # g_1mode_hs (1742 vertices + 745145 edges)
-    # g_1mode_hs_privu (1330 vertices + 520723 edges)
-    # g_1mode_hs_pubu (1464 vertices + 448865)
-  # 1-mode igraph objects [PSI]
-    # g_1mode_psi (43 vertices + 897 edges)
-    # g_1mode_psi_privu (26 vertices + 325 edges)
-    # g_1mode_psi_pubu (17 vertices + 130 edges)
-  # Ego igraph objects [HS]
-    # egos_hs (1742 ego graphs)
-    # egos_hs_privu (1330 ego graphs)
-    # egos_hs_pubu (1464 ego graphs)
-  # Ego igraph objects [PSI]
-    # egos_psi (43 ego graphs)
-    # egos_psi_privu (26 ego graphs)
-    # egos_psi_pubu (17 ego graphs)
-
-
-## --------------------
-## EGO IGRAPH FUNCTION (can utilize order =1, order =2, or both)
-## --------------------
-
-
-plot_ego_graph <- function(univ_id, characteristic, values, keys, colors = c('lightblue', 'lightgreen', 'violet', 'yellow'), title = univ_info[univ_info$univ_id == univ_id, ] %>% select(univ_abbrev) %>% as.character(), graph_order = 'both', margin = 0) {
-
-  network <- egos_psi_privu[[univ_id]]
-    
-  # network object
-  if (graph_order != 'both') {  # order == 1 or 2
-    network <- subgraph.edges(graph = network, eids = E(network)[E(network)$order == graph_order]) # create subgraph network object if order != "both"
-  }
-
-  # Vertex color  
-    if (is.na(characteristic)==TRUE & graph_order %in% c(1,2)  ) { # no characteristics; order = 1 or 2
[…]

### 2024-03-31 scripts/chickent_scratch_4_27_2021.R

@@ -1,55 +1,0 @@
-univ_df %>% glimpse()
-
-univ_info %>% glimpse()
-
-univ_info %>% count(control)
-
-univ_info %>% filter(control != "Public") %>% count(classification)
-
-univ_info %>% filter(control != "Public", classification == 'private_libarts') %>% arrange(univ_name) %>% select(univ_name)
-
-univ_info %>% filter(control != "Public", classification == 'private_national') %>% arrange(univ_name) %>% select(univ_name)
-
-
-
-univ_info %>% filter(control == "Public") %>% count(classification)
-
-
-univ_info %>% filter(control == "Public", classification == 'public_research') %>% arrange(univ_name) %>% select(univ_name)
-
-#####
-
-
-univ_info %>% left_join(y=univ_df, by = c('univ_id' = 'school_id')) %>% glimpse()
-
-# Investigate characteristics of public research; region
-univ_df %>% 
-  select(school_id,region,religion,ranking,ranking_numeric) %>% 
-  right_join(y=univ_info, by = c('school_id' = 'univ_id')) %>% 
-  filter(classification != 'private_libarts') %>% 
-  filter(control == 'Public') %>% count(region)
-
-# investigate number of universities by control and region; don't have good coverage of "west" for private research universities
-univ_df %>% 
-  select(school_id,region,religion,ranking,ranking_numeric) %>% 
-  right_join(y=univ_info, by = c('school_id' = 'univ_id')) %>% 
-  filter(classification != 'private_libarts') %>% 
-  group_by(region) %>% count(control)
-  
-  
-# religion: pretty good mix of religion for private research universities
-
-univ_df %>% 
-  select(school_id,region,religion,ranking,ranking_numeric) %>% 
-  right_join(y=univ_info, by = c('school_id' = 'univ_id')) %>% 
-  filter(classification != 'private_libarts') %>% 
-  group_by(control) %>% count(religion)
-
-
-##############
-############## PRIVATE HIGH SCHOOL CHARACTERISTICS THAT MAY BE OF INTEREST
-##############
-
-privhs_data %>% glimpse()
-
-privhs_data %>% select(school_type,community_type,locale_code) %>% val_labels()

### 2024-03-31 scripts/pss_data_cleaning.R

@@ -1,712 +1,0 @@
-library(tidyverse)
-#library(tidyr)
-#library(readr)
-#library(lubridate)
-#library(stringr)
-#library(kableExtra)
-library(labelled)
-library(haven) 
-#library(stargazer)
-library(Hmisc)
-#library(sjlabelled)
-library(assertthat)
-#library(dplyr)
-
-
-
-###PSS Data
-##Loading & investigating data: PSS (private school data)
-privatehs <- read.csv('./data/pss_1718.csv', header = TRUE, na.strings=c("","NA"), stringsAsFactors=F, colClasses = c('pzip'='character', 'pzip4' = 'character', 'pl_zip' = 'character', 'pl_zip4' = 'character', 'ppin' = 'character')) 
-
-#Investigate the data & data frame
-str(privatehs)
-
-nrow(privatehs) #num of rows: 22,895 observations
-ncol(privatehs) #num of columns: 349 variables
-
-names(privatehs) # variable names 
-names(privatehs) <- tolower(names(privatehs)) #convert to lowercase
-glimpse(privatehs)
-head(privatehs) # prints first 6 obs
-
-privatehs %>% arrange(p270,p280,p290,p300, p305,p320,p330,p325,p316,p318,p310,p332) %>% head()
-
-
-##Labeling variables 
-#Importing data dictionary
-pss_dictionary <- read.csv('./data/pss_dictionary_1718.csv', header = TRUE, na.strings=c("","NA"))  
-pss_dict_subset <- pss_dictionary %>% select(Name, Label)
-
-#Lowercase variable names in dictionary
-names(pss_dict_subset) <- tolower(names(pss_dict_subset))
-pss_dict_subset<- pss_dict_subset %>% mutate(names_lc = tolower(name))
-  #str(pss_dict_subset) # dataframe w/ 349 obs and 3 vars; 
-    #vars = name (var name); label (variable label); names_lc (lower case variable name)
-
-#Loop to label data with dictionary
-for (i in names(privatehs)) { 
-  #description4 <- (pss_dict_subset %>% filter(names_lc == i))$label 
-  description4 <- (pss_dict_subset %>% filter(names_lc == i))$label %>% as.character()
-  var_label(privatehs[[i]]) <- description4 #label variables
-}
-
-#Check variable labels
-privatehs %>% var_label() # variable labels
-
-#Adding value labels
[…]

### 2024-03-31 scripts/pss_data_saving.R

@@ -2,225 +2,149 @@ library(tidyverse)
 library(labelled)
 
 
-# Read in data and dictionary (22895 obs. of 349 variables)
-pss <- read.csv('./data/pss_1718.csv', header = TRUE, na.strings = c('', 'NA'), stringsAsFactors = F,  colClasses = c('PZIP' = 'character', 'PSTANSI' = 'character', 'PCNTY' = 'character'))
-pss_dictionary <- read.csv('./data/pss_dictionary_1718.csv', header = TRUE, na.strings=c('', 'NA'), stringsAsFactors = F)
+pss_vars <- c(
+  # directory info
+  'ppin', 'pinst', 'paddrs', 'pl_add', 'pcity', 'pstabb', 'pzip', 'p415',
+  # offered/enrolled grades 09-12
+  'p265', 'p270', 'p275', 'p280', 'p285', 'p290', 'p295', 'p300',
+  # total students and by gender and race
+  'numstuds', 'p330', 'p325', 'p320', 'p316', 'p310', 'p318', 'p332',
+  # percent students by race
+  'p_white', 'p_black', 'p_hisp', 'p_asian', 'p_indian', 'p_pacific', 'p_tr',
+  # religious affiliation and associations
+  'p430', 'p440', 'p455', 'p460', 'p465', 'p520',
+  # additional info
+  'males', 'p360', 'region', 'ucommtyp'
+)
 
-# Turn variables to lowercase
-names(pss) <- tolower(names(pss))
-names(pss_dictionary) <- tolower(names(pss_dictionary))
-pss_dictionary <- pss_dictionary %>% mutate(names_lc = tolower(name))
+pss_vars_root <- c('ulocale', 'latitude', 'longitude')  # variables w/ suffixes based on year
 
-# Use 0=No/1=Yes instead of 1=Yes/2=No (ie. change the 2 to 0)
-pss <- pss %>% mutate(p265 = ifelse(p265 == 1, 1, 0),
-                      p275 = ifelse(p275 == 1, 1, 0),
-                      p285 = ifelse(p285 == 1, 1, 0),
-                      p295 = ifelse(p295 == 1, 1, 0),
-                      p430 = ifelse(p430 == 1, 1, 0))
+pss_years <- c('1718', '1516', '1314')
 
-# Pad leading 0's
-pss <- pss %>% mutate(pstansi = str_pad(pstansi, 2, 'left', '0'))
 
-# Label variables
-for (i in names(pss)) { 
[…]

### 2024-03-31 scripts/pss_data_saving_batch.R

@@ -1,190 +1,0 @@
-library(tidyverse)
-library(labelled)
-
-
-pss_vars <- c(
-  # directory info
-  'ppin', 'pinst', 'paddrs', 'pl_add', 'pcity', 'pstabb', 'pzip', 'p415',
-  # offered/enrolled grades 09-12
-  'p265', 'p270', 'p275', 'p280', 'p285', 'p290', 'p295', 'p300',
-  # total students and by gender and race
-  'numstuds', 'p330', 'p325', 'p320', 'p316', 'p310', 'p318', 'p332',
-  # percent students by race
-  'p_white', 'p_black', 'p_hisp', 'p_asian', 'p_indian', 'p_pacific', 'p_tr',
-  # religious affiliation and associations
-  'p430', 'p440', 'p455', 'p460', 'p465', 'p520',
-  # additional info
-  'males', 'p360', 'region', 'ucommtyp'
-)
-
-pss_vars_root <- c('ulocale', 'latitude', 'longitude')  # variables w/ suffixes based on year
-
-pss_years <- c('1718', '1516', '1314')
-
-
-for (pss_year in pss_years) {
-  end_year <- str_sub(pss_year, start = 3)
-  
-  # Read in data and dictionary
-  pss <- read.csv(str_c('./data/pss_', pss_year,'.csv'), header = TRUE, na.strings = c('', 'NA'), stringsAsFactors = F,  colClasses = c('PZIP' = 'character', 'pzip' = 'character'))
-  pss_dictionary <- read.csv(str_c('./data/pss_dictionary_', pss_year, '.csv'), header = TRUE, na.strings=c('', 'NA'), stringsAsFactors = F)
-  
-  # Turn variables to lowercase
-  names(pss) <- tolower(names(pss))
-  names(pss_dictionary) <- tolower(names(pss_dictionary))
-  pss_dictionary <- pss_dictionary %>% mutate(names_lc = tolower(name))
-  
-  # Select variables of interest
-  pss <- pss %>% select(c(all_of(pss_vars), str_c(pss_vars_root, end_year)))
-  
-  # Use 0=No/1=Yes instead of 1=Yes/2=No (ie. change the 2 to 0)
-  pss <- pss %>% mutate(p265 = ifelse(p265 == 1, 1, 0),
-                        p275 = ifelse(p275 == 1, 1, 0),
-                        p285 = ifelse(p285 == 1, 1, 0),
-                        p295 = ifelse(p295 == 1, 1, 0),
[…]

### 2024-03-31 scripts/test_layout.R

@@ -1,46 +1,0 @@
-library(igraph)
-
-
-# Get ending coordinates
-coords_kk <- layout_with_kk(g_1mode_pubu_psi)  # kk layout stays the same each time we run it
-coords_fr <- layout_with_fr(g_1mode_pubu_psi)  # fr changes each time we run it
-
-plot(g_1mode_pubu_psi, layout = layout_with_kk)
-plot(g_1mode_pubu_psi, layout = coords_kk)  # equivalent
-
-# Move x-coordinate for 100751 (originally at top right of plot) even more to the right
-coords_kk[1, 1]
-coords_kk[1, 1] <- 5
-
-plot(g_1mode_pubu_psi, layout = layout_with_kk)  # original
-plot(g_1mode_pubu_psi, layout = coords_kk)  # 100751's x-coordinate moved from 2.543199 to 5
-
-# Specifying starting positions for vertices is option for layout_with_fr
-# coords: Optional starting positions for the vertices. If this argument is not NULL then it should be an appropriate matrix of starting coordinates.
-?layout_with_fr
-
-# If we use layout_with_fr, the plot changes each time we run it
-plot(g_1mode_pubu_psi, layout = layout_with_fr)
-
-# Try plotting using coords_kk as starting coords 
-# Plot still changes a lot each time we run it - hard to see effect of specifying starting coords
-plot(g_1mode_pubu_psi, layout = layout_with_fr(g_1mode_pubu_psi, coords = coords_kk))
-
-# Try testing different starting coords to see how it's affecting layout_with_fr
-# Below coordinates will make vertices vertically aligned
-starting_coords <- matrix(c(rep(0, 15), -5:9), ncol = 2)
-
-# Test coordinates on layout_with_kk since it doesn't change each time
-# Note that vertices are not evenly spaced along vertical line - suggesting kk layout moved it from this starting position
-plot(g_1mode_pubu_psi, layout = layout_with_kk(g_1mode_pubu_psi, coords = starting_coords))
-
-# Right now the script had coords specified for plot, which I don't think would have any effect
-plot(g_1mode_pubu_psi, layout = layout_with_kk, coords = starting_coords)
-
-# Test coordinates on layout_with_fr - results change every time
-# Sometimes, we can see more clearly how vertices line up vertically, suggesting that starting coordinates was used, but the fr layout moved it a lot more afterwards
[…]
